### 2014-07-29 text/RoaM_abstract/abstract.tex
inital export

\documentclass[10pt]{article}

\usepackage[style=authoryear-comp, % Citation marks as [Jef65]
            natbib=true,      % Natbib-style cite macros \citeauthor &c.
            hyperref=true,    % Cites in pdf are links to bib
                              % (hyperref conf.)
            maxnames=3,       % truncate name lists if more than 2
                              % names appear
            doi=false,        % no doi's
            url=false,        % no url's
            sortcites=false,  % do NOT sort cites in the style of the
                              % bibliography 
            %backref=true     % insert backrefs in reference section
            ]{biblatex}
\bibliography{MyRefGlobal}

\usepackage{amsfonts}
\usepackage{dsfont}

% \usepackage[colorinlistoftodos,color=lightgray,bordercolor=blue,textsize=footnotesize]{todonotes}

% \usepackage{setspace}
% \doublespacing
\usepackage[left=3.75cm,right=3.75cm,top=3.75cm,bottom=3.75cm]{geometry}

\title{On the Evolution of Choice Principles}
\author{}
\date{}

\begin{document}

\begin{center}
  \begin{large}
    On the Evolution of Choice Principles
  \end{large}
\end{center}

\noindent The widely accepted normative standard of individual decision making
under uncertainty is expected utility maximization. An agent is
rational only if his choices maximize expected utility. In games with
several players, agents who believe that their opponents are rational
might thus rule out certain of the opponents' choices. This kind of
reasoning can be iterated, giving rise to predictions of rational
choice under arbitrarily deep nestings of mutual beliefs in
rationality. % Depending on the detailed specification of what it means
% to have a belief in the opponents' rationality, and to respond
% rationally to such beliefs, standard game-theoretic solution concepts
% are characterized by this nested Theory of Mind reasoning, most
% notably the iterated deletion of strongly dominated strategies in
% strategic games \citep[e.g.][for
% overview]{Perea2012:Epistemic-Game-}.

Empirical data on human solitary or interactive decision-making is at
odds with this idealized picture. For one, human decision makers
systematically deviate from the predictions of expected utility theory
\citep[e.g.][]{TverskyKahnemann1974:Judgement-under,TverskyKahnemann1981:The-Framing-of-}. For
another, human capability for higher-order Theory of Mind (ToM)
reasoning appears to be rather limited \citep[e.g.][inter
alia]{HoCamerer1998:Iterated-Domina,KeyzarLin2003:Limits-on-Theor,VerbruggeMol2008:Learning-to-App,DegenFranke2013:Cost-Based-Prag}.

The usual reactions to this discrepancy between idealized norm and
empirical observation is to either rethink the prescriptive axioms of
rational choice or, alternatively, to devise a descriptive theory to
capture the empirical facts of human psychology of decision-making and
strategic reasoning
\citep[e.g.][]{Camerer2003:Behavioral-Game,GlimcherCamerer2009:Neuroeconomics:}. The
approach taken here is different from either. We refer to a general
decision making rule as a \emph{choice principle}. Formally, a choice
principle is a function that takes a game as input and returns a set
of acts as the decision maker's choice. We then adopt an evolutionary
point of view and ask: which choice principles are successful on
average in recurrent competition with alternative choice principles
(including more or less limited ToM reasoning)?

\citet{Weerdde-WeerdVerbrugge2013:How-much-does-i} address a part of
this question by looking at agent-based simulations of utility
maximizers with different ToM reasoning capabilities when playing
repeatedly selected zero-sum games against each other. The simulations
of \citeauthor{Weerdde-WeerdVerbrugge2013:How-much-does-i} suggest
that there is a benefit to deeper ToM reasoning only up to a fairly
limited depth of reasoning.

Extending and generalizing this line of investigation, we use
numerical simulations to approximate the expected payoff of agents
with a fixed choice principle who play many \emph{arbitrary} 2-player
strategic games, not just a small hand-picked selection. This way we
try to asses the general evolutionary benefit of a choice principle
across an unbiased sample of games, not just for those games that are
of particular technical, philosophical or historical
importance. Additionally, we compare not only different ToM reasoning
capability of utility maximizers, but also variation in the underlying
method of choice. Concretely, we look at level-$k$ utility
maximization and level-$k$ iterated regret minimization (IRM)
\citep{HalpernPass2012:Iterated-Regret}.\footnote{Unlike
  \citeauthor{Weerdde-WeerdVerbrugge2013:How-much-does-i}, we look at
  level-$k$ reasoning models
  \citep[e.g.][]{Crawford2003:Lying-for-Strat,Crawford2007:Lets-Talk-It-Ove},
  not cognitive hierarchy models
  \citep[e.g.][]{CamererHo2004:A-Cognitive-Hie}. The former assume
  that agents of level $k+1$ believe that the opponent is of level
  $k$, while the latter assume a belief in a level-$l$ opponent with
  $l \le k$. Moreover, we assume all games to be one-shot encounters,
  while \citeauthor{Weerdde-WeerdVerbrugge2013:How-much-does-i} look
  at repeated encounters with the same opponent, and the concomitant
  possibility of strategic learning.}  The motivation for looking at
IRM is threefold. For one, regret minimization has been suggested as a
conceptually appealing alternative to utility maximization and a
potentially promising descriptive theory of individual decision-making
\citep{LoomesSugden1982:Regret-Theory:-}. For another, we are able to
show that non-iterated regret minimization outperforms the closely
related MaxiMin security strategy (see below) in evolutionary settings
like the one investigated here, making regret minimization the
evolutionarily best representative of a security strategy that we are
aware of.\footnote{More concretely, so far we have been able to prove
  this result for the class of 2-player symmetric games, and to
  demonstrate that it holds more generally using numerical simulations
  like the one reported here.} Finally, IRM usually requires only few
iteration steps, making it a serious challenger of the standard theory
in terms of limited ToM reasoning as well
\citep[c.f.][]{HalpernPass2012:Iterated-Regret}.

The choice principles we compare are defined as follows. L-0 utility
maximizers have an arbitrary probabilistic belief about the opponent's
behavior and are indifferent between any act that maximizes expected
utility under this belief. L-$k+1$ utility maximizers have an
arbitrary probabilistic belief over all acts that an L-$k$ opponent
would be indifferent about. Formally, if $U$ is a matrix of utilities
for the row player, regret minimization is equivalent to playing
MaxiMin on the derived matrix $U'$, where $U'_{ij} = U_{ij} -
\textrm{max}_{k} U_{kj}$ is the negative regret of choosing act $i$
when the opponent chooses $j$. L-0 regret minimizers are indifferent
between any act that minimizes regret in this sense. An L-$k+1$ regret
minimizer chooses like an L-0 regret minimizer in the reduced game in
which only acts remain that row and column players would choose that
are L-$k$ regret minimizers
\citep[see][]{HalpernPass2012:Iterated-Regret}.

We randomly generate arbitrary strategic games and record the payoff
earned by each choice principle when playing against any other,
including itself. In general, the details of generating arbitrary
games are important to this approach. Some choice principles might be
better in certain classes of games, but not others. For that reason,
we used several algorithms for creating games that are as unbiased and
neutral as possible. We choose neutrality in the selection of games,
because we have at present no better answer to the main empirical
question that is relevant here, namely which kinds of interactive
decision-making situations were most frequent during the critical
stages of cognitive development. For illustration, this abstract
focuses on the results of a simple generic algorithm for constructing
arbitrary asymmetric strategic games with 2 players. The procedure
starts by first picking a random number between 2 and 10 as the number
of acts for each player, say $n$ and $m$. Then, we determine each
entry in the $n \times m$ and $m \times n$ utility matrices of each
player as an integer between 0 and 10, all independently and uniformly
at random.

\begin{table}
  \centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & EU-L0 & EU-L1 & EU-L2 & EU-L3 & EU-L4 & RM-L0 & RM-L1 & RM-L2 \\ 
  \hline
  EU-L0 & 6.754 & 6.764 & 6.729 & 6.889 & 6.790 & 6.747 & 6.767 & 6.767  \\ 
  EU-L1 & 7.155 & 6.696 & 6.666 & 6.609 & 6.949 & 7.004 & 7.072 & 7.071  \\ 
  EU-L2 & 6.692 & 7.412 & 6.959 & 6.850 & 6.973 & 6.457 & 6.554 & 6.556  \\ 
  EU-L3 & 6.707 & 7.002 & 7.610 & 7.132 & 7.165 & 6.474 & 6.524 & 6.525  \\ 
  EU-L4 & 6.827 & 7.075 & 7.327 & 7.716 & 7.417 & 6.649 & 6.699 & 6.701  \\ 
  RM-L0 & 6.713 & 6.754 & 6.711 & 6.850 & 6.741 & 6.709 & 6.728 & 6.729  \\ 
  RM-L1 & 6.877 & 6.851 & 6.803 & 6.941 & 6.874 & 7.085 & 7.107 & 7.107  \\ 
  RM-L2 & 6.879 & 6.853 & 6.803 & 6.943 & 6.875 & 7.086 & 7.117 & 7.117  \\ 
   \hline
\end{tabular}
\caption{Average utilities of level-$k$ utility maximizers and
  level-$k$ regret minimizers over 10.000 arbitrary games (see main
  text). In our sample, regret minimizers of level $k>2$ are
  behaviorally equivalent to RM-L$2$ and are therefore omitted in this table. } 
  \label{tab:MaxUtil}
\end{table}

Table~\ref{tab:MaxUtil} gives the accumulated payoff averaged over
10.000 games sampled in this way, for $0 \le k \le 4$. The table lists
the average payoff for the row principle when playing against the
column principle and can be regarded as a symmetric ``meta-game'' that
captures the evolutionary competition between choice principles. The
only evolutionarily stable strategy (ESS) of this meta-game is EU-L4,
but it is clear (from more extensive simulations) that this is just
because we chose an arbitrary cutoff for depth of
reasoning. Generally, it appears that pure populations of EU-L$k$
players can always be invaded by EU-L$k+1$ players. But,
interestingly, some pure populations of EU-L$k$ players can also be
invaded by EU-L$l$ players, with $l<k$ (see
Table~\ref{tab:MaxUtil}). On the other hand, if $k\ge2$, then RM-L$k$
is a neutrally stable strategy (NSS): regret minimizers of a different
level $k\ge2$ would not be driven to extinction, but would also not
take over the population (because they are behaviorally equivalent in
all games from our random sample).

The results from this example generalize to other game-sampling
routines, as long as they are general and encompassing enough.  While
there is usually no $k$ at which EU-L$k$ is an ESS, there is a small
$k$ (almost always $k\le 3$) for which IRM has reached its fixed point
in all sampled games and RM-L$k'$ is an NSS for all $k' \ge k$. This
is a noteworthy result: on randomly sampled games, it is always
beneficial for utility maximizers to outsmart the opponent by ideally
one level of ToM reasoning; too much ToM outsmarting is harmful. For
IRM, levels of ToM reasoning higher than a few steps are
evolutionarily pointless.

More fine-grained results obtain under the natural hypothesis that ToM
reasoning incurs a cost $c(k) \in \mathds{R}$, proportional to
reasoning depth $k$. In that case, the properties of the cost function
are crucial. If costs are initially small and grow not too
superlinearly in $k$, it still holds that usually no EU-L$k$ is an ESS
because it can be invaded by EU-L$k+1$. However, invasion by EU-L$l$
for $l < k$ is now more prominent than without reasoning costs, so
that mixed populations containing low-level EU-L$k$ players are often
the only dynamic attractors, e.g., under the replicator dynamic. If
costs grow more pronouncedly superlinearly in $k$, there can be $k$
for which EU-L$k$ is an ESS in the meta-game restricted to utility
maximizing choice principles, but this requires very particular cost
functions and is not very likely. The most frequent outcome of
evolutionary competition between EU-L$k$ players under superlinear
costs is a mixed population of fairly low level-$k$ players. But all
of this only holds when RM-L$k$ is excluded from consideration. When
we also look at IMR, adding reasoning costs of any type results in
RM-L$k$ being an ESS for some very low $k$. If ToM reasoning costs
grow pronouncedly superlinearly, this ESS is almost always
unique. This means that, at least under certain assumptions about the
costs of ToM reasoning, the iterated security strategy IRM
evolutionarily outperforms level-$k$ utility maximization.

In sum, our simulation data show that shallow depth of reasoning is
plausibly evolutionarily advantageous in long run competition with
``deep ToM'' strategies. Regret minimization often outperforms utility
maximization in this evolutionary competition, especially when
reasoning costs are added. Although already insightful, our results
are only partial, because many interesting questions have not yet been
addressed. We mention just three obvious extensions for future
work. Firstly, sequential games might yield different results, because
they would induce more ties in strategic form, and hence more reasons
to apply deeper ToM reasoning. Secondly, the payoff of utility
maximization heavily depends on the type of belief about the
opponent's choice. Here we used arbitrary beliefs, but certain
restrictions on belief formation, e.g., using flat beliefs throughout,
might give utility maximizers a better payoff on average. Finally, it
would be interesting to extend our comparison to more choice
principles, e.g., ones including learning from repeated interactions
with the same players
\citep[][]{Weerdde-WeerdVerbrugge2013:How-much-does-i}, or choice
principles building on prospect theory, for example.

\newpage

\printbibliography[heading=bibintoc]

\end{document}

### 2014-07-29 text/RoaM_proceedings/paper.tex
inital export

--- 2014-07-29 text/RoaM_abstract/abstract.tex
@@
-\documentclass[10pt]{article}
+\documentclass{llncs}
 
@@
 % \doublespacing
-\usepackage[left=3.75cm,right=3.75cm,top=3.75cm,bottom=3.75cm]{geometry}
+% \usepackage[left=3.75cm,right=3.75cm,top=3.75cm,bottom=3.75cm]{geometry}
 
 \title{On the Evolution of Choice Principles}
-\author{}
+\titlerunning{On the Evolution of Choice Principles}
+\author{Michael Franke\inst{1} \and Paolo Galeazzi \inst{2}}
+\institute{Department of Linguistics, University of T\"{u}bingen \and
+  Institute for Logic, Language and Computation, Universiteit van Amsterdam}
 \date{}
@@
 
-\begin{center}
-  \begin{large}
-    On the Evolution of Choice Principles
-  \end{large}
-\end{center}
+\maketitle
 
-\noindent The widely accepted normative standard of individual decision making
+\begin{abstract}
+  We compare the evolutionary competition between different choice
+  principles in arbitrary strategic games under one-shot
+  interactions. Choice principles under scrutiny are level-$k$
+  utility maximization and level-$k$ regret minimization. RESULTS \dots
+\end{abstract}
+
+The widely accepted normative standard of individual decision making
 under uncertainty is expected utility maximization. An agent is
@@
 
-\newpage
-
 \printbibliography[heading=bibintoc]

### 2014-07-29 text/RoaM_proceedings/paper.tex
seccom

@@
 \begin{abstract}
-  We compare the evolutionary competition between different choice
-  principles in arbitrary strategic games under one-shot
-  interactions. Choice principles under scrutiny are level-$k$
-  utility maximization and level-$k$ regret minimization. RESULTS \dots
+  We compare level-$k$ utility maximization and level-$k$ regret
+  minimization in evolutionary competition on one-shot plays of
+  arbitrary strategic games. RESULTS \dots
 \end{abstract}

### 2014-07-31 text/RoaM_proceedings/paper.tex
proceedings final

@@
   We compare level-$k$ utility maximization and level-$k$ regret
-  minimization in evolutionary competition on one-shot plays of
-  arbitrary strategic games. RESULTS \dots
+  minimization in evolutionary competition based on averages of
+  one-shot plays over many randomly generated strategic games. Under
+  the assumption that Theory-of-Mind-reasoning of depth $k$ incurs a
+  cost monotonically increasing with $k$, our results show that mixed
+  states with low levels of reasoning depth $k$ can be evolutionary
+  stable with substantial basins of attraction under the replicator
+  dynamics and that regret minimization can outperform utility
+  maximization.
 \end{abstract}
 
-The widely accepted normative standard of individual decision making
-under uncertainty is expected utility maximization. An agent is
-rational only if his choices maximize expected utility. In games with
-several players, agents who believe that their opponents are rational
-might thus rule out certain of the opponents' choices. This kind of
-reasoning can be iterated, giving rise to predictions of rational
-choice under arbitrarily deep nestings of mutual beliefs in
+\noindent The widely accepted normative standard of individual
+decision making under uncertainty is expected utility maximization. An
+agent is rational only if his choices maximize expected utility. In
+games with several players, agents who believe that their opponents
+are rational might thus rule out certain of the opponents'
+choices. This kind of reasoning can be iterated, giving rise to
+predictions of rational choice under arbitrarily deep nestings of
+mutual beliefs in
 rationality. % Depending on the detailed specification of what it means
@@
 with a fixed choice principle who play many \emph{arbitrary} 2-player
-strategic games, not just a small hand-picked selection. This way we
-try to asses the general evolutionary benefit of a choice principle
-across an unbiased sample of games, not just for those games that are
-of particular technical, philosophical or historical
+one-shot strategic games, not just a small hand-picked selection. This
+way we try to assess the general evolutionary benefit of a choice
+principle across an unbiased sample of games, not just for those games
+that are of particular technical, philosophical or historical
 importance. Additionally, we compare not only different ToM reasoning
@@
 maximization and level-$k$ iterated regret minimization (IRM)
-\citep{HalpernPass2012:Iterated-Regret}.\footnote{Unlike
-  \citeauthor{Weerdde-WeerdVerbrugge2013:How-much-does-i}, we look at
-  level-$k$ reasoning models
-  \citep[e.g.][]{Crawford2003:Lying-for-Strat,Crawford2007:Lets-Talk-It-Ove},
-  not cognitive hierarchy models
-  \citep[e.g.][]{CamererHo2004:A-Cognitive-Hie}. The former assume
-  that agents of level $k+1$ believe that the opponent is of level
-  $k$, while the latter assume a belief in a level-$l$ opponent with
-  $l \le k$. Moreover, we assume all games to be one-shot encounters,
-  while \citeauthor{Weerdde-WeerdVerbrugge2013:How-much-does-i} look
-  at repeated encounters with the same opponent, and the concomitant
-  possibility of strategic learning.}  The motivation for looking at
+\citep{HalpernPass2012:Iterated-Regret}. The motivation for looking at
 IRM is threefold. For one, regret minimization has been suggested as a
@@
 
-The choice principles we compare are defined as follows. L-0 utility
-maximizers have an arbitrary probabilistic belief about the opponent's
-behavior and are indifferent between any act that maximizes expected
-utility under this belief. L-$k+1$ utility maximizers have an
-arbitrary probabilistic belief over all acts that an L-$k$ opponent
-would be indifferent about. Formally, if $U$ is a matrix of utilities
-for the row player, regret minimization is equivalent to playing
-MaxiMin on the derived matrix $U'$, where $U'_{ij} = U_{ij} -
-\textrm{max}_{k} U_{kj}$ is the negative regret of choosing act $i$
-when the opponent chooses $j$. L-0 regret minimizers are indifferent
-between any act that minimizes regret in this sense. An L-$k+1$ regret
-minimizer chooses like an L-0 regret minimizer in the reduced game in
-which only acts remain that row and column players would choose that
-are L-$k$ regret minimizers
-\citep[see][]{HalpernPass2012:Iterated-Regret}.
+The choice principles we compare are defined as follows. Look at
+level-$k$ utility maximizers first. L-0 utility maximizers have an
+arbitrary probabilistic belief about the opponent's behavior and are
+indifferent between any act that maximizes expected utility under this
+belief. L-$k+1$ utility maximizers have an arbitrary probabilistic
+belief with support only on acts that an L-$k$ opponent might choose,
+and are indifferent between any act that maximizes expected utility
+under this belief. Notice that this construction is different from
+that of \citet{Weerdde-WeerdVerbrugge2013:How-much-does-i} in several
+respects. Firstly, we look at level-$k$ reasoning models
+\citep[e.g.][]{Crawford2003:Lying-for-Strat,Crawford2007:Lets-Talk-It-Ove},
+not cognitive hierarchy models
+\citep[e.g.][]{CamererHo2004:A-Cognitive-Hie}, like
+\citeauthor{Weerdde-WeerdVerbrugge2013:How-much-does-i} do. The former
+models assume that agents of level $k+1$ believe that the opponent is
+of level $k$, while the latter have a more general belief that the
+opponent is of some level-$l$ with $l \le k$. Moreover, we assume all
+games to be one-shot encounters, while
+\citeauthor{Weerdde-WeerdVerbrugge2013:How-much-does-i} look at
+repeated encounters with the same opponent, and the concomitant
+possibility of strategic learning.
+
+Let's turn next to the definition of level-$k$ regret
+minimizers. Formally, if $U$ is a matrix of utilities for the row
+player, regret minimization is equivalent to playing MaxiMin on the
+derived matrix $U'$, where $U'_{ij} = U_{ij} - \textrm{max}_{k}
+U_{kj}$ is the negative regret of choosing act $i$ when the opponent
+chooses $j$. L-0 regret minimizers are indifferent between any act
+that minimizes regret in this sense. An L-$k+1$ regret minimizer
+chooses like an L-0 regret minimizer in the reduced game in which only
+acts remain that row and column players would choose that are L-$k$
+regret minimizers \citep[see][]{HalpernPass2012:Iterated-Regret}.
 
@@
 
-\begin{table}
+\begin{table}[t]
   \centering
@@
   \hline
-  EU-L0 & 6.754 & 6.764 & 6.729 & 6.889 & 6.790 & 6.747 & 6.767 & 6.767  \\ 
-  EU-L1 & 7.155 & 6.696 & 6.666 & 6.609 & 6.949 & 7.004 & 7.072 & 7.071  \\ 
-  EU-L2 & 6.692 & 7.412 & 6.959 & 6.850 & 6.973 & 6.457 & 6.554 & 6.556  \\ 
-  EU-L3 & 6.707 & 7.002 & 7.610 & 7.132 & 7.165 & 6.474 & 6.524 & 6.525  \\ 
-  EU-L4 & 6.827 & 7.075 & 7.327 & 7.716 & 7.417 & 6.649 & 6.699 & 6.701  \\ 
-  RM-L0 & 6.713 & 6.754 & 6.711 & 6.850 & 6.741 & 6.709 & 6.728 & 6.729  \\ 
-  RM-L1 & 6.877 & 6.851 & 6.803 & 6.941 & 6.874 & 7.085 & 7.107 & 7.107  \\ 
-  RM-L2 & 6.879 & 6.853 & 6.803 & 6.943 & 6.875 & 7.086 & 7.117 & 7.117  \\ 
-   \hline
+  EU-L0 & 6.735 & 6.749 & 6.739 & 6.873 & 6.755 & 6.742 & 6.733 & 6.734 \\ 
+  EU-L1 & 7.126 & 6.650 & 6.649 & 6.610 & 6.954 & 6.969 & 7.016 & 7.017 \\ 
+  EU-L2 & 6.642 & 7.413 & 6.979 & 6.857 & 6.961 & 6.414 & 6.494 & 6.495 \\ 
+  EU-L3 & 6.636 & 6.946 & 7.627 & 7.152 & 7.162 & 6.430 & 6.465 & 6.465 \\ 
+  EU-L4 & 6.780 & 7.038 & 7.314 & 7.734 & 7.388 & 6.592 & 6.620 & 6.619 \\ 
+  RM-L0 & 6.686 & 6.684 & 6.700 & 6.830 & 6.695 & 6.681 & 6.676 & 6.675 \\ 
+  RM-L1 & 6.853 & 6.768 & 6.782 & 6.913 & 6.806 & 7.051 & 7.046 & 7.043 \\ 
+  RM-L2 & 6.856 & 6.770 & 6.784 & 6.916 & 6.810 & 7.052 & 7.057 & 7.053 \\ 
+   \hline \\
 \end{tabular}
@@
 is a neutrally stable strategy (NSS): regret minimizers of a different
-level $k\ge2$ would not be driven to extinction, but would also not
+level $l\ge2$ would not be driven to extinction, but would also not
 take over the population (because they are behaviorally equivalent in
@@
 beneficial for utility maximizers to outsmart the opponent by ideally
-one level of ToM reasoning; too much ToM outsmarting is harmful. For
-IRM, levels of ToM reasoning higher than a few steps are
+one level of ToM reasoning, but too much ToM outsmarting is
+harmful. For IRM, levels of ToM reasoning higher than a few steps are
 evolutionarily pointless.
 
-More fine-grained results obtain under the natural hypothesis that ToM
-reasoning incurs a cost $c(k) \in \mathds{R}$, proportional to
-reasoning depth $k$. In that case, the properties of the cost function
-are crucial. If costs are initially small and grow not too
-superlinearly in $k$, it still holds that usually no EU-L$k$ is an ESS
-because it can be invaded by EU-L$k+1$. However, invasion by EU-L$l$
-for $l < k$ is now more prominent than without reasoning costs, so
-that mixed populations containing low-level EU-L$k$ players are often
-the only dynamic attractors, e.g., under the replicator dynamic. If
-costs grow more pronouncedly superlinearly in $k$, there can be $k$
-for which EU-L$k$ is an ESS in the meta-game restricted to utility
-maximizing choice principles, but this requires very particular cost
-functions and is not very likely. The most frequent outcome of
-evolutionary competition between EU-L$k$ players under superlinear
-costs is a mixed population of fairly low level-$k$ players. But all
-of this only holds when RM-L$k$ is excluded from consideration. When
-we also look at IMR, adding reasoning costs of any type results in
-RM-L$k$ being an ESS for some very low $k$. If ToM reasoning costs
-grow pronouncedly superlinearly, this ESS is almost always
-unique. This means that, at least under certain assumptions about the
-costs of ToM reasoning, the iterated security strategy IRM
-evolutionarily outperforms level-$k$ utility maximization.
+More fine-grained results obtain when we look at the predictions of
+the replicator dynamics on the simulated ``meta-games'' together with
+the natural hypothesis that ToM reasoning incurs a cost $c(k) \in
+\mathds{R}$, which is monotonically increasing with $k$. For
+concreteness, we look at a parameterized cost function $c(k \thinspace
+; \thinspace s, a ) = \sum_{i=0}^{k} a^i \thinspace s$ where $s$ is
+the initial step of growth, and $a$ is a parameter that controls for
+superlinear and sublinear growth. For at least linear growth ($a \ge
+1$), there is a threshold $\theta \approx .391$ such that if $s >
+\theta$, the only attractor is EU-L$0$. With $s$ smaller or not too
+much bigger than $\theta$ and sublinear growth (e.g., $a=0.25$), RM-L1
+is a strong attractor, as well as mixed states of low level
+EU-maximizers. For step $s < \theta$ and $a \le 1$ results are more varied. If $.313
+< s < \theta$, the only attracting state is a mix of EU-L0 and
+EU-L1. If $.011 < s < .313$, RM-L1 is a strict symmetric Nash
+equilibrium and therefore an attractor, but also, depending on $s$,
+mixed states of low-level EU-maximizers are attracting. If $0 < s \le
+.011$ RM-L2 is an attractor, together with mixed states of low level
+EU-maximizers.
 
 In sum, our simulation data show that shallow depth of reasoning is
-plausibly evolutionarily advantageous in long run competition with
-``deep ToM'' strategies. Regret minimization often outperforms utility
+plausibly evolutionarily dominant in long run competition with ``deep
+ToM'' strategies. Regret minimization often outperforms utility
 maximization in this evolutionary competition, especially when
@@
 maximization heavily depends on the type of belief about the
-opponent's choice. Here we used arbitrary beliefs, but certain
-restrictions on belief formation, e.g., using flat beliefs throughout,
-might give utility maximizers a better payoff on average. Finally, it
-would be interesting to extend our comparison to more choice
-principles, e.g., ones including learning from repeated interactions
-with the same players
-\citep[][]{Weerdde-WeerdVerbrugge2013:How-much-does-i}, or choice
+opponent's choice. Here we used arbitrary beliefs compatible with the
+opponent's assumed type, but certain restrictions on belief formation,
+e.g., using maximum-entropy beliefs, might give utility maximizers a
+better payoff on average. Finally, it would be interesting to extend
+our comparison to more choice principles, e.g., ones including
+learning from repeated interactions with the same players
+\citep[e.g.][]{Weerdde-WeerdVerbrugge2013:How-much-does-i}, or choice
 principles building on prospect theory, for example.
+
+\newpage
 

### 2014-08-06 text/RoaM_proceedings/paper.tex
grant info added

@@
 
-\title{On the Evolution of Choice Principles}
-\titlerunning{On the Evolution of Choice Principles}
-\author{Michael Franke\inst{1} \and Paolo Galeazzi \inst{2}}
-\institute{Department of Linguistics, University of T\"{u}bingen \and
-  Institute for Logic, Language and Computation, Universiteit van Amsterdam}
-\date{}
+\title{On the Evolution of Choice Principles} \titlerunning{On the
+  Evolution of Choice Principles} \author{Michael Franke\inst{1} \and
+  Paolo Galeazzi \inst{2}\thanks{ Michael Franke gratefully
+    acknowledges support by NWO-VENI-grant 275-80-004. The research of
+    Paolo Galeazzi leading to these results has received funding from
+    the European Research Council under the European Community's
+    Seventh Framework Programme (FP7/2007-2013)/ERC Grant agreement
+    no. 283963.}}  \institute{Department of Linguistics, University of
+  T\"{u}bingen \and Institute for Logic, Language and Computation,
+  Universiteit van Amsterdam} \date{}
 

### 2015-05-18 paper/paper.tex
paper initial skeleton

\documentclass[fleqn,reqno,10pt]{article}

%========================================
% Packages
%========================================

\usepackage[]{helpers/mypackages}
%\usepackage[natbib=true,style=authoryear-comp,backend=bibtex,doi=false,url=false]{biblatex}
\bibliography{helpers/MyRefLocal}
\usepackage{helpers/myenvironments}
\usepackage{helpers/mycommands}

\usepackage{todonotes}

%========================================
% Standard Layout
%========================================

\usepackage{a4wide}

% Itemize
\renewcommand{\labelitemi}{\large{$\mathbf{\cdot}$}}    % itemize symbols
\renewcommand{\labelitemii}{\large{$\mathbf{\cdot}$}}
\renewcommand{\labelitemiii}{\large{$\mathbf{\cdot}$}}
\renewcommand{\labelitemiv}{\large{$\mathbf{\cdot}$}}
% Description
\renewcommand{\descriptionlabel}[1]{\hspace\labelsep\textsc{#1}}

% Figure Captions
\usepackage{caption} % use corresponding myfiguresize!
\setlength{\captionmargin}{20pt}
\renewcommand{\captionfont}{\small}
\setlength{\belowcaptionskip}{7pt} % standard is 0pt

\title{Rationality, Evolution \& the Environment}
\author{Paolo Galeazzi \& Michael Franke}
\date{current version: May 18th 2015}

\begin{document}
\maketitle

\begin{abstract}
  We study the evolutionary competition of choice principles in meta games.
\end{abstract}

\begin{itemize}
\item We would like to look at the problem of ``rational choice'' from an evolutionary point of
  view: what choice principles would be promoted, which demoted in evolutionary competition
  amongst each other?
\item This depends on the environment; it depends on what choice situations occur. Maybe some
  choice principle is better in some situations, while another one is better in others. 
\item

\end{itemize}

\printbibliography[heading=bibintoc]

\end{document}

### 2015-05-19 code/optimal_decision_rules.r
tweaked code for solitary decision problems

@@ -1,24 +1,35 @@
 require('gtools') # for dirichlet distribution
 require('plyr') # to conveniently manipulate data frames
+require('ggplot2')
+require('reshape2')
 
 max.t=10
 max.a=10
-n.rounds = 1000
+n.rounds = 50000
 
-data = data.frame(p.true = rep(0,n.rounds),
-                  a.best = rep(0,n.rounds),
-                  n.t = rep(0,n.rounds),
-                  n.a = rep(0,n.rounds),
-                  a.br = rep(0,n.rounds),
-                  a.mr = rep(0,n.rounds),
-                  u.br = rep(0,n.rounds),
-                  u.mr = rep(0,n.rounds))
+p.trueL = 0
+a.bestL = 0
+n.tL = 0
+n.aL = 0
+a.brL = 0
+a.mrL = 0
+u.brL = 0
+u.mrL = 0                  
 
 for (i in 1:n.rounds) {
-  n.t = sample(2:max.t,1) # number of states
-  n.a = sample(2:max.a,1) # number of acts
-  u = matrix(sample(-100:100,replace=TRUE,size=n.t*n.a),nrow=n.t,ncol=n.a) # utility matrix
-  p = rdirichlet(1,rep(1,n.t))[1,] # probabilities of states
+  if (max.t > 2){
+    n.t = sample(2:max.t,1) # number of states
+  } else {
+    n.t = 2
+  }
+  if (max.a > 2){
+    n.a = sample(2:max.a,1) # number of acts
+  } else {
+    n.a = 2
+  }
+  u = matrix(sample(0:10,replace=TRUE,size=n.t*n.a),nrow=n.t,ncol=n.a) # utility matrix
+#   p = rdirichlet(1,rep(1,n.t))[1,] # probabilities of states
+  p = rep(1/n.t, n.t)
   t = sample(1:n.t,1) # true state
 #   t = sample(1:n.t,1,prob=p) # true state, with bias
   # get best response
@@ -31,15 +42,24 @@ for (i in 1:n.rounds) {
   rgrt = sapply(1:n.a, function(x) max(best.v - u[,x])) # regret of each act
   a.mr = which.min(rgrt) # act that minimizes regret 
   # record data
-  data$p.true[i] = p[t]
-  data$a.best[i] = which.max(u[t,])
-  data$n.t[i] = n.t
-  data$n.a[i] = n.a
[…]

### 2015-05-20 paper/paper.tex
paper outline

@@
-\documentclass[fleqn,reqno,10pt]{article}
+\documentclass[fleqn,reqno,11pt]{article}
 
@@
 
-\begin{abstract}
-  We study the evolutionary competition of choice principles in meta games.
-\end{abstract}
+\section*{Outline of main argument}
 
 \begin{itemize}
-\item We would like to look at the problem of ``rational choice'' from an evolutionary point of
-  view: what choice principles would be promoted, which demoted in evolutionary competition
-  amongst each other?
-\item This depends on the environment; it depends on what choice situations occur. Maybe some
-  choice principle is better in some situations, while another one is better in others. 
-\item
+\item Evolutionary game theory has become an established philosophical tool for probing into
+  conceptual issues whose complexity requires mathematical modeling. Most applications of EGT
+  look at evolutionary selection of behavior in a single game. This game is then considered
+  fixed, closed and immutable.
+  \begin{itemize}
+  \item there are some notable exceptions where the game is open ended, e.g., by the invention
+    of actions \citep{WordenLevin2007:Evolutionary-es, McKenzie-AlexanderSkymrs2012:Inventing-New-S}
+  \end{itemize}
 
+\item We present an approach to studying evolutionary selection of \emph{choice principles},
+  i.e., ways of choosing consistently across several games. In other words, we would like to
+  look at the problem of ``rational choice'' from an evolutionary point of view: what choice
+  principles would be promoted, which demoted in evolutionary competition amongst each other?
+
+\item This depends on the environment; it depends on what choice situations occur how
+  frequently. Maybe some choice principle is better in some situations, while another one is
+  better in others. To capture the relevant statistics of the environment, we therefore look at
+  the evolutionary competition of choice principles in a ``meta-game'' that consists of the
+  average expected payoffs of choice principles when playing arbitrary games (from a given
+  class). In this sense, a meta-game captures (the modeller's) assumptions about the relevant
+  statistic of the environment in which evolutionary forces operate.
+
+\item To demonstrate how this approach can be theoretically rewarding, we show that, under
+  reasonable additional assumptions, maximization of expected utility is not the only choice
+  principle supported by evolutionary selection. In particular, we show that evolutionary
+  selection can support non-veridical representations of payoffs in terms of regret.
+
+\item We argue that this ``meta-evolutionary'' approach could eventually help explain attested
+  deviations of human decision making from the classical ideal: choice behavior evolved to be an
+  ``ecologically rational'', near-optimal adaptation to the environment \citep{Anderson1990:The-Adaptive-Ch,Anderson1991:Is-human-cognit,GigerenzerGoldstein1996:Reasoning-the-F,ChaterOaksford2000:The-Rational-An}
+
+\end{itemize}
+
+\newpage
+
+\section{Introduction / Motivation}
+
+\begin{itemize}
+\item evolutionary game theory about one game usually
+\item here class of games
+\item therefore partial solution to the ``closed game'' problem
+\item still not infinite, open ended strategy space
+\item focus on one example for this new method: competition between:
+  \begin{itemize}
+  \item probabilistic vs.~non-probabilistic uncertainty
+  \item veridical vs.~regret-based preferences
+  \end{itemize}
+\item contributes to: (i) methodological reflection on evolutionary game theory, (ii) ecological
+  rationality of choice behavior, (iii) evolution of preferences literature
+\end{itemize}
+
+\section{Faces of rationality}
+
+\begin{itemize}
+  \item \todo[inline]{choose uniform consensual terminology for maximization of EU and regret minimization}
+\item classical notion of rationality: maximization of expected utilities
+  \begin{itemize}
+  \item human choice behavior seems to deviate from classical rational choice in many ways
+    \citep[most
+    notably][]{TverskyKahnemann1974:Judgement-under,KahnemannTversky1979:Prospect-Theory}
+  \end{itemize}
+\item historical competitor: regret minimization
+  \begin{itemize}
+  \item introduced by Savage \& Niehans independently
+  \item worked out (in parameterized form) by \citet{LoomesSugden1982:Regret-Theory:-} and
+    argued to outperform prospect theory
+  \item recently rediscovered by game theorists \citep{HalpernPass2012:Iterated-Regret} as a
+    possible partial explanation of some puzzles (e.g., Travellers Dilemma)
+  \end{itemize}
+\item motivate why we are interested in regret minimization; e.g.:
+  \begin{itemize}
+  \item simple historical alternative; certain prima facie plausibility
+  \item has both components of interest:
+    \begin{itemize}
+    \item epistemic component: probabilistic vs.~non-probabilistic uncertainty  (interesting
+      because of the classical Ellsberg paradox)
+    \item payoff component: veridical vs.~non-veridical preference representations (interesting
+      because of a recent interest in the ``evolution of preference'')
+    \item gives us intriguing results that nicely motivate the general approach of meta-games
+    \end{itemize}
+  \end{itemize}
+\end{itemize}
+
+\section{Evolution \& the environment}
+
+here we spell out our model
+
+\subsection{Choice principles}
+
+\begin{itemize}
+\item study evolutionary competition between \emph{choice principles} 
+\item for now a choice principle is a pair (epistemic type, preference type)
+  \begin{itemize}
+  \item two epistemic types:
+    \begin{enumerate}
+    \item probabilistic beliefs (assumed to be flat)
+    \item non-probabilistic beliefs
+    \end{enumerate}
+  \item two preferences types (references to ``evolution of preference'' literature):
+    \begin{enumerate}
+    \item veridical payoff representations
+    \item regret-based payoffs
+    \end{enumerate}
+  \item many other types are conceivable; more in discussion section
+    \begin{itemize}
+    \item we want to keep it simple
+    \item assume that agents are relatively simple as well
+    \item no learning from past encounters \& no reasoning about the opponent: agents simply do
+      not know that there is another player (no strategic thinking possible; in line with idea
+      of evolutionary game theory where agents are ``stupid'' and ``myopic'') \\
+      \textcolor{blue}{this is then the added assumption that may be crude and generally
+        implausible but allows us to deflect the economists' critique}
+    \end{itemize}
+  \item choice principles yield action choices for each game
+    \begin{itemize}
+    \item show how
+    \end{itemize}
+  \item RESULT: types (prob., veridical) and (prob., regret) are choice-equivalent (also
+    mentioned by \citet{HalpernPass2012:Iterated-Regret})
+  \item RESULT: in $2 \times 2$ cases, (prob., veridical), (prob., regret) and (non-prob.,
+    regret) are choice-equivalent (but not for $n \times n$ in general)
+    \begin{itemize}
+    \item still we treat them as separate types because they behave differently under
+      component-wise mutation (see below)
+    \end{itemize}
+  \end{itemize}
+\end{itemize}
+
+\subsection{The environment: meta-games}
+
+\begin{itemize}
+\item imagine huge, virtually infinite population of agents, each carrying a choice principle
+\item agents play a randomly sampled game against a randomly sampled opponent
+\item fitness is based on the average payoff of choice principle A against choice principle B,
+  taken over arbitrary games $g$ and weighted their occurrence probability $P(g)$:
+  $\int_g P(g) \times U_g(\text{CP-A}, \text{CP-B}) \text{d}g$
+\item the occurrence probability of games $g$ is the ``environment'' and, possibly, impossible to
+  derive theoretically, or to measure empirically
+\item here, use a relatively neutral approach instead that is practicable:
+  \begin{itemize}
+  \item games are individuated by their payoff matrices (no framing effects or similar)
+  \item each entry in a payoff matrix is an i.~i.~d.~random variable
+    \begin{itemize}
+    \item approach still incorporates a bias (e.g., against strategic form representations of
+      sequential games)
+    \end{itemize}
+  \end{itemize}
+\item example: average payoffs from numerical simulation of ($2 \times 2$ symmetric games)
+\item example: average payoffs from numerical simulation of ($n \times n$ symmetric games, with
+  $n$ uniformly random (up to some upper-bound))
+\end{itemize}
+
+\subsection{Results}
+
+\textcolor{gray}{keep this clean and concise, formal details (proofs) in appendix}
+
+\subsubsection{$2 \times 2$ symmetric games}
+
+\textcolor{gray}{we isolate this case because it is most basic, and we can offer analytical
+  proofs as well}
+
+\begin{itemize}
+\item given previous results, there are really only two kinds of types to look at:
+  \begin{enumerate}
+  \item (prob., veridical), (prob., regret) and (non-prob., regret) \\ 
+    \textcolor{gray}{[all choice-equivalent in this case]}
+  \item (non-prob., veridical)
+  \end{enumerate}
+\item RESULT: the former class ``dominates'' the latter (our main result, Proposition 1 from
+  TARK paper)
+\item this means that evolutionary dynamics would weed out (non-prob., regret); every
+  population composition between the remaining three is neutrally stable; all interior
+  trajectories (of the replicator dynamic) converge to these
+\item further results (from TARK):
+  \begin{itemize}
+  \item component-wise mutation: abundance of regret types
+  \item exogenously given correlated epistemic types: regret types dominate
+  \item exogenously given uncorrelated epistemic types: regret types dominate
+  \end{itemize}
+\todo[inline]{work out these additional results more carefully; present graphs if possible}
+\end{itemize}
+
+\subsubsection{$n \times n$ symmetric games}
+
+\todo[inline]{work out these additional results more carefully; present graphs if possible}
+
+\section{Discussion}
+
+\begin{itemize}
+\item what we achieved
+\item what could be done next
 \end{itemize}

### 2015-05-20 code/2by2_symmetric_games.r

@@ -2,7 +2,7 @@ source('functions.R')
 CP_names = c("Sec-Reg", "Sec-Id", "Sec-Comp", "Sec-Alt", 
              "Bel-Reg", "Bel-Id", "Bel-Comp", "Bel-Alt")
 
-rounds = 1
+rounds = 10000
 # game_type = c()
 row_util = rep(0,rounds*length(CP_names)^2)
 nActs = rep(2,rounds)
@@ -18,33 +18,33 @@ for (i in 1:rounds){
   
   #   gt = classify_game(U)
   
-  #   br = matrix(rep(rdirichlet(1,rep(1,dim(U)[2]))[1,], each=dim(U)[1]), nrow=dim(U)[1], ncol=dim(U)[2]) # beliefs of row player
+#     br = matrix(rep(rdirichlet(1,rep(1,dim(U)[2]))[1,], each=dim(U)[1]), nrow=dim(U)[1], ncol=dim(U)[2]) # beliefs of row player
   br = 1 # flat beliefs
   
-  choices = c(maximin(regret_transform(U)), #Sec-Reg
+  choices = list(maximin(regret_transform(U)), #Sec-Reg
               maximin(U), # Sec-Id
               maximin(relative_power_transform(U)), # Sec-Alt
               maximin(general_power_transform(U)),  # Sec-Comp
-              max_value(regret_transform(U)), #Bel-Reg
-              max_value(U), # Bel-Id
-              max_value(relative_power_transform(U)), # Bel-Alt
-              max_value(general_power_transform(U))  # Bel-Comp
+              max_value(regret_transform(U), br), #Bel-Reg
+              max_value(U, br), # Bel-Id
+              max_value(relative_power_transform(U), br), # Bel-Alt
+              max_value(general_power_transform(U), br)  # Bel-Comp
   )
   
-  choices.c = c(maximin(regret_transform(U)), #Sec-Reg
-                maximin(U), # Sec-Id
-                maximin(relative_power_transform(U)), # Sec-Alt
-                maximin(general_power_transform(U)),  # Sec-Comp
-                max_value(regret_transform(U)), #Bel-Reg
-                max_value(U), # Bel-Id
-                max_value(relative_power_transform(U)), # Bel-Alt
-                max_value(general_power_transform(U))  # Bel-Comp
-  )
-  
+#   choices.c = list(maximin(regret_transform(U)), #Sec-Reg
+#                 maximin(U), # Sec-Id
+#                 maximin(relative_power_transform(U)), # Sec-Alt
[…]

### 2015-05-20 code/functions.R

@@ -76,14 +76,14 @@ flip_game = function(U){
   return(V)
 }
 
-max_value = function(U){
+max_value = function(U, br){
   if (length(dim(U)) == 3) {
     U = U[,,1]
   }
+  U = U * br
   eus = rowMeans(U)
-  maxs = which.max(eus)
-  i = sample(length(maxs),1)
-  return(maxs[i])
+  maxs = which(eus == max(eus))
+  return(maxs)
 }
 
 maximin = function(U){
@@ -93,8 +93,7 @@ maximin = function(U){
   }
   mins = sapply(1:dim(U)[1], function(x) min(U[x,]))
   maximins = which(mins == max(mins))
-  i = sample(length(maximins),1)
-  return(maximins[i])
+  return(maximins)
 }
 
 regret_transform = function(U){

### 2015-05-20 code/optimal_decision_rules.r

@@ -3,9 +3,9 @@ require('plyr') # to conveniently manipulate data frames
 require('ggplot2')
 require('reshape2')
 
-max.t=10
-max.a=10
-n.rounds = 50000
+max.t=2
+max.a=2
+n.rounds = 5000
 
 p.trueL = 0
 a.bestL = 0

### 2015-05-21 paper/paper.tex
outline tweaks

@@
 \item We argue that this ``meta-evolutionary'' approach could eventually help explain attested
-  deviations of human decision making from the classical ideal: choice behavior evolved to be an
-  ``ecologically rational'', near-optimal adaptation to the environment \citep{Anderson1990:The-Adaptive-Ch,Anderson1991:Is-human-cognit,GigerenzerGoldstein1996:Reasoning-the-F,ChaterOaksford2000:The-Rational-An}
+  deviations of human decision making from the classical ideal: choice behavior evolved to be
+  an ``ecologically rational'', near-optimal adaptation to the environment
+  \citep{Anderson1990:The-Adaptive-Ch,Anderson1991:Is-human-cognit,GigerenzerGoldstein1996:Reasoning-the-F,ChaterOaksford2000:The-Rational-An}. This
+  is inline with recent aspirations to provide an evolutionary rationale for decision making
+  processes
+  \citep[e.g.][]{HammersteinStevens2012:Six-Reasons-for,FawcettHamblin2013:Exposing-the-be}. Here,
+  we seek to contribute to the formal machinery, an extension of evolutionary game theory, that
+  allows to capture statistical properties of the environment
+  \citep[cf.][]{McNamara2013:Towards-a-Riche}.
 
@@
   \item component-wise mutation: abundance of regret types
+    \begin{itemize}
+    \item different evolutionary paths despite the same behavior (contra the ``behavioral
+      gambit'' \citep{FawcettHamblin2013:Exposing-the-be})
+    \end{itemize}
   \item exogenously given correlated epistemic types: regret types dominate

### 2015-05-22 paper/paper.tex
outline redone

@@
 
+\newcommand{\myalert}[1]{\textcolor{red}{#1}}
+
 \title{Rationality, Evolution \& the Environment}
@@
 \item Evolutionary game theory has become an established philosophical tool for probing into
-  conceptual issues whose complexity requires mathematical modeling. Most applications of EGT
-  look at evolutionary selection of behavior in a single game. This game is then considered
-  fixed, closed and immutable.
+  conceptual issues whose complexity requires mathematical modeling.
   \begin{itemize}
-  \item there are some notable exceptions where the game is open ended, e.g., by the invention
-    of actions \citep{WordenLevin2007:Evolutionary-es, McKenzie-AlexanderSkymrs2012:Inventing-New-S}
+  \item helped structure debate about foraging, mating, evolution of cooperation,
+    information-flow, deception etc.
   \end{itemize}
-
-\item We present an approach to studying evolutionary selection of \emph{choice principles},
-  i.e., ways of choosing consistently across several games. In other words, we would like to
-  look at the problem of ``rational choice'' from an evolutionary point of view: what choice
-  principles would be promoted, which demoted in evolutionary competition amongst each other?
-
-\item This depends on the environment; it depends on what choice situations occur how
-  frequently. Maybe some choice principle is better in some situations, while another one is
-  better in others. To capture the relevant statistics of the environment, we therefore look at
-  the evolutionary competition of choice principles in a ``meta-game'' that consists of the
-  average expected payoffs of choice principles when playing arbitrary games (from a given
-  class). In this sense, a meta-game captures (the modeller's) assumptions about the relevant
-  statistic of the environment in which evolutionary forces operate.
-
+\item Most applications of EGT look at evolutionary selection of behavior in a single
+  game. There are two crude simplifications here:
+  \begin{enumerate}
+  \item The stage game is usually considered fixed, closed and immutable.
+    \begin{itemize}
+    \item there are some notable exceptions where the game is open ended, e.g., by the
+      invention of actions \citep{WordenLevin2007:Evolutionary-es,
+        McKenzie-AlexanderSkymrs2012:Inventing-New-S}
+    \end{itemize}
+  \item What evolves are behavioral strategies for the stage game \citep[what][call the
+    ``behavioral gamit'']{FawcettHamblin2013:Exposing-the-be} \myalert{(more references!
+      Gigerenzer etc.)}.
+  \end{enumerate}
+\item It has been argued that we should rather study the evolutionary selection of \emph{choice
+    mechanisms} that are adapted in a rich and variable environment
+  \citep[e.g.][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche}.
+\item However, studies on the adaptive value of choice mechanisms have focused, for the most
+  part, of the evolutionary benefit of learning rules
+  \citep[e.g.][]{ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o}. (\myalert{More
+    references Harley 1981!!!, \dots}). Moreover, only little attention has been paid to
+  modeling the direct (game-theoretic) meta-competition between alternative choice mechanisms
+  \citep[see][for related criticism]{FawcettHamblin2013:Exposing-the-be}.
+\item Here, we would like to make two contributions to the literature on evolution of choice
+  mechanisms:
+  \begin{enumerate}
+  \item On the conceptual side, we argue that paying attention to the evolution of (subjective
+    representations of) preferences matters. Since almost any reasonable learning or
+    decision-making process will make use of some (subjective, agent-internal (possibly
+    unconscious)) representation of the quality of choice options, the question of which such
+    representations are ecologically valuable (i.e., lead to high fitness) is central. In fact,
+    the evolution of (subjective representations of) preferences has recently been studied in
+    theoretical economics as well \myalert{add references}. However, these studies also suffer
+    from the ``behavioral gambit'' and the usual shortcomings of the closedness of the stage game. 
+  \item On the methodological side, we therefore introduce a conservative extension of the
+    standard EGT that allows us to reuse notions such as evolutionary stability / evolutionary
+    dynamics and yet helps us study the evolutionary competition between choice mechanisms in a
+    statistically variable environment. Concretely, we look at the evolutionary competition of
+    choice mechanisms in a ``meta-game'' that consists of the average expected payoffs of
+    choice mechanisms when playing arbitrary games (from a given class). In this sense, a
+    meta-game captures (the modeller's) assumptions about the relevant statistic of the
+    environment in which evolutionary forces operate.
+  \end{enumerate}
+\item To drive home our conceptual point that preference representations can matter, we try to
+  isolate, as good as we can, the evolution of preferences from considerations of learning or
+  other factors feeding a decision mechanism (such as the acquisition of ecologically useful
+  representations (think: beliefs)). (Obviously, eventually, we would like to study the
+  evolution of all of these relevant components in one swoop.)
 \item To demonstrate how this approach can be theoretically rewarding, we show that, under
-  reasonable additional assumptions, maximization of expected utility is not the only choice
-  principle supported by evolutionary selection. In particular, we show that evolutionary
-  selection can support non-veridical representations of payoffs in terms of regret.
-
-\item We argue that this ``meta-evolutionary'' approach could eventually help explain attested
-  deviations of human decision making from the classical ideal: choice behavior evolved to be
-  an ``ecologically rational'', near-optimal adaptation to the environment
+  reasonable additional assumptions, evolutionary selection can support non-veridical
+  representations of payoffs in terms of regret.
+  \begin{itemize}
+  \item We argue that this ``meta-evolutionary'' approach could eventually help explain
+    attested deviations of human decision making from the classical ideal: choice behavior
+    evolved to be an ``ecologically rational'', near-optimal adaptation to the environment
     \citep{Anderson1990:The-Adaptive-Ch,Anderson1991:Is-human-cognit,GigerenzerGoldstein1996:Reasoning-the-F,ChaterOaksford2000:The-Rational-An}. This
@@
     processes
-  \citep[e.g.][]{HammersteinStevens2012:Six-Reasons-for,FawcettHamblin2013:Exposing-the-be}. Here,
-  we seek to contribute to the formal machinery, an extension of evolutionary game theory, that
-  allows to capture statistical properties of the environment
-  \citep[cf.][]{McNamara2013:Towards-a-Riche}.
+    \citep[e.g.][]{HammersteinStevens2012:Six-Reasons-for,FawcettHamblin2013:Exposing-the-be}.
+  \item Non-veridical regret-based representations of payoffs are intuitively appealing (we do,
+    at least on occasion, care about counterfactual or hypothetical losses), but could also
+    help explain, for instance, that decision-makers may violate the independence axiom: human
+    and non-human decision makers can favor $A$ when presented with a choice
+    between $A$ and $B$, but prefer $B$ when presented with $A$, $B$ and $C$ \myalert{(for
+      animals cite from Fawcett page 3)} \myalert{(add
+      citation for human performance)}
+  \item We need to be careful here: we do not want to stress that this approach here (the
+    particular implemenation of a regret-based choice mechanism) explains these empirical
+    findings (better than any other line of explanation). Our point is more general and
+    methodological. Evolution of preferences is something that the literature on evolution of
+    choice mechanisms should care about. We also presented a method that can be useful and an
+    example of that method that should (succinctly) demonstrate our aforementioned conceptual
+    point that evolution of preferences is conceptually important and can give non-trivial,
+    unexpected and philosophically useful results.
+  \end{itemize}
 
@@
 
+\newpage
+
+\section*{Snippets}
+
+\begin{itemize}
+\item We present an approach to studying evolutionary selection of \emph{choice principles},
+  i.e., ways of choosing consistently across several games. In other words, we would like to
+  look at the problem of ``rational choice'' from an evolutionary point of view: what choice
+  principles would be promoted, which demoted in evolutionary competition amongst each other?
+
+\item This depends on the environment; it depends on what choice situations occur how
+  frequently. Maybe some choice principle is better in some situations, while another one is
+  better in others.
+
+\item We argue that this ``meta-evolutionary'' approach could eventually help explain attested
+  deviations of human decision making from the classical ideal: choice behavior evolved to be
+  an ``ecologically rational'', near-optimal adaptation to the environment
+  \citep{Anderson1990:The-Adaptive-Ch,Anderson1991:Is-human-cognit,GigerenzerGoldstein1996:Reasoning-the-F,ChaterOaksford2000:The-Rational-An}. This
+  is inline with recent aspirations to provide an evolutionary rationale for decision making
+  processes
+  \citep[e.g.][]{HammersteinStevens2012:Six-Reasons-for,FawcettHamblin2013:Exposing-the-be}. Here,
+  we seek to contribute to the formal machinery, an extension of evolutionary game theory, that
+  allows to capture statistical properties of the environment
+  \citep[cf.][]{McNamara2013:Towards-a-Riche}.
+\end{itemize}
+
 \end{document}

### 2015-05-27 paper/paper.tex
section 2 by Paolo

--- 2015-05-21 paper/paper.tex
@@
 \usepackage[]{helpers/mypackages}
+
 %\usepackage[natbib=true,style=authoryear-comp,backend=bibtex,doi=false,url=false]{biblatex}
+
 \bibliography{helpers/MyRefLocal}
@@
 \section{Faces of rationality}
+
+VERSION 1
+
+A central pivot in economics and decision theory is the definition of rationality as maximization of subjective preferences.
+The subjectivity of preferences plays a very important role.
+From an agent's standpoint, the amount of, say, money achieved does not necessarily coincide with the amount of subjective utility attained.
+The first to notice this difference between objective utility (goods, money, etc.) and subjective utility (preferences) was D.
+Bernoulli in the famous St.
+Petersburg paradox.
+Moreover, Bernoulli introduced the idea that subjective utility can be represented by an increasing concave function of objective utility.
+This can be considered the birth of modern decision theory.
+Another important step was developed by Kahnemann and Tversky who introduced prospect theory in their famous paper from 1979.
+By means of experimental results they noticed that the decision maker apparently acts as a risk averse agent with respect to gains and as a risk loving agent with respect to losses.
+Consequently, they conjectured that the subjective utility is better representable by an S-shaped utility function, concave in the positive domain of gains and convex in the negative domain of losses.
+More recently, other possible definitions of the subjective utility function have been proposed and justified from a game theoretical point of view (e.g.
+Fehr and Schmidt, Charness and Rabin, etc.).
+The central goal of these studies is to explain/describe the behavior in social dilemmas (e.g., Prisoner's dilemma, public goods game, etc.).
+By means of different subjective utility functions, it is then possible to describe/match the behavior observed in experiments and to explain it as rational (in the sense of maximizing the subjective utility).
+\\
+With this approach it seems that every behavior, no matter how far from the maximization of objective utility, can be deemed as rational if we can only find a subjective utility that justifies that behavior as maximizing the subjective utility.
+Quoting Hegel, (almost) everything real is rational.
+The problem with this approach is that it seems that everything that is observed can be considered rational, given the adequate subjective utility.
+The notion of rationality almost collapses onto the observed behavior.
+
+On the other side, other economists (Alchian, Friedman) seem to link the notion of rationality more tightly to the maximization of objective utility.
+In their classic works they argue that profit maximization is a reasonable assumption for characterizing outcomes in a competitive market because only firms behaving in a manner that is consistent with profit maximization will survive in the long run.
+If the previous accounts of rationality looked more descriptive, this definitely tastes more normative.
+In this sense, the normative notion of rationality is tightly linked to (and almost coincide with) the maximization of objective utility, which is supposed to drive the evolutionary process.
+It follows then that being normative in this sense seems to entail an identification of rationality with maximization of objective utility.
+
+It seems that we are stuck between two extrema.
+On the one hand, if we want to have a descriptive notion of rationality, then it seems we can (almost) always define an appropriate subjective utility whose maximization matches the observed behavior.
+On the other hand, if we want to have a normative approach to rationality, then it seems we have to appeal to evolutionary arguments implying the understanding of rationality as maximization of objective utility.
+
+The meta-game perspective that we introduce here can shed more light on this duality, and opens some space in between the two extrema.
+By keeping the evolutionary approach we want to retain a normative perspective on rationality, but our results show that (under certain conditions) evolution does not necessarily lead to identifying rationality with maximization of objective utility.
+More precisely, from the meta-game perspective many possible subjective transformations of the objective utility are eliminated by evolution, but we find some evolutionarily stable subjective utility maximizers whose utility does not coincide with the objective evolutionary utility.
+This result leaves some room in between the two extrema: we can understand rationality in a normative way, given by evolution, without having to discard all the possible subjective utility representations as irrational.
+
+In particular, in the following we mainly deal with two types of agents: players whose utility function coincides with the objective utility, and players whose subjective utility is defined in terms of regret.
+The justification for this choice is both historical and behavioral.
+Among the possible competitors of utility maximization, regret has always been in a prominent position, both from a descriptive and normative viewpoint.
+Indeed, Bell82 writes
+\begin{quote}
+By explicitly incorporating regret, expected utility theory not only becomes a better descriptive predictor but also may become a more convincing guide for prescribing behavior to decision makers.
+\end{quote}
+
+\citet{LoomesSugden1982:Regret-Theory:-} show that a regret-based theory of choice can match and explain the main experimental results of prospect theory, and claim that
+\begin{quote}
+
+[...] we shall challenge the idea that the conventional axioms constitute the only acceptable basis for rational choice under uncertainty.
+We shall argue that it is no less rational to act in accordance with regret theory, and that conventional expected utility theory therefore represents an unnecessarily restrictive notion of rationality.
+\cite{loosug82}
+
+\end{quote}
+
+...
+
+END VERSION 1
+
+VERSION 2
+
+The importance of aiming at a richer evolutionary game theory has been recently emphasized by many works in theoretical biology and behavioral ecology [Fawcett\&al., McNamara, etc.].
+The biological argument to embrace this goal is related to the criticisms towards the so-called behavioral gambit [Fawcett\&al.].
+The behavioral gambit denotes the standard approach in evolutionary game theory that puts the focus of attention on the expressed behavior, and neglects the underlying mechanisms that generate that behavior.
+From this point of view, the benefit and the reliability coming from the use of evolutionary game theory for biological purposes is also under attack.
+There are good reasons to claim that focusing on the general psychological mechanisms instead of on behavior itself as the phenotype under evolutionary selection can be more faithful and insightful for natural biology and ecology [Fawcett\&al.].
+Standard evolutionary game theory normally models the agents as playing a single fixed game, and as genetically predetermined to play fixed strategies, that consequently are the only target of natural selection in those frameworks.
+Standard models of evolutionary game theory cannot take charge of this shift of perspective until they will keep modelling a single game at a time, and until they will keep focusing on actions considered genetically encoded and fixed.
+''Instead we should expect animals to have evolved a set of psychological mechanisms which enable them to perform well on average across a range of different circumstances''[Fawcett\&al.].
+
+Attempts to overcome the behavioral gambit have recently been developed in economic literature too.
+In the last twenty years economists have been using evolutionary game-theoretical models to study evolution of preferences [cite], instead of evolution of behavior only.
+This approach is called indirect evolutionary approach, because players' behavior and actions stem from their subjective preferences, and it is aimed at investigating what subjective preferences are evolutionarily better off and robust with respect to natural selection.
+This shift from a direct evolutionary approach about observed actions and behavior to an indirect evolutionary approach takes only partly into account the behavioral gambit criticized by biologists and ecologists.
+The reason is that the models of evolution of preferences usually consider only one game at a time.
+This means that there is a single type of interaction that is supposed to drive the whole evolution of preferences: preferences are selected on the basis of one possible interaction only.
+Clearly, this approach does not take into consideration the variety of possible circumstances that animals are supposed to face during their lifetime.
+
+The meta-game model we propose pays heed to both components of the behavioral gambit.
+We retain the indirect evolutionary approach, but our agents in the population play over a class of possible games $\mathcal{G}$.
+In this way we explicitly model a range of different circumstances, as wished by theoretical biologists.
+Consequently, each agent in the population does not represent either a simple behavior or a subjective preference, but a more general player type that associates a subjective preference for each game in the class $\mathcal{G}$.
+The player type is supposed to encode the general psychological mechanisms that generate the behavior for any possible interaction in $\mathcal{G}$.
+These general psychological mechanisms then become the target of evolution, and they are selected based on the average fitness over a class of different interactions.
+
+In particular, in the following we mainly deal with two types of agents: players whose subjective preference coincides with the evolutionary fitness, and players whose subjective preference is defined in terms of regret.
+It turns out that psychological mechanisms and subjective conceptualizations based on regret can outperform more veridical conceptualizations coinciding with the evolutionary fitness.
+This is just an example of the kind of insights and results that we can gain by adopting a meta-game perspective and by shifting the focus of our attention to psychological mechanisms and subjective conceptualizations as the phenotype under selection.
+
+-maybe to add: difference with learning. Fawcett\&al. talk more about differences in learning, whereas we model differences in subjective conceptualizations.
+
+END VERSION 2
 

### 2015-05-27 paper/paper.tex
section 2 by Paolo

@@
 \usepackage[]{helpers/mypackages}
-
 %\usepackage[natbib=true,style=authoryear-comp,backend=bibtex,doi=false,url=false]{biblatex}
-
 \bibliography{helpers/MyRefLocal}
@@
 
+\newcommand{\myalert}[1]{\textcolor{red}{#1}}
+
 \title{Rationality, Evolution \& the Environment}
 \author{Paolo Galeazzi \& Michael Franke}
-\date{current version: May 18th 2015}
+\date{current version: May 27th 2015}
 
@@
 
-\section*{Outline of main argument}
+\section{Introduction / Motivation}
 
@@
     processes
-  \citep[e.g.][]{HammersteinStevens2012:Six-Reasons-for,FawcettHamblin2013:Exposing-the-be}. Here,
-  we seek to contribute to the formal machinery, an extension of evolutionary game theory, that
-  allows to capture statistical properties of the environment
-  \citep[cf.][]{McNamara2013:Towards-a-Riche}.
-
-\end{itemize}
-
-\newpage
-
-\section{Introduction / Motivation}
-
-\begin{itemize}
-\item evolutionary game theory about one game usually
-\item here class of games
-\item therefore partial solution to the ``closed game'' problem
-\item still not infinite, open ended strategy space
-\item focus on one example for this new method: competition between:
-  \begin{itemize}
-  \item probabilistic vs.~non-probabilistic uncertainty
-  \item veridical vs.~regret-based preferences
+    \citep[e.g.][]{HammersteinStevens2012:Six-Reasons-for,FawcettHamblin2013:Exposing-the-be}.
+  \item Non-veridical regret-based representations of payoffs are intuitively appealing (we do,
+    at least on occasion, care about counterfactual or hypothetical losses), but could also
+    help explain, for instance, that decision-makers may violate the independence axiom: human
+    and non-human decision makers can favor $A$ when presented with a choice
+    between $A$ and $B$, but prefer $B$ when presented with $A$, $B$ and $C$ \myalert{(for
+      animals cite from Fawcett page 3)} \myalert{(add
+      citation for human performance)}
+  \item We need to be careful here: we do not want to stress that this approach here (the
+    particular implemenation of a regret-based choice mechanism) explains these empirical
+    findings (better than any other line of explanation). Our point is more general and
+    methodological. Evolution of preferences is something that the literature on evolution of
+    choice mechanisms should care about. We also presented a method that can be useful and an
+    example of that method that should (succinctly) demonstrate our aforementioned conceptual
+    point that evolution of preferences is conceptually important and can give non-trivial,
+    unexpected and philosophically useful results.
   \end{itemize}
@@
 \end{itemize}
+
+\newpage
 

### 2015-05-27 paper/paper.tex
restructuring after Paolo section 2 first drafts

@@
 
-\section{Faces of rationality}
+\section{Rationality \& subjective preference}
 
-VERSION 1
+\subsection{What should be in this section?}
 
-A central pivot in economics and decision theory is the definition of rationality as maximization of subjective preferences.
-The subjectivity of preferences plays a very important role.
-From an agent's standpoint, the amount of, say, money achieved does not necessarily coincide with the amount of subjective utility attained.
-The first to notice this difference between objective utility (goods, money, etc.) and subjective utility (preferences) was D.
-Bernoulli in the famous St.
-Petersburg paradox.
-Moreover, Bernoulli introduced the idea that subjective utility can be represented by an increasing concave function of objective utility.
-This can be considered the birth of modern decision theory.
-Another important step was developed by Kahnemann and Tversky who introduced prospect theory in their famous paper from 1979.
-By means of experimental results they noticed that the decision maker apparently acts as a risk averse agent with respect to gains and as a risk loving agent with respect to losses.
-Consequently, they conjectured that the subjective utility is better representable by an S-shaped utility function, concave in the positive domain of gains and convex in the negative domain of losses.
-More recently, other possible definitions of the subjective utility function have been proposed and justified from a game theoretical point of view (e.g.
-Fehr and Schmidt, Charness and Rabin, etc.).
-The central goal of these studies is to explain/describe the behavior in social dilemmas (e.g., Prisoner's dilemma, public goods game, etc.).
-By means of different subjective utility functions, it is then possible to describe/match the behavior observed in experiments and to explain it as rational (in the sense of maximizing the subjective utility).
-\\
-With this approach it seems that every behavior, no matter how far from the maximization of objective utility, can be deemed as rational if we can only find a subjective utility that justifies that behavior as maximizing the subjective utility.
-Quoting Hegel, (almost) everything real is rational.
-The problem with this approach is that it seems that everything that is observed can be considered rational, given the adequate subjective utility.
-The notion of rationality almost collapses onto the observed behavior.
+\myalert{main purpose of this section: introduce max EU and min regret with some background,
+  definitions, simple example and reasons why we care to look at especially these}
 
-On the other side, other economists (Alchian, Friedman) seem to link the notion of rationality more tightly to the maximization of objective utility.
-In their classic works they argue that profit maximization is a reasonable assumption for characterizing outcomes in a competitive market because only firms behaving in a manner that is consistent with profit maximization will survive in the long run.
-If the previous accounts of rationality looked more descriptive, this definitely tastes more normative.
-In this sense, the normative notion of rationality is tightly linked to (and almost coincide with) the maximization of objective utility, which is supposed to drive the evolutionary process.
-It follows then that being normative in this sense seems to entail an identification of rationality with maximization of objective utility.
+\begin{itemize}
+  \item \todo[inline]{choose uniform consensual terminology for maximization of EU and regret minimization}
+\item classical notion of rationality: maximization of expected utilities
+  \begin{itemize}
+  \item human choice behavior seems to deviate from classical rational choice in many ways
+    \citep[most
+    notably][]{TverskyKahnemann1974:Judgement-under,KahnemannTversky1979:Prospect-Theory}
+  \end{itemize}
+\item historical competitor: regret minimization
+  \begin{itemize}
+  \item introduced by Savage \& Niehans independently
+  \item worked out (in parameterized form) by \citet{LoomesSugden1982:Regret-Theory:-} and
+    argued to outperform prospect theory
+  \item recently rediscovered by game theorists \citep{HalpernPass2012:Iterated-Regret} as a
+    possible partial explanation of some puzzles (e.g., Travellers Dilemma)
+  \end{itemize}
+\item definitions of max EU and min reg (with minimal formal notation); simple example where
+  they differ
+\item motivate why we are interested in regret minimization; e.g.:
+  \begin{itemize}
+  \item simple historical alternative; certain prima facie plausibility
+  \item argued to be empirically adequate (Loomes \& Sugden, Bell)
+  \item gives us intriguing results that nicely motivate the general approach of meta-games
+  \item non-independence of choices also for non-human decision makers (cite)
+  \end{itemize}
+\item here we care about game problems, not solitary decision problems
+\end{itemize}
 
-It seems that we are stuck between two extrema.
-On the one hand, if we want to have a descriptive notion of rationality, then it seems we can (almost) always define an appropriate subjective utility whose maximization matches the observed behavior.
-On the other hand, if we want to have a normative approach to rationality, then it seems we have to appeal to evolutionary arguments implying the understanding of rationality as maximization of objective utility.
+\subsection{Version 1}
 
-The meta-game perspective that we introduce here can shed more light on this duality, and opens some space in between the two extrema.
-By keeping the evolutionary approach we want to retain a normative perspective on rationality, but our results show that (under certain conditions) evolution does not necessarily lead to identifying rationality with maximization of objective utility.
-More precisely, from the meta-game perspective many possible subjective transformations of the objective utility are eliminated by evolution, but we find some evolutionarily stable subjective utility maximizers whose utility does not coincide with the objective evolutionary utility.
-This result leaves some room in between the two extrema: we can understand rationality in a normative way, given by evolution, without having to discard all the possible subjective utility representations as irrational.
+A pivotal element of economics and decision theory is the definition of rationality as
+maximization of subjective preferences. The subjectivity of preferences plays a very important
+role. From an agent's standpoint, the amount of, say, money achieved does not necessarily
+coincide with the amount of subjective utility attained. The first to notice this difference
+between objective utility (goods, money, etc.) and subjective utility (preferences) was
+D. Bernoulli in the famous St. Petersburg paradox. Moreover, Bernoulli introduced the idea that
+subjective utility can be represented by an increasing concave function of objective
+utility. This can be considered the birth of modern decision theory.
 
-In particular, in the following we mainly deal with two types of agents: players whose utility function coincides with the objective utility, and players whose subjective utility is defined in terms of regret.
-The justification for this choice is both historical and behavioral.
-Among the possible competitors of utility maximization, regret has always been in a prominent position, both from a descriptive and normative viewpoint.
-Indeed, Bell82 writes
+Another important step was developed by Kahnemann and Tversky who introduced prospect theory in
+their famous paper from 1979. By means of experimental results they noticed that the decision
+maker apparently acts as a risk averse agent with respect to gains and as a risk loving agent
+with respect to losses. Consequently, they conjectured that the subjective utility is better
+representable by an S-shaped utility function, concave in the positive domain of gains and
+convex in the negative domain of losses.
+
+More recently, other possible definitions of the subjective utility function have been proposed
+and justified from a game theoretical point of view (e.g. Fehr and Schmidt, Charness and Rabin,
+etc.). The central goal of these studies is to explain/describe the behavior in social dilemmas
+(e.g., Prisoner's dilemma, public goods game, etc.). By means of different subjective utility
+functions, it is then possible to describe/match the behavior observed in experiments and to
+explain it as rational (in the sense of maximizing the subjective utility).
+
+With this approach it seems that every behavior, no matter how far from the maximization of
+objective utility, can be deemed as rational if we can only find a subjective utility that
+justifies that behavior as maximizing the subjective utility. Quoting Hegel, (almost)
+everything real is rational. The problem with this approach is that it seems that everything
+that is observed can be considered rational, given the adequate subjective utility. The notion
+of rationality almost collapses onto the observed behavior.
+
+On the other side, other economists (Alchian, Friedman) seem to link the notion of rationality
+more tightly to the maximization of objective utility. In their classic works they argue that
+profit maximization is a reasonable assumption for characterizing outcomes in a competitive
+market because only firms behaving in a manner that is consistent with profit maximization will
+survive in the long run. If the previous accounts of rationality looked more descriptive, this
+definitely tastes more normative. In this sense, the normative notion of rationality is tightly
+linked to (and almost coincide with) the maximization of objective utility, which is supposed
+to drive the evolutionary process. It follows then that being normative in this sense seems to
+entail an identification of rationality with maximization of objective utility.
+
+It seems that we are stuck between two extrema. On the one hand, if we want to have a
+descriptive notion of rationality, then it seems we can (almost) always define an appropriate
+subjective utility whose maximization matches the observed behavior. On the other hand, if we
+want to have a normative approach to rationality, then it seems we have to appeal to
+evolutionary arguments implying the understanding of rationality as maximization of objective
+utility.
+
+The meta-game perspective that we introduce here can shed more light on this duality, and opens
+some space in between the two extrema. By keeping the evolutionary approach we want to retain a
+normative perspective on rationality, but our results show that (under certain conditions)
+evolution does not necessarily lead to identifying rationality with maximization of objective
+utility. More precisely, from the meta-game perspective many possible subjective
+transformations of the objective utility are eliminated by evolution, but we find some
+evolutionarily stable subjective utility maximizers whose utility does not coincide with the
+objective evolutionary utility. This result leaves some room in between the two extrema: we can
+understand rationality in a normative way, given by evolution, without having to discard all
+the possible subjective utility representations as irrational.
+
+In particular, in the following we mainly deal with two types of agents: players whose utility
+function coincides with the objective utility, and players whose subjective utility is defined
+in terms of regret. The justification for this choice is both historical and behavioral. Among
+the possible competitors of utility maximization, regret has always been in a prominent
+position, both from a descriptive and normative viewpoint. Indeed, Bell82 writes
 \begin{quote}
-By explicitly incorporating regret, expected utility theory not only becomes a better descriptive predictor but also may become a more convincing guide for prescribing behavior to decision makers.
+  By explicitly incorporating regret, expected utility theory not only becomes a better
+  descriptive predictor but also may become a more convincing guide for prescribing behavior to
+  decision makers.
+\end{quote}
+\citet{LoomesSugden1982:Regret-Theory:-} show that a regret-based theory of choice can match
+and explain the main experimental results of prospect theory, and claim that
+\begin{quote} [...] we shall challenge the idea that the conventional axioms [of decision
+  theory] constitute the only acceptable basis for rational choice under uncertainty. We shall
+  argue that it is no less rational to act in accordance with regret theory, and that
+  conventional expected utility theory therefore represents an unnecessarily restrictive notion
+  of rationality. \hfill \citep{LoomesSugden1982:Regret-Theory:-}
 \end{quote}
 
-\citet{LoomesSugden1982:Regret-Theory:-} show that a regret-based theory of choice can match and explain the main experimental results of prospect theory, and claim that
-\begin{quote}
-
-[...] we shall challenge the idea that the conventional axioms constitute the only acceptable basis for rational choice under uncertainty.
-We shall argue that it is no less rational to act in accordance with regret theory, and that conventional expected utility theory therefore represents an unnecessarily restrictive notion of rationality.
-\cite{loosug82}
-
-\end{quote}
-
-...
-
-END VERSION 1
-
-VERSION 2
+\subsection{Version 2}
 
@@
 -maybe to add: difference with learning. Fawcett\&al. talk more about differences in learning, whereas we model differences in subjective conceptualizations.
-
-END VERSION 2
-
-\begin{itemize}
-  \item \todo[inline]{choose uniform consensual terminology for maximization of EU and regret minimization}
-\item classical notion of rationality: maximization of expected utilities
-  \begin{itemize}
-  \item human choice behavior seems to deviate from classical rational choice in many ways
-    \citep[most
-    notably][]{TverskyKahnemann1974:Judgement-under,KahnemannTversky1979:Prospect-Theory}
-  \end{itemize}
-\item historical competitor: regret minimization
-  \begin{itemize}
-  \item introduced by Savage \& Niehans independently
-  \item worked out (in parameterized form) by \citet{LoomesSugden1982:Regret-Theory:-} and
-    argued to outperform prospect theory
-  \item recently rediscovered by game theorists \citep{HalpernPass2012:Iterated-Regret} as a
-    possible partial explanation of some puzzles (e.g., Travellers Dilemma)
-  \end{itemize}
-\item motivate why we are interested in regret minimization; e.g.:
-  \begin{itemize}
-  \item simple historical alternative; certain prima facie plausibility
-  \item has both components of interest:
-    \begin{itemize}
-    \item epistemic component: probabilistic vs.~non-probabilistic uncertainty  (interesting
-      because of the classical Ellsberg paradox)
-    \item payoff component: veridical vs.~non-veridical preference representations (interesting
-      because of a recent interest in the ``evolution of preference'')
-    \item gives us intriguing results that nicely motivate the general approach of meta-games
-    \end{itemize}
-  \end{itemize}
-\end{itemize}
 

### 2015-06-05 paper/paper.tex
Paolo rewrite Version 1 of Section 2

@@
   part, of the evolutionary benefit of learning rules
-  \citep[e.g.][]{ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o}. (\myalert{More
-    references Harley 1981!!!, \dots}). Moreover, only little attention has been paid to
+  \citep[e.g.][]{ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o}. (\myalert{More references Harley 1981!!!, \dots}). 
+    Moreover, only little attention has been paid to
   modeling the direct (game-theoretic) meta-competition between alternative choice mechanisms
@@
 
-A pivotal element of economics and decision theory is the definition of rationality as
-maximization of subjective preferences. The subjectivity of preferences plays a very important
+The standard use of the word \textit{rationality} in economics and decision theory is to denote the maximization of subjective expected utility.
+Since the work by vNM [cite], this stance has been justified from the intuitive ''rationality'' of the axioms on the subjective preference relation leading to the representability of the decision maker as a subjective expected utility (SEU) maximizer.
+While in [vNM] the probability of the outcomes is objectively given a priori, Savage54 provides a set of axioms that represent the decision maker (DM) with both a subjective utility over outcomes \textit{and} a \textit{subjective} probability over states of the world.
+Savage's axioms constitute the foundation of subjective expected utility theory, that is normally assumed to define the rational behavior of economic agents.
+
+The subjectivity of preferences plays a very important
 role. From an agent's standpoint, the amount of, say, money achieved does not necessarily
-coincide with the amount of subjective utility attained. The first to notice this difference
+coincide with the amount of subjective utility attained. The first to notice and formally argue for this difference
 between objective utility (goods, money, etc.) and subjective utility (preferences) was
-D. Bernoulli in the famous St. Petersburg paradox. Moreover, Bernoulli introduced the idea that
-subjective utility can be represented by an increasing concave function of objective
+D. Bernoulli in the famous St. Petersburg paradox. Moreover, Bernoulli introduced the idea that a good representation of
+subjective utility can be carried out in terms of an increasing concave function of objective
 utility. This can be considered the birth of modern decision theory.
 
-Another important step was developed by Kahnemann and Tversky who introduced prospect theory in
+However, many violations of Savage's (and vNM's) axioms have been consistently observed in behavioral economics.
+Most of the attention has been focused on the Independence Axiom and the Sure-thing Principle.
+Allais' paradox and Ellsberg's paradox are examples of violations of these two axioms, and they are at the origin of Prospect theory [cite] and ambiguity in decision theory [cite].\\
+
+The main idea behind Ellesberg's paradox and the literature on ambiguity is that DM treats differently objective and subjective uncertainty.
+If the probability measure on the possible states of the world is not given a priori and ''known'', then observed preferences leave no room to represent  DM's beliefs via a probability measure on the possible states.
+The most common solution is then to represent DM's beliefs with a set of probability measures instead of a single one.
+
+Prospect theory was introduced by Kahnemann and Tversky in
 their famous paper from 1979. By means of experimental results they noticed that the decision
@@
 convex in the negative domain of losses.
+\\
 
@@
 etc.). The central goal of these studies is to explain/describe the behavior in social dilemmas
-(e.g., Prisoner's dilemma, public goods game, etc.). By means of different subjective utility
-functions, it is then possible to describe/match the behavior observed in experiments and to
+(e.g., Prisoner's dilemma, public goods game, etc.). In the same spirit of Prospect theory, by means of different subjective utility
+functions it is possible to describe/match the behavior observed in game theoretical experiments and to
 explain it as rational (in the sense of maximizing the subjective utility).
 
-With this approach it seems that every behavior, no matter how far from the maximization of
-objective utility, can be deemed as rational if we can only find a subjective utility that
+With this approach every behavior, no matter how far from the maximization of
+objective utility, can be deemed rational if we can only find a subjective utility that
 justifies that behavior as maximizing the subjective utility. Quoting Hegel, (almost)
-everything real is rational. The problem with this approach is that it seems that everything
-that is observed can be considered rational, given the adequate subjective utility. The notion
+everything real is rational (this is just for fun, I will take it away, no problem). The problem here is that it seems possible to consider rational everything
+that is observed, given the adequate subjective utility. The notion
 of rationality almost collapses onto the observed behavior.
 
-On the other side, other economists (Alchian, Friedman) seem to link the notion of rationality
+On the other side, other economists (Alchian, Friedman) seem to link the notion of rational choice
 more tightly to the maximization of objective utility. In their classic works they argue that
@@
 linked to (and almost coincide with) the maximization of objective utility, which is supposed
-to drive the evolutionary process. It follows then that being normative in this sense seems to
-entail an identification of rationality with maximization of objective utility.
+to drive the evolutionary process. It follows then that being normative in this sense points to an identification of rationality with maximization of objective utility.
 
-It seems that we are stuck between two extrema. On the one hand, if we want to have a
-descriptive notion of rationality, then it seems we can (almost) always define an appropriate
+It seems that we are stuck between two extrema: a too permissive descriptivism and a too restrictive normativism. On the one hand, if we want to have a
+descriptive notion of rationality, then we can (almost) always define an appropriate
 subjective utility whose maximization matches the observed behavior. On the other hand, if we
 want to have a normative approach to rationality, then it seems we have to appeal to
-evolutionary arguments implying the understanding of rationality as maximization of objective
+evolutionary arguments entailing the understanding of rationality as maximization of objective
 utility.
 
-The meta-game perspective that we introduce here can shed more light on this duality, and opens
-some space in between the two extrema. By keeping the evolutionary approach we want to retain a
+There is another violation of Savage's axioms that is particularly relevant for the present work: transitivity of preferences.
+The first of Savage's axioms states that the preference relation is a (total) preorder, i.e., reflexive and transitive.
+Moreover, the preorder axiom is often referred to as the rationality axiom [cite], as to suggest that it is somehow the core of rational preferences.
+Violations of transitivity have been observed and studied in experimental literature [citeTversky69,etc], but can also derive from a more theoretical and normative point of view.
+\\
+In what follows, an important focus of our work will be the role of regret in decision making.
+Regret theory predicts the violation of both transitivity and Independence of Irrelevant Alternatives (IIA).
+[CONNECTING TO Fawcett\&al: this is IIA, not independence]
+
+\subsubsection{Regret theory}
+
+Regret theory has been introduced in decision theory by Savage [] and Niherens [], and later developed by Bell [1982], Loomes and Sugden [1982], and Fishburn [1982] independently.
+Lately, Halpern and Pass show how the use of regret minimization can solve games like the Centipede and the Traveler's dilemma in a way closer to everyday intuition and empirical data.
+In this paper the notion of regret is defined as in [HalPass12]:
+
+DEFINITION(regret): Given a simultaneous-move game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the regret of an action $a_i \in A_i$ is defined by: $\text{reg}(a_i)= \text{max}_{a_{-i}\in A_{-i}} \pi_i(a_i^*,a_{-i})-\pi_i(a_i,a_{-i}) $, where $a_i^*$ is $i$'s best reply to action $a_{-i} $.\\
+
+DEFINITION(regret minimization): Given a simultaneous-move game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, an action $a^{'}_i $ is regret minimizing if $a^{'}_i \in \text{min}_{a_i} \text{max}_{a_{-i}} \pi_i(a_i^*,a_{-i})-\pi_i(a_i,a_{-i}) $.\\
+
+EXAMPLE. Traveler's dilemma maybe? or maybe 2
+
+The meta-game perspective that we introduce here can shed more light on the duality of descriptivism and normativism, and opens
+some space in between the two extrema. 
+By keeping the evolutionary approach we want to retain a
 normative perspective on rationality, but our results show that (under certain conditions)
 evolution does not necessarily lead to identifying rationality with maximization of objective
-utility. More precisely, from the meta-game perspective many possible subjective
+utility.
+
+[More precisely, from the meta-game perspective many possible subjective
 transformations of the objective utility are eliminated by evolution, but we find some
@@
 understand rationality in a normative way, given by evolution, without having to discard all
-the possible subjective utility representations as irrational.
+the possible subjective utility representations as irrational. CHANGE PLACE OF THIS MAYBE]
 
-In particular, in the following we mainly deal with two types of agents: players whose utility
-function coincides with the objective utility, and players whose subjective utility is defined
-in terms of regret. The justification for this choice is both historical and behavioral. Among
+In the following we mainly deal with two types of agents: players whose subjective utility is defined
+in terms of regret (as in DEFINITION), and players whose utility
+function coincides with the objective utility $\pi_i$.
+
+The justification for this choice is both historical and behavioral. Among
 the possible competitors of utility maximization, regret has always been in a prominent
@@
 \citet{LoomesSugden1982:Regret-Theory:-} show that a regret-based theory of choice can match
-and explain the main experimental results of prospect theory, and claim that
+and explain all the main experimental results of prospect theory, and claim that
 \begin{quote} [...] we shall challenge the idea that the conventional axioms [of decision
@@
 -maybe to add: difference with learning. Fawcett\&al. talk more about differences in learning, whereas we model differences in subjective conceptualizations.
+
+[A pivotal element of economics and decision theory is the definition of rationality as
+maximization of subjective preferences.]
 

### 2015-06-10 paper/paper.tex
Paolo new version

@@
 
+\usepackage{bigints}
+\usepackage{MnSymbol}
 \usepackage{a4wide}
@@
 
-The standard use of the word \textit{rationality} in economics and decision theory is to denote the maximization of subjective expected utility.
-Since the work by vNM [cite], this stance has been justified from the intuitive ''rationality'' of the axioms on the subjective preference relation leading to the representability of the decision maker as a subjective expected utility (SEU) maximizer.
-While in [vNM] the probability of the outcomes is objectively given a priori, Savage54 provides a set of axioms that represent the decision maker (DM) with both a subjective utility over outcomes \textit{and} a \textit{subjective} probability over states of the world.
-Savage's axioms constitute the foundation of subjective expected utility theory, that is normally assumed to define the rational behavior of economic agents.
+The standard use of the word \textit{rationality} in economics and decision theory is to denote the maximization of (subjective) expected utility.
+Since the work by vNM [cite], this stance has been justified from the intuitive ''rationality'' of the axioms on the subjective preference relation leading to the representability of the decision maker as an expected utility maximizer.
+While in the axiomatization by [vNM] the probability of the outcomes is objectively given a priori, Savage54 provides a larger set of axioms that represent the decision maker (DM) with both a subjective utility over outcomes \textit{and} a \textit{subjective} probability over states of the world.
+Savage's axioms constitute the foundation of subjective expected utility (SEU) theory, that is normally assumed to define the rational behavior of economic agents.\\
+
+DEFINITION(SEU-maximization): Let $S$ be a set of states of the world, $X$ a set of outcomes and $A$ a set of actions.
+Given a probability measure $P$ on $S$ and a subjective utility function $u:X \rightarrow \mathbb{R} $, an action $a^*: S \rightarrow X $ is SEU-maximizing if $a^* \in \text{argmax}_{a_i \in A} \bigint_S u(a^*(s))dP(s) $.
+\\
 
 The subjectivity of preferences plays a very important
-role. From an agent's standpoint, the amount of, say, money achieved does not necessarily
-coincide with the amount of subjective utility attained. The first to notice and formally argue for this difference
+role for the present work. From an agent's standpoint, the amount $x$ of, say, money achieved does not necessarily
+coincide with the amount of subjective utility attained $u(x)$. 
+Historically,  the first to notice and formally argue for this difference
 between objective utility (goods, money, etc.) and subjective utility (preferences) was
-D. Bernoulli in the famous St. Petersburg paradox. Moreover, Bernoulli introduced the idea that a good representation of
+D. Bernoulli with the famous St. Petersburg paradox in 1738. Moreover, Bernoulli introduced the idea that a good representation of
 subjective utility can be carried out in terms of an increasing concave function of objective
@@
 
-However, many violations of Savage's (and vNM's) axioms have been consistently observed in behavioral economics.
+Empirically, many violations of Savage's (and vNM's) axioms have been consistently observed in behavioral economics.
 Most of the attention has been focused on the Independence Axiom and the Sure-thing Principle.
-Allais' paradox and Ellsberg's paradox are examples of violations of these two axioms, and they are at the origin of Prospect theory [cite] and ambiguity in decision theory [cite].\\
+Allais' paradox and Ellsberg's paradox are examples of violations of these two axioms, and they are at the origin of Prospect theory [cite] and ambiguity in decision theory [cite].
 
 The main idea behind Ellesberg's paradox and the literature on ambiguity is that DM treats differently objective and subjective uncertainty.
-If the probability measure on the possible states of the world is not given a priori and ''known'', then observed preferences leave no room to represent  DM's beliefs via a probability measure on the possible states.
+If the probability measure on the possible states of the world is not given a priori and not ''known'', then observed preferences leave no room to represent  DM's beliefs via a probability measure on the possible states.
 The most common solution is then to represent DM's beliefs with a set of probability measures instead of a single one.
@@
 Prospect theory was introduced by Kahnemann and Tversky in
-their famous paper from 1979. By means of experimental results they noticed that the decision
-maker apparently acts as a risk averse agent with respect to gains and as a risk loving agent
+their famous paper from 1979. By means of experimental results they noticed that DM apparently acts as a risk averse agent with respect to gains and as a risk loving agent
 with respect to losses. Consequently, they conjectured that the subjective utility is better
@@
 convex in the negative domain of losses.
-\\
 
@@
 and justified from a game theoretical point of view (e.g. Fehr and Schmidt, Charness and Rabin,
-etc.). The central goal of these studies is to explain/describe the behavior in social dilemmas
+etc.). The central goal of these studies is to explain/describe the empirical behavior in social dilemmas
 (e.g., Prisoner's dilemma, public goods game, etc.). In the same spirit of Prospect theory, by means of different subjective utility
@@
 explain it as rational (in the sense of maximizing the subjective utility).
-
 With this approach every behavior, no matter how far from the maximization of
 objective utility, can be deemed rational if we can only find a subjective utility that
-justifies that behavior as maximizing the subjective utility. Quoting Hegel, (almost)
-everything real is rational (this is just for fun, I will take it away, no problem). The problem here is that it seems possible to consider rational everything
-that is observed, given the adequate subjective utility. The notion
+justifies that behavior as maximizing the subjective utility. The problem here is that it seems possible to consider rational everything
+that is observed, given the adequate subjective utility function. The notion
 of rationality almost collapses onto the observed behavior.
@@
 survive in the long run. If the previous accounts of rationality looked more descriptive, this
-definitely tastes more normative. In this sense, the normative notion of rationality is tightly
-linked to (and almost coincide with) the maximization of objective utility, which is supposed
+definitely tastes more normative. In this sense, a normative notion of rationality would be tightly
+related to (and almost coincide with) the maximization of objective utility, which is supposed
 to drive the evolutionary process. It follows then that being normative in this sense points to an identification of rationality with maximization of objective utility.
@@
 
+However, it has been argued that in a good theory of choice and decision making the normative and the descriptive components should not come apart. For example, as Douglas Maclean [cite] writes:
+
+\begin{quote}
+The history of the subject reflects strong reasons why the theory of choice should have this dual character. [...] \\
+A normative theory of choice gains credibility from its predictive and explanatory power, for although empirical success itself may not constitute much of a normative argument, the theory of rational behavior is less likely to be found objectionable if rationality turns out to be widespread.
+[...] But if, on the other hand, the normative theory turns out to be incompatible with the best established behavioral theory, then the verification of the normative theory will depend entirely on the intrinsic plausibility of its axioms, and that appeal must be quite strong, strong enough to make us overcome our charitable reluctance to conclude that our actual behavior is systematically irrational.
+\end{quote}
+
 There is another violation of Savage's axioms that is particularly relevant for the present work: transitivity of preferences.
@@
 Moreover, the preorder axiom is often referred to as the rationality axiom [cite], as to suggest that it is somehow the core of rational preferences.
-Violations of transitivity have been observed and studied in experimental literature [citeTversky69,etc], but can also derive from a more theoretical and normative point of view.
+Violations of transitivity have been observed and studied in experimental literature [citeTversky69,etc], but can also be supported from a normative and theoretical point of view.
 \\
@@
 Regret theory has been introduced in decision theory by Savage [] and Niherens [], and later developed by Bell [1982], Loomes and Sugden [1982], and Fishburn [1982] independently.
-Lately, Halpern and Pass show how the use of regret minimization can solve games like the Centipede and the Traveler's dilemma in a way closer to everyday intuition and empirical data.
+Lately, Halpern and Pass [cite] show how the use of regret minimization can solve game theoretical puzzles (like the Centipede and the Traveller's dilemma) in a way that is closer to everyday intuition and empirical data.
 In this paper the notion of regret is defined as in [HalPass12]:
+
+\vspace{.5cm}
 
@@
 
-EXAMPLE. Traveler's dilemma maybe? or maybe 2
+EXAMPLE 1: \textit{Coordination Game.}
 
-The meta-game perspective that we introduce here can shed more light on the duality of descriptivism and normativism, and opens
+Let us consider the coordination game in Figure \ref{coordgame1}.
+
+\begin{figure}
+\begin{center}%
+\begin{tabular}{|c|c|c|}
+\hline 
+ & I & II\tabularnewline
+\hline 
+\hline 
+I & 1;1 & 0;0\tabularnewline
+\hline 
+II & 0;0 & 2;2\tabularnewline
+\hline 
+\end{tabular}\end{center}
+
+\protect\caption{A coordination game}
+\label{coordgame1}
+\end{figure}
+
+It is easy to see that $\text{reg}(I)=2$: when the other player chooses action $I$ the regret of $I$ is $0$ since $I$ is a best reply to $I$, and when the other player chooses $II$ the regret of $I$ is $2$ since $\pi_i(II,II)-\pi_i(I,II)=2$.
+With the same reasoning, $\text{reg}(II)=1$.
+Two regret minimizing players would then choose action $II$, each getting a payoff of $2$.
+In this case regret minimization selects the Pareto-dominant Nash equilibrium.
+$ \medsquare $
+
+\vspace{.5cm}
+
+EXAMPLE 2: \textit{The Traveller's Dilemma.} (HalpernPass12)
+
+Let us now consider the Traveller's Dilemma case.
+The story behind the game goes as follows.
+There are two travellers, Ann and Bob, who lost their luggages.
+Ann and Bob had exactly the same luggage and they had insured the luggages with the same insurance company.
+The insurance policy is that the two travellers have to separately claim a certain amount between 2\$ and 100\$ for the reimbursement, and if they both claim the same amount then they will be reimbursed by that amount.
+Otherwise, if one of them claims more than the other, then the one who claimed the higher amount will get the lower amount minus 2\$, while the one who claimed the lower amount will get what (s)he claimed plus 2\$.
+The game is symmetric, and the payoff function for both players is:\\
+$\pi_i(a_i,a_{-i}) =  \begin{cases} a_i \text{ \hspace{1cm} if } a_i = a_{-i} \\ a_i + 2 \text{ \hspace{.4cm} if } a_i < a_{-i} \\ a_{-i} -2 \text{ \hspace{.25cm} if } a_{-i} < a_i \end{cases}$ \\
+By a simple computation we have:  $\forall a_i \in \lbrace 96\$, ..., 100\$ \rbrace \text{, } \text{reg}(a_i)=3 $ and $\forall a_i \in \lbrace 2\$, ..., 95\$ \rbrace \text{, } \text{reg}(a_i)>3$.
+If we now eliminate all the actions that do not minimize regret in the first place and iterate the regret minimization only on the action set $\lbrace 96\$, ..., 100\$ \rbrace$, we get that 97\$ is the action that minimize regret.
+Indeed, $\text{reg}(97)=2$ and $\forall a_i \in \lbrace 96\$, 98\$, 99\$, 100\$ \rbrace \text{, } \text{reg}(a_i)=3 $.
+Hence, one step of regret minimizing reasoning eliminates all the actions smaller than 96\$, and if we iterate the process once more the unique outcome is 97\$.
+Finally, it is worth noticing that the only rationalizable equilibrium of the game corresponds to the outcome $(2,2)$, that is consequently the only Nash equilibrium, the only perfect equilibrium, and the only sequential equilibrium of the game.
+$ \medsquare $\\
+
+The meta-game perspective that we introduce in this paper can shed more light on the duality of descriptivism and normativism, and opens
 some space in between the two extrema. 
@@
 evolution does not necessarily lead to identifying rationality with maximization of objective
-utility.
-
-[More precisely, from the meta-game perspective many possible subjective
-transformations of the objective utility are eliminated by evolution, but we find some
-evolutionarily stable subjective utility maximizers whose utility does not coincide with the
-objective evolutionary utility. This result leaves some room in between the two extrema: we can
-understand rationality in a normative way, given by evolution, without having to discard all
-the possible subjective utility representations as irrational. CHANGE PLACE OF THIS MAYBE]
+utility, contrary to the intuition of Alchian [cite] and Friedman [cite].
 
@@
 the possible competitors of utility maximization, regret has always been in a prominent
-position, both from a descriptive and normative viewpoint. Indeed, Bell82 writes
+position, both from a descriptive and normative viewpoint. Indeed, Bell82 writes:
 \begin{quote}
@@
 \end{quote}
-\citet{LoomesSugden1982:Regret-Theory:-} show that a regret-based theory of choice can match
+In the same year, Graham Loomes and Robert Sugden \citet{LoomesSugden1982:Regret-Theory:-} show that a regret-based theory of choice can match
 and explain all the main experimental results of prospect theory, and claim that
@@
 \end{quote}
-
-\subsection{Version 2}
-
-The importance of aiming at a richer evolutionary game theory has been recently emphasized by many works in theoretical biology and behavioral ecology [Fawcett\&al., McNamara, etc.].
-The biological argument to embrace this goal is related to the criticisms towards the so-called behavioral gambit [Fawcett\&al.].
-The behavioral gambit denotes the standard approach in evolutionary game theory that puts the focus of attention on the expressed behavior, and neglects the underlying mechanisms that generate that behavior.
-From this point of view, the benefit and the reliability coming from the use of evolutionary game theory for biological purposes is also under attack.
-There are good reasons to claim that focusing on the general psychological mechanisms instead of on behavior itself as the phenotype under evolutionary selection can be more faithful and insightful for natural biology and ecology [Fawcett\&al.].
-Standard evolutionary game theory normally models the agents as playing a single fixed game, and as genetically predetermined to play fixed strategies, that consequently are the only target of natural selection in those frameworks.
-Standard models of evolutionary game theory cannot take charge of this shift of perspective until they will keep modelling a single game at a time, and until they will keep focusing on actions considered genetically encoded and fixed.
-''Instead we should expect animals to have evolved a set of psychological mechanisms which enable them to perform well on average across a range of different circumstances''[Fawcett\&al.].
-
-Attempts to overcome the behavioral gambit have recently been developed in economic literature too.
-In the last twenty years economists have been using evolutionary game-theoretical models to study evolution of preferences [cite], instead of evolution of behavior only.
-This approach is called indirect evolutionary approach, because players' behavior and actions stem from their subjective preferences, and it is aimed at investigating what subjective preferences are evolutionarily better off and robust with respect to natural selection.
-This shift from a direct evolutionary approach about observed actions and behavior to an indirect evolutionary approach takes only partly into account the behavioral gambit criticized by biologists and ecologists.
-The reason is that the models of evolution of preferences usually consider only one game at a time.
-This means that there is a single type of interaction that is supposed to drive the whole evolution of preferences: preferences are selected on the basis of one possible interaction only.
-Clearly, this approach does not take into consideration the variety of possible circumstances that animals are supposed to face during their lifetime.
-
-The meta-game model we propose pays heed to both components of the behavioral gambit.
-We retain the indirect evolutionary approach, but our agents in the population play over a class of possible games $\mathcal{G}$.
-In this way we explicitly model a range of different circumstances, as wished by theoretical biologists.
-Consequently, each agent in the population does not represent either a simple behavior or a subjective preference, but a more general player type that associates a subjective preference for each game in the class $\mathcal{G}$.
-The player type is supposed to encode the general psychological mechanisms that generate the behavior for any possible interaction in $\mathcal{G}$.
-These general psychological mechanisms then become the target of evolution, and they are selected based on the average fitness over a class of different interactions.
-
-In particular, in the following we mainly deal with two types of agents: players whose subjective preference coincides with the evolutionary fitness, and players whose subjective preference is defined in terms of regret.
-It turns out that psychological mechanisms and subjective conceptualizations based on regret can outperform more veridical conceptualizations coinciding with the evolutionary fitness.
-This is just an example of the kind of insights and results that we can gain by adopting a meta-game perspective and by shifting the focus of our attention to psychological mechanisms and subjective conceptualizations as the phenotype under selection.
-
--maybe to add: difference with learning. Fawcett\&al. talk more about differences in learning, whereas we model differences in subjective conceptualizations.
-
-[A pivotal element of economics and decision theory is the definition of rationality as
-maximization of subjective preferences.]
 
@@
 
+[More precisely, from the meta-game perspective many possible subjective
+transformations of the objective utility are eliminated by evolution, but we find some
+evolutionarily stable subjective utility maximizers whose utility does not coincide with the
+objective evolutionary utility. This result leaves some room in between the two extrema: we can
+understand rationality in a normative way, given by evolution, without having to discard all
+the possible subjective utility representations as irrational. CHANGE PLACE OF THIS MAYBE]
+
+\subsection{Version 2}
+
+The importance of aiming at a richer evolutionary game theory has been recently emphasized by many works in theoretical biology and behavioral ecology [Fawcett\&al., McNamara, etc.].
+The biological argument to embrace this goal is related to the criticisms towards the so-called behavioral gambit [Fawcett\&al.].
+The behavioral gambit denotes the standard approach in evolutionary game theory that puts the focus of attention on the expressed behavior, and neglects the underlying mechanisms that generate that behavior.
+From this point of view, the benefit and the reliability coming from the use of evolutionary game theory for biological purposes is also under attack.
+There are good reasons to claim that focusing on the general psychological mechanisms instead of on behavior itself as the phenotype under evolutionary selection can be more faithful and insightful for natural biology and ecology [Fawcett\&al.].
+Standard evolutionary game theory normally models the agents as playing a single fixed game, and as genetically predetermined to play fixed strategies, that consequently are the only target of natural selection in those frameworks.
+Standard models of evolutionary game theory cannot take charge of this shift of perspective until they will keep modelling a single game at a time, and until they will keep focusing on actions considered genetically encoded and fixed.
+''Instead we should expect animals to have evolved a set of psychological mechanisms which enable them to perform well on average across a range of different circumstances''[Fawcett\&al.].
+
+Attempts to overcome the behavioral gambit have recently been developed in economic literature too.
+In the last twenty years economists have been using evolutionary game-theoretical models to study evolution of preferences [cite], instead of evolution of behavior only.
+This approach is called indirect evolutionary approach, because players' behavior and actions stem from their subjective preferences, and it is aimed at investigating what subjective preferences are evolutionarily better off and robust with respect to natural selection.
+This shift from a direct evolutionary approach about observed actions and behavior to an indirect evolutionary approach takes only partly into account the behavioral gambit criticized by biologists and ecologists.
+The reason is that the models of evolution of preferences usually consider only one game at a time.
+This means that there is a single type of interaction that is supposed to drive the whole evolution of preferences: preferences are selected on the basis of one possible interaction only.
+Clearly, this approach does not take into consideration the variety of possible circumstances that animals are supposed to face during their lifetime.
+
+The meta-game model we propose pays heed to both components of the behavioral gambit.
+We retain the indirect evolutionary approach, but our agents in the population play over a class of possible games $\mathcal{G}$.
+In this way we explicitly model a range of different circumstances, as wished by theoretical biologists.
+Consequently, each agent in the population does not represent either a simple behavior or a subjective preference, but a more general player type that associates a subjective preference for each game in the class $\mathcal{G}$.
+The player type is supposed to encode the general psychological mechanisms that generate the behavior for any possible interaction in $\mathcal{G}$.
+These general psychological mechanisms then become the target of evolution, and they are selected based on the average fitness over a class of different interactions.
+
+In particular, in the following we mainly deal with two types of agents: players whose subjective preference coincides with the evolutionary fitness, and players whose subjective preference is defined in terms of regret.
+It turns out that psychological mechanisms and subjective conceptualizations based on regret can outperform more veridical conceptualizations coinciding with the evolutionary fitness.
+This is just an example of the kind of insights and results that we can gain by adopting a meta-game perspective and by shifting the focus of our attention to psychological mechanisms and subjective conceptualizations as the phenotype under selection.
+
+-maybe to add: difference with learning. Fawcett\&al. talk more about differences in learning, whereas we model differences in subjective conceptualizations.
+
+[A pivotal element of economics and decision theory is the definition of rationality as
+maximization of subjective preferences.]
+
 \begin{itemize}

### 2015-08-20 paper/paper.tex
Paolo new version; code adapted for paper

@@
 \usepackage{a4wide}
+
+\usepackage[T1]{fontenc}
 
@@
 DEFINITION(SEU-maximization): Let $S$ be a set of states of the world, $X$ a set of outcomes and $A$ a set of actions.
-Given a probability measure $P$ on $S$ and a subjective utility function $u:X \rightarrow \mathbb{R} $, an action $a^*: S \rightarrow X $ is SEU-maximizing if $a^* \in \text{argmax}_{a_i \in A} \bigint_S u(a^*(s))dP(s) $.
+Given a probability measure $P$ on $S$ and a subjective utility function $u:X \rightarrow \mathbb{R} $, an action $a^*: S \rightarrow X $ is SEU-maximizing if $a^* \in \text{argmax}_{a_i \in A} \int_S u(a^*(s))dP(s) $.
 \\
@@
 
-\subsubsection{Regret theory}
+\subsubsection{Regret theory} \label{sec:regreTheory}
 
@@
 
-\vspace{.5cm}
+\begin{definition}[Pairwise regret] \label{defn:parwreg}
+Given a simultaneous-move game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the regret of player $i$ at profile $(a_i,a_{-i})$ is defined by: $\text{reg}(a_i,a_{-i}):= \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $, where $a_i^\$ \in A_i$ denotes $i$'s best reply to action $a_{-i} $.
+\end{definition}
 
-DEFINITION(regret): Given a simultaneous-move game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the regret of an action $a_i \in A_i$ is defined by: $\text{reg}(a_i)= \text{max}_{a_{-i}\in A_{-i}} \pi_i(a_i^*,a_{-i})-\pi_i(a_i,a_{-i}) $, where $a_i^*$ is $i$'s best reply to action $a_{-i} $.\\
+\begin{definition}[Regret] \label{defn:regret}
+Given a simultaneous-move game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the regret of an action $a_i \in A_i$ is defined by: $\text{reg}(a_i):= \text{max}_{a_{-i}\in A_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $.
+\end{definition}
 
-DEFINITION(regret minimization): Given a simultaneous-move game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, an action $a^{'}_i $ is regret minimizing if $a^{'}_i \in \text{min}_{a_i} \text{max}_{a_{-i}} \pi_i(a_i^*,a_{-i})-\pi_i(a_i,a_{-i}) $.\\
+\begin{definition}[Regret minimization] \label{defn:regmin}
+Given a simultaneous-move game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, an action $a^{r}_i $ is regret minimizing if $a^{r}_i \in \text{min}_{a_i} \text{max}_{a_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $.
+\end{definition}
 
@@
 
-\protect\caption{A coordination game}
+\protect\caption{A coordination game $G^C$}
 \label{coordgame1}
@@
 
-\section{Evolution \& the environment}
+\section{The model}
 
-here we spell out our model
+We consider an evolutionary model that is different, for the best of our knowledge, from all the standard models of evolutionary game theory.
+Given a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, a subjective utility over $G$ is a function $\theta: A \rightarrow \mathbb{R} $, where $ A:=\prod_{i\in N}A_{i} $ as usual.
+We denote by $ \Theta:= \mathbb{R}^{|A|} $ the set of all the subjective utilities over $G$.
+The model we introduce here is a multiple game model, that we also call \textit{multi-game} or \textit{meta-game}, where a \textit{class} $\mathcal{G}$ of fitness games is played in a population.
+All the models used in evolutionary game theory that we are aware of always consider a single game at a time.
+Our extension is meant to capture both a more general notion of environment and a more general notion of phenotype.\\
+There are good reasons to claim that focusing on more general psychological mechanisms instead of on behavior itself as the phenotype under evolutionary selection can be more faithful and insightful for natural biology and ecology [Fawcett\&al.].
+In all classical models the agents are represented as playing a single fixed game, and as genetically predetermined to play fixed strategies, that consequently are the only target of natural selection in those frameworks.
+Standard evolutionary game theory cannot take charge of this shift of perspective until it will keep modelling a single game at a time, and until it will keep focusing on observed behavior only.
+''Instead we should expect animals to have evolved a set of psychological mechanisms which enable them to perform well on average across a range of different circumstances''[Fawcett\&al.].
+[maybe add evolution of preferences here]
+
+In this work we take $\mathcal{G}$ to be the class of symmetric $2 \times 2$ games\footnote{Note that this class includes many of the most famous games extensively considered in game theoretical literature, e.g., Prisoner's dilemma, Chicken game, Stag hunt, etc.}.
+First, a game $G$ is selected from the class of fitness games $\mathcal{G}$, and then players in the population are matched to play the game $G$.
+Each player is a function $\tau: \mathcal{G} \rightarrow  \Theta$, and we call $\tau$ a \textit{player type}, or just a \textit{type}\footnote{Notice that the function $\tau$ is well-defined since, for any symmetric $2 \times 2$ game, the codomain $\Theta=\mathbb{R}^{4}$ is the same.}.
+Intuitively, a type can be interpreted as a way of reasoning, a pattern of conceptualization, a thread that relates different subjective utilities across different games.
+We denote by $T$ the class of player types.
+For each game $G \in \mathcal{G}$, the evolutionary fitness is determined by the objective utility (payoff) function $\pi_G$, but the player's action choice depends on the player's subjective utility function $\tau(G)$, given by the player's type $\tau$.
+Notice that, for any symmetric game $G$, the action sets $(A_1, \dots, A_N)$ and the payoff functions $ (\pi_1, \dots, \pi_N)  $ are the same for all $i\in \lbrace 1, \dots N \rbrace$.
+Consequently, we only write $ A^G $ and $ \pi^G $ for the action set and the payoff function of game $G$, respectively.
+Moreover, in symmetric $2 \times 2$ games we have $A=A^G \times A^G$.
+Then, for $x,y \in A^G$ we denote by $\pi^G(x,y)$ the objective payoff of playing action $x$ in response to action $y$.\\
+
+\subsection{Player types}
+
+The set of all possible player types amouts to the set of all possible functions $ \tau: \mathcal{G} \rightarrow  \Theta $, i.e., $T=\mathbb{R}^{4^{\mathbb{R}^{4}}} $ , but for the sake of simplicity we will focus on types that are relevant and meaningful from a decision-theoretic point of view.
+We are mainly interested in two types: the objective type and the regret type.\\
+Given a game $G$ and Definition \ref{defn:parwreg}, it is straightforward to define the \textit{regret preference} $\theta^{reg}$ and the \textit{regret type} $\tau^{reg}$ as follows.
+
+\begin{definition}[Regret preference] \label{defn:regpref}
+
+For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the regret preference $ \theta^{reg}: A \rightarrow \mathbb{R} $ such that $ \theta^{reg}(a_i,a_{-i})=-\text{reg}(a_i,a_{-i}) $.\footnote{More precisely, this is the negative regret, whereas the (positive) regret, as defined in [halpass], would not have the minus sign at the beginning of the formula.
+Here it will be easier to define the regret in terms of negative regret.}
+
+\end{definition}
+
+\begin{definition}[Regret type] \label{defn:regtype}
+
+Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call regret type the function $\tau^{reg}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{reg}(G)= \theta^{reg}$.
+
+\end{definition}
+
+\noindent Similarly, let us define the \textit{objective preference} $\theta^{\pi}$ and the \textit{objective type} $ \tau^{\pi} $, that we also call $\pi$\textit{-type}, as follows.
+
+\begin{definition}[Objective preference] \label{defn:objpref}
+
+For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the objective preference $ \theta^{\pi}: A \rightarrow \mathbb{R} $ such that $ \theta^{\pi}(a_i,a_{-i})=\pi(a_i,a_{-i}) $.
+
+\end{definition}
+
+\begin{definition}[Objective type] \label{defn:objtype}
+
+Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call objective type, or $\pi$-type, the function $\tau^{\pi}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{\pi}(G)= \theta^{\pi}$.
+
+\end{definition}
+
+\noindent In other words, we consider two prominent player types: a type who has a veridical subjective utility that perfectly matches the objective utility (i.e., the evolutionary fitness); and a type who has a non-veridical regret-based subjective utility.
+
+\iffalse
+(maybe we want to introduce altruistic and competitive only later) Other types of player have been studied in the literature. A famous example is the \textit{altruistic type}.
+
+\begin{definition}[Altruistic preference] \label{defn:altpref}
+
+For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{alt}: A \rightarrow \mathbb{R} $ such that $ \theta^{alt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \sum_{j \neq i} \pi(a_{j},a_{-j})$.\footnote{A more general formulation [see: REFERENCES] would be to define an $ \alpha$-altruistic type, for $\alpha \in [0,1]$, with subjective utility $ \theta^{\alpha lt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \alpha \sum_{j \neq i} \pi(a_{j},a_{-j})$.
+Since we are not interested in the evolution of degrees of altruism here, we simply fix $ \alpha = 1 $.}
+
+\end{definition}
+
+\begin{definition}[Altruistic type] \label{defn:alttype}
+
+Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{alt}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{alt}(G)= \theta^{alt}$.
+
+\end{definition}
+
+\noindent As opposite to the altruistic type, it is possible to define a \textit{competitive type} as follows.
+
+\begin{definition}[Competitive preference] \label{defn:compref}
+
+For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{com}: A \rightarrow \mathbb{R} $ such that $ \theta^{com}(a_i,a_{-i})=\pi(a_i,a_{-i}) - \sum_{j \neq i} \pi(a_{j},a_{-j})$.
+
+\end{definition}
+
+\begin{definition}[Competitive type] \label{defn:comtype}
+
+Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{com}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{com}(G)= \theta^{com}$.
+
+\end{definition}
+
+\fi
+
+\subsection{Epistemic types}
+
+In line with traditional evolutionary game theory, the idea of this work is to model a population of rather unsophisticated and myopic agents that possibly differ from each other with respect to two components: the player type and the epistemic type.
+In full generality, we think of an epistemic type as a general disposition to form beliefs about the co-player’s behavior.
+Players in the population obviously face uncertainty about the composition of the population that they are part of, and consequently about the type of co-player that they are randomly paired with at each round and about the co-player's actions.
+We represent this uncertainty that players entertain in two different ways, a probabilistic flat belief and a non-probabilistic belief.
+This amounts to having two different epistemic types $e$ in the population, $e \in \lbrace \overline{\mu}, \Delta(A_{-i}) \rbrace $, where $\overline{\mu}$ is the probabilistic type and $\Delta(A_{-i})$ is the non-probabilistic type, defined as follows:
+
+\begin{itemize}
+
+\item $ \Delta(A_{-i}):=\lbrace \mu \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu(a_{-i}) = 1 \rbrace$;
+
+\item $\overline{\mu} \in \lbrace \mu \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu(a_{-i}) = 1 \rbrace$ is the probability measure over the co-player's actions such that: $\forall a_{-i} \in A_{-i}$, $\overline{\mu}(a_{-i})= \frac{1}{|A_{-i}|}$.
+
+\end{itemize}
+
+Hence, we consider two possible epistemic states in the face of uncertainty.
+The epistemic type $\Delta(A_{-i})$ represents a situation of non-probabilistic radical uncertainty, where the players are not able to narrow down the set of probability distributions over the co-player's actions and they consider all of them as possible.
+The other epistemic type $\overline{\mu}$ conceptualizes the uncertainty about the population by using the principle of insufficient reason and ascribes equal probability to all the possible alternatives.
+Both options are reasonable and justifiable ways to deal with situations of uncertainty [REFERENCES].
+\\
+Since for the moment we want to model populations of biologically unsophisticated players, we do not endow them with an effective learning procedure.
+Our players encode both a psychological subjective representation of the interaction (player type) and a conceptualization of uncertainty (epistemic type), but they are too simple to have any learning or belief updating procedure.
+From this point of view, we can take the learning process away from natural selection and focus on player types and epistemic types as the target of evolutionary pressure.
+
+\subsection{Uncertainty aversion and maxmin rule}
+
+Given a player type and an epistemic type, there are different ways to produce a behavior.
+A huge body of experimental literature strongly suggests that agents are generally uncertainty (or ambiguity) averse [REF].
+This pattern of behavior in the presence of ucertainty has been famously axiomatized by Gilboa and Schmeidler in a paper from 1989.
+The idea is that being uncertainty averse amounts to behaving in accordance with maximinimizing expected utility over a set of prior probabilities.
+Whenever the set of priors is a singleton, maximinization of expected utility coincides with maximization of expected utility.
+In line with empirical data, we assume that players in the population are uncertainty averse and conform to maxmin expected utility.
+The resulting behavior is then produced by maximinimizing over the subjective utility given by the player type and the set of priors given by the epistemic type.
+\\
+
+\begin{example}
+Consider the game in Figure \ref{coordgame1} again.
+When a player characterized by\footnote{To ease notation in the following we will refer to a player directly as a pair $(player \text{ } type \text{ } \tau,\text{ } epistemic\text{ } type \text{ } e)$.} player type $ \tau^{reg} $ and epistemic type $ \Delta(A_{-i}) $ faces the game in Figure \ref{coordgame1}, her player type gives rise to the representation $\tau^{reg}(G^C)$ in Figure \ref{coordgame1reg}.
+Then, maximinimizing expected utility over the probability simplex $ \Delta(A_{-i}) $ given the game in Figure \ref{coordgame1reg} corresponds to playing the standard maxmin strategy [REF] of that game.\footnote{Notice that this is the case for any game: given a game $G$, maximinimizing expected utility over the probability simplex $ \Delta(A_{-i}) $ amounts to playing the standard maxmin strategy of $G$.} This, in turn, corresponds to the regret minimizing action of the original game $G^C$ of Figure \ref{coordgame1}, namely action $II$, as we have seen in Section \ref{sec:regreTheory}.
+A player $(\tau^{reg},\overline{\mu})$ instead has subjective representation $\tau^{reg}(G^C)$ of Figure \ref{coordgame1reg} and a flat probability measure $\overline{\mu}=(\frac{1}{2}I,\frac{1}{2}II)$ over the co-player's actions.
+Consequently, such a player would play action $II$, i.e., the action that maximinimizes expected utility given the flat probability measure $\overline{\mu}$.\footnote{As we already noticed, maximinimizing expected utility given a probability measure $\mu$ is equivalent to maximizing expected utility given $\mu$.}
+Similarly, a player $(\tau^{\pi},\Delta(A_{-i}))$ will have the subjective representation coinciding with the objective fitness game, i.e., $ \tau^{\pi}(G^C)= G^C $.
+Then, both actions $I$ and $II$ maximinimize expected utility over the probability simplex $ \Delta(A_{-i}) $.
+Hence, a player $(\tau^{\pi},\Delta(A_{-i}))$ will be indifferent between $I$ and $II$, and will randomize with equal probability $(\frac{1}{2}I,\frac{1}{2}II)$.
+Finally, a player $(\tau^{\pi},\overline{\mu})$ maximinimizes the objective fitness game $G^C$ of Figure \ref{coordgame1} with flat probability $\overline{\mu}$ over the co-player's actions, i.e., maximizes objective utility given $\overline{\mu}$.
+In game $G^C$ this yields action $II$.
+
+\begin{figure}
+\begin{center}%
+\begin{tabular}{|c|c|c|}
+\hline 
+ & I & II\tabularnewline
+\hline 
+\hline 
+I & 0;0 & -2;-1\tabularnewline
+\hline 
+II & -1;-2 & 0;0\tabularnewline
+\hline 
+\end{tabular}\end{center}
+
+\protect\caption{Regret representation $\tau^{reg}(G^C)$}
+\label{coordgame1reg}
+\end{figure}
+
+\end{example}
+
+We are now in the position of deriving behavior directly from the pair $(\tau, e)$.
+Definitions \ref{def:utility-belief} and \ref{def:maxminSEU} simply formalize the notions of subjective expected utility and maxmin subjective expective utility, respectively.
+
+\begin{definition} \label{def:utility-belief}
+
+Given a game $G$, an action $a_i \in A_i$, and a belief $\mu \in \lbrace \mu' \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu'(a_{-i}) = 1 \rbrace$, we define $\tau(G)(a_i, \mu):= \sum_{a_{-i} \in A_{-i}} \tau(G)(a_i, a_{-i}) \cdot \mu(a_{-i})$.
+
+\end{definition}
+
+\begin{definition} \label{def:maxminSEU}
+
+Given a game $G$ and a player $(\tau, e)$, we define $\text{maxmin}(\tau(G), e):= \lbrace a'_i \in A_i : a_i \in \text{max}_{a_i \in A_i} \text{ min}_{\mu \in e} \text{ } \tau(G)(a_i, \mu) \rbrace$.
+
+\end{definition}
+
+\noindent Definition \ref{def:expected fitness} gives the expected evolutionary fitness of player $(\tau, e)$ against player $(\tau', e')$ in game $G$.\footnote{As already specified in the previous example, we assume that, whenever the set $\text{maxmin}(\tau(G), e)$ is not a singleton, the player $(\tau, e)$ will mix with equal probability among the actions in $\text{maxmin}(\tau(G), e)$.}
+
+\begin{definition} \label{def:expected fitness}
+
+Given a game $G \in \mathcal{G}$, a player $(\tau, e)$, and a player $(\tau', e')$, we define $\pi^G((\tau, e),(\tau', e')):= \pi^G(\text{maxmin}(\tau(G), e),\text{maxmin}(\tau'(G), e'))$.
+
+\end{definition}
+
+Many other alternatives different from maxmin expected utility could produce behavior: choice rules like minmax, maxmax, and minmin expected utility would similarly generate behavior from a player type and an epistemic type.
+Here we postulate that players are maximinimizers for two main reasons.
+First, our main interest is the evolution of different patterns of subjective conceptualizations of games (player types), and we want to show that the veridical representation (objective type) is not necessarily the fittest and may not be evolutionarily stable.
+Assuming that all players use the maxmin rule independent of their player type allows us to factor the choice rule out of the selection process and to focus on player types.
+Secondly, as already mentioned, among other possible choice rules maxmin is not only intuitively appealing but also corroborated from an empirical point of view.
+
+Before concluding this section, it is worth stressing two important points.
+
+\begin{fact} \label{fact:maxEU-minReg}
+
+For any given single probability $\mu$, maximization of expected utility and minimization of expected regret are behaviorally equivalent.
+
+\end{fact}
+
+\noindent As we have seen in the previous example, this is not the case in the presence of (radical) uncertainty, in the sense of representation of belief state in terms of a set of probability, as in $ \Delta(A_{-i}) $.
+
+\begin{fact} \label{fact:equivalence2x2}
+
+In the class of $2 \times 2$ symmetric games, players $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg},\overline{\mu})$ are behaviorally equivalent.
+
+\end{fact}
+
+\noindent We still treat them as distinct, because they will perform differently with respect to component-wise mutation (see below).
+Moreover, Fact \ref{fact:equivalence2x2} does not hold for $n \times n$ symmetric games in general.
+
+\subsection{Evolution \& the environment}
+
+[MAYBE, put part of Version2 from Snippets here, if not in Introduction]
+
+In standard evolutionary game theory a population of agents plays over a single game, that is supposed to represent the interaction driving the evolutionary dynamics.
+In line with [Fawcett-al.], we claim that the single-game approach is too limiting to encompass the vast variety of interactions that lead evolution.
+Here we propose the meta-game model in order to account for a more general notion of environment.
+By allowing the population to play over a class of possible games, we want to take into consideration a notion of environment that comprises a multitude of possible interactions as the driver of natural selection.
+In this perspective, the meta-game approach represents a model of evolution more faithful and possibly closer to reality.
+\\
+We assume a huge, possibly infinite, population of players $(\tau,e)$.
+At each time, a game $G$ is selected from the class of possible games, and players are randomly paired to play $G$.
+At the end of the play we keep track of the evolutionary fitness achieved by each player.
+Next, another game $G'$ is randomly selected again, and so on.
+The evolutionary fitness of each player is then based on the expected objective payoff over the class $\mathcal{G}$.
+Denoting by $P(G)$ the probability of game $G$ to be selected, the evolutionary fitness of player $(\tau,e)$ against player $(\tau',e')$ is given by:
+
+$$ EF((\tau,e),(\tau',e'))= \int_G  P(G) \cdot \pi^G((\tau, e),(\tau', e')).  $$
+
+\noindent The framework we propose here is a very neutral and flexible tool to model the notion of environment.
+We can take into account many different types of environment by simply changing the class $\mathcal{G}$ of possible games, and in the limit case where $\mathcal{G}$ is a sigleton our model reduces to the standard models of evolutionary game theory.
+By combining field studies and statistics, one could design a more specific class $\mathcal{G}$ with appropriate probabilities $P(G)$ in order to match the natural environment of a given population, but for our theoretical purposes we adopt another approach.
+As already anticipated, we take $\mathcal{G}$ to be the class of $2 \times 2$ symmetric games.
+More precisely, we imagine the class $\mathcal{G}$ to be generated from the generic form table of Figure \ref{generic form table}, where $a,b,c,d$ are i.i.d.
+random variables sampled from a finite set of natural numbers $ \lbrace \underline{n}, \dots, \overline{n}  \rbrace$.
+
+\begin{figure}
+\begin{center}%
+\begin{tabular}{|c|c|c|}
+\hline 
+ & I & II\tabularnewline
+\hline 
+\hline 
+I & a;a & b;c\tabularnewline
+\hline 
+II & c;b & d;d\tabularnewline
+\hline 
+\end{tabular}\end{center}
+
+\protect\caption{generic form table for $2 \times 2$ symmetric games}
+\label{generic form table}
+\end{figure}
+
+\section{Results}
+
+In this section we develop results by means of computer simulations and analytical proofs in parallel.
+
+\subsection{Statics}
+
+Table \ref{tab:reg vs obj} represent the result of simulations over $50.000$ games in $\mathcal{G}$ with $a,b,c,d \in \lbrace  0, \dots, 10 \rbrace$.
+The number in each cell corresponds to the average evolutionary fitness of the row player when matched with the column player.
+
+\begin{table}[]
+\centering
+\caption{Average evolutionary fitness in simulations of 50.000 symmetric $2 \times 2$ games}
+\label{tab:reg vs obj}
+\begin{tabular}{cccll}
+\cline{1-3}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{$\tau^{\pi}, \Delta(A_{-i})$} & \multicolumn{1}{c|}{$\tau^{reg}, \Delta(A_{-i})$} &  &  \\ \cline{1-3}
+\multicolumn{1}{|c|}{$\tau^{\pi}, \Delta(A_{-i})$} & \multicolumn{1}{c|}{6.131} & \multicolumn{1}{c|}{6.128} &  &  \\ \cline{1-3}
+\multicolumn{1}{|c|}{$\tau^{reg}, \Delta(A_{-i})$} & \multicolumn{1}{c|}{6.305} & \multicolumn{1}{c|}{6.302} &  &  \\ \cline{1-3}
+\multicolumn{1}{l}{}   & \multicolumn{1}{l}{}  & \multicolumn{1}{l}{}  &  & 
+\end{tabular}
+\end{table}
+
+Table \ref{tab:reg vs obj} shows that when players in the population are radically uncertain ($\Delta(A_{-i})$), the regret player $ \tau^{reg} $ outperforms the objective type $  \tau^{\pi} $, and $ \tau^{reg} $  is evolutionarily stable whereas $ \tau^{\pi} $ is not.
+This suggests that in the presence of uncertainty, in the sense of a set of probability measures, regret minimization is a better choice rule as compared with standard maxmin from an evolutionary point of view.
+\\
+\noindent Table \ref{tab:reg vs obj 2} reproduces the results about average evolutionary fitness out of 5.000 randomly generated symmetric $2 \times 2$ games when both types of epistemic uncertainty are present in the population.
+As we already highlighted in Fact \ref{fact:equivalence2x2}, $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{reg}, \overline{\mu})$, and $(\tau^{\pi}, \overline{\mu})$ are behaviorally equivalent, and their evolutionary fitness is indeed the same.
+[WARNING: it is not exactly identical here, this is probably related to a difference in tie-breaking that is probably a bit different for player $\tau^{reg}, \Delta(A_{-i})$.
+VERIFY and EQUALIZE.]\\
+Consequently, players $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{reg}, \overline{\mu})$, and $(\tau^{\pi}, \overline{\mu})$ are neutrally stable, and again $(\tau^{\pi}, \Delta(A_{-i}))$ is not.
+
+\begin{table*}[ht]
+\centering
+\begin{tabular}{ccccc}
+  \hline
+ & $\tau^{reg}, \Delta(A_{-i})$ 
+ & $\tau^{\pi}, \Delta(A_{-i})$ 
+ & $\tau^{reg}, \overline{\mu}$ 
+ & $\tau^{\pi}, \overline{\mu}$ \\ 
+  \hline
+  $\tau^{reg}, \Delta(A_{-i})$ & 6.629 & 6.653 &  6.636 & 6.636  \\ 
+  $\tau^{\pi}, \Delta(A_{-i})$  & 6.455 & 6.468 & 6.462 & 6.462  \\ 
+  $\tau^{reg}, \overline{\mu}$ & 6.633 & 6.658 & 6.634 & 6.634  \\ 
+  $\tau^{\pi}, \overline{\mu}$ & 6.633 & 6.658 & 6.634 & 6.634  \\   
+   \hline
+\end{tabular}
+\caption{Average evolutionary fitness in simulations of 5000 symmetric $2 \times 2$ games}
+\label{tab:reg vs obj 2}
+\end{table*}
+
+On the top of what we have seen so far, we can proceed with the main analytical results of the paper, which confirm our achievements from simulations.
+Let us call $\Lambda$ the set of possible players $( \tau, e  )$ in the population.
+We can now state the following proposition.
+
+\begin{proposition} \label{proposition1}
+
+Fix $\Lambda = \lbrace (\tau^{\pi}, \Delta(A_{-i})), (\tau^{reg}, \Delta(A_{-i})) \rbrace$ and $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex, set of i.i.d.
+values.
+Then, $(\tau^{reg}, \Delta(A_{-i}))$ is the only evolutionarily stable player in the population.
+
+\end{proposition}
+
+\begin{proof}
+See Appendix.
+\end{proof}
+
+From Fact \ref{fact:equivalence2x2} and Proposition \ref{proposition1} the following corollary follows.
+
+\begin{corollary} \label{corollary1}
+
+Fix $T = \lbrace \tau^{\pi}, \tau^{reg} \rbrace$, $E = \lbrace \Delta(A_{-i}), \overline{\mu}  \rbrace$, $\Lambda= T \times E$, and $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex, set of i.i.d.
+values.
+Then, players $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$ are neutrally stable, and $(\tau^{\pi}, \Delta(A_{-i}))$ is neither evolutionarily nor neutrally stable.
+
+\end{corollary}
+
+\begin{proof}
+See Appendix.
+\end{proof}
+
+\subsection{More types}
+
+In evolutionary game theory other types of player have been investigated.
+A famous example is the \textit{altruistic type} [REF], introduced in the literature in order to explain the possible survival of altruistic behavior.
+In our framework, we can represent the altruistic type as follows.
+
+\begin{definition}[Altruistic preference] \label{defn:altpref}
+
+For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{alt}: A \rightarrow \mathbb{R} $ such that $ \theta^{alt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \sum_{j \neq i} \pi(a_{j},a_{-j})$.\footnote{A more general formulation [see: REFERENCES] would be to define an $ \alpha$-altruistic type, for $\alpha \in [0,1]$, with subjective utility $ \theta^{\alpha lt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \alpha \sum_{j \neq i} \pi(a_{j},a_{-j})$.
+Since we are not interested in the evolution of degrees of altruism here, we simply fix $ \alpha = 1 $.}
+
+\end{definition}
+
+\begin{definition}[Altruistic type] \label{defn:alttype}
+
+Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{alt}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{alt}(G)= \theta^{alt}$.
+
+\end{definition}
+
+\noindent As opposite to the altruistic type, it is possible to define a \textit{competitive type}.
+
+\begin{definition}[Competitive preference] \label{defn:compref}
+
+For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{com}: A \rightarrow \mathbb{R} $ such that $ \theta^{com}(a_i,a_{-i})=\pi(a_i,a_{-i}) - \sum_{j \neq i} \pi(a_{j},a_{-j})$.
+
+\end{definition}
+
+\begin{definition}[Competitive type] \label{defn:comtype}
+
+Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{com}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{com}(G)= \theta^{com}$.
+
+\end{definition}
+
+Similarly to the evolutionary competition that we simulated before, we can study the evolutionary fitness of this extended set of players when they are all represented in the population.
+Table \ref{tab:Utils-MetaGame} shows the averge fitness of the enlarged competition.
+
+\begin{table*}[ht]
+\centering
+\begin{tabular}{ccccccccc}
+  \hline
+ & $\tau^{reg}, \Delta(A_{-i})$ 
+ & $\tau^{\pi}, \Delta(A_{-i})$ 
+ & $\tau^{alt}, \Delta(A_{-i})$
+ & $\tau^{com}, \Delta(A_{-i})$ \\ 
+  \hline
+  $\tau^{reg}, \Delta(A_{-i})$ & 6.629 & 6.653 & 5.806 & 7.089  \\ 
+  $\tau^{\pi}, \Delta(A_{-i})$  & 6.455 & 6.468 & 6.067 & 6.685  \\ 
+  $\tau^{alt}, \Delta(A_{-i})$ & 6.280 & 6.746 & 5.473 & 6.959 \\ 
+  $\tau^{com}, \Delta(A_{-i})$ & 5.936 & 5.735 & 5.336 & 6.379  \\ 
+   \hline
+\end{tabular}
+\caption{Average evolutionary fitness in simulations of 5000 symmetric $2 \times 2$ games}
+\label{tab:Utils-MetaGame}
+\end{table*}
+
+The following proposition confirms this result.
+
+\begin{proposition} \label{proposition2}
+
+Fix $\Lambda = \lbrace (\tau^{\pi}, \Delta(A_{-i})), (\tau^{reg}, \Delta(A_{-i})), (\tau^{alt}, \Delta(A_{-i})), (\tau^{com}, \Delta(A_{-i})) \rbrace$ and $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex, set of i.i.d.
+values.
+Then, $(\tau^{reg}, \Delta(A_{-i}))$ is the only evolutionarily stable player in the population.
+
+\end{proposition}
+
+\begin{proof}
+See Appendix.
+\end{proof}
+
+Finally, Table \ref{tab:Utils-MetaGame2} shows the average fitness when all the epistemic and player types introduced so far are simultaneously present in the population.
+[SAME WARNING: it is not exactly identical here, this is probably related to a difference in tie-breaking that is probably a bit different for player $\tau^{reg}, \Delta(A_{-i})$.
+VERIFY and EQUALIZE.]\\
+A monomorphic population of regret
+minimizers $\tuple{\tuple{\tau^{reg}, \Delta(A)}}$ is no longer
+evolutionarily stable: it could be invaded by expected utility maximizers of types $\tuple{\tau^{reg}, \bar{\mu}}$ and $\tuple{\tau^{\pi},
+  \bar{\mu}}$. Since the latter are behaviorally equivalent, neither
+is an evolutionarily stable strategy, but could at best be
+\emph{neutrally stable}
+\cite{Maynard-Smith1982:Evolution-and-t}. However, under our simulated
+meta-game payoffs from Table~\ref{tab:Utils-MetaGame2} any population
+consisting entirely of $\tuple{\tau^{reg}, \bar{\mu}}$ and
+$\tuple{\tau^{\pi}, \bar{\mu}}$ can be invaded by regret
+minimizers. This suggests that all three types would persist under
+standard evolutionary dynamics, in various relative proportions.
+
+Simulation results of the (discrete time) \emph{replicator dynamics}
+\cite{TaylorJonker1978:Evolutionary-St} indeed show that random
+initial population configurations are attracted to states with only
+three player types: $\tuple{\tau^{reg}, \Delta(A)}$,
+$\tuple{\tau^{reg}, \bar{\mu}}$ and $\tuple{\tau^{\pi},
+  \bar{\mu}}$. The relative proportions of these depend on the initial
+population. This variability is eradicated if we add a small mutation
+rate to the dynamics. We assume a fixed, small mutation rate
+$\epsilon$ for the probability that a player's preference type
+\emph{or} her epistemic type changes to another random preference type
+or epistemic type. The probability that a player type randomly mutates
+into a completely different player type with altogether different
+preference type and epistemic type would then be $\epsilon^2$. With
+these assumptions about ``local mutations'', numerical simulations of
+the (discrete time) \emph{replicator mutator dynamics}
+\cite{Nowak2006:Evolutionary-Dy} show that for very small
+mutation rates almost all initial populations converge to a single
+fixed point in which the majority of players are regret types. For
+instance, with $\epsilon = 0.001$, almost all initial populations are
+attracted to a final distribution with proportions:
+
+\begin{center}
+  \begin{tabular}{ccc}
+    $\tuple{\tau^{reg}, \Delta(A)}$ & $\tuple{\tau^{reg},
+      \bar{\mu}}$ & $\tuple{\tau^{\pi}, \bar{\mu}}$ \\ \hline
+    0.279  &   0.383 &    0.281 
+  \end{tabular}
+\end{center}
+
+Again, this shows that there are plausible and simple conditions under which
+agents who represent the game in terms of regret may be favored by
+evolutionary selection and that, more specifically, regret minimizers
+are evolutionarily supported.
+
+\begin{table*}[ht]
+\centering
+\begin{tabular}{ccccccccc}
+  \hline
+ & $\tuple{\tau^{reg}, \Delta(A)}$ 
+ & $\tuple{\tau^{\pi}, \Delta(A)}$ 
+ & $\tuple{\tau^{alt}, \Delta(A)}$
+ & $\tuple{\tau^{com}, \Delta(A)}$
+ & $\tuple{\tau^{reg}, \bar{\mu}}$ 
+ & $\tuple{\tau^{\pi}, \bar{\mu}}$ 
+ & $\tuple{\tau^{alt}, \bar{\mu}}$
+ & $\tuple{\tau^{com}, \bar{\mu}}$ \\ 
+  \hline
+  $\tuple{\tau^{reg}, \Delta(A)}$ & 6.629 & 6.653 & 5.806 & 7.089 & 6.636 & 6.636 & 5.793 & 7.463 \\ 
+  $\tuple{\tau^{\pi}, \Delta(A)}$  & 6.455 & 6.468 & 6.067 & 6.685 & 6.462 & 6.462 & 6.065 & 6.834 \\ 
+  $\tuple{\tau^{alt}, \Delta(A)}$ & 6.280 & 6.746 & 5.473 & 6.959 & 6.294 & 6.294 & 5.474 & 7.114 \\ 
+  $\tuple{\tau^{com}, \Delta(A)}$ & 5.936 & 5.735 & 5.336 & 6.379 & 5.929 & 5.929 & 5.327 & 6.538 \\ 
+  $\tuple{\tau^{reg}, \bar{\mu}}$ & 6.633 & 6.658 & 5.810 & 7.081 & 6.634 & 6.634 & 5.802 & 7.454 \\ 
+  $\tuple{\tau^{\pi}, \bar{\mu}}$ & 6.633 & 6.658 & 5.810 & 7.081 & 6.634 & 6.634 & 5.802 & 7.454 \\ 
+  $\tuple{\tau^{alt}, \bar{\mu}}$ & 6.278 & 6.750 & 5.476 & 6.953 & 6.293 & 6.293 & 5.484 & 7.112 \\ 
+  $\tuple{\tau^{com}, \bar{\mu}}$ & 6.311 & 5.885 & 5.475 & 6.536 & 6.299 & 6.299 & 5.466 & 7.123 \\ 
+   \hline
+\end{tabular}
+\caption{Average fitness in simulations of 5000
+  randomly generated $2 \times 2$ symmetric games.}
+\label{tab:Utils-MetaGame2}
+\end{table*}
+
+\subsection{Symmetric $n \times n$ games}
+
+...
+
+\subsection{Dynamics}
+
+ADD RESULTS FOR DYNAMICS
 
@@
 
+\section*{APPENDIX: Proofs}
+
+The proof of Proposition 1 relies on a partition of $\mathcal{G}$,
+and on some lemmas. For brevity, let us denote the regret minimizer
+by RM and the maximinimizer by MM. Since the proof is very long and
+all the other cases are similar and easier to prove, we focus here
+on the case of RM against MM players: we prove that RM is evolutionarily
+stable against MM, but MM is not evolutionarily stable against RM. By $EU_{\mathcal{G}}(x,y)$ we denote the expected \textit{objective} utility (or payoff), in terms
+of evolutionary fitness, of player type $x$ against player type $y$
+with respect to the class of fitness games $\mathcal{G}$.
+
+\medskip{}
+
+\textbf{Proof of Proposition 1.} By definition of evolutionary stability, we have to
+show that in the class $\mathcal{G}$ of symmetric $2\times2$ games generated by i.i.d. sampling
+from a finite or compact and convex set of values, it holds:
+\begin{itemize}
+\item[(i)] $EU_{\mathcal{G}}(RM,RM)>EU_{\mathcal{G}}(MM,RM);$
+\item[(ii)] $EU_{\mathcal{G}}(MM,MM)<EU_{\mathcal{G}}(RM,MM).$
+\end{itemize}
+
+\noindent To show
+the result we will use the following partition of $\mathcal{G}$.
+\begin{enumerate}
+\item Coordination games $\mathcal{G}^{C}$: $a>c$ and $d>b$;
+\item Anti-coordination games $\mathcal{G}^{A}$: $a<c$ and $d<b$;
+\item Strong dominance games $\mathcal{G}^{S}$: aut $(a>c$ and $b>d)$
+aut $(a<c$ and $b<d)$;
+\item Weak dominance games $\mathcal{G}^{W}$: aut $a=c$ aut $b=d$;
+\item Indifferent games $\mathcal{G}^{I}$: $a=c$ and $b=d$.
+\end{enumerate}
+Before proving the lemmas, it is convenient to fix some notation.
+We denote by $G^{C}$ a coordination game in $\mathcal{G}^{C}$ with
+payoffs $a^{G^{C}}$, $b^{G^{C}}$, $c^{G^{C}}$, and $d^{G^{C}}$;
+similarly, for $G^{A}$, $G^{S}$, $G^{W}$, and $G^{I}$. Let us
+call $I_{G^{C}}^{RM}$ the event that a RM player plays action $I$
+in the game $G^{C}$; and similarly for action $II$, for player MM,
+and for games $G^{A}$, $G^{S}$, $G^{W}$ and $G^{I}$. Moreover,
+let us recall the definition of evolutionarily stable strategy and
+neutrally stable strategy.
+
+\medskip{}
+
+\begin{definition}[ESS-NSS]
+A strategy $s^{\$}$ is \emph{evolutionarily stable
+(ESS)} if for any other strategy $s$:
+\begin{enumerate}
+\item $\pi(s^{\$},s^{\$})>\pi(s,s^{\$})$, or
+\item $\pi(s^{\$},s^{\$})=\pi(s,s^{\$})$ and $\pi(s^{\$},s)>\pi(s,s)$.
+\end{enumerate}
+\noindent A strategy $s^{\$}$ is \emph{neutrally stable (NSS)} if
+for any other strategy $s$:
+\begin{enumerate}
+\item $\pi(s^{\$},s^{\$})>\pi(s,s^{\$})$, or
+\item $\pi(s^{\$},s^{\$})=\pi(s,s^{\$})$ and $\pi(s^{\$},s)\geq\pi(s,s)$.
+\end{enumerate}
+\end{definition}
+
+\medskip{}
+
+\begin{lemma}
+RM and MM perform equally well in $\mathcal{G}^{S}$
+and in $\mathcal{G}^{I}$. 
+\end{lemma}
+
+\begin{proof}
+By definition of regret minimization and maximin it
+is easy to check that whenever in a game there is a strongly dominant
+action $a^{\$}$, then $a^{\$}$ is both the maximin action and the
+regret minimizing action. Then, for all the games in $\mathcal{G}^{S}$,
+a RM chooses action $a$ if and only if MM chooses action $a$. Consequently,
+RM and MM always perform equally (well) in $\mathcal{G}^{S}$. In
+the case of $\mathcal{G}^{I}$ it is trivial to see that all the players
+perform equally.
+\end{proof}
+
+\medskip{}
+
+\begin{lemma}
+In $\mathcal{G}^{W}$ RM is evolutionarily stable
+against MM, but MM is not evolutionarily stable against RM.
+\end{lemma}
+
+\begin{proof}
+Assume without loss of generality that $b=d$. We have
+two cases then: (i) $c<b=d$; (ii) $c>b=d$. In the first case it
+is easy to see that RM and MM perform equally well. Indeed, given
+(i) both MM and RM choose action $I$ if $a>c$, and action $II$
+if $c>a$. If case (ii) holds instead, we have that RM plays $I$
+if $a>c$ and $II$ if $c>a$ as before, but MM plays $(\frac{1}{2}I;\frac{1}{2}II)$,
+since both $I$ and $II$ maximize the minimal payoff. Consider now
+a population of RM and MM playing games from the class $\mathcal{G}^{W}$.
+Whenever (i) is the case both RM and MM perform equally. Suppose that
+(ii) is the case and that $a>c$, without loss of generality. Then,
+a RM population is evolutionarily stable against MM by condition 1
+of ESS, since $a>\frac{1}{2}a+\frac{1}{2}c$, whereas a MM population
+is not evolutionarily stable against RM, because clearly $\frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d<\frac{1}{2}a+\frac{1}{2}b$.
+Hence, we have that in general $EU_{\mathcal{G}^{W}}(RM,RM)>EU_{\mathcal{G}^{W}}(MM,RM),\mbox{ and }EU_{\mathcal{G}^{W}}(MM,MM)<EU_{\mathcal{G}^{W}}(RM,MM)$.
+\end{proof}
+
+\medskip{}
+
+Since it is not difficult to see that both RM and MM are evolutionarily
+stable in $\mathcal{G}^{C}$, and that both RM and MM are not evolutionarily
+stable in $\mathcal{G}^{A}$ against each other, the main part of
+the proof will be to show that RM is the only evolutionarily stable
+player in the class $\mathcal{G}^{C}\cup\mathcal{G^{A}}$, that is:
+\begin{itemize}
+\item[(i')] $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,RM)>EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,RM),$
+\item[(ii')] $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,MM)<EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,MM).$
+\end{itemize}
+
+\noindent This part needs some more lemmas to be proven, but firstly we introduce
+the following bijective function $\phi$ between coordination and
+anti-coordination games.
+
+\medskip{}
+
+\begin{definition}[$\phi$]
+$\phi:\mathcal{G}^{C}\rightarrow\mathcal{G^{A}}$,
+such that $\phi(a,b,c,d)=(c,d,a,b)$, is a bijection that for each
+coordination game $G^{C}\in\mathcal{G}^{C}$ with payoffs $(a^{G^{C}},b^{G^{C}},c^{G^{C}},d^{G^{C}})$
+gives the anti-coordination game $G^{A}\in\mathcal{G}^{A}$ with payoffs
+$(a^{G^{A}},b^{G^{A}},c^{G^{A}},d^{G^{A}})=(c^{G^{C}},d^{G^{C}},a^{G^{C}},b^{G^{C}})$.
+\end{definition}
+
+\medskip{}
+
+\begin{lemma}
+Let $P(E)$ be the probability of event $E$, then
+it holds that:
+\begin{itemize}
+\item $P(I_{G^{C}}^{RM})=P(II_{\phi(G^{C})}^{RM})$, and $P(II_{G^{C}}^{RM})=P(I_{\phi(G^{C})}^{RM})$;
+\item $P(I_{G^{C}}^{MM})=P(II_{\phi(G^{C})}^{MM})$, and $P(II_{G^{C}}^{MM})=P(I_{\phi(G^{C})}^{MM})$.
+\end{itemize}
+\end{lemma}
+
+\begin{proof}
+It is easy to check that if $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$,
+a RM player plays action $I$ in $G^{C}$; that if $b^{G^{C}}-d^{G^{C}}<c^{G^{C}}-a^{G^{C}}$,
+RM plays $II$; and that if $b^{G^{C}}-d^{G^{C}}=c^{G^{C}}-a^{G^{C}}$,
+a RM player is indifferent between $I$ and $II$ in $G^{C}$, and
+we assume that randomizes with $(\frac{1}{2}I;\frac{1}{2}II)$. Similarly,
+if $a^{G^{A}}-c^{G^{A}}>d^{G^{A}}-b^{G^{A}}$, a RM player plays action
+$I$ in $G^{A}$; if $a^{G^{A}}-c^{G^{A}}<d^{G^{A}}-b^{G^{A}}$, RM
+plays $II$; and if $a^{G^{A}}-c^{G^{A}}=d^{G^{A}}-b^{G^{A}}$, a
+RM player is indifferent between $I$ and $II$ in $G^{A}$, and randomizes
+with $(\frac{1}{2}I;\frac{1}{2}II)$. Consequently, if $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$,
+then $P(I_{G^{C}}^{RM})=1$, and by definition of $\phi$ we have
+$P(II_{\phi(G^{C})}^{RM})=1$. Likewise, if $b^{G^{C}}-d^{G^{C}}<c^{G^{C}}-a^{G^{C}}$,
+then $P(II_{G^{C}}^{RM})=1=P(I_{\phi(G^{C})}^{RM})$; and if $b^{G^{C}}-d^{G^{C}}=c^{G^{C}}-a^{G^{C}}$,
+then $P(I_{G^{C}}^{RM})=P(II_{G^{C}}^{RM})=\frac{1}{2}=P(II_{\phi(G^{C})}^{RM})=P(I_{\phi(G^{C})}^{RM})$. \\
+In the same way, in coordination games we have that if $b^{G^{C}}>c^{G^{C}}$,
+a MM player plays $I$; if $c^{G^{C}}>b^{G^{C}}$, a MM player plays
+$II$; and if $b^{G^{C}}=c^{G^{C}}$, MM is indifferent between $I$
+and $II$, and plays $(\frac{1}{2}I;\frac{1}{2}II)$. In anti-coordination
+games instead, if $a^{G^{A}}>d^{G^{A}}$, MM plays $I$; if $a^{G^{A}}<d^{G^{A}}$,
+MM plays $II$; if $a^{G^{A}}=d^{G^{A}}$, MM plays $(\frac{1}{2}I;\frac{1}{2}II)$.
+By definition of $\phi$: $P(I_{G^{C}}^{MM})=1=P(II_{\phi(G^{C})}^{MM})$
+if $b^{G^{C}}>c^{G^{C}}$; $P(II_{G^{C}}^{MM})=1=P(I_{\phi(G^{C})}^{MM})$
+if $c^{G^{C}}>b^{G^{C}}$; and $P(I_{G^{C}}^{MM})=P(II_{G^{C}}^{MM})=\frac{1}{2}=P(II_{\phi(G^{C})}^{MM})=P(I_{\phi(G^{C})}^{MM})$
+if $b^{G^{C}}=c^{G^{C}}$.
+\end{proof}
+
+\medskip{}
+
+\begin{lemma}
+$P(\phi(G^{C}))=P(G^{C})$.
+\end{lemma}
+
+\begin{proof}
+By definition, each game $G^{C}\equiv(a^{G^{C}},b^{G^{C}},c^{G^{C}},d^{G^{C}})$
+is such that $a^{G^{C}}>c^{G^{C}}$ and $d^{G^{C}}>b^{G^{C}}$, and
+each game $G^{A}\equiv(a^{G^{A}},b^{G^{A}},c^{G^{A}},d^{G^{A}})$
+is such that $a^{G^{A}}<c^{G^{A}}$ and $d^{G^{A}}>b^{G^{A}}$. Since
+$a,b,c,d$ come from i.i.d. sampling, by simple renaming of variables
+it is clear that the probability of $(a^{G^{C}},b^{G^{C}},c^{G^{C}},d^{G^{C}})$
+is equal to the probability of $(c^{G^{C}},d^{G^{C}},a^{G^{C}},b^{G^{C}})$.
+Hence, $P(\phi(G^{C}))=P(G^{C})$.
+\end{proof}
+
+\medskip{}
+
+\begin{lemma}
+It holds that:
+\begin{itemize}
+\item $a^{G^{C}}>d^{G^{C}}\rightarrow(I_{G^{C}}^{MM}\subset I_{G^{C}}^{RM})$;
+\item $a^{G^{C}}<d^{G^{C}}\rightarrow(II_{G^{C}}^{MM}\subset II_{G^{C}}^{RM})$;
+\item $a^{G^{C}}=d^{G^{C}}\rightarrow I_{G^{C}}^{MM}=I_{G^{C}}^{RM}$.
+\end{itemize}
+\end{lemma}
+
+\begin{proof}
+If $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$, RM plays
+$I$, and if $b^{G^{C}}-d^{G^{C}}=c^{G^{C}}-a^{G^{C}}$, RM plays
+$(\frac{1}{2}I;\frac{1}{2}II)$, whereas if $b^{G^{C}}>c^{G^{C}}$,
+MM plays $I$, and if $b^{G^{C}}=c^{G^{C}}$, MM plays $(\frac{1}{2}I;\frac{1}{2}II)$.
+Then, $I_{G^{C}}^{RM}$ implies that $b^{G^{C}}-d^{G^{C}}\geq c^{G^{C}}-a^{G^{C}}$,
+and $I_{G^{C}}^{MM}$ implies that $b^{G^{C}}\geq c^{G^{C}}$. Moreover,
+on the assumption that $a^{G^{C}}>d^{G^{C}}$, it is easy to check
+that $b^{G^{C}}\geq c^{G^{C}}$ implies $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$.
+Hence, in any $G^{C}$ with $a^{G^{C}}>d^{G^{C}}$ it holds that $I_{G^{C}}^{MM}\mbox{ implies }I_{G^{C}}^{RM}$,
+i.e., $a^{G^{C}}>d^{G^{C}}\rightarrow(I_{G^{C}}^{MM}\subseteq I_{G^{C}}^{RM})$.
+Instead, it is possible that $a^{G^{C}}>d^{G^{C}}$, $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$
+and $b^{G^{C}}<c^{G^{C}}$ hold simultaneously, so that $I_{G^{C}}^{MM}\nsupseteq I_{G^{C}}^{RM}$.
+Consequently: $a^{G^{C}}>d^{G^{C}}\rightarrow(I_{G^{C}}^{MM}\subset I_{G^{C}}^{RM})$.
+By symmetric argument it can be shown that $a^{G^{C}}<d^{G^{C}}\rightarrow(II_{G^{C}}^{MM}\subset II_{G^{C}}^{RM})$
+too. \\
+Finally, when $a^{G^{C}}=d^{G^{C}}$ it holds that: $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$
+iff $b^{G^{C}}>c^{G^{C}}$; $b^{G^{C}}-d^{G^{C}}<c^{G^{C}}-a^{G^{C}}$
+iff $b^{G^{C}}<c^{G^{C}}$; and $b^{G^{C}}-d^{G^{C}}=c^{G^{C}}-a^{G^{C}}$
+iff $b^{G^{C}}=c^{G^{C}}$. Hence, $a^{G^{C}}=d^{G^{C}}\rightarrow I_{G^{C}}^{MM}=I_{G^{C}}^{RM}$.
+\end{proof}
+
+\medskip{}
+
+We are now ready to prove that: 
+\begin{itemize}
+\item[(i')] $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,RM)>EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,RM);$
+\item[(ii')] $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,MM)<EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,MM).$
+\end{itemize}
+We can rewrite $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,RM)>EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,RM)$
+more explicitly as:
+
+\medskip{}
+
+\noindent $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{MM})\cdot d^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{MM})\cdot d^{A}]<\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{RM})\cdot d^{C}+P(I_{G^{C}}^{MM}\cap II_{G^{C}}^{RM})\cdot c^{C}+P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot b^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{MM}\cap I_{G^{A}}^{RM})\cdot a^{A}+P(II_{G^{A}}^{MM}\cap II_{G^{A}}^{RM})\cdot d^{A}+P(I_{G^{A}}^{MM}\cap II_{G^{A}}^{RM})\cdot c^{A}+P(II_{G^{A}}^{MM}\cap I_{G^{A}}^{RM})\cdot b^{A}]$
+
+\medskip{}
+
+\noindent Then, the next derivation follows. By Lemma 5 and 6, we can express
+everything in terms of $G^{C}$ only: 
+\begin{itemize}
+\item $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM})\cdot a^{A}+P(II_{G^{A}}^{RM})\cdot d^{A}]>\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot d^{A}+P(I_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot c^{A}+P(II_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot b^{A}]$
+\item $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}+P(II_{G^{C}}^{RM})\cdot c^{C}+P(I{}_{G^{C}}^{RM})\cdot b^{C}]>\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}]$
+\item $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}+P(II_{G^{C}}^{RM})\cdot c^{C}+P(I{}_{G^{C}}^{RM})\cdot b^{C}]>\sum_{G^{C}}P(G^{C})[a^{C}\cdot(P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))+b^{C}\cdot(P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))+c^{C}\cdot(P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))+d^{C}\cdot(P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]$
+\end{itemize}
+Now let us split into $a>d$ and $a<d$, and consider $a>d$ first.
+Notice that, by Lemma 7, the case $a=d$ is irrelevant in order to
+discriminate between RM and MM. If $a>d$, by Lemma 7 we can eliminate
+the cases where RM plays $II$ and MM plays $I$:
+\begin{itemize}
+\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}+P(II_{G^{C}}^{RM})\cdot c^{C}+P(I{}_{G^{C}}^{RM})\cdot b^{C}]>\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[a^{C}\cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+b^{C}\cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+c^{C}\cdot(P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))+d^{C}\cdot(P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]$
+\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}+P(II_{G^{C}}^{RM})\cdot c^{C}+P(I{}_{G^{C}}^{RM})\cdot b^{C}-a^{C}\cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})-b^{C}\cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})-c^{C}\cdot(P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))-d^{C}\cdot(P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]>0$
+\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[a^{C}\cdot(P(I_{G^{C}}^{RM})-P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))+b^{C}\cdot(P(I{}_{G^{C}}^{RM})-P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))+c^{C}\cdot(P(II_{G^{C}}^{RM})-P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})-P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))+d^{C}\cdot(P(II_{G^{C}}^{RM})-P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})-P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]>0$
+\end{itemize}
+By Lemma 7, it is easy to check that $P(I_{G^{C}}^{RM})-P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})=P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})$
+and $P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})=P(II_{G^{C}}^{RM})$.
+Consequently, we have:
+\begin{itemize}
+\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[a^{C}\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+b^{C}\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})-c^{C}\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})-d^{C}\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})]>0$
+\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[a^{G^{C}}-c^{G^{C}}]>\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[d^{G^{C}}-b^{G^{C}}]$.
+\end{itemize}
+\medskip{}
+
+\noindent We know that $I_{G^{C}}^{RM}$ implies that $b^{G^{C}}-d^{G^{C}}\geq c^{G^{C}}-a^{G^{C}}$,
+and $II_{G^{C}}^{MM}$ implies that $b^{G^{C}}\leq c^{G^{C}}$. From
+$b^{G^{C}}-d^{G^{C}}\geq c^{G^{C}}-a^{G^{C}}$, it is easy to see
+that $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[a^{G^{C}}-c^{G^{C}}]\geq\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[d^{G^{C}}-b^{G^{C}}]$
+holds. When the event $I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}$ obtains
+on the assumption that $a^{G^{C}}>d^{G^{C}}$, there are only three
+possible payoff orderings: $a>c\geq d>b$, $a>d>c>b$, and $a>d>c=b$.
+If games are randomly sampled from a finite set with i.i.d. values
+for $a,b,c$ and $d$, then $a>d>c=b$ occurs with positive probability,
+and the last formula of the derivation holds with strict inequality
+too. Hence, RM is evolutionarily stable when the value set for $a,b,c,d$
+is finite. \\
+If i.i.d. values are sampled from a compact and convex set instead,
+it is again easy to see that $\forall a,d,c\ \exists\epsilon$ such
+that $\forall b\in(d,d+\epsilon)$ the above formula holds with strict
+inequality. We can simply take $\epsilon\equiv\frac{a-c}{2}$, and
+the interval $(d,d+\epsilon)$ always has positive probability. Hence,
+RM is evolutionarily stable when the value set for $a,b,c,d$ is a
+compact and convex set too. \\
+Symmetrically, from $a<d$ in the above derivation we get:
+
+\medskip{}
+
+\noindent $\sum_{G_{a<d}^{C}}P(G_{a<d}^{C})\cdot P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot[d^{C}-b^{C}]>\sum_{G_{a<d}^{C}}P(G_{a<d}^{C})\cdot P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot[a^{C}-c^{C}]$
+
+\medskip{}
+
+\noindent and the same argument follows.
+
+\medskip{}
+
+The second half of the result is that MM is not evolutionarily stable
+against RM in $\mathcal{G}^{C}\cup\mathcal{G^{A}}$: $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,MM)<EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,MM)$.
+As before, we write it more explicitly as:
+
+\medskip{}
+
+\noindent $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{MM})\cdot d^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{MM})\cdot d^{A}]<\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{RM})\cdot d^{C}+P(I_{G^{C}}^{MM}\cap II_{G^{C}}^{RM})\cdot c^{C}+P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot b^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{MM}\cap I_{G^{A}}^{RM})\cdot a^{A}+P(II_{G^{A}}^{MM}\cap II_{G^{A}}^{RM})\cdot d^{A}+P(I_{G^{A}}^{MM}\cap II_{G^{A}}^{RM})\cdot c^{A}+P(II_{G^{A}}^{MM}\cap I_{G^{A}}^{RM})\cdot b^{A}]$.
+\medskip{}
+
+\noindent Similarly to the above derivation, in the end we get:
+
+\medskip{}
+
+\noindent $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot[c^{G^{C}}-a^{G^{C}}]<\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot[b^{G^{C}}-d^{G^{C}}]$.
+
+\medskip{}
+
+\noindent Finally, by the same argument as before we can conclude that MM is
+not evolutionarily stable against RM both when the value set for $a,b,c,d$
+is finite, and when the value set for $a,b,c,d$ is a compact and
+convex set. This concludes the proof. $\dashv$
+
 \printbibliography[heading=bibintoc]

### 2015-08-20 code/2by2_symmetric_games.r

@@ -2,7 +2,7 @@ source('functions.R')
 CP_names = c("Sec-Reg", "Sec-Id", "Sec-Comp", "Sec-Alt", 
              "Bel-Reg", "Bel-Id", "Bel-Comp", "Bel-Alt")
 
-rounds = 10000
+rounds = 100000
 # game_type = c()
 row_util = rep(0,rounds*length(CP_names)^2)
 nActs = rep(2,rounds)

### 2015-08-20 code/RMD_2x2_mixedTypes.R

@@ -2,7 +2,7 @@ require('gtools') # for dirichlet distribution
 require('ggplot2') # for plotting
 
 # get utilities
-load(file = 'buffered_meta_game_2x2_5000samples_flatBel.RDATA')
+load(file = 'buffered_meta_game_2x2.RDATA')
 U = means_total
 
 # parameters

### 2015-08-20 paper/paper.tex
fixed tables; edits results section; added extensions section

@@
 
-\section{Results}
-
-In this section we develop results by means of computer simulations and analytical proofs in parallel.
-
-\subsection{Statics}
-
-Table \ref{tab:reg vs obj} represent the result of simulations over $50.000$ games in $\mathcal{G}$ with $a,b,c,d \in \lbrace  0, \dots, 10 \rbrace$.
-The number in each cell corresponds to the average evolutionary fitness of the row player when matched with the column player.
-
-\begin{table}[]
-\centering
-\caption{Average evolutionary fitness in simulations of 50.000 symmetric $2 \times 2$ games}
-\label{tab:reg vs obj}
-\begin{tabular}{cccll}
-\cline{1-3}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{$\tau^{\pi}, \Delta(A_{-i})$} & \multicolumn{1}{c|}{$\tau^{reg}, \Delta(A_{-i})$} &  &  \\ \cline{1-3}
-\multicolumn{1}{|c|}{$\tau^{\pi}, \Delta(A_{-i})$} & \multicolumn{1}{c|}{6.131} & \multicolumn{1}{c|}{6.128} &  &  \\ \cline{1-3}
-\multicolumn{1}{|c|}{$\tau^{reg}, \Delta(A_{-i})$} & \multicolumn{1}{c|}{6.305} & \multicolumn{1}{c|}{6.302} &  &  \\ \cline{1-3}
-\multicolumn{1}{l}{}   & \multicolumn{1}{l}{}  & \multicolumn{1}{l}{}  &  & 
-\end{tabular}
-\end{table}
-
-Table \ref{tab:reg vs obj} shows that when players in the population are radically uncertain ($\Delta(A_{-i})$), the regret player $ \tau^{reg} $ outperforms the objective type $  \tau^{\pi} $, and $ \tau^{reg} $  is evolutionarily stable whereas $ \tau^{\pi} $ is not.
-This suggests that in the presence of uncertainty, in the sense of a set of probability measures, regret minimization is a better choice rule as compared with standard maxmin from an evolutionary point of view.
-\\
-\noindent Table \ref{tab:reg vs obj 2} reproduces the results about average evolutionary fitness out of 5.000 randomly generated symmetric $2 \times 2$ games when both types of epistemic uncertainty are present in the population.
-As we already highlighted in Fact \ref{fact:equivalence2x2}, $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{reg}, \overline{\mu})$, and $(\tau^{\pi}, \overline{\mu})$ are behaviorally equivalent, and their evolutionary fitness is indeed the same.
-[WARNING: it is not exactly identical here, this is probably related to a difference in tie-breaking that is probably a bit different for player $\tau^{reg}, \Delta(A_{-i})$.
-VERIFY and EQUALIZE.]\\
-Consequently, players $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{reg}, \overline{\mu})$, and $(\tau^{\pi}, \overline{\mu})$ are neutrally stable, and again $(\tau^{\pi}, \Delta(A_{-i}))$ is not.
-
-\begin{table*}[ht]
+\section{Results: the basic model}
+
+In this section we present results of computer simulations and analytical proofs for our basic
+model with the four player types introduced in the previous section.
+
+\subsection{Numerical simulations}
+
+Table~\ref{tab:ExpectedFitness_4Types} gives an approximation of expected fitness, obtained
+from averaging over randomly sampled $100,000$ games in $\mathcal{G}$ with
+$a,b,c,d \in \lbrace 0, \dots, 10 \rbrace$. The number in each cell corresponds to the average
+evolutionary fitness of the row player when matched with the column player. Whenever a player
+type would not select a unique action in a given game, we recorded unbiased averages over
+playing either.
+
+\begin{table}[t]
 \centering
 \begin{tabular}{ccccc}
-  \hline
+  \toprule
  & $\tau^{reg}, \Delta(A_{-i})$ 
@@
  & $\tau^{\pi}, \overline{\mu}$ \\ 
-  \hline
-  $\tau^{reg}, \Delta(A_{-i})$ & 6.629 & 6.653 &  6.636 & 6.636  \\ 
-  $\tau^{\pi}, \Delta(A_{-i})$  & 6.455 & 6.468 & 6.462 & 6.462  \\ 
-  $\tau^{reg}, \overline{\mu}$ & 6.633 & 6.658 & 6.634 & 6.634  \\ 
-  $\tau^{\pi}, \overline{\mu}$ & 6.633 & 6.658 & 6.634 & 6.634  \\   
-   \hline
+  \midrule
+  $\tau^{reg}, \Delta(A_{-i})$ & 6.663 & 6.662 & 6.663 & 6.663 \\ 
+  $\tau^{\pi}, \Delta(A_{-i})$ & 6.486 & 6.484 & 6.486 & 6.486 \\ 
+  $\tau^{reg}, \overline{\mu}$ & 6.663 & 6.662 & 6.663 & 6.663 \\  
+  $\tau^{\pi}, \overline{\mu}$ & 6.663 & 6.662 & 6.663 & 6.663 \\ 
+   \bottomrule
 \end{tabular}                    
-\caption{Average evolutionary fitness in simulations of 5000 symmetric $2 \times 2$ games}
-\label{tab:reg vs obj 2}
-\end{table*}
-
-On the top of what we have seen so far, we can proceed with the main analytical results of the paper, which confirm our achievements from simulations.
-Let us call $\Lambda$ the set of possible players $( \tau, e  )$ in the population.
-We can now state the following proposition.
-
-\begin{proposition} \label{proposition1}
-
-Fix $\Lambda = \lbrace (\tau^{\pi}, \Delta(A_{-i})), (\tau^{reg}, \Delta(A_{-i})) \rbrace$ and $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex, set of i.i.d.
-values.
-Then, $(\tau^{reg}, \Delta(A_{-i}))$ is the only evolutionarily stable player in the population.
-
-\end{proposition}
-
-\begin{proof}
-See Appendix.
-\end{proof}
-
-From Fact \ref{fact:equivalence2x2} and Proposition \ref{proposition1} the following corollary follows.
-
-\begin{corollary} \label{corollary1}
-
-Fix $T = \lbrace \tau^{\pi}, \tau^{reg} \rbrace$, $E = \lbrace \Delta(A_{-i}), \overline{\mu}  \rbrace$, $\Lambda= T \times E$, and $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex, set of i.i.d.
-values.
-Then, players $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$ are neutrally stable, and $(\tau^{\pi}, \Delta(A_{-i}))$ is neither evolutionarily nor neutrally stable.
-
-\end{corollary}
-
-\begin{proof}
-See Appendix.
-\end{proof}
-
-\subsection{More types}
-
-In evolutionary game theory other types of player have been investigated.
-A famous example is the \textit{altruistic type} [REF], introduced in the literature in order to explain the possible survival of altruistic behavior.
-In our framework, we can represent the altruistic type as follows.
-
-\begin{definition}[Altruistic preference] \label{defn:altpref}
-
-For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{alt}: A \rightarrow \mathbb{R} $ such that $ \theta^{alt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \sum_{j \neq i} \pi(a_{j},a_{-j})$.\footnote{A more general formulation [see: REFERENCES] would be to define an $ \alpha$-altruistic type, for $\alpha \in [0,1]$, with subjective utility $ \theta^{\alpha lt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \alpha \sum_{j \neq i} \pi(a_{j},a_{-j})$.
-Since we are not interested in the evolution of degrees of altruism here, we simply fix $ \alpha = 1 $.}
-
-\end{definition}
-
-\begin{definition}[Altruistic type] \label{defn:alttype}
-
-Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{alt}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{alt}(G)= \theta^{alt}$.
-
-\end{definition}
-
-\noindent As opposite to the altruistic type, it is possible to define a \textit{competitive type}.
-
-\begin{definition}[Competitive preference] \label{defn:compref}
-
-For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{com}: A \rightarrow \mathbb{R} $ such that $ \theta^{com}(a_i,a_{-i})=\pi(a_i,a_{-i}) - \sum_{j \neq i} \pi(a_{j},a_{-j})$.
-
-\end{definition}
-
-\begin{definition}[Competitive type] \label{defn:comtype}
-
-Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{com}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{com}(G)= \theta^{com}$.
-
-\end{definition}
-
-Similarly to the evolutionary competition that we simulated before, we can study the evolutionary fitness of this extended set of players when they are all represented in the population.
-Table \ref{tab:Utils-MetaGame} shows the averge fitness of the enlarged competition.
-
-\begin{table*}[ht]
-\centering
-\begin{tabular}{ccccccccc}
-  \hline
- & $\tau^{reg}, \Delta(A_{-i})$ 
- & $\tau^{\pi}, \Delta(A_{-i})$ 
- & $\tau^{alt}, \Delta(A_{-i})$
- & $\tau^{com}, \Delta(A_{-i})$ \\ 
-  \hline
-  $\tau^{reg}, \Delta(A_{-i})$ & 6.629 & 6.653 & 5.806 & 7.089  \\ 
-  $\tau^{\pi}, \Delta(A_{-i})$  & 6.455 & 6.468 & 6.067 & 6.685  \\ 
-  $\tau^{alt}, \Delta(A_{-i})$ & 6.280 & 6.746 & 5.473 & 6.959 \\ 
-  $\tau^{com}, \Delta(A_{-i})$ & 5.936 & 5.735 & 5.336 & 6.379  \\ 
-   \hline
-\end{tabular}
-\caption{Average evolutionary fitness in simulations of 5000 symmetric $2 \times 2$ games}
-\label{tab:Utils-MetaGame}
-\end{table*}
-
-The following proposition confirms this result.
-
-\begin{proposition} \label{proposition2}
-
-Fix $\Lambda = \lbrace (\tau^{\pi}, \Delta(A_{-i})), (\tau^{reg}, \Delta(A_{-i})), (\tau^{alt}, \Delta(A_{-i})), (\tau^{com}, \Delta(A_{-i})) \rbrace$ and $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex, set of i.i.d.
-values.
-Then, $(\tau^{reg}, \Delta(A_{-i}))$ is the only evolutionarily stable player in the population.
-
-\end{proposition}
-
-\begin{proof}
-See Appendix.
-\end{proof}
-
-Finally, Table \ref{tab:Utils-MetaGame2} shows the average fitness when all the epistemic and player types introduced so far are simultaneously present in the population.
-[SAME WARNING: it is not exactly identical here, this is probably related to a difference in tie-breaking that is probably a bit different for player $\tau^{reg}, \Delta(A_{-i})$.
-VERIFY and EQUALIZE.]\\
-A monomorphic population of regret
-minimizers $\tuple{\tuple{\tau^{reg}, \Delta(A)}}$ is no longer
-evolutionarily stable: it could be invaded by expected utility maximizers of types $\tuple{\tau^{reg}, \bar{\mu}}$ and $\tuple{\tau^{\pi},
-  \bar{\mu}}$. Since the latter are behaviorally equivalent, neither
-is an evolutionarily stable strategy, but could at best be
-\emph{neutrally stable}
-\cite{Maynard-Smith1982:Evolution-and-t}. However, under our simulated
-meta-game payoffs from Table~\ref{tab:Utils-MetaGame2} any population
-consisting entirely of $\tuple{\tau^{reg}, \bar{\mu}}$ and
-$\tuple{\tau^{\pi}, \bar{\mu}}$ can be invaded by regret
-minimizers. This suggests that all three types would persist under
-standard evolutionary dynamics, in various relative proportions.
+\caption{Average evolutionary fitness in simulations of 100,000 symmetric $2 \times 2$ games}
+\label{tab:ExpectedFitness_4Types}
+\end{table}
+
+Simulation results reflect Fact~\ref{fact:equivalence2x2} in that all encounters in which
+types $\tau^{reg}, \Delta(A_{-i})$, $\tau^{reg}, \overline{\mu}$ or $\tau^{\pi},
+\overline{\mu}$ are substituted for one another yield identical results. More interestingly,
+Table~\ref{tab:ExpectedFitness_4Types} shows that the maximin strategy $\tau^{\pi},
+\Delta(A_{-i})$ is strictly dominated by either of the three other strategies: in each row
+column (i.e., for each kind of opponent), the maximin strategy is strictly worse than any of
+the three behaviorally equivalent competitors. This has a number of interesting consequences.
+
+Firstly, if we restrict attention to a population of radically uncertain players where only
+epistemic type exists $\Delta(A_{-i})$, the regret type $ \tau^{reg} $ is the only
+evolutionarily stable state; we expect selection that is driven by expected fitness to
+invariably weed out maximin behavior in favor of regret minimization. In other words, in the
+class of random games looked at here, regret minimization is a better choice rule than standard
+maxmin from an evolutionary point of view.
+
+Secondly, if we look at the competition between all four types represented in
+Table~\ref{tab:ExpectedFitness_4Types}, $\tau^{reg}, \Delta(A_{-i})$ is no longer the only
+evolutionarily stable type in this meta-game. Rather, given behavioral equivalence
+(Fact~\ref{fact:equivalence2x2}), types $(\tau^{reg}, \Delta(A_{-i}))$,
+$(\tau^{reg}, \overline{\mu})$, and $(\tau^{\pi}, \overline{\mu})$ are all neutrally stable
+\citep{Maynard-Smith1982:Evolution-and-t}, while $(\tau^{\pi}, \Delta(A_{-i}))$ is strictly
+dominated and so disfavored by fitness-based selection. Based on considerations of evolutionary
+stability in this meta-game, we are drawn to conclude that maximin behavior is weeded out in
+favor of a population with a random distribution of the remaining three types.
 
 Simulation results of the (discrete time) \emph{replicator dynamics}
-\cite{TaylorJonker1978:Evolutionary-St} indeed show that random
-initial population configurations are attracted to states with only
-three player types: $\tuple{\tau^{reg}, \Delta(A)}$,
-$\tuple{\tau^{reg}, \bar{\mu}}$ and $\tuple{\tau^{\pi},
-  \bar{\mu}}$. The relative proportions of these depend on the initial
-population. This variability is eradicated if we add a small mutation
-rate to the dynamics. We assume a fixed, small mutation rate
-$\epsilon$ for the probability that a player's preference type
-\emph{or} her epistemic type changes to another random preference type
-or epistemic type. The probability that a player type randomly mutates
-into a completely different player type with altogether different
-preference type and epistemic type would then be $\epsilon^2$. With
-these assumptions about ``local mutations'', numerical simulations of
-the (discrete time) \emph{replicator mutator dynamics}
-\cite{Nowak2006:Evolutionary-Dy} show that for very small
-mutation rates almost all initial populations converge to a single
-fixed point in which the majority of players are regret types. For
-instance, with $\epsilon = 0.001$, almost all initial populations are
-attracted to a final distribution with proportions:
+\citep{TaylorJonker1978:Evolutionary-St} indeed show that random initial population
+configurations are attracted to states with only three player types:
+$\tuple{\tau^{reg}, \Delta(A)}$, $\tuple{\tau^{reg}, \bar{\mu}}$ and
+$\tuple{\tau^{\pi}, \bar{\mu}}$. The relative proportions of these depend on the initial
+population.
+
+Interestingly, however, this variability is eradicated if we add a small mutation rate to the
+dynamics. We assume a fixed, small mutation rate $\epsilon$ for the probability that a player's
+preference type \emph{or} her epistemic type changes to another random preference type or
+epistemic type. The probability that a player type randomly mutates into a completely different
+player type with altogether different preference type and epistemic type would then be
+$\epsilon^2$. With these assumptions about ``local mutations'', numerical simulations of the
+(discrete time) \emph{replicator mutator dynamics} \citep{Nowak2006:Evolutionary-Dy} show that
+for very small mutation rates almost all initial populations converge to a single fixed point
+in which the majority of players are regret types. For instance, with $\epsilon = 0.001$,
+almost all initial populations are attracted to a final distribution with proportions:
 
@@
 
+What this suggests is that, since biological evolution selects behavior-generating mechanisms,
+not behavior as such, it need not be the case that behaviorally equivalent mechanisms are
+treated equally all the while. If mutation probabilities are a function of individual
+components of such behavior-generating mechanisms, it can be the case that certain components
+are more strongly favored by a process of random mutation and selection. This is exactly the
+case with regret-based subjective preferences in our little toy example here. Since
+regret-based subjective preferences are much better in connection with radical uncertainty than
+veridical preferences are, we see a majority of regret-based preference types paired with
+probabilistic epistemic types. In sum, component-wise mutation could have lead to a majority of
+regret-based players even if they are behaviorally indiscernible from decision makers with
+veridical preferences.
+
+\subsection{Analytical results}
+\label{sec:analytical-results}
+
+Results based on the single meta-game in Table~\ref{tab:Utils-MetaGame}, which was obtained by
+averaging over numerical simulations, are not fully general and possibly spoiled by random
+fluctuations in the sampling procedure. Fortunately, for the case of symmetric $2 \times 2$
+games, the main result that maximin types $(\tau^{\pi}, \Delta(A_{-i}))$ are strictly dominated
+can also be shown analytically for generous general conditions on the nature of $P(G)$.
+
+\begin{proposition} \label{proposition1}
+
+  Let $\Lambda = \lbrace (\tau^{\pi}, \Delta(A_{-i})), (\tau^{reg}, \Delta(A_{-i})) \rbrace$ be
+  the set of possible players $(\tau, e)$ in the population, and let $\mathcal{G}$ be the class
+  of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex,
+  set of i.i.d.~values. Then, $(\tau^{reg}, \Delta(A_{-i}))$ is the only strict Nash
+  equilibrium in the resulting meta-game.
+
+\end{proposition}
+
+\begin{proof}
+See Appendix.
+\end{proof}
+
+From Fact \ref{fact:equivalence2x2} and Proposition \ref{proposition1} the following corollary follows.
+
+\begin{corollary} \label{corollary1}
+
+  Fix $T = \lbrace \tau^{\pi}, \tau^{reg} \rbrace$,
+  $E = \lbrace \Delta(A_{-i}), \overline{\mu} \rbrace$, $\Lambda= T \times E$, and
+  $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite,
+  or compact and convex, set of i.i.d. values. Then, player type $(\tau^{\pi}, \Delta(A_{-i}))$
+  is strictly dominated by $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
+  $(\tau^{reg}, \overline{\mu})$.
+
+\end{corollary}
+
+\begin{proof}
+See Appendix.
+\end{proof}
+
+Corollary~\ref{corollary1} tells us that the results obtained for the meta-game in
+Table~\ref{tab:Utils-MetaGame} hold more generally for any class of games in which the
+probability of encountering a game is the product of independently sampling four identically
+distributed payoff values. As before, player types $(\tau^{reg}, \Delta(A_{-i}))$,
+$(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$ will be neutrally stable,
+and fitness-based selection will tend to weed out maximin-players and leave us with a
+population of arbitrary frequency of $(\tau^{reg}, \Delta(A_{-i}))$,
+$(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$ players.
+
+\section{Extensions}
+\label{sec:extensions}
+
+The basic results from the previous section demonstrate the main conceptual point that we
+wanted to make: non-veridical subjective preference relations can persist under evolutionary
+selection along a gradient of objective fitness. In particular, regret-based preferences can
+not only persist, but even be favored by natural selection if agents are radically
+uncertain. This holds generally for playing arbitrary $2 \times 2$ games whose payoffs are
+sampled identically and independently at random.
+
+How do the basic results from the previous section carry over to more encompassing, richer
+models? Section~\ref{sec:more-types} first considers a further conceptually interesting
+preference types that have been suggested in the recent literature. Section~XZY then looks at
+the basic cast of player types, but considers the case of $n \times n$ games. Finally, to put
+our results into the proper perspective, Section~XZY ends with a brief comparison of game
+situations with cases of solitary decision making.
+
+\subsection{More types}
+\label{sec:more-types}
+
+In evolutionary game theory other types of player have been investigated.
+A famous example is the \textit{altruistic type} [REF], introduced in the literature in order to explain the possible survival of altruistic behavior.
+In our framework, we can represent the altruistic type as follows.
+
+\begin{definition}[Altruistic preference] \label{defn:altpref}
+
+For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{alt}: A \rightarrow \mathbb{R} $ such that $ \theta^{alt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \sum_{j \neq i} \pi(a_{j},a_{-j})$.\footnote{A more general formulation [see: REFERENCES] would be to define an $ \alpha$-altruistic type, for $\alpha \in [0,1]$, with subjective utility $ \theta^{\alpha lt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \alpha \sum_{j \neq i} \pi(a_{j},a_{-j})$.
+Since we are not interested in the evolution of degrees of altruism here, we simply fix $ \alpha = 1 $.}
+
+\end{definition}
+
+\begin{definition}[Altruistic type] \label{defn:alttype}
+
+Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{alt}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{alt}(G)= \theta^{alt}$.
+
+\end{definition}
+
+\noindent As opposite to the altruistic type, it is possible to define a \textit{competitive type}.
+
+\begin{definition}[Competitive preference] \label{defn:compref}
+
+For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{com}: A \rightarrow \mathbb{R} $ such that $ \theta^{com}(a_i,a_{-i})=\pi(a_i,a_{-i}) - \sum_{j \neq i} \pi(a_{j},a_{-j})$.
+
+\end{definition}
+
+\begin{definition}[Competitive type] \label{defn:comtype}
+
+Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{com}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{com}(G)= \theta^{com}$.
+
+\end{definition}
+
+Similarly to the evolutionary competition that we simulated before, we can study the evolutionary fitness of this extended set of players when they are all represented in the population.
+Table \ref{tab:Utils-MetaGame} shows the averge fitness of the enlarged competition.
+
+\begin{table*}[ht]
+\centering
+\begin{tabular}{ccccccccc}
+  \hline
+ & $\tau^{reg}, \Delta(A_{-i})$ 
+ & $\tau^{\pi}, \Delta(A_{-i})$ 
+ & $\tau^{com}, \Delta(A_{-i})$
+ & $\tau^{alt}, \Delta(A_{-i})$ \\ 
+  \hline
+  $\tau^{reg}, \Delta(A_{-i})$ & 6.663 & 6.662 & 5.829 & 7.105 \\ 
+  $\tau^{\pi}, \Delta(A_{-i})$ & 6.486 & 6.484 & 6.088 & 6.703 \\ 
+  $\tau^{com}, \Delta(A_{-i})$ & 6.323 & 6.758 & 5.496 & 6.977 \\ 
+  $\tau^{alt}, \Delta(A_{-i})$ & 5.949 & 5.722 & 5.326 & 6.396 \\ 
+   \hline
+\end{tabular}
+\caption{Average payoff in simulations of 100,000 symmetric $2 \times 2$ games}
+\label{tab:Utils-MetaGame}
+\end{table*}
+
+The following proposition confirms this result.
+
+\begin{proposition} \label{proposition2}
+
+Fix $\Lambda = \lbrace (\tau^{\pi}, \Delta(A_{-i})), (\tau^{reg}, \Delta(A_{-i})), (\tau^{alt}, \Delta(A_{-i})), (\tau^{com}, \Delta(A_{-i})) \rbrace$ and $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex, set of i.i.d.
+values.
+Then, $(\tau^{reg}, \Delta(A_{-i}))$ is the only evolutionarily stable player in the population.
+
+\end{proposition}
+
+\begin{proof}
+See Appendix.
+\end{proof}
+
+Finally, Table \ref{tab:Utils-MetaGame2} shows the average fitness when all the epistemic and
+player types introduced so far are simultaneously present in the population.
+
 Again, this shows that there are plausible and simple conditions under which
@@
  & $\tuple{\tau^{\pi}, \Delta(A)}$ 
+ & $\tuple{\tau^{com}, \Delta(A)}$
  & $\tuple{\tau^{alt}, \Delta(A)}$
- & $\tuple{\tau^{com}, \Delta(A)}$
  & $\tuple{\tau^{reg}, \bar{\mu}}$ 
  & $\tuple{\tau^{\pi}, \bar{\mu}}$ 
- & $\tuple{\tau^{alt}, \bar{\mu}}$
- & $\tuple{\tau^{com}, \bar{\mu}}$ \\ 
-  \hline
-  $\tuple{\tau^{reg}, \Delta(A)}$ & 6.629 & 6.653 & 5.806 & 7.089 & 6.636 & 6.636 & 5.793 & 7.463 \\ 
-  $\tuple{\tau^{\pi}, \Delta(A)}$  & 6.455 & 6.468 & 6.067 & 6.685 & 6.462 & 6.462 & 6.065 & 6.834 \\ 
-  $\tuple{\tau^{alt}, \Delta(A)}$ & 6.280 & 6.746 & 5.473 & 6.959 & 6.294 & 6.294 & 5.474 & 7.114 \\ 
-  $\tuple{\tau^{com}, \Delta(A)}$ & 5.936 & 5.735 & 5.336 & 6.379 & 5.929 & 5.929 & 5.327 & 6.538 \\ 
-  $\tuple{\tau^{reg}, \bar{\mu}}$ & 6.633 & 6.658 & 5.810 & 7.081 & 6.634 & 6.634 & 5.802 & 7.454 \\ 
-  $\tuple{\tau^{\pi}, \bar{\mu}}$ & 6.633 & 6.658 & 5.810 & 7.081 & 6.634 & 6.634 & 5.802 & 7.454 \\ 
-  $\tuple{\tau^{alt}, \bar{\mu}}$ & 6.278 & 6.750 & 5.476 & 6.953 & 6.293 & 6.293 & 5.484 & 7.112 \\ 
-  $\tuple{\tau^{com}, \bar{\mu}}$ & 6.311 & 5.885 & 5.475 & 6.536 & 6.299 & 6.299 & 5.466 & 7.123 \\ 
+ & $\tuple{\tau^{com}, \bar{\mu}}$
+ & $\tuple{\tau^{alt}, \bar{\mu}}$ \\ 
+  \hline
+  $\tuple{\tau^{reg}, \Delta(A)}$ &  6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\  
+  $\tuple{\tau^{\pi}, \Delta(A)}$ &  6.486 & 6.484 & 6.088 & 6.703 & 6.486 & 6.486 & 6.088 & 6.875 \\  
+  $\tuple{\tau^{com}, \Delta(A)}$ &  6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\  
+  $\tuple{\tau^{alt}, \Delta(A)}$ &  5.949 & 5.722 & 5.326 & 6.396 & 5.949 & 5.949 & 5.326 & 6.568 \\  
+  $\tuple{\tau^{reg}, \bar{\mu}}$ &  6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\  
+  $\tuple{\tau^{\pi}, \bar{\mu}}$ &  6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\  
+  $\tuple{\tau^{com}, \bar{\mu}}$ &  6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\  
+  $\tuple{\tau^{alt}, \bar{\mu}}$ &  6.331 & 5.893 & 5.497 & 6.566 & 6.331 & 6.331 & 5.497 & 7.152 \\   
    \hline                          
 \end{tabular}                      
-\caption{Average fitness in simulations of 5000
+\caption{Average payoff in simulations of 100,000
   randomly generated $2 \times 2$ symmetric games.}
@@
 
-\subsection{Symmetric $n \times n$ games}
-
-...
-
-\subsection{Dynamics}
-
-ADD RESULTS FOR DYNAMICS
-
-\subsection{Choice principles}
-
-\begin{itemize}
-\item study evolutionary competition between \emph{choice principles} 
-\item for now a choice principle is a pair (epistemic type, preference type)
-  \begin{itemize}
-  \item two epistemic types:
-    \begin{enumerate}
-    \item probabilistic beliefs (assumed to be flat)
-    \item non-probabilistic beliefs
-    \end{enumerate}
-  \item two preferences types (references to ``evolution of preference'' literature):
-    \begin{enumerate}
-    \item veridical payoff representations
-    \item regret-based payoffs
-    \end{enumerate}
-  \item many other types are conceivable; more in discussion section
-    \begin{itemize}
-    \item we want to keep it simple
-    \item assume that agents are relatively simple as well
-    \item no learning from past encounters \& no reasoning about the opponent: agents simply do
-      not know that there is another player (no strategic thinking possible; in line with idea
-      of evolutionary game theory where agents are ``stupid'' and ``myopic'') \\
-      \textcolor{blue}{this is then the added assumption that may be crude and generally
-        implausible but allows us to deflect the economists' critique}
-    \end{itemize}
-  \item choice principles yield action choices for each game
-    \begin{itemize}
-    \item show how
-    \end{itemize}
-  \item RESULT: types (prob., veridical) and (prob., regret) are choice-equivalent (also
-    mentioned by \citet{HalpernPass2012:Iterated-Regret})
-  \item RESULT: in $2 \times 2$ cases, (prob., veridical), (prob., regret) and (non-prob.,
-    regret) are choice-equivalent (but not for $n \times n$ in general)
-    \begin{itemize}
-    \item still we treat them as separate types because they behave differently under
-      component-wise mutation (see below)
-    \end{itemize}
-  \end{itemize}
-\end{itemize}
-
-\subsection{The environment: meta-games}
-
-\begin{itemize}
-\item imagine huge, virtually infinite population of agents, each carrying a choice principle
-\item agents play a randomly sampled game against a randomly sampled opponent
-\item fitness is based on the average payoff of choice principle A against choice principle B,
-  taken over arbitrary games $g$ and weighted their occurrence probability $P(g)$:
-  $\int_g P(g) \times U_g(\text{CP-A}, \text{CP-B}) \text{d}g$
-\item the occurrence probability of games $g$ is the ``environment'' and, possibly, impossible to
-  derive theoretically, or to measure empirically
-\item here, use a relatively neutral approach instead that is practicable:
-  \begin{itemize}
-  \item games are individuated by their payoff matrices (no framing effects or similar)
-  \item each entry in a payoff matrix is an i.~i.~d.~random variable
-    \begin{itemize}
-    \item approach still incorporates a bias (e.g., against strategic form representations of
-      sequential games)
-    \end{itemize}
-  \end{itemize}
-\item example: average payoffs from numerical simulation of ($2 \times 2$ symmetric games)
-\item example: average payoffs from numerical simulation of ($n \times n$ symmetric games, with
-  $n$ uniformly random (up to some upper-bound))
-\end{itemize}
-
-\subsection{Results}
-
-\textcolor{gray}{keep this clean and concise, formal details (proofs) in appendix}
-
-\subsubsection{$2 \times 2$ symmetric games}
-
-\textcolor{gray}{we isolate this case because it is most basic, and we can offer analytical
-  proofs as well}
-
-\begin{itemize}
-\item given previous results, there are really only two kinds of types to look at:
-  \begin{enumerate}
-  \item (prob., veridical), (prob., regret) and (non-prob., regret) \\ 
-    \textcolor{gray}{[all choice-equivalent in this case]}
-  \item (non-prob., veridical)
-  \end{enumerate}
-\item RESULT: the former class ``dominates'' the latter (our main result, Proposition 1 from
-  TARK paper)
-\item this means that evolutionary dynamics would weed out (non-prob., regret); every
-  population composition between the remaining three is neutrally stable; all interior
-  trajectories (of the replicator dynamic) converge to these
-\item further results (from TARK):
-  \begin{itemize}
-  \item component-wise mutation: abundance of regret types
-    \begin{itemize}
-    \item different evolutionary paths despite the same behavior (contra the ``behavioral
-      gambit'' \citep{FawcettHamblin2013:Exposing-the-be})
-    \end{itemize}
-  \item exogenously given correlated epistemic types: regret types dominate
-  \item exogenously given uncorrelated epistemic types: regret types dominate
-  \end{itemize}
-\todo[inline]{work out these additional results more carefully; present graphs if possible}
-\end{itemize}
-
-\subsubsection{$n \times n$ symmetric games}
-
-\todo[inline]{work out these additional results more carefully; present graphs if possible}
+\subsection{$n \times n$ symmetric games}
+\label{sec:n-times-n}
+
+\subsection{Solitary decisions}
+\label{sec:solitary-decisions}
 
@@
 
-\section*{APPENDIX: Proofs}
+\appendix
+
+\section{Proofs}
 
@@
 
-\section*{Snippets}
+\section{Snippets}
 
@@
 
+\subsection{The environment: meta-games}
+
+\begin{itemize}
+\item imagine huge, virtually infinite population of agents, each carrying a choice principle
+\item agents play a randomly sampled game against a randomly sampled opponent
+\item fitness is based on the average payoff of choice principle A against choice principle B,
+  taken over arbitrary games $g$ and weighted their occurrence probability $P(g)$:
+  $\int_g P(g) \times U_g(\text{CP-A}, \text{CP-B}) \text{d}g$
+\item the occurrence probability of games $g$ is the ``environment'' and, possibly, impossible to
+  derive theoretically, or to measure empirically
+\item here, use a relatively neutral approach instead that is practicable:
+  \begin{itemize}
+  \item games are individuated by their payoff matrices (no framing effects or similar)
+  \item each entry in a payoff matrix is an i.~i.~d.~random variable
+    \begin{itemize}
+    \item approach still incorporates a bias (e.g., against strategic form representations of
+      sequential games)
+    \end{itemize}
+  \end{itemize}
+\item example: average payoffs from numerical simulation of ($2 \times 2$ symmetric games)
+\item example: average payoffs from numerical simulation of ($n \times n$ symmetric games, with
+  $n$ uniformly random (up to some upper-bound))
+\end{itemize}
+
 \end{document}

### 2015-08-20 code/RMD_2x2_meta.R

@@ -1,7 +1,7 @@
 require('gtools') # for dirichlet distribution
 
 # get utilities
-load(file = 'buffered_meta_game_2x2_5000samples_flatBel.RDATA')
+load(file = 'buffered_meta_game_2x2.RDATA')
 U = means_total
 
 # parameters

### 2015-08-20 code/2by2_symmetric_games.r
renaming of code files

@@ -1,79 +1,0 @@
-source('functions.R')
-CP_names = c("Sec-Reg", "Sec-Id", "Sec-Comp", "Sec-Alt", 
-             "Bel-Reg", "Bel-Id", "Bel-Comp", "Bel-Alt")
-
-rounds = 100000
-# game_type = c()
-row_util = rep(0,rounds*length(CP_names)^2)
-nActs = rep(2,rounds)
-
-pb <- txtProgressBar(max = rounds,style = 3)
-
-
-for (i in 1:rounds){
-  setTxtProgressBar(pb, i)
-  
-  U = create_game(ub_util=10, ub_acts=2, symmetric = T)[,,1]
-  nActs[i] = dim(U)[1]
-  
-  #   gt = classify_game(U)
-  
-#     br = matrix(rep(rdirichlet(1,rep(1,dim(U)[2]))[1,], each=dim(U)[1]), nrow=dim(U)[1], ncol=dim(U)[2]) # beliefs of row player
-  br = 1 # flat beliefs
-  
-  choices = list(maximin(regret_transform(U)), #Sec-Reg
-              maximin(U), # Sec-Id
-              maximin(relative_power_transform(U)), # Sec-Alt
-              maximin(general_power_transform(U)),  # Sec-Comp
-              max_value(regret_transform(U), br), #Bel-Reg
-              max_value(U, br), # Bel-Id
-              max_value(relative_power_transform(U), br), # Bel-Alt
-              max_value(general_power_transform(U), br)  # Bel-Comp
-  )
-  
-#   choices.c = list(maximin(regret_transform(U)), #Sec-Reg
-#                 maximin(U), # Sec-Id
-#                 maximin(relative_power_transform(U)), # Sec-Alt
-#                 maximin(general_power_transform(U)),  # Sec-Comp
-#                 max_value(regret_transform(U)), #Bel-Reg
-#                 max_value(U), # Bel-Id
-#                 max_value(relative_power_transform(U)), # Bel-Alt
-#                 max_value(general_power_transform(U))  # Bel-Comp
-#   )
-  
-  for (c in 1:length(CP_names)){
-    for (d in 1:length(CP_names)){
-      payoff = mean(as.vector(U[choices[[c]],choices[[d]]]))
-      row_util[((i-1)*length(CP_names)^2) + ((c-1)*length(CP_names))+(d)] = payoff
-    }
-  }  
-  
-}
-
-data = data.frame( #trial = factor(trial), 
[…]

### 2015-08-20 code/RD.r

@@ -3,8 +3,8 @@ require('ggplot2')
 require('reshape2')
 require('fpc') # for function pamk(.) -> wrapper for kmeans!
 
-load("buffered_meta_game.RDATA")
-U = av_U
+load("buffered_meta_game_2x2.RDATA")
+U = means_total
 
 trials = 50
 rounds = 20000

### 2015-08-20 code/RMD_2x2_meta.R

@@ -1,45 +1,0 @@
-require('gtools') # for dirichlet distribution
-
-# get utilities
-load(file = 'buffered_meta_game_2x2.RDATA')
-U = means_total
-
-# parameters
-e = 0.001 # epsilon mutation probability
-
-getMutationMatrix = function(e){
-  x = 1 - 5*e - 3*e^2
-  m = matrix(c(x, e, e, e, e, e^2, e^2, e^2,
-              e, x, e, e, e^2, e, e^2, e^2,
-              e, e, x, e, e^2, e^2, e, e^2,
-              e, e, e, x, e^2, e^2, e^2, e,
-              e, e^2, e^2, e^2, x, e, e, e,
-              e^2, e, e^2, e^2, e, x, e, e,
-              e^2, e^2, e, e^2, e, e, x, e,
-              e^2, e^2, e^2, e, e, e, e, x), nrow=8, byrow = T)
-  colnames(m) = colnames(U)
-  rownames(m) = rownames(U)
-  return(m)
-}
-
-# initial population
-p = rdirichlet(1, rep(1,8))[1,]
-show(p)
-
-
-m = getMutationMatrix(e)
-
-for (i in 1:10000){
-  eu = rowSums(sweep(U,2,p,'*'))
-  av_eu = sum(eu*p)
-  p = p*eu / av_eu
-  p = colSums(sweep(m,1,p,'*'))
-}
-
-show(p)
-
-barplot(height = p, names.arg = names(p))
-
-d = data.frame(p = p, strategy = factor(names(p), levels = names(p)))
-myplot = ggplot(d, aes(x = strategy, y = p)) + geom_bar(stat = "identity")
-show(myplot)

### 2015-08-20 code/RMD_2x2_mixedTypes.R

@@ -1,44 +1,0 @@
-require('gtools') # for dirichlet distribution
-require('ggplot2') # for plotting
-
-# get utilities
-load(file = 'buffered_meta_game_2x2.RDATA')
-U = means_total
-
-# parameters
-p = 0.01 # probability of being lacking beliefs / playing "maximin"
-
-utilTransform = function(U, p) {
-  # expects a 8x8 meta-game utility matrix
-  # outputs the weighted average of utils if agents play maximin with probabitliy p
-  # maximin play is in rows / columns (1:4)
-  V = U[1:4,1:4]
-  for (i in 1:4){
-    for (j in 1:4){
-      V[i,j] = (p^2 * U[i, j]  + 
-                p*(1-p) * U[i, j+4]  +
-                p*(1-p) * U[i+4 ,j]  +
-                (1-p)^2 * U[i+4 ,j+4] )
-    }
-  }
-  return(V)
-}
-
-V = utilTransform(U,p)
-show(V)
-
-# initial population
-p = rdirichlet(1, rep(1,4))[1,]
-show(p)
-
-for (i in 1:10000){
-  eu = rowSums(sweep(V,2,p,'*'))
-  av_eu = sum(eu*p)
-  p = p*eu / av_eu
-}
-
-show(p)
-
-d = data.frame(p = p, strategy = factor(names(p)))
-myplot = ggplot(d, aes(x = strategy, y = p)) + geom_bar(stat = "identity")
-show(myplot)

### 2015-08-20 code/iterations.r

@@ -1,185 +1,0 @@
-require('gtools') # for dirichlet distribution
-require('abind')
-
-create_game = function(ub_util=10, ub_acts=10, symmetric = F){
-  # creates a random 2-player strategic form game with upper-bounds
-  # on utils and acts
-  if (ub_acts == 2){
-    n_acts = c(2,2)
-  }
-  else{
-    n_acts = sample(2:ub_acts,2,replace=TRUE)
-    if (symmetric == T) {
-      n_acts[2] = n_acts[1]
-    }
-  }
-  U = array(0,dim=c(n_acts,2))
-  U[,,1] = matrix(sample(1:ub_util,prod(n_acts),replace=TRUE),nrow=n_acts[1])
-  if (symmetric==T) {
-    U[,,2] = t(U[,,1])
-  }
-  else{
-    U[,,2] = matrix(sample(1:ub_util,prod(n_acts),replace=TRUE),nrow=n_acts[1]) 
-  }
-  rownames(U) = 1:dim(U)[1]
-  colnames(U) = 1:dim(U)[2]
-  return(U)
-}
-
-create_TD = function(k=100){
-  # creates traveller's dilemma
-  U = array(0,dim=c(k-1,k-1,2))
-  for (x in 2:k){
-    for (y in 2:k){
-      U[k-x+1,k-y+1,1] = min(x,y) + 2*sign(y-x)
-    }
-  }
-  U[,,2] = t(U[,,1])
-  rownames(U)=1:(k-1)
-  colnames(U)=1:(k-1)
-  return(U)
-}
-
-flip_game = function(U){
-  V = array(0,dim=dim(U)[c(2,1,3)])
-  V[,,1] = t(U[,,2])
-  V[,,2] = t(U[,,1])
-  rownames(V) = colnames(U)
-  colnames(V) = rownames(U)
-  return(V)
-}
-
-max_value = function(U){
-  if (length(dim(U)) == 3) {
-    U = U[,,1]
-  }
-  eus = rowMeans(U)
-  maxs = which.max(eus)
-  i = sample(length(maxs),1)
-  return(maxs[i])
-}
-
-maximin = function(U){
-  # returns maximin choice for row player in U
-  if (length(dim(U)) == 3) {
-    U = U[,,1]
-  }
-  mins = sapply(1:dim(U)[1], function(x) min(U[x,]))
-  maximins = which(mins == max(mins))
-#   choices = rep(0,dim(U)[1])
-#   choices[maximins]=1
-  return(maximins)
-}
-
[…]

### 2015-08-20 code/optimal_decision_rules.r

@@ -1,89 +1,0 @@
-require('gtools') # for dirichlet distribution
-require('plyr') # to conveniently manipulate data frames
-require('ggplot2')
-require('reshape2')
-
-max.t=2
-max.a=2
-n.rounds = 5000
-
-p.trueL = 0
-a.bestL = 0
-n.tL = 0
-n.aL = 0
-a.brL = 0
-a.mrL = 0
-u.brL = 0
-u.mrL = 0                  
-
-for (i in 1:n.rounds) {
-  if (max.t > 2){
-    n.t = sample(2:max.t,1) # number of states
-  } else {
-    n.t = 2
-  }
-  if (max.a > 2){
-    n.a = sample(2:max.a,1) # number of acts
-  } else {
-    n.a = 2
-  }
-  u = matrix(sample(0:10,replace=TRUE,size=n.t*n.a),nrow=n.t,ncol=n.a) # utility matrix
-#   p = rdirichlet(1,rep(1,n.t))[1,] # probabilities of states
-  p = rep(1/n.t, n.t)
-  t = sample(1:n.t,1) # true state
-#   t = sample(1:n.t,1,prob=p) # true state, with bias
-  # get best response
-  tmp = u * p
-  eu = sapply(1:n.a, function(x) sum(tmp[,x])) # expected utility
-  a.br = which.max(eu) # best response
-  # get min-regret
-  best.v = sapply(1:n.t, function(x) max(u[x,] )) # best value
-  best.a = sapply(1:n.t, function(x) u[x,which.max(u[x,])] ) # best act
-  rgrt = sapply(1:n.a, function(x) max(best.v - u[,x])) # regret of each act
-  a.mr = which.min(rgrt) # act that minimizes regret 
-  # record data
-  p.trueL[i] = p[t]
-  a.bestL[i] = which.max(u[t,])
-  n.tL[i] = n.t
-  n.aL[i] = n.a
-  a.brL[i] = a.br
-  a.mrL[i] = a.mr
-  u.brL[i] = u[t,a.br]
-  u.mrL[i] = u[t,a.mr]
-}
-
-data = data.frame(p.true = p.trueL,
-                  a.best = a.bestL,
-                  n.t = n.tL,
-                  n.a = n.aL,
-                  a.br = a.brL,
-                  a.mr = a.mrL,
-                  u.br = u.brL,
-                  u.mr = u.mrL)
-
-show(mean(data$u.br))
-show(mean(data$u.mr))
-
[…]

### 2015-08-20 paper/paper.tex
choice evol

@@
 \section{Results: the basic model}
+\label{sec:results:-basic-model}
 
@@
 \subsection{Numerical simulations}
+\label{sec:numer-simul}
 
@@
 
-Similarly to the evolutionary competition that we simulated before, we can study the evolutionary fitness of this extended set of players when they are all represented in the population.
-Table \ref{tab:Utils-MetaGame} shows the averge fitness of the enlarged competition.
-
-\begin{table*}[ht]
+Similarly to the evolutionary competition that we simulated before, we can study the
+evolutionary fitness of this extended set of players when they are all represented in the
+population. Table~\ref{tab:ExpectedFitness_2x2_Full} shows simulation results that approximate the
+expected fitness in the relevant meta-game.
+
+\begin{table}[]
 \centering
-\begin{tabular}{ccccccccc}
-  \hline
- & $\tau^{reg}, \Delta(A_{-i})$ 
- & $\tau^{\pi}, \Delta(A_{-i})$ 
- & $\tau^{com}, \Delta(A_{-i})$
- & $\tau^{alt}, \Delta(A_{-i})$ \\ 
-  \hline
-  $\tau^{reg}, \Delta(A_{-i})$ & 6.663 & 6.662 & 5.829 & 7.105 \\ 
-  $\tau^{\pi}, \Delta(A_{-i})$ & 6.486 & 6.484 & 6.088 & 6.703 \\ 
-  $\tau^{com}, \Delta(A_{-i})$ & 6.323 & 6.758 & 5.496 & 6.977 \\ 
-  $\tau^{alt}, \Delta(A_{-i})$ & 5.949 & 5.722 & 5.326 & 6.396 \\ 
-   \hline
-\end{tabular}
-\caption{Average payoff in simulations of 100,000 symmetric $2 \times 2$ games}
-\label{tab:Utils-MetaGame}
-\end{table*}
-
-The following proposition confirms this result.
-
-\begin{proposition} \label{proposition2}
-
-Fix $\Lambda = \lbrace (\tau^{\pi}, \Delta(A_{-i})), (\tau^{reg}, \Delta(A_{-i})), (\tau^{alt}, \Delta(A_{-i})), (\tau^{com}, \Delta(A_{-i})) \rbrace$ and $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex, set of i.i.d.
-values.
-Then, $(\tau^{reg}, \Delta(A_{-i}))$ is the only evolutionarily stable player in the population.
-
-\end{proposition}
-
-\begin{proof}
-See Appendix.
-\end{proof}
-
-Finally, Table \ref{tab:Utils-MetaGame2} shows the average fitness when all the epistemic and
-player types introduced so far are simultaneously present in the population.
-
-Again, this shows that there are plausible and simple conditions under which
-agents who represent the game in terms of regret may be favored by
-evolutionary selection and that, more specifically, regret minimizers
-are evolutionarily supported.
-
-\begin{table*}[ht]
-\centering
+\footnotesize
 \begin{tabular}{ccccccccc}
@@
   randomly generated $2 \times 2$ symmetric games.}
-\label{tab:Utils-MetaGame2}        
-\end{table*}
+\label{tab:ExpectedFitness_2x2_Full}        
+\end{table}
+
+\todo[inline]{is it true that competitive preferences types are behaviorally equivalent under
+  either epistemic type? can we show that?}
+
+The approximations in Table~\ref{tab:ExpectedFitness_2x2_Full} confirm basic
+intuitions. Averaging over randomly sampled games, everybody would like to have an altruistic
+opponent and nobody would like to play against a competitive opponent. Moreover, altruistic
+types come up strictly dominated by competitive types, but competitive types themselves are
+always worse than any of the behaviorally equivalent types $(\tau^{reg}, \Delta(A_{-i}))$,
+$(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$, except against maximin
+players $\tuple{\tau^{\pi}, \Delta(A)}$. This is a noteworthy results in the light of the fact
+that evolving altruistic preferences have been shown to support cooperative behavior in a
+single stage game \myalert{[CITE]}.\todo{@Paolo: check whether this is true, please!} In
+contrast, averaging over payoffs in multiple stage games, like we do here, makes altruistic
+preferences prime victims of evolutionary eradication.
+
+It is easy to see then that the previous result still obtains for the larger meta-game in
+Table~\ref{tab:ExpectedFitness_2x2_Full}: $(\tau^{reg}, \Delta(A_{-i}))$,
+$(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$ are still neutrally stable;
+all simulations of the (discrete-time) replicator dynamic end in populations consisting of only
+these types in arbitrary proportion.
+
+The following proposition confirms this result.\todo{rephrase to acknowledge all epistemic types}
+
+\begin{proposition} \label{proposition2}
+
+Fix $\Lambda = \lbrace (\tau^{\pi}, \Delta(A_{-i})), (\tau^{reg}, \Delta(A_{-i})), (\tau^{alt}, \Delta(A_{-i})), (\tau^{com}, \Delta(A_{-i})) \rbrace$ and $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex, set of i.i.d.
+values.
+Then, $(\tau^{reg}, \Delta(A_{-i}))$ is the only evolutionarily stable player in the population.
+
+\end{proposition}
+
+\begin{proof}
+See Appendix.\todo{is this there already?}
+\end{proof}
+
+In sum, the presence of other plausible preference types, such as competitive and altruistic
+types does not undermine the previous results about the evolutionary drive towards regret-based
+subjective preferences.
 
@@
 \label{sec:n-times-n}
+
+Results from Section~\ref{sec:results:-basic-model} relied heavily on
+Fact~\ref{fact:equivalence2x2} that regret minimization $\tuple{\tau^{reg}, \Delta(A)}$ is
+behaviorally equivalent with expected regret minimization $\tuple{\tau^{reg}, \bar{\mu}}$ and
+expected utility maximization $\tuple{\tau^{\pi}, \bar{\mu}}$. This is no longer true when we
+look at arbitrary $n \times n$ games with $n \ge 2$.
+
+Table~\ref{tab:ExpectedFitness_10x10} therefore gives approximations for expected fitness in a
+meta-game over a class over a class of $n \times n$ symmetric games where $n$ is randomly drawn
+from $\set{2, \dots, 10}$. Concretely, the numbers in Table~\ref{tab:ExpectedFitness_10x10} are
+averages of payoffs obtained in 100,000 randomly sampled games, where each game was sampled by
+first picking a number of acts $n \in \set{2, \dots, 10}$ uniformly at random, and then filling
+the resulting $n \times n$ payoff matrix of the stage game with i.i.d.~sampled payoffs as
+before.
+
+\begin{table}[]
+\centering
+\footnotesize
+\begin{tabular}{ccccccccc}
+  \hline
+ & $\tuple{\tau^{reg}, \Delta(A)}$ 
+ & $\tuple{\tau^{\pi}, \Delta(A)}$ 
+ & $\tuple{\tau^{com}, \Delta(A)}$
+ & $\tuple{\tau^{alt}, \Delta(A)}$
+ & $\tuple{\tau^{reg}, \bar{\mu}}$ 
+ & $\tuple{\tau^{\pi}, \bar{\mu}}$ 
+ & $\tuple{\tau^{com}, \bar{\mu}}$
+ & $\tuple{\tau^{alt}, \bar{\mu}}$ \\ 
+  \hline
+  $\tuple{\tau^{reg}, \Delta(A)}$ & 6.567 & 6.570 & 5.650 & 6.992 & 6.564 & 6.564 & 5.593 & 7.409 \\
+  $\tuple{\tau^{\pi}, \Delta(A)}$ & 6.476 & 6.483 & 5.896 & 6.818 & 6.484 & 6.484 & 5.850 & 7.124 \\
+  $\tuple{\tau^{com}, \Delta(A)}$ & 6.468 & 6.647 & 5.512 & 7.169 & 6.578 & 6.578 & 5.577 & 7.354 \\
+  $\tuple{\tau^{alt}, \Delta(A)}$ & 5.968 & 5.923 & 5.363 & 6.685 & 5.975 & 5.975 & 5.086 & 6.973 \\
+  $\tuple{\tau^{reg}, \bar{\mu}}$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
+  $\tuple{\tau^{\pi}, \bar{\mu}}$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
+  $\tuple{\tau^{com}, \bar{\mu}}$ & 6.529 & 6.680 & 5.445 & 7.276 & 6.542 & 6.542 & 5.521 & 7.440 \\
+  $\tuple{\tau^{alt}, \bar{\mu}}$ & 6.450 & 6.337 & 5.772 & 6.978 & 6.457 & 6.457 & 5.479 & 7.500 \\
+   \hline                          
+\end{tabular}                      
+\caption{Average payoff in simulations of 100,000
+  randomly generated $n \times n$ symmetric games with $n$ randomly drawn from $\set{2, \dots, 10}$.}
+\label{tab:ExpectedFitness_10x10}        
+\end{table}
 

### 2015-08-20 code/RD.r

@@ -3,7 +3,7 @@ require('ggplot2')
 require('reshape2')
 require('fpc') # for function pamk(.) -> wrapper for kmeans!
 
-load("buffered_meta_game_2x2.RDATA")
+load("buffered_meta_game_10x10.RDATA")
 U = means_total
 
 trials = 50

### 2015-08-21 paper/paper.tex
edits result section

@@
 \author{Paolo Galeazzi \& Michael Franke}
-\date{current version: May 27th 2015}
+\date{current version: August 21st 2015}
 
 \begin{document}
+
+\textbf{some notes and remarks and todo's}
+
+\begin{itemize}
+\item micha: let's have a term for pairs (regret type, epistemic type); I'm inclined to use ``player
+  type'', but that's what you reserved for regret type; maybe use \myalert{meta-type}?
+\item 
+\end{itemize}
+
+\newpage
+
 \maketitle
@@
 
-EXAMPLE 1: \textit{Coordination Game.}
-
-Let us consider the coordination game in Figure \ref{coordgame1}.
+\begin{example}[Coordination Game]
+  Let us consider the coordination game in Figure \ref{coordgame1}. It is easy to see that
+  $\text{reg}(I)=2$: when the other player chooses action $I$ the regret of $I$ is $0$ since
+  $I$ is a best reply to $I$, and when the other player chooses $II$ the regret of $I$ is $2$
+  since $\pi_i(II,II)-\pi_i(I,II)=2$. With the same reasoning, $\text{reg}(II)=1$. Two regret
+  minimizing players would then choose action $II$, each getting a payoff of $2$. In this case
+  regret minimization selects the Pareto-dominant Nash equilibrium. $ \medsquare $
 
@@
 
-It is easy to see that $\text{reg}(I)=2$: when the other player chooses action $I$ the regret of $I$ is $0$ since $I$ is a best reply to $I$, and when the other player chooses $II$ the regret of $I$ is $2$ since $\pi_i(II,II)-\pi_i(I,II)=2$.
-With the same reasoning, $\text{reg}(II)=1$.
-Two regret minimizing players would then choose action $II$, each getting a payoff of $2$.
-In this case regret minimization selects the Pareto-dominant Nash equilibrium.
-$ \medsquare $
-
-\vspace{.5cm}
-
-EXAMPLE 2: \textit{The Traveller's Dilemma.} (HalpernPass12)
-
-Let us now consider the Traveller's Dilemma case.
-The story behind the game goes as follows.
-There are two travellers, Ann and Bob, who lost their luggages.
-Ann and Bob had exactly the same luggage and they had insured the luggages with the same insurance company.
-The insurance policy is that the two travellers have to separately claim a certain amount between 2\$ and 100\$ for the reimbursement, and if they both claim the same amount then they will be reimbursed by that amount.
-Otherwise, if one of them claims more than the other, then the one who claimed the higher amount will get the lower amount minus 2\$, while the one who claimed the lower amount will get what (s)he claimed plus 2\$.
-The game is symmetric, and the payoff function for both players is:\\
-$\pi_i(a_i,a_{-i}) =  \begin{cases} a_i \text{ \hspace{1cm} if } a_i = a_{-i} \\ a_i + 2 \text{ \hspace{.4cm} if } a_i < a_{-i} \\ a_{-i} -2 \text{ \hspace{.25cm} if } a_{-i} < a_i \end{cases}$ \\
+\end{example}
+
+\begin{example}[The Traveller's Dilemma \citep{HalpernPass2012:Iterated-Regret}]
+Let us now consider the Traveller's Dilemma case. The story behind the game goes as
+follows. There are two travellers, Ann and Bob, who lost their luggages. Ann and Bob had
+exactly the same luggage and they had insured the luggages with the same insurance company. The
+insurance policy is that the two travellers have to separately claim a certain amount between
+2\$ and 100\$ for the reimbursement, and if they both claim the same amount then they will be
+reimbursed by that amount. Otherwise, if one of them claims more than the other, then the one
+who claimed the higher amount will get the lower amount minus 2\$, while the one who claimed
+the lower amount will get what (s)he claimed plus 2\$. The game is symmetric, and the payoff
+function for both players is:
+\begin{align*}
+  \pi_i(a_i,a_{-i}) = \begin{cases} a_i \text{ \hspace{1cm} if } a_i = a_{-i} \\ a_i + 2 \text{
+      \hspace{.4cm} if } a_i < a_{-i} \\ a_{-i} -2 \text{ \hspace{.25cm} if } a_{-i} <
+    a_i \end{cases}
+\end{align*}
 By a simple computation we have:  $\forall a_i \in \lbrace 96\$, ..., 100\$ \rbrace \text{, } \text{reg}(a_i)=3 $ and $\forall a_i \in \lbrace 2\$, ..., 95\$ \rbrace \text{, } \text{reg}(a_i)>3$.
@@
 Finally, it is worth noticing that the only rationalizable equilibrium of the game corresponds to the outcome $(2,2)$, that is consequently the only Nash equilibrium, the only perfect equilibrium, and the only sequential equilibrium of the game.
-$ \medsquare $\\
+$ \medsquare $
+
+\end{example}
 
@@
 
-Table~\ref{tab:ExpectedFitness_4Types} gives an approximation of expected fitness, obtained
-from averaging over randomly sampled $100,000$ games in $\mathcal{G}$ with
-$a,b,c,d \in \lbrace 0, \dots, 10 \rbrace$. The number in each cell corresponds to the average
-evolutionary fitness of the row player when matched with the column player. Whenever a player
-type would not select a unique action in a given game, we recorded unbiased averages over
-playing either.
+Table~\ref{tab:ExpectedFitness_4Types} gives an approximation of expected fitness, obtained by
+numerical simulation from averaging over $100,000$ randomly sampled games in $\mathcal{G}$ with
+$a,b,c,d \in \lbrace 0, \dots, 10 \rbrace$. Concretely, games were sampled repeatedly by
+choosing independently four integers $a,b,c,d \in \lbrace 0, \dots, 10 \rbrace$ uniformly at
+random. For each game, a player type's action choices were determined and payoffs from all
+pairwise encounters recorded. (Whenever a player type would not select a unique action in a
+given game, we recorded unbiased averages over playing either action.) The number in each cell
+of Table~\ref{tab:ExpectedFitness_4Types} is the average payoff for the row player type over
+all 100,000 numbers for each pairing of player types obtained in this way. These averages
+approximate the corresponding average evolutionary fitness of the row player when matched with
+the column player.
 
@@
 
-Simulation results reflect Fact~\ref{fact:equivalence2x2} in that all encounters in which
-types $\tau^{reg}, \Delta(A_{-i})$, $\tau^{reg}, \overline{\mu}$ or $\tau^{\pi},
-\overline{\mu}$ are substituted for one another yield identical results. More interestingly,
-Table~\ref{tab:ExpectedFitness_4Types} shows that the maximin strategy $\tau^{\pi},
-\Delta(A_{-i})$ is strictly dominated by either of the three other strategies: in each row
-column (i.e., for each kind of opponent), the maximin strategy is strictly worse than any of
-the three behaviorally equivalent competitors. This has a number of interesting consequences.
-
-Firstly, if we restrict attention to a population of radically uncertain players where only
-epistemic type exists $\Delta(A_{-i})$, the regret type $ \tau^{reg} $ is the only
-evolutionarily stable state; we expect selection that is driven by expected fitness to
-invariably weed out maximin behavior in favor of regret minimization. In other words, in the
-class of random games looked at here, regret minimization is a better choice rule than standard
-maxmin from an evolutionary point of view.
-
-Secondly, if we look at the competition between all four types represented in
-Table~\ref{tab:ExpectedFitness_4Types}, $\tau^{reg}, \Delta(A_{-i})$ is no longer the only
-evolutionarily stable type in this meta-game. Rather, given behavioral equivalence
-(Fact~\ref{fact:equivalence2x2}), types $(\tau^{reg}, \Delta(A_{-i}))$,
-$(\tau^{reg}, \overline{\mu})$, and $(\tau^{\pi}, \overline{\mu})$ are all neutrally stable
-\citep{Maynard-Smith1982:Evolution-and-t}, while $(\tau^{\pi}, \Delta(A_{-i}))$ is strictly
-dominated and so disfavored by fitness-based selection. Based on considerations of evolutionary
-stability in this meta-game, we are drawn to conclude that maximin behavior is weeded out in
-favor of a population with a random distribution of the remaining three types.
+Simulation results obviously reflect Fact~\ref{fact:equivalence2x2} in that all encounters in
+which types $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{reg}, \overline{\mu})$ or
+$(\tau^{\pi}, \overline{\mu})$ are substituted for one another yield identical results. More
+interestingly, Table~\ref{tab:ExpectedFitness_4Types} shows that the maximin strategy
+$(\tau^{\pi}, \Delta(A_{-i}))$ is strictly dominated by either of the three other strategies:
+in each column (i.e., for each kind of opponent), the maximin strategy is strictly worse
+than any of the three behaviorally equivalent competitors. This has a number of interesting
+consequences.
+
+Let's begin with a restricted scenario and look at more and more complex cases afterwards. If
+we restrict attention to a population of radically uncertain players, i.e., where only
+epistemic type $\Delta(A_{-i})$ exists, the regret type $ \tau^{reg} $ is the only
+\emph{evolutionarily stable state}. An evolutionarily stable state is a state which cannot be
+invaded by a small number of mutants. More strongly, since maximin play is strictly dominated,
+we expect selection that is driven by expected fitness to invariably weed out maximin behavior
+in favor of regret minimization. In other words, when taking average payoffs over the class of
+random games looked at here, regret minimization is a better choice rule than standard maxmin
+from an evolutionary point of view, despite the fact that the former, but not the letter
+entertains non-veridical subjective preferences.
+
+Next, if we look at the competition between all four types represented in
+Table~\ref{tab:ExpectedFitness_4Types}, $(\tau^{reg}, \Delta(A_{-i}))$ is no longer
+evolutionarily stable. Rather, given behavioral equivalence (Fact~\ref{fact:equivalence2x2}),
+types $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{reg}, \overline{\mu})$, and
+$(\tau^{\pi}, \overline{\mu})$ are all \emph{neutrally stable}
+\citep{Maynard-Smith1982:Evolution-and-t}. But since $(\tau^{\pi}, \Delta(A_{-i}))$ is strictly
+dominated and so disfavored by fitness-based selection, we are still drawn to conclude that
+maximin behavior is weeded out in favor of a population with a random distribution of the
+remaining three types.
 
@@
 $\tuple{\tau^{\pi}, \bar{\mu}}$. The relative proportions of these depend on the initial
-population.
-
-Interestingly, however, this variability is eradicated if we add a small mutation rate to the
-dynamics. We assume a fixed, small mutation rate $\epsilon$ for the probability that a player's
-preference type \emph{or} her epistemic type changes to another random preference type or
-epistemic type. The probability that a player type randomly mutates into a completely different
-player type with altogether different preference type and epistemic type would then be
-$\epsilon^2$. With these assumptions about ``local mutations'', numerical simulations of the
-(discrete time) \emph{replicator mutator dynamics} \citep{Nowak2006:Evolutionary-Dy} show that
-for very small mutation rates almost all initial populations converge to a single fixed point
-in which the majority of players are regret types. For instance, with $\epsilon = 0.001$,
-almost all initial populations are attracted to a final distribution with proportions:
+population.\todo{check uniform notation for player types: round vs.~square brackets} This
+variability disappears if we add a small mutation rate to the dynamics. We assume a fixed,
+small mutation rate $\epsilon$ for the probability that a player's preference type \emph{or}
+her epistemic type changes to another random preference type or epistemic type. The probability
+that a player type randomly mutates into a completely different player type with altogether
+different preference type and epistemic type would then be $\epsilon^2$. With these assumptions
+about ``component-wise mutations'', numerical simulations of the (discrete time)
+\emph{replicator mutator dynamics} \citep{Nowak2006:Evolutionary-Dy} show that already for very
+small mutation rates almost all initial populations converge to a single fixed point in which
+the majority of players are regret types. For instance, with $\epsilon = 0.001$, almost all
+initial populations are attracted to a final distribution with proportions:\todo{recalculate
+  these numbers for the actual 4x4 game!}
 
@@
 are more strongly favored by a process of random mutation and selection. This is exactly the
-case with regret-based subjective preferences in our little toy example here. Since
-regret-based subjective preferences are much better in connection with radical uncertainty than
-veridical preferences are, we see a majority of regret-based preference types paired with
-probabilistic epistemic types. In sum, component-wise mutation could have lead to a majority of
+case with regret-based subjective preferences in the present example. Since regret-based
+subjective preferences are much better in connection with radical uncertainty than veridical
+preferences are, the proportion of expected regret minimizers in the attracting state is
+substantially higher than that of expected utility maximizers, even though these types are
+behaviorally equivalent. In sum, component-wise mutation could have lead to a majority of
 regret-based players even if they are behaviorally indiscernible from decision makers with
-veridical preferences.
+veridical preferences, because regret types are better off under radical uncertainty.
 
@@
 
-Results based on the single meta-game in Table~\ref{tab:Utils-MetaGame}, which was obtained by
-averaging over numerical simulations, are not fully general and possibly spoiled by random
-fluctuations in the sampling procedure. Fortunately, for the case of symmetric $2 \times 2$
-games, the main result that maximin types $(\tau^{\pi}, \Delta(A_{-i}))$ are strictly dominated
-can also be shown analytically for generous general conditions on the nature of $P(G)$.
+Results based on the single meta-game in Table~\ref{tab:ExpectedFitness_4Types}, which was
+obtained by averaging over numerical simulations, are not fully general and possibly spoiled by
+random fluctuations in the sampling procedure. Fortunately, for the case of symmetric
+$2 \times 2$ games, the main result that maximin types $(\tau^{\pi}, \Delta(A_{-i}))$ are
+strictly dominated can also be shown analytically for generous general conditions on how likely
+randomly sampled games are.
 
@@
   Let $\Lambda = \lbrace (\tau^{\pi}, \Delta(A_{-i})), (\tau^{reg}, \Delta(A_{-i})) \rbrace$ be
-  the set of possible players $(\tau, e)$ in the population, and let $\mathcal{G}$ be the class
+  the set of possible meta-types $(\tau, e)$ in the population, and let $\mathcal{G}$ be the class
   of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex,
@@
 
-Corollary~\ref{corollary1} tells us that the results obtained for the meta-game in
-Table~\ref{tab:Utils-MetaGame} hold more generally for any class of games in which the
-probability of encountering a game is the product of independently sampling four identically
-distributed payoff values. As before, player types $(\tau^{reg}, \Delta(A_{-i}))$,
-$(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$ will be neutrally stable,
-and fitness-based selection will tend to weed out maximin-players and leave us with a
-population of arbitrary frequency of $(\tau^{reg}, \Delta(A_{-i}))$,
-$(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$ players.
-
-\section{Extensions}
-\label{sec:extensions}
-
-The basic results from the previous section demonstrate the main conceptual point that we
-wanted to make: non-veridical subjective preference relations can persist under evolutionary
-selection along a gradient of objective fitness. In particular, regret-based preferences can
+Corollary~\ref{corollary1} tells us that the conclusions drawn in the previous section based on
+the meta-game in Table~\ref{tab:ExpectedFitness_4Types} hold more generally for any class of
+games in which the probability of encountering a game is the product of independently sampling
+four identically distributed payoff values. As before, player types
+$(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
+$(\tau^{reg}, \overline{\mu})$ will be neutrally stable, and fitness-based selection will tend
+to weed out maximin play and leave us with a population of arbitrary frequency of
+$(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
+$(\tau^{reg}, \overline{\mu})$ meta-types.
+
+This shows that there is support for the main conceptual point that we wanted to make:
+non-veridical subjective preference relations \emph{can}, under specific circumstances, persist
+under evolutionary selection based on objective fitness. Moreover, regret-based preferences can
 not only persist, but even be favored by natural selection if agents are radically
@@
 
+\section{Extensions}
+\label{sec:extensions}
+
 How do the basic results from the previous section carry over to more encompassing, richer
-models? Section~\ref{sec:more-types} first considers a further conceptually interesting
-preference types that have been suggested in the recent literature. Section~XZY then looks at
-the basic cast of player types, but considers the case of $n \times n$ games. Finally, to put
-our results into the proper perspective, Section~XZY ends with a brief comparison of game
-situations with cases of solitary decision making.
+models? Section~\ref{sec:more-types} first considers further conceptually interesting
+preference types that have been suggested in the recent literature. Section~\ref{sec:n-times-n}
+then considers the case of $n \times n$ games for $n \ge 2$. Finally, to put our results into
+the proper perspective, Section~\ref{sec:solitary-decisions} ends with a brief comparison of
+game situations with cases of solitary decision making.
 
@@
 
-The approximations in Table~\ref{tab:ExpectedFitness_2x2_Full} confirm basic
-intuitions. Averaging over randomly sampled games, everybody would like to have an altruistic
-opponent and nobody would like to play against a competitive opponent. Moreover, altruistic
-types come up strictly dominated by competitive types, but competitive types themselves are
-always worse than any of the behaviorally equivalent types $(\tau^{reg}, \Delta(A_{-i}))$,
-$(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$, except against maximin
-players $\tuple{\tau^{\pi}, \Delta(A)}$. This is a noteworthy results in the light of the fact
-that evolving altruistic preferences have been shown to support cooperative behavior in a
-single stage game \myalert{[CITE]}.\todo{@Paolo: check whether this is true, please!} In
-contrast, averaging over payoffs in multiple stage games, like we do here, makes altruistic
-preferences prime victims of evolutionary eradication.
+The approximations in Table~\ref{tab:ExpectedFitness_2x2_Full} confirm basic intuitions about
+altruistic and competitive types: averaging over randomly sampled games, everybody would like
+to have an altruistic opponent and nobody would like to play against a competitive
+opponent. Perhaps more surprisingly, altruistic types come up strictly dominated by competitive
+types, but competitive types themselves are worse off against all opponent types except against
+maximin players $\tuple{\tau^{\pi}, \Delta(A)}$ than any of the behaviorally equivalent types
+$(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
+$(\tau^{reg}, \overline{\mu})$.  This is a noteworthy results in the light of the fact that
+evolving altruistic preferences have been shown to support cooperative behavior in a single
+stage game \myalert{[CITE]}. \todo{@Paolo: check whether this is true, please!} In contrast,
+averaging over payoffs in multiple stage games, like we do here, makes altruistic preferences
+prime victims of evolutionary eradication.
 
@@
 $(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$ are still neutrally stable;
-all simulations of the (discrete-time) replicator dynamic end in populations consisting of only
-these types in arbitrary proportion.
-
-The following proposition confirms this result.\todo{rephrase to acknowledge all epistemic types}
+all simulations of the (discrete-time) replicator dynamic on the $8 \times 8$ meta-game from
+Table~\ref{tab:ExpectedFitness_2x2_Full} end up in populations consisting of only these types
+in arbitrary proportion.
+
+The following proposition (partially) confirms this result.\todo{rephrase to acknowledge all
+  epistemic types?}
 
@@
 Results from Section~\ref{sec:results:-basic-model} relied heavily on
-Fact~\ref{fact:equivalence2x2} that regret minimization $\tuple{\tau^{reg}, \Delta(A)}$ is
-behaviorally equivalent with expected regret minimization $\tuple{\tau^{reg}, \bar{\mu}}$ and
-expected utility maximization $\tuple{\tau^{\pi}, \bar{\mu}}$. This is no longer true when we
-look at arbitrary $n \times n$ games with $n \ge 2$.
-
-Table~\ref{tab:ExpectedFitness_10x10} therefore gives approximations for expected fitness in a
-meta-game over a class over a class of $n \times n$ symmetric games where $n$ is randomly drawn
-from $\set{2, \dots, 10}$. Concretely, the numbers in Table~\ref{tab:ExpectedFitness_10x10} are
-averages of payoffs obtained in 100,000 randomly sampled games, where each game was sampled by
-first picking a number of acts $n \in \set{2, \dots, 10}$ uniformly at random, and then filling
-the resulting $n \times n$ payoff matrix of the stage game with i.i.d.~sampled payoffs as
-before.
+Fact~\ref{fact:equivalence2x2} that, for the special case of $2 \times 2$ symmetric games,
+regret minimization $\tuple{\tau^{reg}, \Delta(A)}$ is behaviorally equivalent with expected
+regret minimization $\tuple{\tau^{reg}, \bar{\mu}}$ and expected utility maximization
+$\tuple{\tau^{\pi}, \bar{\mu}}$. This is no longer true when we look at arbitrary $n \times n$
+games with $n \ge 2$. Table~\ref{tab:ExpectedFitness_10x10} therefore gives approximations for
+expected fitness in a meta-game over a class of $n \times n$ symmetric games where
+$n$ is randomly drawn from $\set{2, \dots, 10}$. Concretely, the numbers in
+Table~\ref{tab:ExpectedFitness_10x10} are averages of payoffs obtained in 100,000 randomly
+sampled games, where each game was sampled by first picking a number of acts
+$n \in \set{2, \dots, 10}$ uniformly at random, and then filling the resulting $n \times n$
+payoff matrix of the stage game with i.i.d.~sampled payoffs as before.
 

### 2015-08-21 paper/paper.tex
results section edits

@@
 
-\subsection{What should be in this section?}
-
-\myalert{main purpose of this section: introduce max EU and min regret with some background,
-  definitions, simple example and reasons why we care to look at especially these}
-
-\begin{itemize}
-  \item \todo[inline]{choose uniform consensual terminology for maximization of EU and regret minimization}
-\item classical notion of rationality: maximization of expected utilities
-  \begin{itemize}
-  \item human choice behavior seems to deviate from classical rational choice in many ways
-    \citep[most
-    notably][]{TverskyKahnemann1974:Judgement-under,KahnemannTversky1979:Prospect-Theory}
-  \end{itemize}
-\item historical competitor: regret minimization
-  \begin{itemize}
-  \item introduced by Savage \& Niehans independently
-  \item worked out (in parameterized form) by \citet{LoomesSugden1982:Regret-Theory:-} and
-    argued to outperform prospect theory
-  \item recently rediscovered by game theorists \citep{HalpernPass2012:Iterated-Regret} as a
-    possible partial explanation of some puzzles (e.g., Travellers Dilemma)
-  \end{itemize}
-\item definitions of max EU and min reg (with minimal formal notation); simple example where
-  they differ
-\item motivate why we are interested in regret minimization; e.g.:
-  \begin{itemize}
-  \item simple historical alternative; certain prima facie plausibility
-  \item argued to be empirically adequate (Loomes \& Sugden, Bell)
-  \item gives us intriguing results that nicely motivate the general approach of meta-games
-  \item non-independence of choices also for non-human decision makers (cite)
-  \end{itemize}
-\item here we care about game problems, not solitary decision problems
-\end{itemize}
-
-\subsection{Version 1}
-
-The standard use of the word \textit{rationality} in economics and decision theory is to denote the maximization of (subjective) expected utility.
-Since the work by vNM [cite], this stance has been justified from the intuitive ''rationality'' of the axioms on the subjective preference relation leading to the representability of the decision maker as an expected utility maximizer.
+The standard use of the word \textit{rationality} in economics and decision theory is to denote
+the maximization of (subjective) expected utility. Since the work by vNM [cite], this stance
+has been justified from the intuitive ''rationality'' of the axioms on the subjective
+preference relation leading to the representability of the decision maker as an expected
+utility maximizer.
 While in the axiomatization by [vNM] the probability of the outcomes is objectively given a priori, Savage54 provides a larger set of axioms that represent the decision maker (DM) with both a subjective utility over outcomes \textit{and} a \textit{subjective} probability over states of the world.
@@
 
-DEFINITION(SEU-maximization): Let $S$ be a set of states of the world, $X$ a set of outcomes and $A$ a set of actions.
-Given a probability measure $P$ on $S$ and a subjective utility function $u:X \rightarrow \mathbb{R} $, an action $a^*: S \rightarrow X $ is SEU-maximizing if $a^* \in \text{argmax}_{a_i \in A} \int_S u(a^*(s))dP(s) $.
-\\
+\begin{definition}[SEU-maximization] Let $S$ be a set of states of the world, $X$ a set of
+  outcomes and $A$ a set of actions. Given a probability measure $P$ on $S$ and a subjective
+  utility function $u:X \rightarrow \mathbb{R} $, an action $a^*: S \rightarrow X $ is
+  SEU-maximizing if $a^* \in \text{argmax}_{a_i \in A} \int_S u(a^*(s))dP(s) $.
+\end{definition}
 
@@
 $\tuple{\tau^{\pi}, \bar{\mu}}$. This is no longer true when we look at arbitrary $n \times n$
-games with $n \ge 2$. Table~\ref{tab:ExpectedFitness_10x10} therefore gives approximations for
-expected fitness in a meta-game over a class of $n \times n$ symmetric games where
-$n$ is randomly drawn from $\set{2, \dots, 10}$. Concretely, the numbers in
-Table~\ref{tab:ExpectedFitness_10x10} are averages of payoffs obtained in 100,000 randomly
-sampled games, where each game was sampled by first picking a number of acts
-$n \in \set{2, \dots, 10}$ uniformly at random, and then filling the resulting $n \times n$
-payoff matrix of the stage game with i.i.d.~sampled payoffs as before.
+games with $n \ge 2$. We should therefore see what happens in a broader class of games.
+
+Table~\ref{tab:ExpectedFitness_10x10} therefore gives approximations for expected fitness in a
+meta-game over a class of $n \times n$ symmetric games where $n$ is randomly drawn from
+$\set{2, \dots, 10}$. Concretely, the numbers in Table~\ref{tab:ExpectedFitness_10x10} are
+averages of payoffs obtained in 100,000 randomly sampled games, where each game was sampled by
+first picking a number of acts $n \in \set{2, \dots, 10}$ uniformly at random, and then filling
+the resulting $n \times n$ payoff matrix of the stage game with i.i.d.~sampled payoffs as
+before.
 
@@
 \end{table}
+
+As is to be expected, average payoffs obtained in games with more than 2 acts are higher, as
+can be seen by comparing Table~\ref{tab:ExpectedFitness_10x10} with
+Table~\ref{tab:ExpectedFitness_2x2_Full}. But increases in approximate expected fitness are not
+uniform. Most importantly, the regret minimizing type $\tuple{\tau^{reg}, \Delta(A)}$ is
+strictly dominated by $\tuple{\tau^{reg}, \bar{\mu}}$ and by $\tuple{\tau^{\pi}, \bar{\mu}}$ in
+the meta-game from Table~\ref{tab:ExpectedFitness_10x10}. This means that while regret
+minimization \emph{can} thrive in some evolutionary contexts, there are also contexts where it
+is demonstrably worse off.
+
+Still, although this may be bad news for regret minimizing types
+$\tuple{\tau^{reg}, \Delta(A)}$, it is not the case that regret types \emph{as such} are weeded
+out by selection. Since, by Fact~\ref{fact:maxEU-minReg}, $\tuple{\tau^{reg}, \bar{\mu}}$ and
+$\tuple{\tau^{\pi}, \bar{\mu}}$ are generally behaviorally equivalent, it remains that
+selection based on meta-games constructed from $n \times n$ games will still not eradicate all
+regret types. So, although regret types may not be selected for in this case, they are also not
+selected against.
+
+On the other hand, there are plenty of ways in which the basic insight from
+Proposition~\ref{proposition1} that regret-based preferences can be strictly better than
+veridical objective preferences in case of radical uncertainty could make for situations in
+which evolution would select for regret types exclusively, even in $n \times n$ games. If, for
+example, epistemic types of players are not what biological evolution selects, but rather
+something that the particular choice situation would exogenously give us, then regret-based
+preference \emph{can} again drive out veridical preferences altogether. For concreteness,
+suppose that only preference types compete and that agents' epistemic types are exogenously
+given, in such a way that agents hold flat probabilistic beliefs $\bar{\mu}$ with probability
+$1-p$ and are of type $\Delta(A)$ with probability $p$. This transforms the meta-game from
+Table~\ref{tab:ExpectedFitness_10x10} into the simpler $4 \times 4$ game in which the payoff
+obtained for a preference type is the weighted average over the payoffs of that preference
+types in Table~\ref{tab:ExpectedFitness_10x10}. Setting $p = 0.02$ for illustration, we get the
+meta-game in Table~\ref{tab:ExogeneousEpistemics}.
+
+\begin{table}[]
+\centering
+\begin{tabular}{ccccc}
+  \toprule
+  & $\tau^{reg}$ 
+  & $\tau^{\pi}$ 
+  & $\tau^{com}$
+  & $\tau^{alt}$ \\ 
+  \midrule
+  $\tau^{reg} $ & 6.926 & 6.926 & 5.942 & 7.757 \\ 
+  $\tau^{\pi} $ & 6.924 & 6.924 & 5.948 & 7.751 \\ 
+  $\tau^{com }$ & 6.566 & 6.570 & 5.481 & 7.434 \\ 
+  $\tau^{alt} $ & 6.463 & 6.461 & 5.478 & 7.469 \\ 
+   \bottomrule
+\end{tabular}
+\caption{Meta-game for the evolutionary competition between preference types when epistemic types are exogenously
+  given}
+\label{tab:ExogeneousEpistemics}
+\end{table}
+
+The only evolutionarily stable state of this meta-game is the regret type. Accordingly, all of
+our simulation runs of the (discrete-time) replicator dynamic converged to monomorphic
+regret-type populations. The reason why regret types prosper is because they have a substantial
+payoff advantage if paired with radical uncertainty. If radical uncertainty is exogenously
+given as something unavoidable that happens to agents (e.g., whenever they really have no
+indication as to what the situation holds for them), and even if that happens only very
+infrequently (i.e., for rather low $p$), regret types \emph{can} outperform veridical
+preference types, as well as competitive and altruistic types.
 

### 2015-08-21 code/RD_exogeneous_mix_epistemic.r
added code files after renaming

@@ -1,0 +1,46 @@
+require('gtools') # for dirichlet distribution
+require('ggplot2') # for plotting
+source('functions.R')
+
+# get utilities
+# load(file = 'buffered_meta_game_2x2.RDATA')
+load(file = 'buffered_meta_game_10x10.RDATA')
+U = means_total
+
+# parameters
+p = 0.02 # probability of being lacking beliefs / playing "maximin"
+
+utilTransform = function(U, p) {
+  # expects a 8x8 meta-game utility matrix
+  # outputs the weighted average of utils if agents play maximin with probabitliy p
+  # maximin play is in rows / columns (1:4)
+  V = U[1:4,1:4]
+  for (i in 1:4){
+    for (j in 1:4){
+      V[i,j] = (p^2 * U[i, j]  + 
+                p*(1-p) * U[i, j+4]  +
+                p*(1-p) * U[i+4 ,j]  +
+                (1-p)^2 * U[i+4 ,j+4] )
+    }
+  }
+  return(V)
+}
+
+V = utilTransform(U,p)
+show(xtable(V, digits = 3))
+
+# initial population
+p = rdirichlet(1, rep(1,4))[1,]
+show(p)
+
+for (i in 1:100000){
+  eu = rowSums(sweep(V,2,p,'*'))
+  av_eu = sum(eu*p)
+  p = p*eu / av_eu
+}
+
+show(p)
+
+d = data.frame(p = p, strategy = factor(names(p)))
+myplot = ggplot(d, aes(x = strategy, y = p)) + geom_bar(stat = "identity")
+show(myplot)

### 2015-08-21 code/RMD_component_wise_mutation.r

@@ -1,0 +1,46 @@
+require('gtools') # for dirichlet distribution
+
+# get utilities
+# load(file = 'buffered_meta_game_2x2.RDATA')
+load(file = 'buffered_meta_game_10x10.RDATA')
+U = means_total
+
+# parameters
+e = 0.001 # epsilon mutation probability
+
+getMutationMatrix = function(e){
+  x = 1 - 5*e - 3*e^2
+  m = matrix(c(x, e, e, e, e, e^2, e^2, e^2,
+              e, x, e, e, e^2, e, e^2, e^2,
+              e, e, x, e, e^2, e^2, e, e^2,
+              e, e, e, x, e^2, e^2, e^2, e,
+              e, e^2, e^2, e^2, x, e, e, e,
+              e^2, e, e^2, e^2, e, x, e, e,
+              e^2, e^2, e, e^2, e, e, x, e,
+              e^2, e^2, e^2, e, e, e, e, x), nrow=8, byrow = T)
+  colnames(m) = colnames(U)
+  rownames(m) = rownames(U)
+  return(m)
+}
+
+# initial population
+p = rdirichlet(1, rep(1,8))[1,]
+show(p)
+
+
+m = getMutationMatrix(e)
+
+for (i in 1:100000){
+  eu = rowSums(sweep(U,2,p,'*'))
+  av_eu = sum(eu*p)
+  p = p*eu / av_eu
+  p = colSums(sweep(m,1,p,'*'))
+}
+
+show(p)
+
+barplot(height = p, names.arg = names(p))
+
+d = data.frame(p = p, strategy = factor(names(p), levels = names(p)))
+myplot = ggplot(d, aes(x = strategy, y = p)) + geom_bar(stat = "identity")
+show(myplot)

### 2015-08-21 code/solitary_decision.r

@@ -1,0 +1,89 @@
+require('gtools') # for dirichlet distribution
+require('plyr') # to conveniently manipulate data frames
+require('ggplot2')
+require('reshape2')
+
+max.t=10
+max.a=10
+n.rounds = 5000
+
+p.trueL = 0
+a.bestL = 0
+n.tL = 0
+n.aL = 0
+a.brL = 0
+a.mrL = 0
+u.brL = 0
+u.mrL = 0                  
+
+for (i in 1:n.rounds) {
+  if (max.t > 2){
+    n.t = sample(2:max.t,1) # number of states
+  } else {
+    n.t = 2
+  }
+  if (max.a > 2){
+    n.a = sample(2:max.a,1) # number of acts
+  } else {
+    n.a = 2
+  }
+  u = matrix(sample(0:10,replace=TRUE,size=n.t*n.a),nrow=n.t,ncol=n.a) # utility matrix
+  p = rdirichlet(1,rep(1,n.t))[1,] # probabilities of states
+  # p = rep(1/n.t, n.t)
+  t = sample(1:n.t,1) # true state
+#   t = sample(1:n.t,1,prob=p) # true state, with bias
+  # get best response
+  tmp = u * p
+  eu = sapply(1:n.a, function(x) sum(tmp[,x])) # expected utility
+  a.br = which.max(eu) # best response
+  # get min-regret
+  best.v = sapply(1:n.t, function(x) max(u[x,] )) # best value
+  best.a = sapply(1:n.t, function(x) u[x,which.max(u[x,])] ) # best act
+  rgrt = sapply(1:n.a, function(x) max(best.v - u[,x])) # regret of each act
+  a.mr = which.min(rgrt) # act that minimizes regret 
+  # record data
+  p.trueL[i] = p[t]
+  a.bestL[i] = which.max(u[t,])
+  n.tL[i] = n.t
+  n.aL[i] = n.a
+  a.brL[i] = a.br
+  a.mrL[i] = a.mr
+  u.brL[i] = u[t,a.br]
+  u.mrL[i] = u[t,a.mr]
+}
+
+data = data.frame(p.true = p.trueL,
+                  a.best = a.bestL,
+                  n.t = n.tL,
+                  n.a = n.aL,
+                  a.br = a.brL,
+                  a.mr = a.mrL,
+                  u.br = u.brL,
+                  u.mr = u.mrL)
+
+show(mean(data$u.br))
+show(mean(data$u.mr))
+
[…]

### 2015-08-21 code/symmetric_games.r

@@ -1,0 +1,81 @@
+# computes averages for expected fitness overly randomly sampled stage games
+# outputs an approximation of a "meta-game"
+
+source('functions.R')
+
+CP_names = c("Sec-Reg", "Sec-Id", "Sec-Comp", "Sec-Alt", 
+             "Bel-Reg", "Bel-Id", "Bel-Comp", "Bel-Alt")
+
+rounds = 100000
+max_acts = 2
+
+row_util = rep(0,rounds*length(CP_names)^2)
+nActs = rep(2,rounds)
+
+pb <- txtProgressBar(max = rounds,style = 3)
+
+
+for (i in 1:rounds){
+  setTxtProgressBar(pb, i)
+  
+  U = create_game(ub_util=10, ub_acts=max_acts, symmetric = T)[,,1]
+  nActs[i] = dim(U)[1]
+
+  br = 1 # flat beliefs
+  
+  choices = list(maximin(regret_transform(U)), #Sec-Reg
+              maximin(U), # Sec-Id
+              maximin(relative_power_transform(U)), # Sec-Alt
+              maximin(general_power_transform(U)),  # Sec-Comp
+              max_value(regret_transform(U), br), #Bel-Reg
+              max_value(U, br), # Bel-Id
+              max_value(relative_power_transform(U), br), # Bel-Alt
+              max_value(general_power_transform(U), br)  # Bel-Comp
+  )
+  
+#   choices.c = list(maximin(regret_transform(U)), #Sec-Reg
+#                 maximin(U), # Sec-Id
+#                 maximin(relative_power_transform(U)), # Sec-Alt
+#                 maximin(general_power_transform(U)),  # Sec-Comp
+#                 max_value(regret_transform(U)), #Bel-Reg
+#                 max_value(U), # Bel-Id
+#                 max_value(relative_power_transform(U)), # Bel-Alt
+#                 max_value(general_power_transform(U))  # Bel-Comp
+#   )
+  
+  for (c in 1:length(CP_names)){
+    for (d in 1:length(CP_names)){
+      payoff = mean(as.vector(U[choices[[c]],choices[[d]]]))
+      row_util[((i-1)*length(CP_names)^2) + ((c-1)*length(CP_names))+(d)] = payoff
+    }
+  }  
+  
+}
+
+data = data.frame( #trial = factor(trial), 
+  #                   game_type = factor(game_type, levels=c("coordination", "anti-coordination",
[…]

### 2015-08-21 paper/paper.tex
paper comments added

@@
 
-\textbf{some notes and remarks and todo's}
+\textbf{some general notes and remarks and todo's}
 
@@
   type'', but that's what you reserved for regret type; maybe use \myalert{meta-type}?
-\item 
+\item can we reformulate the main result (proposition 1) in terms of ``strict dominance''
+  and/or strict Nash equilibrium? sometimes the proof is not ideally precise because it
+  actually shows something stronger, namely strict dominance, but everything is formulated in
+  terms of stability; using dominance is also better for arguments about evolutionary dynamics:
+  dynamics can be attracted by states that are not evolutionarily stable (even if there is an
+  ESS), but dominated strategies will die out in any case;
+\item should we give definitions for ESS and NSS in the main text?
+\item should we include definitions of the replicator dynamic and/or the replicator mutator
+  dynamic?
+\item the most important issue with this text is still that we need to motivate why we care
+  about non-probabilistic beliefs and/or security strategies; everything else will fall into
+  place when that is done
 \end{itemize}
@@
 \section{Introduction / Motivation}
+\label{sec:intr--motiv}
+
+\todo[inline]{this is only a dummy introduction; rewrite eventually with a better focus on the
+  results and main conceptual points we would like to drive home}
+
+Evolutionary game theory has become an established philosophical tool for probing into
+conceptual issues whose complexity requires mathematical modeling. However, most applications
+of EGT look at evolutionary selection of behavior in a single \emph{stage game}. There are
+actually two crude but common simplifications in this approach. Firstly, the stage game is
+usually considered fixed, closed and immutable \citep[there are exceptions, of course, such
+as][]{WordenLevin2007:Evolutionary-es, McKenzie-AlexanderSkymrs2012:Inventing-New-S}. Secondly,
+what evolves are behavioral strategies for the stage game \citep[what][call the ``behavioral
+gamit'']{FawcettHamblin2013:Exposing-the-be}.
+
+It has consequently been argued that, instead of focusing on a fixed, immutable stage game and
+the behavioral selection for that stage game alone, we should rather study the evolutionary
+selection of \emph{choice mechanisms} that are adapted in a rich and variable environment
+\citep[e.g.][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche}. However,
+formal accounts of the adaptive value of choice mechanisms have focused, for the most part, on
+the evolutionary benefit of learning rules
+\citep[e.g.][]{ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o}. \todo{More
+  references Harley 1981!!!, O Conor \dots}  Moreover, only little attention has been paid to
+modeling the direct (game-theoretic) meta-competition between alternative choice mechanisms
+\citep[see][for related criticism]{FawcettHamblin2013:Exposing-the-be}.
+
+Here, we would therefore make two contributions to the literature on evolution of choice
+mechanisms. On the conceptual side, we argue that paying attention to the evolution of
+(subjective representations of) preferences matters. Since almost any reasonable learning or
+decision-making process will make use of some (subjective, agent-internal (possibly
+unconscious)) representation of the quality of choice options, the question of which such
+representations are ecologically valuable (i.e., lead to high fitness) is central. Na\"ive
+intuition might convince us that obviously preferences that veridically represent the object
+fitness that evolutionary selection is based upon must surely be the best. We demonstrate that,
+if we take into account how agents represent uncertainty, this na\"ive conclusion is premature.
+
+On the methodological side, we introduce a conservative extension of standard EGT that allows
+us to reuse notions such as evolutionary stability / evolutionary dynamics and yet helps us
+study the evolutionary competition between choice mechanisms in a statistically variable
+environment. Concretely, we look at the evolutionary competition of choice mechanisms in a
+``meta-game'' that consists of the average expected payoffs of choice mechanisms when playing
+arbitrary games (from a given class). In this sense, a meta-game captures (the modeller's)
+assumptions about the relevant statistics of the environment in which evolutionary forces
+operate.
+
+Section~\ref{sec:rati--subj} introduces necessary concepts from formal decision and game
+theory. Section \dots
+
+\todo[inline]{add overview}
+
+\section{Rationality, subjectivity  \& subjective regret}
+\label{sec:rati--subj}
+
+\todo[inline]{would it make sense to tighten and restructure this section a little bit? what
+  about this: rationality says \emph{if} utils, beliefs and rational, then choose this; utils
+  and beliefs are unobservable; in some case utils and preferences \emph{can} be tight to the
+  environment (probability of a fair coin landing heads), in others no (probability of life on
+  Mars); if tight to environment its frequencies and fitness that would pin down a norm for
+  rational behavior, otherwise there's the danger of redescriptionism (just find some belief
+  and preference that rationalizes observed behavior); \dots }
+
+The standard definition of \textit{rationality} in economics and decision theory says that
+choice is rational only if it maximizes (subjective) expected utility. Since the work by vNM
+[cite], this view has been justified from the ``intuitive rationality'' of the axioms on the
+subjective preference relation leading to the representability of the decision maker as an
+expected utility maximizer. \todo{include axioms, or at least those that are mentioned as
+  relevant later} While in the axiomatization by [vNM] the probability of the outcomes is
+objectively given a priori, Savage54 provides a larger set of axioms that represent the
+decision maker (DM) with both a subjective utility over outcomes \textit{and} a
+\textit{subjective} probability over states of the world. Savage's axioms constitute the
+foundation of subjective expected utility (SEU) theory, that is normally assumed to define the
+rational behavior of economic agents.
+
+\begin{definition}[SEU-maximization] Let $S$ be a set of states of the world, $X$ a set of
+  outcomes and $A$ a set of actions. Given a probability measure $P$ on $S$ and a subjective
+  utility function $u:X \rightarrow \mathbb{R} $, an action $a^*: S \rightarrow X $ is
+  SEU-maximizing if $a^* \in \text{argmax}_{a_i \in A} \int_S u(a^*(s))dP(s) $. \todo{do we
+    actually need outcomes for anything in this paper?}
+\end{definition}
+
+The subjectivity of preferences plays a very important
+role for the present work. From an agent's standpoint, the amount $x$ of, say, money achieved does not necessarily
+coincide with the amount of subjective utility attained $u(x)$. 
+Historically,  the first to notice and formally argue for this difference
+between objective utility (goods, money, etc.) and subjective utility (preferences) was
+D. Bernoulli with the famous St. Petersburg paradox in 1738. Moreover, Bernoulli introduced the idea that a good representation of
+subjective utility can be carried out in terms of an increasing concave function of objective
+utility. This can be considered the birth of modern decision theory.
+
+Empirically, many violations of Savage's (and vNM's) axioms have been consistently observed in behavioral economics.
+Most of the attention has been focused on the Independence Axiom and the Sure-thing Principle.
+Allais' paradox and Ellsberg's paradox are examples of violations of these two axioms, and they are at the origin of Prospect theory [cite] and ambiguity in decision theory [cite].
+
+The main idea behind Ellesberg's paradox and the literature on ambiguity is that DM treats differently objective and subjective uncertainty.
+If the probability measure on the possible states of the world is not given a priori and not ''known'', then observed preferences leave no room to represent  DM's beliefs via a probability measure on the possible states.
+The most common solution is then to represent DM's beliefs with a set of probability measures instead of a single one.
+
+Prospect theory was introduced by Kahnemann and Tversky in
+their famous paper from 1979. By means of experimental results they noticed that DM apparently acts as a risk averse agent with respect to gains and as a risk loving agent
+with respect to losses. Consequently, they conjectured that the subjective utility is better
+representable by an S-shaped utility function, concave in the positive domain of gains and
+convex in the negative domain of losses.
+
+More recently, other possible definitions of the subjective utility function have been proposed
+and justified from a game theoretical point of view (e.g. Fehr and Schmidt, Charness and Rabin,
+etc.). The central goal of these studies is to explain/describe the empirical behavior in social dilemmas
+(e.g., Prisoner's dilemma, public goods game, etc.). In the same spirit of Prospect theory, by means of different subjective utility
+functions it is possible to describe/match the behavior observed in game theoretical experiments and to
+explain it as rational (in the sense of maximizing the subjective utility).
+With this approach every behavior, no matter how far from the maximization of
+objective utility, can be deemed rational if we can only find a subjective utility that
+justifies that behavior as maximizing the subjective utility. The problem here is that it seems possible to consider rational everything
+that is observed, given the adequate subjective utility function. The notion
+of rationality almost collapses onto the observed behavior.
+
+On the other side, other economists (Alchian, Friedman) seem to link the notion of rational choice
+more tightly to the maximization of objective utility. In their classic works they argue that
+profit maximization is a reasonable assumption for characterizing outcomes in a competitive
+market because only firms behaving in a manner that is consistent with profit maximization will
+survive in the long run. If the previous accounts of rationality looked more descriptive, this
+definitely tastes more normative. In this sense, a normative notion of rationality would be tightly
+related to (and almost coincide with) the maximization of objective utility, which is supposed
+to drive the evolutionary process. It follows then that being normative in this sense points to an identification of rationality with maximization of objective utility.
+
+It seems that we are stuck between two extrema: a too permissive descriptivism and a too restrictive normativism. On the one hand, if we want to have a
+descriptive notion of rationality, then we can (almost) always define an appropriate
+subjective utility whose maximization matches the observed behavior. On the other hand, if we
+want to have a normative approach to rationality, then it seems we have to appeal to
+evolutionary arguments entailing the understanding of rationality as maximization of objective
+utility.
+
+However, it has been argued that in a good theory of choice and decision making the normative
+and the descriptive components should not come apart. For example, as Douglas Maclean [cite]
+writes:
+
+\todo[inline]{personally, not a big fan of extended quotes; talks: yes, papers: don't know; is
+  this dear to your heart? who's that Maclean anyway? ;-)}
+
+\begin{quote}
+The history of the subject reflects strong reasons why the theory of choice should have this dual character. [...] \\
+A normative theory of choice gains credibility from its predictive and explanatory power, for although empirical success itself may not constitute much of a normative argument, the theory of rational behavior is less likely to be found objectionable if rationality turns out to be widespread.
+[...] But if, on the other hand, the normative theory turns out to be incompatible with the best established behavioral theory, then the verification of the normative theory will depend entirely on the intrinsic plausibility of its axioms, and that appeal must be quite strong, strong enough to make us overcome our charitable reluctance to conclude that our actual behavior is systematically irrational.
+\end{quote}
+
+There is another violation of Savage's axioms that is particularly relevant for the present work: transitivity of preferences.
+The first of Savage's axioms states that the preference relation is a (total) preorder, i.e., reflexive and transitive.
+Moreover, the preorder axiom is often referred to as the rationality axiom [cite], as to suggest that it is somehow the core of rational preferences.
+Violations of transitivity have been observed and studied in experimental literature [citeTversky69,etc], but can also be supported from a normative and theoretical point of view.
+\\
+In what follows, an important focus of our work will be the role of regret in decision making.
+Regret theory predicts the violation of both transitivity and Independence of Irrelevant Alternatives (IIA).
+[CONNECTING TO Fawcett\&al: this is IIA, not independence]
+
+\subsubsection{Regret theory} \label{sec:regreTheory}
+
+Regret theory has been introduced in decision theory by Savage [] and Niherens [], and later developed by Bell [1982], Loomes and Sugden [1982], and Fishburn [1982] independently.
+Lately, Halpern and Pass [cite] show how the use of regret minimization can solve game theoretical puzzles (like the Centipede and the Traveller's dilemma) in a way that is closer to everyday intuition and empirical data.
+In this paper the notion of regret is defined as in [HalPass12]:
+
+\begin{definition}[Pairwise regret] \label{defn:parwreg}
+Given a simultaneous-move game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the regret of player $i$ at profile $(a_i,a_{-i})$ is defined by: $\text{reg}(a_i,a_{-i}):= \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $, where $a_i^\$ \in A_i$ denotes $i$'s best reply to action $a_{-i} $.
+\end{definition}
+
+\begin{definition}[Regret] \label{defn:regret}
+Given a simultaneous-move game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the regret of an action $a_i \in A_i$ is defined by: $\text{reg}(a_i):= \text{max}_{a_{-i}\in A_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $.
+\end{definition}
+
+\begin{definition}[Regret minimization] \label{defn:regmin}
+Given a simultaneous-move game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, an action $a^{r}_i $ is regret minimizing if $a^{r}_i \in \text{min}_{a_i} \text{max}_{a_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $.
+\end{definition}
+
+\begin{example}[Coordination Game]
+  Let us consider the coordination game in Figure \ref{coordgame1}. It is easy to see that
+  $\text{reg}(I)=2$: when the other player chooses action $I$ the regret of $I$ is $0$ since
+  $I$ is a best reply to $I$, and when the other player chooses $II$ the regret of $I$ is $2$
+  since $\pi_i(II,II)-\pi_i(I,II)=2$. With the same reasoning, $\text{reg}(II)=1$. Two regret
+  minimizing players would then choose action $II$, each getting a payoff of $2$. In this case
+  regret minimization selects the Pareto-dominant Nash equilibrium. $ \medsquare $
+
+\begin{figure}
+\begin{center}%
+\begin{tabular}{|c|c|c|}
+\hline 
+ & I & II\tabularnewline
+\hline 
+\hline 
+I & 1;1 & 0;0\tabularnewline
+\hline 
+II & 0;0 & 2;2\tabularnewline
+\hline 
+\end{tabular}\end{center}
+
+\protect\caption{A coordination game $G^C$}
+\label{coordgame1}
+\end{figure}
+
+\end{example}
+
+\begin{example}[The Traveller's Dilemma \citep{HalpernPass2012:Iterated-Regret}]
+Let us now consider the Traveller's Dilemma case. The story behind the game goes as
+follows. There are two travellers, Ann and Bob, who lost their luggages. Ann and Bob had
+exactly the same luggage and they had insured the luggages with the same insurance company. The
+insurance policy is that the two travellers have to separately claim a certain amount between
+2\$ and 100\$ for the reimbursement, and if they both claim the same amount then they will be
+reimbursed by that amount. Otherwise, if one of them claims more than the other, then the one
+who claimed the higher amount will get the lower amount minus 2\$, while the one who claimed
+the lower amount will get what (s)he claimed plus 2\$. The game is symmetric, and the payoff
+function for both players is:
+\begin{align*}
+  \pi_i(a_i,a_{-i}) = \begin{cases} a_i \text{ \hspace{1cm} if } a_i = a_{-i} \\ a_i + 2 \text{
+      \hspace{.4cm} if } a_i < a_{-i} \\ a_{-i} -2 \text{ \hspace{.25cm} if } a_{-i} <
+    a_i \end{cases}
+\end{align*}
+By a simple computation we have:  $\forall a_i \in \lbrace 96\$, ..., 100\$ \rbrace \text{, } \text{reg}(a_i)=3 $ and $\forall a_i \in \lbrace 2\$, ..., 95\$ \rbrace \text{, } \text{reg}(a_i)>3$.
+If we now eliminate all the actions that do not minimize regret in the first place and iterate the regret minimization only on the action set $\lbrace 96\$, ..., 100\$ \rbrace$, we get that 97\$ is the action that minimize regret.
+Indeed, $\text{reg}(97)=2$ and $\forall a_i \in \lbrace 96\$, 98\$, 99\$, 100\$ \rbrace \text{, } \text{reg}(a_i)=3 $.
+Hence, one step of regret minimizing reasoning eliminates all the actions smaller than 96\$, and if we iterate the process once more the unique outcome is 97\$.
+Finally, it is worth noticing that the only rationalizable equilibrium of the game corresponds to the outcome $(2,2)$, that is consequently the only Nash equilibrium, the only perfect equilibrium, and the only sequential equilibrium of the game.
+$ \medsquare $
+
+\end{example}
+
+The meta-game perspective that we introduce in this paper can shed more light on the duality of descriptivism and normativism, and opens
+some space in between the two extrema. 
+By keeping the evolutionary approach we want to retain a
+normative perspective on rationality, but our results show that (under certain conditions)
+evolution does not necessarily lead to identifying rationality with maximization of objective
+utility, contrary to the intuition of Alchian [cite] and Friedman [cite].
+
+In the following we mainly deal with two types of agents: players whose subjective utility is defined
+in terms of regret (as in DEFINITION), and players whose utility
+function coincides with the objective utility $\pi_i$.
+
+The justification for this choice is both historical and behavioral. Among
+the possible competitors of utility maximization, regret has always been in a prominent
+position, both from a descriptive and normative viewpoint. Indeed, Bell82 writes:
+\begin{quote}
+  By explicitly incorporating regret, expected utility theory not only becomes a better
+  descriptive predictor but also may become a more convincing guide for prescribing behavior to
+  decision makers.
+\end{quote}
+In the same year, Graham Loomes and Robert Sugden \citet{LoomesSugden1982:Regret-Theory:-} show that a regret-based theory of choice can match
+and explain all the main experimental results of prospect theory, and claim that
+\begin{quote} [...] we shall challenge the idea that the conventional axioms [of decision
+  theory] constitute the only acceptable basis for rational choice under uncertainty. We shall
+  argue that it is no less rational to act in accordance with regret theory, and that
+  conventional expected utility theory therefore represents an unnecessarily restrictive notion
+  of rationality. \hfill \citep{LoomesSugden1982:Regret-Theory:-}
+\end{quote}
+
+\section{The model}
+\label{sec:model}
+
+\todo[inline]{first two paragraphs here are partly redundant}
+
+We consider an evolutionary model that is different, for the best of our knowledge, from all
+the standard models of evolutionary game theory. Given a game
+$ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, a subjective utility over $G$ is a function
+$\theta: A \rightarrow \mathbb{R} $, where $ A:=\prod_{i\in N}A_{i} $ as usual. We denote by
+$ \Theta:= \mathbb{R}^{|A|} $ the set of all the subjective utilities over $G$. The model we
+introduce here is a multiple game model, that we also call \textit{multi-game} or
+\textit{meta-game}, where a \textit{class} $\mathcal{G}$ of fitness games is played in a
+population. All the models used in evolutionary game theory that we are aware of always
+consider a single game at a time. \todo{better formulate less strongly} Our extension is meant
+to capture both a more general notion of environment and a more general notion of phenotype.
+
+There are good reasons to claim that focusing on more general psychological mechanisms instead
+of on behavior itself as the phenotype under evolutionary selection can be more faithful and
+insightful for natural biology and ecology [Fawcett\&al.].  In all classical models the agents
+are represented as playing a single fixed game, and as genetically predetermined to play fixed
+strategies, that consequently are the only target of natural selection in those
+frameworks. Standard evolutionary game theory cannot take charge of this shift of perspective
+until it will keep modelling a single game at a time, and until it will keep focusing on
+observed behavior only. ''Instead we should expect animals to have evolved a set of
+psychological mechanisms which enable them to perform well on average across a range of
+different circumstances''[Fawcett\&al.]. [maybe add evolution of preferences here]
+
+In this work we take $\mathcal{G}$ to be the class of symmetric $2 \times 2$ games\footnote{Note that this class includes many of the most famous games extensively considered in game theoretical literature, e.g., Prisoner's dilemma, Chicken game, Stag hunt, etc.}.
+First, a game $G$ is selected from the class of fitness games $\mathcal{G}$, and then players in the population are matched to play the game $G$.
+Each player is a function $\tau: \mathcal{G} \rightarrow  \Theta$, and we call $\tau$ a \textit{player type}, or just a \textit{type}\footnote{Notice that the function $\tau$ is well-defined since, for any symmetric $2 \times 2$ game, the codomain $\Theta=\mathbb{R}^{4}$ is the same.}.
+Intuitively, a type can be interpreted as a way of reasoning, a pattern of conceptualization, a thread that relates different subjective utilities across different games.
+We denote by $T$ the class of player types.
+For each game $G \in \mathcal{G}$, the evolutionary fitness is determined by the objective utility (payoff) function $\pi_G$, but the player's action choice depends on the player's subjective utility function $\tau(G)$, given by the player's type $\tau$.
+Notice that, for any symmetric game $G$, the action sets $(A_1, \dots, A_N)$ and the payoff functions $ (\pi_1, \dots, \pi_N)  $ are the same for all $i\in \lbrace 1, \dots N \rbrace$.
+Consequently, we only write $ A^G $ and $ \pi^G $ for the action set and the payoff function of game $G$, respectively.
+Moreover, in symmetric $2 \times 2$ games we have $A=A^G \times A^G$.
+Then, for $x,y \in A^G$ we denote by $\pi^G(x,y)$ the objective payoff of playing action $x$ in response to action $y$.\\
+
+\subsection{Player types}
+
+The set of all possible player types amouts to the set of all possible functions $ \tau: \mathcal{G} \rightarrow  \Theta $, i.e., $T=\mathbb{R}^{4^{\mathbb{R}^{4}}} $ , but for the sake of simplicity we will focus on types that are relevant and meaningful from a decision-theoretic point of view.
+We are mainly interested in two types: the objective type and the regret type.\\
+Given a game $G$ and Definition \ref{defn:parwreg}, it is straightforward to define the
+\textit{regret preference} $\theta^{reg}$ and the \textit{regret type} $\tau^{reg}$ as
+follows.
+
+\todo[inline]{can some of these definitions not be written as one? e.g., regret preference and
+  regret type as one definition? seems more elegant to me, because it's less repetitive (``for
+  a game ...'')}
+
+\begin{definition}[Regret preference] \label{defn:regpref}
+
+For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the regret preference $ \theta^{reg}: A \rightarrow \mathbb{R} $ such that $ \theta^{reg}(a_i,a_{-i})=-\text{reg}(a_i,a_{-i}) $.\footnote{More precisely, this is the negative regret, whereas the (positive) regret, as defined in [halpass], would not have the minus sign at the beginning of the formula.
+Here it will be easier to define the regret in terms of negative regret.}
+
+\end{definition}
+
+\begin{definition}[Regret type] \label{defn:regtype}
+
+Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call regret type the function $\tau^{reg}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{reg}(G)= \theta^{reg}$.
+
+\end{definition}
+
+\noindent Similarly, let us define the \textit{objective preference} $\theta^{\pi}$ and the \textit{objective type} $ \tau^{\pi} $, that we also call $\pi$\textit{-type}, as follows.
+
+\begin{definition}[Objective preference] \label{defn:objpref}
+
+For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the objective preference $ \theta^{\pi}: A \rightarrow \mathbb{R} $ such that $ \theta^{\pi}(a_i,a_{-i})=\pi(a_i,a_{-i}) $.
+
+\end{definition}
+
+\begin{definition}[Objective type] \label{defn:objtype}
+
+Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call objective type, or $\pi$-type, the function $\tau^{\pi}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{\pi}(G)= \theta^{\pi}$.
+
+\end{definition}
+
+\noindent In other words, we consider two prominent player types: a type who has a veridical subjective utility that perfectly matches the objective utility (i.e., the evolutionary fitness); and a type who has a non-veridical regret-based subjective utility.
+
+\iffalse
+(maybe we want to introduce altruistic and competitive only later) Other types of player have been studied in the literature. A famous example is the \textit{altruistic type}.
+
+\begin{definition}[Altruistic preference] \label{defn:altpref}
+
+For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{alt}: A \rightarrow \mathbb{R} $ such that $ \theta^{alt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \sum_{j \neq i} \pi(a_{j},a_{-j})$.\footnote{A more general formulation [see: REFERENCES] would be to define an $ \alpha$-altruistic type, for $\alpha \in [0,1]$, with subjective utility $ \theta^{\alpha lt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \alpha \sum_{j \neq i} \pi(a_{j},a_{-j})$.
+Since we are not interested in the evolution of degrees of altruism here, we simply fix $ \alpha = 1 $.}
+
+\end{definition}
+
+\begin{definition}[Altruistic type] \label{defn:alttype}
+
+Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{alt}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{alt}(G)= \theta^{alt}$.
+
+\end{definition}
+
+\noindent As opposite to the altruistic type, it is possible to define a \textit{competitive type} as follows.
+
+\begin{definition}[Competitive preference] \label{defn:compref}
+
+For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{com}: A \rightarrow \mathbb{R} $ such that $ \theta^{com}(a_i,a_{-i})=\pi(a_i,a_{-i}) - \sum_{j \neq i} \pi(a_{j},a_{-j})$.
+
+\end{definition}
+
+\begin{definition}[Competitive type] \label{defn:comtype}
+
+Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{com}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{com}(G)= \theta^{com}$.
+
+\end{definition}
+
+\fi
+
+\subsection{Epistemic types}
+\label{sec:epistemic-types}
+
+\todo[inline]{I think we really need a better (and earlier) justification for these epistemic
+  types; we could appeal to information available to agents; naturalness of situations in which
+  we cannot attach numbers to our beliefs (life on Mars again) \dots}
+
+In line with traditional evolutionary game theory, the idea of this work is to model a population of rather unsophisticated and myopic agents that possibly differ from each other with respect to two components: the player type and the epistemic type.
+In full generality, we think of an epistemic type as a general disposition to form beliefs about the co-player’s behavior.
+Players in the population obviously face uncertainty about the composition of the population that they are part of, and consequently about the type of co-player that they are randomly paired with at each round and about the co-player's actions.
+We represent this uncertainty that players entertain in two different ways, a probabilistic flat belief and a non-probabilistic belief.
+This amounts to having two different epistemic types $e$ in the population, $e \in \lbrace \overline{\mu}, \Delta(A_{-i}) \rbrace $, where $\overline{\mu}$ is the probabilistic type and $\Delta(A_{-i})$ is the non-probabilistic type, defined as follows:
+
+\begin{itemize}
+
+\item $ \Delta(A_{-i}):=\lbrace \mu \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu(a_{-i}) = 1 \rbrace$;
+
+\item $\overline{\mu} \in \lbrace \mu \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu(a_{-i}) = 1 \rbrace$ is the probability measure over the co-player's actions such that: $\forall a_{-i} \in A_{-i}$, $\overline{\mu}(a_{-i})= \frac{1}{|A_{-i}|}$.
+
+\end{itemize}
+
+Hence, we consider two possible epistemic states in the face of uncertainty.
+The epistemic type $\Delta(A_{-i})$ represents a situation of non-probabilistic radical uncertainty, where the players are not able to narrow down the set of probability distributions over the co-player's actions and they consider all of them as possible.
+The other epistemic type $\overline{\mu}$ conceptualizes the uncertainty about the population by using the principle of insufficient reason and ascribes equal probability to all the possible alternatives.
+Both options are reasonable and justifiable ways to deal with situations of uncertainty [REFERENCES].
+\\
+Since for the moment we want to model populations of biologically unsophisticated players, we do not endow them with an effective learning procedure.
+Our players encode both a psychological subjective representation of the interaction (player type) and a conceptualization of uncertainty (epistemic type), but they are too simple to have any learning or belief updating procedure.
+From this point of view, we can take the learning process away from natural selection and focus on player types and epistemic types as the target of evolutionary pressure.
+
+\subsection{Uncertainty aversion and maxmin rule}
+
+\todo[inline]{this paragraph seems to presuppose familiarity with maxi-minimization (can we
+  write this with a hyphen, any chance?); we should rewrite this or introduce the notion immediately;}
+
+Given a player type and an epistemic type, there are different ways to produce a behavior. A
+huge body of experimental literature strongly suggests that agents are generally uncertainty
+(or ambiguity) averse [REF]. This pattern of behavior in the presence of ucertainty has been
+famously axiomatized by Gilboa and Schmeidler in a paper from 1989. The idea is that being
+uncertainty averse amounts to behaving in accordance with maximinimizing expected utility over
+a set of prior probabilities. Whenever the set of priors is a singleton, maximinization of
+expected utility coincides with maximization of expected utility. In line with empirical data,
+we assume that players in the population are uncertainty averse and conform to maxmin expected
+utility. The resulting behavior is then produced by maximinimizing over the subjective utility
+given by the player type and the set of priors given by the epistemic type.
+
+  \todo[inline]{I would like to suggest to move Figure 2 next to Figure 1; it is already useful
+  for example 1 and could be referred to there already; I would suggest to use subfigures to
+  put both next to each other}
+
+\begin{example}
+  Consider the game in Figure \ref{coordgame1} again. When a player characterized
+  by\footnote{To ease notation in the following we will refer to a player directly as a pair
+    $(player \text{ } type \text{ } \tau,\text{ } epistemic\text{ } type \text{ } e)$.} player
+  type $ \tau^{reg} $ and epistemic type $ \Delta(A_{-i}) $ faces the game in Figure
+  \ref{coordgame1}, her player type gives rise to the representation $\tau^{reg}(G^C)$ in
+  Figure \ref{coordgame1reg}. Then, maximinimizing expected utility over the probability
+  simplex $ \Delta(A_{-i}) $ given the game in Figure \ref{coordgame1reg} corresponds to
+  playing the standard maxmin strategy [REF] of that game.\footnote{Notice that this is the
+    case for any game: given a game $G$, maximinimizing expected utility over the probability
+    simplex $ \Delta(A_{-i}) $ amounts to playing the standard maxmin strategy of $G$.} This,
+  in turn, corresponds to the regret minimizing action of the original game $G^C$ of Figure
+  \ref{coordgame1}, namely action $II$, as we have seen in Section \ref{sec:regreTheory}. A
+  player $(\tau^{reg},\overline{\mu})$ instead has subjective representation $\tau^{reg}(G^C)$
+  of Figure \ref{coordgame1reg} and a flat probability measure
+  $\overline{\mu}=(\frac{1}{2}I,\frac{1}{2}II)$ over the co-player's actions. Consequently,
+  such a player would play action $II$, i.e., the action that maximinimizes expected utility
+  given the flat probability measure $\overline{\mu}$.\footnote{As we already noticed,
+    maximinimizing expected utility given a probability measure $\mu$ is equivalent to
+    maximizing expected utility given $\mu$.}  Similarly, a player
+  $(\tau^{\pi},\Delta(A_{-i}))$ will have the subjective representation coinciding with the
+  objective fitness game, i.e., $ \tau^{\pi}(G^C)= G^C $. Then, both actions $I$ and $II$
+  maximinimize expected utility over the probability simplex $ \Delta(A_{-i}) $. Hence, a
+  player $(\tau^{\pi},\Delta(A_{-i}))$ will be indifferent between $I$ and $II$, and will
+  randomize with equal probability $(\frac{1}{2}I,\frac{1}{2}II)$. Finally, a player
+  $(\tau^{\pi},\overline{\mu})$ maximinimizes the objective fitness game $G^C$ of Figure
+  \ref{coordgame1} with flat probability $\overline{\mu}$ over the co-player's actions, i.e.,
+  maximizes objective utility given $\overline{\mu}$. In game $G^C$ this yields action $II$.
+
+\begin{figure}
+\begin{center}%
+\begin{tabular}{|c|c|c|}
+\hline 
+ & I & II\tabularnewline
+\hline 
+\hline 
+I & 0;0 & -2;-1\tabularnewline
+\hline 
+II & -1;-2 & 0;0\tabularnewline
+\hline 
+\end{tabular}\end{center}
+
+\protect\caption{Regret representation $\tau^{reg}(G^C)$}
+\label{coordgame1reg}
+\end{figure}
+
+\end{example}
+
+We are now in the position of deriving behavior directly from the pair $(\tau, e)$.
+Definitions \ref{def:utility-belief} and \ref{def:maxminSEU} simply formalize the notions of subjective expected utility and maxmin subjective expective utility, respectively.
+
+\begin{definition} \label{def:utility-belief}
+
+Given a game $G$, an action $a_i \in A_i$, and a belief $\mu \in \lbrace \mu' \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu'(a_{-i}) = 1 \rbrace$, we define $\tau(G)(a_i, \mu):= \sum_{a_{-i} \in A_{-i}} \tau(G)(a_i, a_{-i}) \cdot \mu(a_{-i})$.
+
+\end{definition}
+
+\begin{definition} \label{def:maxminSEU}
+
+Given a game $G$ and a player $(\tau, e)$, we define $\text{maxmin}(\tau(G), e):= \lbrace a'_i \in A_i : a_i \in \text{max}_{a_i \in A_i} \text{ min}_{\mu \in e} \text{ } \tau(G)(a_i, \mu) \rbrace$.
+
+\end{definition}
+
+\noindent Definition \ref{def:expected fitness} gives the expected evolutionary fitness of player $(\tau, e)$ against player $(\tau', e')$ in game $G$.\footnote{As already specified in the previous example, we assume that, whenever the set $\text{maxmin}(\tau(G), e)$ is not a singleton, the player $(\tau, e)$ will mix with equal probability among the actions in $\text{maxmin}(\tau(G), e)$.}
+
+\begin{definition} \label{def:expected fitness}
+
+Given a game $G \in \mathcal{G}$, a player $(\tau, e)$, and a player $(\tau', e')$, we define $\pi^G((\tau, e),(\tau', e')):= \pi^G(\text{maxmin}(\tau(G), e),\text{maxmin}(\tau'(G), e'))$.
+
+\end{definition}
+
+\todo[inline]{should we explain here, or very soon, what the resulting types really are: regret
+  minimizers, maximin players \dots}
+
+Many other alternatives different from maxmin expected utility could produce behavior: choice rules like minmax, maxmax, and minmin expected utility would similarly generate behavior from a player type and an epistemic type.
+Here we postulate that players are maximinimizers for two main reasons.
+First, our main interest is the evolution of different patterns of subjective conceptualizations of games (player types), and we want to show that the veridical representation (objective type) is not necessarily the fittest and may not be evolutionarily stable.
+Assuming that all players use the maxmin rule independent of their player type allows us to factor the choice rule out of the selection process and to focus on player types.
+Secondly, as already mentioned, among other possible choice rules maxmin is not only intuitively appealing but also corroborated from an empirical point of view.
+
+Before concluding this section, it is worth stressing two important points.
+
+\begin{fact} \label{fact:maxEU-minReg}
+
+For any given single probability $\mu$, maximization of expected utility and minimization of expected regret are behaviorally equivalent.
+
+\end{fact}
+
+\noindent As we have seen in the previous example, this is not the case in the presence of (radical) uncertainty, in the sense of representation of belief state in terms of a set of probability, as in $ \Delta(A_{-i}) $.
+
+\begin{fact} \label{fact:equivalence2x2}
+
+In the class of $2 \times 2$ symmetric games, players $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg},\overline{\mu})$ are behaviorally equivalent.
+
+\end{fact}
+
+\noindent Two remarks. Firstly, Fact \ref{fact:equivalence2x2} does not hold for $n \times n$
+symmetric games in general. Secondly, we treat behaviorally equivalent types as distinct,
+because we assume that what is selected by biological evolution is not choice behavior as such,
+but the mechanism which generates behavior. This matters in particular if we assume that
+mutations affect different components of the behavior generating mechanisms (see below).
+
+\subsection{Evolution \& the environment}
+
+[MAYBE, put part of Version2 from Snippets here, if not in Introduction]
+
+In standard evolutionary game theory a population of agents plays over a single game, that is supposed to represent the interaction driving the evolutionary dynamics.
+In line with [Fawcett-al.], we claim that the single-game approach is too limiting to encompass the vast variety of interactions that lead evolution.
+Here we propose the meta-game model in order to account for a more general notion of environment.
+By allowing the population to play over a class of possible games, we want to take into consideration a notion of environment that comprises a multitude of possible interactions as the driver of natural selection.
+In this perspective, the meta-game approach represents a model of evolution more faithful and possibly closer to reality.
+\\
+We assume a huge, possibly infinite, population of players $(\tau,e)$.
+At each time, a game $G$ is selected from the class of possible games, and players are randomly paired to play $G$.
+At the end of the play we keep track of the evolutionary fitness achieved by each player.
+Next, another game $G'$ is randomly selected again, and so on.
+The evolutionary fitness of each player is then based on the expected objective payoff over the class $\mathcal{G}$.
+Denoting by $P(G)$ the probability of game $G$ to be selected, the evolutionary fitness of player $(\tau,e)$ against player $(\tau',e')$ is given by:
+
+$$ EF((\tau,e),(\tau',e'))= \int_G  P(G) \cdot \pi^G((\tau, e),(\tau', e')).  $$
+
+\noindent The framework we propose here is a very neutral and flexible tool to model the notion of environment.
+We can take into account many different types of environment by simply changing the class $\mathcal{G}$ of possible games, and in the limit case where $\mathcal{G}$ is a sigleton our model reduces to the standard models of evolutionary game theory.
+By combining field studies and statistics, one could design a more specific class $\mathcal{G}$ with appropriate probabilities $P(G)$ in order to match the natural environment of a given population, but for our theoretical purposes we adopt another approach.
+As already anticipated, we take $\mathcal{G}$ to be the class of $2 \times 2$ symmetric games.
+More precisely, we imagine the class $\mathcal{G}$ to be generated from the generic form table of Figure \ref{generic form table}, where $a,b,c,d$ are i.i.d.
+random variables sampled from a finite set of natural numbers $ \lbrace \underline{n}, \dots, \overline{n}  \rbrace$.
+
+\begin{figure}
+\begin{center}%
+\begin{tabular}{|c|c|c|}
+\hline 
+ & I & II\tabularnewline
+\hline 
+\hline 
+I & a;a & b;c\tabularnewline
+\hline 
+II & c;b & d;d\tabularnewline
+\hline 
+\end{tabular}\end{center}
+
+\protect\caption{generic form table for $2 \times 2$ symmetric games}
+\label{generic form table}
+\end{figure}
+
+\section{Results: the basic model}
+\label{sec:results:-basic-model}
+
+In this section we present results of computer simulations and analytical proofs for our basic
+model with the four player types introduced in the previous section.
+
+\subsection{Numerical simulations}
+\label{sec:numer-simul}
+
+Table~\ref{tab:ExpectedFitness_4Types} gives an approximation of expected fitness, obtained by
+numerical simulation from averaging over $100,000$ randomly sampled games in $\mathcal{G}$ with
+$a,b,c,d \in \lbrace 0, \dots, 10 \rbrace$. Concretely, games were sampled repeatedly by
+choosing independently four integers $a,b,c,d \in \lbrace 0, \dots, 10 \rbrace$ uniformly at
+random. For each game, a player type's action choices were determined and payoffs from all
+pairwise encounters recorded. (Whenever a player type would not select a unique action in a
+given game, we recorded unbiased averages over playing either action.) The number in each cell
+of Table~\ref{tab:ExpectedFitness_4Types} is the average payoff for the row player type over
+all 100,000 numbers for each pairing of player types obtained in this way. These averages
+approximate the corresponding average evolutionary fitness of the row player when matched with
+the column player.
+
+\begin{table}[t]
+\centering
+\begin{tabular}{ccccc}
+  \toprule
+ & $\tau^{reg}, \Delta(A_{-i})$ 
+ & $\tau^{\pi}, \Delta(A_{-i})$ 
+ & $\tau^{reg}, \overline{\mu}$ 
+ & $\tau^{\pi}, \overline{\mu}$ \\ 
+  \midrule
+  $\tau^{reg}, \Delta(A_{-i})$ & 6.663 & 6.662 & 6.663 & 6.663 \\ 
+  $\tau^{\pi}, \Delta(A_{-i})$ & 6.486 & 6.484 & 6.486 & 6.486 \\ 
+  $\tau^{reg}, \overline{\mu}$ & 6.663 & 6.662 & 6.663 & 6.663 \\  
+  $\tau^{\pi}, \overline{\mu}$ & 6.663 & 6.662 & 6.663 & 6.663 \\ 
+   \bottomrule
+\end{tabular}                    
+\caption{Average evolutionary fitness in simulations of 100,000 symmetric $2 \times 2$ games}
+\label{tab:ExpectedFitness_4Types}
+\end{table}
+
+Simulation results obviously reflect Fact~\ref{fact:equivalence2x2} in that all encounters in
+which types $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{reg}, \overline{\mu})$ or
+$(\tau^{\pi}, \overline{\mu})$ are substituted for one another yield identical results. More
+interestingly, Table~\ref{tab:ExpectedFitness_4Types} shows that the maximin strategy
+$(\tau^{\pi}, \Delta(A_{-i}))$ is strictly dominated by either of the three other strategies:
+in each column (i.e., for each kind of opponent), the maximin strategy is strictly worse
+than any of the three behaviorally equivalent competitors. This has a number of interesting
+consequences.
+
+Let's begin with a restricted scenario and look at more and more complex cases afterwards. If
+we restrict attention to a population of radically uncertain players, i.e., where only
+epistemic type $\Delta(A_{-i})$ exists, the regret type $ \tau^{reg} $ is the only
+\emph{evolutionarily stable state}. An evolutionarily stable state is a state which cannot be
+invaded by a small number of mutants. More strongly, since maximin play is strictly dominated,
+we expect selection that is driven by expected fitness to invariably weed out maximin behavior
+in favor of regret minimization. In other words, when taking average payoffs over the class of
+random games looked at here, regret minimization is a better choice rule than standard maxmin
+from an evolutionary point of view, despite the fact that the former, but not the letter
+entertains non-veridical subjective preferences.
+
+Next, if we look at the competition between all four types represented in
+Table~\ref{tab:ExpectedFitness_4Types}, $(\tau^{reg}, \Delta(A_{-i}))$ is no longer
+evolutionarily stable. Rather, given behavioral equivalence (Fact~\ref{fact:equivalence2x2}),
+types $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{reg}, \overline{\mu})$, and
+$(\tau^{\pi}, \overline{\mu})$ are all \emph{neutrally stable}
+\citep{Maynard-Smith1982:Evolution-and-t}. But since $(\tau^{\pi}, \Delta(A_{-i}))$ is strictly
+dominated and so disfavored by fitness-based selection, we are still drawn to conclude that
+maximin behavior is weeded out in favor of a population with a random distribution of the
+remaining three types.
+
+Simulation results of the (discrete time) \emph{replicator dynamics}
+\citep{TaylorJonker1978:Evolutionary-St} indeed show that random initial population
+configurations are attracted to states with only three player types:
+$\tuple{\tau^{reg}, \Delta(A)}$, $\tuple{\tau^{reg}, \bar{\mu}}$ and
+$\tuple{\tau^{\pi}, \bar{\mu}}$. The relative proportions of these depend on the initial
+population.\todo{check uniform notation for player types: round vs.~square brackets} This
+variability disappears if we add a small mutation rate to the dynamics. We assume a fixed,
+small mutation rate $\epsilon$ for the probability that a player's preference type \emph{or}
+her epistemic type changes to another random preference type or epistemic type. The probability
+that a player type randomly mutates into a completely different player type with altogether
+different preference type and epistemic type would then be $\epsilon^2$. With these assumptions
+about ``component-wise mutations'', numerical simulations of the (discrete time)
+\emph{replicator mutator dynamics} \citep{Nowak2006:Evolutionary-Dy} show that already for very
+small mutation rates almost all initial populations converge to a single fixed point in which
+the majority of players are regret types. For instance, with $\epsilon = 0.001$, almost all
+initial populations are attracted to a final distribution with proportions:\todo{recalculate
+  these numbers for the actual 4x4 game!}
+
+\begin{center}
+  \begin{tabular}{ccc}
+    $\tuple{\tau^{reg}, \Delta(A)}$ & $\tuple{\tau^{reg},
+      \bar{\mu}}$ & $\tuple{\tau^{\pi}, \bar{\mu}}$ \\ \hline
+    0.279  &   0.383 &    0.281 
+  \end{tabular}
+\end{center}
+
+What this suggests is that, since biological evolution selects behavior-generating mechanisms,
+not behavior as such, it need not be the case that behaviorally equivalent mechanisms are
+treated equally all the while. If mutation probabilities are a function of individual
+components of such behavior-generating mechanisms, it can be the case that certain components
+are more strongly favored by a process of random mutation and selection. This is exactly the
+case with regret-based subjective preferences in the present example. Since regret-based
+subjective preferences are much better in connection with radical uncertainty than veridical
+preferences are, the proportion of expected regret minimizers in the attracting state is
+substantially higher than that of expected utility maximizers, even though these types are
+behaviorally equivalent. In sum, component-wise mutation could have lead to a majority of
+regret-based players even if they are behaviorally indiscernible from decision makers with
+veridical preferences, because regret types are better off under radical uncertainty.
+
+\subsection{Analytical results}
+\label{sec:analytical-results}
+
+Results based on the single meta-game in Table~\ref{tab:ExpectedFitness_4Types}, which was
+obtained by averaging over numerical simulations, are not fully general and possibly spoiled by
+random fluctuations in the sampling procedure. Fortunately, for the case of symmetric
+$2 \times 2$ games, the main result that maximin types $(\tau^{\pi}, \Delta(A_{-i}))$ are
+strictly dominated can also be shown analytically for generous general conditions on how likely
+randomly sampled games are.
+
+\begin{proposition} \label{proposition1}
+
+  Let $\Lambda = \lbrace (\tau^{\pi}, \Delta(A_{-i})), (\tau^{reg}, \Delta(A_{-i})) \rbrace$ be
+  the set of possible meta-types $(\tau, e)$ in the population, and let $\mathcal{G}$ be the class
+  of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex,
+  set of i.i.d.~values. Then, $(\tau^{reg}, \Delta(A_{-i}))$ is the only strict Nash
+  equilibrium in the resulting meta-game.
+
+\end{proposition}
+
+\begin{proof}
+See Appendix.
+\end{proof}
+
+From Fact \ref{fact:equivalence2x2} and Proposition \ref{proposition1} the following corollary follows.
+
+\begin{corollary} \label{corollary1}
+
+  Fix $T = \lbrace \tau^{\pi}, \tau^{reg} \rbrace$,
+  $E = \lbrace \Delta(A_{-i}), \overline{\mu} \rbrace$, $\Lambda= T \times E$, and
+  $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite,
+  or compact and convex, set of i.i.d. values. Then, player type $(\tau^{\pi}, \Delta(A_{-i}))$
+  is strictly dominated by $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
+  $(\tau^{reg}, \overline{\mu})$.
+
+\end{corollary}
+
+\begin{proof}
+See Appendix.
+\end{proof}
+
+Corollary~\ref{corollary1} tells us that the conclusions drawn in the previous section based on
+the meta-game in Table~\ref{tab:ExpectedFitness_4Types} hold more generally for any class of
+games in which the probability of encountering a game is the product of independently sampling
+four identically distributed payoff values. As before, player types
+$(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
+$(\tau^{reg}, \overline{\mu})$ will be neutrally stable, and fitness-based selection will tend
+to weed out maximin play and leave us with a population of arbitrary frequency of
+$(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
+$(\tau^{reg}, \overline{\mu})$ meta-types.
+
+This shows that there is support for the main conceptual point that we wanted to make:
+non-veridical subjective preference relations \emph{can}, under specific circumstances, persist
+under evolutionary selection based on objective fitness. Moreover, regret-based preferences can
+not only persist, but even be favored by natural selection if agents are radically
+uncertain. This holds generally for playing arbitrary $2 \times 2$ games whose payoffs are
+sampled identically and independently at random.
+
+\section{Extensions}
+\label{sec:extensions}
+
+How do the basic results from the previous section carry over to more encompassing, richer
+models? Section~\ref{sec:more-types} first considers further conceptually interesting
+preference types that have been suggested in the recent literature. Section~\ref{sec:n-times-n}
+then considers the case of $n \times n$ games for $n \ge 2$. Finally, to put our results into
+the proper perspective, Section~\ref{sec:solitary-decisions} ends with a brief comparison of
+game situations with cases of solitary decision making.
+
+\subsection{More types}
+\label{sec:more-types}
+
+In evolutionary game theory other types of player have been investigated.
+A famous example is the \textit{altruistic type} [REF], introduced in the literature in order to explain the possible survival of altruistic behavior.
+In our framework, we can represent the altruistic type as follows.
+
+\begin{definition}[Altruistic preference] \label{defn:altpref}
+
+For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{alt}: A \rightarrow \mathbb{R} $ such that $ \theta^{alt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \sum_{j \neq i} \pi(a_{j},a_{-j})$.\footnote{A more general formulation [see: REFERENCES] would be to define an $ \alpha$-altruistic type, for $\alpha \in [0,1]$, with subjective utility $ \theta^{\alpha lt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \alpha \sum_{j \neq i} \pi(a_{j},a_{-j})$.
+Since we are not interested in the evolution of degrees of altruism here, we simply fix $ \alpha = 1 $.}
+
+\end{definition}
+
+\begin{definition}[Altruistic type] \label{defn:alttype}
+
+Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{alt}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{alt}(G)= \theta^{alt}$.
+
+\end{definition}
+
+\noindent As opposite to the altruistic type, it is possible to define a \textit{competitive type}.
+
+\begin{definition}[Competitive preference] \label{defn:compref}
+
+For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{com}: A \rightarrow \mathbb{R} $ such that $ \theta^{com}(a_i,a_{-i})=\pi(a_i,a_{-i}) - \sum_{j \neq i} \pi(a_{j},a_{-j})$.
+
+\end{definition}
+
+\begin{definition}[Competitive type] \label{defn:comtype}
+
+Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{com}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{com}(G)= \theta^{com}$.
+
+\end{definition}
+
+Similarly to the evolutionary competition that we simulated before, we can study the
+evolutionary fitness of this extended set of players when they are all represented in the
+population. Table~\ref{tab:ExpectedFitness_2x2_Full} shows simulation results that approximate the
+expected fitness in the relevant meta-game.
+
+\begin{table}[]
+\centering
+\footnotesize
+\begin{tabular}{ccccccccc}
+  \hline
+ & $\tuple{\tau^{reg}, \Delta(A)}$ 
+ & $\tuple{\tau^{\pi}, \Delta(A)}$ 
+ & $\tuple{\tau^{com}, \Delta(A)}$
+ & $\tuple{\tau^{alt}, \Delta(A)}$
+ & $\tuple{\tau^{reg}, \bar{\mu}}$ 
+ & $\tuple{\tau^{\pi}, \bar{\mu}}$ 
+ & $\tuple{\tau^{com}, \bar{\mu}}$
+ & $\tuple{\tau^{alt}, \bar{\mu}}$ \\ 
+  \hline
+  $\tuple{\tau^{reg}, \Delta(A)}$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
+  $\tuple{\tau^{\pi}, \Delta(A)}$ & 6.486 & 6.484 & 6.088 & 6.703 & 6.486 & 6.486 & 6.088 & 6.875 \\
+  $\tuple{\tau^{com}, \Delta(A)}$ & 6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\
+  $\tuple{\tau^{alt}, \Delta(A)}$ & 5.949 & 5.722 & 5.326 & 6.396 & 5.949 & 5.949 & 5.326 & 6.568 \\
+  $\tuple{\tau^{reg}, \bar{\mu}}$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
+  $\tuple{\tau^{\pi}, \bar{\mu}}$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
+  $\tuple{\tau^{com}, \bar{\mu}}$ & 6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\
+  $\tuple{\tau^{alt}, \bar{\mu}}$ & 6.331 & 5.893 & 5.497 & 6.566 & 6.331 & 6.331 & 5.497 & 7.152 \\
+   \hline                          
+\end{tabular}                      
+\caption{Average payoff in simulations of 100,000
+  randomly generated $2 \times 2$ symmetric games.}
+\label{tab:ExpectedFitness_2x2_Full}        
+\end{table}
+
+\todo[inline]{is it true that competitive preferences types are behaviorally equivalent under
+  either epistemic type? can we show that?}
+
+The approximations in Table~\ref{tab:ExpectedFitness_2x2_Full} confirm basic intuitions about
+altruistic and competitive types: averaging over randomly sampled games, everybody would like
+to have an altruistic opponent and nobody would like to play against a competitive
+opponent. Perhaps more surprisingly, altruistic types come up strictly dominated by competitive
+types, but competitive types themselves are worse off against all opponent types except against
+maximin players $\tuple{\tau^{\pi}, \Delta(A)}$ than any of the behaviorally equivalent types
+$(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
+$(\tau^{reg}, \overline{\mu})$.  This is a noteworthy results in the light of the fact that
+evolving altruistic preferences have been shown to support cooperative behavior in a single
+stage game \myalert{[CITE]}. \todo{@Paolo: check whether this is true, please!} In contrast,
+averaging over payoffs in multiple stage games, like we do here, makes altruistic preferences
+prime victims of evolutionary eradication.
+
+It is easy to see then that the previous result still obtains for the larger meta-game in
+Table~\ref{tab:ExpectedFitness_2x2_Full}: $(\tau^{reg}, \Delta(A_{-i}))$,
+$(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$ are still neutrally stable;
+all simulations of the (discrete-time) replicator dynamic on the $8 \times 8$ meta-game from
+Table~\ref{tab:ExpectedFitness_2x2_Full} end up in populations consisting of only these types
+in arbitrary proportion.
+
+The following proposition (partially) confirms this result.\todo{rephrase to acknowledge all
+  epistemic types?}
+
+\begin{proposition} \label{proposition2}
+
+Fix $\Lambda = \lbrace (\tau^{\pi}, \Delta(A_{-i})), (\tau^{reg}, \Delta(A_{-i})), (\tau^{alt}, \Delta(A_{-i})), (\tau^{com}, \Delta(A_{-i})) \rbrace$ and $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex, set of i.i.d.
+values.
+Then, $(\tau^{reg}, \Delta(A_{-i}))$ is the only evolutionarily stable player in the population.
+
+\end{proposition}
+
+\begin{proof}
+See Appendix.\todo{is this there already?}
+\end{proof}
+
+In sum, the presence of other plausible preference types, such as competitive and altruistic
+types does not undermine the previous results about the evolutionary drive towards regret-based
+subjective preferences.
+
+\subsection{$n \times n$ symmetric games}
+\label{sec:n-times-n}
+
+Results from Section~\ref{sec:results:-basic-model} relied heavily on
+Fact~\ref{fact:equivalence2x2} that, for the special case of $2 \times 2$ symmetric games,
+regret minimization $\tuple{\tau^{reg}, \Delta(A)}$ is behaviorally equivalent with expected
+regret minimization $\tuple{\tau^{reg}, \bar{\mu}}$ and expected utility maximization
+$\tuple{\tau^{\pi}, \bar{\mu}}$. This is no longer true when we look at arbitrary $n \times n$
+games with $n \ge 2$. We should therefore see what happens in a broader class of games.
+
+Table~\ref{tab:ExpectedFitness_10x10} therefore gives approximations for expected fitness in a
+meta-game over a class of $n \times n$ symmetric games where $n$ is randomly drawn from
+$\set{2, \dots, 10}$. Concretely, the numbers in Table~\ref{tab:ExpectedFitness_10x10} are
+averages of payoffs obtained in 100,000 randomly sampled games, where each game was sampled by
+first picking a number of acts $n \in \set{2, \dots, 10}$ uniformly at random, and then filling
+the resulting $n \times n$ payoff matrix of the stage game with i.i.d.~sampled payoffs as
+before.
+
+\begin{table}[]
+\centering
+\footnotesize
+\begin{tabular}{ccccccccc}
+  \toprule
+ & $\tuple{\tau^{reg}, \Delta(A)}$ 
+ & $\tuple{\tau^{\pi}, \Delta(A)}$ 
+ & $\tuple{\tau^{com}, \Delta(A)}$
+ & $\tuple{\tau^{alt}, \Delta(A)}$
+ & $\tuple{\tau^{reg}, \bar{\mu}}$ 
+ & $\tuple{\tau^{\pi}, \bar{\mu}}$ 
+ & $\tuple{\tau^{com}, \bar{\mu}}$
+ & $\tuple{\tau^{alt}, \bar{\mu}}$ \\ 
+  \midrule
+  $\tuple{\tau^{reg}, \Delta(A)}$ & 6.567 & 6.570 & 5.650 & 6.992 & 6.564 & 6.564 & 5.593 & 7.409 \\
+  $\tuple{\tau^{\pi}, \Delta(A)}$ & 6.476 & 6.483 & 5.896 & 6.818 & 6.484 & 6.484 & 5.850 & 7.124 \\
+  $\tuple{\tau^{com}, \Delta(A)}$ & 6.468 & 6.647 & 5.512 & 7.169 & 6.578 & 6.578 & 5.577 & 7.354 \\
+  $\tuple{\tau^{alt}, \Delta(A)}$ & 5.968 & 5.923 & 5.363 & 6.685 & 5.975 & 5.975 & 5.086 & 6.973 \\
+  $\tuple{\tau^{reg}, \bar{\mu}}$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
+  $\tuple{\tau^{\pi}, \bar{\mu}}$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
+  $\tuple{\tau^{com}, \bar{\mu}}$ & 6.529 & 6.680 & 5.445 & 7.276 & 6.542 & 6.542 & 5.521 & 7.440 \\
+  $\tuple{\tau^{alt}, \bar{\mu}}$ & 6.450 & 6.337 & 5.772 & 6.978 & 6.457 & 6.457 & 5.479 & 7.500 \\
+   \bottomrule                         
+\end{tabular}                      
+\caption{Average payoff in simulations of 100,000
+  randomly generated $n \times n$ symmetric games with $n$ randomly drawn from $\set{2, \dots, 10}$.}
+\label{tab:ExpectedFitness_10x10}        
+\end{table}
+
+As is to be expected, average payoffs obtained in games with more than 2 acts are higher, as
+can be seen by comparing Table~\ref{tab:ExpectedFitness_10x10} with
+Table~\ref{tab:ExpectedFitness_2x2_Full}. But increases in approximate expected fitness are not
+uniform. Most importantly, the regret minimizing type $\tuple{\tau^{reg}, \Delta(A)}$ is
+strictly dominated by $\tuple{\tau^{reg}, \bar{\mu}}$ and by $\tuple{\tau^{\pi}, \bar{\mu}}$ in
+the meta-game from Table~\ref{tab:ExpectedFitness_10x10}. This means that while regret
+minimization \emph{can} thrive in some evolutionary contexts, there are also contexts where it
+is demonstrably worse off.
+
+Still, although this may be bad news for regret minimizing types
+$\tuple{\tau^{reg}, \Delta(A)}$, it is not the case that regret types \emph{as such} are weeded
+out by selection. Since, by Fact~\ref{fact:maxEU-minReg}, $\tuple{\tau^{reg}, \bar{\mu}}$ and
+$\tuple{\tau^{\pi}, \bar{\mu}}$ are generally behaviorally equivalent, it remains that
+selection based on meta-games constructed from $n \times n$ games will still not eradicate all
+regret types. So, although regret types may not be selected for in this case, they are also not
+selected against.
+
+On the other hand, there are plenty of ways in which the basic insight from
+Proposition~\ref{proposition1} that regret-based preferences can be strictly better than
+veridical objective preferences in case of radical uncertainty could make for situations in
+which evolution would select for regret types exclusively, even in $n \times n$ games. If, for
+example, epistemic types of players are not what biological evolution selects, but rather
+something that the particular choice situation would exogenously give us, then regret-based
+preference \emph{can} again drive out veridical preferences altogether. For concreteness,
+suppose that only preference types compete and that agents' epistemic types are exogenously
+given, in such a way that agents hold flat probabilistic beliefs $\bar{\mu}$ with probability
+$1-p$ and are of type $\Delta(A)$ with probability $p$. This transforms the meta-game from
+Table~\ref{tab:ExpectedFitness_10x10} into the simpler $4 \times 4$ game in which the payoff
+obtained for a preference type is the weighted average over the payoffs of that preference
+types in Table~\ref{tab:ExpectedFitness_10x10}. Setting $p = 0.02$ for illustration, we get the
+meta-game in Table~\ref{tab:ExogeneousEpistemics}.
+
+\begin{table}[]
+\centering
+\begin{tabular}{ccccc}
+  \toprule
+  & $\tau^{reg}$ 
+  & $\tau^{\pi}$ 
+  & $\tau^{com}$
+  & $\tau^{alt}$ \\ 
+  \midrule
+  $\tau^{reg} $ & 6.926 & 6.926 & 5.942 & 7.757 \\ 
+  $\tau^{\pi} $ & 6.924 & 6.924 & 5.948 & 7.751 \\ 
+  $\tau^{com }$ & 6.566 & 6.570 & 5.481 & 7.434 \\ 
+  $\tau^{alt} $ & 6.463 & 6.461 & 5.478 & 7.469 \\ 
+   \bottomrule
+\end{tabular}
+\caption{Meta-game for the evolutionary competition between preference types when epistemic types are exogenously
+  given}
+\label{tab:ExogeneousEpistemics}
+\end{table}
+
+The only evolutionarily stable state of this meta-game is the regret type. Accordingly, all of
+our simulation runs of the (discrete-time) replicator dynamic converged to monomorphic
+regret-type populations. The reason why regret types prosper is because they have a substantial
+payoff advantage if paired with radical uncertainty. If radical uncertainty is exogenously
+given as something unavoidable that happens to agents (e.g., whenever they really have no
+indication as to what the situation holds for them), and even if that happens only very
+infrequently (i.e., for rather low $p$), regret types \emph{can} outperform veridical
+preference types, as well as competitive and altruistic types.
+
+\subsection{Solitary decisions}
+\label{sec:solitary-decisions}
+
+\todo[inline]{text in this section and the next is rough and unpolished, only intended to have
+  the basic results recorded, so that we can reshape the article around the basic results}
+
+To see how preference types behave in evolutionary competition based on solitary decision
+problems, we approximated, much in the spirit of meta-games, average accumulated payoffs
+obtained in randomly generated solitary decision problems. For our purposes, a decision problem
+$\tuple{\States, \Acts, \Utils}$ consists of a set of world states $\States$, a set of acts
+$\Acts$, and a utility function $\Utils \mycolon \States \times \Acts \rightarrow
+\mathbb{R}$.
+We generated arbitrary decision problems by selecting numbers of states and acts
+$n_\state, n_\act \in \set{2, \dots, 10}$ and then filling the utility table, so to speak, by
+independently picking a number $\Utils(\state, \act) \in \set{0, 10}$ uniformly at random, just
+as we did before with symmetric games. Unlike with two-player games, we need to also sample the
+actual state of the world, which we selected uniformly at random from the available states in
+the current decision problem. Player types, consisting of epistemic types $\bar{\mu}$ and
+$\Delta(\States)$ and preference types $\tau^{reg}$ and $\tau^{\pi}$, give rise to behavior in
+the same way as before. (It is obviously not possible to carry altruistic or competitive
+preference types over to solitary decision making.) As before, we recorded the behavioral
+decisions for each of the four relevant player types in each sampled decision problem, and
+determined the actual payoff obtained, given the actual state. Average payoff over 100,000 decision
+problems are given in Table~\ref{tab:SolitaryDecisions}.
+
+\begin{table}
+  \centering
+  \begin{tabular}{cccc}
+    \toprule
+   $\tuple{\tau^{reg}, \Delta(A)}$ 
+ & $\tuple{\tau^{\pi}, \Delta(A)}$ 
+ & $\tuple{\tau^{reg}, \bar{\mu}}$ 
+ & $\tuple{\tau^{\pi}, \bar{\mu}}$ 
+ \\ \midrule
+    6.318 & 6.237 & 6.661 & 6.661 \\ \bottomrule
+  \end{tabular}
+  \caption{Average payoffs over 100,000 simulated solitary decision problems}
+  \label{tab:SolitaryDecisions}
+\end{table}
+
+Facts~\ref{fact:maxEU-minReg} and \ref{fact:equivalence2x2} still apply:
+$\tuple{\tau^{reg}, \bar{\mu}}$ and $\tuple{\tau^{\pi}, \bar{\mu}}$ are behaviorally equivalent
+in general, and $\tuple{\tau^{reg}, \Delta(A)}$ is behaviorally equivalent to the former two in
+decision problems with 2 states and 2 acts. \todo{show this?} We see this in part in the
+results in Table~\ref{tab:SolitaryDecisions} in that the averages for $\tuple{\tau^{reg},
+  \bar{\mu}}$ and $\tuple{\tau^{\pi}, \bar{\mu}}$ are identical. But since we included decision
+problems with more acts and more states as well, the averages for regret minimizers
+$\tuple{\tau^{reg}, \Delta(A)}$ are not identical. They are, in fact, lower, but not as low as
+those of the minimax choosers.
+
+What that means is that basically every relevant result about game situations is also borne out
+when reasoning about solitary decisions. Evolutionary selection based on objective fitness will
+not select against regret-based subjective preferences, as these are indistinguishable from
+veridical preferences when paired with probabilistic beliefs. But when paired with
+non-probabilistic belief types, regret-based preferences actually outperform veridical
+preferences. Consequently, if there is a chance, however small, that agents must fall back onto
+non-probabilistic beliefs, evolution will actually positively select for non-veridical
+regret-based preferences.
+
+\subsection{Arbitrary probabilistic beliefs}
+\label{sec:arbitr-prob-beli}
+
+So far, we have assumed that epistemic types $\bar{\mu}$ hold an unbiased, flat belief. It is
+worthwhile considering what happens when this assumption is relaxed and we allow agents with
+probabilistic beliefs to make use of the full spectrum of probabilistic beliefs. It should be
+clear that quality of beliefs directly impacts prospects of successful decision-making: if a
+decision maker knows the actual state, or can put a high level of credence on the actual state,
+accumulated fitness can be expected to be high. We see this, unsurprisingly, in numerical
+simulations. We looked at the average payoff accumulated in 100,000 decision problems sampled
+as before, except that for belief types with probabilistic beliefs we sampled a random
+probabilistic belief $p$ (from an unbiased Dirichlet distribution) and chose the actual world
+state with probability weights $p$. This effectively implements a bias for beliefs of the
+decision maker that tend to put more weight on the actual state (although the procedure does
+admittedly perverse the natural chicken-and-egg logic in this case that the actual world state
+should come first and beliefs be a function of it). As a result, the average payoffs of types
+$\tuple{\tau^{reg}, \bar{\mu}}$ and $\tuple{\tau^{\pi}, \bar{\mu}}$ are still the exact same
+(because we compare what agents with different preference types would do under the same
+beliefs; we are not interested in statistical fluctuations given one type better beliefs by
+pure happenstance), but with $7.125$ notably higher than before. In effect, better
+probabilistic beliefs lead to better decisions. If agents can learn, reason and extrapolate to
+form better probabilistic beliefs, that will help them whenever they take their beliefs into
+account.
+
+But this is orthogonal to the arguments in this paper, where the focus is on possibilities for
+the evolution of non-veridical preferences. We know from Fact~\ref{fact:maxEU-minReg} that
+regret types and veridical preference types, when paired with probabilistic belief types that
+maximize/minimize expectations, are behaviorally equivalent, \emph{no matter what they belief},
+as long as they belief the same. So, if learning, insight and statistical knowledge of a
+recurrent situation \emph{can} be brought to bear, this will not make evolution select against
+regret-based preferences. If, on the other hand, agents have no basis for probabilistic
+beliefs, then we have shown that there are general and basic circumstances in which
+regret-based preferences can actually be selected, despite their non-veridicality.
+
+\section{Discussion}
+
+\begin{itemize}
+\item what we achieved
+\item what could be done next
+\end{itemize}
+
+\appendix
+
+\section{Proofs}
+
+The proof of Proposition 1 relies on a partition of $\mathcal{G}$,
+and on some lemmas. For brevity, let us denote the regret minimizer
+by RM and the maximinimizer by MM. Since the proof is very long and
+all the other cases are similar and easier to prove, we focus here
+on the case of RM against MM players: we prove that RM is evolutionarily
+stable against MM, but MM is not evolutionarily stable against RM. By $EU_{\mathcal{G}}(x,y)$ we denote the expected \textit{objective} utility (or payoff), in terms
+of evolutionary fitness, of player type $x$ against player type $y$
+with respect to the class of fitness games $\mathcal{G}$.
+
+\medskip{}
+
+\textbf{Proof of Proposition 1.} By definition of evolutionary stability, we have to
+show that in the class $\mathcal{G}$ of symmetric $2\times2$ games generated by i.i.d. sampling
+from a finite or compact and convex set of values, it holds:
+\begin{itemize}
+\item[(i)] $EU_{\mathcal{G}}(RM,RM)>EU_{\mathcal{G}}(MM,RM);$
+\item[(ii)] $EU_{\mathcal{G}}(MM,MM)<EU_{\mathcal{G}}(RM,MM).$
+\end{itemize}
+
+\noindent To show
+the result we will use the following partition of $\mathcal{G}$.
+\begin{enumerate}
+\item Coordination games $\mathcal{G}^{C}$: $a>c$ and $d>b$;
+\item Anti-coordination games $\mathcal{G}^{A}$: $a<c$ and $d<b$;
+\item Strong dominance games $\mathcal{G}^{S}$: aut $(a>c$ and $b>d)$
+aut $(a<c$ and $b<d)$;
+\item Weak dominance games $\mathcal{G}^{W}$: aut $a=c$ aut $b=d$;
+\item Indifferent games $\mathcal{G}^{I}$: $a=c$ and $b=d$.
+\end{enumerate}
+Before proving the lemmas, it is convenient to fix some notation.
+We denote by $G^{C}$ a coordination game in $\mathcal{G}^{C}$ with
+payoffs $a^{G^{C}}$, $b^{G^{C}}$, $c^{G^{C}}$, and $d^{G^{C}}$;
+similarly, for $G^{A}$, $G^{S}$, $G^{W}$, and $G^{I}$. Let us
+call $I_{G^{C}}^{RM}$ the event that a RM player plays action $I$
+in the game $G^{C}$; and similarly for action $II$, for player MM,
+and for games $G^{A}$, $G^{S}$, $G^{W}$ and $G^{I}$. Moreover,
+let us recall the definition of evolutionarily stable strategy and
+neutrally stable strategy.
+
+\medskip{}
+
+\begin{definition}[ESS-NSS]
+A strategy $s^{\$}$ is \emph{evolutionarily stable
+(ESS)} if for any other strategy $s$:
+\begin{enumerate}
+\item $\pi(s^{\$},s^{\$})>\pi(s,s^{\$})$, or
+\item $\pi(s^{\$},s^{\$})=\pi(s,s^{\$})$ and $\pi(s^{\$},s)>\pi(s,s)$.
+\end{enumerate}
+\noindent A strategy $s^{\$}$ is \emph{neutrally stable (NSS)} if
+for any other strategy $s$:
+\begin{enumerate}
+\item $\pi(s^{\$},s^{\$})>\pi(s,s^{\$})$, or
+\item $\pi(s^{\$},s^{\$})=\pi(s,s^{\$})$ and $\pi(s^{\$},s)\geq\pi(s,s)$.
+\end{enumerate}
+\end{definition}
+
+\medskip{}
+
+\begin{lemma}
+RM and MM perform equally well in $\mathcal{G}^{S}$
+and in $\mathcal{G}^{I}$. 
+\end{lemma}
+
+\begin{proof}
+By definition of regret minimization and maximin it
+is easy to check that whenever in a game there is a strongly dominant
+action $a^{\$}$, then $a^{\$}$ is both the maximin action and the
+regret minimizing action. Then, for all the games in $\mathcal{G}^{S}$,
+a RM chooses action $a$ if and only if MM chooses action $a$. Consequently,
+RM and MM always perform equally (well) in $\mathcal{G}^{S}$. In
+the case of $\mathcal{G}^{I}$ it is trivial to see that all the players
+perform equally.
+\end{proof}
+
+\medskip{}
+
+\begin{lemma}
+In $\mathcal{G}^{W}$ RM is evolutionarily stable
+against MM, but MM is not evolutionarily stable against RM.
+\end{lemma}
+
+\begin{proof}
+Assume without loss of generality that $b=d$. We have
+two cases then: (i) $c<b=d$; (ii) $c>b=d$. In the first case it
+is easy to see that RM and MM perform equally well. Indeed, given
+(i) both MM and RM choose action $I$ if $a>c$, and action $II$
+if $c>a$. If case (ii) holds instead, we have that RM plays $I$
+if $a>c$ and $II$ if $c>a$ as before, but MM plays $(\frac{1}{2}I;\frac{1}{2}II)$,
+since both $I$ and $II$ maximize the minimal payoff. Consider now
+a population of RM and MM playing games from the class $\mathcal{G}^{W}$.
+Whenever (i) is the case both RM and MM perform equally. Suppose that
+(ii) is the case and that $a>c$, without loss of generality. Then,
+a RM population is evolutionarily stable against MM by condition 1
+of ESS, since $a>\frac{1}{2}a+\frac{1}{2}c$, whereas a MM population
+is not evolutionarily stable against RM, because clearly $\frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d<\frac{1}{2}a+\frac{1}{2}b$.
+Hence, we have that in general $EU_{\mathcal{G}^{W}}(RM,RM)>EU_{\mathcal{G}^{W}}(MM,RM),\mbox{ and }EU_{\mathcal{G}^{W}}(MM,MM)<EU_{\mathcal{G}^{W}}(RM,MM)$.
+\end{proof}
+
+\medskip{}
+
+Since it is not difficult to see that both RM and MM are evolutionarily
+stable in $\mathcal{G}^{C}$, and that both RM and MM are not evolutionarily
+stable in $\mathcal{G}^{A}$ against each other, the main part of
+the proof will be to show that RM is the only evolutionarily stable
+player in the class $\mathcal{G}^{C}\cup\mathcal{G^{A}}$, that is:
+\begin{itemize}
+\item[(i')] $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,RM)>EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,RM),$
+\item[(ii')] $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,MM)<EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,MM).$
+\end{itemize}
+
+\noindent This part needs some more lemmas to be proven, but firstly we introduce
+the following bijective function $\phi$ between coordination and
+anti-coordination games.
+
+\medskip{}
+
+\begin{definition}[$\phi$]
+$\phi:\mathcal{G}^{C}\rightarrow\mathcal{G^{A}}$,
+such that $\phi(a,b,c,d)=(c,d,a,b)$, is a bijection that for each
+coordination game $G^{C}\in\mathcal{G}^{C}$ with payoffs $(a^{G^{C}},b^{G^{C}},c^{G^{C}},d^{G^{C}})$
+gives the anti-coordination game $G^{A}\in\mathcal{G}^{A}$ with payoffs
+$(a^{G^{A}},b^{G^{A}},c^{G^{A}},d^{G^{A}})=(c^{G^{C}},d^{G^{C}},a^{G^{C}},b^{G^{C}})$.
+\end{definition}
+
+\medskip{}
+
+\begin{lemma}
+Let $P(E)$ be the probability of event $E$, then
+it holds that:
+\begin{itemize}
+\item $P(I_{G^{C}}^{RM})=P(II_{\phi(G^{C})}^{RM})$, and $P(II_{G^{C}}^{RM})=P(I_{\phi(G^{C})}^{RM})$;
+\item $P(I_{G^{C}}^{MM})=P(II_{\phi(G^{C})}^{MM})$, and $P(II_{G^{C}}^{MM})=P(I_{\phi(G^{C})}^{MM})$.
+\end{itemize}
+\end{lemma}
+
+\begin{proof}
+It is easy to check that if $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$,
+a RM player plays action $I$ in $G^{C}$; that if $b^{G^{C}}-d^{G^{C}}<c^{G^{C}}-a^{G^{C}}$,
+RM plays $II$; and that if $b^{G^{C}}-d^{G^{C}}=c^{G^{C}}-a^{G^{C}}$,
+a RM player is indifferent between $I$ and $II$ in $G^{C}$, and
+we assume that randomizes with $(\frac{1}{2}I;\frac{1}{2}II)$. Similarly,
+if $a^{G^{A}}-c^{G^{A}}>d^{G^{A}}-b^{G^{A}}$, a RM player plays action
+$I$ in $G^{A}$; if $a^{G^{A}}-c^{G^{A}}<d^{G^{A}}-b^{G^{A}}$, RM
+plays $II$; and if $a^{G^{A}}-c^{G^{A}}=d^{G^{A}}-b^{G^{A}}$, a
+RM player is indifferent between $I$ and $II$ in $G^{A}$, and randomizes
+with $(\frac{1}{2}I;\frac{1}{2}II)$. Consequently, if $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$,
+then $P(I_{G^{C}}^{RM})=1$, and by definition of $\phi$ we have
+$P(II_{\phi(G^{C})}^{RM})=1$. Likewise, if $b^{G^{C}}-d^{G^{C}}<c^{G^{C}}-a^{G^{C}}$,
+then $P(II_{G^{C}}^{RM})=1=P(I_{\phi(G^{C})}^{RM})$; and if $b^{G^{C}}-d^{G^{C}}=c^{G^{C}}-a^{G^{C}}$,
+then $P(I_{G^{C}}^{RM})=P(II_{G^{C}}^{RM})=\frac{1}{2}=P(II_{\phi(G^{C})}^{RM})=P(I_{\phi(G^{C})}^{RM})$. \\
+In the same way, in coordination games we have that if $b^{G^{C}}>c^{G^{C}}$,
+a MM player plays $I$; if $c^{G^{C}}>b^{G^{C}}$, a MM player plays
+$II$; and if $b^{G^{C}}=c^{G^{C}}$, MM is indifferent between $I$
+and $II$, and plays $(\frac{1}{2}I;\frac{1}{2}II)$. In anti-coordination
+games instead, if $a^{G^{A}}>d^{G^{A}}$, MM plays $I$; if $a^{G^{A}}<d^{G^{A}}$,
+MM plays $II$; if $a^{G^{A}}=d^{G^{A}}$, MM plays $(\frac{1}{2}I;\frac{1}{2}II)$.
+By definition of $\phi$: $P(I_{G^{C}}^{MM})=1=P(II_{\phi(G^{C})}^{MM})$
+if $b^{G^{C}}>c^{G^{C}}$; $P(II_{G^{C}}^{MM})=1=P(I_{\phi(G^{C})}^{MM})$
+if $c^{G^{C}}>b^{G^{C}}$; and $P(I_{G^{C}}^{MM})=P(II_{G^{C}}^{MM})=\frac{1}{2}=P(II_{\phi(G^{C})}^{MM})=P(I_{\phi(G^{C})}^{MM})$
+if $b^{G^{C}}=c^{G^{C}}$.
+\end{proof}
+
+\medskip{}
+
+\begin{lemma}
+$P(\phi(G^{C}))=P(G^{C})$.
+\end{lemma}
+
+\begin{proof}
+By definition, each game $G^{C}\equiv(a^{G^{C}},b^{G^{C}},c^{G^{C}},d^{G^{C}})$
+is such that $a^{G^{C}}>c^{G^{C}}$ and $d^{G^{C}}>b^{G^{C}}$, and
+each game $G^{A}\equiv(a^{G^{A}},b^{G^{A}},c^{G^{A}},d^{G^{A}})$
+is such that $a^{G^{A}}<c^{G^{A}}$ and $d^{G^{A}}>b^{G^{A}}$. Since
+$a,b,c,d$ come from i.i.d. sampling, by simple renaming of variables
+it is clear that the probability of $(a^{G^{C}},b^{G^{C}},c^{G^{C}},d^{G^{C}})$
+is equal to the probability of $(c^{G^{C}},d^{G^{C}},a^{G^{C}},b^{G^{C}})$.
+Hence, $P(\phi(G^{C}))=P(G^{C})$.
+\end{proof}
+
+\medskip{}
+
+\begin{lemma}
+It holds that:
+\begin{itemize}
+\item $a^{G^{C}}>d^{G^{C}}\rightarrow(I_{G^{C}}^{MM}\subset I_{G^{C}}^{RM})$;
+\item $a^{G^{C}}<d^{G^{C}}\rightarrow(II_{G^{C}}^{MM}\subset II_{G^{C}}^{RM})$;
+\item $a^{G^{C}}=d^{G^{C}}\rightarrow I_{G^{C}}^{MM}=I_{G^{C}}^{RM}$.
+\end{itemize}
+\end{lemma}
+
+\begin{proof}
+If $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$, RM plays
+$I$, and if $b^{G^{C}}-d^{G^{C}}=c^{G^{C}}-a^{G^{C}}$, RM plays
+$(\frac{1}{2}I;\frac{1}{2}II)$, whereas if $b^{G^{C}}>c^{G^{C}}$,
+MM plays $I$, and if $b^{G^{C}}=c^{G^{C}}$, MM plays $(\frac{1}{2}I;\frac{1}{2}II)$.
+Then, $I_{G^{C}}^{RM}$ implies that $b^{G^{C}}-d^{G^{C}}\geq c^{G^{C}}-a^{G^{C}}$,
+and $I_{G^{C}}^{MM}$ implies that $b^{G^{C}}\geq c^{G^{C}}$. Moreover,
+on the assumption that $a^{G^{C}}>d^{G^{C}}$, it is easy to check
+that $b^{G^{C}}\geq c^{G^{C}}$ implies $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$.
+Hence, in any $G^{C}$ with $a^{G^{C}}>d^{G^{C}}$ it holds that $I_{G^{C}}^{MM}\mbox{ implies }I_{G^{C}}^{RM}$,
+i.e., $a^{G^{C}}>d^{G^{C}}\rightarrow(I_{G^{C}}^{MM}\subseteq I_{G^{C}}^{RM})$.
+Instead, it is possible that $a^{G^{C}}>d^{G^{C}}$, $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$
+and $b^{G^{C}}<c^{G^{C}}$ hold simultaneously, so that $I_{G^{C}}^{MM}\nsupseteq I_{G^{C}}^{RM}$.
+Consequently: $a^{G^{C}}>d^{G^{C}}\rightarrow(I_{G^{C}}^{MM}\subset I_{G^{C}}^{RM})$.
+By symmetric argument it can be shown that $a^{G^{C}}<d^{G^{C}}\rightarrow(II_{G^{C}}^{MM}\subset II_{G^{C}}^{RM})$
+too. \\
+Finally, when $a^{G^{C}}=d^{G^{C}}$ it holds that: $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$
+iff $b^{G^{C}}>c^{G^{C}}$; $b^{G^{C}}-d^{G^{C}}<c^{G^{C}}-a^{G^{C}}$
+iff $b^{G^{C}}<c^{G^{C}}$; and $b^{G^{C}}-d^{G^{C}}=c^{G^{C}}-a^{G^{C}}$
+iff $b^{G^{C}}=c^{G^{C}}$. Hence, $a^{G^{C}}=d^{G^{C}}\rightarrow I_{G^{C}}^{MM}=I_{G^{C}}^{RM}$.
+\end{proof}
+
+\medskip{}
+
+We are now ready to prove that: 
+\begin{itemize}
+\item[(i')] $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,RM)>EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,RM);$
+\item[(ii')] $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,MM)<EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,MM).$
+\end{itemize}
+We can rewrite $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,RM)>EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,RM)$
+more explicitly as:
+
+\medskip{}
+
+\noindent $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{MM})\cdot d^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{MM})\cdot d^{A}]<\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{RM})\cdot d^{C}+P(I_{G^{C}}^{MM}\cap II_{G^{C}}^{RM})\cdot c^{C}+P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot b^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{MM}\cap I_{G^{A}}^{RM})\cdot a^{A}+P(II_{G^{A}}^{MM}\cap II_{G^{A}}^{RM})\cdot d^{A}+P(I_{G^{A}}^{MM}\cap II_{G^{A}}^{RM})\cdot c^{A}+P(II_{G^{A}}^{MM}\cap I_{G^{A}}^{RM})\cdot b^{A}]$
+
+\medskip{}
+
+\noindent Then, the next derivation follows. By Lemma 5 and 6, we can express
+everything in terms of $G^{C}$ only: 
+\begin{itemize}
+\item $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM})\cdot a^{A}+P(II_{G^{A}}^{RM})\cdot d^{A}]>\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot d^{A}+P(I_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot c^{A}+P(II_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot b^{A}]$
+\item $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}+P(II_{G^{C}}^{RM})\cdot c^{C}+P(I{}_{G^{C}}^{RM})\cdot b^{C}]>\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}]$
+\item $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}+P(II_{G^{C}}^{RM})\cdot c^{C}+P(I{}_{G^{C}}^{RM})\cdot b^{C}]>\sum_{G^{C}}P(G^{C})[a^{C}\cdot(P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))+b^{C}\cdot(P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))+c^{C}\cdot(P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))+d^{C}\cdot(P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]$
+\end{itemize}
+Now let us split into $a>d$ and $a<d$, and consider $a>d$ first.
+Notice that, by Lemma 7, the case $a=d$ is irrelevant in order to
+discriminate between RM and MM. If $a>d$, by Lemma 7 we can eliminate
+the cases where RM plays $II$ and MM plays $I$:
+\begin{itemize}
+\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}+P(II_{G^{C}}^{RM})\cdot c^{C}+P(I{}_{G^{C}}^{RM})\cdot b^{C}]>\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[a^{C}\cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+b^{C}\cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+c^{C}\cdot(P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))+d^{C}\cdot(P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]$
+\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}+P(II_{G^{C}}^{RM})\cdot c^{C}+P(I{}_{G^{C}}^{RM})\cdot b^{C}-a^{C}\cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})-b^{C}\cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})-c^{C}\cdot(P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))-d^{C}\cdot(P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]>0$
+\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[a^{C}\cdot(P(I_{G^{C}}^{RM})-P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))+b^{C}\cdot(P(I{}_{G^{C}}^{RM})-P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))+c^{C}\cdot(P(II_{G^{C}}^{RM})-P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})-P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))+d^{C}\cdot(P(II_{G^{C}}^{RM})-P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})-P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]>0$
+\end{itemize}
+By Lemma 7, it is easy to check that $P(I_{G^{C}}^{RM})-P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})=P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})$
+and $P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})=P(II_{G^{C}}^{RM})$.
+Consequently, we have:
+\begin{itemize}
+\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[a^{C}\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+b^{C}\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})-c^{C}\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})-d^{C}\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})]>0$
+\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[a^{G^{C}}-c^{G^{C}}]>\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[d^{G^{C}}-b^{G^{C}}]$.
+\end{itemize}
+\medskip{}
+
+\noindent We know that $I_{G^{C}}^{RM}$ implies that $b^{G^{C}}-d^{G^{C}}\geq c^{G^{C}}-a^{G^{C}}$,
+and $II_{G^{C}}^{MM}$ implies that $b^{G^{C}}\leq c^{G^{C}}$. From
+$b^{G^{C}}-d^{G^{C}}\geq c^{G^{C}}-a^{G^{C}}$, it is easy to see
+that $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[a^{G^{C}}-c^{G^{C}}]\geq\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[d^{G^{C}}-b^{G^{C}}]$
+holds. When the event $I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}$ obtains
+on the assumption that $a^{G^{C}}>d^{G^{C}}$, there are only three
+possible payoff orderings: $a>c\geq d>b$, $a>d>c>b$, and $a>d>c=b$.
+If games are randomly sampled from a finite set with i.i.d. values
+for $a,b,c$ and $d$, then $a>d>c=b$ occurs with positive probability,
+and the last formula of the derivation holds with strict inequality
+too. Hence, RM is evolutionarily stable when the value set for $a,b,c,d$
+is finite. \\
+If i.i.d. values are sampled from a compact and convex set instead,
+it is again easy to see that $\forall a,d,c\ \exists\epsilon$ such
+that $\forall b\in(d,d+\epsilon)$ the above formula holds with strict
+inequality. We can simply take $\epsilon\equiv\frac{a-c}{2}$, and
+the interval $(d,d+\epsilon)$ always has positive probability. Hence,
+RM is evolutionarily stable when the value set for $a,b,c,d$ is a
+compact and convex set too. \\
+Symmetrically, from $a<d$ in the above derivation we get:
+
+\medskip{}
+
+\noindent $\sum_{G_{a<d}^{C}}P(G_{a<d}^{C})\cdot P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot[d^{C}-b^{C}]>\sum_{G_{a<d}^{C}}P(G_{a<d}^{C})\cdot P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot[a^{C}-c^{C}]$
+
+\medskip{}
+
+\noindent and the same argument follows.
+
+\medskip{}
+
+The second half of the result is that MM is not evolutionarily stable
+against RM in $\mathcal{G}^{C}\cup\mathcal{G^{A}}$: $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,MM)<EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,MM)$.
+As before, we write it more explicitly as:
+
+\medskip{}
+
+\noindent $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{MM})\cdot d^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{MM})\cdot d^{A}]<\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{RM})\cdot d^{C}+P(I_{G^{C}}^{MM}\cap II_{G^{C}}^{RM})\cdot c^{C}+P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot b^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{MM}\cap I_{G^{A}}^{RM})\cdot a^{A}+P(II_{G^{A}}^{MM}\cap II_{G^{A}}^{RM})\cdot d^{A}+P(I_{G^{A}}^{MM}\cap II_{G^{A}}^{RM})\cdot c^{A}+P(II_{G^{A}}^{MM}\cap I_{G^{A}}^{RM})\cdot b^{A}]$.
+\medskip{}
+
+\noindent Similarly to the above derivation, in the end we get:
+
+\medskip{}
+
+\noindent $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot[c^{G^{C}}-a^{G^{C}}]<\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot[b^{G^{C}}-d^{G^{C}}]$.
+
+\medskip{}
+
+\noindent Finally, by the same argument as before we can conclude that MM is
+not evolutionarily stable against RM both when the value set for $a,b,c,d$
+is finite, and when the value set for $a,b,c,d$ is a compact and
+convex set. This concludes the proof. $\dashv$
+
+\printbibliography[heading=bibintoc]
+
+\newpage
+
+\section{Snippets}
+
+[More precisely, from the meta-game perspective many possible subjective
+transformations of the objective utility are eliminated by evolution, but we find some
+evolutionarily stable subjective utility maximizers whose utility does not coincide with the
+objective evolutionary utility. This result leaves some room in between the two extrema: we can
+understand rationality in a normative way, given by evolution, without having to discard all
+the possible subjective utility representations as irrational. CHANGE PLACE OF THIS MAYBE]
+
+\subsection{Version 2}
+
+The importance of aiming at a richer evolutionary game theory has been recently emphasized by many works in theoretical biology and behavioral ecology [Fawcett\&al., McNamara, etc.].
+The biological argument to embrace this goal is related to the criticisms towards the so-called behavioral gambit [Fawcett\&al.].
+The behavioral gambit denotes the standard approach in evolutionary game theory that puts the focus of attention on the expressed behavior, and neglects the underlying mechanisms that generate that behavior.
+From this point of view, the benefit and the reliability coming from the use of evolutionary game theory for biological purposes is also under attack.
+There are good reasons to claim that focusing on the general psychological mechanisms instead of on behavior itself as the phenotype under evolutionary selection can be more faithful and insightful for natural biology and ecology [Fawcett\&al.].
+Standard evolutionary game theory normally models the agents as playing a single fixed game, and as genetically predetermined to play fixed strategies, that consequently are the only target of natural selection in those frameworks.
+Standard models of evolutionary game theory cannot take charge of this shift of perspective until they will keep modelling a single game at a time, and until they will keep focusing on actions considered genetically encoded and fixed.
+''Instead we should expect animals to have evolved a set of psychological mechanisms which enable them to perform well on average across a range of different circumstances''[Fawcett\&al.].
+
+Attempts to overcome the behavioral gambit have recently been developed in economic literature too.
+In the last twenty years economists have been using evolutionary game-theoretical models to study evolution of preferences [cite], instead of evolution of behavior only.
+This approach is called indirect evolutionary approach, because players' behavior and actions stem from their subjective preferences, and it is aimed at investigating what subjective preferences are evolutionarily better off and robust with respect to natural selection.
+This shift from a direct evolutionary approach about observed actions and behavior to an indirect evolutionary approach takes only partly into account the behavioral gambit criticized by biologists and ecologists.
+The reason is that the models of evolution of preferences usually consider only one game at a time.
+This means that there is a single type of interaction that is supposed to drive the whole evolution of preferences: preferences are selected on the basis of one possible interaction only.
+Clearly, this approach does not take into consideration the variety of possible circumstances that animals are supposed to face during their lifetime.
+
+The meta-game model we propose pays heed to both components of the behavioral gambit.
+We retain the indirect evolutionary approach, but our agents in the population play over a class of possible games $\mathcal{G}$.
+In this way we explicitly model a range of different circumstances, as wished by theoretical biologists.
+Consequently, each agent in the population does not represent either a simple behavior or a subjective preference, but a more general player type that associates a subjective preference for each game in the class $\mathcal{G}$.
+The player type is supposed to encode the general psychological mechanisms that generate the behavior for any possible interaction in $\mathcal{G}$.
+These general psychological mechanisms then become the target of evolution, and they are selected based on the average fitness over a class of different interactions.
+
+In particular, in the following we mainly deal with two types of agents: players whose subjective preference coincides with the evolutionary fitness, and players whose subjective preference is defined in terms of regret.
+It turns out that psychological mechanisms and subjective conceptualizations based on regret can outperform more veridical conceptualizations coinciding with the evolutionary fitness.
+This is just an example of the kind of insights and results that we can gain by adopting a meta-game perspective and by shifting the focus of our attention to psychological mechanisms and subjective conceptualizations as the phenotype under selection.
+
+-maybe to add: difference with learning. Fawcett\&al. talk more about differences in learning, whereas we model differences in subjective conceptualizations.
+
+[A pivotal element of economics and decision theory is the definition of rationality as
+maximization of subjective preferences.]
+
+\begin{itemize}
+\item We present an approach to studying evolutionary selection of \emph{choice principles},
+  i.e., ways of choosing consistently across several games. In other words, we would like to
+  look at the problem of ``rational choice'' from an evolutionary point of view: what choice
+  principles would be promoted, which demoted in evolutionary competition amongst each other?
+
+\item This depends on the environment; it depends on what choice situations occur how
+  frequently. Maybe some choice principle is better in some situations, while another one is
+  better in others.
+
+\item We argue that this ``meta-evolutionary'' approach could eventually help explain attested
+  deviations of human decision making from the classical ideal: choice behavior evolved to be
+  an ``ecologically rational'', near-optimal adaptation to the environment
+  \citep{Anderson1990:The-Adaptive-Ch,Anderson1991:Is-human-cognit,GigerenzerGoldstein1996:Reasoning-the-F,ChaterOaksford2000:The-Rational-An}. This
+  is inline with recent aspirations to provide an evolutionary rationale for decision making
+  processes
+  \citep[e.g.][]{HammersteinStevens2012:Six-Reasons-for,FawcettHamblin2013:Exposing-the-be}. Here,
+  we seek to contribute to the formal machinery, an extension of evolutionary game theory, that
+  allows to capture statistical properties of the environment
+  \citep[cf.][]{McNamara2013:Towards-a-Riche}.
+\end{itemize}
+
+\subsection{The environment: meta-games}
+
+\begin{itemize}
+\item imagine huge, virtually infinite population of agents, each carrying a choice principle
+\item agents play a randomly sampled game against a randomly sampled opponent
+\item fitness is based on the average payoff of choice principle A against choice principle B,
+  taken over arbitrary games $g$ and weighted their occurrence probability $P(g)$:
+  $\int_g P(g) \times U_g(\text{CP-A}, \text{CP-B}) \text{d}g$
+\item the occurrence probability of games $g$ is the ``environment'' and, possibly, impossible to
+  derive theoretically, or to measure empirically
+\item here, use a relatively neutral approach instead that is practicable:
+  \begin{itemize}
+  \item games are individuated by their payoff matrices (no framing effects or similar)
+  \item each entry in a payoff matrix is an i.~i.~d.~random variable
+    \begin{itemize}
+    \item approach still incorporates a bias (e.g., against strategic form representations of
+      sequential games)
+    \end{itemize}
+  \end{itemize}
+\item example: average payoffs from numerical simulation of ($2 \times 2$ symmetric games)
+\item example: average payoffs from numerical simulation of ($n \times n$ symmetric games, with
+  $n$ uniformly random (up to some upper-bound))
+\end{itemize}
 
@@
 \item However, studies on the adaptive value of choice mechanisms have focused, for the most
-  part, of the evolutionary benefit of learning rules
+  part, on the evolutionary benefit of learning rules
   \citep[e.g.][]{ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o}. (\myalert{More references Harley 1981!!!, \dots}). 
@@
 
-\newpage
-
-\section{Rationality \& subjective preference}
-
-The standard use of the word \textit{rationality} in economics and decision theory is to denote
-the maximization of (subjective) expected utility. Since the work by vNM [cite], this stance
-has been justified from the intuitive ''rationality'' of the axioms on the subjective
-preference relation leading to the representability of the decision maker as an expected
-utility maximizer.
-While in the axiomatization by [vNM] the probability of the outcomes is objectively given a priori, Savage54 provides a larger set of axioms that represent the decision maker (DM) with both a subjective utility over outcomes \textit{and} a \textit{subjective} probability over states of the world.
-Savage's axioms constitute the foundation of subjective expected utility (SEU) theory, that is normally assumed to define the rational behavior of economic agents.\\
-
-\begin{definition}[SEU-maximization] Let $S$ be a set of states of the world, $X$ a set of
-  outcomes and $A$ a set of actions. Given a probability measure $P$ on $S$ and a subjective
-  utility function $u:X \rightarrow \mathbb{R} $, an action $a^*: S \rightarrow X $ is
-  SEU-maximizing if $a^* \in \text{argmax}_{a_i \in A} \int_S u(a^*(s))dP(s) $.
-\end{definition}
-
-The subjectivity of preferences plays a very important
-role for the present work. From an agent's standpoint, the amount $x$ of, say, money achieved does not necessarily
-coincide with the amount of subjective utility attained $u(x)$. 
-Historically,  the first to notice and formally argue for this difference
-between objective utility (goods, money, etc.) and subjective utility (preferences) was
-D. Bernoulli with the famous St. Petersburg paradox in 1738. Moreover, Bernoulli introduced the idea that a good representation of
-subjective utility can be carried out in terms of an increasing concave function of objective
-utility. This can be considered the birth of modern decision theory.
-
-Empirically, many violations of Savage's (and vNM's) axioms have been consistently observed in behavioral economics.
-Most of the attention has been focused on the Independence Axiom and the Sure-thing Principle.
-Allais' paradox and Ellsberg's paradox are examples of violations of these two axioms, and they are at the origin of Prospect theory [cite] and ambiguity in decision theory [cite].
-
-The main idea behind Ellesberg's paradox and the literature on ambiguity is that DM treats differently objective and subjective uncertainty.
-If the probability measure on the possible states of the world is not given a priori and not ''known'', then observed preferences leave no room to represent  DM's beliefs via a probability measure on the possible states.
-The most common solution is then to represent DM's beliefs with a set of probability measures instead of a single one.
-
-Prospect theory was introduced by Kahnemann and Tversky in
-their famous paper from 1979. By means of experimental results they noticed that DM apparently acts as a risk averse agent with respect to gains and as a risk loving agent
-with respect to losses. Consequently, they conjectured that the subjective utility is better
-representable by an S-shaped utility function, concave in the positive domain of gains and
-convex in the negative domain of losses.
-
-More recently, other possible definitions of the subjective utility function have been proposed
-and justified from a game theoretical point of view (e.g. Fehr and Schmidt, Charness and Rabin,
-etc.). The central goal of these studies is to explain/describe the empirical behavior in social dilemmas
-(e.g., Prisoner's dilemma, public goods game, etc.). In the same spirit of Prospect theory, by means of different subjective utility
-functions it is possible to describe/match the behavior observed in game theoretical experiments and to
-explain it as rational (in the sense of maximizing the subjective utility).
-With this approach every behavior, no matter how far from the maximization of
-objective utility, can be deemed rational if we can only find a subjective utility that
-justifies that behavior as maximizing the subjective utility. The problem here is that it seems possible to consider rational everything
-that is observed, given the adequate subjective utility function. The notion
-of rationality almost collapses onto the observed behavior.
-
-On the other side, other economists (Alchian, Friedman) seem to link the notion of rational choice
-more tightly to the maximization of objective utility. In their classic works they argue that
-profit maximization is a reasonable assumption for characterizing outcomes in a competitive
-market because only firms behaving in a manner that is consistent with profit maximization will
-survive in the long run. If the previous accounts of rationality looked more descriptive, this
-definitely tastes more normative. In this sense, a normative notion of rationality would be tightly
-related to (and almost coincide with) the maximization of objective utility, which is supposed
-to drive the evolutionary process. It follows then that being normative in this sense points to an identification of rationality with maximization of objective utility.
-
-It seems that we are stuck between two extrema: a too permissive descriptivism and a too restrictive normativism. On the one hand, if we want to have a
-descriptive notion of rationality, then we can (almost) always define an appropriate
-subjective utility whose maximization matches the observed behavior. On the other hand, if we
-want to have a normative approach to rationality, then it seems we have to appeal to
-evolutionary arguments entailing the understanding of rationality as maximization of objective
-utility.
-
-However, it has been argued that in a good theory of choice and decision making the normative and the descriptive components should not come apart. For example, as Douglas Maclean [cite] writes:
-
-\begin{quote}
-The history of the subject reflects strong reasons why the theory of choice should have this dual character. [...] \\
-A normative theory of choice gains credibility from its predictive and explanatory power, for although empirical success itself may not constitute much of a normative argument, the theory of rational behavior is less likely to be found objectionable if rationality turns out to be widespread.
-[...] But if, on the other hand, the normative theory turns out to be incompatible with the best established behavioral theory, then the verification of the normative theory will depend entirely on the intrinsic plausibility of its axioms, and that appeal must be quite strong, strong enough to make us overcome our charitable reluctance to conclude that our actual behavior is systematically irrational.
-\end{quote}
-
-There is another violation of Savage's axioms that is particularly relevant for the present work: transitivity of preferences.
-The first of Savage's axioms states that the preference relation is a (total) preorder, i.e., reflexive and transitive.
-Moreover, the preorder axiom is often referred to as the rationality axiom [cite], as to suggest that it is somehow the core of rational preferences.
-Violations of transitivity have been observed and studied in experimental literature [citeTversky69,etc], but can also be supported from a normative and theoretical point of view.
-\\
-In what follows, an important focus of our work will be the role of regret in decision making.
-Regret theory predicts the violation of both transitivity and Independence of Irrelevant Alternatives (IIA).
-[CONNECTING TO Fawcett\&al: this is IIA, not independence]
-
-\subsubsection{Regret theory} \label{sec:regreTheory}
-
-Regret theory has been introduced in decision theory by Savage [] and Niherens [], and later developed by Bell [1982], Loomes and Sugden [1982], and Fishburn [1982] independently.
-Lately, Halpern and Pass [cite] show how the use of regret minimization can solve game theoretical puzzles (like the Centipede and the Traveller's dilemma) in a way that is closer to everyday intuition and empirical data.
-In this paper the notion of regret is defined as in [HalPass12]:
-
-\begin{definition}[Pairwise regret] \label{defn:parwreg}
-Given a simultaneous-move game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the regret of player $i$ at profile $(a_i,a_{-i})$ is defined by: $\text{reg}(a_i,a_{-i}):= \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $, where $a_i^\$ \in A_i$ denotes $i$'s best reply to action $a_{-i} $.
-\end{definition}
-
-\begin{definition}[Regret] \label{defn:regret}
-Given a simultaneous-move game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the regret of an action $a_i \in A_i$ is defined by: $\text{reg}(a_i):= \text{max}_{a_{-i}\in A_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $.
-\end{definition}
-
-\begin{definition}[Regret minimization] \label{defn:regmin}
-Given a simultaneous-move game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, an action $a^{r}_i $ is regret minimizing if $a^{r}_i \in \text{min}_{a_i} \text{max}_{a_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $.
-\end{definition}
-
-\begin{example}[Coordination Game]
-  Let us consider the coordination game in Figure \ref{coordgame1}. It is easy to see that
-  $\text{reg}(I)=2$: when the other player chooses action $I$ the regret of $I$ is $0$ since
-  $I$ is a best reply to $I$, and when the other player chooses $II$ the regret of $I$ is $2$
-  since $\pi_i(II,II)-\pi_i(I,II)=2$. With the same reasoning, $\text{reg}(II)=1$. Two regret
-  minimizing players would then choose action $II$, each getting a payoff of $2$. In this case
-  regret minimization selects the Pareto-dominant Nash equilibrium. $ \medsquare $
-
-\begin{figure}
-\begin{center}%
-\begin{tabular}{|c|c|c|}
-\hline 
- & I & II\tabularnewline
-\hline 
-\hline 
-I & 1;1 & 0;0\tabularnewline
-\hline 
-II & 0;0 & 2;2\tabularnewline
-\hline 
-\end{tabular}\end{center}
-
-\protect\caption{A coordination game $G^C$}
-\label{coordgame1}
-\end{figure}
-
-\end{example}
-
-\begin{example}[The Traveller's Dilemma \citep{HalpernPass2012:Iterated-Regret}]
-Let us now consider the Traveller's Dilemma case. The story behind the game goes as
-follows. There are two travellers, Ann and Bob, who lost their luggages. Ann and Bob had
-exactly the same luggage and they had insured the luggages with the same insurance company. The
-insurance policy is that the two travellers have to separately claim a certain amount between
-2\$ and 100\$ for the reimbursement, and if they both claim the same amount then they will be
-reimbursed by that amount. Otherwise, if one of them claims more than the other, then the one
-who claimed the higher amount will get the lower amount minus 2\$, while the one who claimed
-the lower amount will get what (s)he claimed plus 2\$. The game is symmetric, and the payoff
-function for both players is:
-\begin{align*}
-  \pi_i(a_i,a_{-i}) = \begin{cases} a_i \text{ \hspace{1cm} if } a_i = a_{-i} \\ a_i + 2 \text{
-      \hspace{.4cm} if } a_i < a_{-i} \\ a_{-i} -2 \text{ \hspace{.25cm} if } a_{-i} <
-    a_i \end{cases}
-\end{align*}
-By a simple computation we have:  $\forall a_i \in \lbrace 96\$, ..., 100\$ \rbrace \text{, } \text{reg}(a_i)=3 $ and $\forall a_i \in \lbrace 2\$, ..., 95\$ \rbrace \text{, } \text{reg}(a_i)>3$.
-If we now eliminate all the actions that do not minimize regret in the first place and iterate the regret minimization only on the action set $\lbrace 96\$, ..., 100\$ \rbrace$, we get that 97\$ is the action that minimize regret.
-Indeed, $\text{reg}(97)=2$ and $\forall a_i \in \lbrace 96\$, 98\$, 99\$, 100\$ \rbrace \text{, } \text{reg}(a_i)=3 $.
-Hence, one step of regret minimizing reasoning eliminates all the actions smaller than 96\$, and if we iterate the process once more the unique outcome is 97\$.
-Finally, it is worth noticing that the only rationalizable equilibrium of the game corresponds to the outcome $(2,2)$, that is consequently the only Nash equilibrium, the only perfect equilibrium, and the only sequential equilibrium of the game.
-$ \medsquare $
-
-\end{example}
-
-The meta-game perspective that we introduce in this paper can shed more light on the duality of descriptivism and normativism, and opens
-some space in between the two extrema. 
-By keeping the evolutionary approach we want to retain a
-normative perspective on rationality, but our results show that (under certain conditions)
-evolution does not necessarily lead to identifying rationality with maximization of objective
-utility, contrary to the intuition of Alchian [cite] and Friedman [cite].
-
-In the following we mainly deal with two types of agents: players whose subjective utility is defined
-in terms of regret (as in DEFINITION), and players whose utility
-function coincides with the objective utility $\pi_i$.
-
-The justification for this choice is both historical and behavioral. Among
-the possible competitors of utility maximization, regret has always been in a prominent
-position, both from a descriptive and normative viewpoint. Indeed, Bell82 writes:
-\begin{quote}
-  By explicitly incorporating regret, expected utility theory not only becomes a better
-  descriptive predictor but also may become a more convincing guide for prescribing behavior to
-  decision makers.
-\end{quote}
-In the same year, Graham Loomes and Robert Sugden \citet{LoomesSugden1982:Regret-Theory:-} show that a regret-based theory of choice can match
-and explain all the main experimental results of prospect theory, and claim that
-\begin{quote} [...] we shall challenge the idea that the conventional axioms [of decision
-  theory] constitute the only acceptable basis for rational choice under uncertainty. We shall
-  argue that it is no less rational to act in accordance with regret theory, and that
-  conventional expected utility theory therefore represents an unnecessarily restrictive notion
-  of rationality. \hfill \citep{LoomesSugden1982:Regret-Theory:-}
-\end{quote}
-
-\section{The model}
-
-We consider an evolutionary model that is different, for the best of our knowledge, from all the standard models of evolutionary game theory.
-Given a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, a subjective utility over $G$ is a function $\theta: A \rightarrow \mathbb{R} $, where $ A:=\prod_{i\in N}A_{i} $ as usual.
-We denote by $ \Theta:= \mathbb{R}^{|A|} $ the set of all the subjective utilities over $G$.
-The model we introduce here is a multiple game model, that we also call \textit{multi-game} or \textit{meta-game}, where a \textit{class} $\mathcal{G}$ of fitness games is played in a population.
-All the models used in evolutionary game theory that we are aware of always consider a single game at a time.
-Our extension is meant to capture both a more general notion of environment and a more general notion of phenotype.\\
-There are good reasons to claim that focusing on more general psychological mechanisms instead of on behavior itself as the phenotype under evolutionary selection can be more faithful and insightful for natural biology and ecology [Fawcett\&al.].
-In all classical models the agents are represented as playing a single fixed game, and as genetically predetermined to play fixed strategies, that consequently are the only target of natural selection in those frameworks.
-Standard evolutionary game theory cannot take charge of this shift of perspective until it will keep modelling a single game at a time, and until it will keep focusing on observed behavior only.
-''Instead we should expect animals to have evolved a set of psychological mechanisms which enable them to perform well on average across a range of different circumstances''[Fawcett\&al.].
-[maybe add evolution of preferences here]
-
-In this work we take $\mathcal{G}$ to be the class of symmetric $2 \times 2$ games\footnote{Note that this class includes many of the most famous games extensively considered in game theoretical literature, e.g., Prisoner's dilemma, Chicken game, Stag hunt, etc.}.
-First, a game $G$ is selected from the class of fitness games $\mathcal{G}$, and then players in the population are matched to play the game $G$.
-Each player is a function $\tau: \mathcal{G} \rightarrow  \Theta$, and we call $\tau$ a \textit{player type}, or just a \textit{type}\footnote{Notice that the function $\tau$ is well-defined since, for any symmetric $2 \times 2$ game, the codomain $\Theta=\mathbb{R}^{4}$ is the same.}.
-Intuitively, a type can be interpreted as a way of reasoning, a pattern of conceptualization, a thread that relates different subjective utilities across different games.
-We denote by $T$ the class of player types.
-For each game $G \in \mathcal{G}$, the evolutionary fitness is determined by the objective utility (payoff) function $\pi_G$, but the player's action choice depends on the player's subjective utility function $\tau(G)$, given by the player's type $\tau$.
-Notice that, for any symmetric game $G$, the action sets $(A_1, \dots, A_N)$ and the payoff functions $ (\pi_1, \dots, \pi_N)  $ are the same for all $i\in \lbrace 1, \dots N \rbrace$.
-Consequently, we only write $ A^G $ and $ \pi^G $ for the action set and the payoff function of game $G$, respectively.
-Moreover, in symmetric $2 \times 2$ games we have $A=A^G \times A^G$.
-Then, for $x,y \in A^G$ we denote by $\pi^G(x,y)$ the objective payoff of playing action $x$ in response to action $y$.\\
-
-\subsection{Player types}
-
-The set of all possible player types amouts to the set of all possible functions $ \tau: \mathcal{G} \rightarrow  \Theta $, i.e., $T=\mathbb{R}^{4^{\mathbb{R}^{4}}} $ , but for the sake of simplicity we will focus on types that are relevant and meaningful from a decision-theoretic point of view.
-We are mainly interested in two types: the objective type and the regret type.\\
-Given a game $G$ and Definition \ref{defn:parwreg}, it is straightforward to define the \textit{regret preference} $\theta^{reg}$ and the \textit{regret type} $\tau^{reg}$ as follows.
-
-\begin{definition}[Regret preference] \label{defn:regpref}
-
-For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the regret preference $ \theta^{reg}: A \rightarrow \mathbb{R} $ such that $ \theta^{reg}(a_i,a_{-i})=-\text{reg}(a_i,a_{-i}) $.\footnote{More precisely, this is the negative regret, whereas the (positive) regret, as defined in [halpass], would not have the minus sign at the beginning of the formula.
-Here it will be easier to define the regret in terms of negative regret.}
-
-\end{definition}
-
-\begin{definition}[Regret type] \label{defn:regtype}
-
-Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call regret type the function $\tau^{reg}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{reg}(G)= \theta^{reg}$.
-
-\end{definition}
-
-\noindent Similarly, let us define the \textit{objective preference} $\theta^{\pi}$ and the \textit{objective type} $ \tau^{\pi} $, that we also call $\pi$\textit{-type}, as follows.
-
-\begin{definition}[Objective preference] \label{defn:objpref}
-
-For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the objective preference $ \theta^{\pi}: A \rightarrow \mathbb{R} $ such that $ \theta^{\pi}(a_i,a_{-i})=\pi(a_i,a_{-i}) $.
-
-\end{definition}
-
-\begin{definition}[Objective type] \label{defn:objtype}
-
-Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call objective type, or $\pi$-type, the function $\tau^{\pi}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{\pi}(G)= \theta^{\pi}$.
-
-\end{definition}
-
-\noindent In other words, we consider two prominent player types: a type who has a veridical subjective utility that perfectly matches the objective utility (i.e., the evolutionary fitness); and a type who has a non-veridical regret-based subjective utility.
-
-\iffalse
-(maybe we want to introduce altruistic and competitive only later) Other types of player have been studied in the literature. A famous example is the \textit{altruistic type}.
-
-\begin{definition}[Altruistic preference] \label{defn:altpref}
-
-For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{alt}: A \rightarrow \mathbb{R} $ such that $ \theta^{alt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \sum_{j \neq i} \pi(a_{j},a_{-j})$.\footnote{A more general formulation [see: REFERENCES] would be to define an $ \alpha$-altruistic type, for $\alpha \in [0,1]$, with subjective utility $ \theta^{\alpha lt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \alpha \sum_{j \neq i} \pi(a_{j},a_{-j})$.
-Since we are not interested in the evolution of degrees of altruism here, we simply fix $ \alpha = 1 $.}
-
-\end{definition}
-
-\begin{definition}[Altruistic type] \label{defn:alttype}
-
-Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{alt}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{alt}(G)= \theta^{alt}$.
-
-\end{definition}
-
-\noindent As opposite to the altruistic type, it is possible to define a \textit{competitive type} as follows.
-
-\begin{definition}[Competitive preference] \label{defn:compref}
-
-For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{com}: A \rightarrow \mathbb{R} $ such that $ \theta^{com}(a_i,a_{-i})=\pi(a_i,a_{-i}) - \sum_{j \neq i} \pi(a_{j},a_{-j})$.
-
-\end{definition}
-
-\begin{definition}[Competitive type] \label{defn:comtype}
-
-Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{com}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{com}(G)= \theta^{com}$.
-
-\end{definition}
-
-\fi
-
-\subsection{Epistemic types}
-
-In line with traditional evolutionary game theory, the idea of this work is to model a population of rather unsophisticated and myopic agents that possibly differ from each other with respect to two components: the player type and the epistemic type.
-In full generality, we think of an epistemic type as a general disposition to form beliefs about the co-player’s behavior.
-Players in the population obviously face uncertainty about the composition of the population that they are part of, and consequently about the type of co-player that they are randomly paired with at each round and about the co-player's actions.
-We represent this uncertainty that players entertain in two different ways, a probabilistic flat belief and a non-probabilistic belief.
-This amounts to having two different epistemic types $e$ in the population, $e \in \lbrace \overline{\mu}, \Delta(A_{-i}) \rbrace $, where $\overline{\mu}$ is the probabilistic type and $\Delta(A_{-i})$ is the non-probabilistic type, defined as follows:
-
-\begin{itemize}
-
-\item $ \Delta(A_{-i}):=\lbrace \mu \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu(a_{-i}) = 1 \rbrace$;
-
-\item $\overline{\mu} \in \lbrace \mu \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu(a_{-i}) = 1 \rbrace$ is the probability measure over the co-player's actions such that: $\forall a_{-i} \in A_{-i}$, $\overline{\mu}(a_{-i})= \frac{1}{|A_{-i}|}$.
-
-\end{itemize}
-
-Hence, we consider two possible epistemic states in the face of uncertainty.
-The epistemic type $\Delta(A_{-i})$ represents a situation of non-probabilistic radical uncertainty, where the players are not able to narrow down the set of probability distributions over the co-player's actions and they consider all of them as possible.
-The other epistemic type $\overline{\mu}$ conceptualizes the uncertainty about the population by using the principle of insufficient reason and ascribes equal probability to all the possible alternatives.
-Both options are reasonable and justifiable ways to deal with situations of uncertainty [REFERENCES].
-\\
-Since for the moment we want to model populations of biologically unsophisticated players, we do not endow them with an effective learning procedure.
-Our players encode both a psychological subjective representation of the interaction (player type) and a conceptualization of uncertainty (epistemic type), but they are too simple to have any learning or belief updating procedure.
-From this point of view, we can take the learning process away from natural selection and focus on player types and epistemic types as the target of evolutionary pressure.
-
-\subsection{Uncertainty aversion and maxmin rule}
-
-Given a player type and an epistemic type, there are different ways to produce a behavior.
-A huge body of experimental literature strongly suggests that agents are generally uncertainty (or ambiguity) averse [REF].
-This pattern of behavior in the presence of ucertainty has been famously axiomatized by Gilboa and Schmeidler in a paper from 1989.
-The idea is that being uncertainty averse amounts to behaving in accordance with maximinimizing expected utility over a set of prior probabilities.
-Whenever the set of priors is a singleton, maximinization of expected utility coincides with maximization of expected utility.
-In line with empirical data, we assume that players in the population are uncertainty averse and conform to maxmin expected utility.
-The resulting behavior is then produced by maximinimizing over the subjective utility given by the player type and the set of priors given by the epistemic type.
-\\
-
-\begin{example}
-Consider the game in Figure \ref{coordgame1} again.
-When a player characterized by\footnote{To ease notation in the following we will refer to a player directly as a pair $(player \text{ } type \text{ } \tau,\text{ } epistemic\text{ } type \text{ } e)$.} player type $ \tau^{reg} $ and epistemic type $ \Delta(A_{-i}) $ faces the game in Figure \ref{coordgame1}, her player type gives rise to the representation $\tau^{reg}(G^C)$ in Figure \ref{coordgame1reg}.
-Then, maximinimizing expected utility over the probability simplex $ \Delta(A_{-i}) $ given the game in Figure \ref{coordgame1reg} corresponds to playing the standard maxmin strategy [REF] of that game.\footnote{Notice that this is the case for any game: given a game $G$, maximinimizing expected utility over the probability simplex $ \Delta(A_{-i}) $ amounts to playing the standard maxmin strategy of $G$.} This, in turn, corresponds to the regret minimizing action of the original game $G^C$ of Figure \ref{coordgame1}, namely action $II$, as we have seen in Section \ref{sec:regreTheory}.
-A player $(\tau^{reg},\overline{\mu})$ instead has subjective representation $\tau^{reg}(G^C)$ of Figure \ref{coordgame1reg} and a flat probability measure $\overline{\mu}=(\frac{1}{2}I,\frac{1}{2}II)$ over the co-player's actions.
-Consequently, such a player would play action $II$, i.e., the action that maximinimizes expected utility given the flat probability measure $\overline{\mu}$.\footnote{As we already noticed, maximinimizing expected utility given a probability measure $\mu$ is equivalent to maximizing expected utility given $\mu$.}
-Similarly, a player $(\tau^{\pi},\Delta(A_{-i}))$ will have the subjective representation coinciding with the objective fitness game, i.e., $ \tau^{\pi}(G^C)= G^C $.
-Then, both actions $I$ and $II$ maximinimize expected utility over the probability simplex $ \Delta(A_{-i}) $.
-Hence, a player $(\tau^{\pi},\Delta(A_{-i}))$ will be indifferent between $I$ and $II$, and will randomize with equal probability $(\frac{1}{2}I,\frac{1}{2}II)$.
-Finally, a player $(\tau^{\pi},\overline{\mu})$ maximinimizes the objective fitness game $G^C$ of Figure \ref{coordgame1} with flat probability $\overline{\mu}$ over the co-player's actions, i.e., maximizes objective utility given $\overline{\mu}$.
-In game $G^C$ this yields action $II$.
-
-\begin{figure}
-\begin{center}%
-\begin{tabular}{|c|c|c|}
-\hline 
- & I & II\tabularnewline
-\hline 
-\hline 
-I & 0;0 & -2;-1\tabularnewline
-\hline 
-II & -1;-2 & 0;0\tabularnewline
-\hline 
-\end{tabular}\end{center}
-
-\protect\caption{Regret representation $\tau^{reg}(G^C)$}
-\label{coordgame1reg}
-\end{figure}
-
-\end{example}
-
-We are now in the position of deriving behavior directly from the pair $(\tau, e)$.
-Definitions \ref{def:utility-belief} and \ref{def:maxminSEU} simply formalize the notions of subjective expected utility and maxmin subjective expective utility, respectively.
-
-\begin{definition} \label{def:utility-belief}
-
-Given a game $G$, an action $a_i \in A_i$, and a belief $\mu \in \lbrace \mu' \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu'(a_{-i}) = 1 \rbrace$, we define $\tau(G)(a_i, \mu):= \sum_{a_{-i} \in A_{-i}} \tau(G)(a_i, a_{-i}) \cdot \mu(a_{-i})$.
-
-\end{definition}
-
-\begin{definition} \label{def:maxminSEU}
-
-Given a game $G$ and a player $(\tau, e)$, we define $\text{maxmin}(\tau(G), e):= \lbrace a'_i \in A_i : a_i \in \text{max}_{a_i \in A_i} \text{ min}_{\mu \in e} \text{ } \tau(G)(a_i, \mu) \rbrace$.
-
-\end{definition}
-
-\noindent Definition \ref{def:expected fitness} gives the expected evolutionary fitness of player $(\tau, e)$ against player $(\tau', e')$ in game $G$.\footnote{As already specified in the previous example, we assume that, whenever the set $\text{maxmin}(\tau(G), e)$ is not a singleton, the player $(\tau, e)$ will mix with equal probability among the actions in $\text{maxmin}(\tau(G), e)$.}
-
-\begin{definition} \label{def:expected fitness}
-
-Given a game $G \in \mathcal{G}$, a player $(\tau, e)$, and a player $(\tau', e')$, we define $\pi^G((\tau, e),(\tau', e')):= \pi^G(\text{maxmin}(\tau(G), e),\text{maxmin}(\tau'(G), e'))$.
-
-\end{definition}
-
-Many other alternatives different from maxmin expected utility could produce behavior: choice rules like minmax, maxmax, and minmin expected utility would similarly generate behavior from a player type and an epistemic type.
-Here we postulate that players are maximinimizers for two main reasons.
-First, our main interest is the evolution of different patterns of subjective conceptualizations of games (player types), and we want to show that the veridical representation (objective type) is not necessarily the fittest and may not be evolutionarily stable.
-Assuming that all players use the maxmin rule independent of their player type allows us to factor the choice rule out of the selection process and to focus on player types.
-Secondly, as already mentioned, among other possible choice rules maxmin is not only intuitively appealing but also corroborated from an empirical point of view.
-
-Before concluding this section, it is worth stressing two important points.
-
-\begin{fact} \label{fact:maxEU-minReg}
-
-For any given single probability $\mu$, maximization of expected utility and minimization of expected regret are behaviorally equivalent.
-
-\end{fact}
-
-\noindent As we have seen in the previous example, this is not the case in the presence of (radical) uncertainty, in the sense of representation of belief state in terms of a set of probability, as in $ \Delta(A_{-i}) $.
-
-\begin{fact} \label{fact:equivalence2x2}
-
-In the class of $2 \times 2$ symmetric games, players $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg},\overline{\mu})$ are behaviorally equivalent.
-
-\end{fact}
-
-\noindent We still treat them as distinct, because they will perform differently with respect to component-wise mutation (see below).
-Moreover, Fact \ref{fact:equivalence2x2} does not hold for $n \times n$ symmetric games in general.
-
-\subsection{Evolution \& the environment}
-
-[MAYBE, put part of Version2 from Snippets here, if not in Introduction]
-
-In standard evolutionary game theory a population of agents plays over a single game, that is supposed to represent the interaction driving the evolutionary dynamics.
-In line with [Fawcett-al.], we claim that the single-game approach is too limiting to encompass the vast variety of interactions that lead evolution.
-Here we propose the meta-game model in order to account for a more general notion of environment.
-By allowing the population to play over a class of possible games, we want to take into consideration a notion of environment that comprises a multitude of possible interactions as the driver of natural selection.
-In this perspective, the meta-game approach represents a model of evolution more faithful and possibly closer to reality.
-\\
-We assume a huge, possibly infinite, population of players $(\tau,e)$.
-At each time, a game $G$ is selected from the class of possible games, and players are randomly paired to play $G$.
-At the end of the play we keep track of the evolutionary fitness achieved by each player.
-Next, another game $G'$ is randomly selected again, and so on.
-The evolutionary fitness of each player is then based on the expected objective payoff over the class $\mathcal{G}$.
-Denoting by $P(G)$ the probability of game $G$ to be selected, the evolutionary fitness of player $(\tau,e)$ against player $(\tau',e')$ is given by:
-
-$$ EF((\tau,e),(\tau',e'))= \int_G  P(G) \cdot \pi^G((\tau, e),(\tau', e')).  $$
-
-\noindent The framework we propose here is a very neutral and flexible tool to model the notion of environment.
-We can take into account many different types of environment by simply changing the class $\mathcal{G}$ of possible games, and in the limit case where $\mathcal{G}$ is a sigleton our model reduces to the standard models of evolutionary game theory.
-By combining field studies and statistics, one could design a more specific class $\mathcal{G}$ with appropriate probabilities $P(G)$ in order to match the natural environment of a given population, but for our theoretical purposes we adopt another approach.
-As already anticipated, we take $\mathcal{G}$ to be the class of $2 \times 2$ symmetric games.
-More precisely, we imagine the class $\mathcal{G}$ to be generated from the generic form table of Figure \ref{generic form table}, where $a,b,c,d$ are i.i.d.
-random variables sampled from a finite set of natural numbers $ \lbrace \underline{n}, \dots, \overline{n}  \rbrace$.
-
-\begin{figure}
-\begin{center}%
-\begin{tabular}{|c|c|c|}
-\hline 
- & I & II\tabularnewline
-\hline 
-\hline 
-I & a;a & b;c\tabularnewline
-\hline 
-II & c;b & d;d\tabularnewline
-\hline 
-\end{tabular}\end{center}
-
-\protect\caption{generic form table for $2 \times 2$ symmetric games}
-\label{generic form table}
-\end{figure}
-
-\section{Results: the basic model}
-\label{sec:results:-basic-model}
-
-In this section we present results of computer simulations and analytical proofs for our basic
-model with the four player types introduced in the previous section.
-
-\subsection{Numerical simulations}
-\label{sec:numer-simul}
-
-Table~\ref{tab:ExpectedFitness_4Types} gives an approximation of expected fitness, obtained by
-numerical simulation from averaging over $100,000$ randomly sampled games in $\mathcal{G}$ with
-$a,b,c,d \in \lbrace 0, \dots, 10 \rbrace$. Concretely, games were sampled repeatedly by
-choosing independently four integers $a,b,c,d \in \lbrace 0, \dots, 10 \rbrace$ uniformly at
-random. For each game, a player type's action choices were determined and payoffs from all
-pairwise encounters recorded. (Whenever a player type would not select a unique action in a
-given game, we recorded unbiased averages over playing either action.) The number in each cell
-of Table~\ref{tab:ExpectedFitness_4Types} is the average payoff for the row player type over
-all 100,000 numbers for each pairing of player types obtained in this way. These averages
-approximate the corresponding average evolutionary fitness of the row player when matched with
-the column player.
-
-\begin{table}[t]
-\centering
-\begin{tabular}{ccccc}
-  \toprule
- & $\tau^{reg}, \Delta(A_{-i})$ 
- & $\tau^{\pi}, \Delta(A_{-i})$ 
- & $\tau^{reg}, \overline{\mu}$ 
- & $\tau^{\pi}, \overline{\mu}$ \\ 
-  \midrule
-  $\tau^{reg}, \Delta(A_{-i})$ & 6.663 & 6.662 & 6.663 & 6.663 \\ 
-  $\tau^{\pi}, \Delta(A_{-i})$ & 6.486 & 6.484 & 6.486 & 6.486 \\ 
-  $\tau^{reg}, \overline{\mu}$ & 6.663 & 6.662 & 6.663 & 6.663 \\  
-  $\tau^{\pi}, \overline{\mu}$ & 6.663 & 6.662 & 6.663 & 6.663 \\ 
-   \bottomrule
-\end{tabular}                    
-\caption{Average evolutionary fitness in simulations of 100,000 symmetric $2 \times 2$ games}
-\label{tab:ExpectedFitness_4Types}
-\end{table}
-
-Simulation results obviously reflect Fact~\ref{fact:equivalence2x2} in that all encounters in
-which types $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{reg}, \overline{\mu})$ or
-$(\tau^{\pi}, \overline{\mu})$ are substituted for one another yield identical results. More
-interestingly, Table~\ref{tab:ExpectedFitness_4Types} shows that the maximin strategy
-$(\tau^{\pi}, \Delta(A_{-i}))$ is strictly dominated by either of the three other strategies:
-in each column (i.e., for each kind of opponent), the maximin strategy is strictly worse
-than any of the three behaviorally equivalent competitors. This has a number of interesting
-consequences.
-
-Let's begin with a restricted scenario and look at more and more complex cases afterwards. If
-we restrict attention to a population of radically uncertain players, i.e., where only
-epistemic type $\Delta(A_{-i})$ exists, the regret type $ \tau^{reg} $ is the only
-\emph{evolutionarily stable state}. An evolutionarily stable state is a state which cannot be
-invaded by a small number of mutants. More strongly, since maximin play is strictly dominated,
-we expect selection that is driven by expected fitness to invariably weed out maximin behavior
-in favor of regret minimization. In other words, when taking average payoffs over the class of
-random games looked at here, regret minimization is a better choice rule than standard maxmin
-from an evolutionary point of view, despite the fact that the former, but not the letter
-entertains non-veridical subjective preferences.
-
-Next, if we look at the competition between all four types represented in
-Table~\ref{tab:ExpectedFitness_4Types}, $(\tau^{reg}, \Delta(A_{-i}))$ is no longer
-evolutionarily stable. Rather, given behavioral equivalence (Fact~\ref{fact:equivalence2x2}),
-types $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{reg}, \overline{\mu})$, and
-$(\tau^{\pi}, \overline{\mu})$ are all \emph{neutrally stable}
-\citep{Maynard-Smith1982:Evolution-and-t}. But since $(\tau^{\pi}, \Delta(A_{-i}))$ is strictly
-dominated and so disfavored by fitness-based selection, we are still drawn to conclude that
-maximin behavior is weeded out in favor of a population with a random distribution of the
-remaining three types.
-
-Simulation results of the (discrete time) \emph{replicator dynamics}
-\citep{TaylorJonker1978:Evolutionary-St} indeed show that random initial population
-configurations are attracted to states with only three player types:
-$\tuple{\tau^{reg}, \Delta(A)}$, $\tuple{\tau^{reg}, \bar{\mu}}$ and
-$\tuple{\tau^{\pi}, \bar{\mu}}$. The relative proportions of these depend on the initial
-population.\todo{check uniform notation for player types: round vs.~square brackets} This
-variability disappears if we add a small mutation rate to the dynamics. We assume a fixed,
-small mutation rate $\epsilon$ for the probability that a player's preference type \emph{or}
-her epistemic type changes to another random preference type or epistemic type. The probability
-that a player type randomly mutates into a completely different player type with altogether
-different preference type and epistemic type would then be $\epsilon^2$. With these assumptions
-about ``component-wise mutations'', numerical simulations of the (discrete time)
-\emph{replicator mutator dynamics} \citep{Nowak2006:Evolutionary-Dy} show that already for very
-small mutation rates almost all initial populations converge to a single fixed point in which
-the majority of players are regret types. For instance, with $\epsilon = 0.001$, almost all
-initial populations are attracted to a final distribution with proportions:\todo{recalculate
-  these numbers for the actual 4x4 game!}
-
-\begin{center}
-  \begin{tabular}{ccc}
-    $\tuple{\tau^{reg}, \Delta(A)}$ & $\tuple{\tau^{reg},
-      \bar{\mu}}$ & $\tuple{\tau^{\pi}, \bar{\mu}}$ \\ \hline
-    0.279  &   0.383 &    0.281 
-  \end{tabular}
-\end{center}
-
-What this suggests is that, since biological evolution selects behavior-generating mechanisms,
-not behavior as such, it need not be the case that behaviorally equivalent mechanisms are
-treated equally all the while. If mutation probabilities are a function of individual
-components of such behavior-generating mechanisms, it can be the case that certain components
-are more strongly favored by a process of random mutation and selection. This is exactly the
-case with regret-based subjective preferences in the present example. Since regret-based
-subjective preferences are much better in connection with radical uncertainty than veridical
-preferences are, the proportion of expected regret minimizers in the attracting state is
-substantially higher than that of expected utility maximizers, even though these types are
-behaviorally equivalent. In sum, component-wise mutation could have lead to a majority of
-regret-based players even if they are behaviorally indiscernible from decision makers with
-veridical preferences, because regret types are better off under radical uncertainty.
-
-\subsection{Analytical results}
-\label{sec:analytical-results}
-
-Results based on the single meta-game in Table~\ref{tab:ExpectedFitness_4Types}, which was
-obtained by averaging over numerical simulations, are not fully general and possibly spoiled by
-random fluctuations in the sampling procedure. Fortunately, for the case of symmetric
-$2 \times 2$ games, the main result that maximin types $(\tau^{\pi}, \Delta(A_{-i}))$ are
-strictly dominated can also be shown analytically for generous general conditions on how likely
-randomly sampled games are.
-
-\begin{proposition} \label{proposition1}
-
-  Let $\Lambda = \lbrace (\tau^{\pi}, \Delta(A_{-i})), (\tau^{reg}, \Delta(A_{-i})) \rbrace$ be
-  the set of possible meta-types $(\tau, e)$ in the population, and let $\mathcal{G}$ be the class
-  of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex,
-  set of i.i.d.~values. Then, $(\tau^{reg}, \Delta(A_{-i}))$ is the only strict Nash
-  equilibrium in the resulting meta-game.
-
-\end{proposition}
-
-\begin{proof}
-See Appendix.
-\end{proof}
-
-From Fact \ref{fact:equivalence2x2} and Proposition \ref{proposition1} the following corollary follows.
-
-\begin{corollary} \label{corollary1}
-
-  Fix $T = \lbrace \tau^{\pi}, \tau^{reg} \rbrace$,
-  $E = \lbrace \Delta(A_{-i}), \overline{\mu} \rbrace$, $\Lambda= T \times E$, and
-  $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite,
-  or compact and convex, set of i.i.d. values. Then, player type $(\tau^{\pi}, \Delta(A_{-i}))$
-  is strictly dominated by $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
-  $(\tau^{reg}, \overline{\mu})$.
-
-\end{corollary}
-
-\begin{proof}
-See Appendix.
-\end{proof}
-
-Corollary~\ref{corollary1} tells us that the conclusions drawn in the previous section based on
-the meta-game in Table~\ref{tab:ExpectedFitness_4Types} hold more generally for any class of
-games in which the probability of encountering a game is the product of independently sampling
-four identically distributed payoff values. As before, player types
-$(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
-$(\tau^{reg}, \overline{\mu})$ will be neutrally stable, and fitness-based selection will tend
-to weed out maximin play and leave us with a population of arbitrary frequency of
-$(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
-$(\tau^{reg}, \overline{\mu})$ meta-types.
-
-This shows that there is support for the main conceptual point that we wanted to make:
-non-veridical subjective preference relations \emph{can}, under specific circumstances, persist
-under evolutionary selection based on objective fitness. Moreover, regret-based preferences can
-not only persist, but even be favored by natural selection if agents are radically
-uncertain. This holds generally for playing arbitrary $2 \times 2$ games whose payoffs are
-sampled identically and independently at random.
-
-\section{Extensions}
-\label{sec:extensions}
-
-How do the basic results from the previous section carry over to more encompassing, richer
-models? Section~\ref{sec:more-types} first considers further conceptually interesting
-preference types that have been suggested in the recent literature. Section~\ref{sec:n-times-n}
-then considers the case of $n \times n$ games for $n \ge 2$. Finally, to put our results into
-the proper perspective, Section~\ref{sec:solitary-decisions} ends with a brief comparison of
-game situations with cases of solitary decision making.
-
-\subsection{More types}
-\label{sec:more-types}
-
-In evolutionary game theory other types of player have been investigated.
-A famous example is the \textit{altruistic type} [REF], introduced in the literature in order to explain the possible survival of altruistic behavior.
-In our framework, we can represent the altruistic type as follows.
-
-\begin{definition}[Altruistic preference] \label{defn:altpref}
-
-For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{alt}: A \rightarrow \mathbb{R} $ such that $ \theta^{alt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \sum_{j \neq i} \pi(a_{j},a_{-j})$.\footnote{A more general formulation [see: REFERENCES] would be to define an $ \alpha$-altruistic type, for $\alpha \in [0,1]$, with subjective utility $ \theta^{\alpha lt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \alpha \sum_{j \neq i} \pi(a_{j},a_{-j})$.
-Since we are not interested in the evolution of degrees of altruism here, we simply fix $ \alpha = 1 $.}
-
-\end{definition}
-
-\begin{definition}[Altruistic type] \label{defn:alttype}
-
-Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{alt}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{alt}(G)= \theta^{alt}$.
-
-\end{definition}
-
-\noindent As opposite to the altruistic type, it is possible to define a \textit{competitive type}.
-
-\begin{definition}[Competitive preference] \label{defn:compref}
-
-For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{com}: A \rightarrow \mathbb{R} $ such that $ \theta^{com}(a_i,a_{-i})=\pi(a_i,a_{-i}) - \sum_{j \neq i} \pi(a_{j},a_{-j})$.
-
-\end{definition}
-
-\begin{definition}[Competitive type] \label{defn:comtype}
-
-Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{com}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{com}(G)= \theta^{com}$.
-
-\end{definition}
-
-Similarly to the evolutionary competition that we simulated before, we can study the
-evolutionary fitness of this extended set of players when they are all represented in the
-population. Table~\ref{tab:ExpectedFitness_2x2_Full} shows simulation results that approximate the
-expected fitness in the relevant meta-game.
-
-\begin{table}[]
-\centering
-\footnotesize
-\begin{tabular}{ccccccccc}
-  \hline
- & $\tuple{\tau^{reg}, \Delta(A)}$ 
- & $\tuple{\tau^{\pi}, \Delta(A)}$ 
- & $\tuple{\tau^{com}, \Delta(A)}$
- & $\tuple{\tau^{alt}, \Delta(A)}$
- & $\tuple{\tau^{reg}, \bar{\mu}}$ 
- & $\tuple{\tau^{\pi}, \bar{\mu}}$ 
- & $\tuple{\tau^{com}, \bar{\mu}}$
- & $\tuple{\tau^{alt}, \bar{\mu}}$ \\ 
-  \hline
-  $\tuple{\tau^{reg}, \Delta(A)}$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
-  $\tuple{\tau^{\pi}, \Delta(A)}$ & 6.486 & 6.484 & 6.088 & 6.703 & 6.486 & 6.486 & 6.088 & 6.875 \\
-  $\tuple{\tau^{com}, \Delta(A)}$ & 6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\
-  $\tuple{\tau^{alt}, \Delta(A)}$ & 5.949 & 5.722 & 5.326 & 6.396 & 5.949 & 5.949 & 5.326 & 6.568 \\
-  $\tuple{\tau^{reg}, \bar{\mu}}$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
-  $\tuple{\tau^{\pi}, \bar{\mu}}$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
-  $\tuple{\tau^{com}, \bar{\mu}}$ & 6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\
-  $\tuple{\tau^{alt}, \bar{\mu}}$ & 6.331 & 5.893 & 5.497 & 6.566 & 6.331 & 6.331 & 5.497 & 7.152 \\
-   \hline                          
-\end{tabular}                      
-\caption{Average payoff in simulations of 100,000
-  randomly generated $2 \times 2$ symmetric games.}
-\label{tab:ExpectedFitness_2x2_Full}        
-\end{table}
-
-\todo[inline]{is it true that competitive preferences types are behaviorally equivalent under
-  either epistemic type? can we show that?}
-
-The approximations in Table~\ref{tab:ExpectedFitness_2x2_Full} confirm basic intuitions about
-altruistic and competitive types: averaging over randomly sampled games, everybody would like
-to have an altruistic opponent and nobody would like to play against a competitive
-opponent. Perhaps more surprisingly, altruistic types come up strictly dominated by competitive
-types, but competitive types themselves are worse off against all opponent types except against
-maximin players $\tuple{\tau^{\pi}, \Delta(A)}$ than any of the behaviorally equivalent types
-$(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
-$(\tau^{reg}, \overline{\mu})$.  This is a noteworthy results in the light of the fact that
-evolving altruistic preferences have been shown to support cooperative behavior in a single
-stage game \myalert{[CITE]}. \todo{@Paolo: check whether this is true, please!} In contrast,
-averaging over payoffs in multiple stage games, like we do here, makes altruistic preferences
-prime victims of evolutionary eradication.
-
-It is easy to see then that the previous result still obtains for the larger meta-game in
-Table~\ref{tab:ExpectedFitness_2x2_Full}: $(\tau^{reg}, \Delta(A_{-i}))$,
-$(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$ are still neutrally stable;
-all simulations of the (discrete-time) replicator dynamic on the $8 \times 8$ meta-game from
-Table~\ref{tab:ExpectedFitness_2x2_Full} end up in populations consisting of only these types
-in arbitrary proportion.
-
-The following proposition (partially) confirms this result.\todo{rephrase to acknowledge all
-  epistemic types?}
-
-\begin{proposition} \label{proposition2}
-
-Fix $\Lambda = \lbrace (\tau^{\pi}, \Delta(A_{-i})), (\tau^{reg}, \Delta(A_{-i})), (\tau^{alt}, \Delta(A_{-i})), (\tau^{com}, \Delta(A_{-i})) \rbrace$ and $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex, set of i.i.d.
-values.
-Then, $(\tau^{reg}, \Delta(A_{-i}))$ is the only evolutionarily stable player in the population.
-
-\end{proposition}
-
-\begin{proof}
-See Appendix.\todo{is this there already?}
-\end{proof}
-
-In sum, the presence of other plausible preference types, such as competitive and altruistic
-types does not undermine the previous results about the evolutionary drive towards regret-based
-subjective preferences.
-
-\subsection{$n \times n$ symmetric games}
-\label{sec:n-times-n}
-
-Results from Section~\ref{sec:results:-basic-model} relied heavily on
-Fact~\ref{fact:equivalence2x2} that, for the special case of $2 \times 2$ symmetric games,
-regret minimization $\tuple{\tau^{reg}, \Delta(A)}$ is behaviorally equivalent with expected
-regret minimization $\tuple{\tau^{reg}, \bar{\mu}}$ and expected utility maximization
-$\tuple{\tau^{\pi}, \bar{\mu}}$. This is no longer true when we look at arbitrary $n \times n$
-games with $n \ge 2$. We should therefore see what happens in a broader class of games.
-
-Table~\ref{tab:ExpectedFitness_10x10} therefore gives approximations for expected fitness in a
-meta-game over a class of $n \times n$ symmetric games where $n$ is randomly drawn from
-$\set{2, \dots, 10}$. Concretely, the numbers in Table~\ref{tab:ExpectedFitness_10x10} are
-averages of payoffs obtained in 100,000 randomly sampled games, where each game was sampled by
-first picking a number of acts $n \in \set{2, \dots, 10}$ uniformly at random, and then filling
-the resulting $n \times n$ payoff matrix of the stage game with i.i.d.~sampled payoffs as
-before.
-
-\begin{table}[]
-\centering
-\footnotesize
-\begin{tabular}{ccccccccc}
-  \hline
- & $\tuple{\tau^{reg}, \Delta(A)}$ 
- & $\tuple{\tau^{\pi}, \Delta(A)}$ 
- & $\tuple{\tau^{com}, \Delta(A)}$
- & $\tuple{\tau^{alt}, \Delta(A)}$
- & $\tuple{\tau^{reg}, \bar{\mu}}$ 
- & $\tuple{\tau^{\pi}, \bar{\mu}}$ 
- & $\tuple{\tau^{com}, \bar{\mu}}$
- & $\tuple{\tau^{alt}, \bar{\mu}}$ \\ 
-  \hline
-  $\tuple{\tau^{reg}, \Delta(A)}$ & 6.567 & 6.570 & 5.650 & 6.992 & 6.564 & 6.564 & 5.593 & 7.409 \\
-  $\tuple{\tau^{\pi}, \Delta(A)}$ & 6.476 & 6.483 & 5.896 & 6.818 & 6.484 & 6.484 & 5.850 & 7.124 \\
-  $\tuple{\tau^{com}, \Delta(A)}$ & 6.468 & 6.647 & 5.512 & 7.169 & 6.578 & 6.578 & 5.577 & 7.354 \\
-  $\tuple{\tau^{alt}, \Delta(A)}$ & 5.968 & 5.923 & 5.363 & 6.685 & 5.975 & 5.975 & 5.086 & 6.973 \\
-  $\tuple{\tau^{reg}, \bar{\mu}}$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
-  $\tuple{\tau^{\pi}, \bar{\mu}}$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
-  $\tuple{\tau^{com}, \bar{\mu}}$ & 6.529 & 6.680 & 5.445 & 7.276 & 6.542 & 6.542 & 5.521 & 7.440 \\
-  $\tuple{\tau^{alt}, \bar{\mu}}$ & 6.450 & 6.337 & 5.772 & 6.978 & 6.457 & 6.457 & 5.479 & 7.500 \\
-   \hline                          
-\end{tabular}                      
-\caption{Average payoff in simulations of 100,000
-  randomly generated $n \times n$ symmetric games with $n$ randomly drawn from $\set{2, \dots, 10}$.}
-\label{tab:ExpectedFitness_10x10}        
-\end{table}
-
-As is to be expected, average payoffs obtained in games with more than 2 acts are higher, as
-can be seen by comparing Table~\ref{tab:ExpectedFitness_10x10} with
-Table~\ref{tab:ExpectedFitness_2x2_Full}. But increases in approximate expected fitness are not
-uniform. Most importantly, the regret minimizing type $\tuple{\tau^{reg}, \Delta(A)}$ is
-strictly dominated by $\tuple{\tau^{reg}, \bar{\mu}}$ and by $\tuple{\tau^{\pi}, \bar{\mu}}$ in
-the meta-game from Table~\ref{tab:ExpectedFitness_10x10}. This means that while regret
-minimization \emph{can} thrive in some evolutionary contexts, there are also contexts where it
-is demonstrably worse off.
-
-Still, although this may be bad news for regret minimizing types
-$\tuple{\tau^{reg}, \Delta(A)}$, it is not the case that regret types \emph{as such} are weeded
-out by selection. Since, by Fact~\ref{fact:maxEU-minReg}, $\tuple{\tau^{reg}, \bar{\mu}}$ and
-$\tuple{\tau^{\pi}, \bar{\mu}}$ are generally behaviorally equivalent, it remains that
-selection based on meta-games constructed from $n \times n$ games will still not eradicate all
-regret types. So, although regret types may not be selected for in this case, they are also not
-selected against.
-
-On the other hand, there are plenty of ways in which the basic insight from
-Proposition~\ref{proposition1} that regret-based preferences can be strictly better than
-veridical objective preferences in case of radical uncertainty could make for situations in
-which evolution would select for regret types exclusively, even in $n \times n$ games. If, for
-example, epistemic types of players are not what biological evolution selects, but rather
-something that the particular choice situation would exogenously give us, then regret-based
-preference \emph{can} again drive out veridical preferences altogether. For concreteness,
-suppose that only preference types compete and that agents' epistemic types are exogenously
-given, in such a way that agents hold flat probabilistic beliefs $\bar{\mu}$ with probability
-$1-p$ and are of type $\Delta(A)$ with probability $p$. This transforms the meta-game from
-Table~\ref{tab:ExpectedFitness_10x10} into the simpler $4 \times 4$ game in which the payoff
-obtained for a preference type is the weighted average over the payoffs of that preference
-types in Table~\ref{tab:ExpectedFitness_10x10}. Setting $p = 0.02$ for illustration, we get the
-meta-game in Table~\ref{tab:ExogeneousEpistemics}.
-
-\begin{table}[]
-\centering
-\begin{tabular}{ccccc}
-  \toprule
-  & $\tau^{reg}$ 
-  & $\tau^{\pi}$ 
-  & $\tau^{com}$
-  & $\tau^{alt}$ \\ 
-  \midrule
-  $\tau^{reg} $ & 6.926 & 6.926 & 5.942 & 7.757 \\ 
-  $\tau^{\pi} $ & 6.924 & 6.924 & 5.948 & 7.751 \\ 
-  $\tau^{com }$ & 6.566 & 6.570 & 5.481 & 7.434 \\ 
-  $\tau^{alt} $ & 6.463 & 6.461 & 5.478 & 7.469 \\ 
-   \bottomrule
-\end{tabular}
-\caption{Meta-game for the evolutionary competition between preference types when epistemic types are exogenously
-  given}
-\label{tab:ExogeneousEpistemics}
-\end{table}
-
-The only evolutionarily stable state of this meta-game is the regret type. Accordingly, all of
-our simulation runs of the (discrete-time) replicator dynamic converged to monomorphic
-regret-type populations. The reason why regret types prosper is because they have a substantial
-payoff advantage if paired with radical uncertainty. If radical uncertainty is exogenously
-given as something unavoidable that happens to agents (e.g., whenever they really have no
-indication as to what the situation holds for them), and even if that happens only very
-infrequently (i.e., for rather low $p$), regret types \emph{can} outperform veridical
-preference types, as well as competitive and altruistic types.
-
-\subsection{Solitary decisions}
-\label{sec:solitary-decisions}
-
-\section{Discussion}
-
-\begin{itemize}
-\item what we achieved
-\item what could be done next
-\end{itemize}
-
-\appendix
-
-\section{Proofs}
-
-The proof of Proposition 1 relies on a partition of $\mathcal{G}$,
-and on some lemmas. For brevity, let us denote the regret minimizer
-by RM and the maximinimizer by MM. Since the proof is very long and
-all the other cases are similar and easier to prove, we focus here
-on the case of RM against MM players: we prove that RM is evolutionarily
-stable against MM, but MM is not evolutionarily stable against RM. By $EU_{\mathcal{G}}(x,y)$ we denote the expected \textit{objective} utility (or payoff), in terms
-of evolutionary fitness, of player type $x$ against player type $y$
-with respect to the class of fitness games $\mathcal{G}$.
-
-\medskip{}
-
-\textbf{Proof of Proposition 1.} By definition of evolutionary stability, we have to
-show that in the class $\mathcal{G}$ of symmetric $2\times2$ games generated by i.i.d. sampling
-from a finite or compact and convex set of values, it holds:
-\begin{itemize}
-\item[(i)] $EU_{\mathcal{G}}(RM,RM)>EU_{\mathcal{G}}(MM,RM);$
-\item[(ii)] $EU_{\mathcal{G}}(MM,MM)<EU_{\mathcal{G}}(RM,MM).$
-\end{itemize}
-
-\noindent To show
-the result we will use the following partition of $\mathcal{G}$.
-\begin{enumerate}
-\item Coordination games $\mathcal{G}^{C}$: $a>c$ and $d>b$;
-\item Anti-coordination games $\mathcal{G}^{A}$: $a<c$ and $d<b$;
-\item Strong dominance games $\mathcal{G}^{S}$: aut $(a>c$ and $b>d)$
-aut $(a<c$ and $b<d)$;
-\item Weak dominance games $\mathcal{G}^{W}$: aut $a=c$ aut $b=d$;
-\item Indifferent games $\mathcal{G}^{I}$: $a=c$ and $b=d$.
-\end{enumerate}
-Before proving the lemmas, it is convenient to fix some notation.
-We denote by $G^{C}$ a coordination game in $\mathcal{G}^{C}$ with
-payoffs $a^{G^{C}}$, $b^{G^{C}}$, $c^{G^{C}}$, and $d^{G^{C}}$;
-similarly, for $G^{A}$, $G^{S}$, $G^{W}$, and $G^{I}$. Let us
-call $I_{G^{C}}^{RM}$ the event that a RM player plays action $I$
-in the game $G^{C}$; and similarly for action $II$, for player MM,
-and for games $G^{A}$, $G^{S}$, $G^{W}$ and $G^{I}$. Moreover,
-let us recall the definition of evolutionarily stable strategy and
-neutrally stable strategy.
-
-\medskip{}
-
-\begin{definition}[ESS-NSS]
-A strategy $s^{\$}$ is \emph{evolutionarily stable
-(ESS)} if for any other strategy $s$:
-\begin{enumerate}
-\item $\pi(s^{\$},s^{\$})>\pi(s,s^{\$})$, or
-\item $\pi(s^{\$},s^{\$})=\pi(s,s^{\$})$ and $\pi(s^{\$},s)>\pi(s,s)$.
-\end{enumerate}
-\noindent A strategy $s^{\$}$ is \emph{neutrally stable (NSS)} if
-for any other strategy $s$:
-\begin{enumerate}
-\item $\pi(s^{\$},s^{\$})>\pi(s,s^{\$})$, or
-\item $\pi(s^{\$},s^{\$})=\pi(s,s^{\$})$ and $\pi(s^{\$},s)\geq\pi(s,s)$.
-\end{enumerate}
-\end{definition}
-
-\medskip{}
-
-\begin{lemma}
-RM and MM perform equally well in $\mathcal{G}^{S}$
-and in $\mathcal{G}^{I}$. 
-\end{lemma}
-
-\begin{proof}
-By definition of regret minimization and maximin it
-is easy to check that whenever in a game there is a strongly dominant
-action $a^{\$}$, then $a^{\$}$ is both the maximin action and the
-regret minimizing action. Then, for all the games in $\mathcal{G}^{S}$,
-a RM chooses action $a$ if and only if MM chooses action $a$. Consequently,
-RM and MM always perform equally (well) in $\mathcal{G}^{S}$. In
-the case of $\mathcal{G}^{I}$ it is trivial to see that all the players
-perform equally.
-\end{proof}
-
-\medskip{}
-
-\begin{lemma}
-In $\mathcal{G}^{W}$ RM is evolutionarily stable
-against MM, but MM is not evolutionarily stable against RM.
-\end{lemma}
-
-\begin{proof}
-Assume without loss of generality that $b=d$. We have
-two cases then: (i) $c<b=d$; (ii) $c>b=d$. In the first case it
-is easy to see that RM and MM perform equally well. Indeed, given
-(i) both MM and RM choose action $I$ if $a>c$, and action $II$
-if $c>a$. If case (ii) holds instead, we have that RM plays $I$
-if $a>c$ and $II$ if $c>a$ as before, but MM plays $(\frac{1}{2}I;\frac{1}{2}II)$,
-since both $I$ and $II$ maximize the minimal payoff. Consider now
-a population of RM and MM playing games from the class $\mathcal{G}^{W}$.
-Whenever (i) is the case both RM and MM perform equally. Suppose that
-(ii) is the case and that $a>c$, without loss of generality. Then,
-a RM population is evolutionarily stable against MM by condition 1
-of ESS, since $a>\frac{1}{2}a+\frac{1}{2}c$, whereas a MM population
-is not evolutionarily stable against RM, because clearly $\frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d<\frac{1}{2}a+\frac{1}{2}b$.
-Hence, we have that in general $EU_{\mathcal{G}^{W}}(RM,RM)>EU_{\mathcal{G}^{W}}(MM,RM),\mbox{ and }EU_{\mathcal{G}^{W}}(MM,MM)<EU_{\mathcal{G}^{W}}(RM,MM)$.
-\end{proof}
-
-\medskip{}
-
-Since it is not difficult to see that both RM and MM are evolutionarily
-stable in $\mathcal{G}^{C}$, and that both RM and MM are not evolutionarily
-stable in $\mathcal{G}^{A}$ against each other, the main part of
-the proof will be to show that RM is the only evolutionarily stable
-player in the class $\mathcal{G}^{C}\cup\mathcal{G^{A}}$, that is:
-\begin{itemize}
-\item[(i')] $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,RM)>EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,RM),$
-\item[(ii')] $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,MM)<EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,MM).$
-\end{itemize}
-
-\noindent This part needs some more lemmas to be proven, but firstly we introduce
-the following bijective function $\phi$ between coordination and
-anti-coordination games.
-
-\medskip{}
-
-\begin{definition}[$\phi$]
-$\phi:\mathcal{G}^{C}\rightarrow\mathcal{G^{A}}$,
-such that $\phi(a,b,c,d)=(c,d,a,b)$, is a bijection that for each
-coordination game $G^{C}\in\mathcal{G}^{C}$ with payoffs $(a^{G^{C}},b^{G^{C}},c^{G^{C}},d^{G^{C}})$
-gives the anti-coordination game $G^{A}\in\mathcal{G}^{A}$ with payoffs
-$(a^{G^{A}},b^{G^{A}},c^{G^{A}},d^{G^{A}})=(c^{G^{C}},d^{G^{C}},a^{G^{C}},b^{G^{C}})$.
-\end{definition}
-
-\medskip{}
-
-\begin{lemma}
-Let $P(E)$ be the probability of event $E$, then
-it holds that:
-\begin{itemize}
-\item $P(I_{G^{C}}^{RM})=P(II_{\phi(G^{C})}^{RM})$, and $P(II_{G^{C}}^{RM})=P(I_{\phi(G^{C})}^{RM})$;
-\item $P(I_{G^{C}}^{MM})=P(II_{\phi(G^{C})}^{MM})$, and $P(II_{G^{C}}^{MM})=P(I_{\phi(G^{C})}^{MM})$.
-\end{itemize}
-\end{lemma}
-
-\begin{proof}
-It is easy to check that if $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$,
-a RM player plays action $I$ in $G^{C}$; that if $b^{G^{C}}-d^{G^{C}}<c^{G^{C}}-a^{G^{C}}$,
-RM plays $II$; and that if $b^{G^{C}}-d^{G^{C}}=c^{G^{C}}-a^{G^{C}}$,
-a RM player is indifferent between $I$ and $II$ in $G^{C}$, and
-we assume that randomizes with $(\frac{1}{2}I;\frac{1}{2}II)$. Similarly,
-if $a^{G^{A}}-c^{G^{A}}>d^{G^{A}}-b^{G^{A}}$, a RM player plays action
-$I$ in $G^{A}$; if $a^{G^{A}}-c^{G^{A}}<d^{G^{A}}-b^{G^{A}}$, RM
-plays $II$; and if $a^{G^{A}}-c^{G^{A}}=d^{G^{A}}-b^{G^{A}}$, a
-RM player is indifferent between $I$ and $II$ in $G^{A}$, and randomizes
-with $(\frac{1}{2}I;\frac{1}{2}II)$. Consequently, if $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$,
-then $P(I_{G^{C}}^{RM})=1$, and by definition of $\phi$ we have
-$P(II_{\phi(G^{C})}^{RM})=1$. Likewise, if $b^{G^{C}}-d^{G^{C}}<c^{G^{C}}-a^{G^{C}}$,
-then $P(II_{G^{C}}^{RM})=1=P(I_{\phi(G^{C})}^{RM})$; and if $b^{G^{C}}-d^{G^{C}}=c^{G^{C}}-a^{G^{C}}$,
-then $P(I_{G^{C}}^{RM})=P(II_{G^{C}}^{RM})=\frac{1}{2}=P(II_{\phi(G^{C})}^{RM})=P(I_{\phi(G^{C})}^{RM})$. \\
-In the same way, in coordination games we have that if $b^{G^{C}}>c^{G^{C}}$,
-a MM player plays $I$; if $c^{G^{C}}>b^{G^{C}}$, a MM player plays
-$II$; and if $b^{G^{C}}=c^{G^{C}}$, MM is indifferent between $I$
-and $II$, and plays $(\frac{1}{2}I;\frac{1}{2}II)$. In anti-coordination
-games instead, if $a^{G^{A}}>d^{G^{A}}$, MM plays $I$; if $a^{G^{A}}<d^{G^{A}}$,
-MM plays $II$; if $a^{G^{A}}=d^{G^{A}}$, MM plays $(\frac{1}{2}I;\frac{1}{2}II)$.
-By definition of $\phi$: $P(I_{G^{C}}^{MM})=1=P(II_{\phi(G^{C})}^{MM})$
-if $b^{G^{C}}>c^{G^{C}}$; $P(II_{G^{C}}^{MM})=1=P(I_{\phi(G^{C})}^{MM})$
-if $c^{G^{C}}>b^{G^{C}}$; and $P(I_{G^{C}}^{MM})=P(II_{G^{C}}^{MM})=\frac{1}{2}=P(II_{\phi(G^{C})}^{MM})=P(I_{\phi(G^{C})}^{MM})$
-if $b^{G^{C}}=c^{G^{C}}$.
-\end{proof}
-
-\medskip{}
-
-\begin{lemma}
-$P(\phi(G^{C}))=P(G^{C})$.
-\end{lemma}
-
-\begin{proof}
-By definition, each game $G^{C}\equiv(a^{G^{C}},b^{G^{C}},c^{G^{C}},d^{G^{C}})$
-is such that $a^{G^{C}}>c^{G^{C}}$ and $d^{G^{C}}>b^{G^{C}}$, and
-each game $G^{A}\equiv(a^{G^{A}},b^{G^{A}},c^{G^{A}},d^{G^{A}})$
-is such that $a^{G^{A}}<c^{G^{A}}$ and $d^{G^{A}}>b^{G^{A}}$. Since
-$a,b,c,d$ come from i.i.d. sampling, by simple renaming of variables
-it is clear that the probability of $(a^{G^{C}},b^{G^{C}},c^{G^{C}},d^{G^{C}})$
-is equal to the probability of $(c^{G^{C}},d^{G^{C}},a^{G^{C}},b^{G^{C}})$.
-Hence, $P(\phi(G^{C}))=P(G^{C})$.
-\end{proof}
-
-\medskip{}
-
-\begin{lemma}
-It holds that:
-\begin{itemize}
-\item $a^{G^{C}}>d^{G^{C}}\rightarrow(I_{G^{C}}^{MM}\subset I_{G^{C}}^{RM})$;
-\item $a^{G^{C}}<d^{G^{C}}\rightarrow(II_{G^{C}}^{MM}\subset II_{G^{C}}^{RM})$;
-\item $a^{G^{C}}=d^{G^{C}}\rightarrow I_{G^{C}}^{MM}=I_{G^{C}}^{RM}$.
-\end{itemize}
-\end{lemma}
-
-\begin{proof}
-If $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$, RM plays
-$I$, and if $b^{G^{C}}-d^{G^{C}}=c^{G^{C}}-a^{G^{C}}$, RM plays
-$(\frac{1}{2}I;\frac{1}{2}II)$, whereas if $b^{G^{C}}>c^{G^{C}}$,
-MM plays $I$, and if $b^{G^{C}}=c^{G^{C}}$, MM plays $(\frac{1}{2}I;\frac{1}{2}II)$.
-Then, $I_{G^{C}}^{RM}$ implies that $b^{G^{C}}-d^{G^{C}}\geq c^{G^{C}}-a^{G^{C}}$,
-and $I_{G^{C}}^{MM}$ implies that $b^{G^{C}}\geq c^{G^{C}}$. Moreover,
-on the assumption that $a^{G^{C}}>d^{G^{C}}$, it is easy to check
-that $b^{G^{C}}\geq c^{G^{C}}$ implies $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$.
-Hence, in any $G^{C}$ with $a^{G^{C}}>d^{G^{C}}$ it holds that $I_{G^{C}}^{MM}\mbox{ implies }I_{G^{C}}^{RM}$,
-i.e., $a^{G^{C}}>d^{G^{C}}\rightarrow(I_{G^{C}}^{MM}\subseteq I_{G^{C}}^{RM})$.
-Instead, it is possible that $a^{G^{C}}>d^{G^{C}}$, $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$
-and $b^{G^{C}}<c^{G^{C}}$ hold simultaneously, so that $I_{G^{C}}^{MM}\nsupseteq I_{G^{C}}^{RM}$.
-Consequently: $a^{G^{C}}>d^{G^{C}}\rightarrow(I_{G^{C}}^{MM}\subset I_{G^{C}}^{RM})$.
-By symmetric argument it can be shown that $a^{G^{C}}<d^{G^{C}}\rightarrow(II_{G^{C}}^{MM}\subset II_{G^{C}}^{RM})$
-too. \\
-Finally, when $a^{G^{C}}=d^{G^{C}}$ it holds that: $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$
-iff $b^{G^{C}}>c^{G^{C}}$; $b^{G^{C}}-d^{G^{C}}<c^{G^{C}}-a^{G^{C}}$
-iff $b^{G^{C}}<c^{G^{C}}$; and $b^{G^{C}}-d^{G^{C}}=c^{G^{C}}-a^{G^{C}}$
-iff $b^{G^{C}}=c^{G^{C}}$. Hence, $a^{G^{C}}=d^{G^{C}}\rightarrow I_{G^{C}}^{MM}=I_{G^{C}}^{RM}$.
-\end{proof}
-
-\medskip{}
-
-We are now ready to prove that: 
-\begin{itemize}
-\item[(i')] $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,RM)>EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,RM);$
-\item[(ii')] $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,MM)<EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,MM).$
-\end{itemize}
-We can rewrite $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,RM)>EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,RM)$
-more explicitly as:
-
-\medskip{}
-
-\noindent $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{MM})\cdot d^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{MM})\cdot d^{A}]<\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{RM})\cdot d^{C}+P(I_{G^{C}}^{MM}\cap II_{G^{C}}^{RM})\cdot c^{C}+P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot b^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{MM}\cap I_{G^{A}}^{RM})\cdot a^{A}+P(II_{G^{A}}^{MM}\cap II_{G^{A}}^{RM})\cdot d^{A}+P(I_{G^{A}}^{MM}\cap II_{G^{A}}^{RM})\cdot c^{A}+P(II_{G^{A}}^{MM}\cap I_{G^{A}}^{RM})\cdot b^{A}]$
-
-\medskip{}
-
-\noindent Then, the next derivation follows. By Lemma 5 and 6, we can express
-everything in terms of $G^{C}$ only: 
-\begin{itemize}
-\item $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM})\cdot a^{A}+P(II_{G^{A}}^{RM})\cdot d^{A}]>\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot d^{A}+P(I_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot c^{A}+P(II_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot b^{A}]$
-\item $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}+P(II_{G^{C}}^{RM})\cdot c^{C}+P(I{}_{G^{C}}^{RM})\cdot b^{C}]>\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}]$
-\item $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}+P(II_{G^{C}}^{RM})\cdot c^{C}+P(I{}_{G^{C}}^{RM})\cdot b^{C}]>\sum_{G^{C}}P(G^{C})[a^{C}\cdot(P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))+b^{C}\cdot(P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))+c^{C}\cdot(P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))+d^{C}\cdot(P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]$
-\end{itemize}
-Now let us split into $a>d$ and $a<d$, and consider $a>d$ first.
-Notice that, by Lemma 7, the case $a=d$ is irrelevant in order to
-discriminate between RM and MM. If $a>d$, by Lemma 7 we can eliminate
-the cases where RM plays $II$ and MM plays $I$:
-\begin{itemize}
-\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}+P(II_{G^{C}}^{RM})\cdot c^{C}+P(I{}_{G^{C}}^{RM})\cdot b^{C}]>\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[a^{C}\cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+b^{C}\cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+c^{C}\cdot(P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))+d^{C}\cdot(P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]$
-\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}+P(II_{G^{C}}^{RM})\cdot c^{C}+P(I{}_{G^{C}}^{RM})\cdot b^{C}-a^{C}\cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})-b^{C}\cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})-c^{C}\cdot(P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))-d^{C}\cdot(P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]>0$
-\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[a^{C}\cdot(P(I_{G^{C}}^{RM})-P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))+b^{C}\cdot(P(I{}_{G^{C}}^{RM})-P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))+c^{C}\cdot(P(II_{G^{C}}^{RM})-P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})-P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))+d^{C}\cdot(P(II_{G^{C}}^{RM})-P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})-P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]>0$
-\end{itemize}
-By Lemma 7, it is easy to check that $P(I_{G^{C}}^{RM})-P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})=P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})$
-and $P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})=P(II_{G^{C}}^{RM})$.
-Consequently, we have:
-\begin{itemize}
-\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[a^{C}\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+b^{C}\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})-c^{C}\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})-d^{C}\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})]>0$
-\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[a^{G^{C}}-c^{G^{C}}]>\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[d^{G^{C}}-b^{G^{C}}]$.
-\end{itemize}
-\medskip{}
-
-\noindent We know that $I_{G^{C}}^{RM}$ implies that $b^{G^{C}}-d^{G^{C}}\geq c^{G^{C}}-a^{G^{C}}$,
-and $II_{G^{C}}^{MM}$ implies that $b^{G^{C}}\leq c^{G^{C}}$. From
-$b^{G^{C}}-d^{G^{C}}\geq c^{G^{C}}-a^{G^{C}}$, it is easy to see
-that $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[a^{G^{C}}-c^{G^{C}}]\geq\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[d^{G^{C}}-b^{G^{C}}]$
-holds. When the event $I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}$ obtains
-on the assumption that $a^{G^{C}}>d^{G^{C}}$, there are only three
-possible payoff orderings: $a>c\geq d>b$, $a>d>c>b$, and $a>d>c=b$.
-If games are randomly sampled from a finite set with i.i.d. values
-for $a,b,c$ and $d$, then $a>d>c=b$ occurs with positive probability,
-and the last formula of the derivation holds with strict inequality
-too. Hence, RM is evolutionarily stable when the value set for $a,b,c,d$
-is finite. \\
-If i.i.d. values are sampled from a compact and convex set instead,
-it is again easy to see that $\forall a,d,c\ \exists\epsilon$ such
-that $\forall b\in(d,d+\epsilon)$ the above formula holds with strict
-inequality. We can simply take $\epsilon\equiv\frac{a-c}{2}$, and
-the interval $(d,d+\epsilon)$ always has positive probability. Hence,
-RM is evolutionarily stable when the value set for $a,b,c,d$ is a
-compact and convex set too. \\
-Symmetrically, from $a<d$ in the above derivation we get:
-
-\medskip{}
-
-\noindent $\sum_{G_{a<d}^{C}}P(G_{a<d}^{C})\cdot P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot[d^{C}-b^{C}]>\sum_{G_{a<d}^{C}}P(G_{a<d}^{C})\cdot P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot[a^{C}-c^{C}]$
-
-\medskip{}
-
-\noindent and the same argument follows.
-
-\medskip{}
-
-The second half of the result is that MM is not evolutionarily stable
-against RM in $\mathcal{G}^{C}\cup\mathcal{G^{A}}$: $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,MM)<EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,MM)$.
-As before, we write it more explicitly as:
-
-\medskip{}
-
-\noindent $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{MM})\cdot d^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{MM})\cdot d^{A}]<\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{RM})\cdot d^{C}+P(I_{G^{C}}^{MM}\cap II_{G^{C}}^{RM})\cdot c^{C}+P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot b^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{MM}\cap I_{G^{A}}^{RM})\cdot a^{A}+P(II_{G^{A}}^{MM}\cap II_{G^{A}}^{RM})\cdot d^{A}+P(I_{G^{A}}^{MM}\cap II_{G^{A}}^{RM})\cdot c^{A}+P(II_{G^{A}}^{MM}\cap I_{G^{A}}^{RM})\cdot b^{A}]$.
-\medskip{}
-
-\noindent Similarly to the above derivation, in the end we get:
-
-\medskip{}
-
-\noindent $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot[c^{G^{C}}-a^{G^{C}}]<\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot[b^{G^{C}}-d^{G^{C}}]$.
-
-\medskip{}
-
-\noindent Finally, by the same argument as before we can conclude that MM is
-not evolutionarily stable against RM both when the value set for $a,b,c,d$
-is finite, and when the value set for $a,b,c,d$ is a compact and
-convex set. This concludes the proof. $\dashv$
-
-\printbibliography[heading=bibintoc]
-
-\newpage
-
-\section{Snippets}
-
-[More precisely, from the meta-game perspective many possible subjective
-transformations of the objective utility are eliminated by evolution, but we find some
-evolutionarily stable subjective utility maximizers whose utility does not coincide with the
-objective evolutionary utility. This result leaves some room in between the two extrema: we can
-understand rationality in a normative way, given by evolution, without having to discard all
-the possible subjective utility representations as irrational. CHANGE PLACE OF THIS MAYBE]
-
-\subsection{Version 2}
-
-The importance of aiming at a richer evolutionary game theory has been recently emphasized by many works in theoretical biology and behavioral ecology [Fawcett\&al., McNamara, etc.].
-The biological argument to embrace this goal is related to the criticisms towards the so-called behavioral gambit [Fawcett\&al.].
-The behavioral gambit denotes the standard approach in evolutionary game theory that puts the focus of attention on the expressed behavior, and neglects the underlying mechanisms that generate that behavior.
-From this point of view, the benefit and the reliability coming from the use of evolutionary game theory for biological purposes is also under attack.
-There are good reasons to claim that focusing on the general psychological mechanisms instead of on behavior itself as the phenotype under evolutionary selection can be more faithful and insightful for natural biology and ecology [Fawcett\&al.].
-Standard evolutionary game theory normally models the agents as playing a single fixed game, and as genetically predetermined to play fixed strategies, that consequently are the only target of natural selection in those frameworks.
-Standard models of evolutionary game theory cannot take charge of this shift of perspective until they will keep modelling a single game at a time, and until they will keep focusing on actions considered genetically encoded and fixed.
-''Instead we should expect animals to have evolved a set of psychological mechanisms which enable them to perform well on average across a range of different circumstances''[Fawcett\&al.].
-
-Attempts to overcome the behavioral gambit have recently been developed in economic literature too.
-In the last twenty years economists have been using evolutionary game-theoretical models to study evolution of preferences [cite], instead of evolution of behavior only.
-This approach is called indirect evolutionary approach, because players' behavior and actions stem from their subjective preferences, and it is aimed at investigating what subjective preferences are evolutionarily better off and robust with respect to natural selection.
-This shift from a direct evolutionary approach about observed actions and behavior to an indirect evolutionary approach takes only partly into account the behavioral gambit criticized by biologists and ecologists.
-The reason is that the models of evolution of preferences usually consider only one game at a time.
-This means that there is a single type of interaction that is supposed to drive the whole evolution of preferences: preferences are selected on the basis of one possible interaction only.
-Clearly, this approach does not take into consideration the variety of possible circumstances that animals are supposed to face during their lifetime.
-
-The meta-game model we propose pays heed to both components of the behavioral gambit.
-We retain the indirect evolutionary approach, but our agents in the population play over a class of possible games $\mathcal{G}$.
-In this way we explicitly model a range of different circumstances, as wished by theoretical biologists.
-Consequently, each agent in the population does not represent either a simple behavior or a subjective preference, but a more general player type that associates a subjective preference for each game in the class $\mathcal{G}$.
-The player type is supposed to encode the general psychological mechanisms that generate the behavior for any possible interaction in $\mathcal{G}$.
-These general psychological mechanisms then become the target of evolution, and they are selected based on the average fitness over a class of different interactions.
-
-In particular, in the following we mainly deal with two types of agents: players whose subjective preference coincides with the evolutionary fitness, and players whose subjective preference is defined in terms of regret.
-It turns out that psychological mechanisms and subjective conceptualizations based on regret can outperform more veridical conceptualizations coinciding with the evolutionary fitness.
-This is just an example of the kind of insights and results that we can gain by adopting a meta-game perspective and by shifting the focus of our attention to psychological mechanisms and subjective conceptualizations as the phenotype under selection.
-
--maybe to add: difference with learning. Fawcett\&al. talk more about differences in learning, whereas we model differences in subjective conceptualizations.
-
-[A pivotal element of economics and decision theory is the definition of rationality as
-maximization of subjective preferences.]
-
-\begin{itemize}
-\item We present an approach to studying evolutionary selection of \emph{choice principles},
-  i.e., ways of choosing consistently across several games. In other words, we would like to
-  look at the problem of ``rational choice'' from an evolutionary point of view: what choice
-  principles would be promoted, which demoted in evolutionary competition amongst each other?
-
-\item This depends on the environment; it depends on what choice situations occur how
-  frequently. Maybe some choice principle is better in some situations, while another one is
-  better in others.
-
-\item We argue that this ``meta-evolutionary'' approach could eventually help explain attested
-  deviations of human decision making from the classical ideal: choice behavior evolved to be
-  an ``ecologically rational'', near-optimal adaptation to the environment
-  \citep{Anderson1990:The-Adaptive-Ch,Anderson1991:Is-human-cognit,GigerenzerGoldstein1996:Reasoning-the-F,ChaterOaksford2000:The-Rational-An}. This
-  is inline with recent aspirations to provide an evolutionary rationale for decision making
-  processes
-  \citep[e.g.][]{HammersteinStevens2012:Six-Reasons-for,FawcettHamblin2013:Exposing-the-be}. Here,
-  we seek to contribute to the formal machinery, an extension of evolutionary game theory, that
-  allows to capture statistical properties of the environment
-  \citep[cf.][]{McNamara2013:Towards-a-Riche}.
-\end{itemize}
-
-\subsection{The environment: meta-games}
-
-\begin{itemize}
-\item imagine huge, virtually infinite population of agents, each carrying a choice principle
-\item agents play a randomly sampled game against a randomly sampled opponent
-\item fitness is based on the average payoff of choice principle A against choice principle B,
-  taken over arbitrary games $g$ and weighted their occurrence probability $P(g)$:
-  $\int_g P(g) \times U_g(\text{CP-A}, \text{CP-B}) \text{d}g$
-\item the occurrence probability of games $g$ is the ``environment'' and, possibly, impossible to
-  derive theoretically, or to measure empirically
-\item here, use a relatively neutral approach instead that is practicable:
-  \begin{itemize}
-  \item games are individuated by their payoff matrices (no framing effects or similar)
-  \item each entry in a payoff matrix is an i.~i.~d.~random variable
-    \begin{itemize}
-    \item approach still incorporates a bias (e.g., against strategic form representations of
-      sequential games)
-    \end{itemize}
-  \end{itemize}
-\item example: average payoffs from numerical simulation of ($2 \times 2$ symmetric games)
-\item example: average payoffs from numerical simulation of ($n \times n$ symmetric games, with
-  $n$ uniformly random (up to some upper-bound))
-\end{itemize}
-
 \end{document}

### 2015-08-21 code/solitary_decision.r

@@ -5,18 +5,18 @@ require('reshape2')
 
 max.t=10
 max.a=10
-n.rounds = 5000
+n.rounds = 10000
 
-p.trueL = 0
-a.bestL = 0
 n.tL = 0
 n.aL = 0
-a.brL = 0
-a.mrL = 0
 u.brL = 0
-u.mrL = 0                  
+u.mrL = 0
+u.mmL = 0                  
+
+pb <- txtProgressBar(max = n.rounds, style = 3)
 
 for (i in 1:n.rounds) {
+  setTxtProgressBar(pb, i)
   if (max.t > 2){
     n.t = sample(2:max.t,1) # number of states
   } else {
@@ -28,62 +28,35 @@ for (i in 1:n.rounds) {
     n.a = 2
   }
   u = matrix(sample(0:10,replace=TRUE,size=n.t*n.a),nrow=n.t,ncol=n.a) # utility matrix
-  p = rdirichlet(1,rep(1,n.t))[1,] # probabilities of states
+  p = rdirichlet(1,rep(1,n.t))[1,] # probabilities of states (subjective!!)
   # p = rep(1/n.t, n.t)
-  t = sample(1:n.t,1) # true state
-#   t = sample(1:n.t,1,prob=p) # true state, with bias
+  # t = sample(1:n.t,1) # true state
+  t = sample(1:n.t,1,prob=p) # true state, with bias
   # get best response
-  tmp = u * p
-  eu = sapply(1:n.a, function(x) sum(tmp[,x])) # expected utility
-  a.br = which.max(eu) # best response
+  eu = colSums(u * p) # expected utility
+  a.br = which(eu == max(eu)) # best responses (can be several)
   # get min-regret
   best.v = sapply(1:n.t, function(x) max(u[x,] )) # best value
-  best.a = sapply(1:n.t, function(x) u[x,which.max(u[x,])] ) # best act
   rgrt = sapply(1:n.a, function(x) max(best.v - u[,x])) # regret of each act
-  a.mr = which.min(rgrt) # act that minimizes regret 
+  a.mr = which(rgrt == min(rgrt)) # acts that minimize regret (can be several)
+  # get maximin security strategty
+  mins = sapply(1:n.a, function(x) min(u[,x])) # worst case for each act
+  a.mm = which(mins == max(mins))
   # record data
-  p.trueL[i] = p[t]
-  a.bestL[i] = which.max(u[t,])
[…]

### 2015-08-21 code/solitary_decision_data_analysis.r

@@ -1,0 +1,34 @@
+require('gtools') # for dirichlet distribution
+require('plyr') # to conveniently manipulate data frames
+require('ggplot2')
+require('reshape2')
+
+# load('data_solitary_decisions_10x10.RDATA')
+
+grandMeans = c(br = mean(data$u.br), mr = mean(data$u.mr), mm = mean(data$u.mm))
+show(grandMeans)
+
+means = ddply(data, .(data$n.t,data$n.a), summarise,
+              N = length(u.br),
+              mean.br= mean(u.br) ,
+              sd.br = sd(u.br),
+              mean.mr= mean(u.mr), 
+              sd.mr = sd(u.mr),
+              mean.mm= mean(u.mm), 
+              sd.mm = sd(u.mm),
+              best  = c("br", "mr", "mm")[which.max(c(mean(u.br), mean(u.mr), mean(u.mm)))],
+              worst = c("br", "mr", "mm")[which.min(c(mean(u.br), mean(u.mr), mean(u.mm)))])
+
+meansLong = melt(data = means, id.vars = c("data$n.t", "data$n.a"), measure.vars = c("mean.br", "mean.mr", "mean.mm"))
+colnames(meansLong)[1] = "n.t"
+colnames(meansLong)[2] = "n.a"
+
+
+meansPlot = ggplot(data = meansLong, aes(x = n.a, y = value, col = variable)) +
+  geom_line() + geom_point() + facet_wrap(~ n.t, nrow = 3)
+
+show(meansPlot)
+
+
+
+

### 2015-08-21 paper/paper.tex
minor edits

@@
   place when that is done
+\item an important ingredient in our argument pro regret is that radical uncertainty could be
+  exogenously given; as it stands this occurs rather ``suddenly'' in the paper and should
+  ideally be prepared and motivated earlier (e.g., in Sections 2 and 3)
+\item a major contribution of our paper is the ``meta-game'' approach, but in the current
+  version I feel that this is not stressed sufficiently; the introduction and the beginning of
+  section 3 could do a bit more to carve out this idea as something generally cool; especially
+  the formula from 3.4 could occur earlier (albeit in more general notation);
 \end{itemize}
@@
 regret types and veridical preference types, when paired with probabilistic belief types that
-maximize/minimize expectations, are behaviorally equivalent, \emph{no matter what they belief},
+maximize/minimize expectations, are behaviorally equivalent, \emph{no matter what they believe},
 as long as they belief the same. So, if learning, insight and statistical knowledge of a

### 2015-09-15 paper/paper.tex
Paolo added paragraphs on imprecise beliefs

@@
 
-In line with traditional evolutionary game theory, the idea of this work is to model a population of rather unsophisticated and myopic agents that possibly differ from each other with respect to two components: the player type and the epistemic type.
+Consider the following problem.
+I have, on the desk in front of me, a bag containing either red or black marbles.
+There is no further information about the distribution of the two colors.
+What is then the probability that I will draw a red marble?
+As in Walley91-96, we are not talking about physical probability, but rather about epistemic probability, i.e., the subjective probability that an agent would attribute to an event.
+In the literature there are two traditional ways of answering this kind of questions.
+According to standard Bayesianism, one should always be able to determine a precise betting rate (that immediately translates into a precise probability), which is fair, in the sense that the DM is indifferent between betting on or against red at the fair rate, and would bet on red at any rate that is more favourable than the fair rate and against red at any rate that is less favourable.
+In this case, a strict Bayesian, in the absence of any further information, would probably rely on the principle of insufficient reason and answer that the DM should have a uniform distribution that considers all the outcomes equipossible.
+\\
+The second answer involves imprecise probabilities and is related to the literature about uncertainty, or ambiguity.
+Many authors argued in favor of this kind of approach [e.g., Walley91-96, Levi74, GardenforsANDSahlin82].
+Since it is consistent with the information available that all the marbles are red, or that no marble is red, the resulting model should take it into account and specify a lower probability of red $\underline{P}(R)$ and an upper probability of red $\overline{P}(R)$ that define an interval of possible probabilistic beliefs [$\underline{P}(R), \overline{P}(R)$].
+Given the information available in this case we would have $\underline{P}(R)=0$ and $\overline{P}(R)=1$.
+This approach appears particularly relevant and appropriate in a game theoretical context.
+Indeed, in a recent paper [Battigalliet al.15] Battigalli et al.
+write
+\begin{quote}
+Such uncertainty is inherent in situations of strategic interaction. This is quite obvious when such situations have been faced only a few times.
+\end{quote}
+In decision theory, the imprecise probability model is in line with most of the representation results about uncertainty [GilboaSchmeidler89,KMM06], and seems justified by empirical observations too (see below).
+Walley91-96 is a seminal work in the area, and also introduces learning procedures to get useful inferences and narrow down the probability set [$\underline{P}(R), \overline{P}(R)$] after observing data.
+Since we want to study the evolution of meta-types, the present work does not address the probem of drawing inferences from observations, and we do not endow the players with any learning procedure yet.\\
+In line with traditional evolutionary game theory, the idea of this work is to model a population of rather unsophisticated and myopic agents.
+%that possibly differ from each other with respect to two components: the player type and the epistemic type.
+The players
+The players encode both a psychological subjective representation of the interaction (player type) and a conceptualization of uncertainty (epistemic type), but they are too simple to have any learning or belief updating procedure.
+From this point of view, we can take the learning process away from natural selection and focus on player types and epistemic types as the target of evolutionary pressure.
+
 In full generality, we think of an epistemic type as a general disposition to form beliefs about the co-player’s behavior.
 Players in the population obviously face uncertainty about the composition of the population that they are part of, and consequently about the type of co-player that they are randomly paired with at each round and about the co-player's actions.
-We represent this uncertainty that players entertain in two different ways, a probabilistic flat belief and a non-probabilistic belief.
-This amounts to having two different epistemic types $e$ in the population, $e \in \lbrace \overline{\mu}, \Delta(A_{-i}) \rbrace $, where $\overline{\mu}$ is the probabilistic type and $\Delta(A_{-i})$ is the non-probabilistic type, defined as follows:
+We represent this uncertainty by the use of both the approaches presented above: a uniform distribution and a probability set.
+This amounts to having two different epistemic types $e$ in the population, $e \in \lbrace \overline{\mu}, \Delta(A_{-i}) \rbrace $, where $\overline{\mu}$ stands for the uniform distribution and $\Delta(A_{-i})$ is the probability set, defined as follows:
 
@@
 Hence, we consider two possible epistemic states in the face of uncertainty.
-The epistemic type $\Delta(A_{-i})$ represents a situation of non-probabilistic radical uncertainty, where the players are not able to narrow down the set of probability distributions over the co-player's actions and they consider all of them as possible.
+The epistemic type $\Delta(A_{-i})$ represents a situation of non-Bayesian radical uncertainty, where the players are not able to narrow down the set of probability distributions to a single one and they consider all of them as possible.
 The other epistemic type $\overline{\mu}$ conceptualizes the uncertainty about the population by using the principle of insufficient reason and ascribes equal probability to all the possible alternatives.
-Both options are reasonable and justifiable ways to deal with situations of uncertainty [REFERENCES].
+As we have seen, both options are reasonable and justifiable ways to deal with situations of uncertainty [REFERENCES].
 \\
-Since for the moment we want to model populations of biologically unsophisticated players, we do not endow them with an effective learning procedure.
-Our players encode both a psychological subjective representation of the interaction (player type) and a conceptualization of uncertainty (epistemic type), but they are too simple to have any learning or belief updating procedure.
-From this point of view, we can take the learning process away from natural selection and focus on player types and epistemic types as the target of evolutionary pressure.
 
@@
 
-\noindent $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{MM})\cdot d^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{MM})\cdot d^{A}]<\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{RM})\cdot d^{C}+P(I_{G^{C}}^{MM}\cap II_{G^{C}}^{RM})\cdot c^{C}+P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot b^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{MM}\cap I_{G^{A}}^{RM})\cdot a^{A}+P(II_{G^{A}}^{MM}\cap II_{G^{A}}^{RM})\cdot d^{A}+P(I_{G^{A}}^{MM}\cap II_{G^{A}}^{RM})\cdot c^{A}+P(II_{G^{A}}^{MM}\cap I_{G^{A}}^{RM})\cdot b^{A}]$
-
+\noindent $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM})\cdot a^{A}+P(II_{G^{A}}^{RM})\cdot d^{A}]>\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot d^{A}+P(I_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot c^{A}+P(II_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot b^{A}]$
 \medskip{}
@@
 convex set. This concludes the proof. $\dashv$
+
+\textbf{Proof of Proposition 2.} First we prove that regret type is evolutionarily stable against altruistic type and that altruistic type is not evolutionarily stable against regret type, and second we show that regret type is evolutionarily stable against competitive type and that competitive type is not evolutionarily stable against regret type.
+We make use of the same partition of $\mathcal{G}$ introduced in the proof of Proposition 1.
+Again, to ease notation let us write ALT and COM in the place of $(\tau^{alt}, \Delta(A))$ and $(\tau^{com}, \Delta(A))$, respectively.
+
+\begin{lemma}
+In $\mathcal{G}^I$, RM and ALT perform equally well.
+\end{lemma}
+
+\begin{proof}
+Trivial.
+\end{proof}
+
+\begin{lemma}
+In $\mathcal{G}^S$, RM is evolutionarily stable against ALT, and ALT is not evolutionarily stable against RM. 
+\end{lemma}
+
+\begin{proof}
+Let us assume, without loss of generality, that $a>c$ and $b>d$.
+We already know that RM always plays the dominant action $I$, then a population of RM players always coordinates on $I$ with a payoff of $a$.
+It is possible instead that an ALT player plays the dominated action $II$, for instance when $2d > 2a$ and $2a < b+c$.
+Then, the payoff of an ALT invader against a population of RMs is $c$.
+Since $a>c$ by assumption, we get that a RM population cannot be invaded by ALT players in this case.
+When $b+c < 2a$ and $b+c < 2d$, ALT will play $(\frac{1}{2}I;\frac{1}{2}II)$ for an expected payoff of $\frac{1}{2} a + \frac{1}{2} c$.
+Since $a > \frac{1}{2} a + \frac{1}{2} c$, a population of RMs is evolutionarily stable against ALT.
+\\
+When $2d > 2a$ and $2a < b+c$, an ALT population plays action $II$ for a payoff of $d$, whereas a RM invader plays action $I$ for a payoff of $b$.
+By assumption $b>d$, hence a population of ALTs would not be evolutionarily stable in this case.
+When $b+c < 2a$ and $b+c < 2d$, the expected payoff of a population of ALTs is $\frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d$, while the expected payoff of a RM invader is $\frac{1}{2}a+\frac{1}{2}b$.
+Since $\frac{1}{2}a+\frac{1}{2}b > \frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d$, we have that an ALT population is not evolutionarily stable against RM.
+\end{proof}
+
+\begin{lemma}
+In $\mathcal{G}^W$, RM is evolutionarily stable against ALT, and ALT is not evolutionarily stable against RM. 
+\end{lemma}
+
+\begin{proof}
+Let us assume, WLOG, that $b=d$ and $a>c$.
+We know that RM always plays the (weakly) dominant action $I$.
+Again, a RM population always coordinates on $I$ for a payoff of $a$, whereas when $2d > 2a$ and $2a < b+c$ an ALT invader plays $II$.
+Then, the payoff of an ALT invader against a population of RMs is $c$.
+Since $a>c$ by assumption, we get that a RM population cannot be invaded by ALT players in this case.
+When $b+c < 2a$ and $b+c < 2d$, ALT plays $(\frac{1}{2}I;\frac{1}{2}II)$ for an expected payoff of $\frac{1}{2} a + \frac{1}{2} c$.
+Since $a > \frac{1}{2} a + \frac{1}{2} c$, a population of RMs is evolutionarily stable against ALT.
+\\
+When $2d > 2a$ and $2a < b+c$, an ALT population plays action $II$ for a payoff of $d$, whereas a RM invader plays action $I$ for a payoff of $b$.
+Since $b=d$, we have to check the second condition for ESS: an ALT against RM gets $c$, and RM against RM gets $a$.
+By assumption $a>c$, hence an ALT population would be invaded by RM players in this case.
+When $b+c < 2a$ and $b+c < 2d$, the expected payoff of a population of ALTs is $\frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d$, while the expected payoff of a RM invader is $\frac{1}{2}a+\frac{1}{2}b$.
+Since $\frac{1}{2}a+\frac{1}{2}b > \frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d$, we again have that an ALT population is not evolutionarily stable against RM.
+\end{proof}
+
+\begin{lemma}
+In $\mathcal{G}^C$, RM is evolutionarily stable against ALT, and ALT is not evolutionarily stable against RM. 
+\end{lemma}
+
+\begin{proof}
+Let's assume, WLOG, that $a>d$.
+We know that RM plays $I$ if $ a-c > d-b $ and $II$ if $ a-c < d-b $, whereas  ALT plays $I$ if $2d<b+c$, otherwise ALT plays $(\frac{1}{2}I;\frac{1}{2}II)$.
+If $2d<b+c$, then $d-b<c-d$, hence $c>d$.
+Consequently, when $2d<b+c$ the expected payoff of an ALT population is $a$
+\end{proof}
 

### 2015-09-15 paper/paper.tex
rewrite section 2

@@
 %\usepackage[natbib=true,style=authoryear-comp,backend=bibtex,doi=false,url=false]{biblatex}
-\bibliography{helpers/MyRefLocal}
+% \bibliography{helpers/MyRefLocal}
+\bibliography{MyRefGlobal}
 \usepackage{helpers/myenvironments}
@@
 \author{Paolo Galeazzi \& Michael Franke}
-\date{current version: August 21st 2015}
+\date{current version: September 15th 2015}
 
@@
 
-\section{Rationality, subjectivity  \& subjective regret}
+\section{Rationality, subjectivity, beliefs \& preferences}
 \label{sec:rati--subj}
 
-\todo[inline]{would it make sense to tighten and restructure this section a little bit? what
-  about this: rationality says \emph{if} utils, beliefs and rational, then choose this; utils
-  and beliefs are unobservable; in some case utils and preferences \emph{can} be tight to the
-  environment (probability of a fair coin landing heads), in others no (probability of life on
-  Mars); if tight to environment its frequencies and fitness that would pin down a norm for
-  rational behavior, otherwise there's the danger of redescriptionism (just find some belief
-  and preference that rationalizes observed behavior); \dots }
-
-The standard definition of \textit{rationality} in economics and decision theory says that
-choice is rational only if it maximizes (subjective) expected utility. Since the work by vNM
-[cite], this view has been justified from the ``intuitive rationality'' of the axioms on the
-subjective preference relation leading to the representability of the decision maker as an
-expected utility maximizer. \todo{include axioms, or at least those that are mentioned as
-  relevant later} While in the axiomatization by [vNM] the probability of the outcomes is
-objectively given a priori, Savage54 provides a larger set of axioms that represent the
-decision maker (DM) with both a subjective utility over outcomes \textit{and} a
-\textit{subjective} probability over states of the world. Savage's axioms constitute the
-foundation of subjective expected utility (SEU) theory, that is normally assumed to define the
-rational behavior of economic agents.
+The standard textbook definition of \textit{rationality} in economics and decision theory
+traces back to the seminal work of \citet{Neumannvon-NeumannMorgenstern1944:Theory-of-Games}
+and \citet{Savage1954:The-Foundations}. It says that choice is rational only if it maximizes
+(subjective) expected utility.
+
+\begin{definition}[Rational choice from maximization of expected utility] Let $S$ be a (finite)
+  set of states of the world and $A$ a (finite) set of actions. Given a probability
+  distribution $P$ over $S$ and a utility function
+  $u \mycolon S \times A \rightarrow \mathbb{R} $, an action $a^* \in A$ is a rational choice
+  only if it maximizes the \emph{(subjective) expected utility}
+  $\EU(a^*) = \sum_{s \in S} P(s) \ u(s, a^*)$: $a^* \in \text{argmax}_{a_i \in A} \EU(a^*)
+  $. \todo{Give finite formulation? Everything we do here is finite}
+\end{definition}
+
+\noindent Expected utility is subjective in the sense that it is a function of subjective
+preferences and subjective beliefs of the decision maker (DM). To wit, a choice can be
+rational, i.e., the best choice from the DM's point of view, even if based on peculiar beliefs
+and/or aberrant preferences. (Indeed, while
+\citeauthor{Neumannvon-NeumannMorgenstern1944:Theory-of-Games} assumed that probabilities were
+objectively given, it was \citet{Savage1954:The-Foundations} who famously extended von Neumann
+and Morgenstern's axiomatization to include a subjective notion of probabilistic beliefs on top
+of the subjective notion of preference that von Neumann and Morgenstern started out with.)
+
+If beliefs and preferences are subjective, there is room for \emph{rationalization} or
+\emph{redescriptionism} of observable behavior. Prospect theory is, perhaps, the most prominent
+example. \citet{KahnemannTversky1979:Prospect-Theory} looked at experimental data from human
+choices in suitably defined tasks and demonstrated that what appears to be violations of
+rationality norms can be explained as rational on the assumption that subjects' beliefs and
+preferences deviate systematically from the objectively given parameters in the presented
+choice task (e.g., by taking into account reference points and diminishing returns for both
+gains and losses). Similarly, tinkering with the notion of subjective utility, in particular by
+including social preferences such as fairness, reciprocity or similar, allows us to describe as
+rational empirically observed behavior in social dilemmas, such as the prisoners' dilemma or
+public goods games, that might otherwise appear irrational (e.g. Fehr and Schmidt, Charness and
+Rabin, etc.).\todo{@Paolo: please include proper references}
+
+It could be objected that, without additional constraints, the notion of rationality is likely
+to collapse, as it seems possible to deem rational everything that is observed, given the
+freedom to adjust beliefs and preferences freely. Of course, there are many ways in which
+ascription of beliefs and preferences is constrained further by normative considerations of
+rationality. \todo{speak about Dutch books here?} To begin with, if the DM's uncertainty is
+about objective chance, it can be argued that subjective beliefs should conform (at least
+roughly) to objective chance. Similarly, in certain situations it may make sense to postulate
+on normative grounds that subjective preferences should be oriented towards tracking objective
+utility. For instance, in their classic work \myalert{(Alchian, Friedman)} argue that profit
+maximization is a reasonable assumption for characterizing outcomes in a competitive market
+because only firms behaving in a manner that is consistent with profit maximization will
+survive in the long run.\todo{@Paolo: please add references}
+
+An alternative to descriptive vs.~normative views on rationality is \emph{adaptationism}
+\citep[e.g.][]{HagenChater2012:Decision-Making}. \todo{more references} Adaptationism aims to
+explain choice behavior by appeal to evolutionary considerations. The key idea is that we
+should see decision makers (human and other life forms) as having evolved mechanisms for
+choosing that were fitness enhancing (in the relevant domains of choice making, at the relevant
+time of evolution). When it comes to preferences, this is clearly related to Alchian and
+Friedman's argument that firms \emph{should} optimize that which makes them ``live,'' so to
+speak. For biological agents, the argument would be that subjective preferences \emph{should}
+track whatever determines objective fitness.
+
+Taking inspiration from recent economic literature on the evolution of preference, we would
+like to put this latter idea to the test. We
+
+\bigskip
+
+ Since the work by vNM [cite], this view has been justified from
+the ``intuitive rationality'' of the axioms on the subjective preference relation leading to
+the representability of the decision maker as an expected utility maximizer. \todo{include
+  axioms, or at least those that are mentioned as relevant later} While in the axiomatization
+by [vNM] the probability of the outcomes is objectively given a priori, Savage54 provides a
+larger set of axioms that represent the decision maker (DM) with both a subjective utility over
+outcomes \textit{and} a \textit{subjective} probability over states of the world. Savage's
+axioms constitute the foundation of subjective expected utility (SEU) theory, that is normally
+assumed to define the rational behavior of economic agents.
 

### 2015-10-03 paper/paper.tex
reshuffle first sections

@@
 \usepackage{todonotes}
+\usepackage{subcaption}
 
@@
 \author{Paolo Galeazzi \& Michael Franke}
-\date{current version: September 15th 2015}
+\date{current version: October 3rd 2015}
 
@@
   only if it maximizes the \emph{(subjective) expected utility}
-  $\EU(a^*) = \sum_{s \in S} P(s) \ u(s, a^*)$: $a^* \in \text{argmax}_{a_i \in A} \EU(a^*)
-  $. \todo{Give finite formulation? Everything we do here is finite}
+  $\EU(a) = \sum_{s \in S} P(s) \ u(s, a)$: $a^* \in \text{argmax}_{a \in A} \EU(a)
+  $.
 \end{definition}
@@
 choice task (e.g., by taking into account reference points and diminishing returns for both
-gains and losses). Similarly, tinkering with the notion of subjective utility, in particular by
-including social preferences such as fairness, reciprocity or similar, allows us to describe as
-rational empirically observed behavior in social dilemmas, such as the prisoners' dilemma or
+gains and losses).  Similarly, tinkering with the notion of subjective utility, in particular
+by including social preferences such as fairness, reciprocity or similar, allows us to describe
+as rational empirically observed behavior in social dilemmas, such as the prisoners' dilemma or
 public goods games, that might otherwise appear irrational (e.g. Fehr and Schmidt, Charness and
@@
 about objective chance, it can be argued that subjective beliefs should conform (at least
-roughly) to objective chance. Similarly, in certain situations it may make sense to postulate
-on normative grounds that subjective preferences should be oriented towards tracking objective
-utility. For instance, in their classic work \myalert{(Alchian, Friedman)} argue that profit
-maximization is a reasonable assumption for characterizing outcomes in a competitive market
-because only firms behaving in a manner that is consistent with profit maximization will
-survive in the long run.\todo{@Paolo: please add references}
+roughly) to objective chance. When the DM's uncertainty cannot be anchored in an objective
+notion of chance, then temporal consistency in his decision making should at least constrain
+his subjective belief, else he fall prey to exploitation by Dutch books. Similarly, in certain
+situations it may make sense to postulate on normative grounds that subjective preferences
+should be oriented towards tracking objective utility, e.g., fitness. For instance, in their
+classic work \myalert{(Alchian, Friedman)} argue that profit maximization is a reasonable
+assumption for characterizing outcomes in a competitive market because only firms behaving in a
+manner that is consistent with profit maximization will survive in the long run.\todo{@Paolo:
+  please add references}
 
@@
 Taking inspiration from recent economic literature on the evolution of preference, we would
-like to put this latter idea to the test. We
-
-\bigskip
-
- Since the work by vNM [cite], this view has been justified from
-the ``intuitive rationality'' of the axioms on the subjective preference relation leading to
-the representability of the decision maker as an expected utility maximizer. \todo{include
-  axioms, or at least those that are mentioned as relevant later} While in the axiomatization
-by [vNM] the probability of the outcomes is objectively given a priori, Savage54 provides a
-larger set of axioms that represent the decision maker (DM) with both a subjective utility over
-outcomes \textit{and} a \textit{subjective} probability over states of the world. Savage's
-axioms constitute the foundation of subjective expected utility (SEU) theory, that is normally
-assumed to define the rational behavior of economic agents.
-
-\begin{definition}[SEU-maximization] Let $S$ be a set of states of the world, $X$ a set of
-  outcomes and $A$ a set of actions. Given a probability measure $P$ on $S$ and a subjective
-  utility function $u:X \rightarrow \mathbb{R} $, an action $a^*: S \rightarrow X $ is
-  SEU-maximizing if $a^* \in \text{argmax}_{a_i \in A} \int_S u(a^*(s))dP(s) $. \todo{do we
-    actually need outcomes for anything in this paper?}
-\end{definition}
-
-The subjectivity of preferences plays a very important
-role for the present work. From an agent's standpoint, the amount $x$ of, say, money achieved does not necessarily
-coincide with the amount of subjective utility attained $u(x)$. 
-Historically,  the first to notice and formally argue for this difference
-between objective utility (goods, money, etc.) and subjective utility (preferences) was
-D. Bernoulli with the famous St. Petersburg paradox in 1738. Moreover, Bernoulli introduced the idea that a good representation of
-subjective utility can be carried out in terms of an increasing concave function of objective
-utility. This can be considered the birth of modern decision theory.
-
-Empirically, many violations of Savage's (and vNM's) axioms have been consistently observed in behavioral economics.
-Most of the attention has been focused on the Independence Axiom and the Sure-thing Principle.
-Allais' paradox and Ellsberg's paradox are examples of violations of these two axioms, and they are at the origin of Prospect theory [cite] and ambiguity in decision theory [cite].
-
-The main idea behind Ellesberg's paradox and the literature on ambiguity is that DM treats differently objective and subjective uncertainty.
-If the probability measure on the possible states of the world is not given a priori and not ''known'', then observed preferences leave no room to represent  DM's beliefs via a probability measure on the possible states.
-The most common solution is then to represent DM's beliefs with a set of probability measures instead of a single one.
-
-Prospect theory was introduced by Kahnemann and Tversky in
-their famous paper from 1979. By means of experimental results they noticed that DM apparently acts as a risk averse agent with respect to gains and as a risk loving agent
-with respect to losses. Consequently, they conjectured that the subjective utility is better
-representable by an S-shaped utility function, concave in the positive domain of gains and
-convex in the negative domain of losses.
-
-More recently, other possible definitions of the subjective utility function have been proposed
-and justified from a game theoretical point of view (e.g. Fehr and Schmidt, Charness and Rabin,
-etc.). The central goal of these studies is to explain/describe the empirical behavior in social dilemmas
-(e.g., Prisoner's dilemma, public goods game, etc.). In the same spirit of Prospect theory, by means of different subjective utility
-functions it is possible to describe/match the behavior observed in game theoretical experiments and to
-explain it as rational (in the sense of maximizing the subjective utility).
-With this approach every behavior, no matter how far from the maximization of
-objective utility, can be deemed rational if we can only find a subjective utility that
-justifies that behavior as maximizing the subjective utility. The problem here is that it seems possible to consider rational everything
-that is observed, given the adequate subjective utility function. The notion
-of rationality almost collapses onto the observed behavior.
-
-On the other side, other economists (Alchian, Friedman) seem to link the notion of rational choice
-more tightly to the maximization of objective utility. In their classic works they argue that
-profit maximization is a reasonable assumption for characterizing outcomes in a competitive
-market because only firms behaving in a manner that is consistent with profit maximization will
-survive in the long run. If the previous accounts of rationality looked more descriptive, this
-definitely tastes more normative. In this sense, a normative notion of rationality would be tightly
-related to (and almost coincide with) the maximization of objective utility, which is supposed
-to drive the evolutionary process. It follows then that being normative in this sense points to an identification of rationality with maximization of objective utility.
-
-It seems that we are stuck between two extrema: a too permissive descriptivism and a too restrictive normativism. On the one hand, if we want to have a
-descriptive notion of rationality, then we can (almost) always define an appropriate
-subjective utility whose maximization matches the observed behavior. On the other hand, if we
-want to have a normative approach to rationality, then it seems we have to appeal to
-evolutionary arguments entailing the understanding of rationality as maximization of objective
-utility.
-
-However, it has been argued that in a good theory of choice and decision making the normative
-and the descriptive components should not come apart. For example, as Douglas Maclean [cite]
-writes:
-
-\todo[inline]{personally, not a big fan of extended quotes; talks: yes, papers: don't know; is
-  this dear to your heart? who's that Maclean anyway? ;-)}
-
-\begin{quote}
-The history of the subject reflects strong reasons why the theory of choice should have this dual character. [...] \\
-A normative theory of choice gains credibility from its predictive and explanatory power, for although empirical success itself may not constitute much of a normative argument, the theory of rational behavior is less likely to be found objectionable if rationality turns out to be widespread.
-[...] But if, on the other hand, the normative theory turns out to be incompatible with the best established behavioral theory, then the verification of the normative theory will depend entirely on the intrinsic plausibility of its axioms, and that appeal must be quite strong, strong enough to make us overcome our charitable reluctance to conclude that our actual behavior is systematically irrational.
-\end{quote}
-
-There is another violation of Savage's axioms that is particularly relevant for the present work: transitivity of preferences.
-The first of Savage's axioms states that the preference relation is a (total) preorder, i.e., reflexive and transitive.
-Moreover, the preorder axiom is often referred to as the rationality axiom [cite], as to suggest that it is somehow the core of rational preferences.
-Violations of transitivity have been observed and studied in experimental literature [citeTversky69,etc], but can also be supported from a normative and theoretical point of view.
-\\
-In what follows, an important focus of our work will be the role of regret in decision making.
-Regret theory predicts the violation of both transitivity and Independence of Irrelevant Alternatives (IIA).
-[CONNECTING TO Fawcett\&al: this is IIA, not independence]
+like to put this latter idea to the test. We present a formal argument intended to support two
+points: (i) subjective preferences that differ from objective fitness can be sustained and even
+be adaptive; this is brought to the foreground if we acknowledge that (ii) it is important to
+take into account the potential mutual dependence of subjective preferences and subjective
+beliefs in adaptationist approaches to decision making. More specifically, we show that
+subjective, non-veridical preference representations based on a notion of regret can be
+adaptive and even outperform objective, veridical representations of the actual fitness, when
+agents, at least on occasion, lack the ability to form reasonable probabilistic beliefs, in
+which case they hold imprecise probabilistic beliefs (CITE). The following Section~XYZ will
+introduce the basic notions needed for this argument, namely regret, imprecise probabilistic
+beliefs and security strategies.
+
+The method by which we want to advance our argument is to integrate ideas from the recent
+literature on preference evolution (CITE) with basic tenets of adaptationism: we are interested
+in studying the evolutionary competition of choice mechanism, conceived here as pairs of
+(general ways of) subjective preference and subjective belief
+representation. \textcolor{red}{EXAND}. This method is further detailed in
+Section~\ref{sec:model}.
+
+\section{Regret, imprecise probabilistic beliefs, choice mechanisms}
 
@@
 
-Regret theory has been introduced in decision theory by Savage [] and Niherens [], and later developed by Bell [1982], Loomes and Sugden [1982], and Fishburn [1982] independently.
-Lately, Halpern and Pass [cite] show how the use of regret minimization can solve game theoretical puzzles (like the Centipede and the Traveller's dilemma) in a way that is closer to everyday intuition and empirical data.
-In this paper the notion of regret is defined as in [HalPass12]:
-
-\begin{definition}[Pairwise regret] \label{defn:parwreg}
-Given a simultaneous-move game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the regret of player $i$ at profile $(a_i,a_{-i})$ is defined by: $\text{reg}(a_i,a_{-i}):= \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $, where $a_i^\$ \in A_i$ denotes $i$'s best reply to action $a_{-i} $.
-\end{definition}
-
-\begin{definition}[Regret] \label{defn:regret}
-Given a simultaneous-move game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the regret of an action $a_i \in A_i$ is defined by: $\text{reg}(a_i):= \text{max}_{a_{-i}\in A_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $.
-\end{definition}
-
-\begin{definition}[Regret minimization] \label{defn:regmin}
-Given a simultaneous-move game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, an action $a^{r}_i $ is regret minimizing if $a^{r}_i \in \text{min}_{a_i} \text{max}_{a_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $.
+\todo[inline]{this section starts off presupposing to much formal stuff for a philosophy
+  audience; we should first say why we look at games, then give the definition of a game, then
+  define regret, then example, ...}
+
+Regret theory has been introduced in decision theory by Savage [] and Niherens [], and later
+developed by Bell [1982], Loomes and Sugden [1982], and Fishburn [1982] independently. Lately,
+\citet{HalpernPass2012:Iterated-Regret} showed how the use of regret minimization can solve
+game theoretical puzzles (like the Centipede and the Traveller's dilemma) in a way that is
+closer to everyday intuition and empirical data. In this paper the notion of regret is defined
+as in \citet{HalpernPass2012:Iterated-Regret}:
+
+\begin{definition}[Regret, regret minimization] \label{defn:regret} Given a simultaneous-move
+  game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the regret of player $i$ at profile
+  $(a_i,a_{-i})$ is $\text{reg}(a_i,a_{-i}):= \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $, where
+  $a_i^\$ \in A_i$ denotes $i$'s best reply to action $a_{-i} $. The regret of an action
+  $a_i \in A_i$ is then
+  $\text{reg}(a_i):= \text{max}_{a_{-i}\in A_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $. An
+  action $a^{r}_i $ is regret minimizing if
+  $a^{r}_i \in \text{min}_{a_i} \text{max}_{a_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $.
 \end{definition}
@@
 \begin{figure}
-\begin{center}%
-\begin{tabular}{|c|c|c|}
+
+  \begin{subfigure}[b]{0.4\textwidth}
+    \centering
+    \begin{tabular}{ccc}
+      \toprule
+      & I & II \\
+      \midrule
+      I & 1;1 & 0;0 \\
       \hline 
- & I & II\tabularnewline
+      II & 0;0 & 2;2\\
+      \bottomrule
+    \end{tabular}
+    \caption{Coordination game $G^C$}
+    \label{coordgame1}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.4\textwidth}
+    \centering
+    \begin{tabular}{ccc}
+      \toprule
+      & I & II \\
+      \midrule
+      I & 0;0 & -2;-1 \\
       \hline 
-\hline 
-I & 1;1 & 0;0\tabularnewline
-\hline 
-II & 0;0 & 2;2\tabularnewline
-\hline 
-\end{tabular}\end{center}
-
-\protect\caption{A coordination game $G^C$}
-\label{coordgame1}
+      II & -1;-2 & 0;0\\
+      \bottomrule
+    \end{tabular}
+    \caption{Regret representation $\tau^{reg}(G^C)$}
+    \label{coordgame1reg}
+  \end{subfigure}
+  \caption{A coordination game (left) and its regret representation (right).}
+    \label{coordgame1mainFig}
 \end{figure}
@@
 
-The meta-game perspective that we introduce in this paper can shed more light on the duality of descriptivism and normativism, and opens
-some space in between the two extrema. 
-By keeping the evolutionary approach we want to retain a
-normative perspective on rationality, but our results show that (under certain conditions)
-evolution does not necessarily lead to identifying rationality with maximization of objective
-utility, contrary to the intuition of Alchian [cite] and Friedman [cite].
-
-In the following we mainly deal with two types of agents: players whose subjective utility is defined
-in terms of regret (as in DEFINITION), and players whose utility
-function coincides with the objective utility $\pi_i$.
-
-The justification for this choice is both historical and behavioral. Among
-the possible competitors of utility maximization, regret has always been in a prominent
-position, both from a descriptive and normative viewpoint. Indeed, Bell82 writes:
+\todo[inline]{add results about regret: reg min is security choice on negative regret transform
+(related to Figure 1b); regret choice equal to veridical in case of probabilistic beliefs and
+maximization of expected gains}
+
+\subsection{Imprecise probabilistic beliefs}
+\label{sec:impr-prob-beli}
+
+Consider the following problem.
+I have, on the desk in front of me, a bag containing either red or black marbles.
+There is no further information about the distribution of the two colors.
+What is then the probability that I will draw a red marble?
+As in Walley91-96, we are not talking about physical probability, but rather about epistemic probability, i.e., the subjective probability that an agent attributes to an event.
+In the literature there are two traditional ways of answering this kind of questions.
+According to standard Bayesianism, one should always be able to determine a precise betting rate (that immediately translates into a precise probability distribution), which is fair, in the sense that the DM is indifferent between betting on or against red at the fair rate, and would bet on red at any rate that is more favourable than the fair rate and against red at any rate that is less favourable.
+In this case, a strict Bayesian, in the absence of any further information, would probably rely on the principle of insufficient reason and answer that the DM should have a uniform distribution that considers all the outcomes equipossible.
+\\
+The second answer involves imprecise probabilities and is related to the literature about uncertainty, or ambiguity.
+Many authors argued in favor of this kind of approach [e.g., Walley91-96, Levi74, GardenforsANDSahlin82].
+Since it is consistent with the information available that all the marbles are red, or that no marble is red, the resulting model should take it into account and specify a lower probability of red $\underline{P}(R)$ and an upper probability of red $\overline{P}(R)$ that define an interval of possible probabilistic beliefs [$\underline{P}(R), \overline{P}(R)$].
+Given the information available in this case we would have $\underline{P}(R)=0$ and $\overline{P}(R)=1$.
+This approach appears particularly relevant and appropriate in a game theoretical context.
+Indeed, in a recent paper [Battigalliet al.15] Battigalli et al.
+write
 \begin{quote}
-  By explicitly incorporating regret, expected utility theory not only becomes a better
-  descriptive predictor but also may become a more convincing guide for prescribing behavior to
-  decision makers.
+Such uncertainty is inherent in situations of strategic interaction. This is quite obvious when such situations have been faced only a few times.
 \end{quote}
-In the same year, Graham Loomes and Robert Sugden \citet{LoomesSugden1982:Regret-Theory:-} show that a regret-based theory of choice can match
-and explain all the main experimental results of prospect theory, and claim that
-\begin{quote} [...] we shall challenge the idea that the conventional axioms [of decision
-  theory] constitute the only acceptable basis for rational choice under uncertainty. We shall
-  argue that it is no less rational to act in accordance with regret theory, and that
-  conventional expected utility theory therefore represents an unnecessarily restrictive notion
-  of rationality. \hfill \citep{LoomesSugden1982:Regret-Theory:-}
-\end{quote}
+In decision theory, the imprecise probability model is in line with most of the representation results about uncertainty [GilboaSchmeidler89,KMM06], and seems justified by empirical observations too (see below).
+Walley91-96 is a seminal work in the area, that also introduces learning procedures to get useful inferences and narrow down the probability set [$\underline{P}(R), \overline{P}(R)$] after observing data.
+Since we want to study the evolution of meta-types, the present work does not address the probem of drawing inferences from observations, and for the moment we do not endow the players with any learning procedure.\\
+In line with traditional evolutionary game theory, we model a population of rather unsophisticated and myopic agents.
+%that possibly differ from each other with respect to two components: the player type and the epistemic type.
+The players
+The players encode both a psychological subjective representation of the interaction (player type) and a conceptualization of uncertainty (epistemic type), but they are too simple to have any learning or belief updating procedure.
+From this point of view, we can take the learning process away from natural selection and focus on player types and epistemic types as the target of evolutionary pressure.
+
+In full generality, we think of an epistemic type as a general disposition to form beliefs about the co-player’s behavior.
+Players in the population obviously face uncertainty about the composition of the population that they are part of, and consequently about the type of co-player that they are randomly paired with at each round and about the co-player's actions.
+We represent this uncertainty by the use of both the approaches presented above: a uniform distribution and a probability set.
+This amounts to having two different epistemic types $e$ in the population, $e \in \lbrace \overline{\mu}, \Delta(A_{-i}) \rbrace $, where $\overline{\mu}$ stands for the uniform distribution and $\Delta(A_{-i})$ is the probability set, defined as follows:
+
+\begin{itemize}
+
+\item $ \Delta(A_{-i}):=\lbrace \mu \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu(a_{-i}) = 1 \rbrace$;
+
+\item $\overline{\mu} \in \lbrace \mu \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu(a_{-i}) = 1 \rbrace$ is the probability measure over the co-player's actions such that: $\forall a_{-i} \in A_{-i}$, $\overline{\mu}(a_{-i})= \frac{1}{|A_{-i}|}$.
+
+\end{itemize}
+
+Hence, we consider two possible epistemic states in the face of uncertainty.
+The epistemic type $\Delta(A_{-i})$ represents a situation of non-Bayesian radical uncertainty, where the players are not able to narrow down the set of probability distributions to a single one and they consider all of them as possible.
+The other epistemic type $\overline{\mu}$ conceptualizes the uncertainty about the population by using the principle of insufficient reason and ascribes equal probability to all the possible alternatives.
+As we have seen, both options are reasonable and justifiable ways to deal with situations of uncertainty [REFERENCES].
+\\
+
+\newpage
 
@@
 given by the player type and the set of priors given by the epistemic type.
-
-  \todo[inline]{I would like to suggest to move Figure 2 next to Figure 1; it is already useful
-  for example 1 and could be referred to there already; I would suggest to use subfigures to
-  put both next to each other}
 
@@
   maximizes objective utility given $\overline{\mu}$. In game $G^C$ this yields action $II$.
-
-\begin{figure}
-\begin{center}%
-\begin{tabular}{|c|c|c|}
-\hline 
- & I & II\tabularnewline
-\hline 
-\hline 
-I & 0;0 & -2;-1\tabularnewline
-\hline 
-II & -1;-2 & 0;0\tabularnewline
-\hline 
-\end{tabular}\end{center}
-
-\protect\caption{Regret representation $\tau^{reg}(G^C)$}
-\label{coordgame1reg}
-\end{figure}
 
@@
 
+\bigskip
+
+\begin{itemize}
+\item The meta-game perspective that we introduce in this paper can shed more light on the duality of descriptivism and normativism, and opens
+some space in between the two extrema. 
+By keeping the evolutionary approach we want to retain a
+normative perspective on rationality, but our results show that (under certain conditions)
+evolution does not necessarily lead to identifying rationality with maximization of objective
+utility, contrary to the intuition of Alchian [cite] and Friedman [cite].
+
+In the following we mainly deal with two types of agents: players whose subjective utility is defined
+in terms of regret (as in DEFINITION), and players whose utility
+function coincides with the objective utility $\pi_i$.
+
+The justification for this choice is both historical and behavioral. Among
+the possible competitors of utility maximization, regret has always been in a prominent
+position, both from a descriptive and normative viewpoint. Indeed, Bell82 writes:
+\begin{quote}
+  By explicitly incorporating regret, expected utility theory not only becomes a better
+  descriptive predictor but also may become a more convincing guide for prescribing behavior to
+  decision makers.
+\end{quote}
+In the same year, Graham Loomes and Robert Sugden \citet{LoomesSugden1982:Regret-Theory:-} show that a regret-based theory of choice can match
+and explain all the main experimental results of prospect theory, and claim that
+\begin{quote} [...] we shall challenge the idea that the conventional axioms [of decision
+  theory] constitute the only acceptable basis for rational choice under uncertainty. We shall
+  argue that it is no less rational to act in accordance with regret theory, and that
+  conventional expected utility theory therefore represents an unnecessarily restrictive notion
+  of rationality. \hfill \citep{LoomesSugden1982:Regret-Theory:-}
+\end{quote}
+\end{itemize}
+
 \end{document}

### 2015-10-04 paper/paper.tex
minor edits

@@
 
-\begin{definition}[Rational choice from maximization of expected utility] Let $S$ be a (finite)
-  set of states of the world and $A$ a (finite) set of actions. Given a probability
-  distribution $P$ over $S$ and a utility function
+\begin{definition}[Rational choice from maximization of expected utility]
+  \label{def:rationality}
+  Let $S$ be a (finite) set of states of the world and $A$ a (finite) set of actions. Given a
+  probability distribution $P$ over $S$ and a utility function
   $u \mycolon S \times A \rightarrow \mathbb{R} $, an action $a^* \in A$ is a rational choice
   only if it maximizes the \emph{(subjective) expected utility}
-  $\EU(a) = \sum_{s \in S} P(s) \ u(s, a)$: $a^* \in \text{argmax}_{a \in A} \EU(a)
-  $.
+  $\EU(a) = \sum_{s \in S} P(s) \ u(s, a)$: $a^* \in \text{argmax}_{a \in A} \EU(a) $.
 \end{definition}
@@
 ascription of beliefs and preferences is constrained further by normative considerations of
-rationality. \todo{speak about Dutch books here?} To begin with, if the DM's uncertainty is
-about objective chance, it can be argued that subjective beliefs should conform (at least
-roughly) to objective chance. When the DM's uncertainty cannot be anchored in an objective
-notion of chance, then temporal consistency in his decision making should at least constrain
-his subjective belief, else he fall prey to exploitation by Dutch books. Similarly, in certain
-situations it may make sense to postulate on normative grounds that subjective preferences
-should be oriented towards tracking objective utility, e.g., fitness. For instance, in their
-classic work \myalert{(Alchian, Friedman)} argue that profit maximization is a reasonable
-assumption for characterizing outcomes in a competitive market because only firms behaving in a
-manner that is consistent with profit maximization will survive in the long run.\todo{@Paolo:
-  please add references}
+rationality. To begin with, if the DM's uncertainty is about objective chance, it can be argued
+that subjective beliefs should conform (at least roughly) to objective chance. When the DM's
+uncertainty cannot be anchored in an objective notion of chance, then temporal consistency in
+his decision making should at least constrain his subjective beliefs, else he fall prey to
+exploitation by Dutch books. Similarly, in certain situations it may make sense to postulate on
+normative grounds that subjective preferences should be oriented towards tracking objective
+utility, e.g., fitness. For instance, in their classic work \myalert{(Alchian, Friedman)} argue
+that profit maximization is a reasonable assumption for characterizing outcomes in a
+competitive market because only firms behaving in a manner that is consistent with profit
+maximization will survive in the long run.\todo{@Paolo: please add references}
 
@@
 \citep[e.g.][]{HagenChater2012:Decision-Making}. \todo{more references} Adaptationism aims to
-explain choice behavior by appeal to evolutionary considerations. The key idea is that we
-should see decision makers (human and other life forms) as having evolved mechanisms for
-choosing that were fitness enhancing (in the relevant domains of choice making, at the relevant
-time of evolution). When it comes to preferences, this is clearly related to Alchian and
-Friedman's argument that firms \emph{should} optimize that which makes them ``live,'' so to
-speak. For biological agents, the argument would be that subjective preferences \emph{should}
-track whatever determines objective fitness.
-
-Taking inspiration from recent economic literature on the evolution of preference, we would
-like to put this latter idea to the test. We present a formal argument intended to support two
-points: (i) subjective preferences that differ from objective fitness can be sustained and even
-be adaptive; this is brought to the foreground if we acknowledge that (ii) it is important to
-take into account the potential mutual dependence of subjective preferences and subjective
-beliefs in adaptationist approaches to decision making. More specifically, we show that
-subjective, non-veridical preference representations based on a notion of regret can be
-adaptive and even outperform objective, veridical representations of the actual fitness, when
-agents, at least on occasion, lack the ability to form reasonable probabilistic beliefs, in
-which case they hold imprecise probabilistic beliefs (CITE). The following Section~XYZ will
-introduce the basic notions needed for this argument, namely regret, imprecise probabilistic
-beliefs and security strategies.
+explain choice behavior by appeal to evolutionary considerations. The key idea is that decision
+makers (human and other life forms) have evolved choice mechanisms which were fitness enhancing
+(in the relevant domains of choice making, at the relevant time of evolution). When it comes to
+preferences, this is clearly related to Alchian and Friedman's argument that firms
+\emph{should} optimize that which makes them ``live,'' so to speak. For biological agents, the
+argument would be that subjective preferences \emph{should} track whatever determines objective
+fitness.
+
+We would like to put this latter idea to the test. We present a formal argument intended to
+support the conclusion that subjective preferences that differ from objective fitness can be
+adaptive. This is brought to the foreground if we acknowledge the potential mutual dependence
+of subjective preferences and subjective beliefs in adaptationist approaches to decision
+making. More specifically, we show that subjective, non-veridical preference representations
+based on a notion of regret
+\citep[e.g.][]{Savage1951:The-theory-of-s,LoomesSugden1982:Regret-Theory:-}\todo{add
+  references?}\ can be adaptive and even outperform objective, veridical representations of the
+actual fitness, when agents, at least on occasion, hold imprecise probabilistic beliefs
+(CITE).
 
@@
 in studying the evolutionary competition of choice mechanism, conceived here as pairs of
-(general ways of) subjective preference and subjective belief
-representation. \textcolor{red}{EXAND}. This method is further detailed in
-Section~\ref{sec:model}.
-
-\section{Regret, imprecise probabilistic beliefs, choice mechanisms}
-
-\subsubsection{Regret theory} \label{sec:regreTheory}
+subjective preference and subjective belief representation. Evolutionary competition between
+choice mechanisms is driven by the expected objective fitness that each choice mechanisms
+accrues when put to use repeatedly in a range of choice situations. We focus on the more
+complex case of multi-agent decision making first, i.e., game situations. Solitary decision
+making is then easy to deal with subsequently.
+
+The following Section~XYZ will introduce the basic notions needed in the remainder. Section~XYZ
+details our method of using ``meta-games''. \dots
+
+\section{Basic notions}
+\label{sec:basic-notions}
+
+A strategic game is a tuple $ G=\tuple{ N, (A_i , \pi_i)_{i \in N} }$ with $N$ a set of
+players, $A_i$ a set of acts and $\pi_i$ a payoff function for each player $i \in N$. The
+classical notion of rationality from Definition~\ref{def:rationality} also applies to
+games. Let $A_{-i} = \bigtimes A_j$ for all $j \neq i$ be the set of all profiles of acts for
+all players excepts $i$. Then player $i$ has a belief $\Delta(A_{-i})$ about the behavior of
+his opponents.
+
+\subsection{Regret theory} \label{sec:regreTheory}
 

### 2015-10-04 paper/paper.tex
minor edits

@@
 
+\subsection{Games} \label{sec:games}
+
 A strategic game is a tuple $ G=\tuple{ N, (A_i , \pi_i)_{i \in N} }$ with $N$ a set of
@@
 games. Let $A_{-i} = \bigtimes A_j$ for all $j \neq i$ be the set of all profiles of acts for
-all players excepts $i$. Then player $i$ has a belief $\Delta(A_{-i})$ about the behavior of
-his opponents.
+all players excepts $i$. If player $i$ has a belief $\mu_i \in \Delta(A_{-i})$ about the
+behavior of his opponents, he chooses rationally only his choice $a^*_i$ maximizes expected
+utility $\EU(a) = \sum_{a_{-i} \in A_{-i}} \mu_i \myts \pi_i(a_i, a_{-i})$.
+
+We focus here on symmetric games with two players. A two-player game is symmetric if An example
+is given in Figure~\ref{coordgame1}. \textcolor{red}{EXPAND}
+
+\begin{itemize}
+\item include here: minimax and choice given a belief
+\end{itemize}
+
+\todo[inline]{should we define NE, ESS/NSS here? dominance? we should include \emph{best
+    reply}, because it is used in the definition of regret.}
 
 \subsection{Regret theory} \label{sec:regreTheory}
-
-\todo[inline]{this section starts off presupposing to much formal stuff for a philosophy
-  audience; we should first say why we look at games, then give the definition of a game, then
-  define regret, then example, ...}
 
@@
 \begin{example}[Coordination Game]
-  Let us consider the coordination game in Figure \ref{coordgame1}. It is easy to see that
-  $\text{reg}(I)=2$: when the other player chooses action $I$ the regret of $I$ is $0$ since
-  $I$ is a best reply to $I$, and when the other player chooses $II$ the regret of $I$ is $2$
-  since $\pi_i(II,II)-\pi_i(I,II)=2$. With the same reasoning, $\text{reg}(II)=1$. Two regret
-  minimizing players would then choose action $II$, each getting a payoff of $2$. In this case
-  regret minimization selects the Pareto-dominant Nash equilibrium. $ \medsquare $
+  Let us consider the coordination game in Figure \ref{coordgame1}. Figure~\ref{coordgame1reg}
+  shows the pairwise regrets and the regrets of each row-player action. It is easy to see that
+  $\text{reg}(I)=2$: when the other player chooses action $I$ the pairwise regret $reg(I,I)$ is
+  $0$ since $I$ is a best reply to $I$, and when the other player chooses $II$ the pairwise
+  regret $reg(I, II)$ is $2$ since $\pi_i(II,II)-\pi_i(I,II)=2$. With the same reasoning,
+  $\text{reg}(II)=1$. Two regret minimizing players would then choose action $II$, each getting
+  a payoff of $2$. In this case regret minimization selects the Pareto-dominant Nash
+  equilibrium.\todo{explain Pareto-dominant NE; otherwise skip it?} $ \medsquare $
 
@@
 
-  \begin{subfigure}[b]{0.4\textwidth}
+  \begin{subfigure}[b]{0.3\textwidth}
     \centering
@@
       \midrule
-      I & 1;1 & 0;0 \\
-      \hline 
-      II & 0;0 & 2;2\\
+      I & 1 & 0 \\
+      II & 0 & 2\\
       \bottomrule
@@
   \end{subfigure}
-  \hfill
-  \begin{subfigure}[b]{0.4\textwidth}
+  \hspace{1cm}
+  \begin{subfigure}[b]{0.5\textwidth}
     \centering
-    \begin{tabular}{ccc}
+    \begin{tabular}{cccc}
       \toprule
-      & I & II \\
+      & $reg( \cdot, I)$ & $reg(\cdot, II)$ & $reg(\cdot)$ \\
       \midrule
-      I & 0;0 & -2;-1 \\
-      \hline 
-      II & -1;-2 & 0;0\\
+      I  & 0 & 2 & 2 \\ 
+      II & 1 & 0 & 1\\
       \bottomrule
     \end{tabular}
-    \caption{Regret representation $\tau^{reg}(G^C)$}
+    \caption{Pairwise regrets representation $\tau^{reg}(G^C)$}
     \label{coordgame1reg}
   \end{subfigure}
-  \caption{A coordination game (left) and its regret representation (right).}
+  \caption{A coordination game (left) and regrets associated with each row-player actions (right).}
     \label{coordgame1mainFig}

### 2015-10-04 paper/paper.tex
restructuring and minor edits

@@
 
-We focus here on symmetric games with two players. A two-player game is symmetric if An example
-is given in Figure~\ref{coordgame1}. \textcolor{red}{EXPAND}
-
-\begin{itemize}
-\item include here: minimax and choice given a belief
-\end{itemize}
+We focus here on symmetric games with two players. A two-player game is symmetric if players
+have the same action set, $A_1 = A_2$, and payoffs are symmetric:
+$\pi_1(\myact{k}, \myact{l}) = \pi_2(\myact{l}, \myact{k})$ for all $k$ and $j$. An example is
+given in Figure~\ref{coordgame1}, which shows a coordination game. The numbers give the payoff
+for player choosing the row against an opponent who chooses the column acts. Since the game is
+symmetric, it suffices to give just these numbers. A rational player would choose $I$ exactly
+when he beliefs that his opponent will choose $I$ with a probability at least
+$\nicefrac{2}{3}$.
+
+If an agent does not have a concrete probabilistic belief, the \emph{minimax rule} would tell
+him to choose act $\act^*$ only if it maximizes payoffs for all worst case scenarios, i.e.,
+$\act^* \in \argmax_{\myact{i} \in \Acts_i} \min_{\myact{j} \in \Acts_j} \pi_i(\myact{i},
+\myact{j})$.
+Yet another option is to follow \emph{Laplace's rule} which is to choose $\act^*$ only if
+$\act^* \in \argmax_{a \in A}  \sum_{a'} \pi(a, a')$. Laplace's rule is to rationally choosing under a
+\emph{flat belief} that assigns equal probability to all of the opponent's choices.
 

### 2015-10-05 paper/paper.tex
sec 2 eddits

--- 2015-10-04 paper/paper.tex
@@
 A strategic game is a tuple $ G=\tuple{ N, (A_i , \pi_i)_{i \in N} }$ with $N$ a set of
-players, $A_i$ a set of acts and $\pi_i$ a payoff function for each player $i \in N$. The
-classical notion of rationality from Definition~\ref{def:rationality} also applies to
-games. Let $A_{-i} = \bigtimes A_j$ for all $j \neq i$ be the set of all profiles of acts for
-all players excepts $i$. If player $i$ has a belief $\mu_i \in \Delta(A_{-i})$ about the
-behavior of his opponents, he chooses rationally only his choice $a^*_i$ maximizes expected
-utility $\EU(a) = \sum_{a_{-i} \in A_{-i}} \mu_i \myts \pi_i(a_i, a_{-i})$.
-
-We focus here on symmetric games with two players. A two-player game is symmetric if An example
-is given in Figure~\ref{coordgame1}. \textcolor{red}{EXPAND}
-
-\begin{itemize}
-\item include here: minimax and choice given a belief
-\end{itemize}
-
-\todo[inline]{should we define NE, ESS/NSS here? dominance? we should include \emph{best
-    reply}, because it is used in the definition of regret.}
+players, $A_i$ a set of acts and $\pi_i$ a payoff function for each player $i \in N$. For the
+most part, this paper will focus on symmetric games with two players. A two-player game is
+symmetric if players have the same action set, $A_1 = A_2$, and payoffs are symmetric:
+$\pi_1(\myact{k}, \myact{l}) = \pi_2(\myact{l}, \myact{k})$ for all $k$ and $j$. An example is
+given in Figure~\ref{coordgame1}, which shows a coordination game. The numbers give the payoff
+for the player choosing the row against an opponent who chooses the column acts. Since the game
+is symmetric, it suffices to give just these numbers.
+
+With some due simplification, there are two types of approaches to solving games: one focuses
+on the individual agents' perpectives and gives \emph{choice rules}, another considers sets of
+choices of all agents that are, in some sense or other, locked-in. Let's look at either in
+turn, to the extent necessary for this paper:
+
+\paragraph{Choice rules.} The classical notion of rationality from
+Definition~\ref{def:rationality} also applies to games. Let $A_{-i} = \bigtimes A_j$ for all
+$j \neq i$ be the set of all profiles of acts for all players except $i$. If player $i$ has a
+belief $\mu_i \in \Delta(A_{-i})$ about the behavior of his opponents, he chooses rationally
+only if his choice $a^*_i$ maximizes expected utility
+$\EU(a) = \sum_{\act_{-i} \in \Acts_{-i}} \mu_i(\act_{-i}) \myts \pi_i(a_i, a_{-i})$. So this
+is a choice rule, based on \emph{maximization of expected utilities}. It requires a
+probabilistic belief about the opponents' action choices. In the example from
+Figure~\ref{coordgame1}, a rational player would choose $I$ exactly when he believes that his
+opponent will choose $I$ with a probability at least $\nicefrac{2}{3}$.
+
+If an agent does not have a concrete probabilistic belief (see also
+Section~\ref{sec:impr-prob-beli} below), other rules of choice are available. Perhaps the most
+well-known, the \emph{maximin rule}, would tell the agent to choose act $\act^*$ only if it
+maximizes payoffs for all worst case scenarios, i.e.,
+$\act^* \in \argmax_{\myact{i} \in \Acts_i} \min_{\myact{j} \in \Acts_j} \pi_i(\myact{i},
+\myact{j})$. For the example in Figure~\ref{coordgame1}, the maximim rule looks at the minima
+in each row, asking: what is the worst possible out come for each possible act? It is $0$ in
+either case. Consequently, the maximin rule would not favor either act; players choosing by the
+maximin rule would be indifferent between acts $I$ and $II$.
+
+Another well-known choice rule is \emph{Laplace's rule} which prescribes to choose $\act^*$ if
+$\act^* \in \argmax_{a \in A} \sum_{a'} \pi(a, a')$. Laplace's rule is equivalent to rationally
+choosing under a \emph{flat belief} that assigns equal probability to all of the opponent's
+choices. In the coordination game of Figure~\ref{coordgame1}, Laplace's rule selects act $II$.
+
+\paragraph{Equilibrium \& stability.}
+
+\begin{itemize}
+\item \textcolor{red}{add here:}
+  \begin{itemize}
+  \item NE, strict, weak
+  \item ESS, NSS
+  \end{itemize}
+\end{itemize}
+
+\todo[inline]{should we also include here: dominance}
 
@@
 
-Regret theory has been introduced in decision theory by Savage [] and Niherens [], and later
-developed by Bell [1982], Loomes and Sugden [1982], and Fishburn [1982] independently. Lately,
-\citet{HalpernPass2012:Iterated-Regret} showed how the use of regret minimization can solve
-game theoretical puzzles (like the Centipede and the Traveller's dilemma) in a way that is
-closer to everyday intuition and empirical data. In this paper the notion of regret is defined
-as in \citet{HalpernPass2012:Iterated-Regret}:
+Regret theory has been introduced in decision theory by \citet{Savage1951:The-theory-of-s} and
+Niherens [], and later developed by Bell [1982], Loomes and Sugden [1982], and Fishburn [1982]
+independently. Lately, \citet{HalpernPass2012:Iterated-Regret} showed how the use of regret
+minimization can give solutions to game theoretical puzzles (like the Traveller's dilemma, see
+Example~\ref{example:TravelersDilemma}) in a way that is closer to everyday intuition and
+empirical data. In this paper the notion of regret is defined as in
+\citet{HalpernPass2012:Iterated-Regret}:
 
 \begin{definition}[Regret, regret minimization] \label{defn:regret} Given a simultaneous-move
-  game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the regret of player $i$ at profile
-  $(a_i,a_{-i})$ is $\text{reg}(a_i,a_{-i}):= \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $, where
-  $a_i^\$ \in A_i$ denotes $i$'s best reply to action $a_{-i} $. The regret of an action
-  $a_i \in A_i$ is then
+  game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the \emph{pairwise regret} of player
+  $i$ at profile $(a_i,a_{-i})$ is
+  $\text{reg}(a_i,a_{-i}):= \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $, where
+  $a_i^\$ \in \argmax_{a_i \in A_i} \pi_i(a_i, a_{-i})$ denotes $i$'s best reply to the
+  opponents' actions $a_{-i}$. The \emph{regret} of a$a_i$ is then
   $\text{reg}(a_i):= \text{max}_{a_{-i}\in A_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $. An
@@
   regret $reg(I, II)$ is $2$ since $\pi_i(II,II)-\pi_i(I,II)=2$. With the same reasoning,
-  $\text{reg}(II)=1$. Two regret minimizing players would then choose action $II$, each getting
-  a payoff of $2$. In this case regret minimization selects the Pareto-dominant Nash
-  equilibrium.\todo{explain Pareto-dominant NE; otherwise skip it?} $ \medsquare $
+  $\text{reg}(II)=1$. A regret minimizing player would therefore choose action $II$. $ \medsquare $
 
@@
 \begin{example}[The Traveller's Dilemma \citep{HalpernPass2012:Iterated-Regret}]
+\label{example:TravelersDilemma}
 Let us now consider the Traveller's Dilemma case. The story behind the game goes as
@@
 \end{align*}
-By a simple computation we have:  $\forall a_i \in \lbrace 96\$, ..., 100\$ \rbrace \text{, } \text{reg}(a_i)=3 $ and $\forall a_i \in \lbrace 2\$, ..., 95\$ \rbrace \text{, } \text{reg}(a_i)>3$.
-If we now eliminate all the actions that do not minimize regret in the first place and iterate the regret minimization only on the action set $\lbrace 96\$, ..., 100\$ \rbrace$, we get that 97\$ is the action that minimize regret.
-Indeed, $\text{reg}(97)=2$ and $\forall a_i \in \lbrace 96\$, 98\$, 99\$, 100\$ \rbrace \text{, } \text{reg}(a_i)=3 $.
-Hence, one step of regret minimizing reasoning eliminates all the actions smaller than 96\$, and if we iterate the process once more the unique outcome is 97\$.
-Finally, it is worth noticing that the only rationalizable equilibrium of the game corresponds to the outcome $(2,2)$, that is consequently the only Nash equilibrium, the only perfect equilibrium, and the only sequential equilibrium of the game.
+By a simple computation we have:  $\forall a_i \in \lbrace 96\$, ..., 100\$ \rbrace \text{, }
+\text{reg}(a_i)=3 $ and $\forall a_i \in \lbrace 2\$, ..., 95\$ \rbrace \text{, }
+\text{reg}(a_i)>3$. If we now eliminate all the actions that do not minimize regret in the
+first place and iterate the regret minimization only on the action set $\lbrace 96\$, ...,
+100\$ \rbrace$, we get that 97\$ is the action that minimize regret. Indeed, $\text{reg}(97)=2$
+and $\forall a_i \in \lbrace 96\$, 98\$, 99\$, 100\$ \rbrace \text{, } \text{reg}(a_i)=3
+$. Hence, one step of regret minimizing reasoning eliminates all the actions smaller than 96\$,
+and if we iterate the process once more the unique outcome is 97\$. Finally, it is worth
+noticing that the only rationalizable equilibrium of the game corresponds to the outcome
+$(2,2)$, that is consequently the only Nash equilibrium, the only perfect equilibrium, and the
+only sequential equilibrium of the game.
+
+\begin{itemize}
+\item \textcolor{red}{add here:}
+  \begin{itemize}  
+  \item outcome of rationalizability (max-EU)
+  \item outcome of maximin rule
+  \item outcome of Laplace rule
+  \end{itemize}
+
+\end{itemize}
+
  $ \medsquare $
@@
 
-\todo[inline]{add results about regret: reg min is security choice on negative regret transform
-(related to Figure 1b); regret choice equal to veridical in case of probabilistic beliefs and
-maximization of expected gains}
+Regret minimization is intimately related to the maximin rule. Let the \emph{negative regret
+  transform} of a strategic game $G$ be the game $G'$ derived from $G$ by substituting the
+payoff $\pi_i(a_i, a_{-i})$ of all players in $G$ by the negative pairwise regret
+$reg(a_i,a_{-1})$. For example, the negative regret transform of the game in
+Figure~\ref{coordgame1} would have the following payoff matrix, i.e., the negatives of the
+pairwise regrets given in Figure~\ref{coordgame1}:
+
+\begin{center}
+    \begin{tabular}{ccc}
+      \toprule
+      & I & II \\
+      \midrule
+      I & -1 & 0 \\
+      II & 0 & -2\\
+      \bottomrule
+    \end{tabular}
+\end{center}
+
+\noindent The acts selected by the maximin rule for the negative regret transpose are exactly
+the acts selected by regret minimization for the original game.
+
+This means that we can think of the maximin rule and regret minimization as being two
+instantiations of the same choice rule, but operating on different subjective representations
+of utility: while maximin considers actual objective payoffs, regret minimization considers
+non-veridical, regret-based subjective utilities. As the example of Figure~\ref{coordgame1}
+shows, the same choice rule can give different behavioral predictions on different preference
+representations. While maximin is indifferent between $I$ and $II$, regret minimization
+uniquely selects $II$.
+
+When we think of regret as a non-veridical subjective payoff representation, we can also pair
+it with other choice rules, such as the maximization of expected utility and Laplace's rule
+(which is just a special case of the former). It turns out, however, that this makes no
+noticeable difference:
+
+\begin{fact} \label{fact:maxEU-minReg} For any strategic game $G$ and any arbitrary
+  probabilistic belief $\mu \in \Delta(A_{-i})$ about the opponents' behavior, the acts
+  selected by maximization of expected utility for $G$ under $\mu$ are exactly the acts
+  selected by the maximization of expected utility for the negative regret transform of $G$
+  under $\mu$ \citep[e.g.][]{HalpernPass2012:Iterated-Regret}.
+\end{fact}
+
+\noindent In other words, given the same probabilistic belief, maximization of expected
+(objective) payoff and minimization of expected (subjective) regret are behaviorally
+equivalent. This holds for arbitrary games, as well as for solitary decision situations.
+
+\bigskip
+
+In sum, we have so far considered four different types of choice rules, each differing along a
+preference and a belief dimension. As for preference representations, agents could either
+target objective payoffs, or consider non-veridical subjective regret transformations. As for
+beliefs, agents could either hold probabilistic belief or not. In the former case, we would
+assume that they maximize expectations under whatever preference representation they hold; in
+the latter, we would assume that they play maximin based on their preference
+representations. There are doubtlessly many more possible preference and belief types, but
+these are the main characters in the plot to follow.
+
+\newpage
 

### 2015-10-06 paper/paper.tex
paper sec 3 rewrite

@@
 support the conclusion that subjective preferences that differ from objective fitness can be
-adaptive. This is brought to the foreground if we acknowledge the potential mutual dependence
-of subjective preferences and subjective beliefs in adaptationist approaches to decision
+adaptive. We argue that it is important to take into account the potential mutual dependence of
+subjective preferences and subjective beliefs in adaptationist approaches to decision
 making. More specifically, we show that subjective, non-veridical preference representations
@@
   references?}\ can be adaptive and even outperform objective, veridical representations of the
-actual fitness, when agents, at least on occasion, hold imprecise probabilistic beliefs
-(CITE).
+actual fitness, when agents, at least on occasion, hold imprecise probabilistic beliefs (CITE)
+and make decisions based on a security choice rule (here: the maximin rule).
 
@@
 
-The following Section~XYZ will introduce the basic notions needed in the remainder. Section~XYZ
-details our method of using ``meta-games''. \dots
-
-\section{Basic notions}
+The following Section~XYZ will introduce the choice mechanisms that we will focus in on in the
+remainder. Section~XYZ details our method of using ``meta-games''. \dots
+
+\section{The cast}
 \label{sec:basic-notions}
@@
 on the individual agents' perpectives and gives \emph{choice rules}, another considers sets of
-choices of all agents that are, in some sense or other, locked-in. Let's look at either in
-turn, to the extent necessary for this paper:
+choices of all agents that are, in some sense or other, locked-in. We will look at the former
+here; the latter will be relevant only later, when turn to evolutionary competition between
+choice mechanisms in Section~\ref{sec:model}.\footnote{We make a subtle distinction here
+  between \emph{choice rules} and \emph{choice mechanisms}: the former refers to a function of
+  mapping (subjective) preferences and uncertainty unto choices of acts; the latter is more
+  encompassing and contains the choice rule, together with the particular way of forming or
+  representing preferences and uncertainty.}
 
@@
 choices. In the coordination game of Figure~\ref{coordgame1}, Laplace's rule selects act $II$.
-
-\paragraph{Equilibrium \& stability.}
-
-\begin{itemize}
-\item \textcolor{red}{add here:}
-  \begin{itemize}
-  \item NE, strict, weak
-  \item ESS, NSS
-  \end{itemize}
-\end{itemize}
-
-\todo[inline]{should we also include here: dominance}
 
@@
 
-\newpage
+Before we turn to evolutionary competition between choice mechanisms, we should justify our
+focus on the two choice rules. In the following we argue that both the minimax rule, as well as
+the Laplace rule can be viewed as the same choice rule under different representations of
+uncertainty.
 

### 2015-11-02 paper/paper.tex
minor edits introduction; from here split work

@@
 \author{Paolo Galeazzi \& Michael Franke}
-\date{current version: October 3rd 2015}
+\date{current version: November 2nd 2015}
 
@@
 
-\textbf{some general notes and remarks and todo's}
-
-\begin{itemize}
-\item micha: let's have a term for pairs (regret type, epistemic type); I'm inclined to use ``player
-  type'', but that's what you reserved for regret type; maybe use \myalert{meta-type}?
-\item can we reformulate the main result (proposition 1) in terms of ``strict dominance''
-  and/or strict Nash equilibrium? sometimes the proof is not ideally precise because it
-  actually shows something stronger, namely strict dominance, but everything is formulated in
-  terms of stability; using dominance is also better for arguments about evolutionary dynamics:
-  dynamics can be attracted by states that are not evolutionarily stable (even if there is an
-  ESS), but dominated strategies will die out in any case;
-\item should we give definitions for ESS and NSS in the main text?
-\item should we include definitions of the replicator dynamic and/or the replicator mutator
-  dynamic?
-\item the most important issue with this text is still that we need to motivate why we care
-  about non-probabilistic beliefs and/or security strategies; everything else will fall into
-  place when that is done
-\item an important ingredient in our argument pro regret is that radical uncertainty could be
-  exogenously given; as it stands this occurs rather ``suddenly'' in the paper and should
-  ideally be prepared and motivated earlier (e.g., in Sections 2 and 3)
-\item a major contribution of our paper is the ``meta-game'' approach, but in the current
-  version I feel that this is not stressed sufficiently; the introduction and the beginning of
-  section 3 could do a bit more to carve out this idea as something generally cool; especially
-  the formula from 3.4 could occur earlier (albeit in more general notation);
-\end{itemize}
-
-\newpage
+% \textbf{some general notes and remarks and todo's}
+
+% \begin{itemize}
+% \item micha: let's have a term for pairs (regret type, epistemic type); I'm inclined to use ``player
+%   type'', but that's what you reserved for regret type; maybe use \myalert{meta-type}?
+% \item can we reformulate the main result (proposition 1) in terms of ``strict dominance''
+%   and/or strict Nash equilibrium? sometimes the proof is not ideally precise because it
+%   actually shows something stronger, namely strict dominance, but everything is formulated in
+%   terms of stability; using dominance is also better for arguments about evolutionary dynamics:
+%   dynamics can be attracted by states that are not evolutionarily stable (even if there is an
+%   ESS), but dominated strategies will die out in any case;
+% \item should we give definitions for ESS and NSS in the main text?
+% \item should we include definitions of the replicator dynamic and/or the replicator mutator
+%   dynamic?
+% \item the most important issue with this text is still that we need to motivate why we care
+%   about non-probabilistic beliefs and/or security strategies; everything else will fall into
+%   place when that is done
+% \item an important ingredient in our argument pro regret is that radical uncertainty could be
+%   exogenously given; as it stands this occurs rather ``suddenly'' in the paper and should
+%   ideally be prepared and motivated earlier (e.g., in Sections 2 and 3)
+% \item a major contribution of our paper is the ``meta-game'' approach, but in the current
+%   version I feel that this is not stressed sufficiently; the introduction and the beginning of
+%   section 3 could do a bit more to carve out this idea as something generally cool; especially
+%   the formula from 3.4 could occur earlier (albeit in more general notation);
+% \end{itemize}
+
+% \newpage
 
@@
 \label{sec:intr--motiv}
-
-\todo[inline]{this is only a dummy introduction; rewrite eventually with a better focus on the
-  results and main conceptual points we would like to drive home}
 
@@
 actually two crude but common simplifications in this approach. Firstly, the stage game is
-usually considered fixed, closed and immutable \citep[there are exceptions, of course, such
-as][]{WordenLevin2007:Evolutionary-es, McKenzie-AlexanderSkymrs2012:Inventing-New-S}. Secondly,
-what evolves are behavioral strategies for the stage game \citep[what][call the ``behavioral
-gamit'']{FawcettHamblin2013:Exposing-the-be}.
+usually considered fixed, closed and immutable. Secondly, what evolves are behavioral
+strategies for the stage game.
 
@@
 
-Here, we would therefore make two contributions to the literature on evolution of choice
-mechanisms. On the conceptual side, we argue that paying attention to the evolution of
-(subjective representations of) preferences matters. Since almost any reasonable learning or
-decision-making process will make use of some (subjective, agent-internal (possibly
+This makes two contributions to the literature on evolution of choice mechanisms: one
+methodological and one conceptual. Firstly, on the methodological side, we introduce a
+conservative extension of standard EGT that allows us to reuse notions such as evolutionary
+stability / evolutionary dynamics for the study of the evolutionary competition between choice
+mechanisms in a statistically variable environment. Concretely, we look at the evolutionary
+competition of choice mechanisms in a ``meta-game'' that consists of the average expected
+payoffs of choice mechanisms when playing arbitrary games (from a given class). In this sense,
+a meta-game captures (the modeller's) assumptions about the relevant statistics of the
+environment in which evolutionary forces operate.
+
+Secondly, and in order to show that our method is useful for a conceptual debate about
+evolution of choice mechanisms, we argue that paying attention to the interaction of subjective
+belief and subjective preference representations is important. Since almost any reasonable
+learning or decision-making process will make use of some (subjective, agent-internal (possibly
 unconscious)) representation of the quality of choice options, the question of which such
 representations are ecologically valuable (i.e., lead to high fitness) is central. Na\"ive
-intuition might convince us that obviously preferences that veridically represent the object
-fitness that evolutionary selection is based upon must surely be the best. We demonstrate that,
-if we take into account how agents represent uncertainty, this na\"ive conclusion is premature.
-
-On the methodological side, we introduce a conservative extension of standard EGT that allows
-us to reuse notions such as evolutionary stability / evolutionary dynamics and yet helps us
-study the evolutionary competition between choice mechanisms in a statistically variable
-environment. Concretely, we look at the evolutionary competition of choice mechanisms in a
-``meta-game'' that consists of the average expected payoffs of choice mechanisms when playing
-arbitrary games (from a given class). In this sense, a meta-game captures (the modeller's)
-assumptions about the relevant statistics of the environment in which evolutionary forces
-operate.
-
-Section~\ref{sec:rati--subj} introduces necessary concepts from formal decision and game
-theory. Section \dots
+intuition might convince us that preferences that veridically represent the actual, true
+fitness measure that evolutionary selection is based upon must surely be the best. We
+demonstrate that, if we take into account how agents represent uncertainty, this na\"ive
+conclusion is premature.
 
@@
   only if it maximizes the \emph{(subjective) expected utility}
-  $\EU(a) = \sum_{s \in S} P(s) \ u(s, a)$: $a^* \in \text{argmax}_{a \in A} \EU(a) $.
+  $\EU(a) = \sum_{s \in S} P(s) \ u(s, a)$.
 \end{definition}
@@
 rational, i.e., the best choice from the DM's point of view, even if based on peculiar beliefs
-and/or aberrant preferences. (Indeed, while
-\citeauthor{Neumannvon-NeumannMorgenstern1944:Theory-of-Games} assumed that probabilities were
-objectively given, it was \citet{Savage1954:The-Foundations} who famously extended von Neumann
-and Morgenstern's axiomatization to include a subjective notion of probabilistic beliefs on top
-of the subjective notion of preference that von Neumann and Morgenstern started out with.)
+and/or aberrant preferences. % (Indeed, while
+% \citeauthor{Neumannvon-NeumannMorgenstern1944:Theory-of-Games} assumed that probabilities were
+% objectively given, it was \citet{Savage1954:The-Foundations} who famously extended von Neumann
+% and Morgenstern's axiomatization to include a subjective notion of probabilistic beliefs on top
+% of the subjective notion of preference that von Neumann and Morgenstern started out with.)
 
@@
 choices in suitably defined tasks and demonstrated that what appears to be violations of
-rationality norms can be explained as rational on the assumption that subjects' beliefs and
-preferences deviate systematically from the objectively given parameters in the presented
-choice task (e.g., by taking into account reference points and diminishing returns for both
-gains and losses).  Similarly, tinkering with the notion of subjective utility, in particular
-by including social preferences such as fairness, reciprocity or similar, allows us to describe
-as rational empirically observed behavior in social dilemmas, such as the prisoners' dilemma or
-public goods games, that might otherwise appear irrational (e.g. Fehr and Schmidt, Charness and
-Rabin, etc.).\todo{@Paolo: please include proper references}
+rationality norms can be explained on the assumption that subjects' beliefs and preferences
+deviate systematically from the objectively given parameters in the presented choice task
+(e.g., by taking into account reference points and diminishing returns for both gains and
+losses).  Similarly, tinkering with the notion of subjective utility, in particular by
+including social preferences such as fairness, reciprocity or similar, allows us to describe as
+rational empirically observed behavior in situations of social decision making, such as the
+prisoners' dilemma or public goods games, that might otherwise appear irrational (e.g. Fehr and
+Schmidt, Charness and Rabin, etc.).\todo{@Paolo: please include proper references}
 
@@
 to collapse, as it seems possible to deem rational everything that is observed, given the
-freedom to adjust beliefs and preferences freely. Of course, there are many ways in which
+freedom to adjust beliefs and preferences at will. But there are many ways in which
 ascription of beliefs and preferences is constrained further by normative considerations of
@@
 makers (human and other life forms) have evolved choice mechanisms which were fitness enhancing
-(in the relevant domains of choice making, at the relevant time of evolution). When it comes to
+in the relevant domains of choice making, at the relevant time of evolution. When it comes to
 preferences, this is clearly related to Alchian and Friedman's argument that firms
@@
   references?}\ can be adaptive and even outperform objective, veridical representations of the
-actual fitness, when agents, at least on occasion, hold imprecise probabilistic beliefs (CITE)
+actual, true fitness, when agents, at least on occasion, hold imprecise probabilistic beliefs (CITE)
 and make decisions based on a security choice rule (here: the maximin rule).
@@
 
-The following Section~XYZ will introduce the choice mechanisms that we will focus in on in the
-remainder. Section~XYZ details our method of using ``meta-games''. \dots
-
 \section{The cast}
@@
 given in Figure~\ref{coordgame1}, which shows a coordination game. The numbers give the payoff
-for the player choosing the row against an opponent who chooses the column acts. Since the game
-is symmetric, it suffices to give just these numbers.
+for the player choosing a row act against an opponent choosing a column act. Since the game is
+symmetric, it suffices to give just these numbers.
 
@@
 Definition~\ref{def:rationality} also applies to games. Let $A_{-i} = \bigtimes A_j$ for all
-$j \neq i$ be the set of all profiles of acts for all players except $i$. If player $i$ has a
-belief $\mu_i \in \Delta(A_{-i})$ about the behavior of his opponents, he chooses rationally
-only if his choice $a^*_i$ maximizes expected utility
+$j \neq i$ be the set of all \emph{profiles} of acts for all players except $i$. If player $i$
+has a belief $\mu_i \in \Delta(A_{-i})$ about the behavior of his opponents, he chooses
+rationally only if his choice $a^*_i$ maximizes expected utility
 $\EU(a) = \sum_{\act_{-i} \in \Acts_{-i}} \mu_i(\act_{-i}) \myts \pi_i(a_i, a_{-i})$. So this
@@
 well-known, the \emph{maximin rule}, would tell the agent to choose act $\act^*$ only if it
-maximizes payoffs for all worst case scenarios, i.e.,
+maximizes payoffs for all worst case scenarios. For a strategic game with 2 players this can be
+formalized as
 $\act^* \in \argmax_{\myact{i} \in \Acts_i} \min_{\myact{j} \in \Acts_j} \pi_i(\myact{i},
-\myact{j})$. For the example in Figure~\ref{coordgame1}, the maximim rule looks at the minima
-in each row, asking: what is the worst possible out come for each possible act? It is $0$ in
-either case. Consequently, the maximin rule would not favor either act; players choosing by the
+\myact{j})$.
+For the example in Figure~\ref{coordgame1}, the maximim rule looks at the minima in each row,
+asking: what is the worst possible out come for each row act? It is $0$ in either
+case. Consequently, the maximin rule would not favor either act; players choosing by the
 maximin rule would be indifferent between acts $I$ and $II$.
@@
 
-\begin{definition}[Regret, regret minimization] \label{defn:regret} Given a simultaneous-move
-  game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the \emph{pairwise regret} of player
-  $i$ at profile $(a_i,a_{-i})$ is
+\begin{definition}[Regret, regret minimization] \label{defn:regret} Given a strategic game
+  $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the \emph{pairwise regret} of player $i$'s
+  act $a_i$ against profile $a_{-1}$ is
   $\text{reg}(a_i,a_{-i}):= \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $, where
   $a_i^\$ \in \argmax_{a_i \in A_i} \pi_i(a_i, a_{-i})$ denotes $i$'s best reply to the
-  opponents' actions $a_{-i}$. The \emph{regret} of a$a_i$ is then
+  opponents' actions $a_{-i}$. The \emph{regret} of $a_i$ is then
   $\text{reg}(a_i):= \text{max}_{a_{-i}\in A_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $. An
-  action $a^{r}_i $ is regret minimizing if
-  $a^{r}_i \in \text{min}_{a_i} \text{max}_{a_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $.
+  action $a^{*}_i $ is regret minimizing if
+  $a^{*}_i \in \text{min}_{a_i} \text{max}_{a_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $.
 \end{definition}
@@
   Let us consider the coordination game in Figure \ref{coordgame1}. Figure~\ref{coordgame1reg}
-  shows the pairwise regrets and the regrets of each row-player action. It is easy to see that
-  $\text{reg}(I)=2$: when the other player chooses action $I$ the pairwise regret $reg(I,I)$ is
-  $0$ since $I$ is a best reply to $I$, and when the other player chooses $II$ the pairwise
-  regret $reg(I, II)$ is $2$ since $\pi_i(II,II)-\pi_i(I,II)=2$. With the same reasoning,
-  $\text{reg}(II)=1$. A regret minimizing player would therefore choose action $II$. $ \medsquare $
+  shows the pairwise regrets and the regrets of each row-player action. We have
+  $\text{reg}(I)=2$, because when the other player chooses action $I$ the pairwise regret
+  $reg(I,I)$ is $0$ since $I$ is a best reply to $I$, and when the other player chooses $II$
+  the pairwise regret $reg(I, II)$ is $2$ since $\pi_i(II,II)-\pi_i(I,II)=2$. With the same
+  reasoning, $\text{reg}(II)=1$. A regret minimizing player would therefore choose act
+  $II$. $ \medsquare $
 
@@
 Regret minimization is intimately related to the maximin rule. Let the \emph{negative regret
-  transform} of a strategic game $G$ be the game $G'$ derived from $G$ by substituting the
-payoff $\pi_i(a_i, a_{-i})$ of all players in $G$ by the negative pairwise regret
-$reg(a_i,a_{-1})$. For example, the negative regret transform of the game in
-Figure~\ref{coordgame1} would have the following payoff matrix, i.e., the negatives of the
-pairwise regrets given in Figure~\ref{coordgame1}:
+  transform} of a strategic game $G$ be the game $G'$ derived from $G$ by replacing the payoff
+function $\pi$ of $G$ with $\pi'$ such that $\pi'_i(a_i, a_{-i}) = - reg(a_i,a_{-1})$, i.e.,
+the payoff of all players is the pairwise negative regret (under the payoffs from $G$). For
+example, the negative regret transform of the game in Figure~\ref{coordgame1} would have the
+following payoff matrix, i.e., the negatives of the pairwise regrets given in
+Figure~\ref{coordgame1reg}:
 
@@
       \midrule
-      I & -1 & 0 \\
-      II & 0 & -2\\
+      I & 0 & -2 \\
+      II & -1 & 0\\
       \bottomrule
@@
 equivalent. This holds for arbitrary games, as well as for solitary decision situations.
+
+\todo[inline]{Minor edits up to here}
 

### 2015-11-02 paper/paper.tex
rewrite section 4

@@
 
-\section{The model}
+\section{Meta-games and the evolution of choice mechanisms}
 \label{sec:model}
 
-\todo[inline]{first two paragraphs here are partly redundant}
-
-We consider an evolutionary model that is different, for the best of our knowledge, from all
-the standard models of evolutionary game theory. Given a game
-$ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, a subjective utility over $G$ is a function
-$\theta: A \rightarrow \mathbb{R} $, where $ A:=\prod_{i\in N}A_{i} $ as usual. We denote by
-$ \Theta:= \mathbb{R}^{|A|} $ the set of all the subjective utilities over $G$. The model we
-introduce here is a multiple game model, that we also call \textit{multi-game} or
-\textit{meta-game}, where a \textit{class} $\mathcal{G}$ of fitness games is played in a
-population. All the models used in evolutionary game theory that we are aware of always
-consider a single game at a time. \todo{better formulate less strongly} Our extension is meant
-to capture both a more general notion of environment and a more general notion of phenotype.
-
-There are good reasons to claim that focusing on more general psychological mechanisms instead
-of on behavior itself as the phenotype under evolutionary selection can be more faithful and
-insightful for natural biology and ecology [Fawcett\&al.].  In all classical models the agents
-are represented as playing a single fixed game, and as genetically predetermined to play fixed
-strategies, that consequently are the only target of natural selection in those
-frameworks. Standard evolutionary game theory cannot take charge of this shift of perspective
-until it will keep modelling a single game at a time, and until it will keep focusing on
-observed behavior only. ''Instead we should expect animals to have evolved a set of
-psychological mechanisms which enable them to perform well on average across a range of
-different circumstances''[Fawcett\&al.]. [maybe add evolution of preferences here]
-
-In this work we take $\mathcal{G}$ to be the class of symmetric $2 \times 2$ games\footnote{Note that this class includes many of the most famous games extensively considered in game theoretical literature, e.g., Prisoner's dilemma, Chicken game, Stag hunt, etc.}.
-First, a game $G$ is selected from the class of fitness games $\mathcal{G}$, and then players in the population are matched to play the game $G$.
-Each player is a function $\tau: \mathcal{G} \rightarrow  \Theta$, and we call $\tau$ a \textit{player type}, or just a \textit{type}\footnote{Notice that the function $\tau$ is well-defined since, for any symmetric $2 \times 2$ game, the codomain $\Theta=\mathbb{R}^{4}$ is the same.}.
-Intuitively, a type can be interpreted as a way of reasoning, a pattern of conceptualization, a thread that relates different subjective utilities across different games.
-We denote by $T$ the class of player types.
-For each game $G \in \mathcal{G}$, the evolutionary fitness is determined by the objective utility (payoff) function $\pi_G$, but the player's action choice depends on the player's subjective utility function $\tau(G)$, given by the player's type $\tau$.
-Notice that, for any symmetric game $G$, the action sets $(A_1, \dots, A_N)$ and the payoff functions $ (\pi_1, \dots, \pi_N)  $ are the same for all $i\in \lbrace 1, \dots N \rbrace$.
-Consequently, we only write $ A^G $ and $ \pi^G $ for the action set and the payoff function of game $G$, respectively.
-Moreover, in symmetric $2 \times 2$ games we have $A=A^G \times A^G$.
-Then, for $x,y \in A^G$ we denote by $\pi^G(x,y)$ the objective payoff of playing action $x$ in response to action $y$.\\
-
-\subsection{Player types}
-
-The set of all possible player types amouts to the set of all possible functions $ \tau: \mathcal{G} \rightarrow  \Theta $, i.e., $T=\mathbb{R}^{4^{\mathbb{R}^{4}}} $ , but for the sake of simplicity we will focus on types that are relevant and meaningful from a decision-theoretic point of view.
-We are mainly interested in two types: the objective type and the regret type.\\
-Given a game $G$ and Definition \ref{defn:parwreg}, it is straightforward to define the
-\textit{regret preference} $\theta^{reg}$ and the \textit{regret type} $\tau^{reg}$ as
-follows.
-
-\todo[inline]{can some of these definitions not be written as one? e.g., regret preference and
-  regret type as one definition? seems more elegant to me, because it's less repetitive (``for
-  a game ...'')}
-
-\begin{definition}[Regret preference] \label{defn:regpref}
-
-For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the regret preference $ \theta^{reg}: A \rightarrow \mathbb{R} $ such that $ \theta^{reg}(a_i,a_{-i})=-\text{reg}(a_i,a_{-i}) $.\footnote{More precisely, this is the negative regret, whereas the (positive) regret, as defined in [halpass], would not have the minus sign at the beginning of the formula.
-Here it will be easier to define the regret in terms of negative regret.}
-
-\end{definition}
-
-\begin{definition}[Regret type] \label{defn:regtype}
-
-Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call regret type the function $\tau^{reg}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{reg}(G)= \theta^{reg}$.
-
-\end{definition}
-
-\noindent Similarly, let us define the \textit{objective preference} $\theta^{\pi}$ and the \textit{objective type} $ \tau^{\pi} $, that we also call $\pi$\textit{-type}, as follows.
-
-\begin{definition}[Objective preference] \label{defn:objpref}
-
-For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the objective preference $ \theta^{\pi}: A \rightarrow \mathbb{R} $ such that $ \theta^{\pi}(a_i,a_{-i})=\pi(a_i,a_{-i}) $.
-
-\end{definition}
-
-\begin{definition}[Objective type] \label{defn:objtype}
-
-Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call objective type, or $\pi$-type, the function $\tau^{\pi}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{\pi}(G)= \theta^{\pi}$.
-
-\end{definition}
-
-\noindent In other words, we consider two prominent player types: a type who has a veridical subjective utility that perfectly matches the objective utility (i.e., the evolutionary fitness); and a type who has a non-veridical regret-based subjective utility.
-
-\iffalse
-(maybe we want to introduce altruistic and competitive only later) Other types of player have been studied in the literature. A famous example is the \textit{altruistic type}.
-
-\begin{definition}[Altruistic preference] \label{defn:altpref}
-
-For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{alt}: A \rightarrow \mathbb{R} $ such that $ \theta^{alt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \sum_{j \neq i} \pi(a_{j},a_{-j})$.\footnote{A more general formulation [see: REFERENCES] would be to define an $ \alpha$-altruistic type, for $\alpha \in [0,1]$, with subjective utility $ \theta^{\alpha lt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \alpha \sum_{j \neq i} \pi(a_{j},a_{-j})$.
-Since we are not interested in the evolution of degrees of altruism here, we simply fix $ \alpha = 1 $.}
-
-\end{definition}
-
-\begin{definition}[Altruistic type] \label{defn:alttype}
-
-Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{alt}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{alt}(G)= \theta^{alt}$.
-
-\end{definition}
-
-\noindent As opposite to the altruistic type, it is possible to define a \textit{competitive type} as follows.
-
-\begin{definition}[Competitive preference] \label{defn:compref}
-
-For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{com}: A \rightarrow \mathbb{R} $ such that $ \theta^{com}(a_i,a_{-i})=\pi(a_i,a_{-i}) - \sum_{j \neq i} \pi(a_{j},a_{-j})$.
-
-\end{definition}
-
-\begin{definition}[Competitive type] \label{defn:comtype}
-
-Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{com}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{com}(G)= \theta^{com}$.
-
-\end{definition}
-
-\fi
-
-\subsection{Epistemic types}
-\label{sec:epistemic-types}
-
-\todo[inline]{I think we really need a better (and earlier) justification for these epistemic
-  types; we could appeal to information available to agents; naturalness of situations in which
-  we cannot attach numbers to our beliefs (life on Mars again) \dots}
-
-Consider the following problem.
-I have, on the desk in front of me, a bag containing either red or black marbles.
-There is no further information about the distribution of the two colors.
-What is then the probability that I will draw a red marble?
-As in Walley91-96, we are not talking about physical probability, but rather about epistemic probability, i.e., the subjective probability that an agent would attribute to an event.
-In the literature there are two traditional ways of answering this kind of questions.
-According to standard Bayesianism, one should always be able to determine a precise betting rate (that immediately translates into a precise probability), which is fair, in the sense that the DM is indifferent between betting on or against red at the fair rate, and would bet on red at any rate that is more favourable than the fair rate and against red at any rate that is less favourable.
-In this case, a strict Bayesian, in the absence of any further information, would probably rely on the principle of insufficient reason and answer that the DM should have a uniform distribution that considers all the outcomes equipossible.
-\\
-The second answer involves imprecise probabilities and is related to the literature about uncertainty, or ambiguity.
-Many authors argued in favor of this kind of approach [e.g., Walley91-96, Levi74, GardenforsANDSahlin82].
-Since it is consistent with the information available that all the marbles are red, or that no marble is red, the resulting model should take it into account and specify a lower probability of red $\underline{P}(R)$ and an upper probability of red $\overline{P}(R)$ that define an interval of possible probabilistic beliefs [$\underline{P}(R), \overline{P}(R)$].
-Given the information available in this case we would have $\underline{P}(R)=0$ and $\overline{P}(R)=1$.
-This approach appears particularly relevant and appropriate in a game theoretical context.
-Indeed, in a recent paper [Battigalliet al.15] Battigalli et al.
-write
-\begin{quote}
-Such uncertainty is inherent in situations of strategic interaction. This is quite obvious when such situations have been faced only a few times.
-\end{quote}
-In decision theory, the imprecise probability model is in line with most of the representation results about uncertainty [GilboaSchmeidler89,KMM06], and seems justified by empirical observations too (see below).
-Walley91-96 is a seminal work in the area, and also introduces learning procedures to get useful inferences and narrow down the probability set [$\underline{P}(R), \overline{P}(R)$] after observing data.
-Since we want to study the evolution of meta-types, the present work does not address the probem of drawing inferences from observations, and we do not endow the players with any learning procedure yet.\\
-In line with traditional evolutionary game theory, the idea of this work is to model a population of rather unsophisticated and myopic agents.
-%that possibly differ from each other with respect to two components: the player type and the epistemic type.
-The players
-The players encode both a psychological subjective representation of the interaction (player type) and a conceptualization of uncertainty (epistemic type), but they are too simple to have any learning or belief updating procedure.
-From this point of view, we can take the learning process away from natural selection and focus on player types and epistemic types as the target of evolutionary pressure.
-
-In full generality, we think of an epistemic type as a general disposition to form beliefs about the co-player’s behavior.
-Players in the population obviously face uncertainty about the composition of the population that they are part of, and consequently about the type of co-player that they are randomly paired with at each round and about the co-player's actions.
-We represent this uncertainty by the use of both the approaches presented above: a uniform distribution and a probability set.
-This amounts to having two different epistemic types $e$ in the population, $e \in \lbrace \overline{\mu}, \Delta(A_{-i}) \rbrace $, where $\overline{\mu}$ stands for the uniform distribution and $\Delta(A_{-i})$ is the probability set, defined as follows:
-
-\begin{itemize}
-
-\item $ \Delta(A_{-i}):=\lbrace \mu \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu(a_{-i}) = 1 \rbrace$;
-
-\item $\overline{\mu} \in \lbrace \mu \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu(a_{-i}) = 1 \rbrace$ is the probability measure over the co-player's actions such that: $\forall a_{-i} \in A_{-i}$, $\overline{\mu}(a_{-i})= \frac{1}{|A_{-i}|}$.
-
-\end{itemize}
-
-Hence, we consider two possible epistemic states in the face of uncertainty.
-The epistemic type $\Delta(A_{-i})$ represents a situation of non-Bayesian radical uncertainty, where the players are not able to narrow down the set of probability distributions to a single one and they consider all of them as possible.
-The other epistemic type $\overline{\mu}$ conceptualizes the uncertainty about the population by using the principle of insufficient reason and ascribes equal probability to all the possible alternatives.
-As we have seen, both options are reasonable and justifiable ways to deal with situations of uncertainty [REFERENCES].
-\\
-
-\subsection{Uncertainty aversion and maxmin rule}
-
-\todo[inline]{this paragraph seems to presuppose familiarity with maxi-minimization (can we
-  write this with a hyphen, any chance?); we should rewrite this or introduce the notion immediately;}
-
-Given a player type and an epistemic type, there are different ways to produce a behavior. A
-huge body of experimental literature strongly suggests that agents are generally uncertainty
-(or ambiguity) averse [REF]. This pattern of behavior in the presence of ucertainty has been
-famously axiomatized by Gilboa and Schmeidler in a paper from 1989. The idea is that being
-uncertainty averse amounts to behaving in accordance with maximinimizing expected utility over
-a set of prior probabilities. Whenever the set of priors is a singleton, maximinization of
-expected utility coincides with maximization of expected utility. In line with empirical data,
-we assume that players in the population are uncertainty averse and conform to maxmin expected
-utility. The resulting behavior is then produced by maximinimizing over the subjective utility
-given by the player type and the set of priors given by the epistemic type.
-
-\begin{example}
-  Consider the game in Figure \ref{coordgame1} again. When a player characterized
-  by\footnote{To ease notation in the following we will refer to a player directly as a pair
-    $(player \text{ } type \text{ } \tau,\text{ } epistemic\text{ } type \text{ } e)$.} player
-  type $ \tau^{reg} $ and epistemic type $ \Delta(A_{-i}) $ faces the game in Figure
-  \ref{coordgame1}, her player type gives rise to the representation $\tau^{reg}(G^C)$ in
-  Figure \ref{coordgame1reg}. Then, maximinimizing expected utility over the probability
-  simplex $ \Delta(A_{-i}) $ given the game in Figure \ref{coordgame1reg} corresponds to
-  playing the standard maxmin strategy [REF] of that game.\footnote{Notice that this is the
-    case for any game: given a game $G$, maximinimizing expected utility over the probability
-    simplex $ \Delta(A_{-i}) $ amounts to playing the standard maxmin strategy of $G$.} This,
-  in turn, corresponds to the regret minimizing action of the original game $G^C$ of Figure
-  \ref{coordgame1}, namely action $II$, as we have seen in Section \ref{sec:regreTheory}. A
-  player $(\tau^{reg},\overline{\mu})$ instead has subjective representation $\tau^{reg}(G^C)$
-  of Figure \ref{coordgame1reg} and a flat probability measure
-  $\overline{\mu}=(\frac{1}{2}I,\frac{1}{2}II)$ over the co-player's actions. Consequently,
-  such a player would play action $II$, i.e., the action that maximinimizes expected utility
-  given the flat probability measure $\overline{\mu}$.\footnote{As we already noticed,
-    maximinimizing expected utility given a probability measure $\mu$ is equivalent to
-    maximizing expected utility given $\mu$.}  Similarly, a player
-  $(\tau^{\pi},\Delta(A_{-i}))$ will have the subjective representation coinciding with the
-  objective fitness game, i.e., $ \tau^{\pi}(G^C)= G^C $. Then, both actions $I$ and $II$
-  maximinimize expected utility over the probability simplex $ \Delta(A_{-i}) $. Hence, a
-  player $(\tau^{\pi},\Delta(A_{-i}))$ will be indifferent between $I$ and $II$, and will
-  randomize with equal probability $(\frac{1}{2}I,\frac{1}{2}II)$. Finally, a player
-  $(\tau^{\pi},\overline{\mu})$ maximinimizes the objective fitness game $G^C$ of Figure
-  \ref{coordgame1} with flat probability $\overline{\mu}$ over the co-player's actions, i.e.,
-  maximizes objective utility given $\overline{\mu}$. In game $G^C$ this yields action $II$.
-
-\end{example}
-
-We are now in the position of deriving behavior directly from the pair $(\tau, e)$.
-Definitions \ref{def:utility-belief} and \ref{def:maxminSEU} simply formalize the notions of subjective expected utility and maxmin subjective expective utility, respectively.
-
-\begin{definition} \label{def:utility-belief}
-
-Given a game $G$, an action $a_i \in A_i$, and a belief $\mu \in \lbrace \mu' \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu'(a_{-i}) = 1 \rbrace$, we define $\tau(G)(a_i, \mu):= \sum_{a_{-i} \in A_{-i}} \tau(G)(a_i, a_{-i}) \cdot \mu(a_{-i})$.
-
-\end{definition}
-
-\begin{definition} \label{def:maxminSEU}
-
-Given a game $G$ and a player $(\tau, e)$, we define $\text{maxmin}(\tau(G), e):= \lbrace a'_i \in A_i : a_i \in \text{max}_{a_i \in A_i} \text{ min}_{\mu \in e} \text{ } \tau(G)(a_i, \mu) \rbrace$.
-
-\end{definition}
-
-\noindent Definition \ref{def:expected fitness} gives the expected evolutionary fitness of player $(\tau, e)$ against player $(\tau', e')$ in game $G$.\footnote{As already specified in the previous example, we assume that, whenever the set $\text{maxmin}(\tau(G), e)$ is not a singleton, the player $(\tau, e)$ will mix with equal probability among the actions in $\text{maxmin}(\tau(G), e)$.}
-
-\begin{definition} \label{def:expected fitness}
-
-Given a game $G \in \mathcal{G}$, a player $(\tau, e)$, and a player $(\tau', e')$, we define $\pi^G((\tau, e),(\tau', e')):= \pi^G(\text{maxmin}(\tau(G), e),\text{maxmin}(\tau'(G), e'))$.
-
-\end{definition}
-
-\todo[inline]{should we explain here, or very soon, what the resulting types really are: regret
-  minimizers, maximin players \dots}
-
-Many other alternatives different from maxmin expected utility could produce behavior: choice rules like minmax, maxmax, and minmin expected utility would similarly generate behavior from a player type and an epistemic type.
-Here we postulate that players are maximinimizers for two main reasons.
-First, our main interest is the evolution of different patterns of subjective conceptualizations of games (player types), and we want to show that the veridical representation (objective type) is not necessarily the fittest and may not be evolutionarily stable.
-Assuming that all players use the maxmin rule independent of their player type allows us to factor the choice rule out of the selection process and to focus on player types.
-Secondly, as already mentioned, among other possible choice rules maxmin is not only intuitively appealing but also corroborated from an empirical point of view.
-
-Before concluding this section, it is worth stressing two important points.
-
-\begin{fact} \label{fact:maxEU-minReg}
-
-For any given single probability $\mu$, maximization of expected utility and minimization of expected regret are behaviorally equivalent.
-
-\end{fact}
-
-\noindent As we have seen in the previous example, this is not the case in the presence of (radical) uncertainty, in the sense of representation of belief state in terms of a set of probability, as in $ \Delta(A_{-i}) $.
-
-\begin{fact} \label{fact:equivalence2x2}
-
-In the class of $2 \times 2$ symmetric games, players $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg},\overline{\mu})$ are behaviorally equivalent.
-
-\end{fact}
-
-\noindent Two remarks. Firstly, Fact \ref{fact:equivalence2x2} does not hold for $n \times n$
-symmetric games in general. Secondly, we treat behaviorally equivalent types as distinct,
-because we assume that what is selected by biological evolution is not choice behavior as such,
-but the mechanism which generates behavior. This matters in particular if we assume that
-mutations affect different components of the behavior generating mechanisms (see below).
-
-\subsection{Evolution \& the environment}
-
-[MAYBE, put part of Version2 from Snippets here, if not in Introduction]
-
-In standard evolutionary game theory a population of agents plays over a single game, that is supposed to represent the interaction driving the evolutionary dynamics.
-In line with [Fawcett-al.], we claim that the single-game approach is too limiting to encompass the vast variety of interactions that lead evolution.
-Here we propose the meta-game model in order to account for a more general notion of environment.
-By allowing the population to play over a class of possible games, we want to take into consideration a notion of environment that comprises a multitude of possible interactions as the driver of natural selection.
-In this perspective, the meta-game approach represents a model of evolution more faithful and possibly closer to reality.
-\\
-We assume a huge, possibly infinite, population of players $(\tau,e)$.
-At each time, a game $G$ is selected from the class of possible games, and players are randomly paired to play $G$.
-At the end of the play we keep track of the evolutionary fitness achieved by each player.
-Next, another game $G'$ is randomly selected again, and so on.
-The evolutionary fitness of each player is then based on the expected objective payoff over the class $\mathcal{G}$.
-Denoting by $P(G)$ the probability of game $G$ to be selected, the evolutionary fitness of player $(\tau,e)$ against player $(\tau',e')$ is given by:
-
-$$ EF((\tau,e),(\tau',e'))= \int_G  P(G) \cdot \pi^G((\tau, e),(\tau', e')).  $$
-
-\noindent The framework we propose here is a very neutral and flexible tool to model the notion of environment.
-We can take into account many different types of environment by simply changing the class $\mathcal{G}$ of possible games, and in the limit case where $\mathcal{G}$ is a sigleton our model reduces to the standard models of evolutionary game theory.
-By combining field studies and statistics, one could design a more specific class $\mathcal{G}$ with appropriate probabilities $P(G)$ in order to match the natural environment of a given population, but for our theoretical purposes we adopt another approach.
-As already anticipated, we take $\mathcal{G}$ to be the class of $2 \times 2$ symmetric games.
-More precisely, we imagine the class $\mathcal{G}$ to be generated from the generic form table of Figure \ref{generic form table}, where $a,b,c,d$ are i.i.d.
-random variables sampled from a finite set of natural numbers $ \lbrace \underline{n}, \dots, \overline{n}  \rbrace$.
+Evolutionary game theory has established itself as a useful tool for testing consequences of
+sets of assumptions about complex evolutionary processes. However, the standard approach in
+evolutionary game theory is not enough for our purposes, because it (i) fixes a single
+\emph{stage game} (e.g., the prisoner's dilemma) and (ii) assumes that the object of
+evolutionary selection is behavior for that very game. Following a similar line of argument
+\citep[e.g.][]{FawcettHamblin2013:Exposing-the-be}, we therefore turn towards the evolutionary
+competition of \emph{choice mechanisms}, i.e., general ways of selecting concrete behavior
+across a range of different situations. As a consequence, the expected fitness of a choice
+mechanism will not be determined by only a single (elementary) stage game, but it will be a
+complex function of the statistical properties of the environment: we have to take into account
+how frequently particular concrete situations of choice making are.
+
+For concreteness, let us fix a class of strategic games $\mathcal{G}$ and a probability measure
+$P \in \Delta(\mathcal{G})$ that gives the occurrence probability $P(G)$ of each game
+$G \in \mathcal{G}$. Together, a class of games and a probability measure over it can be
+thought of as a model of the environment in which different choice mechanisms compete. Let $C$
+the a set of choice mechanisms that we care about. Then each choice mechanism $c \in C$ is a
+associated with an \emph{action selection function} $S_c$ that maps any $G \in \mathcal{G}$
+onto some action $S_c(G)$ of game $G$.\footnote{In all subsequent formal and simulation results
+  we assume that, whenever a choice mechanisms is selects indifferently a set of actions, the
+  agent will realize each with the same (flat) probability. For ease of parlor, we often do as
+  if there was a tie-break rule.} Different choice mechanisms can select the same act in some
+games. More importantly even, different choice mechanisms can have exactly the same action
+selection functions on a particular class of games $\mathcal{G}$. This is because we think of
+the object of evolutionary selection, not as the realized behavior but as the way behavior is
+specified. (We will see below that this can make an important difference, e.g., in the light of
+mutation.)
+
+Imagine a huge, possibly infinite society of agents, each of which carries a choice mechanism
+from $C$. For simplicity, let's assume that $C$ is finite and that $\mathcal{G}$ is
+a finite set of two-player strategic games. The expected fitness $EF(c_1)$ of an agent with
+choice principle $c_1$ is determined by the probability $P(c_2)$ of meeting an agent with
+choice principle $c_2$, which we will assume is the frequency of $c_2$ in the population, the
+probability $P(G)$ of playing game $G \in \mathcal{G}$ and the concrete payoff
+$\pi^G(c_1 \mid c_2)$ that the player with $c_1$ obtains when playing against a player with
+$c_2$ in $G$, which is uniquely defined by the associated action selection rules:
+\begin{align*}
+  EF(c_1) = \sum_{c_2 \in C} P(c_2) \cdot \sum_{G \in \mathcal{G}}  P(G) \cdot \pi^G(c_1 \mid c_2)\,.
+\end{align*}
+Similarly, the expected fitness of a $c_1$-agent, when playing against a $c_2$ agent is:
+\begin{align}
+  \label{eq:ExpectedPayoffs}
+  EF(c_1 \mid c_2) = \sum_{G \in \mathcal{G}}  P(G) \cdot \pi^G(c_1 \mid c_2)\,.
+\end{align}
+
+Notice that expected fitness of a choice mechanism is defined entirely in parallel to the
+expected fitness of an act in a fixed stage game, except that where the latter has a simple
+payoff function, the former has an expectation over payoffs in a statistically rich
+environment. That means that we can think of evolutionary competition between choice mechanisms
+in terms of payoffs defined by a \emph{meta-game} over $\mathcal{G}$ whose ``acts'' are choice
+mechanisms and whose ``payoffs'' are the expected payoffs in
+Equation~(\ref{eq:ExpectedPayoffs}).\footnote{Allowing games in $\mathcal{G}$ that have
+  different numbers of players makes matters more complicated, but we neglect these
+  complications here, because we focus entirely on 2-player games.}
+
+\section{The basic model}
+\label{sec:basic-model-1}
+
+To demonstrate the usefulness of a meta-game approach, let us concentrate first on a basic
+model that contains the four choice mechanisms obtained from crossing the preference and belief
+types introduced in Section~\ref{sec:basic-notions}.  For particular empirical purposes, one
+could consult a more specific class $\mathcal{G}$ with appropriate, possibly empirically
+determined probabilities $P(G)$ in order to match the natural environment of a given
+population. But for our theoretical purposes we adopt another approach. For a first basic
+model, let $\mathcal{G}$ be a set of symmetric 2-player games with $2$ acts. (We will look at
+extensions and generalizations in Section~\ref{sec:extensions}). More precisely, we imagine the
+class $\mathcal{G}$ to be generated from the generic form table of Figure \ref{generic form
+  table}, where $a,b,c,d$ are i.i.d.~random variables sampled from a finite set of natural
+numbers $ \lbrace 0, \dots, 10 \rbrace$.
 
@@
 
-\section{Results: the basic model}
+\subsection{Player types}
+
+The set of all possible player types amouts to the set of all possible functions $ \tau: \mathcal{G} \rightarrow  \Theta $, i.e., $T=\mathbb{R}^{4^{\mathbb{R}^{4}}} $ , but for the sake of simplicity we will focus on types that are relevant and meaningful from a decision-theoretic point of view.
+We are mainly interested in two types: the objective type and the regret type.\\
+Given a game $G$ and Definition \ref{defn:parwreg}, it is straightforward to define the
+\textit{regret preference} $\theta^{reg}$ and the \textit{regret type} $\tau^{reg}$ as
+follows.
+
+\todo[inline]{can some of these definitions not be written as one? e.g., regret preference and
+  regret type as one definition? seems more elegant to me, because it's less repetitive (``for
+  a game ...'')}
+
+\begin{definition}[Regret preference] \label{defn:regpref}
+
+For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the regret preference $ \theta^{reg}: A \rightarrow \mathbb{R} $ such that $ \theta^{reg}(a_i,a_{-i})=-\text{reg}(a_i,a_{-i}) $.\footnote{More precisely, this is the negative regret, whereas the (positive) regret, as defined in [halpass], would not have the minus sign at the beginning of the formula.
+Here it will be easier to define the regret in terms of negative regret.}
+
+\end{definition}
+
+\begin{definition}[Regret type] \label{defn:regtype}
+
+Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call regret type the function $\tau^{reg}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{reg}(G)= \theta^{reg}$.
+
+\end{definition}
+
+\noindent Similarly, let us define the \textit{objective preference} $\theta^{\pi}$ and the \textit{objective type} $ \tau^{\pi} $, that we also call $\pi$\textit{-type}, as follows.
+
+\begin{definition}[Objective preference] \label{defn:objpref}
+
+For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the objective preference $ \theta^{\pi}: A \rightarrow \mathbb{R} $ such that $ \theta^{\pi}(a_i,a_{-i})=\pi(a_i,a_{-i}) $.
+
+\end{definition}
+
+\begin{definition}[Objective type] \label{defn:objtype}
+
+Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call objective type, or $\pi$-type, the function $\tau^{\pi}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{\pi}(G)= \theta^{\pi}$.
+
+\end{definition}
+
+\noindent In other words, we consider two prominent player types: a type who has a veridical subjective utility that perfectly matches the objective utility (i.e., the evolutionary fitness); and a type who has a non-veridical regret-based subjective utility.
+
+\section{Results for the basic model}
 \label{sec:results:-basic-model}

### 2015-11-04 paper/paper.tex
Paolo's edits Section 3; before drastic rewrite

@@
 
-If an agent does not have a concrete probabilistic belief (see also
+If an agent does not have a precise probabilistic belief (see also
 Section~\ref{sec:impr-prob-beli} below), other rules of choice are available. Perhaps the most
@@
 Regret minimization is intimately related to the maximin rule. Let the \emph{negative regret
-  transform} of a strategic game $G$ be the game $G'$ derived from $G$ by replacing the payoff
+  transformation} of a strategic game $G$ be the game $G'$ derived from $G$ by replacing the payoff
 function $\pi$ of $G$ with $\pi'$ such that $\pi'_i(a_i, a_{-i}) = - reg(a_i,a_{-1})$, i.e.,
@@
 
-\noindent The acts selected by the maximin rule for the negative regret transpose are exactly
+\noindent The acts selected by the maximin rule for the negative regret transformation are exactly
 the acts selected by regret minimization for the original game.
@@
 
-In sum, we have so far considered four different types of choice rules, each differing along a
+In sum, we have so far considered four different alternatives, each differing along a
 preference and a belief dimension. As for preference representations, agents could either
-target objective payoffs, or consider non-veridical subjective regret transformations. As for
+target objective payoffs, or consider non-veridical subjective regret transformations.
+Given a game $G$, we will denote by $ \tau^{reg}(G)$ the regret representation (corresponding to the negative regret transformation) of the game, and $\tau^{\pi}(G)$ the objective representation (corresponding to the identity transformation) of the game.
+\\
+As for
 beliefs, agents could either hold probabilistic belief or not. In the former case, we would
@@
 
-Before we turn to evolutionary competition between choice mechanisms, we should justify our
-focus on the two choice rules. In the following we argue that both the minimax rule, as well as
-the Laplace rule can be viewed as the same choice rule under different representations of
+Before we turn to evolutionary competition between choice principles, we should justify our
+focus on the two choice rules. In the following we argue that both the minimax rule, as well as the maximization of expected utility 
+(and the Laplace rule as a special case) can be viewed as the same choice rule under different representations of
 uncertainty.
@@
 \label{sec:impr-prob-beli}
+
+Consider the following problem.
+I have, on the desk in front of me, a bag containing either red or black marbles.
+There is no further information about the distribution of the two colors.
+What is then the probability that I will draw a red marble?
+As in Walley91-96, we are not talking about physical probability, but rather about epistemic probability, i.e., the subjective probability that an agent attributes to an event.
+In the literature there are two traditional ways of answering this kind of questions.
+According to standard Bayesianism, one should always be able to determine a precise betting rate (that immediately translates into a precise probability distribution), which is fair, in the sense that the DM is indifferent between betting on or against red at the fair rate, and would bet on red at any rate that is more favourable than the fair rate and against red at any rate that is less favourable.
+In this case, a strict Bayesian, in the absence of any further information, would probably rely on the principle of insufficient reason and answer that the DM should have a uniform distribution that considers all the outcomes equipossible.
+\\
+The second answer involves imprecise probabilities and is related to the literature about unmeasurable uncertainty.
+Many authors argued in favor of this kind of approach [e.g., Walley91-96, Levi74, GardenforsANDSahlin82].
+Since it is consistent with the information available that all the marbles are red, or that no marble is red, the resulting model should take it into account and specify a lower probability of red $\underline{P}(R)$ and an upper probability of red $\overline{P}(R)$ that define an interval of possible probabilistic beliefs [$\underline{P}(R), \overline{P}(R)$].
+Given the information available in this case we would have $\underline{P}(R)=0$ and $\overline{P}(R)=1$.
+This approach appears particularly relevant and appropriate in a game theoretical context.
+Indeed, in a recent paper [Battigalliet al.15] Battigalli et al.
+write
+
+\begin{quote}
+Such uncertainty is inherent in situations of strategic interaction. This is quite obvious when such situations have been faced only a few times.
+\end{quote}
+
+In decision theory, the imprecise probability model is in line with most of the representation results about uncertainty [GilboaSchmeidler89,KMM06], and seems justified by empirical observations too.
+
+A prominent example is Ellsberg's paradox.
+A bag contains 90 marbles, 30 are red and the remaining 60 are either black or yellow.
+A marble is to be drawn and DM can win 100€ if she guesses the color of the drawn marble.
+The DM is offered two different bets.
+In the first one she can choose to bet either on red (R) or on yellow (Y), while in the second she can bet either on red or black (RB) or on yellow or black (YB), as shown in Table \ref{Ellsberg}.
+
+\definecolor{yellow}{RGB}{255,188,1}
+
+\begin{table}[h]
+\centering
+\begin{tabular}{@{}llll@{}}
+\cmidrule(l){2-4}
+\multicolumn{1}{c}{} & {\color{red}R}   & {\color{yellow}Y}   & B   \\ \cmidrule(l){2-4} 
+$f_{{\color{red}R}}$              & 100 & 0   & 0   \\
+$f_{{\color{yellow}Y}}$              & 0   & 100 & 0   \\
+$f_{{\color{red}R}B}$            & 100 & 0   & 100 \\
+$f_{{\color{yellow}Y}B}$             & 0   & 100 & 100 \\ \bottomrule
+\end{tabular}
+\caption{Ellsberg's paradox}
+\label{Ellsberg}
+\end{table}
+
+The pattern consistently observed in experimets is: $f_{{\color{red}R}} \succ f_{{\color{yellow}Y}}$ and $f_{{\color{red}R}B} \prec f_{{\color{yellow}Y}B}$.
+This is clearly incompatible with any precise probabilistic belief about the proportion of black and yellow marbles.
+This kind of behavior has been
+famously axiomatized by Gilboa and Schmeidler in a paper from 1989.
+The choice pattern is normally explained in terms of aversion to uncertainty, and the standard representation is given by means of probability sets together with maxmin rule.
+We can think of the DM in Ellsberg's example as maximinimizing expected utility over the probability set $ [\underline{P}(R)=\frac{1}{3},\underline{P}(Y)=0,\underline{P}(B)=0,\overline{P}(R)=\frac{1}{3},\overline{P}(Y)=\frac{2}{3},\overline{P}(B)=\frac{2}{3}]  $.
+This amounts to calculating for any probability distribution contained in the probability set the expected utility of any available action, and then to choosing the action that guarantees the highest minimal expected utility.
+The following observation is then trivial.
+
+\begin{fact} \label{fact:singleton probability set}
+Whenever the probability set is a singleton, maximinization of
+expected utility coincides with maximization of expected utility.
+\end{fact}
+
+A huge body of experimental literature strongly suggests that agents are generally uncertainty
+averse [REF]. In line with empirical data,
+we assume that players in the population are uncertainty averse and conform to maxmin expected
+utility. The resulting behavior is then produced by maximinimizing the subjective utility
+given by the player type over the set of probabilities given by the belief state, or epistemic type, of the agent.
+
+In full generality, we think of an epistemic type as a general disposition to form beliefs about the co-player’s behavior.
+Players in the population obviously face uncertainty about the composition of the population that they are part of, and consequently about the type of co-player that they are randomly paired with at each round and about the co-player's actions.
+We represent this uncertainty in two different ways that correspond to the two approaches discussed above: a Bayesian uniform distribution and an imprecise probability set.
+This amounts to having two different epistemic types, $ \overline{\mu}$ and $ \Delta(A_{-i}) \rbrace $, where $\overline{\mu}$ stands for the uniform distribution and $\Delta(A_{-i})$ is the probability set, defined as follows:
+
+\begin{itemize}
+
+\item $ \Delta(A_{-i}):=\lbrace \mu \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu(a_{-i}) = 1 \rbrace$;
+
+\item $\overline{\mu} \in \Delta(A_{-i})$ is the probability measure over the co-player's actions such that: $\forall a_{-i} \in A_{-i}$, $\overline{\mu}(a_{-i})= \frac{1}{|A_{-i}|}$.
+
+\end{itemize}
+
+Hence, we consider two possible epistemic states in the face of uncertainty.
+The epistemic type $\Delta(A_{-i})$ represents a situation of non-Bayesian radical uncertainty, where the players are not able to narrow down the set of probability distributions to a single one and they consider all of them as possible.
+The other epistemic type $\overline{\mu}$ conceptualizes the uncertainty about the population by using the principle of insufficient reason and ascribes equal probability to all the possible alternatives.
+As we have seen, both options are reasonable and justifiable ways to deal with situations of uncertainty [REFERENCES].
+\\
+
+To sum up, here we consider the choice of an action as depending on two features: the subjective preference and the belief state. Definition \ref{def:choice rule} makes this point clear.
+
+\begin{definition} \label{def:choice rule}
+
+Given a set of subjective preferences $\Theta$ and a set of epistemic types $E$, we define \textit{choice rule} a function $\kappa: \Theta \times E  \rightarrow A_i$ that associates an action choice to a pair $(\theta, e) \in \Theta \times E$.
+
+\end{definition}
+
+According to what we argued in this section, we will assume that the choice rule that turns subjective preferences and beliefs into actions is maxmin expected utility.
+
+\begin{example}
+  Consider the game in Figure \ref{coordgame1} again. When a player characterized
+  by\footnote{To ease notation in the following we will refer to a player directly as a pair
+    $(player \text{ } type \text{ } \tau,\text{ } epistemic\text{ } type \text{ } e)$.} player
+  type $ \tau^{reg} $ and epistemic type $ \Delta(A_{-i}) $ faces the game in Figure
+  \ref{coordgame1}, her player type gives rise to the representation $\tau^{reg}(G^C)$ in
+  Figure \ref{coordgame1reg}. Then, maximinimizing expected utility over the probability
+  simplex $ \Delta(A_{-i}) $ given the game in Figure \ref{coordgame1reg} corresponds to
+  playing the standard maxmin strategy [REF] of that game.\footnote{Notice that this is the
+    case for any game: given a game $G$, maximinimizing expected utility over the probability
+    simplex $ \Delta(A_{-i}) $ amounts to playing the standard maxmin strategy of $G$.} This,
+  in turn, corresponds to the regret minimizing action of the original game $G^C$ of Figure
+  \ref{coordgame1}, namely action $II$, as we have seen in Section \ref{sec:regreTheory}. A
+  player $(\tau^{reg},\overline{\mu})$ instead has subjective representation $\tau^{reg}(G^C)$
+  of Figure \ref{coordgame1reg} and a flat probability measure
+  $\overline{\mu}=(\frac{1}{2}I,\frac{1}{2}II)$ over the co-player's actions. Consequently,
+  such a player would play action $II$, i.e., the action that maximinimizes expected utility
+  given the flat probability measure $\overline{\mu}$.\footnote{As we already noticed,
+    maximinimizing expected utility given a probability measure $\mu$ is equivalent to
+    maximizing expected utility given $\mu$.}  Similarly, a player
+  $(\tau^{\pi},\Delta(A_{-i}))$ will have the subjective representation coinciding with the
+  objective fitness game, i.e., $ \tau^{\pi}(G^C)= G^C $. Then, both actions $I$ and $II$
+  maximinimize expected utility over the probability simplex $ \Delta(A_{-i}) $. Hence, a
+  player $(\tau^{\pi},\Delta(A_{-i}))$ will be indifferent between $I$ and $II$, and will
+  randomize with equal probability $(\frac{1}{2}I,\frac{1}{2}II)$. Finally, a player
+  $(\tau^{\pi},\overline{\mu})$ maximinimizes the objective fitness game $G^C$ of Figure
+  \ref{coordgame1} with flat probability $\overline{\mu}$ over the co-player's actions, i.e.,
+  maximizes objective utility given $\overline{\mu}$. In game $G^C$ this yields action $II$.
+
+\begin{figure}
+\begin{center}%
+\begin{tabular}{|c|c|c|}
+\hline 
+ & I & II\tabularnewline
+\hline 
+\hline 
+I & 0;0 & -2;-1\tabularnewline
+\hline 
+II & -1;-2 & 0;0\tabularnewline
+\hline 
+\end{tabular}\end{center}
+
+\protect\caption{Regret representation $\tau^{reg}(G^C)$}
+\label{coordgame1reg}
+\end{figure}
+
+\end{example}
+
+We are now in the position of deriving behavior directly from the pair $(\tau, e)$.
+Definitions \ref{def:utility-belief} and \ref{def:maxminSEU} simply formalize the notions of subjective expected utility and maxmin subjective expective utility, respectively.
+
+\begin{definition} \label{def:utility-belief}
+
+Given a game $G$, an action $a_i \in A_i$, and a belief $\mu \in \lbrace \mu' \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu'(a_{-i}) = 1 \rbrace$, we define $\tau(G)(a_i, \mu):= \sum_{a_{-i} \in A_{-i}} \tau(G)(a_i, a_{-i}) \cdot \mu(a_{-i})$.
+
+\end{definition}
+
+\begin{definition} \label{def:maxminSEU}
+
+Given a game $G$ and a player $(\tau, e)$, we define $\text{maxmin}(\tau(G), e):= \lbrace a'_i \in A_i : a_i \in \text{max}_{a_i \in A_i} \text{ min}_{\mu \in e} \text{ } \tau(G)(a_i, \mu) \rbrace$.
+
+\end{definition}
+
+\noindent Definition \ref{def:expected fitness} gives the expected evolutionary fitness of player $(\tau, e)$ against player $(\tau', e')$ in game $G$.\footnote{As already specified in the previous example, we assume that, whenever the set $\text{maxmin}(\tau(G), e)$ is not a singleton, the player $(\tau, e)$ will mix with equal probability among the actions in $\text{maxmin}(\tau(G), e)$.}
+
+\begin{definition} \label{def:expected fitness}
+
+Given a game $G \in \mathcal{G}$, a player $(\tau, e)$, and a player $(\tau', e')$, we define $\pi^G((\tau, e),(\tau', e')):= \pi^G(\text{maxmin}(\tau(G), e),\text{maxmin}(\tau'(G), e'))$.
+
+\end{definition}
+
+%\todo[inline]{should we explain here, or very soon, what the resulting types really are: regret minimizers, maximin players \dots}
+
+Many other alternatives different from maxmin could produce behavior: choice rules like minmax, maxmax, and minmin would similarly generate behavior in case of a lack of precise probabilistic belief.
+Here we postulate that players use maxmin for two main reasons that we will expand in the next section.
+First, among other possible choice rules maxmin is not only intuitively appealing but also corroborated from an empirical point of view.
+Secondly, as it will be clear in the following, our main interest is the evolution of different patterns of subjective conceptualizations of games (player types), and we want to show that the veridical representation (objective type) is not necessarily the fittest and may not be evolutionarily stable.
+Assuming that all players use a fixed rule (maxmin) independent of their player type allows us to factor the choice rule out of the selection process and to focus on player types.
+
+Before concluding this section, it is worth stressing that player $(\tau^{\pi}, \Delta(A_{-i}))$ turns out to be the objective maximinimizer, player $(\tau^{reg}, \Delta(A_{-i}))$ is the regret minimizer, player $(\tau^{\pi}, \overline{\mu})$ is the objective expected utility maximizer, and player $(\tau^{reg}, \overline{\mu})$ is the expected regret minimizer.
+Moreover, the following fact holds.
+
+\iffalse
+
+\begin{fact} \label{fact:maxEU-minReg}
+
+For any probability measure $\mu$, maximization of expected utility and minimization of expected regret are behaviorally equivalent.
+
+\end{fact}
+
+\noindent As we have seen in the previous example, this is not the case in the presence of (radical) uncertainty, in the sense of representation of belief state in terms of a set of probability, as in $ \Delta(A_{-i}) $.
+\fi
+
+\begin{fact} \label{fact:equivalence2x2}
+
+In the class of $2 \times 2$ symmetric games, players $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg},\overline{\mu})$ are behaviorally equivalent.
+
+\end{fact}
+
+\noindent Two remarks. Firstly, Fact \ref{fact:equivalence2x2} does not hold for $n \times n$
+symmetric games in general. Secondly, we treat behaviorally equivalent types as distinct,
+because we assume that what is selected by biological evolution is not choice behavior as such,
+but the mechanism which generates behavior. This matters in particular if we assume that
+mutations affect different components of the behavior generating mechanisms (see below).
+
+\iffalse
+
+\subsection{Epistemic types}
+\label{sec:epistemic-types}
+
+\todo[inline]{I think we really need a better (and earlier) justification for these epistemic
+  types; we could appeal to information available to agents; naturalness of situations in which
+  we cannot attach numbers to our beliefs (life on Mars again) \dots}
 
@@
 write
+
 \begin{quote}
@@
 \end{quote}
+
 In decision theory, the imprecise probability model is in line with most of the representation results about uncertainty [GilboaSchmeidler89,KMM06], and seems justified by empirical observations too (see below).
@@
 \\
+
+\subsection{Uncertainty aversion and maxmin rule}
+
+\todo[inline]{this paragraph seems to presuppose familiarity with maxi-minimization (can we
+  write this with a hyphen, any chance?); we should rewrite this or introduce the notion immediately;}
+
+An important part of the latest literature, both experimental and theoretical, in decision theory deals with the issue of uncertainty, also called ambiguity.
+Technically, there is uncertainty about an event when no precise objective probability distribution about the possible outcomes is given.
+A prominent example is the above mentioned Ellsberg's paradox.
+A bag contains 90 marbles, 30 are red and the remaining 60 are either black or yellow.
+A marble is to be drawn and DM can win 100€ if she guesses the color of the drawn marble.
+The DM is offered two different bets.
+In the first one she can choose to bet either on red (R) or on yellow (Y), while in the second she can bet either on red or black (RB) or on yellow or black (YB), as shown in Table \ref{Ellsberg}.
+
+\definecolor{yellow}{RGB}{255,188,1}
+
+\begin{table}[h]
+\centering
+\begin{tabular}{@{}llll@{}}
+\cmidrule(l){2-4}
+\multicolumn{1}{c}{} & {\color{red}R}   & {\color{yellow}Y}   & B   \\ \cmidrule(l){2-4} 
+$f_{{\color{red}R}}$              & 100 & 0   & 0   \\
+$f_{{\color{yellow}Y}}$              & 0   & 100 & 0   \\
+$f_{{\color{red}R}B}$            & 100 & 0   & 100 \\
+$f_{{\color{yellow}Y}B}$             & 0   & 100 & 100 \\ \bottomrule
+\end{tabular}
+\caption{Ellsberg's paradox}
+\label{Ellsberg}
+\end{table}
+
+The pattern consistently observed in experimets is: $f_{{\color{red}R}} \succ f_{{\color{yellow}Y}}$ and $f_{{\color{red}R}B} \prec f_{{\color{yellow}Y}B}$.
+This is clearly incompatible with any precise probabilistic belief about the proportion of black and yellow marbles.
+This kind of behavior has been
+famously axiomatized by Gilboa and Schmeidler in a paper from 1989.
+The choice pattern is normally explained in terms of aversion to uncertainty, and the standard representation is given by means of probability sets together with maxmin rule.
+We can think of the DM in Ellsberg's example as maximinimizing expected utility over the probability set $ [\underline{P}(R)=\frac{1}{3},\underline{P}(Y)=0,\underline{P}(B)=0,\overline{P}(R)=\frac{1}{3},\overline{P}(Y)=\frac{2}{3},\overline{P}(B)=\frac{2}{3}]  $.
+This amounts to calculating for any probability distribution contained in the probability set the expected utility of any available action, and then to choosing the action that guarantees the highest minimal expected utility.
+Whenever the set of priors is a singleton, maximinization of
+expected utility coincides with maximization of expected utility.\\
+%Given a player type and an epistemic type, there are different ways to produce a behavior. 
+A huge body of experimental literature strongly suggests that agents are generally uncertainty
+(or ambiguity) averse [REF]. In line with empirical data,
+we assume that players in the population are uncertainty averse and conform to maxmin expected
+utility. The resulting behavior is then produced by maximinimizing the subjective utility
+given by the player type over the set of priors given by the epistemic type.
+
+  \todo[inline]{I would like to suggest to move Figure 2 next to Figure 1; it is already useful
+  for example 1 and could be referred to there already; I would suggest to use subfigures to
+  put both next to each other}
+
+\begin{example}
+  Consider the game in Figure \ref{coordgame1} again. When a player characterized
+  by\footnote{To ease notation in the following we will refer to a player directly as a pair
+    $(player \text{ } type \text{ } \tau,\text{ } epistemic\text{ } type \text{ } e)$.} player
+  type $ \tau^{reg} $ and epistemic type $ \Delta(A_{-i}) $ faces the game in Figure
+  \ref{coordgame1}, her player type gives rise to the representation $\tau^{reg}(G^C)$ in
+  Figure \ref{coordgame1reg}. Then, maximinimizing expected utility over the probability
+  simplex $ \Delta(A_{-i}) $ given the game in Figure \ref{coordgame1reg} corresponds to
+  playing the standard maxmin strategy [REF] of that game.\footnote{Notice that this is the
+    case for any game: given a game $G$, maximinimizing expected utility over the probability
+    simplex $ \Delta(A_{-i}) $ amounts to playing the standard maxmin strategy of $G$.} This,
+  in turn, corresponds to the regret minimizing action of the original game $G^C$ of Figure
+  \ref{coordgame1}, namely action $II$, as we have seen in Section \ref{sec:regreTheory}. A
+  player $(\tau^{reg},\overline{\mu})$ instead has subjective representation $\tau^{reg}(G^C)$
+  of Figure \ref{coordgame1reg} and a flat probability measure
+  $\overline{\mu}=(\frac{1}{2}I,\frac{1}{2}II)$ over the co-player's actions. Consequently,
+  such a player would play action $II$, i.e., the action that maximinimizes expected utility
+  given the flat probability measure $\overline{\mu}$.\footnote{As we already noticed,
+    maximinimizing expected utility given a probability measure $\mu$ is equivalent to
+    maximizing expected utility given $\mu$.}  Similarly, a player
+  $(\tau^{\pi},\Delta(A_{-i}))$ will have the subjective representation coinciding with the
+  objective fitness game, i.e., $ \tau^{\pi}(G^C)= G^C $. Then, both actions $I$ and $II$
+  maximinimize expected utility over the probability simplex $ \Delta(A_{-i}) $. Hence, a
+  player $(\tau^{\pi},\Delta(A_{-i}))$ will be indifferent between $I$ and $II$, and will
+  randomize with equal probability $(\frac{1}{2}I,\frac{1}{2}II)$. Finally, a player
+  $(\tau^{\pi},\overline{\mu})$ maximinimizes the objective fitness game $G^C$ of Figure
+  \ref{coordgame1} with flat probability $\overline{\mu}$ over the co-player's actions, i.e.,
+  maximizes objective utility given $\overline{\mu}$. In game $G^C$ this yields action $II$.
+
+\begin{figure}
+\begin{center}%
+\begin{tabular}{|c|c|c|}
+\hline 
+ & I & II\tabularnewline
+\hline 
+\hline 
+I & 0;0 & -2;-1\tabularnewline
+\hline 
+II & -1;-2 & 0;0\tabularnewline
+\hline 
+\end{tabular}\end{center}
+
+\protect\caption{Regret representation $\tau^{reg}(G^C)$}
+\label{coordgame1reg}
+\end{figure}
+
+\end{example}
+
+We are now in the position of deriving behavior directly from the pair $(\tau, e)$.
+Definitions \ref{def:utility-belief} and \ref{def:maxminSEU} simply formalize the notions of subjective expected utility and maxmin subjective expective utility, respectively.
+
+\begin{definition} \label{def:utility-belief}
+
+Given a game $G$, an action $a_i \in A_i$, and a belief $\mu \in \lbrace \mu' \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu'(a_{-i}) = 1 \rbrace$, we define $\tau(G)(a_i, \mu):= \sum_{a_{-i} \in A_{-i}} \tau(G)(a_i, a_{-i}) \cdot \mu(a_{-i})$.
+
+\end{definition}
+
+\begin{definition} \label{def:maxminSEU}
+
+Given a game $G$ and a player $(\tau, e)$, we define $\text{maxmin}(\tau(G), e):= \lbrace a'_i \in A_i : a_i \in \text{max}_{a_i \in A_i} \text{ min}_{\mu \in e} \text{ } \tau(G)(a_i, \mu) \rbrace$.
+
+\end{definition}
+
+\noindent Definition \ref{def:expected fitness} gives the expected evolutionary fitness of player $(\tau, e)$ against player $(\tau', e')$ in game $G$.\footnote{As already specified in the previous example, we assume that, whenever the set $\text{maxmin}(\tau(G), e)$ is not a singleton, the player $(\tau, e)$ will mix with equal probability among the actions in $\text{maxmin}(\tau(G), e)$.}
+
+\begin{definition} \label{def:expected fitness}
+
+Given a game $G \in \mathcal{G}$, a player $(\tau, e)$, and a player $(\tau', e')$, we define $\pi^G((\tau, e),(\tau', e')):= \pi^G(\text{maxmin}(\tau(G), e),\text{maxmin}(\tau'(G), e'))$.
+
+\end{definition}
+
+%\todo[inline]{should we explain here, or very soon, what the resulting types really are: regret minimizers, maximin players \dots}
+
+Many other alternatives different from maxmin expected utility could produce behavior: choice rules like minmax, maxmax, and minmin expected utility would similarly generate behavior from a player type and an epistemic type.
+Here we postulate that players are maximinimizers for two main reasons.
+First, as already mentioned, among other possible choice rules maxmin is not only intuitively appealing but also corroborated from an empirical point of view.
+Secondly, our main interest is the evolution of different patterns of subjective conceptualizations of games (player types), and we want to show that the veridical representation (objective type) is not necessarily the fittest and may not be evolutionarily stable.
+Assuming that all players use the maxmin rule independent of their player type allows us to factor the choice rule out of the selection process and to focus on player types.
+
+Before concluding this section, it is worth stressing that player $(\tau^{\pi}, \Delta(A_{-i}))$ turns out to be the objective maximinimizer, player $(\tau^{reg}, \Delta(A_{-i}))$ is the regret minimizer, player $(\tau^{\pi}, \overline{\mu})$ is the objective expected utility maximizer, and player $(\tau^{reg}, \overline{\mu})$ is the expected regret minimizer.
+Moreover, the following facts hold.
+
+\begin{fact} \label{fact:maxEU-minReg}
+
+For any probability measure $\mu$, maximization of expected utility and minimization of expected regret are behaviorally equivalent.
+
+\end{fact}
+
+\noindent As we have seen in the previous example, this is not the case in the presence of (radical) uncertainty, in the sense of representation of belief state in terms of a set of probability, as in $ \Delta(A_{-i}) $.
+
+\begin{fact} \label{fact:equivalence2x2}
+
+In the class of $2 \times 2$ symmetric games, players $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg},\overline{\mu})$ are behaviorally equivalent.
+
+\end{fact}
+
+\noindent Two remarks. Firstly, Fact \ref{fact:equivalence2x2} does not hold for $n \times n$
+symmetric games in general. Secondly, we treat behaviorally equivalent types as distinct,
+because we assume that what is selected by biological evolution is not choice behavior as such,
+but the mechanism which generates behavior. This matters in particular if we assume that
+mutations affect different components of the behavior generating mechanisms (see below).
+
+\fi
 
@@
 
-\noindent To show
+\noindent Let us consider the case of sampling from a finite set of values first. To show
 the result we will use the following partition of $\mathcal{G}$.
@@
 
-\noindent $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM})\cdot a^{A}+P(II_{G^{A}}^{RM})\cdot d^{A}]>\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot d^{A}+P(I_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot c^{A}+P(II_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot b^{A}]$
+\noindent $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})\cdot c^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM}\cap I_{G^{A}}^{RM})\cdot a^{A}+P(II_{G^{A}}^{RM}\cap II_{G^{A}}^{RM})\cdot d^{A}+P(I_{G^{A}}^{RM}\cap II_{G^{A}}^{RM})\cdot b^{A}+P(II_{G^{A}}^{RM}\cap I_{G^{A}}^{RM})\cdot c^{A}] > \sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot d^{A}+P(I_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot c^{A}+P(II_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot b^{A}]$
 \medskip{}
@@
 \begin{itemize}
-\item $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM})\cdot a^{A}+P(II_{G^{A}}^{RM})\cdot d^{A}]>\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot d^{A}+P(I_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot c^{A}+P(II_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot b^{A}]$
-\item $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}+P(II_{G^{C}}^{RM})\cdot c^{C}+P(I{}_{G^{C}}^{RM})\cdot b^{C}]>\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}]$
-\item $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}+P(II_{G^{C}}^{RM})\cdot c^{C}+P(I{}_{G^{C}}^{RM})\cdot b^{C}]>\sum_{G^{C}}P(G^{C})[a^{C}\cdot(P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))+b^{C}\cdot(P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))+c^{C}\cdot(P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))+d^{C}\cdot(P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]$
-\end{itemize}
-Now let us split into $a>d$ and $a<d$, and consider $a>d$ first.
+
+\item $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})\cdot c^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM}\cap I_{G^{A}}^{RM})\cdot a^{A}+P(II_{G^{A}}^{RM}\cap II_{G^{A}}^{RM})\cdot d^{A}+P(I_{G^{A}}^{RM}\cap II_{G^{A}}^{RM})\cdot b^{A}+P(II_{G^{A}}^{RM}\cap I_{G^{A}}^{RM})\cdot c^{A}] > \sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot d^{A}+P(I_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot c^{A}+P(II_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot b^{A}]$
+
+\item $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})\cdot c^{C} +P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})\cdot c^{C}+P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})\cdot a^{C}] > \sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}]$
+
+\item $\sum_{G^{C}}P(G^{C})[a^{C} \cdot (P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}) + P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})) + b^{C} \cdot  (P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM}) + P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})) + c^{C} \cdot (P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}) +P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})) + d^{C} \cdot (P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}))]> \sum_{G^{C}}P(G^{C})[a^{C} \cdot (P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + b^{C} \cdot (P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + c^{C} \cdot (P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + d^{C} \cdot (P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]$
+
+\end{itemize}
+
+\noindent Now let us split into $a>d$ and $a<d$, and consider $a>d$ first.
 Notice that, by Lemma 7, the case $a=d$ is irrelevant in order to
@@
 the cases where RM plays $II$ and MM plays $I$:
-\begin{itemize}
-\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}+P(II_{G^{C}}^{RM})\cdot c^{C}+P(I{}_{G^{C}}^{RM})\cdot b^{C}]>\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[a^{C}\cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+b^{C}\cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+c^{C}\cdot(P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))+d^{C}\cdot(P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]$
-\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[P(I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM})\cdot d^{C}+P(II_{G^{C}}^{RM})\cdot c^{C}+P(I{}_{G^{C}}^{RM})\cdot b^{C}-a^{C}\cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})-b^{C}\cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})-c^{C}\cdot(P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))-d^{C}\cdot(P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]>0$
-\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[a^{C}\cdot(P(I_{G^{C}}^{RM})-P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))+b^{C}\cdot(P(I{}_{G^{C}}^{RM})-P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))+c^{C}\cdot(P(II_{G^{C}}^{RM})-P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})-P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))+d^{C}\cdot(P(II_{G^{C}}^{RM})-P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})-P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]>0$
-\end{itemize}
-By Lemma 7, it is easy to check that $P(I_{G^{C}}^{RM})-P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})=P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})$
-and $P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})=P(II_{G^{C}}^{RM})$.
+
+\begin{itemize}
+
+\item $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot (P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}) + P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})) + b^{C} \cdot  (P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM}) + P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})) + c^{C} \cdot (P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}) +P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})) + d^{C} \cdot (P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}))]>
+\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}) + b^{C} \cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}) + c^{C} \cdot (P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + d^{C} \cdot (P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]$
+
+\item $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot (P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}) + P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})- P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + b^{C} \cdot  (P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM}) + P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})- P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + c^{C} \cdot (P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}) +P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})- P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + d^{C} \cdot (P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})- P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]> 0$
+
+\end{itemize}
+
+\noindent We now distinguish between two cases: (1) $ a-c = d-b $ and (2) $  a-c \neq d-b $.
+Notice that $P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM}) \neq 0$ if and only if case (1) obtains, and that $a>d$ and (1) imply $II_{G^{C}}^{MM}$.
+Then, from (1) we have:
+
+\begin{itemize}
+
+\item $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot (P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}) + P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})) + b^{C} \cdot  (P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM}) + P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})) + c^{C} \cdot (P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}) +P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})- P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + d^{C} \cdot (P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})- P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]> 0$
+
+\item $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot (\frac{1}{4}+\frac{1}{4}) + b^{C} \cdot  (\frac{1}{4}+\frac{1}{4}) + c^{C} \cdot (\frac{1}{4}+\frac{1}{4}-\frac{1}{2}-\frac{1}{2}) + d^{C} \cdot (\frac{1}{4}+\frac{1}{4}-\frac{1}{2}-\frac{1}{2})]> 0$
+
+\item $\sum_{G_{a>d}^{C}} P(G^{C})[\frac{1}{2}a^{C}+ \frac{1}{2}b^{C} - \frac{1}{2}c^{C} - \frac{1}{2}d^{C}]> 0$
+
+\end{itemize}
+
+\noindent Since we have assumed $ a-c = d-b $, the last inequality is not satisfied. We have instead:
+
+$$ \sum_{G_{a>d}^{C}} P(G^{C})[\frac{1}{2}a^{C}+ \frac{1}{2}b^{C} - \frac{1}{2}c^{C} - \frac{1}{2}d^{C}]= 0 $$
+
+\noindent This means that, when (1) is the case, RM and MM are neutrally stable. To prove the result we then have to show that the inequality is strict in favor of RM when case (2) obtains. \\
+When (2) is the case, it is easy to check, by Lemma 7, that $P(I_{G^{C}}^{RM} \cap I_{G^{C}}^{RM})-P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})=P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})$
+and $P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})=P(II_{G^{C}}^{RM} \cap II_{G^{C}}^{RM})$.
 Consequently, we have:
-\begin{itemize}
-\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})[a^{C}\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+b^{C}\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})-c^{C}\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})-d^{C}\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})]>0$
-\item $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[a^{G^{C}}-c^{G^{C}}]>\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[d^{G^{C}}-b^{G^{C}}]$.
+
+\begin{itemize}
+
+\item $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot (P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}) - P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + b^{C} \cdot  (P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})- P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + c^{C} \cdot (P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})- P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + d^{C} \cdot (P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})- P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]> 0$
+
+\item $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}) + b^{C} \cdot  P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}) - c^{C} \cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}) - d^{C} \cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})]> 0$
+
+\item $\sum_{G_{a>d}^{C}} P(G^{C})[P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot (a^{C} + b^{C} - c^{C} - d^{C})]> 0$
+
 \end{itemize}
@@
 
-\noindent We know that $I_{G^{C}}^{RM}$ implies that $b^{G^{C}}-d^{G^{C}}\geq c^{G^{C}}-a^{G^{C}}$,
-and $II_{G^{C}}^{MM}$ implies that $b^{G^{C}}\leq c^{G^{C}}$. From
-$b^{G^{C}}-d^{G^{C}}\geq c^{G^{C}}-a^{G^{C}}$, it is easy to see
-that $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[a^{G^{C}}-c^{G^{C}}]\geq\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[d^{G^{C}}-b^{G^{C}}]$
-holds. When the event $I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}$ obtains
-on the assumption that $a^{G^{C}}>d^{G^{C}}$, there are only three
-possible payoff orderings: $a>c\geq d>b$, $a>d>c>b$, and $a>d>c=b$.
-If games are randomly sampled from a finite set with i.i.d. values
-for $a,b,c$ and $d$, then $a>d>c=b$ occurs with positive probability,
-and the last formula of the derivation holds with strict inequality
-too. Hence, RM is evolutionarily stable when the value set for $a,b,c,d$
-is finite. \\
-If i.i.d. values are sampled from a compact and convex set instead,
-it is again easy to see that $\forall a,d,c\ \exists\epsilon$ such
-that $\forall b\in(d,d+\epsilon)$ the above formula holds with strict
-inequality. We can simply take $\epsilon\equiv\frac{a-c}{2}$, and
-the interval $(d,d+\epsilon)$ always has positive probability. Hence,
-RM is evolutionarily stable when the value set for $a,b,c,d$ is a
-compact and convex set too. \\
-Symmetrically, from $a<d$ in the above derivation we get:
-
-\medskip{}
-
-\noindent $\sum_{G_{a<d}^{C}}P(G_{a<d}^{C})\cdot P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot[d^{C}-b^{C}]>\sum_{G_{a<d}^{C}}P(G_{a<d}^{C})\cdot P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot[a^{C}-c^{C}]$
-
-\medskip{}
-
-\noindent and the same argument follows.
+\noindent We know that $I_{G^{C}}^{RM}$ implies that $a^{G^{C}}-c^{G^{C}}\geq d^{G^{C}}-b^{G^{C}}$.
+%and $II_{G^{C}}^{MM}$ implies that $b^{G^{C}}\leq c^{G^{C}}$. 
+Since we have assumed that $a^{G^{C}}-c^{G^{C}}\neq d^{G^{C}}-b^{G^{C}}$, we have that $a^{G^{C}}-c^{G^{C}} > d^{G^{C}}-b^{G^{C}}$. Hence, the inequality 
+$$\sum_{G_{a>d}^{C}} P(G^{C})[P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot (a^{C} + b^{C} - c^{C} - d^{C})]> 0$$
+is satisfied. So, when (2) obtains, RM is evolutionarily stable against MM.
+%From $b^{G^{C}}-d^{G^{C}}\geq c^{G^{C}}-a^{G^{C}}$, it is easy to see that $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[a^{G^{C}}-c^{G^{C}}]\geq\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[d^{G^{C}}-b^{G^{C}}]$ holds.
+When the event $I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}$ obtains on the assumption that $a^{G^{C}}>d^{G^{C}}$, there are only three possible payoff orderings: $a>c\geq d>b$, $a>d>c>b$, and $a>d>c=b$.
+If games are randomly sampled from a finite set with i.i.d.
+values for $a,b,c$ and $d$, then $a>d>c=b$ occurs with positive probability, and the last formula of the derivation holds with strict inequality too.
+Hence, RM is evolutionarily stable when the value set for $a,b,c,d$ is finite.
+\\
+%If i.i.d.
+values are sampled from a compact and convex set instead, it is again easy to see that $\forall a,d,c\ \exists\epsilon$ such that $\forall b\in(d,d+\epsilon)$ the above formula holds with strict inequality.
+We can simply take $\epsilon\equiv\frac{a-c}{2}$, and the interval $(d,d+\epsilon)$ always has positive probability.
+Hence, RM is evolutionarily stable when the value set for $a,b,c,d$ is a compact and convex set too.
+\\
+Symmetrically, from $a<d$ and by distinguishing between the two cases (1) and (2) as before, in the end  we get:
+
+\begin{itemize}
+
+\item[(1)] $\sum_{G_{a<d}^{C}} P(G^{C})[-\frac{1}{2}a^{C}- \frac{1}{2}b^{C} + \frac{1}{2}c^{C} + \frac{1}{2}d^{C}]= 0$; and
+
+\item[(2)] $\sum_{G_{a<d}^{C}} P(G^{C})[P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot (-a^{C} - b^{C} + c^{C} + d^{C})]> 0$.
+
+\end{itemize}
+
+\noindent Hence, we can conclude that RM is evolutionarily stable against MM in the class $\mathcal{G}^{C}\cup\mathcal{G^{A}}$. \\
+In the case of sampling i.i.d.
+values from a real interval instead, games in $\mathcal{G}^I $ and $\mathcal{G}^W $ never arise, and the proof is the same for the remaining games in $\mathcal{G}^S $,  $\mathcal{G}^C $ and $\mathcal{G}^A $.
 
@@
 
-\noindent $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{MM})\cdot d^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{MM})\cdot d^{A}]<\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{RM})\cdot d^{C}+P(I_{G^{C}}^{MM}\cap II_{G^{C}}^{RM})\cdot c^{C}+P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot b^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{MM}\cap I_{G^{A}}^{RM})\cdot a^{A}+P(II_{G^{A}}^{MM}\cap II_{G^{A}}^{RM})\cdot d^{A}+P(I_{G^{A}}^{MM}\cap II_{G^{A}}^{RM})\cdot c^{A}+P(II_{G^{A}}^{MM}\cap I_{G^{A}}^{RM})\cdot b^{A}]$.
+\noindent $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})\cdot b^{C}+P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{MM})\cdot c^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{MM}\cap I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{MM}\cap II_{G^{A}}^{MM})\cdot d^{A}+P(I_{G^{A}}^{MM}\cap II_{G^{A}}^{MM})\cdot b^{A}+P(II_{G^{A}}^{MM}\cap I_{G^{A}}^{MM})\cdot c^{A}] < \sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot c^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot d^{A}+P(I_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot b^{A}+P(II_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot c^{A}]$.
 \medskip{}
 
-\noindent Similarly to the above derivation, in the end we get:
+\noindent When $a>d$, similarly to the above derivation, we get:
 
 \medskip{}
-
-\noindent $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot[c^{G^{C}}-a^{G^{C}}]<\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{RM})\cdot[b^{G^{C}}-d^{G^{C}}]$.
-
+\noindent $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot (P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{MM}) + P(I_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})- P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}) - P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + b^{C} \cdot  (P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{MM}) + P(I_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})- P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}) - P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + c^{C} \cdot (P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{MM}) +P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + d^{C} \cdot (P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})+P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{MM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]< 0$
 \medskip{}
 
-\noindent Finally, by the same argument as before we can conclude that MM is
+\noindent We now distinguish between (1) $b=c$, (2) $b>c$, and (3) $b<c$. Notice that either (1) or (2), together with $a>d$, implies $I_{G^{C}}^{RM}$. Then we obtain: 
+\begin{itemize}
+
+\item[(1)] $\sum_{G_{a<d}^{C}} P(G^{C})[-\frac{1}{2}a^{C} - \frac{1}{2}b^{C} + \frac{1}{2}c^{C} + \frac{1}{2}d^{C}]< 0$;
+
+\item[(2)] $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot (P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{MM}) - P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + b^{C} \cdot  (P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{MM}) - P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))]= 0$;
+
+\item[(3)] $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot (- P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + b^{C} \cdot  (- P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + c^{C} \cdot (P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + d^{C} \cdot (P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))] \leq 0$.
+
+\end{itemize}
+
+\noindent When $a<d$, the derivation proceeds symmetrically and we get:
+
+\begin{itemize}
+
+\item[(1)] $\sum_{G_{a<d}^{C}} P(G^{C})[\frac{1}{2}a^{C} + \frac{1}{2}b^{C} - \frac{1}{2}c^{C} - \frac{1}{2}d^{C}]< 0$;
+
+\item[(2)] $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot (P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{MM}) - P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + b^{C} \cdot  (P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{MM}) - P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + c^{C} \cdot (- P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + d^{C} \cdot (- P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))] \leq 0$
+
+\item[(3)] $\sum_{G_{a>d}^{C}} P(G^{C})[c^{C} \cdot (P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + d^{C} \cdot (P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))] = 0$.
+
+\end{itemize}
+
+\noindent Finally, we can conclude that MM is
 not evolutionarily stable against RM both when the value set for $a,b,c,d$
@@
 convex set. This concludes the proof. $\dashv$
+
+\newpage
 

### 2015-11-04 paper/paper.tex
rewrite section 3

@@
 
-\title{Rationality, Evolution \& the Environment}
+\title{Rationality, Regret, Evolution \& the Environment}
 \author{Paolo Galeazzi \& Michael Franke}
-\date{current version: November 2nd 2015}
+\date{current version: November 4, 2015}
 
@@
 usually considered fixed, closed and immutable. Secondly, what evolves are behavioral
-strategies for the stage game.
-
-It has consequently been argued that, instead of focusing on a fixed, immutable stage game and
-the behavioral selection for that stage game alone, we should rather study the evolutionary
-selection of \emph{choice mechanisms} that are adapted in a rich and variable environment
-\citep[e.g.][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche}. However,
-formal accounts of the adaptive value of choice mechanisms have focused, for the most part, on
-the evolutionary benefit of learning rules
-\citep[e.g.][]{ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o}. \todo{More
-  references Harley 1981!!!, O Conor \dots}  Moreover, only little attention has been paid to
-modeling the direct (game-theoretic) meta-competition between alternative choice mechanisms
-\citep[see][for related criticism]{FawcettHamblin2013:Exposing-the-be}.
-
-This makes two contributions to the literature on evolution of choice mechanisms: one
+strategies for the stage game. It has consequently been argued that, instead of focusing on a
+fixed, immutable stage game and the behavioral selection for that stage game alone, we should
+rather study the evolutionary selection of \emph{choice mechanisms} that are adapted in a rich
+and variable environment
+\citep[e.g.][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche}. % However,
+% formal accounts of the adaptive value of choice mechanisms have focused, for the most part, on
+% the evolutionary benefit of learning rules
+% \citep[e.g.][]{ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o}. \todo{More
+%   references Harley 1981!!!, O Conor \dots} Moreover,
+But only little attention has been paid to modeling the evolutionary competition between choice
+mechanisms in a game-theoretic framework \citep[but
+see][]{ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o}.\todo{More references
+  Harley 1981!!!, O Conor \dots}.
+
+This paper makes two contributions to the literature on evolution of choice mechanisms: one
 methodological and one conceptual. Firstly, on the methodological side, we introduce a
@@
 mechanisms in a statistically variable environment. Concretely, we look at the evolutionary
-competition of choice mechanisms in a ``meta-game'' that consists of the average expected
-payoffs of choice mechanisms when playing arbitrary games (from a given class). In this sense,
-a meta-game captures (the modeller's) assumptions about the relevant statistics of the
-environment in which evolutionary forces operate.
+competition of choice mechanisms in a ``meta-game'' whose payoffs represent the average
+expected fitness choice mechanisms when playing arbitrary games (from a given class) against
+themselves. In this sense, a meta-game captures (the modeller's) assumptions about the relevant
+statistics of the environment in which evolutionary forces operate.
 
@@
 demonstrate that, if we take into account how agents represent uncertainty, this na\"ive
-conclusion is premature.
+conclusion is premature. Under certain reasonable epistemic conditions, non-veridical
+preference representations in terms of regret can be evolutionarily beneficial.
 
@@
 to collapse, as it seems possible to deem rational everything that is observed, given the
-freedom to adjust beliefs and preferences at will. But there are many ways in which
-ascription of beliefs and preferences is constrained further by normative considerations of
-rationality. To begin with, if the DM's uncertainty is about objective chance, it can be argued
-that subjective beliefs should conform (at least roughly) to objective chance. When the DM's
-uncertainty cannot be anchored in an objective notion of chance, then temporal consistency in
-his decision making should at least constrain his subjective beliefs, else he fall prey to
-exploitation by Dutch books. Similarly, in certain situations it may make sense to postulate on
-normative grounds that subjective preferences should be oriented towards tracking objective
-utility, e.g., fitness. For instance, in their classic work \myalert{(Alchian, Friedman)} argue
-that profit maximization is a reasonable assumption for characterizing outcomes in a
-competitive market because only firms behaving in a manner that is consistent with profit
-maximization will survive in the long run.\todo{@Paolo: please add references}
+freedom to adjust beliefs and preferences at will. But there are many ways in which ascriptions
+of beliefs and preferences are constrained by normative considerations of rationality. To begin
+with, if the DM's uncertainty is about objective chance, it can be argued that subjective
+beliefs should conform (at least roughly) to objective chance. When the DM's uncertainty cannot
+be anchored in an objective notion of chance, then temporal consistency in his decision making
+should at least constrain his subjective beliefs, else he fall prey to exploitation by Dutch
+books. Similarly, in certain situations it may make sense to postulate on normative grounds
+that subjective preferences should be oriented towards tracking objective utility, e.g.,
+fitness. For instance, in their classic work \myalert{(Alchian, Friedman)} argue that profit
+maximization is a reasonable assumption for characterizing outcomes in a competitive market
+because only firms behaving in a manner that is consistent with profit maximization will
+survive in the long run.\todo{@Paolo: please add references}
 
@@
 literature on preference evolution (CITE) with basic tenets of adaptationism: we are interested
-in studying the evolutionary competition of choice mechanism, conceived here as pairs of
-subjective preference and subjective belief representation. Evolutionary competition between
+in studying the evolutionary competition of choice mechanisms, conceived here as pairs of
+subjective preference and subjective belief representations. Evolutionary competition between
 choice mechanisms is driven by the expected objective fitness that each choice mechanisms
@@
 complex case of multi-agent decision making first, i.e., game situations. Solitary decision
-making is then easy to deal with subsequently.
-
-\section{The cast}
+making is then easy to deal with subsequently. The next section introduces the choice
+mechanisms we focus on. After that, Section~\ref{sec:model} introduces the ``meta-game''
+modeling approach.
+
+\section{Choice mechanisms: preferences, beliefs and action choice}
 \label{sec:basic-notions}
-
-\subsection{Games} \label{sec:games}
 
@@
 
-With some due simplification, there are two types of approaches to solving games: one focuses
-on the individual agents' perpectives and gives \emph{choice rules}, another considers sets of
-choices of all agents that are, in some sense or other, locked-in. We will look at the former
-here; the latter will be relevant only later, when turn to evolutionary competition between
-choice mechanisms in Section~\ref{sec:model}.\footnote{We make a subtle distinction here
-  between \emph{choice rules} and \emph{choice mechanisms}: the former refers to a function of
-  mapping (subjective) preferences and uncertainty unto choices of acts; the latter is more
-  encompassing and contains the choice rule, together with the particular way of forming or
-  representing preferences and uncertainty.}
-
-\paragraph{Choice rules.} The classical notion of rationality from
-Definition~\ref{def:rationality} also applies to games. Let $A_{-i} = \bigtimes A_j$ for all
-$j \neq i$ be the set of all \emph{profiles} of acts for all players except $i$. If player $i$
-has a belief $\mu_i \in \Delta(A_{-i})$ about the behavior of his opponents, he chooses
-rationally only if his choice $a^*_i$ maximizes expected utility
+With some due simplification, there are two types of approaches to solving games. One looks at
+a collection of players (e.g., a whole population of them) and considers sets of choices of all
+players that are, in some sense or other, stable or in equilibrium. Another approach is to
+focus on each individual agent's perpective and specify which of her actions the agent
+\emph{should} choose if she is rational. We will look at the latter here; the former will be
+relevant only later, when turn to evolutionary competition between choice mechanisms in
+Section~\ref{sec:model}. We will first look at what we call \emph{choice rules}: classical
+proposals of how rational agents should choose acts. We will then introduce our notion of
+\emph{choice mechanism} which makes explicit several elements that choice rules might brush
+under the table.
+
+\subsection{Choice rules} 
+\label{sec:choice-rules}
+
+For the purposes of this paper, we think of a choice rule as a function that takes a
+(strategic) game as input and delivers a choice of action for that game. The literatures has
+suggested a number of choice rules that aspire to capture a normative element of rational
+choice. For reasons that will become clear as we go along, we focus here on three classical
+choice rules: (i) maximin, (ii) Laplace and (iii) regret minimization.
+
+But first an important digression. Rational choice from maximization of expected utilities, as
+given in Definition~\ref{def:rationality}, is \emph{not} a choice rule in the present sense, if
+we apply it strictly. Although the notion applies to game situations, of course, it requires an
+additional component, namely a belief of the DM, before it can say which acts the DM should
+choose. Let $A_{-i} = \bigtimes A_j$ for all $j \neq i$ be the set of all \emph{profiles} of
+acts for all players except $i$. If player $i$ has a belief $\mu_i \in \Delta(A_{-i})$ about
+the behavior of his opponents, he chooses rationally only if his choice $a^*_i$ maximizes
+expected utility
 $\EU(a) = \sum_{\act_{-i} \in \Acts_{-i}} \mu_i(\act_{-i}) \myts \pi_i(a_i, a_{-i})$. So this
-is a choice rule, based on \emph{maximization of expected utilities}. It requires a
-probabilistic belief about the opponents' action choices. In the example from
-Figure~\ref{coordgame1}, a rational player would choose $I$ exactly when he believes that his
-opponent will choose $I$ with a probability at least $\nicefrac{2}{3}$.
-
-If an agent does not have a precise probabilistic belief (see also
-Section~\ref{sec:impr-prob-beli} below), other rules of choice are available. Perhaps the most
-well-known, the \emph{maximin rule}, would tell the agent to choose act $\act^*$ only if it
+requires a probabilistic belief about the opponents' action choices. In the example from
+Figure~\ref{coordgame1}, a rational player would choose act $I$ exactly when he believes that
+his opponent will choose act $I$ with a probability at least $\nicefrac{2}{3}$.
+
+Perhaps the most well-known choice rule that does not require explicitly stating the DM's
+beliefs is the \emph{maximin rule}. It tells our agent to choose act $\act^*$ only if it
 maximizes payoffs for all worst case scenarios. For a strategic game with 2 players this can be
@@
 For the example in Figure~\ref{coordgame1}, the maximim rule looks at the minima in each row,
-asking: what is the worst possible out come for each row act? It is $0$ in either
+asking: what is the worst possible outcome for each row act? It is $0$ in either
 case. Consequently, the maximin rule would not favor either act; players choosing by the
@@
 
-\subsection{Regret theory} \label{sec:regreTheory}
-
-Regret theory has been introduced in decision theory by \citet{Savage1951:The-theory-of-s} and
-Niherens [], and later developed by Bell [1982], Loomes and Sugden [1982], and Fishburn [1982]
-independently. Lately, \citet{HalpernPass2012:Iterated-Regret} showed how the use of regret
-minimization can give solutions to game theoretical puzzles (like the Traveller's dilemma, see
-Example~\ref{example:TravelersDilemma}) in a way that is closer to everyday intuition and
-empirical data. In this paper the notion of regret is defined as in
+The final choice rule that is relevant for our purposes here is \emph{regret
+  minimization}. Regret theory has been introduced in decision theory by
+\citet{Savage1951:The-theory-of-s} and Niherens [], and later developed by Bell [1982], Loomes
+and Sugden [1982], and Fishburn [1982] independently. Lately,
+\citet{HalpernPass2012:Iterated-Regret} showed how the use of regret minimization can give
+solutions to game theoretical puzzles (like the Traveller's dilemma) in a way that is closer to
+everyday intuition and empirical data. In this paper the notion of regret is defined as in
 \citet{HalpernPass2012:Iterated-Regret}:
@@
 
-\begin{example}[Coordination Game]
-  Let us consider the coordination game in Figure \ref{coordgame1}. Figure~\ref{coordgame1reg}
-  shows the pairwise regrets and the regrets of each row-player action. We have
+To illustrate, Figure~\ref{coordgame1reg} shows the pairwise regrets and the regrets of each
+row-player action for the coordination game in Figure \ref{coordgame1}. We have
 $\text{reg}(I)=2$, because when the other player chooses action $I$ the pairwise regret
-  $reg(I,I)$ is $0$ since $I$ is a best reply to $I$, and when the other player chooses $II$
-  the pairwise regret $reg(I, II)$ is $2$ since $\pi_i(II,II)-\pi_i(I,II)=2$. With the same
-  reasoning, $\text{reg}(II)=1$. A regret minimizing player would therefore choose act
-  $II$. $ \medsquare $
+$reg(I,I)$ is $0$ since $I$ is a best reply to $I$, and when the other player chooses $II$ the
+pairwise regret $reg(I, II)$ is $2$ since $\pi_i(II,II)-\pi_i(I,II)=2$. With the same
+reasoning, $\text{reg}(II)=1$. A regret minimizing player would therefore choose act $II$.
 
@@
 
-\end{example}
-
-\begin{example}[The Traveller's Dilemma \citep{HalpernPass2012:Iterated-Regret}]
-\label{example:TravelersDilemma}
-Let us now consider the Traveller's Dilemma case. The story behind the game goes as
-follows. There are two travellers, Ann and Bob, who lost their luggages. Ann and Bob had
-exactly the same luggage and they had insured the luggages with the same insurance company. The
-insurance policy is that the two travellers have to separately claim a certain amount between
-2\$ and 100\$ for the reimbursement, and if they both claim the same amount then they will be
-reimbursed by that amount. Otherwise, if one of them claims more than the other, then the one
-who claimed the higher amount will get the lower amount minus 2\$, while the one who claimed
-the lower amount will get what (s)he claimed plus 2\$. The game is symmetric, and the payoff
-function for both players is:
-\begin{align*}
-  \pi_i(a_i,a_{-i}) = \begin{cases} a_i \text{ \hspace{1cm} if } a_i = a_{-i} \\ a_i + 2 \text{
-      \hspace{.4cm} if } a_i < a_{-i} \\ a_{-i} -2 \text{ \hspace{.25cm} if } a_{-i} <
-    a_i \end{cases}
-\end{align*}
-By a simple computation we have:  $\forall a_i \in \lbrace 96\$, ..., 100\$ \rbrace \text{, }
-\text{reg}(a_i)=3 $ and $\forall a_i \in \lbrace 2\$, ..., 95\$ \rbrace \text{, }
-\text{reg}(a_i)>3$. If we now eliminate all the actions that do not minimize regret in the
-first place and iterate the regret minimization only on the action set $\lbrace 96\$, ...,
-100\$ \rbrace$, we get that 97\$ is the action that minimize regret. Indeed, $\text{reg}(97)=2$
-and $\forall a_i \in \lbrace 96\$, 98\$, 99\$, 100\$ \rbrace \text{, } \text{reg}(a_i)=3
-$. Hence, one step of regret minimizing reasoning eliminates all the actions smaller than 96\$,
-and if we iterate the process once more the unique outcome is 97\$. Finally, it is worth
-noticing that the only rationalizable equilibrium of the game corresponds to the outcome
-$(2,2)$, that is consequently the only Nash equilibrium, the only perfect equilibrium, and the
-only sequential equilibrium of the game.
-
-\begin{itemize}
-\item \textcolor{red}{add here:}
-  \begin{itemize}  
-  \item outcome of rationalizability (max-EU)
-  \item outcome of maximin rule
-  \item outcome of Laplace rule
-  \end{itemize}
-
-\end{itemize}
-
- $ \medsquare $
-
-\end{example}
+% \begin{example}[The Traveller's Dilemma \citep{HalpernPass2012:Iterated-Regret}]
+% \label{example:TravelersDilemma}
+% Let us now consider the Traveller's Dilemma case. The story behind the game goes as
+% follows. There are two travellers, Ann and Bob, who lost their luggages. Ann and Bob had
+% exactly the same luggage and they had insured the luggages with the same insurance company. The
+% insurance policy is that the two travellers have to separately claim a certain amount between
+% 2\$ and 100\$ for the reimbursement, and if they both claim the same amount then they will be
+% reimbursed by that amount. Otherwise, if one of them claims more than the other, then the one
+% who claimed the higher amount will get the lower amount minus 2\$, while the one who claimed
+% the lower amount will get what (s)he claimed plus 2\$. The game is symmetric, and the payoff
+% function for both players is:
+% \begin{align*}
+%   \pi_i(a_i,a_{-i}) = \begin{cases} a_i \text{ \hspace{1cm} if } a_i = a_{-i} \\ a_i + 2 \text{
+%       \hspace{.4cm} if } a_i < a_{-i} \\ a_{-i} -2 \text{ \hspace{.25cm} if } a_{-i} <
+%     a_i \end{cases}
+% \end{align*}
+% By a simple computation we have:  $\forall a_i \in \lbrace 96\$, ..., 100\$ \rbrace \text{, }
+% \text{reg}(a_i)=3 $ and $\forall a_i \in \lbrace 2\$, ..., 95\$ \rbrace \text{, }
+% \text{reg}(a_i)>3$. If we now eliminate all the actions that do not minimize regret in the
+% first place and iterate the regret minimization only on the action set $\lbrace 96\$, ...,
+% 100\$ \rbrace$, we get that 97\$ is the action that minimize regret. Indeed, $\text{reg}(97)=2$
+% and $\forall a_i \in \lbrace 96\$, 98\$, 99\$, 100\$ \rbrace \text{, } \text{reg}(a_i)=3
+% $. Hence, one step of regret minimizing reasoning eliminates all the actions smaller than 96\$,
+% and if we iterate the process once more the unique outcome is 97\$. Finally, it is worth
+% noticing that the only rationalizable equilibrium of the game corresponds to the outcome
+% $(2,2)$, that is consequently the only Nash equilibrium, the only perfect equilibrium, and the
+% only sequential equilibrium of the game.
+
+% \begin{itemize}
+% \item \textcolor{red}{add here:}
+%   \begin{itemize}  
+%   \item outcome of rationalizability (max-EU)
+%   \item outcome of maximin rule
+%   \item outcome of Laplace rule
+%   \end{itemize}
+
+% \end{itemize}
+
+%  $ \medsquare $
+
+% \end{example}
 
@@
 
-\noindent The acts selected by the maximin rule for the negative regret transformation are exactly
-the acts selected by regret minimization for the original game.
-
-This means that we can think of the maximin rule and regret minimization as being two
-instantiations of the same choice rule, but operating on different subjective representations
-of utility: while maximin considers actual objective payoffs, regret minimization considers
-non-veridical, regret-based subjective utilities. As the example of Figure~\ref{coordgame1}
-shows, the same choice rule can give different behavioral predictions on different preference
-representations. While maximin is indifferent between $I$ and $II$, regret minimization
-uniquely selects $II$.
-
-When we think of regret as a non-veridical subjective payoff representation, we can also pair
-it with other choice rules, such as the maximization of expected utility and Laplace's rule
-(which is just a special case of the former). It turns out, however, that this makes no
-noticeable difference:
-
-\begin{fact} \label{fact:maxEU-minReg} For any strategic game $G$ and any arbitrary
-  probabilistic belief $\mu \in \Delta(A_{-i})$ about the opponents' behavior, the acts
-  selected by maximization of expected utility for $G$ under $\mu$ are exactly the acts
-  selected by the maximization of expected utility for the negative regret transform of $G$
-  under $\mu$ \citep[e.g.][]{HalpernPass2012:Iterated-Regret}.
-\end{fact}
-
-\noindent In other words, given the same probabilistic belief, maximization of expected
-(objective) payoff and minimization of expected (subjective) regret are behaviorally
-equivalent. This holds for arbitrary games, as well as for solitary decision situations.
-
-\todo[inline]{Minor edits up to here}
-
-\bigskip
-
-In sum, we have so far considered four different alternatives, each differing along a
-preference and a belief dimension. As for preference representations, agents could either
-target objective payoffs, or consider non-veridical subjective regret transformations.
-Given a game $G$, we will denote by $ \tau^{reg}(G)$ the regret representation (corresponding to the negative regret transformation) of the game, and $\tau^{\pi}(G)$ the objective representation (corresponding to the identity transformation) of the game.
-\\
-As for
-beliefs, agents could either hold probabilistic belief or not. In the former case, we would
-assume that they maximize expectations under whatever preference representation they hold; in
-the latter, we would assume that they play maximin based on their preference
-representations. There are doubtlessly many more possible preference and belief types, but
-these are the main characters in the plot to follow.
-
-Before we turn to evolutionary competition between choice principles, we should justify our
-focus on the two choice rules. In the following we argue that both the minimax rule, as well as the maximization of expected utility 
-(and the Laplace rule as a special case) can be viewed as the same choice rule under different representations of
-uncertainty.
+\noindent Acts selected by the maximin rule for the negative regret transformation of $G$ are
+always exactly the acts selected by regret minimization for the original game $G$.\todo{can we
+  cite a paper that proves this? should we give a proof ourselves?}
+
+This means that we can think of the maximin rule and regret minimization as essentially the
+same operation on different subjective representations of preference: while maximin considers
+actual objective payoffs (as defined by the modeller's game), regret minimization considers
+non-veridical, regret-based subjective preferences. As the example of Figure~\ref{coordgame1}
+shows, different subjective preferences can give rise to different choice prescriptions all
+else equal. While maximin is indifferent between $I$ and $II$, regret minimization uniquely
+selects $II$.
+
+In sum, a choice rule is a normative prescription of action choices for a rational agent in any
+game situation. Choice rules may rest on implicit assumptions about what the DM believes (e.g.,
+when interpreting Laplace rule as rational choice under flat beliefs). They may also make
+implicit assumptions about what the DM prefers (e.g., when reconstructing regret minimization
+in terms of maximin-choices on the regret transformation). This is rather messy. To disentangle
+and avoid confusion, we turn to choice mechanisms.
+
+\subsection{Choice mechanisms}
+\label{sec:choice-mechanisms}
+
+We think of a choice mechanism as a function that maps a game (or more generally any decision
+situation) onto a triple that consists of: (i) the DM's \emph{subjective preferences} (possibly
+diverging from the actual objective payoffs defined ) in the game, (ii) the DM's
+\emph{subjective beliefs} about the opponents' behavior, and (iii) an \emph{action selection
+  function} which maps the former two components onto a concrete choice of action in the
+game. A choice mechanism could be a set of distinct heuristics (the DM's \emph{adaptive
+  toolbox}) that have little in common
+\citep[e.g.][]{TverskyKahnemann1981:The-Framing-of-,GigerenzerGoldstein1996:Reasoning-the-F,ScheibehenneRieskamp2013:Testing-the-Ada}. But
+to keep matters simple, we will here only look at choice mechanisms that use a uniform way of
+forming preferences and beliefs and a uniform way of making choices based on them. More
+concretely, we focus on two \emph{preference types} and two \emph{belief types}, and neglect
+variation in the action selection component.
+
+We are most interested here in studying whether evolutionary pressure could support
+non-veridical subjective preferences under certain conditions. We therefore focus on two
+\emph{preference types}: veridical types $\tau^\pi$, who use the actual payoff function $\pi$ of the
+actual game $G$, and regret types $\tau^{reg}$, who look at the regret transformation of the
+actual game $G$.
+
+It turns out that whether $\tau^{reg}$ can have a fitness advantage over $\tau^\pi$ depends on
+the general \emph{kind} of (probabilistic) beliefs that DM's form about the opponent's
+behavior. In other words, we even abstract away from the content of the DM's beliefs about his
+opponents' behavior that he could have acquired by learning or observation, but first turn on
+the more general question of how uncertainty should be represented in order to interact with
+subjective preferences in such a way that the resulting behavior will be fitness enhancing for
+the DM in the long run. We consider therefore two \emph{belief types} (to be defined below):
+imprecise belief types $\Delta(A_{-i})$, who have a set of probabilistic beliefs about the
+opponents' behavior and precise belief types $\overline{\mu}$ who have a single probabilistic
+belief.
+
+The following subsection describes what these belief types are and how a single action
+selection function (maximin expected utility) gives rise to an intersting parallel with
+classical choice rules.
 
@@
 \\
+
+\subsection{Choice mechanisms \& classical choice rules}
+
+Fixing the action selection component to maximin expected utility, and allowing two belief and
+two preference types, we end up with four basic choice mechanisms summed up in
+Table~\ref{tab:CMs}. Different choice mechanisms can give rise to identical action predictions,
+either in a restricted class of games, or in general. This is also the case here.
+
+\begin{table}[t]
+  \centering
+  \begin{tabular}{ccc}
+    preference type & belief type & corresponding choice rule \\ \midrule
+    $\tau^\pi$ & $\overline{\mu}$ & Laplace \\
+    $\tau^\pi$ & $\Delta(A_{-i})$ & maximin \\ 
+    $\tau^{reg}$ & $\overline{\mu}$ & Laplace \\
+    $\tau^{reg}$ & $\Delta(A_{-i})$ & regret minimization \\ 
+  \end{tabular}
+  \caption{Overview relevant choice mechanisms and the corresponding (behaviorally equivalent) classical choice rule}
+  \label{tab:CMs}
+\end{table}
+
+\begin{fact} \label{fact:maxEU-minReg} For any strategic game $G$ and any arbitrary
+  probabilistic belief $\mu \in \Delta(A_{-i})$ about the opponents' behavior, the acts
+  selected by maximization of expected utility for $G$ under $\mu$ are exactly the acts
+  selected by the maximization of expected utility for the negative regret transform of $G$
+  under $\mu$ \citep[e.g.][]{HalpernPass2012:Iterated-Regret}.
+\end{fact}
+
+\noindent In other words, given the same probabilistic belief, maximization of expected
+(objective) payoff and minimization of expected (subjective) regret are behaviorally
+equivalent. This holds for arbitrary games, as well as for solitary decision situations. On the
+other hand, the following does not hold in general:
+
+\begin{fact} \label{fact:equivalence2x2}
+In the class of $2 \times 2$ symmetric games, players $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg},\overline{\mu})$ are behaviorally equivalent.
+\end{fact}
+
+Moreover, our choice mechanism $(\tau^{\pi}, \Delta(A_{-i}))$ turns out to be the objective
+maximinimizer, player $(\tau^{reg}, \Delta(A_{-i}))$ is the regret minimizer, player
+$(\tau^{\pi}, \overline{\mu})$ is the objective expected utility maximizer, and player
+$(\tau^{reg}, \overline{\mu})$ is the expected regret minimizer. In other words, behaviorally,
+the choice mechanisms we defined here correspond to the classical choice rules in
+Table~\ref{tab:CMs}.
+
+\bigskip
+\bigskip
+
+\todo[inline]{Micha rewrite up to here!!! Please check which bits of text/information from the
+  following need to be integrated and what can go.}
+
+\bigskip
+\bigskip
+
+In sum, we have so far considered four different alternatives, each differing along a
+preference and a belief dimension. As for preference representations, agents could either
+target objective payoffs, or consider non-veridical subjective regret transformations.
+Given a game $G$, we will denote by $ \tau^{reg}(G)$ the regret representation (corresponding to the negative regret transformation) of the game, and $\tau^{\pi}(G)$ the objective representation (corresponding to the identity transformation) of the game.
+\\
+As for
+beliefs, agents could either hold probabilistic belief or not. In the former case, we would
+assume that they maximize expectations under whatever preference representation they hold; in
+the latter, we would assume that they play maximin based on their preference
+representations. There are doubtlessly many more possible preference and belief types, but
+these are the main characters in the plot to follow.
+
+Before we turn to evolutionary competition between choice principles, we should justify our
+focus on the two choice rules. In the following we argue that both the minimax rule, as well as the maximization of expected utility 
+(and the Laplace rule as a special case) can be viewed as the same choice rule under different representations of
+uncertainty.
 
@@
 
-\begin{figure}
-\begin{center}%
-\begin{tabular}{|c|c|c|}
-\hline 
- & I & II\tabularnewline
-\hline 
-\hline 
-I & 0;0 & -2;-1\tabularnewline
-\hline 
-II & -1;-2 & 0;0\tabularnewline
-\hline 
-\end{tabular}\end{center}
-
-\protect\caption{Regret representation $\tau^{reg}(G^C)$}
-\label{coordgame1reg}
-\end{figure}
-
 \end{example}
@@
 
-Before concluding this section, it is worth stressing that player $(\tau^{\pi}, \Delta(A_{-i}))$ turns out to be the objective maximinimizer, player $(\tau^{reg}, \Delta(A_{-i}))$ is the regret minimizer, player $(\tau^{\pi}, \overline{\mu})$ is the objective expected utility maximizer, and player $(\tau^{reg}, \overline{\mu})$ is the expected regret minimizer.
-Moreover, the following fact holds.
-
 \iffalse
@@
 \fi
-
-\begin{fact} \label{fact:equivalence2x2}
-
-In the class of $2 \times 2$ symmetric games, players $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg},\overline{\mu})$ are behaviorally equivalent.
-
-\end{fact}
-
-\noindent Two remarks. Firstly, Fact \ref{fact:equivalence2x2} does not hold for $n \times n$
-symmetric games in general. Secondly, we treat behaviorally equivalent types as distinct,
-because we assume that what is selected by biological evolution is not choice behavior as such,
-but the mechanism which generates behavior. This matters in particular if we assume that
-mutations affect different components of the behavior generating mechanisms (see below).
 
@@
 configurations are attracted to states with only three player types:
-$\tuple{\tau^{reg}, \Delta(A)}$, $\tuple{\tau^{reg}, \bar{\mu}}$ and
-$\tuple{\tau^{\pi}, \bar{\mu}}$. The relative proportions of these depend on the initial
+$\tuple{\tau^{reg}, \Delta(A)}$, $\tuple{\tau^{reg}, \overline{\mu}}$ and
+$\tuple{\tau^{\pi}, \overline{\mu}}$. The relative proportions of these depend on the initial
 population.\todo{check uniform notation for player types: round vs.~square brackets} This
@@
     $\tuple{\tau^{reg}, \Delta(A)}$ & $\tuple{\tau^{reg},
-      \bar{\mu}}$ & $\tuple{\tau^{\pi}, \bar{\mu}}$ \\ \hline
+      \overline{\mu}}$ & $\tuple{\tau^{\pi}, \overline{\mu}}$ \\ \hline
     0.279  &   0.383 &    0.281 
@@
  & $\tuple{\tau^{alt}, \Delta(A)}$
- & $\tuple{\tau^{reg}, \bar{\mu}}$ 
- & $\tuple{\tau^{\pi}, \bar{\mu}}$ 
- & $\tuple{\tau^{com}, \bar{\mu}}$
- & $\tuple{\tau^{alt}, \bar{\mu}}$ \\ 
+ & $\tuple{\tau^{reg}, \overline{\mu}}$ 
+ & $\tuple{\tau^{\pi}, \overline{\mu}}$ 
+ & $\tuple{\tau^{com}, \overline{\mu}}$
+ & $\tuple{\tau^{alt}, \overline{\mu}}$ \\ 
   \hline
@@
   $\tuple{\tau^{alt}, \Delta(A)}$ & 5.949 & 5.722 & 5.326 & 6.396 & 5.949 & 5.949 & 5.326 & 6.568 \\
-  $\tuple{\tau^{reg}, \bar{\mu}}$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
-  $\tuple{\tau^{\pi}, \bar{\mu}}$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
-  $\tuple{\tau^{com}, \bar{\mu}}$ & 6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\
-  $\tuple{\tau^{alt}, \bar{\mu}}$ & 6.331 & 5.893 & 5.497 & 6.566 & 6.331 & 6.331 & 5.497 & 7.152 \\
+  $\tuple{\tau^{reg}, \overline{\mu}}$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
+  $\tuple{\tau^{\pi}, \overline{\mu}}$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
+  $\tuple{\tau^{com}, \overline{\mu}}$ & 6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\
+  $\tuple{\tau^{alt}, \overline{\mu}}$ & 6.331 & 5.893 & 5.497 & 6.566 & 6.331 & 6.331 & 5.497 & 7.152 \\
    \hline                          
@@
 regret minimization $\tuple{\tau^{reg}, \Delta(A)}$ is behaviorally equivalent with expected
-regret minimization $\tuple{\tau^{reg}, \bar{\mu}}$ and expected utility maximization
-$\tuple{\tau^{\pi}, \bar{\mu}}$. This is no longer true when we look at arbitrary $n \times n$
+regret minimization $\tuple{\tau^{reg}, \overline{\mu}}$ and expected utility maximization
+$\tuple{\tau^{\pi}, \overline{\mu}}$. This is no longer true when we look at arbitrary $n \times n$
 games with $n \ge 2$. We should therefore see what happens in a broader class of games.
@@
  & $\tuple{\tau^{alt}, \Delta(A)}$
- & $\tuple{\tau^{reg}, \bar{\mu}}$ 
- & $\tuple{\tau^{\pi}, \bar{\mu}}$ 
- & $\tuple{\tau^{com}, \bar{\mu}}$
- & $\tuple{\tau^{alt}, \bar{\mu}}$ \\ 
+ & $\tuple{\tau^{reg}, \overline{\mu}}$ 
+ & $\tuple{\tau^{\pi}, \overline{\mu}}$ 
+ & $\tuple{\tau^{com}, \overline{\mu}}$
+ & $\tuple{\tau^{alt}, \overline{\mu}}$ \\ 
   \midrule
@@
   $\tuple{\tau^{alt}, \Delta(A)}$ & 5.968 & 5.923 & 5.363 & 6.685 & 5.975 & 5.975 & 5.086 & 6.973 \\
-  $\tuple{\tau^{reg}, \bar{\mu}}$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
-  $\tuple{\tau^{\pi}, \bar{\mu}}$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
-  $\tuple{\tau^{com}, \bar{\mu}}$ & 6.529 & 6.680 & 5.445 & 7.276 & 6.542 & 6.542 & 5.521 & 7.440 \\
-  $\tuple{\tau^{alt}, \bar{\mu}}$ & 6.450 & 6.337 & 5.772 & 6.978 & 6.457 & 6.457 & 5.479 & 7.500 \\
+  $\tuple{\tau^{reg}, \overline{\mu}}$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
+  $\tuple{\tau^{\pi}, \overline{\mu}}$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
+  $\tuple{\tau^{com}, \overline{\mu}}$ & 6.529 & 6.680 & 5.445 & 7.276 & 6.542 & 6.542 & 5.521 & 7.440 \\
+  $\tuple{\tau^{alt}, \overline{\mu}}$ & 6.450 & 6.337 & 5.772 & 6.978 & 6.457 & 6.457 & 5.479 & 7.500 \\
    \bottomrule                         
@@
 uniform. Most importantly, the regret minimizing type $\tuple{\tau^{reg}, \Delta(A)}$ is
-strictly dominated by $\tuple{\tau^{reg}, \bar{\mu}}$ and by $\tuple{\tau^{\pi}, \bar{\mu}}$ in
+strictly dominated by $\tuple{\tau^{reg}, \overline{\mu}}$ and by $\tuple{\tau^{\pi}, \overline{\mu}}$ in
 the meta-game from Table~\ref{tab:ExpectedFitness_10x10}. This means that while regret
@@
 $\tuple{\tau^{reg}, \Delta(A)}$, it is not the case that regret types \emph{as such} are weeded
-out by selection. Since, by Fact~\ref{fact:maxEU-minReg}, $\tuple{\tau^{reg}, \bar{\mu}}$ and
-$\tuple{\tau^{\pi}, \bar{\mu}}$ are generally behaviorally equivalent, it remains that
+out by selection. Since, by Fact~\ref{fact:maxEU-minReg}, $\tuple{\tau^{reg}, \overline{\mu}}$ and
+$\tuple{\tau^{\pi}, \overline{\mu}}$ are generally behaviorally equivalent, it remains that
 selection based on meta-games constructed from $n \times n$ games will still not eradicate all
@@
 suppose that only preference types compete and that agents' epistemic types are exogenously
-given, in such a way that agents hold flat probabilistic beliefs $\bar{\mu}$ with probability
+given, in such a way that agents hold flat probabilistic beliefs $\overline{\mu}$ with probability
 $1-p$ and are of type $\Delta(A)$ with probability $p$. This transforms the meta-game from
@@
 actual state of the world, which we selected uniformly at random from the available states in
-the current decision problem. Player types, consisting of epistemic types $\bar{\mu}$ and
+the current decision problem. Player types, consisting of epistemic types $\overline{\mu}$ and
 $\Delta(\States)$ and preference types $\tau^{reg}$ and $\tau^{\pi}$, give rise to behavior in
@@
  & $\tuple{\tau^{\pi}, \Delta(A)}$ 
- & $\tuple{\tau^{reg}, \bar{\mu}}$ 
- & $\tuple{\tau^{\pi}, \bar{\mu}}$ 
+ & $\tuple{\tau^{reg}, \overline{\mu}}$ 
+ & $\tuple{\tau^{\pi}, \overline{\mu}}$ 
  \\ \midrule
@@
 Facts~\ref{fact:maxEU-minReg} and \ref{fact:equivalence2x2} still apply:
-$\tuple{\tau^{reg}, \bar{\mu}}$ and $\tuple{\tau^{\pi}, \bar{\mu}}$ are behaviorally equivalent
+$\tuple{\tau^{reg}, \overline{\mu}}$ and $\tuple{\tau^{\pi}, \overline{\mu}}$ are behaviorally equivalent
 in general, and $\tuple{\tau^{reg}, \Delta(A)}$ is behaviorally equivalent to the former two in
@@
 results in Table~\ref{tab:SolitaryDecisions} in that the averages for $\tuple{\tau^{reg},
-  \bar{\mu}}$ and $\tuple{\tau^{\pi}, \bar{\mu}}$ are identical. But since we included decision
+  \overline{\mu}}$ and $\tuple{\tau^{\pi}, \overline{\mu}}$ are identical. But since we included decision
 problems with more acts and more states as well, the averages for regret minimizers
@@
 
-So far, we have assumed that epistemic types $\bar{\mu}$ hold an unbiased, flat belief. It is
+So far, we have assumed that epistemic types $\overline{\mu}$ hold an unbiased, flat belief. It is
 worthwhile considering what happens when this assumption is relaxed and we allow agents with
@@
 should come first and beliefs be a function of it). As a result, the average payoffs of types
-$\tuple{\tau^{reg}, \bar{\mu}}$ and $\tuple{\tau^{\pi}, \bar{\mu}}$ are still the exact same
+$\tuple{\tau^{reg}, \overline{\mu}}$ and $\tuple{\tau^{\pi}, \overline{\mu}}$ are still the exact same
 (because we compare what agents with different preference types would do under the same

### 2015-11-05 paper/paper.tex
Paolo tweaks to Sec 3.3 and beyond

@@
 
+\subsection{Choice mechanisms take2}
+
+In the previous section we introduced choice rules generating behavior in a game as functions from a game to an action choice.
+In the general form, given a class of games $\mathcal{G}$, a choice rule is then thought as a function $c: \mathcal{G} \rightarrow A_i $.
+In this section instead we want to show that a more intelligible and perspicuous way of understanding behavior generating mechanisms may be as functions of a subjective preference and an epistemic state of the agents.
+Then, given a set of subjective preferences $ \Theta $ [@Paolo: minimally define subjective preferences somewhere above] and a set of epistemic states (or belief types) $E$, a choice mechanism is a function $\kappa: \Theta \times E \rightarrow A_i $.
+We will see in a moment that from this perspective we gain a more unified and structured insight on the choice rules presented above.
+
+More
+concretely, we focus on two \emph{preference types} and two \emph{belief types}.
+We view a preference type as a function $\tau: \mathcal{G} \rightarrow \Theta$, and a belief type as a general disposition to form beliefs about the co-player’s behavior.
+The two possible dispositions that we take account of are probabilistic (precise) belief and non-probabilistic (imprecise) belief, as we will explain in the next section.
+
+We are most interested here in studying whether evolutionary pressure could support
+non-veridical subjective preferences under certain conditions. We therefore consider two
+\emph{preference types}: veridical type $\tau^\pi$, who uses the actual payoff function $\pi$ of the
+actual game $G$, and regret type $\tau^{reg}$, who looks at the regret transformation of the
+actual game $G$.
+
+The choice mechanism that we use in this paper is \textit{maxmin expected utility} [GS89], for reasons that will be clear and justified in the following two sections.
+
 \subsection{Imprecise probabilistic beliefs}
@@
 According to standard Bayesianism, one should always be able to determine a precise betting rate (that immediately translates into a precise probability distribution), which is fair, in the sense that the DM is indifferent between betting on or against red at the fair rate, and would bet on red at any rate that is more favourable than the fair rate and against red at any rate that is less favourable.
-In this case, a strict Bayesian, in the absence of any further information, would probably rely on the principle of insufficient reason and answer that the DM should have a uniform distribution that considers all the outcomes equipossible.
+In the case of the bag on my desk, a strict Bayesian, in the absence of any further information, would probably rely on the \textit{principle of insufficient reason} and answer that the DM should have a uniform distribution that considers all the outcomes equipossible.
 \\
@@
 Given the information available in this case we would have $\underline{P}(R)=0$ and $\overline{P}(R)=1$.
-This approach appears particularly relevant and appropriate in a game theoretical context.
+This approach appears particularly relevant in a game theoretical context.
 Indeed, in a recent paper [Battigalliet al.15] Battigalli et al.
@@
 
-In decision theory, the imprecise probability model is in line with most of the representation results about uncertainty [GilboaSchmeidler89,KMM06], and seems justified by empirical observations too.
+In evolutionary game theory, for instance, players in a population obviously face uncertainty about the composition of the population that they are part of, and consequently about the co-player that they are randomly paired with at each round and about the co-player's action.
+We represent this uncertainty in two different ways that correspond to the two approaches discussed above: a Bayesian uniform distribution and an imprecise probability set.
+This amounts to having two different belief types, $ \overline{\mu}$ and $ \Delta(A_{-i}) \rbrace $, where $\overline{\mu}$ stands for the uniform distribution and $\Delta(A_{-i})$ is the probability set, defined as follows:
+
+\begin{itemize}
+
+\item $ \Delta(A_{-i}):=\lbrace \mu \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu(a_{-i}) = 1 \rbrace$;
+
+\item $\overline{\mu} \in \Delta(A_{-i})$ is the probability measure over the co-player's actions such that: $\forall a_{-i} \in A_{-i}$, $\overline{\mu}(a_{-i})= \frac{1}{|A_{-i}|}$.
+
+\end{itemize}
+
+Hence, we consider two possible epistemic states in the face of uncertainty.
+The belief type $\Delta(A_{-i})$ represents a situation of non-Bayesian radical uncertainty, where the players are not able to narrow down the set of probability distributions to a single one and they consider all of them as possible.
+The other belief type $\overline{\mu}$ conceptualizes the uncertainty about the population by using the principle of insufficient reason and ascribes equal probability to all the possible alternatives.
+As we have seen, both options are reasonable and justifiable ways to deal with situations of uncertainty [REFERENCES].
+\\
+
+In decision theory, the imprecise probability model is in line with most of the representation results in decision making under uncertainty [GilboaSchmeidler89,KMM06], and seems justified by empirical observations too.
 
@@
 
-A huge body of experimental literature strongly suggests that agents are generally uncertainty
+Evidence from experimental literature suggests that agents are mainly uncertainty
 averse [REF]. In line with empirical data,
@@
 utility. The resulting behavior is then produced by maximinimizing the subjective utility
-given by the player type over the set of probabilities given by the belief state, or epistemic type, of the agent.
-
-In full generality, we think of an epistemic type as a general disposition to form beliefs about the co-player’s behavior.
-Players in the population obviously face uncertainty about the composition of the population that they are part of, and consequently about the type of co-player that they are randomly paired with at each round and about the co-player's actions.
-We represent this uncertainty in two different ways that correspond to the two approaches discussed above: a Bayesian uniform distribution and an imprecise probability set.
-This amounts to having two different epistemic types, $ \overline{\mu}$ and $ \Delta(A_{-i}) \rbrace $, where $\overline{\mu}$ stands for the uniform distribution and $\Delta(A_{-i})$ is the probability set, defined as follows:
-
-\begin{itemize}
-
-\item $ \Delta(A_{-i}):=\lbrace \mu \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu(a_{-i}) = 1 \rbrace$;
-
-\item $\overline{\mu} \in \Delta(A_{-i})$ is the probability measure over the co-player's actions such that: $\forall a_{-i} \in A_{-i}$, $\overline{\mu}(a_{-i})= \frac{1}{|A_{-i}|}$.
-
-\end{itemize}
-
-Hence, we consider two possible epistemic states in the face of uncertainty.
-The epistemic type $\Delta(A_{-i})$ represents a situation of non-Bayesian radical uncertainty, where the players are not able to narrow down the set of probability distributions to a single one and they consider all of them as possible.
-The other epistemic type $\overline{\mu}$ conceptualizes the uncertainty about the population by using the principle of insufficient reason and ascribes equal probability to all the possible alternatives.
-As we have seen, both options are reasonable and justifiable ways to deal with situations of uncertainty [REFERENCES].
-\\
+given by the player (preference, UNIFORM TERMINOLOGY CHECK) type over the set of probabilities given by the belief type of the agent.
 
@@
 
-Fixing the action selection component to maximin expected utility, and allowing two belief and
-two preference types, we end up with four basic choice mechanisms summed up in
-Table~\ref{tab:CMs}. Different choice mechanisms can give rise to identical action predictions,
+Fixing the choice mechanism (action selection component) to maximin expected utility, and allowing two belief and
+two preference types, we regain all the choice rules considered in sectionNN from a more general and unified standpoint, as it is summed up in
+Table~\ref{tab:CMs}. \\
+We are now in the position of formally deriving behavior from a pair $(\theta, e) \in \Theta \times E$.
+
+\begin{definition} \label{def:utility-belief}
+
+Given a game $G$, an action $a_i \in A_i$, and a belief $\mu \in \lbrace \mu' \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu'(a_{-i}) = 1 \rbrace$, we define $\tau(G)(a_i, \mu):= \sum_{a_{-i} \in A_{-i}} \tau(G)(a_i, a_{-i}) \cdot \mu(a_{-i})$.
+
+\end{definition}
+
+\begin{definition} \label{def:maxminSEU}
+
+Given a game $G$ and a player $(\tau, e)$, we define $\text{maxmin}(\tau(G), e):= \lbrace a'_i \in A_i : a_i \in \text{max}_{a_i \in A_i} \text{ min}_{\mu \in e} \text{ } \tau(G)(a_i, \mu) \rbrace$.
+
+\end{definition}
+
+[[\noindent Definition \ref{def:expected fitness} gives the expected evolutionary fitness of player $(\tau, e)$ against player $(\tau', e')$ in game $G$.\footnote{As already specified in the previous example, we assume that, whenever the set $\text{maxmin}(\tau(G), e)$ is not a singleton, the player $(\tau, e)$ will mix with equal probability among the actions in $\text{maxmin}(\tau(G), e)$.}
+[OF COURSE we will postpone the definition of evolutionary fitness, it is only momentarily here!]
+\begin{definition} \label{def:expected fitness}
+
+Given a game $G \in \mathcal{G}$, a player $(\tau, e)$, and a player $(\tau', e')$, we define $\pi^G((\tau, e),(\tau', e')):= \pi^G(\text{maxmin}(\tau(G), e),\text{maxmin}(\tau'(G), e'))$.
+
+\end{definition}
+[OF COURSE we will postpone the definition of evolutionary fitness, it is only momentarily here!]]]
+
+It is then worth stressing here that $\kappa(\tau^{\pi}, \Delta(A_{-i}))$ turns out to be the objective
+maximinimizer, $\kappa(\tau^{reg}, \Delta(A_{-i}))$ corresponds to the regret minimizer,
+$\kappa(\tau^{\pi}, \overline{\mu})$ is the objective expected utility maximizer (with flat beliefs), and
+$\kappa(\tau^{reg}, \overline{\mu})$ is the expected regret minimizer (with flat beliefs).
+Moreover, different subjective preferences and belief types can give rise to identical action predictions,
 either in a restricted class of games, or in general. This is also the case here.
@@
 \end{fact}
-
-Moreover, our choice mechanism $(\tau^{\pi}, \Delta(A_{-i}))$ turns out to be the objective
-maximinimizer, player $(\tau^{reg}, \Delta(A_{-i}))$ is the regret minimizer, player
-$(\tau^{\pi}, \overline{\mu})$ is the objective expected utility maximizer, and player
-$(\tau^{reg}, \overline{\mu})$ is the expected regret minimizer. In other words, behaviorally,
-the choice mechanisms we defined here correspond to the classical choice rules in
-Table~\ref{tab:CMs}.
-
-\bigskip
-\bigskip
-
-\todo[inline]{Micha rewrite up to here!!! Please check which bits of text/information from the
-  following need to be integrated and what can go.}
-
-\bigskip
-\bigskip
-
-In sum, we have so far considered four different alternatives, each differing along a
-preference and a belief dimension. As for preference representations, agents could either
-target objective payoffs, or consider non-veridical subjective regret transformations.
-Given a game $G$, we will denote by $ \tau^{reg}(G)$ the regret representation (corresponding to the negative regret transformation) of the game, and $\tau^{\pi}(G)$ the objective representation (corresponding to the identity transformation) of the game.
-\\
-As for
-beliefs, agents could either hold probabilistic belief or not. In the former case, we would
-assume that they maximize expectations under whatever preference representation they hold; in
-the latter, we would assume that they play maximin based on their preference
-representations. There are doubtlessly many more possible preference and belief types, but
-these are the main characters in the plot to follow.
-
-Before we turn to evolutionary competition between choice principles, we should justify our
-focus on the two choice rules. In the following we argue that both the minimax rule, as well as the maximization of expected utility 
-(and the Laplace rule as a special case) can be viewed as the same choice rule under different representations of
-uncertainty.
-
-To sum up, here we consider the choice of an action as depending on two features: the subjective preference and the belief state. Definition \ref{def:choice rule} makes this point clear.
-
-\begin{definition} \label{def:choice rule}
-
-Given a set of subjective preferences $\Theta$ and a set of epistemic types $E$, we define \textit{choice rule} a function $\kappa: \Theta \times E  \rightarrow A_i$ that associates an action choice to a pair $(\theta, e) \in \Theta \times E$.
-
-\end{definition}
-
-According to what we argued in this section, we will assume that the choice rule that turns subjective preferences and beliefs into actions is maxmin expected utility.
 
@@
 
-We are now in the position of deriving behavior directly from the pair $(\tau, e)$.
-Definitions \ref{def:utility-belief} and \ref{def:maxminSEU} simply formalize the notions of subjective expected utility and maxmin subjective expective utility, respectively.
-
-\begin{definition} \label{def:utility-belief}
-
-Given a game $G$, an action $a_i \in A_i$, and a belief $\mu \in \lbrace \mu' \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu'(a_{-i}) = 1 \rbrace$, we define $\tau(G)(a_i, \mu):= \sum_{a_{-i} \in A_{-i}} \tau(G)(a_i, a_{-i}) \cdot \mu(a_{-i})$.
-
-\end{definition}
-
-\begin{definition} \label{def:maxminSEU}
-
-Given a game $G$ and a player $(\tau, e)$, we define $\text{maxmin}(\tau(G), e):= \lbrace a'_i \in A_i : a_i \in \text{max}_{a_i \in A_i} \text{ min}_{\mu \in e} \text{ } \tau(G)(a_i, \mu) \rbrace$.
-
-\end{definition}
-
-\noindent Definition \ref{def:expected fitness} gives the expected evolutionary fitness of player $(\tau, e)$ against player $(\tau', e')$ in game $G$.\footnote{As already specified in the previous example, we assume that, whenever the set $\text{maxmin}(\tau(G), e)$ is not a singleton, the player $(\tau, e)$ will mix with equal probability among the actions in $\text{maxmin}(\tau(G), e)$.}
-
-\begin{definition} \label{def:expected fitness}
-
-Given a game $G \in \mathcal{G}$, a player $(\tau, e)$, and a player $(\tau', e')$, we define $\pi^G((\tau, e),(\tau', e')):= \pi^G(\text{maxmin}(\tau(G), e),\text{maxmin}(\tau'(G), e'))$.
-
-\end{definition}
-
 %\todo[inline]{should we explain here, or very soon, what the resulting types really are: regret minimizers, maximin players \dots}
@@
 
+\bigskip
+\bigskip
+
+\todo[inline]{PAOLO rewrite up to here!!! BUT the last 2-3 paragraphs must be rearranged a bit more!}
+
+\bigskip
+\bigskip
+
+In sum, we have so far considered four different alternatives, each differing along a
+preference and a belief dimension. As for preference representations, agents could either
+target objective payoffs, or consider non-veridical subjective regret transformations.
+Given a game $G$, we will denote by $ \tau^{reg}(G)$ the regret representation (corresponding to the negative regret transformation) of the game, and $\tau^{\pi}(G)$ the objective representation (corresponding to the identity transformation) of the game.
+\\
+As for
+beliefs, agents could either hold probabilistic belief or not. In the former case, we would
+assume that they maximize expectations under whatever preference representation they hold; in
+the latter, we would assume that they play maximin based on their preference
+representations. There are doubtlessly many more possible preference and belief types, but
+these are the main characters in the plot to follow.
+
+Before we turn to evolutionary competition between choice principles, we should justify our
+focus on the two choice rules. In the following we argue that both the minimax rule, as well as the maximization of expected utility 
+(and the Laplace rule as a special case) can be viewed as the same choice rule under different representations of
+uncertainty.
+
+To sum up, here we consider the choice of an action as depending on two features: the subjective preference and the belief state. Definition \ref{def:choice rule} makes this point clear.
+
+\begin{definition} \label{def:choice rule}
+
+Given a set of subjective preferences $\Theta$ and a set of epistemic types $E$, we define \textit{choice rule} a function $\kappa: \Theta \times E  \rightarrow A_i$ that associates an action choice to a pair $(\theta, e) \in \Theta \times E$.
+
+\end{definition}
+
+According to what we argued in this section, we will assume that the choice rule that turns subjective preferences and beliefs into actions is maxmin expected utility.
+
 \iffalse
@@
 \noindent As we have seen in the previous example, this is not the case in the presence of (radical) uncertainty, in the sense of representation of belief state in terms of a set of probability, as in $ \Delta(A_{-i}) $.
-\fi
-
-\iffalse
-
-\subsection{Epistemic types}
-\label{sec:epistemic-types}
-
-\todo[inline]{I think we really need a better (and earlier) justification for these epistemic
-  types; we could appeal to information available to agents; naturalness of situations in which
-  we cannot attach numbers to our beliefs (life on Mars again) \dots}
-
-Consider the following problem.
-I have, on the desk in front of me, a bag containing either red or black marbles.
-There is no further information about the distribution of the two colors.
-What is then the probability that I will draw a red marble?
-As in Walley91-96, we are not talking about physical probability, but rather about epistemic probability, i.e., the subjective probability that an agent attributes to an event.
-In the literature there are two traditional ways of answering this kind of questions.
-According to standard Bayesianism, one should always be able to determine a precise betting rate (that immediately translates into a precise probability distribution), which is fair, in the sense that the DM is indifferent between betting on or against red at the fair rate, and would bet on red at any rate that is more favourable than the fair rate and against red at any rate that is less favourable.
-In this case, a strict Bayesian, in the absence of any further information, would probably rely on the principle of insufficient reason and answer that the DM should have a uniform distribution that considers all the outcomes equipossible.
-\\
-The second answer involves imprecise probabilities and is related to the literature about uncertainty, or ambiguity.
-Many authors argued in favor of this kind of approach [e.g., Walley91-96, Levi74, GardenforsANDSahlin82].
-Since it is consistent with the information available that all the marbles are red, or that no marble is red, the resulting model should take it into account and specify a lower probability of red $\underline{P}(R)$ and an upper probability of red $\overline{P}(R)$ that define an interval of possible probabilistic beliefs [$\underline{P}(R), \overline{P}(R)$].
-Given the information available in this case we would have $\underline{P}(R)=0$ and $\overline{P}(R)=1$.
-This approach appears particularly relevant and appropriate in a game theoretical context.
-Indeed, in a recent paper [Battigalliet al.15] Battigalli et al.
-write
-
-\begin{quote}
-Such uncertainty is inherent in situations of strategic interaction. This is quite obvious when such situations have been faced only a few times.
-\end{quote}
-
-In decision theory, the imprecise probability model is in line with most of the representation results about uncertainty [GilboaSchmeidler89,KMM06], and seems justified by empirical observations too (see below).
-Walley91-96 is a seminal work in the area, that also introduces learning procedures to get useful inferences and narrow down the probability set [$\underline{P}(R), \overline{P}(R)$] after observing data.
-Since we want to study the evolution of meta-types, the present work does not address the probem of drawing inferences from observations, and for the moment we do not endow the players with any learning procedure.\\
-In line with traditional evolutionary game theory, we model a population of rather unsophisticated and myopic agents.
-%that possibly differ from each other with respect to two components: the player type and the epistemic type.
-The players
-The players encode both a psychological subjective representation of the interaction (player type) and a conceptualization of uncertainty (epistemic type), but they are too simple to have any learning or belief updating procedure.
-From this point of view, we can take the learning process away from natural selection and focus on player types and epistemic types as the target of evolutionary pressure.
-
-In full generality, we think of an epistemic type as a general disposition to form beliefs about the co-player’s behavior.
-Players in the population obviously face uncertainty about the composition of the population that they are part of, and consequently about the type of co-player that they are randomly paired with at each round and about the co-player's actions.
-We represent this uncertainty by the use of both the approaches presented above: a uniform distribution and a probability set.
-This amounts to having two different epistemic types $e$ in the population, $e \in \lbrace \overline{\mu}, \Delta(A_{-i}) \rbrace $, where $\overline{\mu}$ stands for the uniform distribution and $\Delta(A_{-i})$ is the probability set, defined as follows:
-
-\begin{itemize}
-
-\item $ \Delta(A_{-i}):=\lbrace \mu \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu(a_{-i}) = 1 \rbrace$;
-
-\item $\overline{\mu} \in \lbrace \mu \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu(a_{-i}) = 1 \rbrace$ is the probability measure over the co-player's actions such that: $\forall a_{-i} \in A_{-i}$, $\overline{\mu}(a_{-i})= \frac{1}{|A_{-i}|}$.
-
-\end{itemize}
-
-Hence, we consider two possible epistemic states in the face of uncertainty.
-The epistemic type $\Delta(A_{-i})$ represents a situation of non-Bayesian radical uncertainty, where the players are not able to narrow down the set of probability distributions to a single one and they consider all of them as possible.
-The other epistemic type $\overline{\mu}$ conceptualizes the uncertainty about the population by using the principle of insufficient reason and ascribes equal probability to all the possible alternatives.
-As we have seen, both options are reasonable and justifiable ways to deal with situations of uncertainty [REFERENCES].
-\\
-
-\subsection{Uncertainty aversion and maxmin rule}
-
-\todo[inline]{this paragraph seems to presuppose familiarity with maxi-minimization (can we
-  write this with a hyphen, any chance?); we should rewrite this or introduce the notion immediately;}
-
-An important part of the latest literature, both experimental and theoretical, in decision theory deals with the issue of uncertainty, also called ambiguity.
-Technically, there is uncertainty about an event when no precise objective probability distribution about the possible outcomes is given.
-A prominent example is the above mentioned Ellsberg's paradox.
-A bag contains 90 marbles, 30 are red and the remaining 60 are either black or yellow.
-A marble is to be drawn and DM can win 100€ if she guesses the color of the drawn marble.
-The DM is offered two different bets.
-In the first one she can choose to bet either on red (R) or on yellow (Y), while in the second she can bet either on red or black (RB) or on yellow or black (YB), as shown in Table \ref{Ellsberg}.
-
-\definecolor{yellow}{RGB}{255,188,1}
-
-\begin{table}[h]
-\centering
-\begin{tabular}{@{}llll@{}}
-\cmidrule(l){2-4}
-\multicolumn{1}{c}{} & {\color{red}R}   & {\color{yellow}Y}   & B   \\ \cmidrule(l){2-4} 
-$f_{{\color{red}R}}$              & 100 & 0   & 0   \\
-$f_{{\color{yellow}Y}}$              & 0   & 100 & 0   \\
-$f_{{\color{red}R}B}$            & 100 & 0   & 100 \\
-$f_{{\color{yellow}Y}B}$             & 0   & 100 & 100 \\ \bottomrule
-\end{tabular}
-\caption{Ellsberg's paradox}
-\label{Ellsberg}
-\end{table}
-
-The pattern consistently observed in experimets is: $f_{{\color{red}R}} \succ f_{{\color{yellow}Y}}$ and $f_{{\color{red}R}B} \prec f_{{\color{yellow}Y}B}$.
-This is clearly incompatible with any precise probabilistic belief about the proportion of black and yellow marbles.
-This kind of behavior has been
-famously axiomatized by Gilboa and Schmeidler in a paper from 1989.
-The choice pattern is normally explained in terms of aversion to uncertainty, and the standard representation is given by means of probability sets together with maxmin rule.
-We can think of the DM in Ellsberg's example as maximinimizing expected utility over the probability set $ [\underline{P}(R)=\frac{1}{3},\underline{P}(Y)=0,\underline{P}(B)=0,\overline{P}(R)=\frac{1}{3},\overline{P}(Y)=\frac{2}{3},\overline{P}(B)=\frac{2}{3}]  $.
-This amounts to calculating for any probability distribution contained in the probability set the expected utility of any available action, and then to choosing the action that guarantees the highest minimal expected utility.
-Whenever the set of priors is a singleton, maximinization of
-expected utility coincides with maximization of expected utility.\\
-%Given a player type and an epistemic type, there are different ways to produce a behavior. 
-A huge body of experimental literature strongly suggests that agents are generally uncertainty
-(or ambiguity) averse [REF]. In line with empirical data,
-we assume that players in the population are uncertainty averse and conform to maxmin expected
-utility. The resulting behavior is then produced by maximinimizing the subjective utility
-given by the player type over the set of priors given by the epistemic type.
-
-  \todo[inline]{I would like to suggest to move Figure 2 next to Figure 1; it is already useful
-  for example 1 and could be referred to there already; I would suggest to use subfigures to
-  put both next to each other}
-
-\begin{example}
-  Consider the game in Figure \ref{coordgame1} again. When a player characterized
-  by\footnote{To ease notation in the following we will refer to a player directly as a pair
-    $(player \text{ } type \text{ } \tau,\text{ } epistemic\text{ } type \text{ } e)$.} player
-  type $ \tau^{reg} $ and epistemic type $ \Delta(A_{-i}) $ faces the game in Figure
-  \ref{coordgame1}, her player type gives rise to the representation $\tau^{reg}(G^C)$ in
-  Figure \ref{coordgame1reg}. Then, maximinimizing expected utility over the probability
-  simplex $ \Delta(A_{-i}) $ given the game in Figure \ref{coordgame1reg} corresponds to
-  playing the standard maxmin strategy [REF] of that game.\footnote{Notice that this is the
-    case for any game: given a game $G$, maximinimizing expected utility over the probability
-    simplex $ \Delta(A_{-i}) $ amounts to playing the standard maxmin strategy of $G$.} This,
-  in turn, corresponds to the regret minimizing action of the original game $G^C$ of Figure
-  \ref{coordgame1}, namely action $II$, as we have seen in Section \ref{sec:regreTheory}. A
-  player $(\tau^{reg},\overline{\mu})$ instead has subjective representation $\tau^{reg}(G^C)$
-  of Figure \ref{coordgame1reg} and a flat probability measure
-  $\overline{\mu}=(\frac{1}{2}I,\frac{1}{2}II)$ over the co-player's actions. Consequently,
-  such a player would play action $II$, i.e., the action that maximinimizes expected utility
-  given the flat probability measure $\overline{\mu}$.\footnote{As we already noticed,
-    maximinimizing expected utility given a probability measure $\mu$ is equivalent to
-    maximizing expected utility given $\mu$.}  Similarly, a player
-  $(\tau^{\pi},\Delta(A_{-i}))$ will have the subjective representation coinciding with the
-  objective fitness game, i.e., $ \tau^{\pi}(G^C)= G^C $. Then, both actions $I$ and $II$
-  maximinimize expected utility over the probability simplex $ \Delta(A_{-i}) $. Hence, a
-  player $(\tau^{\pi},\Delta(A_{-i}))$ will be indifferent between $I$ and $II$, and will
-  randomize with equal probability $(\frac{1}{2}I,\frac{1}{2}II)$. Finally, a player
-  $(\tau^{\pi},\overline{\mu})$ maximinimizes the objective fitness game $G^C$ of Figure
-  \ref{coordgame1} with flat probability $\overline{\mu}$ over the co-player's actions, i.e.,
-  maximizes objective utility given $\overline{\mu}$. In game $G^C$ this yields action $II$.
-
-\begin{figure}
-\begin{center}%
-\begin{tabular}{|c|c|c|}
-\hline 
- & I & II\tabularnewline
-\hline 
-\hline 
-I & 0;0 & -2;-1\tabularnewline
-\hline 
-II & -1;-2 & 0;0\tabularnewline
-\hline 
-\end{tabular}\end{center}
-
-\protect\caption{Regret representation $\tau^{reg}(G^C)$}
-\label{coordgame1reg}
-\end{figure}
-
-\end{example}
-
-We are now in the position of deriving behavior directly from the pair $(\tau, e)$.
-Definitions \ref{def:utility-belief} and \ref{def:maxminSEU} simply formalize the notions of subjective expected utility and maxmin subjective expective utility, respectively.
-
-\begin{definition} \label{def:utility-belief}
-
-Given a game $G$, an action $a_i \in A_i$, and a belief $\mu \in \lbrace \mu' \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu'(a_{-i}) = 1 \rbrace$, we define $\tau(G)(a_i, \mu):= \sum_{a_{-i} \in A_{-i}} \tau(G)(a_i, a_{-i}) \cdot \mu(a_{-i})$.
-
-\end{definition}
-
-\begin{definition} \label{def:maxminSEU}
-
-Given a game $G$ and a player $(\tau, e)$, we define $\text{maxmin}(\tau(G), e):= \lbrace a'_i \in A_i : a_i \in \text{max}_{a_i \in A_i} \text{ min}_{\mu \in e} \text{ } \tau(G)(a_i, \mu) \rbrace$.
-
-\end{definition}
-
-\noindent Definition \ref{def:expected fitness} gives the expected evolutionary fitness of player $(\tau, e)$ against player $(\tau', e')$ in game $G$.\footnote{As already specified in the previous example, we assume that, whenever the set $\text{maxmin}(\tau(G), e)$ is not a singleton, the player $(\tau, e)$ will mix with equal probability among the actions in $\text{maxmin}(\tau(G), e)$.}
-
-\begin{definition} \label{def:expected fitness}
-
-Given a game $G \in \mathcal{G}$, a player $(\tau, e)$, and a player $(\tau', e')$, we define $\pi^G((\tau, e),(\tau', e')):= \pi^G(\text{maxmin}(\tau(G), e),\text{maxmin}(\tau'(G), e'))$.
-
-\end{definition}
-
-%\todo[inline]{should we explain here, or very soon, what the resulting types really are: regret minimizers, maximin players \dots}
-
-Many other alternatives different from maxmin expected utility could produce behavior: choice rules like minmax, maxmax, and minmin expected utility would similarly generate behavior from a player type and an epistemic type.
-Here we postulate that players are maximinimizers for two main reasons.
-First, as already mentioned, among other possible choice rules maxmin is not only intuitively appealing but also corroborated from an empirical point of view.
-Secondly, our main interest is the evolution of different patterns of subjective conceptualizations of games (player types), and we want to show that the veridical representation (objective type) is not necessarily the fittest and may not be evolutionarily stable.
-Assuming that all players use the maxmin rule independent of their player type allows us to factor the choice rule out of the selection process and to focus on player types.
-
-Before concluding this section, it is worth stressing that player $(\tau^{\pi}, \Delta(A_{-i}))$ turns out to be the objective maximinimizer, player $(\tau^{reg}, \Delta(A_{-i}))$ is the regret minimizer, player $(\tau^{\pi}, \overline{\mu})$ is the objective expected utility maximizer, and player $(\tau^{reg}, \overline{\mu})$ is the expected regret minimizer.
-Moreover, the following facts hold.
-
-\begin{fact} \label{fact:maxEU-minReg}
-
-For any probability measure $\mu$, maximization of expected utility and minimization of expected regret are behaviorally equivalent.
-
-\end{fact}
-
-\noindent As we have seen in the previous example, this is not the case in the presence of (radical) uncertainty, in the sense of representation of belief state in terms of a set of probability, as in $ \Delta(A_{-i}) $.
-
-\begin{fact} \label{fact:equivalence2x2}
-
-In the class of $2 \times 2$ symmetric games, players $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg},\overline{\mu})$ are behaviorally equivalent.
-
-\end{fact}
-
-\noindent Two remarks. Firstly, Fact \ref{fact:equivalence2x2} does not hold for $n \times n$
-symmetric games in general. Secondly, we treat behaviorally equivalent types as distinct,
-because we assume that what is selected by biological evolution is not choice behavior as such,
-but the mechanism which generates behavior. This matters in particular if we assume that
-mutations affect different components of the behavior generating mechanisms (see below).
-
 \fi

### 2015-11-05 paper/paper.tex
rewrite up to Sec 3.3

@@
 
-\title{Rationality, Regret, Evolution \& the Environment}
-\author{Paolo Galeazzi \& Michael Franke}
-\date{current version: November 4, 2015}
+\title{Smart Representations: {R}ationality, Regret, Evolution \& the Environment}
+\author{Paolo Galeazzi \& Michael Franke} \date{current version: November 5, 2015}
 
@@
 conceptual issues whose complexity requires mathematical modeling. However, most applications
-of EGT look at evolutionary selection of behavior in a single \emph{stage game}. There are
-actually two crude but common simplifications in this approach. Firstly, the stage game is
-usually considered fixed, closed and immutable. Secondly, what evolves are behavioral
-strategies for the stage game. It has consequently been argued that, instead of focusing on a
-fixed, immutable stage game and the behavioral selection for that stage game alone, we should
-rather study the evolutionary selection of \emph{choice mechanisms} that are adapted in a rich
-and variable environment
-\citep[e.g.][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche}. % However,
-% formal accounts of the adaptive value of choice mechanisms have focused, for the most part, on
-% the evolutionary benefit of learning rules
-% \citep[e.g.][]{ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o}. \todo{More
-%   references Harley 1981!!!, O Conor \dots} Moreover,
+look at evolutionary selection of behavior in a single \emph{stage game}. There are two common
+simplifications in this approach. Firstly, the stage game is usually considered fixed, closed
+and immutable. Secondly, what evolves are behavioral strategies for the stage game. It has
+consequently been argued that, instead of focusing on a fixed, immutable stage game and the
+behavioral selection for that stage game alone, we should rather study the evolutionary
+competition of \emph{choice mechanisms} under selective pressure in a rich and variable
+environment \citep[e.g.][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche}.
 But only little attention has been paid to modeling the evolutionary competition between choice
@@
 
-This paper makes two contributions to the literature on evolution of choice mechanisms: one
-methodological and one conceptual. Firstly, on the methodological side, we introduce a
-conservative extension of standard EGT that allows us to reuse notions such as evolutionary
-stability / evolutionary dynamics for the study of the evolutionary competition between choice
-mechanisms in a statistically variable environment. Concretely, we look at the evolutionary
-competition of choice mechanisms in a ``meta-game'' whose payoffs represent the average
-expected fitness choice mechanisms when playing arbitrary games (from a given class) against
-themselves. In this sense, a meta-game captures (the modeller's) assumptions about the relevant
-statistics of the environment in which evolutionary forces operate.
-
-Secondly, and in order to show that our method is useful for a conceptual debate about
-evolution of choice mechanisms, we argue that paying attention to the interaction of subjective
-belief and subjective preference representations is important. Since almost any reasonable
-learning or decision-making process will make use of some (subjective, agent-internal (possibly
-unconscious)) representation of the quality of choice options, the question of which such
-representations are ecologically valuable (i.e., lead to high fitness) is central. Na\"ive
-intuition might convince us that preferences that veridically represent the actual, true
-fitness measure that evolutionary selection is based upon must surely be the best. We
-demonstrate that, if we take into account how agents represent uncertainty, this na\"ive
-conclusion is premature. Under certain reasonable epistemic conditions, non-veridical
-preference representations in terms of regret can be evolutionarily beneficial.
+If agents deal with a rich and varied environment, they face many different choice
+situations. A crucial part of a choice mechanism (conceived of as a mapping from a choice
+situation to a concrete choice of action) is a \emph{subjective representation} of that choice
+situation, i.e., the agents' manner of representing their preferences and the manner of forming
+decision relevant beliefs. Since almost any reasonable learning or decision-making process will
+make use of some (subjective, agent-internal (possibly unconscious)) representation of the
+quality of choice options, the question of which such representations are ecologically valuable
+(i.e., lead to high fitness) is central and has been subject of recent interest
+(\textcolor{red}{CITE literature on evolution of preferences}). Na\"ive intuition might
+convince us that preferences that veridically represent the actual, true fitness measure that
+evolutionary selection is based upon must surely be the best. We demonstrate that, if we take
+into account how agents represent uncertainty, this na\"ive conclusion is premature. Under
+certain reasonable epistemic conditions, non-veridical preference representations in terms of
+regret can be evolutionarily beneficial.
+
+To show this, we study the evolutionary competition of choice mechanisms, or more specifically
+the competition of subjective representations of choice situations, in a variable
+environment. Concretely, we look at evolutionary ``meta-games'' whose ``acts'' are types of
+subjective representations of games and whose ``payoffs'' represent the average expected
+fitness that choice mechanisms using these representation types would accrue when playing
+arbitrary games (from a given class, with a given occurrence probability) against other
+subjective representations of games. In this sense, a meta-game captures (the modeller's)
+assumptions about the relevant statistics of the environment in which evolutionary forces
+operate, while we are still able to use standard methods from evolutionary game theory, like
+stability or evolutionary dynamics.
 
@@
 subjective preferences and subjective beliefs in adaptationist approaches to decision
-making. More specifically, we show that subjective, non-veridical preference representations
-based on a notion of regret
-\citep[e.g.][]{Savage1951:The-theory-of-s,LoomesSugden1982:Regret-Theory:-}\todo{add
-  references?}\ can be adaptive and even outperform objective, veridical representations of the
-actual, true fitness, when agents, at least on occasion, hold imprecise probabilistic beliefs (CITE)
-and make decisions based on a security choice rule (here: the maximin rule).
-
-The method by which we want to advance our argument is to integrate ideas from the recent
-literature on preference evolution (CITE) with basic tenets of adaptationism: we are interested
-in studying the evolutionary competition of choice mechanisms, conceived here as pairs of
-subjective preference and subjective belief representations. Evolutionary competition between
-choice mechanisms is driven by the expected objective fitness that each choice mechanisms
-accrues when put to use repeatedly in a range of choice situations. We focus on the more
-complex case of multi-agent decision making first, i.e., game situations. Solitary decision
-making is then easy to deal with subsequently. The next section introduces the choice
-mechanisms we focus on. After that, Section~\ref{sec:model} introduces the ``meta-game''
-modeling approach.
+making. In other words, we focus on the evolutionary competition between \emph{subjective
+  representation schemes}: general ways of forming subjective preferences and types of
+subjective beliefs. We show that subjective, non-veridical preference representations based on
+a notion of regret \citep[e.g.][]{Savage1951:The-theory-of-s,LoomesSugden1982:Regret-Theory:-}
+can be adaptive and even outperform objective, veridical representations of the actual, true
+fitness, when agents, at least on occasion, hold \emph{imprecise probabilistic beliefs}
+(\textcolor{red}{CITATIONS}) and make decisions based on a security choice rule (here: the
+maximin rule applied to expected utility). The next section introduces all of these notions
+(precise/imprecise beliefs, veridical/regret representations, \dots) in detail.
+
+% The method by which we want to advance our argument is to integrate ideas from the recent
+% literature on preference evolution (CITE) with basic tenets of adaptationism: we are interested
+% in studying the evolutionary competition of choice mechanisms, conceived here as pairs of
+% subjective preference and subjective belief representations. Evolutionary competition between
+% choice mechanisms is driven by the expected objective fitness that each choice mechanisms
+% accrues when put to use repeatedly in a range of choice situations. We focus on the more
+% complex case of multi-agent decision making first, i.e., game situations. Solitary decision
+% making is then easy to deal with subsequently. The next section introduces the choice
+% mechanisms we focus on. After that, Section~\ref{sec:model} introduces the ``meta-game''
+% modeling approach.
 
@@
 \emph{choice mechanism} which makes explicit several elements that choice rules might brush
-under the table.
+under the table, in particular the crucial notion of a subjective representation scheme whose
+evolutionary selection we are most interested in.
 
@@
 For the purposes of this paper, we think of a choice rule as a function that takes a
-(strategic) game as input and delivers a choice of action for that game. The literatures has
+(strategic) game as input and outputs a choice of action for that game. The literatures has
 suggested a number of choice rules that aspire to capture a normative element of rational
@@
 
-But first an important digression. Rational choice from maximization of expected utilities, as
-given in Definition~\ref{def:rationality}, is \emph{not} a choice rule in the present sense, if
-we apply it strictly. Although the notion applies to game situations, of course, it requires an
-additional component, namely a belief of the DM, before it can say which acts the DM should
-choose. Let $A_{-i} = \bigtimes A_j$ for all $j \neq i$ be the set of all \emph{profiles} of
-acts for all players except $i$. If player $i$ has a belief $\mu_i \in \Delta(A_{-i})$ about
-the behavior of his opponents, he chooses rationally only if his choice $a^*_i$ maximizes
-expected utility
+Rational choice from maximization of expected utilities, as given in
+Definition~\ref{def:rationality}, is \emph{not} a choice rule in the present sense. Although
+the notion applies to game situations, of course, it requires an additional component, namely a
+belief of the DM, before it can say which acts the DM should choose. Let
+$A_{-i} = \bigtimes A_j$ for all $j \neq i$ be the set of all \emph{profiles} of acts for all
+players except $i$. If player $i$ has a belief $\mu_i \in \Delta(A_{-i})$ about the behavior of
+his opponents, he chooses rationally only if his choice $a^*_i$ maximizes expected utility
 $\EU(a) = \sum_{\act_{-i} \in \Acts_{-i}} \mu_i(\act_{-i}) \myts \pi_i(a_i, a_{-i})$. So this
@@
 \citet{Savage1951:The-theory-of-s} and Niherens [], and later developed by Bell [1982], Loomes
-and Sugden [1982], and Fishburn [1982] independently. Lately,
+and Sugden [1982], and Fishburn [1982] independently.\todo{fix references}\ Lately,
 \citet{HalpernPass2012:Iterated-Regret} showed how the use of regret minimization can give
@@
 row-player action for the coordination game in Figure \ref{coordgame1}. We have
-$\text{reg}(I)=2$, because when the other player chooses action $I$ the pairwise regret
-$reg(I,I)$ is $0$ since $I$ is a best reply to $I$, and when the other player chooses $II$ the
-pairwise regret $reg(I, II)$ is $2$ since $\pi_i(II,II)-\pi_i(I,II)=2$. With the same
-reasoning, $\text{reg}(II)=1$. A regret minimizing player would therefore choose act $II$.
+$\text{reg}(I)=2$, because when the other player chooses act $I$ the pairwise regret
+$\text{reg}(I,I)$ is $0$ since $I$ is a best reply to act $I$, and when the other player
+chooses act $II$ the pairwise regret $\text{reg}(I, II)$ is $2$ since
+$\pi_i(II,II)-\pi_i(I,II)=2$. With the same reasoning, $\text{reg}(II)=1$. A regret minimizing
+player would therefore choose act $II$.
 
@@
       \toprule
-      & $reg( \cdot, I)$ & $reg(\cdot, II)$ & $reg(\cdot)$ \\
+      & $\text{reg}( \cdot, I)$ & $\text{reg}(\cdot, II)$ & $\text{reg}(\cdot)$ \\
       \midrule
@@
     \end{tabular}
-    \caption{Pairwise regrets representation $\tau^{reg}(G^C)$}
+    \caption{Pairwise regrets and regrets}
     \label{coordgame1reg}
   \end{subfigure}
-  \caption{A coordination game (left) and regrets associated with each row-player actions (right).}
+  \caption{A coordination game (left) and regrets associated with each row-player acts (right).}
     \label{coordgame1mainFig}
@@
 
-We think of a choice mechanism as a function that maps a game (or more generally any decision
-situation) onto a triple that consists of: (i) the DM's \emph{subjective preferences} (possibly
-diverging from the actual objective payoffs defined ) in the game, (ii) the DM's
-\emph{subjective beliefs} about the opponents' behavior, and (iii) an \emph{action selection
-  function} which maps the former two components onto a concrete choice of action in the
-game. A choice mechanism could be a set of distinct heuristics (the DM's \emph{adaptive
-  toolbox}) that have little in common
+A \emph{choice mechanism} is a map from choice situations to action choices that, unlike choice
+rules, contains an explicit level of subjective representation of a decision situation. For our
+purposes, we should think of a choice mechanism is a pair of functions $\gamma$ and $\kappa$,
+where $\gamma$ is a \emph{subjective representation scheme} and $\kappa$ is an \emph{action
+  selection function} (see FigureXYZ).\todo{make figure when notation and terminology are
+  fixed}\ The subjective representation scheme $\gamma$ maps a game (or more generally any
+decision situation) onto a subjective representation of the game (or choice situation) and
+other decision-relevant beliefs (e.g., about what the opponent is likely to play). The action
+selection function $\kappa$ takes such a subjective representation that $\gamma$ returns, and
+maps it onto a concrete action choice. The crucial bit for our purposes here is the
+representation function $\gamma$, because we are interested in which ways of conceptualizing a
+decision situation are evolutionarily successful.
+
+More generally even, a choice mechanism could be a set of distinct heuristics (the DM's
+\emph{adaptive toolbox}) that have little in common
 \citep[e.g.][]{TverskyKahnemann1981:The-Framing-of-,GigerenzerGoldstein1996:Reasoning-the-F,ScheibehenneRieskamp2013:Testing-the-Ada}. But
-to keep matters simple, we will here only look at choice mechanisms that use a uniform way of
-forming preferences and beliefs and a uniform way of making choices based on them. More
-concretely, we focus on two \emph{preference types} and two \emph{belief types}, and neglect
-variation in the action selection component.
-
-We are most interested here in studying whether evolutionary pressure could support
-non-veridical subjective preferences under certain conditions. We therefore focus on two
-\emph{preference types}: veridical types $\tau^\pi$, who use the actual payoff function $\pi$ of the
-actual game $G$, and regret types $\tau^{reg}$, who look at the regret transformation of the
-actual game $G$.
-
-It turns out that whether $\tau^{reg}$ can have a fitness advantage over $\tau^\pi$ depends on
-the general \emph{kind} of (probabilistic) beliefs that DM's form about the opponent's
-behavior. In other words, we even abstract away from the content of the DM's beliefs about his
-opponents' behavior that he could have acquired by learning or observation, but first turn on
-the more general question of how uncertainty should be represented in order to interact with
-subjective preferences in such a way that the resulting behavior will be fitness enhancing for
-the DM in the long run. We consider therefore two \emph{belief types} (to be defined below):
-imprecise belief types $\Delta(A_{-i})$, who have a set of probabilistic beliefs about the
-opponents' behavior and precise belief types $\overline{\mu}$ who have a single probabilistic
-belief.
-
-The following subsection describes what these belief types are and how a single action
-selection function (maximin expected utility) gives rise to an intersting parallel with
-classical choice rules.
-
-\subsection{Choice mechanisms take2}
-
-In the previous section we introduced choice rules generating behavior in a game as functions from a game to an action choice.
-In the general form, given a class of games $\mathcal{G}$, a choice rule is then thought as a function $c: \mathcal{G} \rightarrow A_i $.
-In this section instead we want to show that a more intelligible and perspicuous way of understanding behavior generating mechanisms may be as functions of a subjective preference and an epistemic state of the agents.
-Then, given a set of subjective preferences $ \Theta $ [@Paolo: minimally define subjective preferences somewhere above] and a set of epistemic states (or belief types) $E$, a choice mechanism is a function $\kappa: \Theta \times E \rightarrow A_i $.
-We will see in a moment that from this perspective we gain a more unified and structured insight on the choice rules presented above.
-
-More
-concretely, we focus on two \emph{preference types} and two \emph{belief types}.
-We view a preference type as a function $\tau: \mathcal{G} \rightarrow \Theta$, and a belief type as a general disposition to form beliefs about the co-player’s behavior.
-The two possible dispositions that we take account of are probabilistic (precise) belief and non-probabilistic (imprecise) belief, as we will explain in the next section.
-
-We are most interested here in studying whether evolutionary pressure could support
-non-veridical subjective preferences under certain conditions. We therefore consider two
-\emph{preference types}: veridical type $\tau^\pi$, who uses the actual payoff function $\pi$ of the
-actual game $G$, and regret type $\tau^{reg}$, who looks at the regret transformation of the
-actual game $G$.
-
-The choice mechanism that we use in this paper is \textit{maxmin expected utility} [GS89], for reasons that will be clear and justified in the following two sections.
+to keep matters simple and implementable for a start, we will here only look at choice
+mechanisms that differ only with respect to their subjective representation function $\gamma$,
+which in turn is conceived of as a \emph{uniform} way of forming preference and belief
+\emph{types}. \textcolor{red}{Formally, $\gamma$ is a function in
+  $\mathcal{G} \rightarrow \Theta \times E$, where \dots. Then, given a set of subjective
+  preferences $ \Theta $ [@Paolo: minimally define subjective preferences somewhere above] and
+  a set of epistemic states (or belief types) $E$, a choice mechanism is a function
+  $\kappa: \Theta \times E \rightarrow A_i $.}
+
+\textcolor{red}{More concretely, we focus on two \emph{preference types} and two \emph{belief
+    types}. We view a preference type as a function $\tau: \mathcal{G} \rightarrow \Theta$, and
+  a belief type as a general disposition to form beliefs about the co-player’s behavior. The
+  two possible dispositions that we take account of are probabilistic (precise) belief and
+  non-probabilistic (imprecise) belief, as we will explain in the next section.}
+
+\textcolor{red}{We are most interested here in studying whether evolutionary pressure could
+  support non-veridical subjective preferences under certain conditions. We therefore consider
+  two \emph{preference types}: veridical type $\tau^\pi$, who uses the actual payoff function
+  $\pi$ of the actual game $G$, and regret type $\tau^{reg}$, who looks at the regret
+  transformation of the actual game $G$.}
+
+\textcolor{red}{The choice mechanism that we use in this paper is \textit{maxmin expected
+    utility} [GS89], for reasons that will be clear and justified in the following two
+  sections.  }
+
+% It turns out that whether $\tau^{reg}$ can have a fitness advantage over $\tau^\pi$ depends on
+% the general \emph{kind} of (probabilistic) beliefs that DM's form about the opponent's
+% behavior. In other words, we even abstract away from the content of the DM's beliefs about his
+% opponents' behavior that he could have acquired by learning or observation, but first turn on
+% the more general question of how uncertainty should be represented in order to interact with
+% subjective preferences in such a way that the resulting behavior will be fitness enhancing for
+% the DM in the long run. We consider therefore two \emph{belief types} (to be defined below):
+% imprecise belief types $\Delta(A_{-i})$, who have a set of probabilistic beliefs about the
+% opponents' behavior and precise belief types $\overline{\mu}$ who have a single probabilistic
+% belief.
+
+% The following subsection describes what these belief types are and how a single action
+% selection function (maximin expected utility) gives rise to an intersting parallel with
+% classical choice rules.
 

### 2015-11-06 paper/paper.tex
tweaks and extracted bib
Paolo fixes Sec 3.3

@@
 % \bibliography{helpers/MyRefLocal}
-\bibliography{MyRefGlobal}
+\bibliography{choicePrince}
 \usepackage{helpers/myenvironments}
@@
 
-A strategic game is a tuple $ G=\tuple{ N, (A_i , \pi_i)_{i \in N} }$ with $N$ a set of
-players, $A_i$ a set of acts and $\pi_i$ a payoff function for each player $i \in N$. For the
+A strategic game is a tuple $ G=\tuple{ N, (A_i , \pi_i)_{i \in N} }$ with $N$ a finite set of
+players, $A_i$ a finite set of acts and $\pi_i$ a payoff function for each player $i \in N$. For the
 most part, this paper will focus on symmetric games with two players. A two-player game is
@@
 which in turn is conceived of as a \emph{uniform} way of forming preference and belief
-\emph{types}. \textcolor{red}{Formally, $\gamma$ is a function in
-  $\mathcal{G} \rightarrow \Theta \times E$, where \dots. Then, given a set of subjective
-  preferences $ \Theta $ [@Paolo: minimally define subjective preferences somewhere above] and
-  a set of epistemic states (or belief types) $E$, a choice mechanism is a function
-  $\kappa: \Theta \times E \rightarrow A_i $.}
-
-\textcolor{red}{More concretely, we focus on two \emph{preference types} and two \emph{belief
+\emph{types}.
+
+Formally, given a class $ \mathcal{G} $ of games, $\gamma: \mathcal{G} \rightarrow \Theta \times E$ is a function that assigns a subjective preference $\theta \in \Theta$ and an epistemic state (or belief type) $e \in E$ to any game $G \in \mathcal{G}$.\footnote{Given a game $G$, the set $ \Theta $ is the set of all subjective preferences, or subjective utility functions, on $G$.
+I.e., $\Theta$ is the set of all functions $\theta: A \rightarrow \mathbb{R}$.}
+Then, given a set of subjective
+  preferences $ \Theta $ and
+  a set of or belief types $E$, an action selection function is a function
+  $\kappa: \Theta \times E \rightarrow A_i $, that associates any subjective representation of the game $ (\theta,e) \in \Theta \times E$ with an action $a^{*} \in A_i $.
+
+More concretely, we focus on two (\textit{subjective}) \emph{preference types} and two \emph{belief
     types}. We view a preference type as a function $\tau: \mathcal{G} \rightarrow \Theta$, and
   a belief type as a general disposition to form beliefs about the co-player’s behavior. The
-  two possible dispositions that we take account of are probabilistic (precise) belief and
-  non-probabilistic (imprecise) belief, as we will explain in the next section.}
-
-\textcolor{red}{We are most interested here in studying whether evolutionary pressure could
-  support non-veridical subjective preferences under certain conditions. We therefore consider
-  two \emph{preference types}: veridical type $\tau^\pi$, who uses the actual payoff function
-  $\pi$ of the actual game $G$, and regret type $\tau^{reg}$, who looks at the regret
-  transformation of the actual game $G$.}
-
-\textcolor{red}{The choice mechanism that we use in this paper is \textit{maxmin expected
+  two possible dispositions that we take account of are precise probabilistic belief and
+  imprecise belief, as we will explain in the next section.
+
+Since we are most interested here in studying whether evolutionary pressure could
+  support non-veridical subjective preferences, the two preference types that we consider are: the veridical type $\tau^\pi$, who uses the actual payoff function
+  $\pi$ of the actual game $G$, and the regret type $\tau^{reg}$, who looks at the regret
+  transformation of the actual game $G$.
+
+Finally, the action selection function $\kappa$ that we use in this paper is \textit{maxmin expected
     utility} [GS89], for reasons that will be clear and justified in the following two
-  sections.  }
+  sections.
 
@@
 We represent this uncertainty in two different ways that correspond to the two approaches discussed above: a Bayesian uniform distribution and an imprecise probability set.
-This amounts to having two different belief types, $ \overline{\mu}$ and $ \Delta(A_{-i}) \rbrace $, where $\overline{\mu}$ stands for the uniform distribution and $\Delta(A_{-i})$ is the probability set, defined as follows:
+This amounts to having two different belief types, $ \overline{\mu}$ and $ \Delta(A_{-i})$, where $\overline{\mu}$ stands for the uniform distribution and $\Delta(A_{-i})$ is the probability set, defined as follows:
 
@@
 
-In decision theory, the imprecise probability model is in line with most of the representation results in decision making under uncertainty [GilboaSchmeidler89,KMM06], and seems justified by empirical observations too.
+In decision theory, the imprecise probability model is in line with most of the representation results of decision making under uncertainty [GilboaSchmeidler89,KMM06], and seems justified by empirical observations too.
 
@@
 famously axiomatized by Gilboa and Schmeidler in a paper from 1989.
-The choice pattern is normally explained in terms of aversion to uncertainty, and the standard representation is given by means of probability sets together with maxmin rule.
-We can think of the DM in Ellsberg's example as maximinimizing expected utility over the probability set $ [\underline{P}(R)=\frac{1}{3},\underline{P}(Y)=0,\underline{P}(B)=0,\overline{P}(R)=\frac{1}{3},\overline{P}(Y)=\frac{2}{3},\overline{P}(B)=\frac{2}{3}]  $.
-This amounts to calculating for any probability distribution contained in the probability set the expected utility of any available action, and then to choosing the action that guarantees the highest minimal expected utility.
+The choice pattern is normally explained in terms of aversion to uncertainty, and the standard representation is given by means of a set of probability measures together with maxmin rule.
+We can think of the DM in Ellsberg's example as maximinimizing expected utility over the probability set $ [\underline{P}(R)=\overline{P}(R)=\frac{1}{3},\underline{P}(Y)=0,\underline{P}(B)=0,\overline{P}(Y)=\frac{2}{3},\overline{P}(B)=\frac{2}{3}]  $.
+This amounts to calculating for any probability measure contained in the probability set the expected utility of any available action, and then to choosing the action that guarantees the highest minimal expected utility.
 The following observation is then trivial.
@@
 utility. The resulting behavior is then produced by maximinimizing the subjective utility
-given by the player (preference, UNIFORM TERMINOLOGY CHECK) type over the set of probabilities given by the belief type of the agent.
+given by the player's preference type over the set of probabilities given by the belief type.
 
@@
 
-Fixing the choice mechanism (action selection component) to maximin expected utility, and allowing two belief and
+By fixing the action selection component to maximin expected utility, and allowing two belief and
 two preference types, we regain all the choice rules considered in sectionNN from a more general and unified standpoint, as it is summed up in
@@
 
-Given a game $G$ and a player $(\tau, e)$, we define $\text{maxmin}(\tau(G), e):= \lbrace a'_i \in A_i : a_i \in \text{max}_{a_i \in A_i} \text{ min}_{\mu \in e} \text{ } \tau(G)(a_i, \mu) \rbrace$.
+Given a game $G$, a preference type $\tau$ and a belief type $e$, we define $\kappa(\tau(G), e):= \lbrace a_i \in A_i : a_i \in \text{max}_{a'_i \in A_i} \text{ min}_{\mu \in e} \text{ } \tau(G)(a'_i, \mu) \rbrace$.\footnote{As already specified in the previous example, we assume that, whenever the set $\kappa(\tau(G), e)$ is not a singleton, the player $(\tau, e)$ will mix with equal probability among the actions in $\kappa(\tau(G), e)$.}
 
@@
 
-[[\noindent Definition \ref{def:expected fitness} gives the expected evolutionary fitness of player $(\tau, e)$ against player $(\tau', e')$ in game $G$.\footnote{As already specified in the previous example, we assume that, whenever the set $\text{maxmin}(\tau(G), e)$ is not a singleton, the player $(\tau, e)$ will mix with equal probability among the actions in $\text{maxmin}(\tau(G), e)$.}
+[[\noindent Definition \ref{def:expected fitness} gives the expected evolutionary fitness of player $(\tau, e)$ against player $(\tau', e')$ in game $G$.
 [OF COURSE we will postpone the definition of evolutionary fitness, it is only momentarily here!]
@@
 
-Given a game $G \in \mathcal{G}$, a player $(\tau, e)$, and a player $(\tau', e')$, we define $\pi^G((\tau, e),(\tau', e')):= \pi^G(\text{maxmin}(\tau(G), e),\text{maxmin}(\tau'(G), e'))$.
+Given a game $G \in \mathcal{G}$, a player $(\tau, e)$, and a player $(\tau', e')$, we define $\pi^G((\tau, e),(\tau', e')):= \pi^G(\kappa(\tau(G), e),\kappa(\tau'(G), e'))$.
 
@@
 
-It is then worth stressing here that $\kappa(\tau^{\pi}, \Delta(A_{-i}))$ turns out to be the objective
+It is then worth stressing here that $\kappa(\tau^{\pi}, \Delta(A_{-i}))$ turns out to be the actual payoff
 maximinimizer, $\kappa(\tau^{reg}, \Delta(A_{-i}))$ corresponds to the regret minimizer,
-$\kappa(\tau^{\pi}, \overline{\mu})$ is the objective expected utility maximizer (with flat beliefs), and
+$\kappa(\tau^{\pi}, \overline{\mu})$ is the expected actual payoff maximizer (with flat beliefs), and
 $\kappa(\tau^{reg}, \overline{\mu})$ is the expected regret minimizer (with flat beliefs).
@@
 \noindent In other words, given the same probabilistic belief, maximization of expected
-(objective) payoff and minimization of expected (subjective) regret are behaviorally
+(objective) payoff and minimization of expected regret are behaviorally
 equivalent. This holds for arbitrary games, as well as for solitary decision situations. On the
@@
 Many other alternatives different from maxmin could produce behavior: choice rules like minmax, maxmax, and minmin would similarly generate behavior in case of a lack of precise probabilistic belief.
-Here we postulate that players use maxmin for two main reasons that we will expand in the next section.
+As it should be clear by now, here we postulate that players use maxmin for two main reasons.
 First, among other possible choice rules maxmin is not only intuitively appealing but also corroborated from an empirical point of view.
-Secondly, as it will be clear in the following, our main interest is the evolution of different patterns of subjective conceptualizations of games (player types), and we want to show that the veridical representation (objective type) is not necessarily the fittest and may not be evolutionarily stable.
-Assuming that all players use a fixed rule (maxmin) independent of their player type allows us to factor the choice rule out of the selection process and to focus on player types.
+Secondly, our main interest is the evolution of different patterns of subjective conceptualizations of games, and we want to show that the veridical representation is not necessarily the fittest and may not be evolutionarily stable.
+Assuming that all players use a fixed rule (maxmin expected utility) independent of their preference and belief type allows us to factor the choice rule out of the selection process and to focus on subjective representations only.
 
@@
 
-\todo[inline]{PAOLO rewrite up to here!!! BUT the last 2-3 paragraphs must be rearranged a bit more!}
+\todo[inline]{PAOLO rewrites up to here!!! }
 
@@
 \bigskip
-
-In sum, we have so far considered four different alternatives, each differing along a
-preference and a belief dimension. As for preference representations, agents could either
-target objective payoffs, or consider non-veridical subjective regret transformations.
-Given a game $G$, we will denote by $ \tau^{reg}(G)$ the regret representation (corresponding to the negative regret transformation) of the game, and $\tau^{\pi}(G)$ the objective representation (corresponding to the identity transformation) of the game.
-\\
-As for
-beliefs, agents could either hold probabilistic belief or not. In the former case, we would
-assume that they maximize expectations under whatever preference representation they hold; in
-the latter, we would assume that they play maximin based on their preference
-representations. There are doubtlessly many more possible preference and belief types, but
-these are the main characters in the plot to follow.
-
-Before we turn to evolutionary competition between choice principles, we should justify our
-focus on the two choice rules. In the following we argue that both the minimax rule, as well as the maximization of expected utility 
-(and the Laplace rule as a special case) can be viewed as the same choice rule under different representations of
-uncertainty.
-
-To sum up, here we consider the choice of an action as depending on two features: the subjective preference and the belief state. Definition \ref{def:choice rule} makes this point clear.
-
-\begin{definition} \label{def:choice rule}
-
-Given a set of subjective preferences $\Theta$ and a set of epistemic types $E$, we define \textit{choice rule} a function $\kappa: \Theta \times E  \rightarrow A_i$ that associates an action choice to a pair $(\theta, e) \in \Theta \times E$.
-
-\end{definition}
-
-According to what we argued in this section, we will assume that the choice rule that turns subjective preferences and beliefs into actions is maxmin expected utility.
 

### 2015-11-06 paper/paper.tex
minor edits

@@
 see][]{ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o}.\todo{More references
-  Harley 1981!!!, O Conor \dots}.
+  Harley 1981!!!, O Conor \dots}
 
 If agents deal with a rich and varied environment, they face many different choice
-situations. A crucial part of a choice mechanism (conceived of as a mapping from a choice
-situation to a concrete choice of action) is a \emph{subjective representation} of that choice
-situation, i.e., the agents' manner of representing their preferences and the manner of forming
-decision relevant beliefs. Since almost any reasonable learning or decision-making process will
-make use of some (subjective, agent-internal (possibly unconscious)) representation of the
-quality of choice options, the question of which such representations are ecologically valuable
-(i.e., lead to high fitness) is central and has been subject of recent interest
-(\textcolor{red}{CITE literature on evolution of preferences}). Na\"ive intuition might
-convince us that preferences that veridically represent the actual, true fitness measure that
-evolutionary selection is based upon must surely be the best. We demonstrate that, if we take
-into account how agents represent uncertainty, this na\"ive conclusion is premature. Under
-certain reasonable epistemic conditions, non-veridical preference representations in terms of
-regret can be evolutionarily beneficial.
+situations. A crucial part of any choice mechanism is a \emph{subjective representation} of the
+choice situation, e.g., the agent's manner of representing their preferences and her way of
+forming decision relevant beliefs in the case of uncertainty. Since almost any reasonable
+learning or decision-making process will make use of some (subjective, agent-internal (possibly
+unconscious)) representation of the quality of choice options, the question of which such
+representations are ecologically valuable (i.e., lead to high fitness) is central and has been
+subject of recent interest (\textcolor{red}{CITE literature on evolution of
+  preferences}). Na\"ive intuition might convince us that preferences that veridically
+represent the actual, true fitness measure that evolutionary selection is based upon must
+surely be the best. We demonstrate that, if we take into account how agents represent
+uncertainty, this na\"ive conclusion is premature. Under certain reasonable epistemic
+conditions, non-veridical preference representations can be evolutionarily beneficial.
 
@@
 fitness that choice mechanisms using these representation types would accrue when playing
-arbitrary games (from a given class, with a given occurrence probability) against other
-subjective representations of games. In this sense, a meta-game captures (the modeller's)
-assumptions about the relevant statistics of the environment in which evolutionary forces
-operate, while we are still able to use standard methods from evolutionary game theory, like
-stability or evolutionary dynamics.
+arbitrary games (from a given class, with a given occurrence probability). In this sense, a
+meta-game captures (the modeller's) assumptions about the relevant statistics of the
+environment in which evolutionary forces operate, while we are still able to use standard
+methods from evolutionary game theory, like stability or evolutionary dynamics.
 
@@
 For the purposes of this paper, we think of a choice rule as a function that takes a
-(strategic) game as input and outputs a choice of action for that game. The literatures has
+(strategic) game as input and outputs a choice of action for that game. The literature has
 suggested a number of choice rules that aspire to capture a normative element of rational
-choice. For reasons that will become clear as we go along, we focus here on three classical
-choice rules: (i) maximin, (ii) Laplace and (iii) regret minimization.
+choice. We focus here on three classical choice rules: (i) maximin, (ii) Laplace and (iii)
+regret minimization.
 
@@
 rules, contains an explicit level of subjective representation of a decision situation. For our
-purposes, we should think of a choice mechanism is a pair of functions $\gamma$ and $\kappa$,
+purposes, we should think of a choice mechanism as a pair of functions $\gamma$ and $\kappa$,
 where $\gamma$ is a \emph{subjective representation scheme} and $\kappa$ is an \emph{action
@@
 other decision-relevant beliefs (e.g., about what the opponent is likely to play). The action
-selection function $\kappa$ takes such a subjective representation that $\gamma$ returns, and
+selection function $\kappa$ takes such a subjective representation that $\gamma$ returns and
 maps it onto a concrete action choice. The crucial bit for our purposes here is the
-representation function $\gamma$, because we are interested in which ways of conceptualizing a
-decision situation are evolutionarily successful.
-
-More generally even, a choice mechanism could be a set of distinct heuristics (the DM's
-\emph{adaptive toolbox}) that have little in common
+representation function $\gamma$, because we are interested in studying which ways of
+conceptualizing a decision situation are evolutionarily successful.
+
+A choice mechanism could be a set of distinct heuristics (the DM's \emph{adaptive toolbox})
+that have little in common
 \citep[e.g.][]{TverskyKahnemann1981:The-Framing-of-,GigerenzerGoldstein1996:Reasoning-the-F,ScheibehenneRieskamp2013:Testing-the-Ada}. But
@@
 which in turn is conceived of as a \emph{uniform} way of forming preference and belief
-\emph{types}.
-
-Formally, given a class $ \mathcal{G} $ of games, $\gamma: \mathcal{G} \rightarrow \Theta \times E$ is a function that assigns a subjective preference $\theta \in \Theta$ and an epistemic state (or belief type) $e \in E$ to any game $G \in \mathcal{G}$.\footnote{Given a game $G$, the set $ \Theta $ is the set of all subjective preferences, or subjective utility functions, on $G$.
-I.e., $\Theta$ is the set of all functions $\theta: A \rightarrow \mathbb{R}$.}
-Then, given a set of subjective
-  preferences $ \Theta $ and
-  a set of or belief types $E$, an action selection function is a function
-  $\kappa: \Theta \times E \rightarrow A_i $, that associates any subjective representation of the game $ (\theta,e) \in \Theta \times E$ with an action $a^{*} \in A_i $.
-
-More concretely, we focus on two (\textit{subjective}) \emph{preference types} and two \emph{belief
-    types}. We view a preference type as a function $\tau: \mathcal{G} \rightarrow \Theta$, and
-  a belief type as a general disposition to form beliefs about the co-player’s behavior. The
-  two possible dispositions that we take account of are precise probabilistic belief and
-  imprecise belief, as we will explain in the next section.
-
-Since we are most interested here in studying whether evolutionary pressure could
-  support non-veridical subjective preferences, the two preference types that we consider are: the veridical type $\tau^\pi$, who uses the actual payoff function
+\emph{types}: we look at general \emph{subjective representation schemes}.
+
+Formally, given a class $ \mathcal{G} $ of strategic games,
+$\gamma_i: \mathcal{G} \rightarrow \Theta_i \times E_i$ is a function that assigns a subjective
+preference $\theta_i \in \Theta_i$ and an epistemic state $e_i \in E_i$ to any game
+$G \in \mathcal{G}$ for some agent $i$. A subjective preference $\theta_i$ for game $G$ and
+agent $i$ is just a payoff function for $i$ suitable to the acts and co-players in
+$G$. Crucially, this subjective payoff function can be different from the actual payoff in $G$,
+which we interpret as the objective fitness. An epistemic state $e_i$ for game $G$ and agent
+$i$ is some specification of $i$'s uncertainty about the co-players' behavior. Finally, an
+action selection function for agent $i$ is a function
+$\kappa_i: \Theta_i \times E_i \rightarrow \pow{A_i} $, that associates any subjective
+representation of the game $ (\theta_i,e_i) \in \Theta_i \times E_i$ with a set of prescribed
+actions for $i$ in $G$ under $i$'s subjective representation of $G$. We drop the index $i$ for
+readability in the following.
+
+We focus on two (\textit{subjective}) \emph{preference types} and two \emph{belief types}. We
+view a preference type as a function $\tau: \mathcal{G} \rightarrow \Theta$, and a belief type
+as a general disposition to form beliefs about the co-player’s behavior. The two possible
+dispositions that we take account of are precise probabilistic belief and imprecise belief, as
+we will explain in the next section. Since we are most interested here in studying whether
+evolutionary pressure could support non-veridical subjective preferences, the two preference
+types that we consider are: the veridical type $\tau^\pi$, who uses the actual payoff function
 $\pi$ of the actual game $G$, and the regret type $\tau^{reg}$, who looks at the regret
-  transformation of the actual game $G$.
-
-Finally, the action selection function $\kappa$ that we use in this paper is \textit{maxmin expected
-    utility} [GS89], for reasons that will be clear and justified in the following two
-  sections.
+transformation of the actual game $G$. Finally, the action selection function $\kappa$ that we
+use in this paper is \textit{maxmin expected utility} [GS89], for reasons that will be clear
+and justified in the following two sections.
 
@@
 % behavior. In other words, we even abstract away from the content of the DM's beliefs about his
-% opponents' behavior that he could have acquired by learning or observation, but first turn on
+% opponents' behavior that he could have acquiresd by learning or observation, but first turn on
 % the more general question of how uncertainty should be represented in order to interact with
@@
 
-In evolutionary game theory, for instance, players in a population obviously face uncertainty about the composition of the population that they are part of, and consequently about the co-player that they are randomly paired with at each round and about the co-player's action.
+In evolutionary game theory, for instance, players in a population obviously face uncertainty about the composition of the population that they are part of, and consequently about the co-player that they are randomly paired with at each round and about the co-players' action.
 We represent this uncertainty in two different ways that correspond to the two approaches discussed above: a Bayesian uniform distribution and an imprecise probability set.
@@
 
-\item $\overline{\mu} \in \Delta(A_{-i})$ is the probability measure over the co-player's actions such that: $\forall a_{-i} \in A_{-i}$, $\overline{\mu}(a_{-i})= \frac{1}{|A_{-i}|}$.
+\item $\overline{\mu} \in \Delta(A_{-i})$ is the probability measure over the co-players' actions such that: $\forall a_{-i} \in A_{-i}$, $\overline{\mu}(a_{-i})= \frac{1}{|A_{-i}|}$.
 

### 2015-11-10 paper/paper.tex
Paolo references inserted

@@
 
-\usepackage[]{helpers/mypackages}
-%\usepackage[natbib=true,style=authoryear-comp,backend=bibtex,doi=false,url=false]{biblatex}
-% \bibliography{helpers/MyRefLocal}
-\bibliography{choicePrince}
+\usepackage{etex}
+\usepackage[nobiblatex]{helpers/mypackages}
+\usepackage[backend=bibtex,natbib=true,style=authoryear-comp,backend=bibtex,doi=false,url=false]{biblatex}
+\bibliography{choicePrince,biblio}
 \usepackage{helpers/myenvironments}
@@
 Evolutionary game theory has become an established philosophical tool for probing into
-conceptual issues whose complexity requires mathematical modeling. However, most applications
+conceptual issues whose complexity requires mathematical modelling. However, most applications
 look at evolutionary selection of behavior in a single \emph{stage game}. There are two common
@@
 But only little attention has been paid to modeling the evolutionary competition between choice
-mechanisms in a game-theoretic framework \citep[but
+mechanisms in a game-theoretical framework \citep[but
 see][]{ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o}.\todo{More references
@@
 representations are ecologically valuable (i.e., lead to high fitness) is central and has been
-subject of recent interest (\textcolor{red}{CITE literature on evolution of
-  preferences}). Na\"ive intuition might convince us that preferences that veridically
+subject of recent interest \citep[e.g.][]{algweib13,DekElyYlan07,Sam01,RobSam11}. Na\"ive intuition might convince us that preferences that veridically
 represent the actual, true fitness measure that evolutionary selection is based upon must
@@
 The standard textbook definition of \textit{rationality} in economics and decision theory
-traces back to the seminal work of \citet{Neumannvon-NeumannMorgenstern1944:Theory-of-Games}
+traces back to the seminal work of \citet{deFinetti37}, \citet{Neumannvon-NeumannMorgenstern1944:Theory-of-Games}
 and \citet{Savage1954:The-Foundations}. It says that choice is rational only if it maximizes
@@
 rational empirically observed behavior in situations of social decision making, such as the
-prisoners' dilemma or public goods games, that might otherwise appear irrational (e.g. Fehr and
-Schmidt, Charness and Rabin, etc.).\todo{@Paolo: please include proper references}
+prisoners' dilemma or public goods games, that might otherwise appear irrational \citep[e.g.][]{fehrschmidt99,charrab02}.
 
 It could be objected that, without additional constraints, the notion of rationality is likely
-to collapse, as it seems possible to deem rational everything that is observed, given the
+to collapse, as it seems possible to deem rational almost everything that is observed, given the
 freedom to adjust beliefs and preferences at will. But there are many ways in which ascriptions
@@
 \emph{should} optimize that which makes them ``live,'' so to speak. For biological agents, the
-argument would be that subjective preferences \emph{should} track whatever determines objective
+argument would be that subjective preferences \emph{should} stay as close as possible to whatever determines objective
 fitness.
@@
 making. In other words, we focus on the evolutionary competition between \emph{subjective
-  representation schemes}: general ways of forming subjective preferences and types of
+  representation schemes}: general ways of forming subjective preferences and
 subjective beliefs. We show that subjective, non-veridical preference representations based on
-a notion of regret \citep[e.g.][]{Savage1951:The-theory-of-s,LoomesSugden1982:Regret-Theory:-}
+a notion of regret \citep[e.g.][]{Savage1951:The-theory-of-s,}
 can be adaptive and even outperform objective, veridical representations of the actual, true
@@
 
-A strategic game is a tuple $ G=\tuple{ N, (A_i , \pi_i)_{i \in N} }$ with $N$ a finite set of
+A simultaneous-move game is a tuple $ G=\tuple{ N, (A_i , \pi_i)_{i \in N} }$ with $N$ a finite set of
 players, $A_i$ a finite set of acts and $\pi_i$ a payoff function for each player $i \in N$. For the
@@
 symmetric if players have the same action set, $A_1 = A_2$, and payoffs are symmetric:
-$\pi_1(\myact{k}, \myact{l}) = \pi_2(\myact{l}, \myact{k})$ for all $k$ and $j$. An example is
+$\pi_1(a_k, a_j) = \pi_2(a_j, a_k)$ for all $a_j,a_k \in A_1$. An example is
 given in Figure~\ref{coordgame1}, which shows a coordination game. The numbers give the payoff
@@
 Definition~\ref{def:rationality}, is \emph{not} a choice rule in the present sense. Although
-the notion applies to game situations, of course, it requires an additional component, namely a
+the notion applies to game situations, it requires an additional component, namely a
 belief of the DM, before it can say which acts the DM should choose. Let
@@
 his opponents, he chooses rationally only if his choice $a^*_i$ maximizes expected utility
-$\EU(a) = \sum_{\act_{-i} \in \Acts_{-i}} \mu_i(\act_{-i}) \myts \pi_i(a_i, a_{-i})$. So this
+$\EU(a_i) := \sum_{\act_{-i} \in \Acts_{-i}} \mu_i(\act_{-i}) \myts \pi_i(a_i, a_{-i})$. So this
 requires a probabilistic belief about the opponents' action choices. In the example from
@@
 asking: what is the worst possible outcome for each row act? It is $0$ in either
-case. Consequently, the maximin rule would not favor either act; players choosing by the
+case. Consequently, the maximin rule would not favor either act: players choosing by the
 maximin rule would be indifferent between acts $I$ and $II$.
@@
 Another well-known choice rule is \emph{Laplace's rule} which prescribes to choose $\act^*$ if
-$\act^* \in \argmax_{a \in A} \sum_{a'} \pi(a, a')$. Laplace's rule is equivalent to rationally
-choosing under a \emph{flat belief} that assigns equal probability to all of the opponent's
+$\act^* \in \argmax_{a \in A} \sum_{a'} \pi(a, a')$. Laplace's rule is equivalent to expected utility maximization under a \emph{flat belief} that assigns equal probability to all of the opponent's
 choices. In the coordination game of Figure~\ref{coordgame1}, Laplace's rule selects act $II$.
@@
 The final choice rule that is relevant for our purposes here is \emph{regret
-  minimization}. Regret theory has been introduced in decision theory by
-\citet{Savage1951:The-theory-of-s} and Niherens [], and later developed by Bell [1982], Loomes
-and Sugden [1982], and Fishburn [1982] independently.\todo{fix references}\ Lately,
+  minimization}. The notion of regret in decision theory dates back at least to the work by
+\citet{Savage1951:The-theory-of-s}, and has later been developed by \citet{bell82}, \citet{fish82} and \citet{loosug82} independently. Lately,
 \citet{HalpernPass2012:Iterated-Regret} showed how the use of regret minimization can give
@@
 agent $i$ is just a payoff function for $i$ suitable to the acts and co-players in
-$G$. Crucially, this subjective payoff function can be different from the actual payoff in $G$,
-which we interpret as the objective fitness. An epistemic state $e_i$ for game $G$ and agent
+$G$. Crucially, this subjective payoff function can be different from the actual payoff function $\pi^G$ of $G$,
+which we interpret as the objective evolutionary fitness. An epistemic state $e_i$ for game $G$ and agent
 $i$ is some specification of $i$'s uncertainty about the co-players' behavior. Finally, an
@@
 The second answer involves imprecise probabilities and is related to the literature about unmeasurable uncertainty.
-Many authors argued in favor of this kind of approach [e.g., Walley91-96, Levi74, GardenforsANDSahlin82].
+Many authors argued in favor of this kind of approach \citep[e.g.][]{levi74,gardsah82,walley96}.
 Since it is consistent with the information available that all the marbles are red, or that no marble is red, the resulting model should take it into account and specify a lower probability of red $\underline{P}(R)$ and an upper probability of red $\overline{P}(R)$ that define an interval of possible probabilistic beliefs [$\underline{P}(R), \overline{P}(R)$].
@@
 This approach appears particularly relevant in a game theoretical context.
-Indeed, in a recent paper [Battigalliet al.15] Battigalli et al.
-write
+Indeed, in a recent paper \citet{BattCerrMM15} write
 
@@
 The other belief type $\overline{\mu}$ conceptualizes the uncertainty about the population by using the principle of insufficient reason and ascribes equal probability to all the possible alternatives.
-As we have seen, both options are reasonable and justifiable ways to deal with situations of uncertainty [REFERENCES].
+As we have seen, both options are reasonable and justifiable ways to deal with situations of uncertainty.
 \\
 
-In decision theory, the imprecise probability model is in line with most of the representation results of decision making under uncertainty [GilboaSchmeidler89,KMM06], and seems justified by empirical observations too.
-
-A prominent example is Ellsberg's paradox.
+In decision theory, the imprecise probability model is in line with most of the representation results of decision making under uncertainty \citep[e.g.][]{gilsch89,KlibMarMuk05}, and seems justified by empirical observations too.
+
+A prominent example is Ellsberg's paradox (\citet{ells61}).
 A bag contains 90 marbles, 30 are red and the remaining 60 are either black or yellow.
@@
 
-[[\noindent Definition \ref{def:expected fitness} gives the expected evolutionary fitness of player $(\tau, e)$ against player $(\tau', e')$ in game $G$.
-[OF COURSE we will postpone the definition of evolutionary fitness, it is only momentarily here!]
-\begin{definition} \label{def:expected fitness}
-
-Given a game $G \in \mathcal{G}$, a player $(\tau, e)$, and a player $(\tau', e')$, we define $\pi^G((\tau, e),(\tau', e')):= \pi^G(\kappa(\tau(G), e),\kappa(\tau'(G), e'))$.
-
-\end{definition}
-[OF COURSE we will postpone the definition of evolutionary fitness, it is only momentarily here!]]]
-
-It is then worth stressing here that $\kappa(\tau^{\pi}, \Delta(A_{-i}))$ turns out to be the actual payoff
+It is then worth stressing that $\kappa(\tau^{\pi}, \Delta(A_{-i}))$ turns out to be the actual payoff
 maximinimizer, $\kappa(\tau^{reg}, \Delta(A_{-i}))$ corresponds to the regret minimizer,
@@
   in turn, corresponds to the regret minimizing action of the original game $G^C$ of Figure
-  \ref{coordgame1}, namely action $II$, as we have seen in Section \ref{sec:regreTheory}. A
+  \ref{coordgame1}, namely action $II$, as we have seen in Section \ref{sec:choice-rules}. A
   player $(\tau^{reg},\overline{\mu})$ instead has subjective representation $\tau^{reg}(G^C)$
@@
 
-\bigskip
-\bigskip
-
-\todo[inline]{PAOLO rewrites up to here!!! }
-
-\bigskip
-\bigskip
-
 \iffalse
@@
 
-Evolutionary game theory has established itself as a useful tool for testing consequences of
-sets of assumptions about complex evolutionary processes. However, the standard approach in
-evolutionary game theory is not enough for our purposes, because it (i) fixes a single
+The standard approach in
+evolutionary game theory is not enough for our purposes, because it (i) fixes a unique and immutable
 \emph{stage game} (e.g., the prisoner's dilemma) and (ii) assumes that the object of
-evolutionary selection is behavior for that very game. Following a similar line of argument
+evolutionary selection is behavior for that very game. Following a line of argument coming from theoretical biology and behavioral ecology
 \citep[e.g.][]{FawcettHamblin2013:Exposing-the-be}, we therefore turn towards the evolutionary
 competition of \emph{choice mechanisms}, i.e., general ways of selecting concrete behavior
-across a range of different situations. As a consequence, the expected fitness of a choice
-mechanism will not be determined by only a single (elementary) stage game, but it will be a
+across a range of different situations, defined by the two functions $\gamma$ and $\kappa$. With this approach, the expected fitness of a choice
+mechanism will not be determined by a unique stage game, but it will be a
 complex function of the statistical properties of the environment: we have to take into account
@@
 $G \in \mathcal{G}$. Together, a class of games and a probability measure over it can be
-thought of as a model of the environment in which different choice mechanisms compete. Let $C$
-the a set of choice mechanisms that we care about. Then each choice mechanism $c \in C$ is a
-associated with an \emph{action selection function} $S_c$ that maps any $G \in \mathcal{G}$
-onto some action $S_c(G)$ of game $G$.\footnote{In all subsequent formal and simulation results
-  we assume that, whenever a choice mechanisms is selects indifferently a set of actions, the
-  agent will realize each with the same (flat) probability. For ease of parlor, we often do as
-  if there was a tie-break rule.} Different choice mechanisms can select the same act in some
-games. More importantly even, different choice mechanisms can have exactly the same action
-selection functions on a particular class of games $\mathcal{G}$. This is because we think of
-the object of evolutionary selection, not as the realized behavior but as the way behavior is
-specified. (We will see below that this can make an important difference, e.g., in the light of
-mutation.)
-
-Imagine a huge, possibly infinite society of agents, each of which carries a choice mechanism
-from $C$. For simplicity, let's assume that $C$ is finite and that $\mathcal{G}$ is
-a finite set of two-player strategic games. The expected fitness $EF(c_1)$ of an agent with
-choice principle $c_1$ is determined by the probability $P(c_2)$ of meeting an agent with
-choice principle $c_2$, which we will assume is the frequency of $c_2$ in the population, the
-probability $P(G)$ of playing game $G \in \mathcal{G}$ and the concrete payoff
-$\pi^G(c_1 \mid c_2)$ that the player with $c_1$ obtains when playing against a player with
-$c_2$ in $G$, which is uniquely defined by the associated action selection rules:
-\begin{align*}
-  EF(c_1) = \sum_{c_2 \in C} P(c_2) \cdot \sum_{G \in \mathcal{G}}  P(G) \cdot \pi^G(c_1 \mid c_2)\,.
-\end{align*}
-Similarly, the expected fitness of a $c_1$-agent, when playing against a $c_2$ agent is:
+thought of as a model of the environment in which different choice mechanisms compete.
+As we have seen in Definition \ref{def:maxminSEU}, given a game $G \in \mathcal{G}$, a choice mechanism prescribes the action(s) $\kappa(\gamma(G))$.
+Now imagine a huge, possibly infinite society of agents, each of which carries a choice mechanism, and a class $\mathcal{G}$ of symmetric two player games for simplicity.
+Definition \ref{def:expected evolutionary payoff} gives the expected evolutionary payoff of choice mechanism $\kappa(\tau, e)$ against choice mechanism $\kappa(\tau', e')$ in game $G \in \mathcal{G}$.
+
+\begin{definition} \label{def:expected evolutionary payoff}
+
+Given a game $G \in \mathcal{G}$, a choice mechanism $\kappa(\tau, e)$, and a choice mechanism $\kappa(\tau', e')$, we define $$\pi^G(\kappa(\tau(G), e),\kappa(\tau'(G), e')):= \sum_{a_i \in \kappa(\tau(G), e)} \sum_{a_j \in \kappa(\tau'(G), e')} \pi^G(a_i , a_j) \cdot \frac{1}{|\kappa(\tau(G), e)|} \cdot \frac{1}{|\kappa(\tau'(G), e')|}.$$
+
+\end{definition}
+
+Then the expected fitness $EF(\kappa(\tau, e))$ of an agent with
+choice mechanism $\kappa(\tau, e)$ is determined by the probability $P((\tau',e'))$ of meeting an agent with
+choice mechanism $\kappa(\tau',e')$, which we will assume is the frequency of $(\tau',e')$ in the population, the
+probability $P(G)$ of playing game $G \in \mathcal{G}$ and the evolutionary payoff
+$\pi^G(\kappa(\tau, e),\kappa(\tau', e'))$:
+
 \begin{align}
-  \label{eq:ExpectedPayoffs}
-  EF(c_1 \mid c_2) = \sum_{G \in \mathcal{G}}  P(G) \cdot \pi^G(c_1 \mid c_2)\,.
+\label{eq:EF}
+  EF(\kappa(\tau, e)) := \sum_{G \in \mathcal{G}} \sum_{(\tau',e') \in T \times E} P(G) \cdot P((\tau',e')) \cdot \pi^G (\kappa(\tau(G), e),\kappa(\tau'(G), e'))\,.
 \end{align}
 
-Notice that expected fitness of a choice mechanism is defined entirely in parallel to the
-expected fitness of an act in a fixed stage game, except that where the latter has a simple
+\noindent Similarly, the expected fitness of a choice mechanism $\kappa(\tau, e)$, when playing against another choice mechanism $\kappa(\tau', e')$ is:
+\begin{align}
+  \label{eq:pairwiseEF}
+  EF(\kappa(\tau, e),\kappa(\tau', e')) := \sum_{G \in \mathcal{G}}  P(G) \cdot \pi^G(\kappa(\tau(G), e),\kappa(\tau'(G), e'))\,.
+\end{align}
+
+Notice that the expected fitness of a choice mechanism is defined entirely in parallel to the
+expected payoff of an act in a fixed stage game (Definition \ref{def:expected evolutionary payoff}), except that where the latter has a simple
 payoff function, the former has an expectation over payoffs in a statistically rich
@@
 in terms of payoffs defined by a \emph{meta-game} over $\mathcal{G}$ whose ``acts'' are choice
-mechanisms and whose ``payoffs'' are the expected payoffs in
-Equation~(\ref{eq:ExpectedPayoffs}).\footnote{Allowing games in $\mathcal{G}$ that have
-  different numbers of players makes matters more complicated, but we neglect these
-  complications here, because we focus entirely on 2-player games.}
+mechanisms and whose ``payoffs'' are the expected evolutionary payoffs of
+Equation~(\ref{eq:pairwiseEF}).\footnote{Allowing games in $\mathcal{G}$ with different numbers of players makes matters formally, but not conceptually, more complicated.
+In the following we will focus entirely on two player games, hence we can neglect further complications for the moment.}
+
+\bigskip
+\bigskip
+
+\todo[inline]{PAOLO rewrites up to here!!! }
+
+\bigskip
+\bigskip
 

### 2015-12-14 paper/paper.tex
Paolo edits with conclusion

@@
 
-\title{Smart Representations: {R}ationality, Regret, Evolution \& the Environment}
+\title{Smart Representations: {R}ationality and Evolution in a Richer  Environment}
 \author{Paolo Galeazzi \& Michael Franke} \date{current version: November 5, 2015}
@@
 
-\section{Introduction / Motivation}
+\section{Introduction}
 \label{sec:intr--motiv}
+
+\begin{quotation} \textit{This is what I aim at, because the point of philosophy is to start with something so simple as not to seem worth stating, and to end with something so paradoxical that no one will believe it.} \citep{Russ18} \end{quotation}
 
@@
 competition of \emph{choice mechanisms} under selective pressure in a rich and variable
-environment \citep[e.g.][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche}. 
+environment \citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche}. 
 But only little attention has been paid to modeling the evolutionary competition between choice
@@
 forming decision relevant beliefs in the case of uncertainty. Since almost any reasonable
-learning or decision-making process will make use of some (subjective, agent-internal (possibly
-unconscious)) representation of the quality of choice options, the question of which such
+learning or decision making process will make use of some (subjective, agent-internal, possibly
+unconscious) representation of both beliefs and the quality of choice options, the question of which such
 representations are ecologically valuable (i.e., lead to high fitness) is central and has been
-subject of recent interest \citep[e.g.][]{algweib13,DekElyYlan07,Sam01,RobSam11}. Na\"ive intuition might convince us that preferences that veridically
+subject of recent interest also in economics literature \citep[e.g.,][]{algweib13,DekElyYlan07,RobSam11}. Na\"ive intuition might convince us that preferences that veridically
 represent the actual, true fitness measure that evolutionary selection is based upon must
-surely be the best. We demonstrate that, if we take into account how agents represent
+surely be the best. We demonstrate that, if we take into account the different ways agents may cope with
 uncertainty, this na\"ive conclusion is premature. Under certain reasonable epistemic
@@
 the competition of subjective representations of choice situations, in a variable
-environment. Concretely, we look at evolutionary ``meta-games'' whose ``acts'' are types of
-subjective representations of games and whose ``payoffs'' represent the average expected
-fitness that choice mechanisms using these representation types would accrue when playing
+environment. Concretely, we look at evolutionary ``meta-games'' whose ``acts'' are choice mechanisms and whose ``payoffs'' represent the average expected
+fitness that different choice mechanisms would accrue when playing
 arbitrary games (from a given class, with a given occurrence probability). In this sense, a
@@
 
-\todo[inline]{add overview}
+Section \ref{sec:rati--subj} overviews different accounts of rationality in decision making and relates the approach we take here to the existing literature on the topic.
+Section \ref{sec:basic-notions} introduces the various decision- and game-theoretic notions that will be later used in the evolutionary analysis.
+Sections \ref{sec:model} and \ref{sec:basic-model-1} define the evolutionary framework, and Section \ref{sec:results:-basic-model} presents the main results of the paper.
+Section \ref{sec:extensions} extends the evolutionary analysis by introducing more choice mechanisms in the model and by investigating the evolutionary performances of different choice mechanisms when facing arbitrary decision problems.
+Finally, in Section \ref{sec:conclusion} we comment on the results achieved and future perspectives.
 
@@
   Let $S$ be a (finite) set of states of the world and $A$ a (finite) set of actions. Given a
-  probability distribution $P$ over $S$ and a utility function
+  probability distribution $\mu$ over $S$ and a utility function
   $u \mycolon S \times A \rightarrow \mathbb{R} $, an action $a^* \in A$ is a rational choice
-  only if it maximizes the \emph{(subjective) expected utility}
-  $\EU(a) = \sum_{s \in S} P(s) \ u(s, a)$.
+ if it maximizes the \emph{(subjective) expected utility} 
+  $\EU(a) = \sum_{s \in S} \mu(s) \ u(s, a)$.
 \end{definition}
@@
 rational empirically observed behavior in situations of social decision making, such as the
-prisoners' dilemma or public goods games, that might otherwise appear irrational \citep[e.g.][]{fehrschmidt99,charrab02}.
+prisoners' dilemma or public goods games, that might otherwise appear irrational \citep[e.g.,][]{fehrschmidt99,charrab02}.
 
@@
 An alternative to descriptive vs.~normative views on rationality is \emph{adaptationism}
-\citep[e.g.][]{HagenChater2012:Decision-Making}. \todo{more references} Adaptationism aims to
+\citep[e.g.,][]{HagenChater2012:Decision-Making}. \todo{more references} Adaptationism aims to
 explain choice behavior by appeal to evolutionary considerations. The key idea is that decision
@@
 subjective beliefs. We show that subjective, non-veridical preference representations based on
-a notion of regret \citep[e.g.][]{Savage1951:The-theory-of-s,}
+a notion of regret \citep[e.g.,][]{Savage1951:The-theory-of-s,}
 can be adaptive and even outperform objective, veridical representations of the actual, true
 fitness, when agents, at least on occasion, hold \emph{imprecise probabilistic beliefs}
-(\textcolor{red}{CITATIONS}) and make decisions based on a security choice rule (here: the
-maximin rule applied to expected utility). The next section introduces all of these notions
+\citep[e.g.,][]{gilsch89,levi74,gardsah82} and make decisions based on a security choice rule (here: the
+maxmin rule applied to expected utility). The next section introduces all these notions
 (precise/imprecise beliefs, veridical/regret representations, \dots) in detail.
@@
 suggested a number of choice rules that aspire to capture a normative element of rational
-choice. We focus here on three classical choice rules: (i) maximin, (ii) Laplace and (iii)
+choice. We focus here on three classical choice rules: (i) maxmin, (ii) Laplace and (iii)
 regret minimization.
@@
 Perhaps the most well-known choice rule that does not require explicitly stating the DM's
-beliefs is the \emph{maximin rule}. It tells our agent to choose act $\act^*$ only if it
+beliefs is the \emph{maxmin rule}. It tells our agent to choose act $\act^*$ only if it
 maximizes payoffs for all worst case scenarios. For a strategic game with 2 players this can be
@@
 asking: what is the worst possible outcome for each row act? It is $0$ in either
-case. Consequently, the maximin rule would not favor either act: players choosing by the
-maximin rule would be indifferent between acts $I$ and $II$.
+case. Consequently, the maxmin rule would not favor either act: players choosing by the
+maxmin rule would be indifferent between acts $I$ and $II$.
 
@@
 
-\begin{definition}[Regret, regret minimization] \label{defn:regret} Given a strategic game
+\begin{definition}[Regret, Regret Minimization] \label{defn:regret} Given a strategic game
   $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the \emph{pairwise regret} of player $i$'s
@@
 %   \item outcome of rationalizability (max-EU)
-%   \item outcome of maximin rule
+%   \item outcome of maxmin rule
 %   \item outcome of Laplace rule
@@
 
-Regret minimization is intimately related to the maximin rule. Let the \emph{negative regret
+Regret minimization is intimately related to the maxmin rule. Let the \emph{negative regret
   transformation} of a strategic game $G$ be the game $G'$ derived from $G$ by replacing the payoff
@@
 the payoff of all players is the pairwise negative regret (under the payoffs from $G$). For
-example, the negative regret transform of the game in Figure~\ref{coordgame1} would have the
+example, the negative regret transformation of the game in Figure~\ref{coordgame1} would have the
 following payoff matrix, i.e., the negatives of the pairwise regrets given in
@@
 
-\noindent Acts selected by the maximin rule for the negative regret transformation of $G$ are
+\noindent Acts selected by the maxmin rule for the negative regret transformation of $G$ are
 always exactly the acts selected by regret minimization for the original game $G$.\todo{can we
@@
 
-This means that we can think of the maximin rule and regret minimization as essentially the
-same operation on different subjective representations of preference: while maximin considers
+This means that we can think of the maxmin rule and regret minimization as essentially the
+same operation on different subjective representations of preference: while maxmin considers
 actual objective payoffs (as defined by the modeller's game), regret minimization considers
@@
 shows, different subjective preferences can give rise to different choice prescriptions all
-else equal. While maximin is indifferent between $I$ and $II$, regret minimization uniquely
+else equal. While maxmin is indifferent between $I$ and $II$, regret minimization uniquely
 selects $II$.
@@
 implicit assumptions about what the DM prefers (e.g., when reconstructing regret minimization
-in terms of maximin-choices on the regret transformation). This is rather messy. To disentangle
+in terms of maxmin-choices on the regret transformation). This is rather messy. To disentangle
 and avoid confusion, we turn to choice mechanisms.
@@
 rules, contains an explicit level of subjective representation of a decision situation. For our
-purposes, we should think of a choice mechanism as a pair of functions $\gamma$ and $\kappa$,
+purposes, we should think of a choice mechanism as a pair of functions ($\gamma,\kappa$),
 where $\gamma$ is a \emph{subjective representation scheme} and $\kappa$ is an \emph{action
@@
   fixed}\ The subjective representation scheme $\gamma$ maps a game (or more generally any
-decision situation) onto a subjective representation of the game (or choice situation) and
+choice situation) onto a subjective representation of the game (or choice situation) and
 other decision-relevant beliefs (e.g., about what the opponent is likely to play). The action
@@
 that have little in common
-\citep[e.g.][]{TverskyKahnemann1981:The-Framing-of-,GigerenzerGoldstein1996:Reasoning-the-F,ScheibehenneRieskamp2013:Testing-the-Ada}. But
+\citep[e.g.,][]{TverskyKahnemann1981:The-Framing-of-,GigerenzerGoldstein1996:Reasoning-the-F,ScheibehenneRieskamp2013:Testing-the-Ada}. But
 to keep matters simple and implementable for a start, we will here only look at choice
@@
 Formally, given a class $ \mathcal{G} $ of strategic games,
-$\gamma_i: \mathcal{G} \rightarrow \Theta_i \times E_i$ is a function that assigns a subjective
-preference $\theta_i \in \Theta_i$ and an epistemic state $e_i \in E_i$ to any game
-$G \in \mathcal{G}$ for some agent $i$. A subjective preference $\theta_i$ for game $G$ and
-agent $i$ is just a payoff function for $i$ suitable to the acts and co-players in
-$G$. Crucially, this subjective payoff function can be different from the actual payoff function $\pi^G$ of $G$,
-which we interpret as the objective evolutionary fitness. An epistemic state $e_i$ for game $G$ and agent
-$i$ is some specification of $i$'s uncertainty about the co-players' behavior. Finally, an
+$\gamma_i: \mathcal{G} \rightarrow \Theta \times E$ is a function that assigns a subjective
+preference $\theta \in \Theta$ and an epistemic state $e \in E$ to any game
+$G \in \mathcal{G}$ for some agent $i$.
+A subjective preference $\theta$ for game $G$ is just a subjective utility function $\theta:A \rightarrow \mathbb{R}$.
+Crucially, this subjective utility function can be different from the actual payoff function $\pi^G$ of $G$,
+which we interpret as the objective evolutionary fitness. An epistemic state $e$ for game $G$ is some specification of a player's uncertainty about the co-players' behavior. Finally, an
 action selection function for agent $i$ is a function
-$\kappa_i: \Theta_i \times E_i \rightarrow \pow{A_i} $, that associates any subjective
-representation of the game $ (\theta_i,e_i) \in \Theta_i \times E_i$ with a set of prescribed
+$\kappa_i: \Theta \times E \rightarrow \pow{A_i} $, that associates any subjective
+representation of the game $ (\theta,e) \in \Theta \times E$ with a set of prescribed
 actions for $i$ in $G$ under $i$'s subjective representation of $G$. We drop the index $i$ for
@@
 transformation of the actual game $G$. Finally, the action selection function $\kappa$ that we
-use in this paper is \textit{maxmin expected utility} [GS89], for reasons that will be clear
+use in this paper is \textit{maxmin expected utility} \citep{gilsch89}, for reasons that will be clear
 and justified in the following two sections.
@@
 % The following subsection describes what these belief types are and how a single action
-% selection function (maximin expected utility) gives rise to an intersting parallel with
+% selection function (maxmin expected utility) gives rise to an intersting parallel with
 % classical choice rules.
@@
 What is then the probability that I will draw a red marble?
-As in Walley91-96, we are not talking about physical probability, but rather about epistemic probability, i.e., the subjective probability that an agent attributes to an event.
+As in \citet{walley96}, we are not talking about physical probability, but rather about epistemic probability, i.e., the subjective probability that an agent attributes to an event.
 In the literature there are two traditional ways of answering this kind of questions.
@@
 The second answer involves imprecise probabilities and is related to the literature about unmeasurable uncertainty.
-Many authors argued in favor of this kind of approach \citep[e.g.][]{levi74,gardsah82,walley96}.
+Many authors argued in favor of this kind of approach \citep[e.g.,][]{levi74,gardsah82,walley96}.
 Since it is consistent with the information available that all the marbles are red, or that no marble is red, the resulting model should take it into account and specify a lower probability of red $\underline{P}(R)$ and an upper probability of red $\overline{P}(R)$ that define an interval of possible probabilistic beliefs [$\underline{P}(R), \overline{P}(R)$].
@@
 This approach appears particularly relevant in a game theoretical context.
-Indeed, in a recent paper \citet{BattCerrMM15} write
+Indeed, in a recent paper \citet{BattCerrMM15} write:
 
@@
 We represent this uncertainty in two different ways that correspond to the two approaches discussed above: a Bayesian uniform distribution and an imprecise probability set.
-This amounts to having two different belief types, $ \overline{\mu}$ and $ \Delta(A_{-i})$, where $\overline{\mu}$ stands for the uniform distribution and $\Delta(A_{-i})$ is the probability set, defined as follows:
-
-\begin{itemize}
-
-\item $ \Delta(A_{-i}):=\lbrace \mu \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu(a_{-i}) = 1 \rbrace$;
-
-\item $\overline{\mu} \in \Delta(A_{-i})$ is the probability measure over the co-players' actions such that: $\forall a_{-i} \in A_{-i}$, $\overline{\mu}(a_{-i})= \frac{1}{|A_{-i}|}$.
+This amounts to having two different belief types, $ \overline{\mu}$ and $ \Delta $, where $\overline{\mu}$ stands for the uniform distribution and $\Delta$ is the probability set, defined as follows:
+
+\begin{itemize}
+
+\item $ \Delta \equiv \Delta(A_{-i}) :=\lbrace \mu \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu(a_{-i}) = 1 \rbrace$;
+
+\item $\overline{\mu} \in \Delta$ is the probability measure over the co-players' actions such that: $\forall a_{-i} \in A_{-i}$, $\overline{\mu}(a_{-i})= \frac{1}{|A_{-i}|}$.
 
@@
 Hence, we consider two possible epistemic states in the face of uncertainty.
-The belief type $\Delta(A_{-i})$ represents a situation of non-Bayesian radical uncertainty, where the players are not able to narrow down the set of probability distributions to a single one and they consider all of them as possible.
+The belief type $\Delta$ represents a situation of non-Bayesian radical uncertainty, where the players are not able to narrow down the set of probability distributions to a single one and they consider all of them as possible.
 The other belief type $\overline{\mu}$ conceptualizes the uncertainty about the population by using the principle of insufficient reason and ascribes equal probability to all the possible alternatives.
@@
 
-In decision theory, the imprecise probability model is in line with most of the representation results of decision making under uncertainty \citep[e.g.][]{gilsch89,KlibMarMuk05}, and seems justified by empirical observations too.
+In decision theory, the imprecise probability model is in line with most of the representation results of decision making under uncertainty \citep[e.g.,][]{gilsch89,KlibMarMuk05,GhirMar02}, and seems justified by empirical observations too.
 
@@
 \begin{fact} \label{fact:singleton probability set}
-Whenever the probability set is a singleton, maximinization of
+Whenever the probability set is a singleton, maximinimization of
 expected utility coincides with maximization of expected utility.
@@
 
-By fixing the action selection component to maximin expected utility, and allowing two belief and
+By fixing the action selection component to maxmin expected utility, and allowing two belief and
 two preference types, we regain all the choice rules considered in sectionNN from a more general and unified standpoint, as it is summed up in
@@
 
-It is then worth stressing that $\kappa(\tau^{\pi}, \Delta(A_{-i}))$ turns out to be the actual payoff
-maximinimizer, $\kappa(\tau^{reg}, \Delta(A_{-i}))$ corresponds to the regret minimizer,
+It is then worth stressing that $\kappa(\tau^{\pi}, \Delta)$ turns out to be the actual payoff
+maximinimizer, $\kappa(\tau^{reg}, \Delta)$ corresponds to the regret minimizer,
 $\kappa(\tau^{\pi}, \overline{\mu})$ is the expected actual payoff maximizer (with flat beliefs), and
@@
     $\tau^\pi$ & $\overline{\mu}$ & Laplace \\
-    $\tau^\pi$ & $\Delta(A_{-i})$ & maximin \\ 
+    $\tau^\pi$ & $\Delta$ & maxmin \\ 
     $\tau^{reg}$ & $\overline{\mu}$ & Laplace \\
-    $\tau^{reg}$ & $\Delta(A_{-i})$ & regret minimization \\ 
+    $\tau^{reg}$ & $\Delta$ & regret minimization \\ 
   \end{tabular}
@@
 \begin{fact} \label{fact:maxEU-minReg} For any strategic game $G$ and any arbitrary
-  probabilistic belief $\mu \in \Delta(A_{-i})$ about the opponents' behavior, the acts
+  probabilistic belief $\mu \in \Delta$ about the opponents' behavior, the acts
   selected by maximization of expected utility for $G$ under $\mu$ are exactly the acts
-  selected by the maximization of expected utility for the negative regret transform of $G$
-  under $\mu$ \citep[e.g.][]{HalpernPass2012:Iterated-Regret}.
+  selected by the maximization of expected utility for the negative regret transformation of $G$
+  under $\mu$ \citep[e.g.,][]{HalpernPass2012:Iterated-Regret}.
 \end{fact}
@@
 \begin{fact} \label{fact:equivalence2x2}
-In the class of $2 \times 2$ symmetric games, players $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg},\overline{\mu})$ are behaviorally equivalent.
+In the class of $2 \times 2$ symmetric games, players $(\tau^{reg}, \Delta)$, $(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg},\overline{\mu})$ are behaviorally equivalent.
 \end{fact}
@@
   Consider the game in Figure \ref{coordgame1} again. When a player characterized
-  by\footnote{To ease notation in the following we will refer to a player directly as a pair
-    $(player \text{ } type \text{ } \tau,\text{ } epistemic\text{ } type \text{ } e)$.} player
-  type $ \tau^{reg} $ and epistemic type $ \Delta(A_{-i}) $ faces the game in Figure
-  \ref{coordgame1}, her player type gives rise to the representation $\tau^{reg}(G^C)$ in
+  by\footnote{To ease notation in the following we will refer to the pair
+    $(\text{preference type } \tau,\text{ belief type } e)$ as the \textit{player type}.} preference
+  type $ \tau^{reg} $ and belief type $ \Delta $ faces the game in Figure
+  \ref{coordgame1}, her preference type gives rise to the representation $\tau^{reg}(G^C)$ in
   Figure \ref{coordgame1reg}. Then, maximinimizing expected utility over the probability
-  simplex $ \Delta(A_{-i}) $ given the game in Figure \ref{coordgame1reg} corresponds to
+  simplex $ \Delta $ given the game in Figure \ref{coordgame1reg} corresponds to
   playing the standard maxmin strategy [REF] of that game.\footnote{Notice that this is the
     case for any game: given a game $G$, maximinimizing expected utility over the probability
-    simplex $ \Delta(A_{-i}) $ amounts to playing the standard maxmin strategy of $G$.} This,
+    simplex $ \Delta $ amounts to playing the standard maxmin strategy of $G$.} This,
   in turn, corresponds to the regret minimizing action of the original game $G^C$ of Figure
@@
   such a player would play action $II$, i.e., the action that maximinimizes expected utility
-  given the flat probability measure $\overline{\mu}$.\footnote{As we already noticed,
-    maximinimizing expected utility given a probability measure $\mu$ is equivalent to
-    maximizing expected utility given $\mu$.}  Similarly, a player
-  $(\tau^{\pi},\Delta(A_{-i}))$ will have the subjective representation coinciding with the
+  given the flat probability measure $\overline{\mu}$. Similarly, a player
+  $(\tau^{\pi},\Delta)$ will have the subjective representation coinciding with the
   objective fitness game, i.e., $ \tau^{\pi}(G^C)= G^C $. Then, both actions $I$ and $II$
-  maximinimize expected utility over the probability simplex $ \Delta(A_{-i}) $. Hence, a
-  player $(\tau^{\pi},\Delta(A_{-i}))$ will be indifferent between $I$ and $II$, and will
+  maximinimize expected utility over the probability simplex $ \Delta $. Hence, a
+  player $(\tau^{\pi},\Delta)$ will be indifferent between $I$ and $II$, and will
   randomize with equal probability $(\frac{1}{2}I,\frac{1}{2}II)$. Finally, a player
@@
 
-%\todo[inline]{should we explain here, or very soon, what the resulting types really are: regret minimizers, maximin players \dots}
+%\todo[inline]{should we explain here, or very soon, what the resulting types really are: regret minimizers, maxmin players \dots}
 
@@
 
-\noindent As we have seen in the previous example, this is not the case in the presence of (radical) uncertainty, in the sense of representation of belief state in terms of a set of probability, as in $ \Delta(A_{-i}) $.
+\noindent As we have seen in the previous example, this is not the case in the presence of (radical) uncertainty, in the sense of representation of belief state in terms of a set of probability, as in $ \Delta $.
 \fi
-
-\newpage
 
@@
 evolutionary selection is behavior for that very game. Following a line of argument coming from theoretical biology and behavioral ecology
-\citep[e.g.][]{FawcettHamblin2013:Exposing-the-be}, we therefore turn towards the evolutionary
+\citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be}, we therefore turn towards the evolutionary
 competition of \emph{choice mechanisms}, i.e., general ways of selecting concrete behavior
@@
 
-Then the expected fitness $EF(\kappa(\tau, e))$ of an agent with
+\noindent Then the expected evolutionary fitness $EF_{\mathcal{G}}(\kappa(\tau, e))$ of an agent with
 choice mechanism $\kappa(\tau, e)$ is determined by the probability $P((\tau',e'))$ of meeting an agent with
@@
 \label{eq:EF}
-  EF(\kappa(\tau, e)) := \sum_{G \in \mathcal{G}} \sum_{(\tau',e') \in T \times E} P(G) \cdot P((\tau',e')) \cdot \pi^G (\kappa(\tau(G), e),\kappa(\tau'(G), e'))\,.
+  EF_{\mathcal{G}}(\kappa(\tau, e)) := \sum_{G \in \mathcal{G}} \sum_{(\tau',e') \in T \times E} P(G) \cdot P((\tau',e')) \cdot \pi^G (\kappa(\tau(G), e),\kappa(\tau'(G), e'))\,.
 \end{align}
@@
   \label{eq:pairwiseEF}
-  EF(\kappa(\tau, e),\kappa(\tau', e')) := \sum_{G \in \mathcal{G}}  P(G) \cdot \pi^G(\kappa(\tau(G), e),\kappa(\tau'(G), e'))\,.
+  EF_{\mathcal{G}}(\kappa(\tau, e),\kappa(\tau', e')) := \sum_{G \in \mathcal{G}}  P(G) \cdot \pi^G(\kappa(\tau(G), e),\kappa(\tau'(G), e'))\,.
 \end{align}
@@
 
-\bigskip
-\bigskip
-
-\todo[inline]{PAOLO rewrites up to here!!! }
-
-\bigskip
-\bigskip
-
 \section{The basic model}
@@
 determined probabilities $P(G)$ in order to match the natural environment of a given
-population. But for our theoretical purposes we adopt another approach. For a first basic
-model, let $\mathcal{G}$ be a set of symmetric 2-player games with $2$ acts. (We will look at
-extensions and generalizations in Section~\ref{sec:extensions}). More precisely, we imagine the
-class $\mathcal{G}$ to be generated from the generic form table of Figure \ref{generic form
+population. But for our theoretical purposes we adopt another approach.
+
+For a first basic
+model, let $\mathcal{G}$ be a set of symmetric two player games with two acts. (We will look at
+extensions and generalizations in Section~\ref{sec:extensions}). More concretely, we imagine the
+class $\mathcal{G}$ to be generated from the generic form table of Table \ref{generic form
   table}, where $a,b,c,d$ are i.i.d.~random variables sampled from a finite set of natural
 numbers $ \lbrace 0, \dots, 10 \rbrace$.
-
+After a game $G \in \mathcal{G}$ is generated, players in the population are randomly paired to play the game $G$.
+Each player represents a choice mechanism, and selects an action accordingly.
+At the end of the game, the evolutionary payoffs of each player are recorded, another game $G' \in \mathcal{G}$ is generated, players are randomly paired again, and so on.
+
+\iffalse
 \begin{figure}
@@
 \end{figure}
-
-\subsection{Player types}
-
-The set of all possible player types amouts to the set of all possible functions $ \tau: \mathcal{G} \rightarrow  \Theta $, i.e., $T=\mathbb{R}^{4^{\mathbb{R}^{4}}} $ , but for the sake of simplicity we will focus on types that are relevant and meaningful from a decision-theoretic point of view.
-We are mainly interested in two types: the objective type and the regret type.\\
+\fi
+
+\begin{table}[]
+\centering
+%\caption{generic form table for $2 \times 2$ symmetric games}
+%\label{generic form table}
+\begin{tabular}{|l|l|l|}
+\hline
+ & $I$ & $II$ \\ \hline
+$I$ & $a;a$ & $b;c$ \\ \hline
+$II$ & $c;b$ & $d;d$ \\ \hline
+\end{tabular}
+\caption{Generic form table for $2 \times 2$ symmetric games}
+\label{generic form table}
+\end{table}
+
+\subsection{Preference types}
+
+The set of all possible preference types $T$ amounts to the set of all possible functions $ \tau: \mathcal{G} \rightarrow  \Theta $, i.e., $\tau: \mathbb{R}^{4} \rightarrow \mathbb{R}^{4} $.
+However, here we want to focus on some subsets of $T$ that are also meaningful from a decision-theoretic point of view.
+As introduced in Section \ref{sec:basic-notions}, we are mainly interested in two types: the objective type and the regret type.
+In other words, we consider two prominent preference types: a type who has a veridical subjective utility that perfectly matches the objective utility (i.e., the evolutionary fitness), and a type who has a non-veridical regret-based subjective utility.
+
+\iffalse
+
 Given a game $G$ and Definition \ref{defn:parwreg}, it is straightforward to define the
@@
 
-\todo[inline]{can some of these definitions not be written as one? e.g., regret preference and
-  regret type as one definition? seems more elegant to me, because it's less repetitive (``for
-  a game ...'')}
-
 \begin{definition}[Regret preference] \label{defn:regpref}
@@
 
-\noindent In other words, we consider two prominent player types: a type who has a veridical subjective utility that perfectly matches the objective utility (i.e., the evolutionary fitness); and a type who has a non-veridical regret-based subjective utility.
+\fi
 
@@
 
-In this section we present results of computer simulations and analytical proofs for our basic
-model with the four player types introduced in the previous section.
+In this section we present results of computer simulations and analytical proofs for the basic
+model with the four choice mechanisms introduced in the previous sections.
 
@@
 numerical simulation from averaging over $100,000$ randomly sampled games in $\mathcal{G}$ with
-$a,b,c,d \in \lbrace 0, \dots, 10 \rbrace$. Concretely, games were sampled repeatedly by
+$a,b,c,d \in \lbrace 0, \dots, 10 \rbrace$. Games were sampled repeatedly by
 choosing independently four integers $a,b,c,d \in \lbrace 0, \dots, 10 \rbrace$ uniformly at
@@
   \toprule
- & $\tau^{reg}, \Delta(A_{-i})$ 
- & $\tau^{\pi}, \Delta(A_{-i})$ 
+ & $\tau^{reg}, \Delta$ 
+ & $\tau^{\pi}, \Delta$ 
  & $\tau^{reg}, \overline{\mu}$ 
@@
   \midrule
-  $\tau^{reg}, \Delta(A_{-i})$ & 6.663 & 6.662 & 6.663 & 6.663 \\ 
-  $\tau^{\pi}, \Delta(A_{-i})$ & 6.486 & 6.484 & 6.486 & 6.486 \\ 
+  $\tau^{reg}, \Delta$ & 6.663 & 6.662 & 6.663 & 6.663 \\ 
+  $\tau^{\pi}, \Delta$ & 6.486 & 6.484 & 6.486 & 6.486 \\ 
   $\tau^{reg}, \overline{\mu}$ & 6.663 & 6.662 & 6.663 & 6.663 \\  
@@
 Simulation results obviously reflect Fact~\ref{fact:equivalence2x2} in that all encounters in
-which types $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{reg}, \overline{\mu})$ or
+which types $(\tau^{reg}, \Delta)$, $(\tau^{reg}, \overline{\mu})$ or
 $(\tau^{\pi}, \overline{\mu})$ are substituted for one another yield identical results. More
-interestingly, Table~\ref{tab:ExpectedFitness_4Types} shows that the maximin strategy
-$(\tau^{\pi}, \Delta(A_{-i}))$ is strictly dominated by either of the three other strategies:
-in each column (i.e., for each kind of opponent), the maximin strategy is strictly worse
+interestingly, Table~\ref{tab:ExpectedFitness_4Types} shows that the maxmin strategy
+$(\tau^{\pi}, \Delta)$ is strictly dominated by either of the three other strategies:
+in each column (i.e., for each kind of opponent), the maxmin strategy is strictly worse
 than any of the three behaviorally equivalent competitors. This has a number of interesting
@@
 we restrict attention to a population of radically uncertain players, i.e., where only
-epistemic type $\Delta(A_{-i})$ exists, the regret type $ \tau^{reg} $ is the only
+belief type $\Delta$ exists, a population of regret types $ \tau^{reg} $ is the only
 \emph{evolutionarily stable state}. An evolutionarily stable state is a state which cannot be
-invaded by a small number of mutants. More strongly, since maximin play is strictly dominated,
-we expect selection that is driven by expected fitness to invariably weed out maximin behavior
+invaded by a small number of mutants. More strongly, since maxmin play is strictly dominated,
+we expect selection that is driven by expected fitness to invariably weed out maxmin behavior
 in favor of regret minimization. In other words, when taking average payoffs over the class of
-random games looked at here, regret minimization is a better choice rule than standard maxmin
-from an evolutionary point of view, despite the fact that the former, but not the letter
+random games considered here, regret minimization is a better choice mechanism than standard maxmin
+from an evolutionary point of view, despite the fact that the former, but not the latter,
 entertains non-veridical subjective preferences.
@@
 Next, if we look at the competition between all four types represented in
-Table~\ref{tab:ExpectedFitness_4Types}, $(\tau^{reg}, \Delta(A_{-i}))$ is no longer
+Table~\ref{tab:ExpectedFitness_4Types}, $(\tau^{reg}, \Delta)$ is no longer
 evolutionarily stable. Rather, given behavioral equivalence (Fact~\ref{fact:equivalence2x2}),
-types $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{reg}, \overline{\mu})$, and
+types $(\tau^{reg}, \Delta)$, $(\tau^{reg}, \overline{\mu})$, and
 $(\tau^{\pi}, \overline{\mu})$ are all \emph{neutrally stable}
-\citep{Maynard-Smith1982:Evolution-and-t}. But since $(\tau^{\pi}, \Delta(A_{-i}))$ is strictly
+\citep{Maynard-Smith1982:Evolution-and-t}. But since $(\tau^{\pi}, \Delta)$ is strictly
 dominated and so disfavored by fitness-based selection, we are still drawn to conclude that
-maximin behavior is weeded out in favor of a population with a random distribution of the
+maxmin behavior is weeded out in favor of a population with a random distribution of the
 remaining three types.
@@
 configurations are attracted to states with only three player types:
-$\tuple{\tau^{reg}, \Delta(A)}$, $\tuple{\tau^{reg}, \overline{\mu}}$ and
-$\tuple{\tau^{\pi}, \overline{\mu}}$. The relative proportions of these depend on the initial
-population.\todo{check uniform notation for player types: round vs.~square brackets} This
+$(\tau^{reg}, \Delta)$, $(\tau^{reg}, \overline{\mu})$ and
+$(\tau^{\pi}, \overline{\mu})$. The relative proportions of these depend on the initial
+population.\todo{check uniform notation for player types: round vs.~square brackets}  Nonetheless, this
 variability disappears if we add a small mutation rate to the dynamics. We assume a fixed,
 small mutation rate $\epsilon$ for the probability that a player's preference type \emph{or}
-her epistemic type changes to another random preference type or epistemic type. The probability
-that a player type randomly mutates into a completely different player type with altogether
-different preference type and epistemic type would then be $\epsilon^2$. With these assumptions
+her belief type changes to another preference type or belief type. The probability
+that a player randomly mutates into a completely different player with altogether
+different preference type and belief type would then be $\epsilon^2$. With these assumptions
 about ``component-wise mutations'', numerical simulations of the (discrete time)
@@
   \begin{tabular}{ccc}
-    $\tuple{\tau^{reg}, \Delta(A)}$ & $\tuple{\tau^{reg},
-      \overline{\mu}}$ & $\tuple{\tau^{\pi}, \overline{\mu}}$ \\ \hline
+    $(\tau^{reg}, \Delta)$ & $(\tau^{reg},
+      \overline{\mu})$ & $(\tau^{\pi}, \overline{\mu})$ \\ \hline
     0.279  &   0.383 &    0.281 
@@
 treated equally all the while. If mutation probabilities are a function of individual
-components of such behavior-generating mechanisms, it can be the case that certain components
+components (i.e., preference and belief types) of such behavior-generating mechanisms, it can be the case that certain components
 are more strongly favored by a process of random mutation and selection. This is exactly the
@@
 behaviorally equivalent. In sum, component-wise mutation could have lead to a majority of
-regret-based players even if they are behaviorally indiscernible from decision makers with
+regret-based players even if, in the context of two-by-two symmetric games, they are behaviorally indiscernible from decision makers with
 veridical preferences, because regret types are better off under radical uncertainty.
@@
 obtained by averaging over numerical simulations, are not fully general and possibly spoiled by
-random fluctuations in the sampling procedure. Fortunately, for the case of symmetric
-$2 \times 2$ games, the main result that maximin types $(\tau^{\pi}, \Delta(A_{-i}))$ are
+random fluctuations in the sampling procedure. Fortunately, for the case of two-by-two symmetric games, the main result that maxmin types $(\tau^{\pi}, \Delta)$ are
 strictly dominated can also be shown analytically for generous general conditions on how likely
-randomly sampled games are.
+randomly sampled games are. Let $\Lambda$ denote the set of player types in the population, and fix $\kappa$ to be maxmin expected utility as usual.
 
@@
 
-  Let $\Lambda = \lbrace (\tau^{\pi}, \Delta(A_{-i})), (\tau^{reg}, \Delta(A_{-i})) \rbrace$ be
-  the set of possible meta-types $(\tau, e)$ in the population, and let $\mathcal{G}$ be the class
-  of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex,
-  set of i.i.d.~values. Then, $(\tau^{reg}, \Delta(A_{-i}))$ is the only strict Nash
+ Fix $\Lambda = \lbrace (\tau^{\pi}, \Delta), (\tau^{reg}, \Delta) \rbrace$, and let $\mathcal{G}$ be the class
+  of $2 \times 2$ symmetric games with payoffs sampled from a
+  set of i.i.d.~values with at least three elements in the support. Then, $(\tau^{reg}, \Delta)$ is the only (strict) Nash
   equilibrium in the resulting meta-game.
@@
 
-From Fact \ref{fact:equivalence2x2} and Proposition \ref{proposition1} the following corollary follows.
+\noindent The next corollary about evolutionary stability follows from proposition \ref{proposition1}.
 
 \begin{corollary} \label{corollary1}
+
+Fix $\Lambda = \lbrace (\tau^{\pi}, \Delta), (\tau^{reg}, \Delta) \rbrace$, and let $\mathcal{G}$ be the class
+  of $2 \times 2$ symmetric games with payoffs sampled from a
+  set of i.i.d.~values with at least three elements in the support. Then, the unique evolutionarily stable state is a monomorphic population of $(\tau^{reg}, \Delta)$-players.
+
+\iffalse
 
@@
   $(\tau^{reg}, \overline{\mu})$.
+\fi
 
@@
 
-Corollary~\ref{corollary1} tells us that the conclusions drawn in the previous section based on
+Proposition \ref{proposition1} and Corollary~\ref{corollary1} tell us that the conclusions drawn in the previous section based on
 the meta-game in Table~\ref{tab:ExpectedFitness_4Types} hold more generally for any class of
 games in which the probability of encountering a game is the product of independently sampling
-four identically distributed payoff values. As before, player types
-$(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
-$(\tau^{reg}, \overline{\mu})$ will be neutrally stable, and fitness-based selection will tend
-to weed out maximin play and leave us with a population of arbitrary frequency of
-$(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
-$(\tau^{reg}, \overline{\mu})$ meta-types.
+four identically distributed payoff values. As before,
+$(\tau^{reg}, \Delta)$, $(\tau^{\pi}, \overline{\mu})$, and
+$(\tau^{reg}, \overline{\mu})$ players will be neutrally stable, and fitness-based selection will tend
+to weed out maxmin play and leave us with a population of arbitrary frequency of
+$(\tau^{reg}, \Delta)$, $(\tau^{\pi}, \overline{\mu})$, and
+$(\tau^{reg}, \overline{\mu})$ players.
 
@@
 not only persist, but even be favored by natural selection if agents are radically
-uncertain. This holds generally for playing arbitrary $2 \times 2$ games whose payoffs are
+uncertain. This holds generally for playing arbitrary $2 \times 2$ symmetric games whose payoffs are
 sampled identically and independently at random.
@@
 How do the basic results from the previous section carry over to more encompassing, richer
-models? Section~\ref{sec:more-types} first considers further conceptually interesting
-preference types that have been suggested in the recent literature. Section~\ref{sec:n-times-n}
-then considers the case of $n \times n$ games for $n \ge 2$. Finally, to put our results into
-the proper perspective, Section~\ref{sec:solitary-decisions} ends with a brief comparison of
+models? Section~\ref{sec:more-types} first introduces further conceptually interesting
+preference types that have been considered in evolutionary game theory. Section~\ref{sec:n-times-n}
+then addresses the case of $n \times n$ games for $n \ge 2$. Finally, to put our results into
+a broader perspective, Section~\ref{sec:solitary-decisions} ends with a brief comparison of
 game situations with cases of solitary decision making.
@@
 
+\iffalse
+
 \begin{definition}[Altruistic preference] \label{defn:altpref}
@@
 
+\fi
+
 \begin{definition}[Altruistic type] \label{defn:alttype}
 
-Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{alt}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{alt}(G)= \theta^{alt}$.
+Given a two player game  $ G $, the \textit{altruistic type} $\tau^{alt}$ is characterized by the subjective utility function $\tau^{alt}(G)(a_i, a_j):=\pi_i(a_i,a_j) + \pi_j(a_i,a_j)$.\footnote{A more general formulation would be to define an $ \alpha$-altruistic type, for $\alpha \in [0,1]$, with subjective utility $ \tau^{\alpha lt}(G)(a_i, a_j):=\pi_i(a_i,a_j) + \alpha \pi_j(a_i,a_j)$.
+Since we are not interested in the evolution of degrees of altruism, here we simply fix $ \alpha = 1 $.}
 
@@
 
+\iffalse
+
 \begin{definition}[Competitive preference] \label{defn:compref}
 
-For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{com}: A \rightarrow \mathbb{R} $ such that $ \theta^{com}(a_i,a_{-i})=\pi(a_i,a_{-i}) - \sum_{j \neq i} \pi(a_{j},a_{-j})$.
+For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the competitive preference $ \theta^{com}: A \rightarrow \mathbb{R} $ such that $ \theta^{com}(a_i,a_{-i})=\pi(a_i,a_{-i}) - \sum_{j \neq i} \pi(a_{j},a_{-j})$.
 
@@
 
+\fi
+
 \begin{definition}[Competitive type] \label{defn:comtype}
 
-Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call altruistic type the function $\tau^{com}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{com}(G)= \theta^{com}$.
+Given a two player game  $ G $, the \textit{competitive type} $\tau^{com}$ is characterized by the subjective utility function $\tau^{com}(G)(a_i, a_j):=\pi_i(a_i,a_j) - \pi_j(a_i,a_j)$.
 
@@
   \hline
- & $\tuple{\tau^{reg}, \Delta(A)}$ 
- & $\tuple{\tau^{\pi}, \Delta(A)}$ 
- & $\tuple{\tau^{com}, \Delta(A)}$
- & $\tuple{\tau^{alt}, \Delta(A)}$
- & $\tuple{\tau^{reg}, \overline{\mu}}$ 
- & $\tuple{\tau^{\pi}, \overline{\mu}}$ 
- & $\tuple{\tau^{com}, \overline{\mu}}$
- & $\tuple{\tau^{alt}, \overline{\mu}}$ \\ 
+ & $(\tau^{reg}, \Delta)$ 
+ & $(\tau^{\pi}, \Delta)$ 
+ & $(\tau^{com}, \Delta)$
+ & $(\tau^{alt}, \Delta)$
+ & $(\tau^{reg}, \overline{\mu})$ 
+ & $(\tau^{\pi}, \overline{\mu})$ 
+ & $(\tau^{com}, \overline{\mu})$
+ & $(\tau^{alt}, \overline{\mu})$ \\ 
   \hline
-  $\tuple{\tau^{reg}, \Delta(A)}$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
-  $\tuple{\tau^{\pi}, \Delta(A)}$ & 6.486 & 6.484 & 6.088 & 6.703 & 6.486 & 6.486 & 6.088 & 6.875 \\
-  $\tuple{\tau^{com}, \Delta(A)}$ & 6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\
-  $\tuple{\tau^{alt}, \Delta(A)}$ & 5.949 & 5.722 & 5.326 & 6.396 & 5.949 & 5.949 & 5.326 & 6.568 \\
-  $\tuple{\tau^{reg}, \overline{\mu}}$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
-  $\tuple{\tau^{\pi}, \overline{\mu}}$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
-  $\tuple{\tau^{com}, \overline{\mu}}$ & 6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\
-  $\tuple{\tau^{alt}, \overline{\mu}}$ & 6.331 & 5.893 & 5.497 & 6.566 & 6.331 & 6.331 & 5.497 & 7.152 \\
+  $(\tau^{reg}, \Delta)$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
+  $(\tau^{\pi}, \Delta)$ & 6.486 & 6.484 & 6.088 & 6.703 & 6.486 & 6.486 & 6.088 & 6.875 \\
+  $(\tau^{com}, \Delta)$ & 6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\
+  $(\tau^{alt}, \Delta)$ & 5.949 & 5.722 & 5.326 & 6.396 & 5.949 & 5.949 & 5.326 & 6.568 \\
+  $(\tau^{reg}, \overline{\mu})$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
+  $(\tau^{\pi}, \overline{\mu})$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
+  $(\tau^{com}, \overline{\mu})$ & 6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\
+  $(\tau^{alt}, \overline{\mu})$ & 6.331 & 5.893 & 5.497 & 6.566 & 6.331 & 6.331 & 5.497 & 7.152 \\
    \hline                          
@@
 \caption{Average payoff in simulations of 100,000
-  randomly generated $2 \times 2$ symmetric games.}
+  randomly generated $2 \times 2$ symmetric games}
 \label{tab:ExpectedFitness_2x2_Full}        
@@
 types, but competitive types themselves are worse off against all opponent types except against
-maximin players $\tuple{\tau^{\pi}, \Delta(A)}$ than any of the behaviorally equivalent types
-$(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
-$(\tau^{reg}, \overline{\mu})$.  This is a noteworthy results in the light of the fact that
+maxmin players $(\tau^{\pi}, \Delta)$ than any of the behaviorally equivalent types
+$(\tau^{reg}, \Delta)$, $(\tau^{\pi}, \overline{\mu})$, and
+$(\tau^{reg}, \overline{\mu})$. 
+\iffalse
+This is a noteworthy results in the light of the fact that
 evolving altruistic preferences have been shown to support cooperative behavior in a single
-stage game \myalert{[CITE]}. \todo{@Paolo: check whether this is true, please!} In contrast,
+stage game \myalert{[CITE]}. In contrast,
 averaging over payoffs in multiple stage games, like we do here, makes altruistic preferences
 prime victims of evolutionary eradication.
-
+\fi
 It is easy to see then that the previous result still obtains for the larger meta-game in
-Table~\ref{tab:ExpectedFitness_2x2_Full}: $(\tau^{reg}, \Delta(A_{-i}))$,
+Table~\ref{tab:ExpectedFitness_2x2_Full}: $(\tau^{reg}, \Delta)$,
 $(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$ are still neutrally stable;
 all simulations of the (discrete-time) replicator dynamic on the $8 \times 8$ meta-game from
-Table~\ref{tab:ExpectedFitness_2x2_Full} end up in populations consisting of only these types
+Table~\ref{tab:ExpectedFitness_2x2_Full} end up in populations consisting of only these players
 in arbitrary proportion.
+
+\iffalse
 
@@
 
-Fix $\Lambda = \lbrace (\tau^{\pi}, \Delta(A_{-i})), (\tau^{reg}, \Delta(A_{-i})), (\tau^{alt}, \Delta(A_{-i})), (\tau^{com}, \Delta(A_{-i})) \rbrace$ and $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex, set of i.i.d.
+Fix $\Lambda = \lbrace (\tau^{\pi}, \Delta), (\tau^{reg}, \Delta), (\tau^{alt}, \Delta), (\tau^{com}, \Delta) \rbrace$ and $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex, set of i.i.d.
 values.
-Then, $(\tau^{reg}, \Delta(A_{-i}))$ is the only evolutionarily stable player in the population.
+Then, $(\tau^{reg}, \Delta)$ is the only evolutionarily stable player in the population.
 
@@
 
+\fi
+
 In sum, the presence of other plausible preference types, such as competitive and altruistic
@@
 
-\subsection{$n \times n$ symmetric games}
+\subsection{More actions: $n \times n$ symmetric games}
 \label{sec:n-times-n}
@@
 Fact~\ref{fact:equivalence2x2} that, for the special case of $2 \times 2$ symmetric games,
-regret minimization $\tuple{\tau^{reg}, \Delta(A)}$ is behaviorally equivalent with expected
-regret minimization $\tuple{\tau^{reg}, \overline{\mu}}$ and expected utility maximization
-$\tuple{\tau^{\pi}, \overline{\mu}}$. This is no longer true when we look at arbitrary $n \times n$
+regret minimization $(\tau^{reg}, \Delta)$ is behaviorally equivalent with expected
+regret minimization $(\tau^{reg}, \overline{\mu})$ and expected utility maximization
+$(\tau^{\pi}, \overline{\mu})$. This is no longer true when we look at arbitrary $n \times n$
 games with $n \ge 2$. We should therefore see what happens in a broader class of games.
 
-Table~\ref{tab:ExpectedFitness_10x10} therefore gives approximations for expected fitness in a
+Table~\ref{tab:ExpectedFitness_10x10} gives approximations for expected fitness in a
 meta-game over a class of $n \times n$ symmetric games where $n$ is randomly drawn from
@@
   \toprule
- & $\tuple{\tau^{reg}, \Delta(A)}$ 
- & $\tuple{\tau^{\pi}, \Delta(A)}$ 
- & $\tuple{\tau^{com}, \Delta(A)}$
- & $\tuple{\tau^{alt}, \Delta(A)}$
- & $\tuple{\tau^{reg}, \overline{\mu}}$ 
- & $\tuple{\tau^{\pi}, \overline{\mu}}$ 
- & $\tuple{\tau^{com}, \overline{\mu}}$
- & $\tuple{\tau^{alt}, \overline{\mu}}$ \\ 
+ & $(\tau^{reg}, \Delta)$ 
+ & $(\tau^{\pi}, \Delta)$ 
+ & $(\tau^{com}, \Delta)$
+ & $(\tau^{alt}, \Delta)$
+ & $(\tau^{reg}, \overline{\mu})$ 
+ & $(\tau^{\pi}, \overline{\mu})$ 
+ & $(\tau^{com}, \overline{\mu})$
+ & $(\tau^{alt}, \overline{\mu})$ \\ 
   \midrule
-  $\tuple{\tau^{reg}, \Delta(A)}$ & 6.567 & 6.570 & 5.650 & 6.992 & 6.564 & 6.564 & 5.593 & 7.409 \\
-  $\tuple{\tau^{\pi}, \Delta(A)}$ & 6.476 & 6.483 & 5.896 & 6.818 & 6.484 & 6.484 & 5.850 & 7.124 \\
-  $\tuple{\tau^{com}, \Delta(A)}$ & 6.468 & 6.647 & 5.512 & 7.169 & 6.578 & 6.578 & 5.577 & 7.354 \\
-  $\tuple{\tau^{alt}, \Delta(A)}$ & 5.968 & 5.923 & 5.363 & 6.685 & 5.975 & 5.975 & 5.086 & 6.973 \\
-  $\tuple{\tau^{reg}, \overline{\mu}}$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
-  $\tuple{\tau^{\pi}, \overline{\mu}}$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
-  $\tuple{\tau^{com}, \overline{\mu}}$ & 6.529 & 6.680 & 5.445 & 7.276 & 6.542 & 6.542 & 5.521 & 7.440 \\
-  $\tuple{\tau^{alt}, \overline{\mu}}$ & 6.450 & 6.337 & 5.772 & 6.978 & 6.457 & 6.457 & 5.479 & 7.500 \\
+  $(\tau^{reg}, \Delta)$ & 6.567 & 6.570 & 5.650 & 6.992 & 6.564 & 6.564 & 5.593 & 7.409 \\
+  $(\tau^{\pi}, \Delta)$ & 6.476 & 6.483 & 5.896 & 6.818 & 6.484 & 6.484 & 5.850 & 7.124 \\
+  $(\tau^{com}, \Delta)$ & 6.468 & 6.647 & 5.512 & 7.169 & 6.578 & 6.578 & 5.577 & 7.354 \\
+  $(\tau^{alt}, \Delta)$ & 5.968 & 5.923 & 5.363 & 6.685 & 5.975 & 5.975 & 5.086 & 6.973 \\
+  $(\tau^{reg}, \overline{\mu})$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
+  $(\tau^{\pi}, \overline{\mu})$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
+  $(\tau^{com}, \overline{\mu})$ & 6.529 & 6.680 & 5.445 & 7.276 & 6.542 & 6.542 & 5.521 & 7.440 \\
+  $(\tau^{alt}, \overline{\mu})$ & 6.450 & 6.337 & 5.772 & 6.978 & 6.457 & 6.457 & 5.479 & 7.500 \\
    \bottomrule                         
@@
 Table~\ref{tab:ExpectedFitness_2x2_Full}. But increases in approximate expected fitness are not
-uniform. Most importantly, the regret minimizing type $\tuple{\tau^{reg}, \Delta(A)}$ is
-strictly dominated by $\tuple{\tau^{reg}, \overline{\mu}}$ and by $\tuple{\tau^{\pi}, \overline{\mu}}$ in
+uniform. Most importantly, the regret minimizing type $(\tau^{reg}, \Delta)$ is
+strictly dominated by $(\tau^{reg}, \overline{\mu})$ and by $(\tau^{\pi}, \overline{\mu})$ in
 the meta-game from Table~\ref{tab:ExpectedFitness_10x10}. This means that while regret
@@
 Still, although this may be bad news for regret minimizing types
-$\tuple{\tau^{reg}, \Delta(A)}$, it is not the case that regret types \emph{as such} are weeded
-out by selection. Since, by Fact~\ref{fact:maxEU-minReg}, $\tuple{\tau^{reg}, \overline{\mu}}$ and
-$\tuple{\tau^{\pi}, \overline{\mu}}$ are generally behaviorally equivalent, it remains that
+$(\tau^{reg}, \Delta)$, it is not the case that regret types \emph{as such} are weeded
+out by selection. Since, by Fact~\ref{fact:maxEU-minReg}, $(\tau^{reg}, \overline{\mu})$ and
+$(\tau^{\pi}, \overline{\mu})$ are generally behaviorally equivalent, it remains that
 selection based on meta-games constructed from $n \times n$ games will still not eradicate all
@@
 preference \emph{can} again drive out veridical preferences altogether. For concreteness,
-suppose that only preference types compete and that agents' epistemic types are exogenously
+suppose that only preference types compete and that agents' belief types are exogenously
 given, in such a way that agents hold flat probabilistic beliefs $\overline{\mu}$ with probability
-$1-p$ and are of type $\Delta(A)$ with probability $p$. This transforms the meta-game from
+$1-p$ and are of type $\Delta$ with probability $p$. This transforms the meta-game from
 Table~\ref{tab:ExpectedFitness_10x10} into the simpler $4 \times 4$ game in which the payoff
@@
 payoff advantage if paired with radical uncertainty. If radical uncertainty is exogenously
-given as something unavoidable that happens to agents (e.g., whenever they really have no
-indication as to what the situation holds for them), and even if that happens only very
-infrequently (i.e., for rather low $p$), regret types \emph{can} outperform veridical
+given as something unavoidable that happens to agents (e.g., in situation where they really have no
+way of narrowing down the probability set), and even if that happens only very
+infrequently (i.e., for rather low $p$), regret types \emph{will} outperform veridical
 preference types, as well as competitive and altruistic types.
@@
 
-To see how preference types behave in evolutionary competition based on solitary decision
+To see how different choice mechanisms behave in evolutionary competition based on solitary decision
 problems, we approximated, much in the spirit of meta-games, average accumulated payoffs
 obtained in randomly generated solitary decision problems. For our purposes, a decision problem
-$\tuple{\States, \Acts, \Utils}$ consists of a set of world states $\States$, a set of acts
-$\Acts$, and a utility function $\Utils \mycolon \States \times \Acts \rightarrow
+$\tuple{S, \Acts, u}$ consists of a set of world states $S$, a set of acts
+$\Acts$, and a utility function $u \mycolon S \times \Acts \rightarrow
 \mathbb{R}$.
 We generated arbitrary decision problems by selecting numbers of states and acts
-$n_\state, n_\act \in \set{2, \dots, 10}$ and then filling the utility table, so to speak, by
-independently picking a number $\Utils(\state, \act) \in \set{0, 10}$ uniformly at random, just
+$n_s, n_\act \in \set{2, \dots, 10}$ and then filling the utility table, so to speak, by
+independently picking a number $u(s, \act) \in \set{0, 10}$ uniformly at random, just
 as we did before with symmetric games. Unlike with two-player games, we need to also sample the
@@
 the current decision problem. Player types, consisting of epistemic types $\overline{\mu}$ and
-$\Delta(\States)$ and preference types $\tau^{reg}$ and $\tau^{\pi}$, give rise to behavior in
-the same way as before. (It is obviously not possible to carry altruistic or competitive
+$\Delta$ and preference types $\tau^{reg}$ and $\tau^{\pi}$, give rise to behavior in
+the same way as before.\footnote{Obviously, now with $ \Delta \equiv \Delta(S) :=\lbrace \mu \in \mathbb{R}^{S}: \sum_{s \in S} \mu(s) = 1 \rbrace$.} (It is obviously not possible to carry altruistic or competitive
 preference types over to solitary decision making.) As before, we recorded the behavioral
@@
     \toprule
-   $\tuple{\tau^{reg}, \Delta(A)}$ 
- & $\tuple{\tau^{\pi}, \Delta(A)}$ 
- & $\tuple{\tau^{reg}, \overline{\mu}}$ 
- & $\tuple{\tau^{\pi}, \overline{\mu}}$ 
+   $(\tau^{reg}, \Delta)$ 
+ & $(\tau^{\pi}, \Delta)$ 
+ & $(\tau^{reg}, \overline{\mu})$ 
+ & $(\tau^{\pi}, \overline{\mu})$ 
  \\ \midrule
@@
 Facts~\ref{fact:maxEU-minReg} and \ref{fact:equivalence2x2} still apply:
-$\tuple{\tau^{reg}, \overline{\mu}}$ and $\tuple{\tau^{\pi}, \overline{\mu}}$ are behaviorally equivalent
-in general, and $\tuple{\tau^{reg}, \Delta(A)}$ is behaviorally equivalent to the former two in
+$(\tau^{reg}, \overline{\mu})$ and $(\tau^{\pi}, \overline{\mu})$ are behaviorally equivalent
+in general, and $(\tau^{reg}, \Delta)$ is behaviorally equivalent to the former two in
 decision problems with 2 states and 2 acts. \todo{show this?} We see this in part in the
-results in Table~\ref{tab:SolitaryDecisions} in that the averages for $\tuple{\tau^{reg},
-  \overline{\mu}}$ and $\tuple{\tau^{\pi}, \overline{\mu}}$ are identical. But since we included decision
+results in Table~\ref{tab:SolitaryDecisions} in that the averages for $(\tau^{reg},
+  \overline{\mu})$ and $(\tau^{\pi}, \overline{\mu})$ are identical. But since we included decision
 problems with more acts and more states as well, the averages for regret minimizers
-$\tuple{\tau^{reg}, \Delta(A)}$ are not identical. They are, in fact, lower, but not as low as
+$(\tau^{reg}, \Delta)$ are not identical to the one of $(\tau^{reg},
+  \overline{\mu})$ and $(\tau^{\pi}, \overline{\mu})$. They are, in fact, lower, but not as low as
 those of the minimax choosers.
 
-What that means is that basically every relevant result about game situations is also borne out
+What that means is that basically every relevant result we have seen about game situations is also borne out
 when reasoning about solitary decisions. Evolutionary selection based on objective fitness will
@@
 
+\iffalse
 \subsection{Arbitrary probabilistic beliefs}
@@
 probabilistic beliefs to make use of the full spectrum of probabilistic beliefs. It should be
-clear that quality of beliefs directly impacts prospects of successful decision-making: if a
+clear that quality of beliefs directly impacts prospects of successful decision making: if a
 decision maker knows the actual state, or can put a high level of credence on the actual state,
@@
 regret-based preferences can actually be selected, despite their non-veridicality.
-
-\section{Discussion}
-
-\begin{itemize}
-\item what we achieved
-\item what could be done next
-\end{itemize}
+\fi
+
+\section{Conclusion} \label{sec:conclusion}
+
+The assumption that players and decision makers maximize their (subjective) preferences is central through all economic literature, and the maximization of actual (objective) payoffs is often justified by appealing to evolutionary arguments and natural
+selection. In contrast to the standard view, we showed the
+existence of player types with subjective utilities different
+from the actual payoffs that can outperform types whose
+subjective utilities coincide with the actual payoffs.
+While the literature on evolution of preference has focused
+on fixed games, or fixed types of games, we have adopted a
+more general approach here. We suggested that attention
+to “meta-games” is crucial, because what may be a good
+subjective representation in one type of game (e.g., cooperative preferences in the Prisoner’s Dilemma class) need not
+be generally beneficial. Taken together, we presented a variety of plausible circumstances in which evolutionary competition between choice
+mechanisms on a larger class of games can favor subjective
+preference representations focusing on regret.
+
+Finally, we hope to help the research direction towards a broader perspective on evolutionary game theory, as outlined by recent works in theoretical biology \citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be}.
+In partcular, the meta-game approach allows the researcher to both explicitly model the relevant features of the environment and shift the target of evolution from plain behavior to more general behavioral patterns, or choice mechanisms.
+Several uses and improvements of the present model are still possible in many respects.
+We can sketch some of them here.
+For example, the evolutionary investigation of different risk and ambiguity attitudes when competing against each other in an evolutionarily richer environment may bring new insights on both behavioral and theoretic decision making under uncertainty, as well as on many issues in theoretical biology and behavioral ecology.
 
@@
 
-The proof of Proposition 1 relies on a partition of $\mathcal{G}$,
+The proof of Proposition \ref{proposition1} relies on a partition of $\mathcal{G}$,
 and on some lemmas. For brevity, let us denote the regret minimizer
-by RM and the maximinimizer by MM. Since the proof is very long and
-all the other cases are similar and easier to prove, we focus here
-on the case of RM against MM players: we prove that RM is evolutionarily
-stable against MM, but MM is not evolutionarily stable against RM. By $EU_{\mathcal{G}}(x,y)$ we denote the expected \textit{objective} utility (or payoff), in terms
-of evolutionary fitness, of player type $x$ against player type $y$
+by $R$ and the maximinimizer by $M$, i.e, $R \equiv \kappa(\tau^{reg}, \Delta)$ and $M \equiv  \kappa(\tau^{\pi}, \Delta)$.
+Recall from Equation \ref{eq:pairwiseEF} that $EF_{\mathcal{G}}(X,Y)$ denotes the expected evolutionary fitness of choice mechanism $X$ against choice mechanism $Y$
 with respect to the class of fitness games $\mathcal{G}$.
 
-\medskip{}
-
-\textbf{Proof of Proposition 1.} By definition of evolutionary stability, we have to
-show that in the class $\mathcal{G}$ of symmetric $2\times2$ games generated by i.i.d. sampling
-from a finite or compact and convex set of values, it holds:
-\begin{itemize}
-\item[(i)] $EU_{\mathcal{G}}(RM,RM)>EU_{\mathcal{G}}(MM,RM);$
-\item[(ii)] $EU_{\mathcal{G}}(MM,MM)<EU_{\mathcal{G}}(RM,MM).$
-\end{itemize}
-
-\noindent Let us consider the case of sampling from a finite set of values first. To show
+\vspace{.5cm}
+
+\noindent \textbf{Proof of Proposition \ref{proposition1}.} By definition of strict Nash equilibrium, we have to
+show that in the class $\mathcal{G}$ of symmetric $2\times2$ games with payoffs sampled from a set of i.i.d. values with at least 3 elements in the support, it holds:
+\begin{itemize}
+\item[(i)] $EF_{\mathcal{G}}(R,R)>EF_{\mathcal{G}}(M,R);$
+\item[(ii)] $EF_{\mathcal{G}}(M,M)<EF_{\mathcal{G}}(R,M).$
+\end{itemize}
+
+\noindent To show
 the result we will use the following partition of $\mathcal{G}$.
 \begin{enumerate}
-\item Coordination games $\mathcal{G}^{C}$: $a>c$ and $d>b$;
-\item Anti-coordination games $\mathcal{G}^{A}$: $a<c$ and $d<b$;
-\item Strong dominance games $\mathcal{G}^{S}$: aut $(a>c$ and $b>d)$
+\item Coordination games $\mathcal{C}$: $a>c$ and $d>b$;
+\item Anti-coordination games $\mathcal{A}$: $a<c$ and $d<b$;
+\item Strong dominance games $\mathcal{S}$: aut $(a>c$ and $b>d)$
 aut $(a<c$ and $b<d)$;
-\item Weak dominance games $\mathcal{G}^{W}$: aut $a=c$ aut $b=d$;
-\item Indifferent games $\mathcal{G}^{I}$: $a=c$ and $b=d$.
+\item Weak dominance games $\mathcal{W}$: aut $a=c$ aut $b=d$;
+\item Boring games $\mathcal{B}$: $a=c$ and $b=d$.
 \end{enumerate}
-Before proving the lemmas, it is convenient to fix some notation.
-We denote by $G^{C}$ a coordination game in $\mathcal{G}^{C}$ with
-payoffs $a^{G^{C}}$, $b^{G^{C}}$, $c^{G^{C}}$, and $d^{G^{C}}$;
-similarly, for $G^{A}$, $G^{S}$, $G^{W}$, and $G^{I}$. Let us
-call $I_{G^{C}}^{RM}$ the event that a RM player plays action $I$
-in the game $G^{C}$; and similarly for action $II$, for player MM,
-and for games $G^{A}$, $G^{S}$, $G^{W}$ and $G^{I}$. Moreover,
-let us recall the definition of evolutionarily stable strategy and
-neutrally stable strategy.
+Before proving the lemmas, it is convenient to fix some notation. Let us call $x,y,z$ the 3 elements in the support, and without loss of generality suppose that $ x > y > z $. 
+We denote by $C$ a coordination game in $\mathcal{C}$ with
+payoffs $a_{C}$, $b_{C}$, $c_{C}$, and $d_{C}$;
+similarly for games $A \in \mathcal{A}$, $S \in \mathcal{S}$, $W \in \mathcal{W}$, and $B \in \mathcal{B}$. 
+Let us denote by $I_{RC}$ the event that a $R$-player plays action $I$ in the game $C$; and similarly for action $II$, for player $M$, and for games $A$, $S$, $W$ and $B$.
+We first consider the case of i.i.d.
+sampling with finite support.
 
@@
 
-\begin{definition}[ESS-NSS]
+\begin{lemma} \label{lemma:S-B games}
+$R$ and $M$ perform equally well in $\mathcal{S}$
+and in $\mathcal{B}$. 
+\end{lemma}
+
+\begin{proof}
+By definition of regret minimization and maxmin it
+is easy to check that whenever in a game there is a strongly dominant
+action $a^{\$}$, then $a^{\$}$ is both the maxmin action and the
+regret minimizing action. Then, for all the games in $\mathcal{S}$,
+$R$ chooses action $a$ if and only if $M$ chooses action $a$. Consequently,
+$R$ and $M$ always perform equally (well) in $\mathcal{S}$. In
+the case of $\mathcal{B}$ it is trivial to see that all the players
+perform equally.
+\end{proof}
+
+\medskip{}
+
+\begin{lemma} \label{lemma:W games}
+In $\mathcal{W}$, $(R,R)$ is the only (strict) Nash equilibrium.
+\end{lemma}
+
+\begin{proof}
+Assume without loss of generality that $b=d$. There are two situations that we have to check: (i) $b=d \geq a,c$ and $ a \neq c $; (ii) $b=d \leq a,c$ and $ a \neq c $.
+In the first case it
+is easy to see that $R$ and $M$ perform equally well. Indeed, given
+(i), both $R$ and $M$ choose action $I$ if $a>c$, and action $II$
+if $c>a$. If case (ii) holds instead, we have that $R$ plays $I$
+if $a>c$ and $II$ if $c>a$ as before, but $M$ plays $(\frac{1}{2}I;\frac{1}{2}II)$,
+since both $I$ and $II$ maximize the minimal payoff. Consider now
+a population of $R$ and $M$ playing games from the class $\mathcal{W}$.
+Whenever (i) is the case both $R$ and $M$ perform equally. Suppose that
+(ii) is the case and that $a>c$, without loss of generality.
+Then,  $EF(R,R)=a>\frac{1}{2}a+\frac{1}{2}c=EF(M,R)$, whereas $EF(M,M)=\frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d<\frac{1}{2}a+\frac{1}{2}b=EF(R,M)$.
+Hence, we have that in general $EF_{\mathcal{W}}(R,R)>EF_{\mathcal{W}}(M,R),\mbox{ and }EF_{\mathcal{W}}(M,M)<EF_{\mathcal{W}}(R,M)$.
+\end{proof}
+
+\medskip{}
+
+Since it is not difficult to see that both $(R,R)$ and $(M,M)$ are strict Nash equilibria in $\mathcal{C}$, and that $(R,R)$ and $(M,M)$ are not Nash equilibria in $\mathcal{A}$, the main part of
+the proof will be to show that $(R,R)$ is the only (strict) Nash equilibrium in the class $\mathcal{C}\cup\mathcal{A}$, that is:
+\begin{itemize}
+\item[(i')] $EF_{\mathcal{C}\cup\mathcal{A}}(R,R)>EF_{\mathcal{C}\cup\mathcal{A}}(M,R),$
+\item[(ii')] $EF_{\mathcal{C}\cup\mathcal{A}}(M,M)<EF_{\mathcal{C}\cup\mathcal{A}}(R,M).$
+\end{itemize}
+
+\noindent This part needs some more lemmas to be proven, but firstly we introduce
+the following bijective function $\phi$ between coordination and
+anti-coordination games.
+
+\medskip{}
+
+\begin{definition}[$\phi$] \label{def:bijection phi}
+The permutation $\phi(a,b,c,d)=(c,d,a,b)$ defines a bijective function $\phi:\mathcal{C}\rightarrow\mathcal{A}$ that for each
+coordination game $C\in\mathcal{C}$ with payoffs $(a_{C},b_{C},c_{C},d_{C})$
+gives the anti-coordination game $A\in\mathcal{A}$ with payoffs
+$(a_{A},b_{A},c_{A},d_{A})=(c_{C},d_{C},a_{C},b_{C})$.
+\end{definition}
+
+\medskip{}
+
+\begin{lemma} \label{lemma:probabilities coord-ant}
+$P(\phi(C))=P(C)$.
+\end{lemma}
+
+\begin{proof}
+By definition, each game $C\equiv(a_{C},b_{C},c_{C},d_{C})$
+is such that $a_{C}>c_{C}$ and $d_{C}>b_{C}$, and
+each game $A\equiv(a_{A},b_{A},c_{A},d_{A})$
+is such that $a_{A}<c_{A}$ and $d_{A}>b_{A}$. Given that
+$a,b,c,d$ are i.i.d. random variables and that a sequence of i.i.d. random variables is exchangeable,
+it is clear that the probability of $(a_{C},b_{C},c_{C},d_{C})$ equals the probability of $(c_{C},d_{C},a_{C},b_{C})$.
+Hence, $P(\phi(C))=P(C)$.
+\end{proof}
+
+\medskip{}
+
+\begin{lemma} \label{lemma:probabilities actions coord-ant}
+Let $P(E)$ be the probability of event $E$, then
+it holds that:
+\begin{itemize}
+\item $P(I_{RC})=P(II_{R\phi(C)})$, and $P(II_{RC})=P(I_{R\phi(C)})$;
+\item $P(I_{MC})=P(II_{M\phi(C)})$, and $P(II_{MC})=P(I_{M\phi(C)})$.
+\end{itemize}
+\end{lemma}
+
+\begin{proof}
+It is easy to check that if $b_{C}-d_{C}>c_{C}-a_{C}$,
+a $R$-player plays action $I$ in $C$; that if $b_{C}-d_{C}<c_{C}-a_{C}$,
+$R$ plays $II$; and that if $b_{C}-d_{C}=c_{C}-a_{C}$,
+a $R$-player is indifferent between $I$ and $II$ in $C$, and
+we assume that randomizes with $(\frac{1}{2}I;\frac{1}{2}II)$. Similarly,
+if $a_{A}-c_{A}>d_{A}-b_{A}$, a $R$-player plays action
+$I$ in $A$; if $a_{A}-c_{A}<d_{A}-b_{A}$, $R$
+plays $II$; and if $a_{A}-c_{A}=d_{A}-b_{A}$, a
+$R$-player is indifferent between $I$ and $II$ in $A$, and randomizes
+with $(\frac{1}{2}I;\frac{1}{2}II)$. Consequently, if $b_{C}-d_{C}>c_{C}-a_{C}$,
+then $P(I_{RC})=1$, and by definition of $\phi$ we have
+$P(II_{R\phi(C)})=1$. Likewise, if $b_{C}-d_{C}<c_{C}-a_{C}$,
+then $P(II_{RC})=1=P(I_{R\phi(C)})$; and if $b_{C}-d_{C}=c_{C}-a_{C}$,
+then $P(I_{RC})=P(II_{RC})=\frac{1}{2}=P(II_{R\phi(C)})=P(I_{R\phi(C)})$. \\
+In the same way, in coordination games we have that if $b_{C}>c_{C}$,
+a $M$-player plays $I$; if $c_{C}>b_{C}$, a $M$-player plays
+$II$; and if $b_{C}=c_{C}$, $M$ is indifferent between $I$
+and $II$, and plays $(\frac{1}{2}I;\frac{1}{2}II)$. In anti-coordination
+games instead, if $a_{A}>d_{A}$, $M$ plays $I$; if $a_{A}<d_{A}$,
+$M$ plays $II$; if $a_{A}=d_{A}$, $M$ plays $(\frac{1}{2}I;\frac{1}{2}II)$.
+By definition of $\phi$: $P(I_{MC})=1=P(II_{M\phi(C)})$
+if $b_{C}>c_{C}$; $P(II_{MC})=1=P(I_{M\phi(C)})$
+if $c_{C}>b_{C}$; and $P(I_{MC})=P(II_{MC})=\frac{1}{2}=P(II_{M\phi(C)})=P(I_{M\phi(C)})$
+if $b_{C}=c_{C}$.
+\end{proof}
+
+\medskip{}
+
+\begin{lemma} \label{lemma:action implications}
+It holds that:
+\begin{itemize}
+\item $a_{C}>d_{C}\rightarrow(I_{MC}\subset I_{RC})$;
+\item $a_{C}<d_{C}\rightarrow(II_{MC}\subset II_{RC})$;
+\item $a^{C}=d^{C}\rightarrow I_{MC}=I_{RC}$.
+\end{itemize}
+\end{lemma}
+
+\begin{proof}
+If $b_{C}-d_{C}>c_{C}-a_{C}$, $R$ plays
+$I$, and if $b_{C}-d_{C}=c_{C}-a_{C}$, $R$ plays
+$(\frac{1}{2}I;\frac{1}{2}II)$, whereas if $b_{C}>c_{C}$,
+$M$ plays $I$, and if $b_{C}=c_{C}$, $M$ plays $(\frac{1}{2}I;\frac{1}{2}II)$.
+Then, $I_{RC}$ implies that $b_{C}-d_{C}\geq c_{C}-a_{C}$,
+and $I_{MC}$ implies that $b_{C}\geq c_{C}$. Moreover,
+on the assumption that $a_{C}>d_{C}$, it is easy to check
+that $b_{C}\geq c_{C}$ implies $b_{C}-d_{C}>c_{C}-a_{C}$.
+Hence, in any $C$ with $a_{C}>d_{C}$ it holds that $I_{MC}\mbox{ implies }I_{RC}$,
+i.e., $a_{C}>d_{C}\rightarrow(I_{MC}\subseteq I_{RC})$.
+Instead, it is possible that $a_{C}>d_{C}$, $b_{C}-d_{C}>c_{C}-a_{C}$
+and $b_{C}<c_{C}$ hold simultaneously, so that $I_{MC}\nsupseteq I_{RC}$.
+Consequently: $a_{C}>d_{C}\rightarrow(I_{MC}\subset I_{RC})$.
+By symmetric argument it can be shown that $a_{C}<d_{C}\rightarrow(II_{MC}\subset II_{RC})$
+too. \\
+Finally, when $a_{C}=d_{C}$ it holds that: $b_{C}-d_{C}>c_{C}-a_{C}$
+iff $b_{C}>c_{C}$; $b_{C}-d_{C}<c_{C}-a_{C}$
+iff $b_{C}<c_{C}$; and $b_{C}-d_{C}=c_{C}-a_{C}$
+iff $b_{C}=c_{C}$. Hence, $a_{C}=d_{C}\rightarrow I_{MC}=I_{RC}$.
+\end{proof}
+
+\medskip{}
+
+\noindent We are now ready to prove that:
+\begin{itemize}
+\item[(i')] $EF_{\mathcal{C}\cup\mathcal{A}}(R,R)>EF_{\mathcal{C}\cup\mathcal{A}}(M,R);$
+\item[(ii')] $EF_{\mathcal{C}\cup\mathcal{A}}(M,M)<EF_{\mathcal{C}\cup\mathcal{A}}(R,M).$
+\end{itemize}
+We can rewrite $EF_{\mathcal{C}\cup\mathcal{A}}(R,R)>EF_{\mathcal{C}\cup\mathcal{A}}(M,R)$
+more explicitly as:
+
+\medskip{}
+
+\noindent $\sum_{C \in \mathcal{C}}P(C)[P(I_{RC}\cap I_{RC})\cdot a_{C}+P(II_{RC}\cap II_{RC})\cdot d_{C}+P(I_{RC}\cap II_{RC})\cdot b_{C}+P(II_{RC}\cap I_{RC})\cdot c_{C}]+\sum_{A \in \mathcal{A}}P(A)[P(I_{RA}\cap I_{RA})\cdot a_{A}+P(II_{RA}\cap II_{RA})\cdot d_{A}+P(I_{RA}\cap II_{RA})\cdot b_{A}+P(II_{RA}\cap I_{RA})\cdot c_{A}] > \sum_{C \in \mathcal{C}}P(C)[P(I_{RC}\cap I_{MC})\cdot a_{C}+P(II_{RC}\cap II_{MC})\cdot d_{C}+P(I_{RC}\cap II_{MC})\cdot c_{C}+P(II_{RC}\cap I_{MC})\cdot b_{C}]+\sum_{A \in \mathcal{A}}P(A)[P(I_{RA}\cap I_{MA})\cdot a_{A}+P(II_{RA}\cap II_{MA})\cdot d_{A}+P(I_{RA}\cap II_{MA})\cdot c_{A}+P(II_{RA}\cap I_{MA})\cdot b_{A}]$
+\medskip{}
+
+\noindent Then, the next derivation follows. By Lemma \ref{lemma:probabilities coord-ant} and Lemma \ref{lemma:probabilities actions coord-ant}, we can express
+everything in terms of $C$ only:
+\begin{itemize}
+
+%\item $\sum_{C}P(C)[P(I_{RC}\cap I_{RC})\cdot a_{C}+P(II_{RC}\cap II_{RC})\cdot d_{C}+P(I_{RC}\cap II_{RC})\cdot b_{C}+P(II_{RC}\cap I_{RC})\cdot c_{C}]+\sum_{A}P(A)[P(I_{RA}\cap I_{RA})\cdot a_{A}+P(II_{RA}\cap II_{RA})\cdot d_{A}+P(I_{RA}\cap II_{RA})\cdot b_{A}+P(II_{RA}\cap I_{RA})\cdot c_{A}] > \sum_{C}P(C)[P(I_{RC}\cap I_{MC})\cdot a_{C}+P(II_{RC}\cap II_{MC})\cdot d_{C}+P(I_{RC}\cap II_{MC})\cdot c_{C}+P(II_{RC}\cap I_{MC})\cdot b_{C}]+\sum_{A}P(A)[P(I_{RA}\cap I_{MA})\cdot a_{A}+P(II_{RA}\cap II_{MA})\cdot d_{A}+P(I_{RA}\cap II_{MA})\cdot c_{A}+P(II_{RA}\cap I_{MA})\cdot b_{A}]$
+
+\item $\sum_{C}P(C)[P(I_{RC}\cap I_{RC})\cdot a_{C}+P(II_{RC}\cap II_{RC})\cdot d_{C}+P(I_{RC}\cap II_{RC})\cdot b_{C}+P(II_{RC}\cap I_{RC})\cdot c_{C} +P(II_{RC}\cap II_{RC})\cdot c_{C}+P(I_{RC}\cap I_{RC})\cdot b_{C}+P(II_{RC}\cap I_{RC})\cdot d_{C}+P(I_{RC}\cap II_{RC})\cdot a_{C}] > \sum_{C}P(C)[P(I_{RC}\cap I_{MC})\cdot a_{C}+P(II_{RC}\cap II_{MC})\cdot d_{C}+P(I_{RC}\cap II_{MC})\cdot c_{C}+P(II_{RC}\cap I_{MC})\cdot b_{C}+P(II_{RC}\cap II_{MC})\cdot c_{C}+P(I_{RC}\cap I_{MC})\cdot b_{C}+P(II_{RC}\cap I_{MC})\cdot a_{C}+P(I_{RC}\cap II_{MC})\cdot d_{C}]$
+
+\item $\sum_{C}P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) + P(I_{RC}\cap II_{RC})) + b_{C} \cdot  (P(I_{RC}\cap II_{RC}) + P(I_{RC}\cap I_{RC})) + c_{C} \cdot (P(II_{RC}\cap I_{RC}) +P(II_{RC}\cap II_{RC})) + d_{C} \cdot (P(II_{RC}\cap II_{RC})+P(II_{RC}\cap I_{RC}))]> \sum_{C}P(C)[a_{C} \cdot (P(I_{RC}\cap I_{MC})+P(II_{RC}\cap I_{MC})) + b_{C} \cdot (P(II_{RC}\cap I_{MC})+P(I_{RC}\cap I_{MC})) + c_{C} \cdot (P(I_{RC}\cap II_{MC})+P(II_{RC}\cap II_{MC})) + d_{C} \cdot (P(II_{RC}\cap II_{MC})+P(I_{RC}\cap II_{MC}))]$
+
+\end{itemize}
+
+\noindent Now let us split into $a>d$ and $a<d$, and consider $a>d$ first.
+Notice that, by Lemma \ref{lemma:action implications}, the case $a=d$ is irrelevant in order to
+discriminate between $R$ and $M$. If $a>d$, by Lemma \ref{lemma:action implications} we can eliminate
+the cases where $R$ plays $II$ and $M$ plays $I$:
+
+\begin{itemize}
+
+\item $\sum_{C_{a>d}} P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) + P(I_{RC}\cap II_{RC})) + b_{C} \cdot  (P(I_{RC}\cap II_{RC}) + P(I_{RC}\cap I_{RC})) + c_{C} \cdot (P(II_{RC}\cap I_{RC}) +P(II_{RC}\cap II_{RC})) + d_{C} \cdot (P(II_{RC}\cap II_{RC})+P(II_{RC}\cap I_{RC}))]>
+\sum_{C_{a>d}} P(C)[a_{C} \cdot P(I_{RC}\cap I_{MC}) + b_{C} \cdot P(I_{RC}\cap I_{MC}) + c_{C} \cdot (P(I_{RC}\cap II_{MC})+P(II_{RC}\cap II_{MC})) + d_{C} \cdot (P(II_{RC}\cap II_{MC})+P(I_{RC}\cap II_{MC}))]$
+
+\item $\sum_{C_{a>d}} P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) + P(I_{RC}\cap II_{RC})- P(I_{RC}\cap I_{MC})) + b_{C} \cdot  (P(I_{RC}\cap II_{RC}) + P(I_{RC}\cap I_{RC})- P(I_{RC}\cap I_{MC})) + c_{C} \cdot (P(II_{RC}\cap I_{RC}) +P(II_{RC}\cap II_{RC})- P(I_{RC}\cap II_{MC})- P(II_{RC}\cap II_{MC})) + d_{C} \cdot (P(II_{RC}\cap II_{RC})+P(II_{RC}\cap I_{RC})- P(II_{RC}\cap II_{MC})- P(I_{RC}\cap II_{MC}))]> 0$
+
+\end{itemize}
+
+\noindent We now distinguish between two cases: (1) $ a-c = d-b $ and (2) $  a-c \neq d-b $.
+Notice that $P(I_{RC}\cap II_{RC}) \neq 0$ if and only if case (1) obtains, and that $a>d$ and (1) imply $II_{MC}$.
+Then, from (1) we have\footnote{Note that when we have only 3 elements in the support it is not guaranteed that case (1), together with $a>d$, may arise in a coordination game, whereas it is guaranteed that case (2), together with $a>d$, occurs with some positive probability.
+If we take for instance $x= 5, y= 2, z= 1$, then case (1) cannot obtain, whereas if we take $x= 3, y= 2, z= 1$, both (1) and (2) may obtain ($a=3, b=1, c=2, d=2$ for case (1), and $a=3, b=1, c=2, d=2$ for case (2).
+Moreover, under the assumption that $a>d$, having 3 elements in the support is a necessary and sufficient condition for case (2) to have positive occurrence in a coordination game.
+As it will be clear in the following, a positive occurrence of case (2) only is enough for the theorem to hold.}:
+
+\begin{itemize}
+
+\item $\sum_{C_{a>d}} P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) + P(I_{RC}\cap II_{RC})) + b_{C} \cdot  (P(I_{RC}\cap II_{RC}) + P(I_{RC}\cap I_{RC})) + c_{C} \cdot (P(II_{RC}\cap I_{RC}) +P(II_{RC}\cap II_{RC})- P(I_{RC}\cap II_{MC})- P(II_{RC}\cap II_{MC})) + d_{C} \cdot (P(II_{RC}\cap II_{RC})+P(II_{RC}\cap I_{RC})- P(II_{RC}\cap II_{MC})- P(I_{RC}\cap II_{MC}))]> 0$
+
+\item $\sum_{C_{a>d}} P(C)[a_{C} \cdot (\frac{1}{4}+\frac{1}{4}) + b_{C} \cdot  (\frac{1}{4}+\frac{1}{4}) + c_{C} \cdot (\frac{1}{4}+\frac{1}{4}-\frac{1}{2}-\frac{1}{2}) + d_{C} \cdot (\frac{1}{4}+\frac{1}{4}-\frac{1}{2}-\frac{1}{2})]> 0$
+
+\item $\sum_{C_{a>d}} P(C)[\frac{1}{2}a_{C}+ \frac{1}{2}b_{C} - \frac{1}{2}c_{C} - \frac{1}{2}d_{C}]> 0$
+
+\end{itemize}
+
+\noindent Since we have assumed $ a-c = d-b $, the last inequality is not satisfied. We have instead:
+
+$$ \sum_{C_{a>d}} P(C)[\frac{1}{2}a_{C}+ \frac{1}{2}b_{C} - \frac{1}{2}c_{C} - \frac{1}{2}d_{C}]= 0 $$
+
+\noindent This means that, when (1) is the case, $(R,R)$ is not a strict Nash equilibrium. To prove that $(R,R)$ is strict we then have to show that the inequality is strict when case (2) obtains. \\
+When (2) is the case, it is easy to check, by Lemma \ref{lemma:action implications}, that $P(I_{RC} \cap I_{RC})-P(I_{RC}\cap I_{MC})=P(I_{RC}\cap II_{MC})$
+and $P(II_{RC}\cap II_{MC})=P(II_{RC} \cap II_{RC})$.
+Consequently, we have:
+
+\begin{itemize}
+
+\item $\sum_{C_{a>d}} P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) - P(I_{RC}\cap I_{MC})) + b_{C} \cdot  (P(I_{RC}\cap I_{RC})- P(I_{RC}\cap I_{MC})) + c_{C} \cdot (P(II_{RC}\cap II_{RC})- P(I_{RC}\cap II_{MC})- P(II_{RC}\cap II_{MC})) + d_{C} \cdot (P(II_{RC}\cap II_{RC})- P(II_{RC}\cap II_{MC})- P(I_{RC}\cap II_{MC}))]> 0$
+
+\item $\sum_{C_{a>d}} P(C)[a_{C} \cdot P(I_{RC}\cap II_{MC}) + b_{C} \cdot  P(I_{RC}\cap II_{MC}) - c_{C} \cdot P(I_{RC}\cap II_{MC}) - d_{C} \cdot P(I_{RC}\cap II_{MC})]> 0$
+
+\item $\sum_{C_{a>d}} P(C)[P(I_{RC}\cap II_{MC})\cdot (a_{C} + b_{C} - c_{C} - d_{C})]> 0$
+
+\end{itemize}
+\medskip{}
+
+\noindent We know that $I_{RC}$ implies that $a_{C}-c_{C}\geq d_{C}-b_{C}$.
+%and $II_{MC}$ implies that $b_{C}\leq c_{C}$. 
+Since we have assumed that $a_{C}-c_{C}\neq d_{C}-b_{C}$, we have that $a_{C}-c_{C} > d_{C}-b_{C}$. Hence, the inequality 
+$$\sum_{C_{a>d}} P(C)[P(I_{RC}\cap II_{MC})\cdot (a_{C} + b_{C} - c_{C} - d_{C})]> 0$$
+is satisfied. So, when (2) obtains, $(R,R)$ is a strict Nash equilibrium.
+%From $b_{C}-d_{C}\geq c_{C}-a_{C}$, it is easy to see that $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{RC}\cap II_{MC})\cdot[a_{C}-c_{C}]\geq\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{RC}\cap II_{MC})\cdot[d_{C}-b_{C}]$ holds.
+When the event $I_{RC}\cap II_{MC}$ obtains on the assumption that $a_{C}>d_{C}$, there are only three possible payoff orderings: $a>c\geq d>b$, $a>d>c>b$, and $a>d>c=b$.
+If games are randomly sampled from a finite set with i.i.d.
+values for $a,b,c$ and $d$, then $a>d>c=b$ occurs with positive probability, and the last formula of the derivation holds with strict inequality too.
+Hence, RM is evolutionarily stable when the value set for $a,b,c,d$ is finite.
+\\
+%If i.i.d.
+values are sampled from a compact and convex set instead, it is again easy to see that $\forall a,d,c\ \exists\epsilon$ such that $\forall b\in(d,d+\epsilon)$ the above formula holds with strict inequality.
+We can simply take $\epsilon\equiv\frac{a-c}{2}$, and the interval $(d,d+\epsilon)$ always has positive probability.
+Hence, RM is evolutionarily stable when the value set for $a,b,c,d$ is a compact and convex set too.
+\\
+Symmetrically, from $a<d$ and by distinguishing between the two cases (1) and (2) as before, in the end  we get:
+
+\begin{itemize}
+
+\item[(1)] $\sum_{C_{a<d}} P(C)[-\frac{1}{2}a_{C}- \frac{1}{2}b_{C} + \frac{1}{2}c_{C} + \frac{1}{2}d_{C}]= 0$; and
+
+\item[(2)] $\sum_{C_{a<d}} P(C)[P(II_{RC}\cap I_{MC})\cdot (-a_{C} - b_{C} + c_{C} + d_{C})]> 0$.
+
+\end{itemize}
+
+\noindent Hence, we can conclude that $(R,R)$ is a strict Nash equilibrium in the class $\mathcal{C}\cup\mathcal{A}$. \\
+In case of i.i.d.
+sampling with infinite support instead, games in $\mathcal{B} $ and $\mathcal{W} $ never arise, and the proof is the same for the remaining games in $\mathcal{S}$,  $\mathcal{C} $ and $\mathcal{A} $.
+
+\medskip{}
+
+The second half of the result is that $(M,M)$ is not a (strict) Nash equilibrium in $\mathcal{C}\cup\mathcal{A}$: $EF_{\mathcal{C}\cup\mathcal{A}}(M,M)<EF_{\mathcal{C}\cup\mathcal{A}}(R,M)$.
+As before, we write it more explicitly as:
+
+\medskip{}
+
+\noindent $\sum_{C}P(C)[P(I_{MC}\cap I_{MC})\cdot a_{C}+P(II_{MC}\cap II_{MC})\cdot d_{C}+P(I_{MC}\cap II_{MC})\cdot b_{C}+P(II_{MC}\cap I_{MC})\cdot c_{C}]+\sum_{A}P(A)[P(I_{MA}\cap I_{MA})\cdot a_{A}+P(II_{MA}\cap II_{MA})\cdot d_{A}+P(I_{MA}\cap II_{MA})\cdot b_{A}+P(II_{MA}\cap I_{MA})\cdot c_{A}] < \sum_{C}P(C)[P(I_{RC}\cap I_{MC})\cdot a_{C}+P(II_{RC}\cap II_{MC})\cdot d_{C}+P(I_{RC}\cap II_{MC})\cdot b_{C}+P(II_{RC}\cap I_{MC})\cdot c_{C}]+\sum_{A}P(A)[P(I_{RA}\cap I_{MA})\cdot a_{A}+P(II_{RA}\cap II_{MA})\cdot d_{A}+P(I_{RA}\cap II_{MA})\cdot b_{A}+P(II_{RA}\cap I_{MA})\cdot c_{A}]$.
+\medskip{}
+
+\noindent When $a>d$, similarly to the above derivation, we get:
+
+\medskip{}
+\noindent $\sum_{C_{a>d}} P(C)[a_{C} \cdot (P(I_{MC}\cap I_{MC}) + P(I_{MC}\cap II_{MC})- P(I_{RC}\cap I_{MC}) - P(I_{RC}\cap II_{MC})) + b_{C} \cdot  (P(I_{MC}\cap I_{MC}) + P(I_{MC}\cap II_{MC})- P(I_{RC}\cap I_{MC}) - P(I_{RC}\cap II_{MC})) + c_{C} \cdot (P(II_{MC}\cap I_{MC}) +P(II_{MC}\cap II_{MC})- P(II_{RC}\cap II_{MC})) + d_{C} \cdot (P(II_{MC}\cap II_{MC})+P(II_{MC}\cap I_{MC})- P(II_{RC}\cap II_{MC}))]< 0$
+\medskip{}
+
+\noindent We now distinguish between (1) $b=c$, (2) $b>c$, and (3) $b<c$.
+Notice that either (1) or (2), together with $a>d$, implies $I_{RC}$.
+Then we obtain\footnote{Note that here, when we only have 3 elements in the support, case (2) is impossible.
+However, we can insure that cases (1) and (3) will eventually obtain.
+Again, this will be enough for the theorem to hold.}:
+\begin{itemize}
+
+\item[(1)] $\sum_{C_{a>d}} P(C)[-\frac{1}{2}a_{C} - \frac{1}{2}b_{C} + \frac{1}{2}c_{C} + \frac{1}{2}d_{C}]< 0$;
+
+\item[(2)] $\sum_{C_{a>d}} P(C)[a_{C} \cdot (P(I_{MC}\cap I_{MC}) - P(I_{RC}\cap I_{MC})) + b_{C} \cdot  (P(I_{MC}\cap I_{MC}) - P(I_{RC}\cap I_{MC}))]= 0$;
+
+\item[(3)] $\sum_{C_{a>d}} P(C)[a_{C} \cdot (- P(I_{RC}\cap II_{MC})) + b_{C} \cdot  (- P(I_{RC}\cap II_{MC})) + c_{C} \cdot (P(II_{MC}\cap II_{MC})- P(II_{RC}\cap II_{MC})) + d_{C} \cdot (P(II_{MC}\cap II_{MC})- P(II_{RC}\cap II_{MC}))] \leq 0$.
+
+\end{itemize}
+
+\noindent When $a<d$, the derivation proceeds symmetrically and we get:
+
+\begin{itemize}
+
+\item[(1)] $\sum_{C_{a<d}} P(C)[\frac{1}{2}a_{C} + \frac{1}{2}b_{C} - \frac{1}{2}c_{C} - \frac{1}{2}d_{C}]< 0$;
+
+\item[(2)] $\sum_{C_{a<d}} P(C)[a_{C} \cdot (P(I_{MC}\cap I_{MC}) - P(I_{RC}\cap I_{MC})) + b_{C} \cdot  (P(I_{MC}\cap I_{MC}) - P(I_{RC}\cap I_{MC})) + c_{C} \cdot (- P(II_{RC}\cap I_{MC})) + d_{C} \cdot (- P(II_{RC}\cap I_{MC}))] \leq 0$
+
+\item[(3)] $\sum_{C_{a<d}} P(C)[c_{C} \cdot (P(II_{MC}\cap II_{MC})- P(II_{RC}\cap II_{MC})) + d_{C} \cdot (P(II_{MC}\cap II_{MC})- P(II_{RC}\cap II_{MC}))] = 0$.
+
+\end{itemize}
+
+\noindent Finally, we can conclude that $(M,M)$ is
+not a (strict) Nash equilibrium, and therefore $(R,R)$ is the unique strict Nash equilibrium. \\
+As before, when we have i.i.d.
+sampling with infinite support, games in $\mathcal{W}$ and $\mathcal{B}$ never occur, and the proof is the same for all the other cases.
+Hence, both when the support of $a,b,c,d$
+is finite, and when the support is infinite, $(R,R)$ is the only (strict) Nash equilibrium. This concludes the proof. $\dashv$
+
+\vspace{1cm}
+
+\noindent \textbf{Proof of Corollary \ref{corollary1}.} Let us recall the definition of evolutionarily stable strategy and neutrally stable strategy.
+
+\medskip{}
+
+\begin{definition}[ESS-NSS] \label{def:ESS-NSS}
 A strategy $s^{\$}$ is \emph{evolutionarily stable
@@
 
-\begin{lemma}
-RM and MM perform equally well in $\mathcal{G}^{S}$
-and in $\mathcal{G}^{I}$. 
-\end{lemma}
-
-\begin{proof}
-By definition of regret minimization and maximin it
-is easy to check that whenever in a game there is a strongly dominant
-action $a^{\$}$, then $a^{\$}$ is both the maximin action and the
-regret minimizing action. Then, for all the games in $\mathcal{G}^{S}$,
-a RM chooses action $a$ if and only if MM chooses action $a$. Consequently,
-RM and MM always perform equally (well) in $\mathcal{G}^{S}$. In
-the case of $\mathcal{G}^{I}$ it is trivial to see that all the players
-perform equally.
-\end{proof}
-
-\medskip{}
-
-\begin{lemma}
-In $\mathcal{G}^{W}$ RM is evolutionarily stable
-against MM, but MM is not evolutionarily stable against RM.
-\end{lemma}
-
-\begin{proof}
-Assume without loss of generality that $b=d$. We have
-two cases then: (i) $c<b=d$; (ii) $c>b=d$. In the first case it
-is easy to see that RM and MM perform equally well. Indeed, given
-(i) both MM and RM choose action $I$ if $a>c$, and action $II$
-if $c>a$. If case (ii) holds instead, we have that RM plays $I$
-if $a>c$ and $II$ if $c>a$ as before, but MM plays $(\frac{1}{2}I;\frac{1}{2}II)$,
-since both $I$ and $II$ maximize the minimal payoff. Consider now
-a population of RM and MM playing games from the class $\mathcal{G}^{W}$.
-Whenever (i) is the case both RM and MM perform equally. Suppose that
-(ii) is the case and that $a>c$, without loss of generality. Then,
-a RM population is evolutionarily stable against MM by condition 1
-of ESS, since $a>\frac{1}{2}a+\frac{1}{2}c$, whereas a MM population
-is not evolutionarily stable against RM, because clearly $\frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d<\frac{1}{2}a+\frac{1}{2}b$.
-Hence, we have that in general $EU_{\mathcal{G}^{W}}(RM,RM)>EU_{\mathcal{G}^{W}}(MM,RM),\mbox{ and }EU_{\mathcal{G}^{W}}(MM,MM)<EU_{\mathcal{G}^{W}}(RM,MM)$.
-\end{proof}
-
-\medskip{}
-
-Since it is not difficult to see that both RM and MM are evolutionarily
-stable in $\mathcal{G}^{C}$, and that both RM and MM are not evolutionarily
-stable in $\mathcal{G}^{A}$ against each other, the main part of
-the proof will be to show that RM is the only evolutionarily stable
-player in the class $\mathcal{G}^{C}\cup\mathcal{G^{A}}$, that is:
-\begin{itemize}
-\item[(i')] $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,RM)>EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,RM),$
-\item[(ii')] $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,MM)<EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,MM).$
-\end{itemize}
-
-\noindent This part needs some more lemmas to be proven, but firstly we introduce
-the following bijective function $\phi$ between coordination and
-anti-coordination games.
-
-\medskip{}
-
-\begin{definition}[$\phi$]
-$\phi:\mathcal{G}^{C}\rightarrow\mathcal{G^{A}}$,
-such that $\phi(a,b,c,d)=(c,d,a,b)$, is a bijection that for each
-coordination game $G^{C}\in\mathcal{G}^{C}$ with payoffs $(a^{G^{C}},b^{G^{C}},c^{G^{C}},d^{G^{C}})$
-gives the anti-coordination game $G^{A}\in\mathcal{G}^{A}$ with payoffs
-$(a^{G^{A}},b^{G^{A}},c^{G^{A}},d^{G^{A}})=(c^{G^{C}},d^{G^{C}},a^{G^{C}},b^{G^{C}})$.
+\noindent Then we extend Definition \ref{def:ESS-NSS} to include choice mechanisms.
+
+\begin{definition}[ESM-NSM] \label{def:ESM-NSM}
+Given a class of games $\mathcal{G}$, a choice mechanism $(\gamma, \kappa)$ is \emph{evolutionarily stable
+(ESM)} if for any other choice mechanism $(\gamma', \kappa')$:
+\begin{enumerate}
+\item $EF_{\mathcal{G}}((\gamma, \kappa),(\gamma, \kappa))>EF_{\mathcal{G}}((\gamma', \kappa'),(\gamma, \kappa))$, or
+\item $EF_{\mathcal{G}}((\gamma, \kappa),(\gamma, \kappa))=EF_{\mathcal{G}}((\gamma', \kappa'),(\gamma, \kappa))$ and $EF_{\mathcal{G}}((\gamma, \kappa),(\gamma', \kappa'))>EF_{\mathcal{G}}((\gamma', \kappa'),(\gamma', \kappa'))$.
+\end{enumerate}
+\noindent A choice mechanism $(\gamma, \kappa)$ is \emph{neutrally stable (NSM)} if
+for any other choice mechanism $(\gamma', \kappa')$:
+\begin{enumerate}
+\item $EF_{\mathcal{G}}((\gamma, \kappa),(\gamma, \kappa))>EF_{\mathcal{G}}((\gamma', \kappa'),(\gamma, \kappa))$, or
+\item $EF_{\mathcal{G}}((\gamma, \kappa),(\gamma, \kappa))= EF_{\mathcal{G}}((\gamma', \kappa'),(\gamma, \kappa))$ and $EF_{\mathcal{G}}((\gamma, \kappa),(\gamma', \kappa'))\geq EF_{\mathcal{G}}((\gamma', \kappa'),(\gamma', \kappa'))$.
+\end{enumerate}
 \end{definition}
 
-\medskip{}
-
-\begin{lemma}
-Let $P(E)$ be the probability of event $E$, then
-it holds that:
-\begin{itemize}
-\item $P(I_{G^{C}}^{RM})=P(II_{\phi(G^{C})}^{RM})$, and $P(II_{G^{C}}^{RM})=P(I_{\phi(G^{C})}^{RM})$;
-\item $P(I_{G^{C}}^{MM})=P(II_{\phi(G^{C})}^{MM})$, and $P(II_{G^{C}}^{MM})=P(I_{\phi(G^{C})}^{MM})$.
-\end{itemize}
-\end{lemma}
-
-\begin{proof}
-It is easy to check that if $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$,
-a RM player plays action $I$ in $G^{C}$; that if $b^{G^{C}}-d^{G^{C}}<c^{G^{C}}-a^{G^{C}}$,
-RM plays $II$; and that if $b^{G^{C}}-d^{G^{C}}=c^{G^{C}}-a^{G^{C}}$,
-a RM player is indifferent between $I$ and $II$ in $G^{C}$, and
-we assume that randomizes with $(\frac{1}{2}I;\frac{1}{2}II)$. Similarly,
-if $a^{G^{A}}-c^{G^{A}}>d^{G^{A}}-b^{G^{A}}$, a RM player plays action
-$I$ in $G^{A}$; if $a^{G^{A}}-c^{G^{A}}<d^{G^{A}}-b^{G^{A}}$, RM
-plays $II$; and if $a^{G^{A}}-c^{G^{A}}=d^{G^{A}}-b^{G^{A}}$, a
-RM player is indifferent between $I$ and $II$ in $G^{A}$, and randomizes
-with $(\frac{1}{2}I;\frac{1}{2}II)$. Consequently, if $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$,
-then $P(I_{G^{C}}^{RM})=1$, and by definition of $\phi$ we have
-$P(II_{\phi(G^{C})}^{RM})=1$. Likewise, if $b^{G^{C}}-d^{G^{C}}<c^{G^{C}}-a^{G^{C}}$,
-then $P(II_{G^{C}}^{RM})=1=P(I_{\phi(G^{C})}^{RM})$; and if $b^{G^{C}}-d^{G^{C}}=c^{G^{C}}-a^{G^{C}}$,
-then $P(I_{G^{C}}^{RM})=P(II_{G^{C}}^{RM})=\frac{1}{2}=P(II_{\phi(G^{C})}^{RM})=P(I_{\phi(G^{C})}^{RM})$. \\
-In the same way, in coordination games we have that if $b^{G^{C}}>c^{G^{C}}$,
-a MM player plays $I$; if $c^{G^{C}}>b^{G^{C}}$, a MM player plays
-$II$; and if $b^{G^{C}}=c^{G^{C}}$, MM is indifferent between $I$
-and $II$, and plays $(\frac{1}{2}I;\frac{1}{2}II)$. In anti-coordination
-games instead, if $a^{G^{A}}>d^{G^{A}}$, MM plays $I$; if $a^{G^{A}}<d^{G^{A}}$,
-MM plays $II$; if $a^{G^{A}}=d^{G^{A}}$, MM plays $(\frac{1}{2}I;\frac{1}{2}II)$.
-By definition of $\phi$: $P(I_{G^{C}}^{MM})=1=P(II_{\phi(G^{C})}^{MM})$
-if $b^{G^{C}}>c^{G^{C}}$; $P(II_{G^{C}}^{MM})=1=P(I_{\phi(G^{C})}^{MM})$
-if $c^{G^{C}}>b^{G^{C}}$; and $P(I_{G^{C}}^{MM})=P(II_{G^{C}}^{MM})=\frac{1}{2}=P(II_{\phi(G^{C})}^{MM})=P(I_{\phi(G^{C})}^{MM})$
-if $b^{G^{C}}=c^{G^{C}}$.
-\end{proof}
-
-\medskip{}
-
-\begin{lemma}
-$P(\phi(G^{C}))=P(G^{C})$.
-\end{lemma}
-
-\begin{proof}
-By definition, each game $G^{C}\equiv(a^{G^{C}},b^{G^{C}},c^{G^{C}},d^{G^{C}})$
-is such that $a^{G^{C}}>c^{G^{C}}$ and $d^{G^{C}}>b^{G^{C}}$, and
-each game $G^{A}\equiv(a^{G^{A}},b^{G^{A}},c^{G^{A}},d^{G^{A}})$
-is such that $a^{G^{A}}<c^{G^{A}}$ and $d^{G^{A}}>b^{G^{A}}$. Since
-$a,b,c,d$ come from i.i.d. sampling, by simple renaming of variables
-it is clear that the probability of $(a^{G^{C}},b^{G^{C}},c^{G^{C}},d^{G^{C}})$
-is equal to the probability of $(c^{G^{C}},d^{G^{C}},a^{G^{C}},b^{G^{C}})$.
-Hence, $P(\phi(G^{C}))=P(G^{C})$.
-\end{proof}
-
-\medskip{}
-
-\begin{lemma}
-It holds that:
-\begin{itemize}
-\item $a^{G^{C}}>d^{G^{C}}\rightarrow(I_{G^{C}}^{MM}\subset I_{G^{C}}^{RM})$;
-\item $a^{G^{C}}<d^{G^{C}}\rightarrow(II_{G^{C}}^{MM}\subset II_{G^{C}}^{RM})$;
-\item $a^{G^{C}}=d^{G^{C}}\rightarrow I_{G^{C}}^{MM}=I_{G^{C}}^{RM}$.
-\end{itemize}
-\end{lemma}
-
-\begin{proof}
-If $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$, RM plays
-$I$, and if $b^{G^{C}}-d^{G^{C}}=c^{G^{C}}-a^{G^{C}}$, RM plays
-$(\frac{1}{2}I;\frac{1}{2}II)$, whereas if $b^{G^{C}}>c^{G^{C}}$,
-MM plays $I$, and if $b^{G^{C}}=c^{G^{C}}$, MM plays $(\frac{1}{2}I;\frac{1}{2}II)$.
-Then, $I_{G^{C}}^{RM}$ implies that $b^{G^{C}}-d^{G^{C}}\geq c^{G^{C}}-a^{G^{C}}$,
-and $I_{G^{C}}^{MM}$ implies that $b^{G^{C}}\geq c^{G^{C}}$. Moreover,
-on the assumption that $a^{G^{C}}>d^{G^{C}}$, it is easy to check
-that $b^{G^{C}}\geq c^{G^{C}}$ implies $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$.
-Hence, in any $G^{C}$ with $a^{G^{C}}>d^{G^{C}}$ it holds that $I_{G^{C}}^{MM}\mbox{ implies }I_{G^{C}}^{RM}$,
-i.e., $a^{G^{C}}>d^{G^{C}}\rightarrow(I_{G^{C}}^{MM}\subseteq I_{G^{C}}^{RM})$.
-Instead, it is possible that $a^{G^{C}}>d^{G^{C}}$, $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$
-and $b^{G^{C}}<c^{G^{C}}$ hold simultaneously, so that $I_{G^{C}}^{MM}\nsupseteq I_{G^{C}}^{RM}$.
-Consequently: $a^{G^{C}}>d^{G^{C}}\rightarrow(I_{G^{C}}^{MM}\subset I_{G^{C}}^{RM})$.
-By symmetric argument it can be shown that $a^{G^{C}}<d^{G^{C}}\rightarrow(II_{G^{C}}^{MM}\subset II_{G^{C}}^{RM})$
-too. \\
-Finally, when $a^{G^{C}}=d^{G^{C}}$ it holds that: $b^{G^{C}}-d^{G^{C}}>c^{G^{C}}-a^{G^{C}}$
-iff $b^{G^{C}}>c^{G^{C}}$; $b^{G^{C}}-d^{G^{C}}<c^{G^{C}}-a^{G^{C}}$
-iff $b^{G^{C}}<c^{G^{C}}$; and $b^{G^{C}}-d^{G^{C}}=c^{G^{C}}-a^{G^{C}}$
-iff $b^{G^{C}}=c^{G^{C}}$. Hence, $a^{G^{C}}=d^{G^{C}}\rightarrow I_{G^{C}}^{MM}=I_{G^{C}}^{RM}$.
-\end{proof}
-
-\medskip{}
-
-We are now ready to prove that: 
-\begin{itemize}
-\item[(i')] $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,RM)>EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,RM);$
-\item[(ii')] $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,MM)<EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,MM).$
-\end{itemize}
-We can rewrite $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,RM)>EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,RM)$
-more explicitly as:
-
-\medskip{}
-
-\noindent $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})\cdot c^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM}\cap I_{G^{A}}^{RM})\cdot a^{A}+P(II_{G^{A}}^{RM}\cap II_{G^{A}}^{RM})\cdot d^{A}+P(I_{G^{A}}^{RM}\cap II_{G^{A}}^{RM})\cdot b^{A}+P(II_{G^{A}}^{RM}\cap I_{G^{A}}^{RM})\cdot c^{A}] > \sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot d^{A}+P(I_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot c^{A}+P(II_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot b^{A}]$
-\medskip{}
-
-\noindent Then, the next derivation follows. By Lemma 5 and 6, we can express
-everything in terms of $G^{C}$ only: 
-\begin{itemize}
-
-\item $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})\cdot c^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM}\cap I_{G^{A}}^{RM})\cdot a^{A}+P(II_{G^{A}}^{RM}\cap II_{G^{A}}^{RM})\cdot d^{A}+P(I_{G^{A}}^{RM}\cap II_{G^{A}}^{RM})\cdot b^{A}+P(II_{G^{A}}^{RM}\cap I_{G^{A}}^{RM})\cdot c^{A}] > \sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot d^{A}+P(I_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot c^{A}+P(II_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot b^{A}]$
-
-\item $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})\cdot c^{C} +P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})\cdot c^{C}+P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})\cdot a^{C}] > \sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot c^{C}+P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}]$
-
-\item $\sum_{G^{C}}P(G^{C})[a^{C} \cdot (P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}) + P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})) + b^{C} \cdot  (P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM}) + P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})) + c^{C} \cdot (P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}) +P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})) + d^{C} \cdot (P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}))]> \sum_{G^{C}}P(G^{C})[a^{C} \cdot (P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + b^{C} \cdot (P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + c^{C} \cdot (P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + d^{C} \cdot (P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]$
-
-\end{itemize}
-
-\noindent Now let us split into $a>d$ and $a<d$, and consider $a>d$ first.
-Notice that, by Lemma 7, the case $a=d$ is irrelevant in order to
-discriminate between RM and MM. If $a>d$, by Lemma 7 we can eliminate
-the cases where RM plays $II$ and MM plays $I$:
-
-\begin{itemize}
-
-\item $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot (P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}) + P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})) + b^{C} \cdot  (P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM}) + P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})) + c^{C} \cdot (P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}) +P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})) + d^{C} \cdot (P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}))]>
-\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}) + b^{C} \cdot P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}) + c^{C} \cdot (P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + d^{C} \cdot (P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]$
-
-\item $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot (P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}) + P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})- P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + b^{C} \cdot  (P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM}) + P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})- P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + c^{C} \cdot (P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}) +P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})- P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + d^{C} \cdot (P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})- P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]> 0$
-
-\end{itemize}
-
-\noindent We now distinguish between two cases: (1) $ a-c = d-b $ and (2) $  a-c \neq d-b $.
-Notice that $P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM}) \neq 0$ if and only if case (1) obtains, and that $a>d$ and (1) imply $II_{G^{C}}^{MM}$.
-Then, from (1) we have:
-
-\begin{itemize}
-
-\item $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot (P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}) + P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})) + b^{C} \cdot  (P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{RM}) + P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})) + c^{C} \cdot (P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}) +P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})- P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + d^{C} \cdot (P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})- P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]> 0$
-
-\item $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot (\frac{1}{4}+\frac{1}{4}) + b^{C} \cdot  (\frac{1}{4}+\frac{1}{4}) + c^{C} \cdot (\frac{1}{4}+\frac{1}{4}-\frac{1}{2}-\frac{1}{2}) + d^{C} \cdot (\frac{1}{4}+\frac{1}{4}-\frac{1}{2}-\frac{1}{2})]> 0$
-
-\item $\sum_{G_{a>d}^{C}} P(G^{C})[\frac{1}{2}a^{C}+ \frac{1}{2}b^{C} - \frac{1}{2}c^{C} - \frac{1}{2}d^{C}]> 0$
-
-\end{itemize}
-
-\noindent Since we have assumed $ a-c = d-b $, the last inequality is not satisfied. We have instead:
-
-$$ \sum_{G_{a>d}^{C}} P(G^{C})[\frac{1}{2}a^{C}+ \frac{1}{2}b^{C} - \frac{1}{2}c^{C} - \frac{1}{2}d^{C}]= 0 $$
-
-\noindent This means that, when (1) is the case, RM and MM are neutrally stable. To prove the result we then have to show that the inequality is strict in favor of RM when case (2) obtains. \\
-When (2) is the case, it is easy to check, by Lemma 7, that $P(I_{G^{C}}^{RM} \cap I_{G^{C}}^{RM})-P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})=P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})$
-and $P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})=P(II_{G^{C}}^{RM} \cap II_{G^{C}}^{RM})$.
-Consequently, we have:
-
-\begin{itemize}
-
-\item $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot (P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM}) - P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + b^{C} \cdot  (P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{RM})- P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + c^{C} \cdot (P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})- P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + d^{C} \cdot (P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{RM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})- P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]> 0$
-
-\item $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}) + b^{C} \cdot  P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}) - c^{C} \cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}) - d^{C} \cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})]> 0$
-
-\item $\sum_{G_{a>d}^{C}} P(G^{C})[P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot (a^{C} + b^{C} - c^{C} - d^{C})]> 0$
-
-\end{itemize}
-\medskip{}
-
-\noindent We know that $I_{G^{C}}^{RM}$ implies that $a^{G^{C}}-c^{G^{C}}\geq d^{G^{C}}-b^{G^{C}}$.
-%and $II_{G^{C}}^{MM}$ implies that $b^{G^{C}}\leq c^{G^{C}}$. 
-Since we have assumed that $a^{G^{C}}-c^{G^{C}}\neq d^{G^{C}}-b^{G^{C}}$, we have that $a^{G^{C}}-c^{G^{C}} > d^{G^{C}}-b^{G^{C}}$. Hence, the inequality 
-$$\sum_{G_{a>d}^{C}} P(G^{C})[P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot (a^{C} + b^{C} - c^{C} - d^{C})]> 0$$
-is satisfied. So, when (2) obtains, RM is evolutionarily stable against MM.
-%From $b^{G^{C}}-d^{G^{C}}\geq c^{G^{C}}-a^{G^{C}}$, it is easy to see that $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[a^{G^{C}}-c^{G^{C}}]\geq\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot[d^{G^{C}}-b^{G^{C}}]$ holds.
-When the event $I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}$ obtains on the assumption that $a^{G^{C}}>d^{G^{C}}$, there are only three possible payoff orderings: $a>c\geq d>b$, $a>d>c>b$, and $a>d>c=b$.
-If games are randomly sampled from a finite set with i.i.d.
-values for $a,b,c$ and $d$, then $a>d>c=b$ occurs with positive probability, and the last formula of the derivation holds with strict inequality too.
-Hence, RM is evolutionarily stable when the value set for $a,b,c,d$ is finite.
-\\
-%If i.i.d.
-values are sampled from a compact and convex set instead, it is again easy to see that $\forall a,d,c\ \exists\epsilon$ such that $\forall b\in(d,d+\epsilon)$ the above formula holds with strict inequality.
-We can simply take $\epsilon\equiv\frac{a-c}{2}$, and the interval $(d,d+\epsilon)$ always has positive probability.
-Hence, RM is evolutionarily stable when the value set for $a,b,c,d$ is a compact and convex set too.
-\\
-Symmetrically, from $a<d$ and by distinguishing between the two cases (1) and (2) as before, in the end  we get:
-
-\begin{itemize}
-
-\item[(1)] $\sum_{G_{a<d}^{C}} P(G^{C})[-\frac{1}{2}a^{C}- \frac{1}{2}b^{C} + \frac{1}{2}c^{C} + \frac{1}{2}d^{C}]= 0$; and
-
-\item[(2)] $\sum_{G_{a<d}^{C}} P(G^{C})[P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot (-a^{C} - b^{C} + c^{C} + d^{C})]> 0$.
-
-\end{itemize}
-
-\noindent Hence, we can conclude that RM is evolutionarily stable against MM in the class $\mathcal{G}^{C}\cup\mathcal{G^{A}}$. \\
-In the case of sampling i.i.d.
-values from a real interval instead, games in $\mathcal{G}^I $ and $\mathcal{G}^W $ never arise, and the proof is the same for the remaining games in $\mathcal{G}^S $,  $\mathcal{G}^C $ and $\mathcal{G}^A $.
-
-\medskip{}
-
-The second half of the result is that MM is not evolutionarily stable
-against RM in $\mathcal{G}^{C}\cup\mathcal{G^{A}}$: $EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(MM,MM)<EU_{\mathcal{G}^{C}\cup\mathcal{G^{A}}}(RM,MM)$.
-As before, we write it more explicitly as:
-
-\medskip{}
-
-\noindent $\sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})\cdot b^{C}+P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{MM})\cdot c^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{MM}\cap I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{MM}\cap II_{G^{A}}^{MM})\cdot d^{A}+P(I_{G^{A}}^{MM}\cap II_{G^{A}}^{MM})\cdot b^{A}+P(II_{G^{A}}^{MM}\cap I_{G^{A}}^{MM})\cdot c^{A}] < \sum_{G^{C}}P(G^{C})[P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot a^{C}+P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot d^{C}+P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})\cdot b^{C}+P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})\cdot c^{C}]+\sum_{G^{A}}P(G^{A})[P(I_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot a^{A}+P(II_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot d^{A}+P(I_{G^{A}}^{RM}\cap II_{G^{A}}^{MM})\cdot b^{A}+P(II_{G^{A}}^{RM}\cap I_{G^{A}}^{MM})\cdot c^{A}]$.
-\medskip{}
-
-\noindent When $a>d$, similarly to the above derivation, we get:
-
-\medskip{}
-\noindent $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot (P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{MM}) + P(I_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})- P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}) - P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + b^{C} \cdot  (P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{MM}) + P(I_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})- P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}) - P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + c^{C} \cdot (P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{MM}) +P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + d^{C} \cdot (P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})+P(II_{G^{C}}^{MM}\cap I_{G^{C}}^{MM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))]< 0$
-\medskip{}
-
-\noindent We now distinguish between (1) $b=c$, (2) $b>c$, and (3) $b<c$. Notice that either (1) or (2), together with $a>d$, implies $I_{G^{C}}^{RM}$. Then we obtain: 
-\begin{itemize}
-
-\item[(1)] $\sum_{G_{a<d}^{C}} P(G^{C})[-\frac{1}{2}a^{C} - \frac{1}{2}b^{C} + \frac{1}{2}c^{C} + \frac{1}{2}d^{C}]< 0$;
-
-\item[(2)] $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot (P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{MM}) - P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + b^{C} \cdot  (P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{MM}) - P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))]= 0$;
-
-\item[(3)] $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot (- P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + b^{C} \cdot  (- P(I_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + c^{C} \cdot (P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + d^{C} \cdot (P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))] \leq 0$.
-
-\end{itemize}
-
-\noindent When $a<d$, the derivation proceeds symmetrically and we get:
-
-\begin{itemize}
-
-\item[(1)] $\sum_{G_{a<d}^{C}} P(G^{C})[\frac{1}{2}a^{C} + \frac{1}{2}b^{C} - \frac{1}{2}c^{C} - \frac{1}{2}d^{C}]< 0$;
-
-\item[(2)] $\sum_{G_{a>d}^{C}} P(G^{C})[a^{C} \cdot (P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{MM}) - P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + b^{C} \cdot  (P(I_{G^{C}}^{MM}\cap I_{G^{C}}^{MM}) - P(I_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + c^{C} \cdot (- P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM})) + d^{C} \cdot (- P(II_{G^{C}}^{RM}\cap I_{G^{C}}^{MM}))] \leq 0$
-
-\item[(3)] $\sum_{G_{a>d}^{C}} P(G^{C})[c^{C} \cdot (P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM})) + d^{C} \cdot (P(II_{G^{C}}^{MM}\cap II_{G^{C}}^{MM})- P(II_{G^{C}}^{RM}\cap II_{G^{C}}^{MM}))] = 0$.
-
-\end{itemize}
-
-\noindent Finally, we can conclude that MM is
-not evolutionarily stable against RM both when the value set for $a,b,c,d$
-is finite, and when the value set for $a,b,c,d$ is a compact and
-convex set. This concludes the proof. $\dashv$
-
-\newpage
-
-\textbf{Proof of Proposition 2.} First we prove that regret type is evolutionarily stable against altruistic type and that altruistic type is not evolutionarily stable against regret type, and second we show that regret type is evolutionarily stable against competitive type and that competitive type is not evolutionarily stable against regret type.
-We make use of the same partition of $\mathcal{G}$ introduced in the proof of Proposition 1.
-Again, to ease notation let us write ALT and COM in the place of $(\tau^{alt}, \Delta(A))$ and $(\tau^{com}, \Delta(A))$, respectively.
-
-\begin{lemma}
-In $\mathcal{G}^I$, RM and ALT perform equally well.
-\end{lemma}
-
-\begin{proof}
-Trivial.
-\end{proof}
-
-\begin{lemma}
-In $\mathcal{G}^S$, RM is evolutionarily stable against ALT, and ALT is not evolutionarily stable against RM. 
-\end{lemma}
-
-\begin{proof}
-Let us assume, without loss of generality, that $a>c$ and $b>d$.
-We already know that RM always plays the dominant action $I$, then a population of RM players always coordinates on $I$ with a payoff of $a$.
-It is possible instead that an ALT player plays the dominated action $II$, for instance when $2d > 2a$ and $2a < b+c$.
-Then, the payoff of an ALT invader against a population of RMs is $c$.
-Since $a>c$ by assumption, we get that a RM population cannot be invaded by ALT players in this case.
-When $b+c < 2a$ and $b+c < 2d$, ALT will play $(\frac{1}{2}I;\frac{1}{2}II)$ for an expected payoff of $\frac{1}{2} a + \frac{1}{2} c$.
-Since $a > \frac{1}{2} a + \frac{1}{2} c$, a population of RMs is evolutionarily stable against ALT.
-\\
-When $2d > 2a$ and $2a < b+c$, an ALT population plays action $II$ for a payoff of $d$, whereas a RM invader plays action $I$ for a payoff of $b$.
-By assumption $b>d$, hence a population of ALTs would not be evolutionarily stable in this case.
-When $b+c < 2a$ and $b+c < 2d$, the expected payoff of a population of ALTs is $\frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d$, while the expected payoff of a RM invader is $\frac{1}{2}a+\frac{1}{2}b$.
-Since $\frac{1}{2}a+\frac{1}{2}b > \frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d$, we have that an ALT population is not evolutionarily stable against RM.
-\end{proof}
-
-\begin{lemma}
-In $\mathcal{G}^W$, RM is evolutionarily stable against ALT, and ALT is not evolutionarily stable against RM. 
-\end{lemma}
-
-\begin{proof}
-Let us assume, WLOG, that $b=d$ and $a>c$.
-We know that RM always plays the (weakly) dominant action $I$.
-Again, a RM population always coordinates on $I$ for a payoff of $a$, whereas when $2d > 2a$ and $2a < b+c$ an ALT invader plays $II$.
-Then, the payoff of an ALT invader against a population of RMs is $c$.
-Since $a>c$ by assumption, we get that a RM population cannot be invaded by ALT players in this case.
-When $b+c < 2a$ and $b+c < 2d$, ALT plays $(\frac{1}{2}I;\frac{1}{2}II)$ for an expected payoff of $\frac{1}{2} a + \frac{1}{2} c$.
-Since $a > \frac{1}{2} a + \frac{1}{2} c$, a population of RMs is evolutionarily stable against ALT.
-\\
-When $2d > 2a$ and $2a < b+c$, an ALT population plays action $II$ for a payoff of $d$, whereas a RM invader plays action $I$ for a payoff of $b$.
-Since $b=d$, we have to check the second condition for ESS: an ALT against RM gets $c$, and RM against RM gets $a$.
-By assumption $a>c$, hence an ALT population would be invaded by RM players in this case.
-When $b+c < 2a$ and $b+c < 2d$, the expected payoff of a population of ALTs is $\frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d$, while the expected payoff of a RM invader is $\frac{1}{2}a+\frac{1}{2}b$.
-Since $\frac{1}{2}a+\frac{1}{2}b > \frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d$, we again have that an ALT population is not evolutionarily stable against RM.
-\end{proof}
-
-\begin{lemma}
-In $\mathcal{G}^C$, RM is evolutionarily stable against ALT, and ALT is not evolutionarily stable against RM. 
-\end{lemma}
-
-\begin{proof}
-Let's assume, WLOG, that $a>d$.
-We know that RM plays $I$ if $ a-c > d-b $ and $II$ if $ a-c < d-b $, whereas  ALT plays $I$ if $2d<b+c$, otherwise ALT plays $(\frac{1}{2}I;\frac{1}{2}II)$.
-If $2d<b+c$, then $d-b<c-d$, hence $c>d$.
-Consequently, when $2d<b+c$ the expected payoff of an ALT population is $a$
-\end{proof}
+\noindent From Proposition \ref{proposition1} we know that:
+
+\begin{itemize}
+\item[(i)] $EF_{\mathcal{G}}(R,R)>EF_{\mathcal{G}}(M,R);$
+\item[(ii)] $EF_{\mathcal{G}}(M,M)<EF_{\mathcal{G}}(R,M).$
+\end{itemize}
+
+\noindent Then, from Definition \ref{def:ESM-NSM} it immediately follows that the unique evolutionarily stable state is a monomorphic population of $R$-players. $\dashv$
 
 \printbibliography[heading=bibintoc]
+
+\iffalse
 
@@
   processes
-  \citep[e.g.][]{HammersteinStevens2012:Six-Reasons-for,FawcettHamblin2013:Exposing-the-be}. Here,
+  \citep[e.g.,][]{HammersteinStevens2012:Six-Reasons-for,FawcettHamblin2013:Exposing-the-be}. Here,
   we seek to contribute to the formal machinery, an extension of evolutionary game theory, that
@@
     mechanisms} that are adapted in a rich and variable environment
-  \citep[e.g.][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche}.
+  \citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche}.
 \item However, studies on the adaptive value of choice mechanisms have focused, for the most
   part, on the evolutionary benefit of learning rules
-  \citep[e.g.][]{ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o}. (\myalert{More references Harley 1981!!!, \dots}). 
+  \citep[e.g.,][]{ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o}. (\myalert{More references Harley 1981!!!, \dots}). 
     Moreover, only little attention has been paid to
@@
     representations of) preferences matters. Since almost any reasonable learning or
-    decision-making process will make use of some (subjective, agent-internal (possibly
+    decision making process will make use of some (subjective, agent-internal (possibly
     unconscious)) representation of the quality of choice options, the question of which such
@@
     processes
-    \citep[e.g.][]{HammersteinStevens2012:Six-Reasons-for,FawcettHamblin2013:Exposing-the-be}.
+    \citep[e.g.,][]{HammersteinStevens2012:Six-Reasons-for,FawcettHamblin2013:Exposing-the-be}.
   \item Non-veridical regret-based representations of payoffs are intuitively appealing (we do,
@@
 \end{quote}
-In the same year, Graham Loomes and Robert Sugden \citet{LoomesSugden1982:Regret-Theory:-} show that a regret-based theory of choice can match
+In the same year, Graham Loomes and Robert Sugden \citet{loosug82} show that a regret-based theory of choice can match
 and explain all the main experimental results of prospect theory, and claim that
@@
   conventional expected utility theory therefore represents an unnecessarily restrictive notion
-  of rationality. \hfill \citep{LoomesSugden1982:Regret-Theory:-}
+  of rationality. \hfill \citep{loosug82}
 \end{quote}
@@
 
+\newpage
+
+\textbf{Proof of Proposition 2.} First we prove that regret type is evolutionarily stable against altruistic type and that altruistic type is not evolutionarily stable against regret type, and second we show that regret type is evolutionarily stable against competitive type and that competitive type is not evolutionarily stable against regret type.
+We make use of the same partition of $\mathcal{G}$ introduced in the proof of Proposition 1.
+Again, to ease notation let us write ALT and COM in the place of $(\tau^{alt}, \Delta)$ and $(\tau^{com}, \Delta)$, respectively.
+
+\begin{lemma}
+In $\mathcal{G}^I$, RM and ALT perform equally well.
+\end{lemma}
+
+\begin{proof}
+Trivial.
+\end{proof}
+
+\begin{lemma}
+In $\mathcal{G}^S$, RM is evolutionarily stable against ALT, and ALT is not evolutionarily stable against RM. 
+\end{lemma}
+
+\begin{proof}
+Let us assume, without loss of generality, that $a>c$ and $b>d$.
+We already know that RM always plays the dominant action $I$, then a population of RM players always coordinates on $I$ with a payoff of $a$.
+It is possible instead that an ALT player plays the dominated action $II$, for instance when $2d > 2a$ and $2a < b+c$.
+Then, the payoff of an ALT invader against a population of RMs is $c$.
+Since $a>c$ by assumption, we get that a RM population cannot be invaded by ALT players in this case.
+When $b+c < 2a$ and $b+c < 2d$, ALT will play $(\frac{1}{2}I;\frac{1}{2}II)$ for an expected payoff of $\frac{1}{2} a + \frac{1}{2} c$.
+Since $a > \frac{1}{2} a + \frac{1}{2} c$, a population of RMs is evolutionarily stable against ALT.
+\\
+When $2d > 2a$ and $2a < b+c$, an ALT population plays action $II$ for a payoff of $d$, whereas a RM invader plays action $I$ for a payoff of $b$.
+By assumption $b>d$, hence a population of ALTs would not be evolutionarily stable in this case.
+When $b+c < 2a$ and $b+c < 2d$, the expected payoff of a population of ALTs is $\frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d$, while the expected payoff of a RM invader is $\frac{1}{2}a+\frac{1}{2}b$.
+Since $\frac{1}{2}a+\frac{1}{2}b > \frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d$, we have that an ALT population is not evolutionarily stable against RM.
+\end{proof}
+
+\begin{lemma}
+In $\mathcal{G}^W$, RM is evolutionarily stable against ALT, and ALT is not evolutionarily stable against RM. 
+\end{lemma}
+
+\begin{proof}
+Let us assume, WLOG, that $b=d$ and $a>c$.
+We know that RM always plays the (weakly) dominant action $I$.
+Again, a RM population always coordinates on $I$ for a payoff of $a$, whereas when $2d > 2a$ and $2a < b+c$ an ALT invader plays $II$.
+Then, the payoff of an ALT invader against a population of RMs is $c$.
+Since $a>c$ by assumption, we get that a RM population cannot be invaded by ALT players in this case.
+When $b+c < 2a$ and $b+c < 2d$, ALT plays $(\frac{1}{2}I;\frac{1}{2}II)$ for an expected payoff of $\frac{1}{2} a + \frac{1}{2} c$.
+Since $a > \frac{1}{2} a + \frac{1}{2} c$, a population of RMs is evolutionarily stable against ALT.
+\\
+When $2d > 2a$ and $2a < b+c$, an ALT population plays action $II$ for a payoff of $d$, whereas a RM invader plays action $I$ for a payoff of $b$.
+Since $b=d$, we have to check the second condition for ESS: an ALT against RM gets $c$, and RM against RM gets $a$.
+By assumption $a>c$, hence an ALT population would be invaded by RM players in this case.
+When $b+c < 2a$ and $b+c < 2d$, the expected payoff of a population of ALTs is $\frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d$, while the expected payoff of a RM invader is $\frac{1}{2}a+\frac{1}{2}b$.
+Since $\frac{1}{2}a+\frac{1}{2}b > \frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d$, we again have that an ALT population is not evolutionarily stable against RM.
+\end{proof}
+
+\begin{lemma}
+In $\mathcal{G}^C$, RM is evolutionarily stable against ALT, and ALT is not evolutionarily stable against RM. 
+\end{lemma}
+
+\begin{proof}
+Let's assume, WLOG, that $a>d$.
+We know that RM plays $I$ if $ a-c > d-b $ and $II$ if $ a-c < d-b $, whereas  ALT plays $I$ if $2d<b+c$, otherwise ALT plays $(\frac{1}{2}I;\frac{1}{2}II)$.
+If $2d<b+c$, then $d-b<c-d$, hence $c>d$.
+Consequently, when $2d<b+c$ the expected payoff of an ALT population is $a$
+\end{proof}
+
+\fi
+
 \end{document}

### 2015-12-14 paper/graph.tex
graph added

\documentclass{article}

\usepackage[]{mypackages}

\usepackage{mycommands}

\usepackage{verbatim}
\usepackage[active,tightpage]{preview}
\PreviewEnvironment{tikzpicture}
\setlength\PreviewBorder{5pt}

\usetikzlibrary{positioning,arrows,calc,fit}

% \usepackage{pgfplots}

\begin{document}

\begin{tikzpicture}[node distance = 2.5cm]

  \begin{scope}

    \node[] (environment) {};

    \node[rounded corners, draw, rectangle, minimum height = 0.75cm, text width=6cm, text
    centered, below of = environment, node distance = 2cm] (situation)
    {\textbf{decision situation} $d$};

    \node[rounded corners, draw, rectangle, minimum height = 0.75cm, text width=6cm, text
    centered, below of = situation] (representation) 
    {\textbf{subjective representation} $s$ of $d$ \\ \textcolor{gray}{[preference, beliefs, \dots]}};

    \node[rounded corners, draw, rectangle, minimum height = 0.75cm, text width=6cm, text centered, below of = representation] (action)
    {\textbf{action choice} $a$ based on $s$};

    \node[rounded corners, draw, rectangle, minimum height = 0.75cm, text width=6cm, text
    centered, below of = action] (payoff) {\textbf{payoff} for $a$ in $d$};

    \draw[->, thick]
    ([xshift=-1.75cm]environment.center)--([xshift=-1.75cm,yshift=0.5cm]situation.center)
    node[midway, right] {environment presents random $d$};

    \draw[->, thick]
    ([xshift=-1.75cm,yshift=-0.5cm]situation.center)--([xshift=-1.75cm,yshift=0.55cm]representation.center)
    node[midway, right] {subj.~representation scheme $\gamma$};

    \draw[->, thick]
    ([xshift=-1.75cm,yshift=-0.55cm]representation.center)--([xshift=-1.75cm,yshift=0.5cm]action.center)
    node[midway, right] {action selection function $\kappa$};

    \draw[->, thick]
    ([xshift=-1.75cm,yshift=-0.55cm]action.center)--([xshift=-1.75cm,yshift=0.5cm]payoff.center)
    node[midway, right] {};

    \node[minimum height = 0.75cm, text width=6cm, text
    centered, right of = representation, xshift = 2cm, rotate = 90] (mechanism) {choice mechanism};

    \begin{pgfonlayer}{background}
             \node [rounded corners,
       very thick,draw=black!40,fit={($(situation.south)+(0,+30pt)$) 
                                 ($(mechanism.west)+(+5pt,0)$) 
                                 ($(action.north)+(0,-30pt)$) 
                                 ($(representation.west)+(-7pt,0)$)}] (box) {};
    \end{pgfonlayer}

  \end{scope}

\end{tikzpicture}

\begin{tikzpicture}[]

  \begin{scope}

    \node (tpic) at ( -5,0)  {\includegraphics[width=4cm]{s1_vx.png}};

    \node (cpic) at (0,0)    {\includegraphics[width=4cm]{s1_v2.png}};

    \node (dpic) at ( 5,0)   {\includegraphics[width=4cm]{s2_v1.png}};

    \node (tlabel) at (-5, -4) {\Large{\mystate{t}}};

    \node (clabel) at (  0,-4) {\Large{$\mystate{c}^*$}};

    \node (dlabel) at (5,-4)   {\Large{\mystate{d}}};

    \node (mainlabel) at (0, -5.3) {\Large{Possible Referents}};

    \begin{pgfonlayer}{background}
       \node [thick,draw=black!40,fit=(tpic) (dlabel) (mainlabel) (dpic)] {};
    \end{pgfonlayer}
  \end{scope}

\begin{scope}[xshift = 7.5cm, yshift = -2.8cm, x=1.05cm, y = 1.1cm]

    \node (tpic) at  (0,3)    {\includegraphics[height=1.4cm]{v2.png}};
    \node (d1pic) at (3,3)    {\includegraphics[height=1.4cm]{s1.png}};
    \node (cpic) at  (0,0)    {\includegraphics[height=1.4cm]{s2.png}};
    \node (d2pic) at (3,0)    {\includegraphics[height=1.4cm]{v1.png}};

    \node (tlabel) at  (0,2)  {\Large{\mymessg{t}}};
    \node (d1label) at (3,2)  {\Large{$\mymessg{c}^*$}};
    \node (clabel) at  (0,-1) {\Large{\mymessg{d1}}};
    \node (d2label) at (3,-1) {\Large{\mymessg{d2}}};

    \node (mainlabel) at (1.5, 4.3) {\Large{Message Options}};

    \begin{pgfonlayer}{background}
       \node [thick,draw=black!40,fit=(tpic) (d2label) (mainlabel) (d2pic)] {};
    \end{pgfonlayer}
  \end{scope}

\end{tikzpicture}

\end{document}

### 2015-12-16 paper/graph.tex
rewrite intro

@@
     centered, below of = environment, node distance = 2cm] (situation)
-    {\textbf{decision situation} $d$};
+    {environment produces random \\ \textbf{decision situation} $d$};
 
@@
     centered, below of = action] (payoff) {\textbf{payoff} for $a$ in $d$};
-
-    \draw[->, thick]
-    ([xshift=-1.75cm]environment.center)--([xshift=-1.75cm,yshift=0.5cm]situation.center)
-    node[midway, right] {environment presents random $d$};
 
@@
     \begin{pgfonlayer}{background}
-             \node [rounded corners,
-       very thick,draw=black!40,fit={($(situation.south)+(0,+30pt)$) 
-                                 ($(mechanism.west)+(+5pt,0)$) 
-                                 ($(action.north)+(0,-30pt)$) 
-                                 ($(representation.west)+(-7pt,0)$)}] (box) {};
+             \node [rounded corners, dashed,
+       very thick,draw=black!40,fit={($(situation.south)+(0,-10pt)$) 
+                                     ($(mechanism.west)+(+5pt,+42pt)$) 
+                                     % ($(action.north)+(0,+10pt)$) 
+                                     ($(representation.west)+(-7pt,0)$)
+                                   }] (box) {};
     \end{pgfonlayer}

### 2015-12-16 paper/paper.tex
rewrite intro

@@
 
+\usetikzlibrary{positioning,arrows,calc,fit}
 %========================================
@@
 
-\begin{quotation} \textit{This is what I aim at, because the point of philosophy is to start with something so simple as not to seem worth stating, and to end with something so paradoxical that no one will believe it.} \citep{Russ18} \end{quotation}
+% \begin{quotation} \textit{This is what I aim at, because the point of philosophy is to start with something so simple as not to seem worth stating, and to end with something so paradoxical that no one will believe it.} \citep{Russ18} \end{quotation}
 
 Evolutionary game theory has become an established philosophical tool for probing into
-conceptual issues whose complexity requires mathematical modelling. However, most applications
-look at evolutionary selection of behavior in a single \emph{stage game}. There are two common
-simplifications in this approach. Firstly, the stage game is usually considered fixed, closed
-and immutable. Secondly, what evolves are behavioral strategies for the stage game. It has
-consequently been argued that, instead of focusing on a fixed, immutable stage game and the
-behavioral selection for that stage game alone, we should rather study the evolutionary
-competition of \emph{choice mechanisms} under selective pressure in a rich and variable
-environment \citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche}. 
-But only little attention has been paid to modeling the evolutionary competition between choice
-mechanisms in a game-theoretical framework \citep[but
-see][]{ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o}.\todo{More references
+conceptual issues whose complexity requires mathematical modelling at a high level of
+abstraction.  Abstraction entails simplifying assumptions. Evolutionary game models heavily
+simplify reality in many ways as well. Two simplifications relevant here are that the
+environment is represented as a fixed, closed and immutable \emph{stage game} and that the
+focus of evolutionary selection is behavior for this stage game alone. In contrast, some argue
+for studying instead the evolutionary competition of general \emph{choice mechanisms} in a rich
+and variable environment
+\citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche}. To show that
+there is no tension here, this paper introduces a method for reconciling established notions of
+evolutionary game theory with evolutionary selection of choice mechanisms in variable
+environments \citep[see related work
+by][]{ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o}.\todo{More references
   Harley 1981!!!, O Conor \dots}
@@
 situations. A crucial part of any choice mechanism is a \emph{subjective representation} of the
-choice situation, e.g., the agent's manner of representing their preferences and her way of
-forming decision relevant beliefs in the case of uncertainty. Since almost any reasonable
-learning or decision making process will make use of some (subjective, agent-internal, possibly
-unconscious) representation of both beliefs and the quality of choice options, the question of which such
-representations are ecologically valuable (i.e., lead to high fitness) is central and has been
-subject of recent interest also in economics literature \citep[e.g.,][]{algweib13,DekElyYlan07,RobSam11}. Na\"ive intuition might convince us that preferences that veridically
-represent the actual, true fitness measure that evolutionary selection is based upon must
-surely be the best. We demonstrate that, if we take into account the different ways agents may cope with
-uncertainty, this na\"ive conclusion is premature. Under certain reasonable epistemic
-conditions, non-veridical preference representations can be evolutionarily beneficial.
-
-To show this, we study the evolutionary competition of choice mechanisms, or more specifically
-the competition of subjective representations of choice situations, in a variable
-environment. Concretely, we look at evolutionary ``meta-games'' whose ``acts'' are choice mechanisms and whose ``payoffs'' represent the average expected
-fitness that different choice mechanisms would accrue when playing
-arbitrary games (from a given class, with a given occurrence probability). In this sense, a
-meta-game captures (the modeller's) assumptions about the relevant statistics of the
-environment in which evolutionary forces operate, while we are still able to use standard
-methods from evolutionary game theory, like stability or evolutionary dynamics.
-
-Section \ref{sec:rati--subj} overviews different accounts of rationality in decision making and relates the approach we take here to the existing literature on the topic.
-Section \ref{sec:basic-notions} introduces the various decision- and game-theoretic notions that will be later used in the evolutionary analysis.
-Sections \ref{sec:model} and \ref{sec:basic-model-1} define the evolutionary framework, and Section \ref{sec:results:-basic-model} presents the main results of the paper.
-Section \ref{sec:extensions} extends the evolutionary analysis by introducing more choice mechanisms in the model and by investigating the evolutionary performances of different choice mechanisms when facing arbitrary decision problems.
-Finally, in Section \ref{sec:conclusion} we comment on the results achieved and future perspectives.
-
-\section{Rationality, subjectivity, beliefs \& preferences}
+choice situation, in particular a manner of forming preferences and beliefs about a possibly
+uncertain world. This paper asks: which preference and belief representations are ecologically
+valuable (i.e., lead to high fitness)? The evolution of preferences has been subject of recent
+interest in theoretical economics \citep[e.g.,][]{algweib13,DekElyYlan07,RobSam11}. The
+particular contribution of this paper is to provide a case, spelled out formally, that
+questions about the evolution of preferences cannot be separated from questions about the
+evolution of beliefs. As a point in case, we demonstrate that if agents have imprecise
+probabilistic beliefs \citep[e.g.][]{gardsah82,levi74,walley96}, preference representations in
+terms of regret that deviate from the
+true, objective fitness that evolutionary selection operates on can be selected for.
+
+% To show this, we study the evolutionary competition of choice mechanisms, or more
+% specifically the competition of subjective representations of choice situations, in a
+% variable environment. Concretely, we look at evolutionary ``meta-games'' whose ``acts'' are
+% choice mechanisms and whose ``payoffs'' represent the average expected fitness that different
+% choice mechanisms would accrue when playing arbitrary games (from a given class, with a given
+% occurrence probability). In this sense, a meta-game captures (the modeller's) assumptions
+% about the relevant statistics of the environment in which evolutionary forces operate, while
+% we are still able to use standard methods from evolutionary game theory, like stability or
+% evolutionary dynamics.
+
+Section \ref{sec:rati--subj} reviews different accounts of rationality in decision theory and
+relates the approach we take here to the existing literature on the topic. Section
+\ref{sec:basic-notions} introduces relevant decision- and game-theoretic notions. Sections
+\ref{sec:model} and \ref{sec:basic-model-1} define the evolutionary framework, and Section
+\ref{sec:results:-basic-model} presents the main results of the paper. Section
+\ref{sec:extensions} extends the evolutionary analysis by introducing more choice mechanisms in
+the model and by investigating the evolutionary performances of different choice mechanisms
+when facing arbitrary decision problems. Finally, in Section \ref{sec:conclusion} we reflect on
+the results achieved.
+
+\todo[inline]{rewrite overview after restructuring}
+
+\section{Rationality, subjective beliefs \& preferences and the evolution of choice mechanisms}
 \label{sec:rati--subj}
@@
 If beliefs and preferences are subjective, there is room for \emph{rationalization} or
-\emph{redescriptionism} of observable behavior. Prospect theory is, perhaps, the most prominent
-example. \citet{KahnemannTversky1979:Prospect-Theory} looked at experimental data from human
-choices in suitably defined tasks and demonstrated that what appears to be violations of
-rationality norms can be explained on the assumption that subjects' beliefs and preferences
-deviate systematically from the objectively given parameters in the presented choice task
-(e.g., by taking into account reference points and diminishing returns for both gains and
-losses).  Similarly, tinkering with the notion of subjective utility, in particular by
-including social preferences such as fairness, reciprocity or similar, allows us to describe as
-rational empirically observed behavior in situations of social decision making, such as the
-prisoners' dilemma or public goods games, that might otherwise appear irrational \citep[e.g.,][]{fehrschmidt99,charrab02}.
-
-It could be objected that, without additional constraints, the notion of rationality is likely
-to collapse, as it seems possible to deem rational almost everything that is observed, given the
-freedom to adjust beliefs and preferences at will. But there are many ways in which ascriptions
-of beliefs and preferences are constrained by normative considerations of rationality. To begin
-with, if the DM's uncertainty is about objective chance, it can be argued that subjective
-beliefs should conform (at least roughly) to objective chance. When the DM's uncertainty cannot
-be anchored in an objective notion of chance, then temporal consistency in his decision making
-should at least constrain his subjective beliefs, else he fall prey to exploitation by Dutch
-books. Similarly, in certain situations it may make sense to postulate on normative grounds
-that subjective preferences should be oriented towards tracking objective utility, e.g.,
-fitness. For instance, in their classic work \myalert{(Alchian, Friedman)} argue that profit
-maximization is a reasonable assumption for characterizing outcomes in a competitive market
-because only firms behaving in a manner that is consistent with profit maximization will
-survive in the long run.\todo{@Paolo: please add references}
-
-An alternative to descriptive vs.~normative views on rationality is \emph{adaptationism}
-\citep[e.g.,][]{HagenChater2012:Decision-Making}. \todo{more references} Adaptationism aims to
-explain choice behavior by appeal to evolutionary considerations. The key idea is that decision
-makers (human and other life forms) have evolved choice mechanisms which were fitness enhancing
-in the relevant domains of choice making, at the relevant time of evolution. When it comes to
-preferences, this is clearly related to Alchian and Friedman's argument that firms
-\emph{should} optimize that which makes them ``live,'' so to speak. For biological agents, the
-argument would be that subjective preferences \emph{should} stay as close as possible to whatever determines objective
-fitness.
+\emph{redescriptionism} of observable behavior. For example,
+\citet{KahnemannTversky1979:Prospect-Theory} famously demonstrated that what appear to be
+violations of rationality norms in human decision making can be explained on the assumption
+that subjects' beliefs and preferences deviate systematically from the objectively given
+parameters in the presented choice task. Similarly for social decision making, including social
+preferences such as fairness, reciprocity or similar, allows us to describe as rational
+empirically observed behavior, such as in experimental prisoners' dilemmas or public goods
+games, that might otherwise appear irrational \citep[e.g.,][]{fehrschmidt99,charrab02}.
+
+The main objection to redescriptionism is that, without additional constraints, the notion of
+rationality is likely to collapse, as it seems possible to deem rational almost everything that
+is observed, given the freedom to adjust beliefs and preferences at will. \emph{Normativism}
+therefore emphasizes that there are many ways in which ascriptions of beliefs and preferences
+are constrained by normative considerations of rationality as well. As for beliefs, where
+possible, subjective beliefs should reflect objective chance. Where this is impossible,
+temporal consistency of choices constrains rational subjective beliefs, else exploitation by
+Dutch books is possible. As for preferences, in certain situations it may make sense to
+postulate on normative grounds that subjective preferences should be oriented towards tracking
+objective fitness. For instance, profit maximization seems a reasonable assumption for
+characterizing outcomes in a competitive market because only firms behaving in a manner that is
+consistent with profit maximization will survive in the long run \myalert{(Alchian,
+  Friedman)}.\todo{@Paolo: please add references}
+
+An alternative view on rationality of choice is \emph{adaptationism}
+\citep[e.g.,][]{Anderson1991:Is-human-cognit,ChaterOaksford2000:The-Rational-An,HagenChater2012:Decision-Making}. \todo{more
+  references} Adaptationism aims to explain choice behavior by appeal to evolutionary
+considerations: DMs have acquired choice mechanisms that outperform other manners of choice
+making in a rich and variable environment. A choice mechanism could be a set of distinct
+heuristics (the DM's \emph{adaptive toolbox}) that have little in common
+\citep[e.g.,][]{TverskyKahnemann1981:The-Framing-of-,GigerenzerGoldstein1996:Reasoning-the-F,ScheibehenneRieskamp2013:Testing-the-Ada}. But
+to relate to the philosophical debate about the nature of rational choice, we here suggest to
+think of a choice mechanism as a map from choice situations to action choices that contains an
+explicit level of subjective representation of a decision situation (see
+Figure~\ref{fig:ChoiceMechanism}).
+
+\begin{figure}
+  \centering
+  \begin{tikzpicture}[node distance = 2.5cm]
+
+  \begin{scope}
+
+    \node[] (environment) {};
+
+    \node[rounded corners, draw, rectangle, minimum height = 0.75cm, text width=6cm, text
+    centered, below of = environment, node distance = 2cm] (situation)
+    {environment produces random \\ \textbf{decision situation} $d$};
+
+    \node[rounded corners, draw, rectangle, minimum height = 0.75cm, text width=6cm, text
+    centered, below of = situation] (representation) 
+    {\textbf{subjective representation} $s$ of $d$ \\ \textcolor{gray}{[preference, beliefs, \dots]}};
+
+    \node[rounded corners, draw, rectangle, minimum height = 0.75cm, text width=6cm, text centered, below of = representation] (action)
+    {\textbf{action choice} $a$ based on $s$};
+
+    \node[rounded corners, draw, rectangle, minimum height = 0.75cm, text width=6cm, text
+    centered, below of = action] (payoff) {\textbf{payoff} for $a$ in $d$};
+
+    \draw[->, thick]
+    ([xshift=-1.75cm,yshift=-0.5cm]situation.center)--([xshift=-1.75cm,yshift=0.55cm]representation.center)
+    node[midway, right] {subj.~representation scheme $\gamma$};
+
+    \draw[->, thick]
+    ([xshift=-1.75cm,yshift=-0.55cm]representation.center)--([xshift=-1.75cm,yshift=0.5cm]action.center)
+    node[midway, right] {action selection function $\kappa$};
+
+    \draw[->, thick]
+    ([xshift=-1.75cm,yshift=-0.55cm]action.center)--([xshift=-1.75cm,yshift=0.5cm]payoff.center)
+    node[midway, right] {};
+
+    \node[minimum height = 0.75cm, text width=6cm, text
+    centered, right of = representation, xshift = 2cm, rotate = 90] (mechanism) {choice mechanism};
+
+    \begin{pgfonlayer}{background}
+             \node [rounded corners, dashed,
+       very thick,draw=black!40,fit={($(situation.south)+(0,-10pt)$) 
+                                     ($(mechanism.west)+(+5pt,+42pt)$) 
+                                     % ($(action.north)+(0,+10pt)$) 
+                                     ($(representation.west)+(-7pt,0)$)
+                                   }] (box) {};
+    \end{pgfonlayer}
+
+  \end{scope}
+
+\end{tikzpicture}
+  \caption{bla bla bla}
+  \label{fig:ChoiceMechanism}
+\end{figure}
+
+\bigskip
+
+ To make an adaptationist argument precise, we need
+some
+
+ When it comes to preferences, this is clearly
+related to Alchian and Friedman's argument that firms \emph{should} optimize that which makes
+them ``live,'' so to speak. For biological agents, the argument would be that subjective
+preferences \emph{should} stay as close as possible to whatever determines objective fitness.
 

### 2015-12-17 paper/paper.tex
paper rewrite

@@
 conceptual issues whose complexity requires mathematical modelling at a high level of
-abstraction.  Abstraction entails simplifying assumptions. Evolutionary game models heavily
-simplify reality in many ways as well. Two simplifications relevant here are that the
-environment is represented as a fixed, closed and immutable \emph{stage game} and that the
-focus of evolutionary selection is behavior for this stage game alone. In contrast, some argue
-for studying instead the evolutionary competition of general \emph{choice mechanisms} in a rich
-and variable environment
+abstraction.  Abstraction entails simplifying assumptions. Evolutionary game models frequently
+simplify reality in two ways that are relevant for present purposes. Firstly, the environment
+is represented as a fixed, closed and immutable \emph{stage game}; secondly, the focus of
+evolutionary selection is behavior for this stage game alone. In contrast, some argue for
+studying instead the evolutionary competition of general \emph{choice mechanisms} in a rich and
+variable environment
 \citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche}. To show that
@@
 
-If agents deal with a rich and varied environment, they face many different choice
-situations. A crucial part of any choice mechanism is a \emph{subjective representation} of the
-choice situation, in particular a manner of forming preferences and beliefs about a possibly
-uncertain world. This paper asks: which preference and belief representations are ecologically
-valuable (i.e., lead to high fitness)? The evolution of preferences has been subject of recent
-interest in theoretical economics \citep[e.g.,][]{algweib13,DekElyYlan07,RobSam11}. The
-particular contribution of this paper is to provide a case, spelled out formally, that
-questions about the evolution of preferences cannot be separated from questions about the
-evolution of beliefs. As a point in case, we demonstrate that if agents have imprecise
-probabilistic beliefs \citep[e.g.][]{gardsah82,levi74,walley96}, preference representations in
-terms of regret that deviate from the
-true, objective fitness that evolutionary selection operates on can be selected for.
+If agents deal with a rich and variable environment, they face many different choice
+situations. A choice mechanism associates decision situations with action choices. A crucial
+part of any choice mechanism is a \emph{subjective representation} of the decision situation,
+in particular a manner of forming preferences and beliefs about a possibly uncertain world (see
+Figure~\ref{fig:ChoiceMechanism} below). This paper asks: which preference and belief
+representations are ecologically valuable (i.e., lead to high fitness)? The evolution of
+preferences has been subject of recent interest in theoretical economics
+\citep[e.g.,][]{algweib13,DekElyYlan07,RobSam11}. The particular contribution of this paper is
+to provide a case, spelled out formally, that questions of preference evolution should take
+variability in belief representation into account as well. As a point in case, we demonstrate
+that if agents have imprecise probabilistic beliefs \citep[e.g.][]{gardsah82,levi74,walley96},
+preference representations in terms of regret that deviate from the true, objective fitness
+that evolutionary selection operates on can be selected for.
 
@@
   references} Adaptationism aims to explain choice behavior by appeal to evolutionary
-considerations: DMs have acquired choice mechanisms that outperform other manners of choice
-making in a rich and variable environment. A choice mechanism could be a set of distinct
-heuristics (the DM's \emph{adaptive toolbox}) that have little in common
+considerations: DMs have acquired choice mechanisms that have proved to be adpative in a rich
+and variable environment. A choice mechanism could be a set of distinct heuristics (the DM's
+\emph{adaptive toolbox}) that have little in common
 \citep[e.g.,][]{TverskyKahnemann1981:The-Framing-of-,GigerenzerGoldstein1996:Reasoning-the-F,ScheibehenneRieskamp2013:Testing-the-Ada}. But
@@
 explicit level of subjective representation of a decision situation (see
-Figure~\ref{fig:ChoiceMechanism}).
+Figure~\ref{fig:ChoiceMechanism}). We are most interested in the question which subjective
+representation schemes, i.e., general ways of forming preferences and beliefs, are better than
+others.
 
@@
   \centering
-  \begin{tikzpicture}[node distance = 2.5cm]
+  \begin{tikzpicture}[node distance = 2.25cm]
 
@@
 
-    \node[rounded corners, draw, rectangle, minimum height = 0.75cm, text width=6cm, text centered, below of = representation] (action)
+    \node[rounded corners, draw, rectangle, minimum height = 0.75cm, text width=6cm, text
+    centered, below of = representation] (action)
     {\textbf{action choice} $a$ based on $s$};
@@
     \node[rounded corners, draw, rectangle, minimum height = 0.75cm, text width=6cm, text
-    centered, below of = action] (payoff) {\textbf{payoff} for $a$ in $d$};
+    centered, below of = action,node distance = 1.5cm] (payoff) {\textbf{payoff} for $a$ in $d$};
 
@@
        very thick,draw=black!40,fit={($(situation.south)+(0,-10pt)$) 
-                                     ($(mechanism.west)+(+5pt,+42pt)$) 
+                                     ($(mechanism.west)+(+5pt,+50pt)$) 
                                      % ($(action.north)+(0,+10pt)$) 
@@
 \end{tikzpicture}
-  \caption{bla bla bla}
+  \caption{Schematic representation of action choice. A choice mechanism maps decision
+    situation $d$ to action choice $a$ by way of representing $d$ in terms of subjective
+    preferences and subjective beliefs.}
   \label{fig:ChoiceMechanism}
 \end{figure}
+
+Fitness of a subjective representation scheme is measured in terms of the fitness of a
+choice mechanism that contains it, all else equal. Fitness of a choice mechanism $c$ is the
+expected payoff of $c$ over arbitrary decision situations $d$:
+\begin{align*}
+  F(c) = \int P(d) \  \utils(c,d) \text{ d} d \,,
+\end{align*}
+where $P(d)$ is the probability (density) of $d$ occurring, i.e., our model of the statistical
+properties of a rich and variable environment, and $\Utils(c,d)$ i the payoff of the
+act selected by $c$ in $d$.
+
+The same logic also applies to situations of social decision making. A game $g$ is also a
+decision situation, albeit a more complex one. A choice mechanism $c$ maps $g$ onto an action
+choice in $g$. The fitness of $c$ is then:
+\begin{align*}
+  F(c) = \int \int P(g) \  P(c') \  \utils(c,c',g) \text{ d} g \,,
+\end{align*}
+where $P(g)$ is the probability (density) of game $g$, $P(c')$ is the probability of
+encountering a co-player who uses choice mechanism $c'$ and $\utils(c,c',g)$ is the payoff for
+a $c$-player in $g$ against the $c'$-player, given by the payoff in $g$ of the actions that $c$
+and $c'$ select in $g$. For the most part, we will focus on the more complex case of social
+decision making here. Results about solitary decision making follow almost directly.
+
+\begin{itemize}
+\item meta-games
+\end{itemize}
+
+\bigskip
 
@@
 % The following subsection describes what these belief types are and how a single action
-% selection function (maxmin expected utility) gives rise to an intersting parallel with
+% selection function (maxmopin expected utility) gives rise to an intersting parallel with
 % classical choice rules.

### 2015-12-17 paper/paper.tex
minor edits

@@
 explicit level of subjective representation of a decision situation (see
-Figure~\ref{fig:ChoiceMechanism}). We are most interested in the question which subjective
-representation schemes, i.e., general ways of forming preferences and beliefs, are better than
-others.
+Figure~\ref{fig:ChoiceMechanism}). We are most interested in the question which
+\emph{subjective representation schemes}, i.e., general ways of forming preferences and
+beliefs, are better than others from an evolutionary point of view.
 
@@
 
-Fitness of a subjective representation scheme is measured in terms of the fitness of a
-choice mechanism that contains it, all else equal. Fitness of a choice mechanism $c$ is the
+The fitness of a subjective representation scheme is measured in terms of the fitness of a
+choice mechanism that contains it, all else equal. The fitness of a choice mechanism $c$ is the
 expected payoff of $c$ over arbitrary decision situations $d$:
-\begin{align*}
+\begin{align}
+  \label{eq:FittnessChoiceMechSolitary}
   F(c) = \int P(d) \  \utils(c,d) \text{ d} d \,,
-\end{align*}
-where $P(d)$ is the probability (density) of $d$ occurring, i.e., our model of the statistical
-properties of a rich and variable environment, and $\Utils(c,d)$ i the payoff of the
-act selected by $c$ in $d$.
+\end{align}
+where $P(d)$ is the probability (density) of $d$ occurring and $\Utils(c,d)$ i the payoff of
+the act selected by $c$ in $d$. Probability measure $P(d)$ is our model of the statistical
+properties of a rich and variable environment.
 
@@
 decision situation, albeit a more complex one. A choice mechanism $c$ maps $g$ onto an action
-choice in $g$. The fitness of $c$ is then:
-\begin{align*}
+choice in $g$. The fitness of $c$ is then:\footnote{We assume for simplicity of exposition that
+  all games with positive occurrence probability are two player games.}
+\begin{align}
+  \label{eq:FittnessChoiceMechGame}
   F(c) = \int \int P(g) \  P(c') \  \utils(c,c',g) \text{ d} g \,,
-\end{align*}
+\end{align}
 where $P(g)$ is the probability (density) of game $g$, $P(c')$ is the probability of
@@
 and $c'$ select in $g$. For the most part, we will focus on the more complex case of social
-decision making here. Results about solitary decision making follow almost directly.
+decision making here. Results about solitary decision making follow from parallel arguments
+(see Section~\ref{sec:extensions}).
+
+\emph{Meta games} are abstract models for the evolutionary competition between choice
+mechanisms in social decision making contexts. The expected payoff for a $c$-player of a random
+encounter with a $c'$-player is the average of payoffs obtained in a random game $g$ weighted
+by $g$'s occurrence probability:
+\begin{align}
+  F(c, c') = \int P(g) \  \utils(c,c',g) \text{ d} g \,.
+\end{align}
+A meta game is a strategic game whose action set is the set of competing choice mechanism and
+whose payoff function is $F(c,c')$ from above.
+
+\begin{definition}[Meta game]
+  \label{def:MetaGame}
+  Let $C$ be a set of choice mechanisms and let $P(g)$ give the occurrence probability of game
+  $g$ in the environment. The meta game for this case is one-population evolutionary game with
+  strategies $C$ and payoff function $\pi \mycolon C \times C \rightarrow \mathbb{R}$ such that
+  $\pi(c,c') = F(c,c') = \int P(g) \ \utils(c,c',g) \text{ d} g$.
+\end{definition}
+
+\bigskip
 
@@
 \item meta-games
+\item general schemes (for regularity)
+\item which schemes (for simplicity, yet interesting argument)
 \end{itemize}

### 2015-12-17 paper/paper.tex
sec com paper rewrite

@@
 
-\section{Rationality, subjective beliefs \& preferences and the evolution of choice mechanisms}
+\section{Rationality, subjective representation schemes \& meta games}
 \label{sec:rati--subj}
@@
   \label{eq:FittnessChoiceMechSolitary}
-  F(c) = \int P(d) \  \utils(c,d) \text{ d} d \,,
+  F(c) = \int P(d) \  \utils_d(c) \text{ d} d \,,
 \end{align}
-where $P(d)$ is the probability (density) of $d$ occurring and $\Utils(c,d)$ i the payoff of
+where $P(d)$ is the probability (density) of $d$ occurring and $\Utils_d(c)$ i the payoff of
 the act selected by $c$ in $d$. Probability measure $P(d)$ is our model of the statistical
@@
   \label{eq:FittnessChoiceMechGame}
-  F(c) = \int \int P(g) \  P(c') \  \utils(c,c',g) \text{ d} g \,,
+  F(c) = \int \int P(g) \  P(c') \  \utils_g(c,c') \text{ d} g \,,
 \end{align}
 where $P(g)$ is the probability (density) of game $g$, $P(c')$ is the probability of
-encountering a co-player who uses choice mechanism $c'$ and $\utils(c,c',g)$ is the payoff for
+encountering a co-player who uses choice mechanism $c'$ and $\utils_g(c,c')$ is the payoff for
 a $c$-player in $g$ against the $c'$-player, given by the payoff in $g$ of the actions that $c$
@@
 \emph{Meta games} are abstract models for the evolutionary competition between choice
-mechanisms in social decision making contexts. The expected payoff for a $c$-player of a random
+mechanisms in social decision making contexts. The expected payoff for a $c$-player in a random
 encounter with a $c'$-player is the average of payoffs obtained in a random game $g$ weighted
@@
 \begin{align}
-  F(c, c') = \int P(g) \  \utils(c,c',g) \text{ d} g \,.
+  F(c, c') = \int P(g) \  \utils_g(c,c') \text{ d} g \,.
 \end{align}
-A meta game is a strategic game whose action set is the set of competing choice mechanism and
-whose payoff function is $F(c,c')$ from above.
 
@@
   Let $C$ be a set of choice mechanisms and let $P(g)$ give the occurrence probability of game
-  $g$ in the environment. The meta game for this case is one-population evolutionary game with
-  strategies $C$ and payoff function $\pi \mycolon C \times C \rightarrow \mathbb{R}$ such that
-  $\pi(c,c') = F(c,c') = \int P(g) \ \utils(c,c',g) \text{ d} g$.
+  $g$ in the environment. The meta game that captures selection of choice mechanisms in this
+  environment is the one-population evolutionary game with strategies $C$ and payoff function
+  $\pi \mycolon C \times C \rightarrow \mathbb{R}$ such that
+  $\pi(c,c') = F(c,c')$.
 \end{definition}
 
-\bigskip
-
-\begin{itemize}
-\item meta-games
-\item general schemes (for regularity)
-\item which schemes (for simplicity, yet interesting argument)
-\end{itemize}
-
-\bigskip
-
-\bigskip
-
- To make an adaptationist argument precise, we need
-some
-
- When it comes to preferences, this is clearly
-related to Alchian and Friedman's argument that firms \emph{should} optimize that which makes
-them ``live,'' so to speak. For biological agents, the argument would be that subjective
-preferences \emph{should} stay as close as possible to whatever determines objective fitness.
-
-We would like to put this latter idea to the test. We present a formal argument intended to
-support the conclusion that subjective preferences that differ from objective fitness can be
-adaptive. We argue that it is important to take into account the potential mutual dependence of
-subjective preferences and subjective beliefs in adaptationist approaches to decision
-making. In other words, we focus on the evolutionary competition between \emph{subjective
-  representation schemes}: general ways of forming subjective preferences and
-subjective beliefs. We show that subjective, non-veridical preference representations based on
-a notion of regret \citep[e.g.,][]{Savage1951:The-theory-of-s,}
-can be adaptive and even outperform objective, veridical representations of the actual, true
-fitness, when agents, at least on occasion, hold \emph{imprecise probabilistic beliefs}
-\citep[e.g.,][]{gilsch89,levi74,gardsah82} and make decisions based on a security choice rule (here: the
-maxmin rule applied to expected utility). The next section introduces all these notions
-(precise/imprecise beliefs, veridical/regret representations, \dots) in detail.
-
-% The method by which we want to advance our argument is to integrate ideas from the recent
-% literature on preference evolution (CITE) with basic tenets of adaptationism: we are interested
-% in studying the evolutionary competition of choice mechanisms, conceived here as pairs of
-% subjective preference and subjective belief representations. Evolutionary competition between
-% choice mechanisms is driven by the expected objective fitness that each choice mechanisms
-% accrues when put to use repeatedly in a range of choice situations. We focus on the more
-% complex case of multi-agent decision making first, i.e., game situations. Solitary decision
-% making is then easy to deal with subsequently. The next section introduces the choice
-% mechanisms we focus on. After that, Section~\ref{sec:model} introduces the ``meta-game''
-% modeling approach.
+Standard notions of evolutionary game theory can be applied to meta games as well. A choice
+principle $c$ is a strict Nash equilibrium if $F(c,c) > F(c',c)$ for all $c'$; it is
+evolutionarily stable if for all $c'$ either (i) $F(c,c) > F(c',c)$ or (ii) $F(c,c) = F(c',c)$
+and $F(c,c') > F(c',c')$. It is neutrally stable if for all $c'$ either (i) $F(c,c) > F(c',c)$
+or (ii) $F(c,c) = F(c',c)$ and $F(c,c') \ge F(c',c')$. Similarly, evolutionary dynamics can be
+applied to meta games. We will later turn towards the replicator dynamic
+\citep{TaylorJonker1978:Evolutionary-St} and the replicator mutator dynamic
+\citep[e.g.][]{Nowak2006:Evolutionary-Dy}.\todo{footnote with caveat about agent-level
+  processes}
+
+We submit that meta games are a useful tool for structuring and sharpening conceptual inquiry
+in a domain, evolutionary justifications, that is notorious for its fuzziness and
+elusiveness. To show how this approach can be applied to benefit conceptual debate, we consider
+the evolution of preference. Concretely, we here pit two different ways of representing
+preferences against each other: (i) veridical representations that correctly reflect objective
+fitness, and (ii) non-veridical subjective preferences in terms of regret
+\citep[e.g.,][]{Savage1951:The-theory-of-s,}. We show that subjective, non-veridical preference
+representations based on a notion of regret can be adaptive and even outperform objective,
+veridical representations of the actual, true fitness, when agents, at least on occasion, hold
+\emph{imprecise probabilistic beliefs} \citep[e.g.,][]{gilsch89,levi74,gardsah82} and make
+decisions based on a security choice rule (here: the maxmin rule applied to expected
+utility).
+
+This case study strips the generality of a meta game approach down to a perspicuous comparison
+between only four choice mechanisms: the cross-product of two different preference
+representations (veridical vs.~regret) and two different belief representations (precise
+vs.~imprecise). The following section is dedicated to introduce and justify this exclusive
+selection.
 
@@
 
-A simultaneous-move game is a tuple $ G=\tuple{ N, (A_i , \pi_i)_{i \in N} }$ with $N$ a finite set of
-players, $A_i$ a finite set of acts and $\pi_i$ a payoff function for each player $i \in N$. For the
-most part, this paper will focus on symmetric games with two players. A two-player game is
-symmetric if players have the same action set, $A_1 = A_2$, and payoffs are symmetric:
-$\pi_1(a_k, a_j) = \pi_2(a_j, a_k)$ for all $a_j,a_k \in A_1$. An example is
-given in Figure~\ref{coordgame1}, which shows a coordination game. The numbers give the payoff
-for the player choosing a row act against an opponent choosing a column act. Since the game is
-symmetric, it suffices to give just these numbers.
-
-With some due simplification, there are two types of approaches to solving games. One looks at
-a collection of players (e.g., a whole population of them) and considers sets of choices of all
-players that are, in some sense or other, stable or in equilibrium. Another approach is to
-focus on each individual agent's perpective and specify which of her actions the agent
-\emph{should} choose if she is rational. We will look at the latter here; the former will be
-relevant only later, when turn to evolutionary competition between choice mechanisms in
-Section~\ref{sec:model}. We will first look at what we call \emph{choice rules}: classical
-proposals of how rational agents should choose acts. We will then introduce our notion of
-\emph{choice mechanism} which makes explicit several elements that choice rules might brush
-under the table, in particular the crucial notion of a subjective representation scheme whose
-evolutionary selection we are most interested in.
-
-\subsection{Choice rules} 
+\subsection{Classical rules for rational choice} 
 \label{sec:choice-rules}
 
-For the purposes of this paper, we think of a choice rule as a function that takes a
-(strategic) game as input and outputs a choice of action for that game. The literature has
-suggested a number of choice rules that aspire to capture a normative element of rational
-choice. We focus here on three classical choice rules: (i) maxmin, (ii) Laplace and (iii)
-regret minimization.
+The classical literature on rational choice contains a number of proposals for which acts a
+player \emph{should} choose if she is rational. Maximization of expected utilities, as
+given in Definition~\ref{def:rationality}, is only one of them. Here, we consider three others:
+(i) maxmin, (ii) Laplace's rule and (iii) regret minimization. All of these apply to games and
+solitary decision situations. We focus on games, but definitions carry over straightforwardly.
+
+A strategic game is a tuple $ G=\tuple{ N, (A_i , \pi_i)_{i \in N} }$ with $N$ a finite set of
+players, $A_i$ a finite set of acts and $\pi_i$ a payoff function for each player $i \in N$.
+For the most part, this paper will focus on symmetric games with two players. A two-player game
+is symmetric if players have the same action set, $A_1 = A_2$, and payoffs are symmetric:
+$\pi_1(a_k, a_j) = \pi_2(a_j, a_k)$ for all $a_j,a_k \in A_1$. An example is given in
+Figure~\ref{coordgame1}. The numbers give the payoff for the player choosing a row act against
+an opponent choosing a column act. Since the game is symmetric, it suffices to give just these
+numbers.
 
 Rational choice from maximization of expected utilities, as given in
-Definition~\ref{def:rationality}, is \emph{not} a choice rule in the present sense. Although
-the notion applies to game situations, it requires an additional component, namely a
-belief of the DM, before it can say which acts the DM should choose. Let
-$A_{-i} = \bigtimes A_j$ for all $j \neq i$ be the set of all \emph{profiles} of acts for all
-players except $i$. If player $i$ has a belief $\mu_i \in \Delta(A_{-i})$ about the behavior of
-his opponents, he chooses rationally only if his choice $a^*_i$ maximizes expected utility
-$\EU(a_i) := \sum_{\act_{-i} \in \Acts_{-i}} \mu_i(\act_{-i}) \myts \pi_i(a_i, a_{-i})$. So this
-requires a probabilistic belief about the opponents' action choices. In the example from
+Definition~\ref{def:rationality}, applies to games. To say which acts are rational, it requires
+specifying a belief of the DM. Let $A_{-i} = \bigtimes A_j$ for all $j \neq i$ be the set of
+all \emph{profiles} of acts for all players except $i$. If player $i$ has a belief
+$\mu_i \in \Delta(A_{-i})$ about the behavior of his opponents, he chooses rationally only if
+his choice $a^*_i$ maximizes expected utility
+$\EU(a_i) := \sum_{\act_{-i} \in \Acts_{-i}} \mu_i(\act_{-i}) \myts \pi_i(a_i, a_{-i})$. So
+this requires a probabilistic belief about the opponents' action choices. In the example from
 Figure~\ref{coordgame1}, a rational player would choose act $I$ exactly when he believes that
-his opponent will choose act $I$ with a probability at least $\nicefrac{2}{3}$.
+his opponent will choose act $I$ with a probability of at least $\nicefrac{2}{3}$.
 
@@
 Another well-known choice rule is \emph{Laplace's rule} which prescribes to choose $\act^*$ if
-$\act^* \in \argmax_{a \in A} \sum_{a'} \pi(a, a')$. Laplace's rule is equivalent to expected utility maximization under a \emph{flat belief} that assigns equal probability to all of the opponent's
-choices. In the coordination game of Figure~\ref{coordgame1}, Laplace's rule selects act $II$.
+$\act^* \in \argmax_{a \in A} \sum_{a'} \pi(a, a')$. Laplace's rule is equivalent to expected
+utility maximization under a \emph{flat belief} that assigns equal probability to all of the
+opponent's choices. In the coordination game of Figure~\ref{coordgame1}, Laplace's rule selects
+act $II$.\todo{definitions for maxmin and Laplace are for 2 player games only; rest for
+  $n$-players; fix!}
 
@@
   \end{subfigure}
-  \caption{A coordination game (left) and regrets associated with each row-player acts (right).}
+  \caption{A coordination game (left) and regrets associated with the row player's acts (right).}
     \label{coordgame1mainFig}
@@
 
-This means that we can think of the maxmin rule and regret minimization as essentially the
-same operation on different subjective representations of preference: while maxmin considers
-actual objective payoffs (as defined by the modeller's game), regret minimization considers
-non-veridical, regret-based subjective preferences. As the example of Figure~\ref{coordgame1}
-shows, different subjective preferences can give rise to different choice prescriptions all
-else equal. While maxmin is indifferent between $I$ and $II$, regret minimization uniquely
-selects $II$.
-
-In sum, a choice rule is a normative prescription of action choices for a rational agent in any
-game situation. Choice rules may rest on implicit assumptions about what the DM believes (e.g.,
-when interpreting Laplace rule as rational choice under flat beliefs). They may also make
-implicit assumptions about what the DM prefers (e.g., when reconstructing regret minimization
-in terms of maxmin-choices on the regret transformation). This is rather messy. To disentangle
-and avoid confusion, we turn to choice mechanisms.
+This means that we can think of the maxmin rule and regret minimization as essentially the same
+operation on different subjective representations of preference: while maxmin considers actual
+objective payoffs, regret minimization considers non-veridical, regret-based subjective
+preferences. As the example of Figure~\ref{coordgame1} shows, different subjective preferences
+can give rise to different choice prescriptions all else equal. While maxmin is indifferent
+between $I$ and $II$, regret minimization uniquely selects $II$.
+
+In sum, classical proposals for rational choice are normative prescription of action choices
+for a rational agent. Such prescriptions may rest on implicit assumptions about what the DM
+believes (e.g., when interpreting Laplace's rule as rational choice under flat beliefs). They may
+also make implicit assumptions about what the DM prefers (e.g., when reconstructing regret
+minimization in terms of maxmin-choices on the regret transformation). This is rather messy. To
+disentangle and avoid confusion, we turn to choice mechanisms.
 
@@
 rules, contains an explicit level of subjective representation of a decision situation. For our
-purposes, we should think of a choice mechanism as a pair of functions ($\gamma,\kappa$),
-where $\gamma$ is a \emph{subjective representation scheme} and $\kappa$ is an \emph{action
-  selection function} (see FigureXYZ).\todo{make figure when notation and terminology are
-  fixed}\ The subjective representation scheme $\gamma$ maps a game (or more generally any
-choice situation) onto a subjective representation of the game (or choice situation) and
-other decision-relevant beliefs (e.g., about what the opponent is likely to play). The action
-selection function $\kappa$ takes such a subjective representation that $\gamma$ returns and
-maps it onto a concrete action choice. The crucial bit for our purposes here is the
-representation function $\gamma$, because we are interested in studying which ways of
-conceptualizing a decision situation are evolutionarily successful.
-
-A choice mechanism could be a set of distinct heuristics (the DM's \emph{adaptive toolbox})
-that have little in common
-\citep[e.g.,][]{TverskyKahnemann1981:The-Framing-of-,GigerenzerGoldstein1996:Reasoning-the-F,ScheibehenneRieskamp2013:Testing-the-Ada}. But
-to keep matters simple and implementable for a start, we will here only look at choice
-mechanisms that differ only with respect to their subjective representation function $\gamma$,
-which in turn is conceived of as a \emph{uniform} way of forming preference and belief
-\emph{types}: we look at general \emph{subjective representation schemes}.
-
-Formally, given a class $ \mathcal{G} $ of strategic games,
-$\gamma_i: \mathcal{G} \rightarrow \Theta \times E$ is a function that assigns a subjective
-preference $\theta \in \Theta$ and an epistemic state $e \in E$ to any game
-$G \in \mathcal{G}$ for some agent $i$.
-A subjective preference $\theta$ for game $G$ is just a subjective utility function $\theta:A \rightarrow \mathbb{R}$.
-Crucially, this subjective utility function can be different from the actual payoff function $\pi^G$ of $G$,
-which we interpret as the objective evolutionary fitness. An epistemic state $e$ for game $G$ is some specification of a player's uncertainty about the co-players' behavior. Finally, an
+purposes, we should think of a choice mechanism as a pair of functions ($\gamma,\kappa$), where
+$\gamma$ is a \emph{subjective representation scheme} and $\kappa$ is an \emph{action selection
+  function} (see Figure~\ref{fig:ChoiceMechanism}). The subjective representation scheme
+$\gamma$ maps a decision situation onto a subjective representation of that decision
+situation. The action selection function $\kappa$ maps such a subjective representation onto a
+concrete action choice.
+
+% The crucial bit for our purposes here is the representation function
+% $\gamma$, because we are interested in studying which ways of conceptualizing a decision
+% situation are evolutionarily successful.
+
+Formally, given a class $\mathcal{G} $ of strategic games, the subjective representation scheme
+for agent $i$ is a function $\gamma_i: \mathcal{G} \rightarrow \Theta \times E$ that gives a
+subjective preference $\theta \in \Theta$ and an epistemic state $e \in E$ for any game
+$G \in \mathcal{G}$. A subjective preference $\theta$ for game $G$ and agent $i$ is just a
+utility function for $G$. This can but need not be different from the actual payoff function of
+$G$, which we interpret as the objective evolutionary fitness. An epistemic state $e$ for game
+$G$ is some specification of a player's uncertainty about the co-players' behavior. Finally, an
 action selection function for agent $i$ is a function
 $\kappa_i: \Theta \times E \rightarrow \pow{A_i} $, that associates any subjective
-representation of the game $ (\theta,e) \in \Theta \times E$ with a set of prescribed
-actions for $i$ in $G$ under $i$'s subjective representation of $G$. We drop the index $i$ for
+representation of the game $ (\theta,e) \in \Theta \times E$ with a set of prescribed actions
+for $i$ in $G$ under $i$'s subjective representation of $G$. We drop the index $i$ for
 readability in the following.
+
+\bigskip
+
+To keep matters simple the focus is on \emph{uniform}
+and \emph{general} ways of forming preference and beliefs consistently across decision
+situations.
+
+\bigskip
 

### 2015-12-17 paper/paper.tex
sec com paper rewrite

@@
 
-Formally, given a class $\mathcal{G} $ of strategic games, the subjective representation scheme
+Formally, given a class of strategic games $\mathcal{G}$, the subjective representation scheme
 for agent $i$ is a function $\gamma_i: \mathcal{G} \rightarrow \Theta \times E$ that gives a
 subjective preference $\theta \in \Theta$ and an epistemic state $e \in E$ for any game
-$G \in \mathcal{G}$. A subjective preference $\theta$ for game $G$ and agent $i$ is just a
-utility function for $G$. This can but need not be different from the actual payoff function of
-$G$, which we interpret as the objective evolutionary fitness. An epistemic state $e$ for game
-$G$ is some specification of a player's uncertainty about the co-players' behavior. Finally, an
-action selection function for agent $i$ is a function
+$G \in \mathcal{G}$. A subjective preference $\theta$ for $G$ and $i$ is just a utility
+function for $G$. This can but need not be different from the actual payoff function of $G$. An
+epistemic state $e$ for $G$ and $i$ is some specification of $i$'s uncertainty about the
+co-players' behavior. Finally, an action selection function for agent $i$ is a function
 $\kappa_i: \Theta \times E \rightarrow \pow{A_i} $, that associates any subjective
-representation of the game $ (\theta,e) \in \Theta \times E$ with a set of prescribed actions
+representation $\gamma_i(G) = (\theta,e)$ of $G$ with a set of prescribed actions
 for $i$ in $G$ under $i$'s subjective representation of $G$. We drop the index $i$ for
@@
 
-\bigskip
-
-To keep matters simple the focus is on \emph{uniform}
-and \emph{general} ways of forming preference and beliefs consistently across decision
-situations.
-
-\bigskip
-
-We focus on two (\textit{subjective}) \emph{preference types} and two \emph{belief types}. We
-view a preference type as a function $\tau: \mathcal{G} \rightarrow \Theta$, and a belief type
-as a general disposition to form beliefs about the co-player’s behavior. The two possible
-dispositions that we take account of are precise probabilistic belief and imprecise belief, as
-we will explain in the next section. Since we are most interested here in studying whether
-evolutionary pressure could support non-veridical subjective preferences, the two preference
-types that we consider are: the veridical type $\tau^\pi$, who uses the actual payoff function
-$\pi$ of the actual game $G$, and the regret type $\tau^{reg}$, who looks at the regret
-transformation of the actual game $G$. Finally, the action selection function $\kappa$ that we
-use in this paper is \textit{maxmin expected utility} \citep{gilsch89}, for reasons that will be clear
-and justified in the following two sections.
+To keep matters simple the focus is on \emph{uniform} and \emph{general} ways of forming
+preferences and beliefs consistently across decision situations. We consider two
+\emph{preference types} and two \emph{belief types}: subjective preferences either coincide
+with the actual, true payoffs or are given by the regret transformation of the actual game;
+beliefs are either precise probabilistic beliefs modelled by a single probability distribution,
+or they are imprecise probabilistic beliefs modelled by a set of probability distributions. The
+action selection function $\kappa$ is fixed to \textit{maxmin expected utility}
+\citep{gilsch89}, for reasons explained in the following.
 

### 2015-12-18 paper/paper.tex
sec com

@@
 that if agents have imprecise probabilistic beliefs \citep[e.g.][]{gardsah82,levi74,walley96},
-preference representations in terms of regret that deviate from the true, objective fitness
-that evolutionary selection operates on can be selected for.
+preference representations in terms of regret can be selected for, even though they may deviate
+from the true, objective fitness that evolutionary selection operates on.
 
@@
 \end{align}
-where $P(d)$ is the probability (density) of $d$ occurring and $\Utils_d(c)$ i the payoff of
+where $P(d)$ is the probability (density) of $d$ occurring and $\Utils_d(c)$ is the payoff of
 the act selected by $c$ in $d$. Probability measure $P(d)$ is our model of the statistical
@@
   $\pi \mycolon C \times C \rightarrow \mathbb{R}$ such that
-  $\pi(c,c') = F(c,c')$.
+  $\pi(c,c') = F(c,c') = \int P(g) \  \utils_g(c,c') \text{ d} g$.
 \end{definition}
@@
 
+\section{Choice mechanisms: preferences, beliefs and action choice}
+\label{sec:basic-notions}
+
 We submit that meta games are a useful tool for structuring and sharpening conceptual inquiry
-in a domain, evolutionary justifications, that is notorious for its fuzziness and
-elusiveness. To show how this approach can be applied to benefit conceptual debate, we consider
-the evolution of preference. Concretely, we here pit two different ways of representing
-preferences against each other: (i) veridical representations that correctly reflect objective
-fitness, and (ii) non-veridical subjective preferences in terms of regret
+in a domain that is notorious for its fuzziness and elusiveness. To show how this approach can
+be applied to the benefit of conceptual debate, we consider the evolution of preference
+\citep[e.g.,][]{algweib13,DekElyYlan07,RobSam11}. Concretely, we here pit two different ways of
+representing preferences against each other: (i) veridical representations that correctly
+reflect objective fitness, and (ii) non-veridical subjective preferences in terms of regret
 \citep[e.g.,][]{Savage1951:The-theory-of-s,}. We show that subjective, non-veridical preference
@@
 decisions based on a security choice rule (here: the maxmin rule applied to expected
-utility).
-
-This case study strips the generality of a meta game approach down to a perspicuous comparison
-between only four choice mechanisms: the cross-product of two different preference
-representations (veridical vs.~regret) and two different belief representations (precise
-vs.~imprecise). The following section is dedicated to introduce and justify this exclusive
-selection.
-
-\section{Choice mechanisms: preferences, beliefs and action choice}
-\label{sec:basic-notions}
-
-\subsection{Classical rules for rational choice} 
+utility). This case study strips the generality of a meta game approach down to a perspicuous
+comparison between only four choice mechanisms, summarized in Table~\ref{tab:CMs}: the
+cross-product of two different preference representations (veridical vs.~regret) and two
+different belief representations (precise vs.~imprecise).
+
+\begin{table}[t]
+  \centering
+  \begin{tabular}{cccc}
+    \multicolumn{2}{c}{subjective representation} & action selection & corresponding choice
+    rule \\  \cmidrule(r){1-2}
+    preference type & belief type  \\ \midrule
+    objective fitness & precise & maxmin EU &  Laplace \\
+    objective fitness & precise & maxmin EU & maxmin \\ 
+    regret & imprecise & maxmin EU & Laplace \\
+    regret & imprecise & maxmin EU & regret minimization \\ 
+  \end{tabular}
+  \caption{Overview relevant choice mechanisms and the corresponding (behaviorally equivalent)
+    classic choice rules. All notions are explained in the main text.}
+  \label{tab:CMs}
+\end{table}
+
+This exclusive selection of choice mechanisms is motivated by a number of
+considerations. Firstly, the set of conceivable choice mechanisms is vast. Most of that
+conceivable vastness is utter nonsense. Some selection of plausible candidates is required in
+any case. Secondly, a severe restriction to only a small number of suitable candidates will
+help demonstrate more distinctly how a meta game approach may help structure philosophical
+inquiry. This is our main goal. Thirdly, our case study adds to the recent literature on the
+evolution of preferences by clearly demonstrating the possibly non-trivial interaction between
+preference and belief representations, all else equal. This is our secondary goal. Finally, the
+four choice mechanism that we look at here, although phrased in terms of preference and belief
+representations, map onto well-known classic proposals for rational choice (see
+Table~\ref{tab:CMs}). In other words, there is also an argument by historical relevance for our
+selection. To see this, we first recapitulate the relevant classics ---to have a handy label,
+we call them \emph{classic rules}--- and then show how they relate to our notion of choice
+mechanism.
+
+\subsection{Classic rules for rational choice} 
 \label{sec:choice-rules}
 
-The classical literature on rational choice contains a number of proposals for which acts a
-player \emph{should} choose if she is rational. Maximization of expected utilities, as
+The classic literature on rational choice contains a number of proposals for which acts a
+player should choose if she is rational. Maximization of expected utilities, as
 given in Definition~\ref{def:rationality}, is only one of them. Here, we consider three others:
@@
 players, $A_i$ a finite set of acts and $\pi_i$ a payoff function for each player $i \in N$.
-For the most part, this paper will focus on symmetric games with two players. A two-player game
-is symmetric if players have the same action set, $A_1 = A_2$, and payoffs are symmetric:
+Part of this paper will focus on symmetric games with two players. A two-player game is
+symmetric if players have the same action set, $A_1 = A_2$, and payoffs are symmetric:
 $\pi_1(a_k, a_j) = \pi_2(a_j, a_k)$ for all $a_j,a_k \in A_1$. An example is given in
@@
 Rational choice from maximization of expected utilities, as given in
-Definition~\ref{def:rationality}, applies to games. To say which acts are rational, it requires
-specifying a belief of the DM. Let $A_{-i} = \bigtimes A_j$ for all $j \neq i$ be the set of
-all \emph{profiles} of acts for all players except $i$. If player $i$ has a belief
+Definition~\ref{def:rationality}, applies to games as follows. To say which acts are rational,
+it requires specifying a belief of the DM. Let $A_{-i} = \bigtimes A_j$ for all $j \neq i$ be
+the set of all \emph{profiles} of acts for all players except $i$. If player $i$ has a belief
 $\mu_i \in \Delta(A_{-i})$ about the behavior of his opponents, he chooses rationally only if
 his choice $a^*_i$ maximizes expected utility
-$\EU(a_i) := \sum_{\act_{-i} \in \Acts_{-i}} \mu_i(\act_{-i}) \myts \pi_i(a_i, a_{-i})$. So
-this requires a probabilistic belief about the opponents' action choices. In the example from
-Figure~\ref{coordgame1}, a rational player would choose act $I$ exactly when he believes that
-his opponent will choose act $I$ with a probability of at least $\nicefrac{2}{3}$.
-
-Perhaps the most well-known choice rule that does not require explicitly stating the DM's
+$\EU(a_i) := \sum_{\act_{-i} \in \Acts_{-i}} \mu_i(\act_{-i}) \myts \pi_i(a_i, a_{-i})$. For
+the example in Figure~\ref{coordgame1}, a rational player would choose act $I$ exactly when he
+believes that his opponent will choose act $I$ with a probability of at least
+$\nicefrac{2}{3}$.
+
+Perhaps the most well-known classic rule that does not require explicitly stating the DM's
 beliefs is the \emph{maxmin rule}. It tells our agent to choose act $\act^*$ only if it
-maximizes payoffs for all worst case scenarios. For a strategic game with 2 players this can be
-formalized as
-$\act^* \in \argmax_{\myact{i} \in \Acts_i} \min_{\myact{j} \in \Acts_j} \pi_i(\myact{i},
-\myact{j})$.
+maximizes payoffs for all worst case scenarios:
+$\act^* \in \argmax_{\myact{i} \in \Acts_i} \min_{\myact{-i} \in \Acts_{-1}} \pi_i(\myact{i},
+\myact{-1})$.
 For the example in Figure~\ref{coordgame1}, the maximim rule looks at the minima in each row,
 asking: what is the worst possible outcome for each row act? It is $0$ in either
-case. Consequently, the maxmin rule would not favor either act: players choosing by the
-maxmin rule would be indifferent between acts $I$ and $II$.
-
-Another well-known choice rule is \emph{Laplace's rule} which prescribes to choose $\act^*$ if
-$\act^* \in \argmax_{a \in A} \sum_{a'} \pi(a, a')$. Laplace's rule is equivalent to expected
-utility maximization under a \emph{flat belief} that assigns equal probability to all of the
-opponent's choices. In the coordination game of Figure~\ref{coordgame1}, Laplace's rule selects
-act $II$.\todo{definitions for maxmin and Laplace are for 2 player games only; rest for
-  $n$-players; fix!}
-
-The final choice rule that is relevant for our purposes here is \emph{regret
+case. Consequently, the maxmin rule would not favor either act: players choosing by the maxmin
+rule would be indifferent between acts $I$ and $II$.
+
+\emph{Laplace's rule} selects $\act^*$ if
+$\act^* \in \argmax_{\myact{-i} \in \Acts_{-i}} \sum_{\myact{-i}} \pi(\myact{i}, \myact{-i})$.
+Laplace's rule is equivalent to expected utility maximization under a \emph{flat belief} that
+assigns equal probability to all of the opponents' choices. In the coordination game of
+Figure~\ref{coordgame1}, Laplace's rule selects act $II$.
+
+The final classic rule that is relevant for our purposes here is \emph{regret
   minimization}. The notion of regret in decision theory dates back at least to the work by
@@
 \noindent Acts selected by the maxmin rule for the negative regret transformation of $G$ are
-always exactly the acts selected by regret minimization for the original game $G$.\todo{can we
-  cite a paper that proves this? should we give a proof ourselves?}
+always exactly the acts selected by regret minimization for the original game $G$.
 
@@
 
-In sum, classical proposals for rational choice are normative prescription of action choices
+In sum, classic proposals for rational choice are normative prescription of action choices
 for a rational agent. Such prescriptions may rest on implicit assumptions about what the DM
@@
 
-A \emph{choice mechanism} is a map from choice situations to action choices that, unlike choice
-rules, contains an explicit level of subjective representation of a decision situation. For our
-purposes, we should think of a choice mechanism as a pair of functions ($\gamma,\kappa$), where
-$\gamma$ is a \emph{subjective representation scheme} and $\kappa$ is an \emph{action selection
-  function} (see Figure~\ref{fig:ChoiceMechanism}). The subjective representation scheme
-$\gamma$ maps a decision situation onto a subjective representation of that decision
-situation. The action selection function $\kappa$ maps such a subjective representation onto a
-concrete action choice.
-
-% The crucial bit for our purposes here is the representation function
-% $\gamma$, because we are interested in studying which ways of conceptualizing a decision
-% situation are evolutionarily successful.
+A \emph{choice mechanism} is a map from choice situations to action choices that, unlike the
+classic rules visited above, contains an explicit level of subjective representation of a
+decision situation. Let us think of a choice mechanism as a pair of functions
+($\gamma,\kappa$), where $\gamma$ is a \emph{subjective representation scheme} and $\kappa$ is
+an \emph{action selection function} (see Figure~\ref{fig:ChoiceMechanism}).
+
+The subjective representation scheme $\gamma_i$ of agent $i$ is a function $\gamma_i$ that
+takes a strategic game $G = \tuple{ N, (A_i , \pi_i)_{i \in N} }$ and maps it onto
+$\gamma_i(G) = (\theta, e_i)$ where
+$\theta \mycolon \bigtimes_{i \in N} A_i \rightarrow \mathbb{R}$ is a (subjective) payoff
+function for agent $i$ suitable for $G$.
+
+$\mathcal{G} \rightarrow \Theta \times E$, where $\mathcal{G}$ is a class of
 
@@
 epistemic state $e$ for $G$ and $i$ is some specification of $i$'s uncertainty about the
-co-players' behavior. Finally, an action selection function for agent $i$ is a function
+co-players' behavior.
+
+\bigskip
+
+The action selection function $\kappa$ maps such a subjective representation onto a concrete
+action choice. An action selection function for agent $i$ is a function
 $\kappa_i: \Theta \times E \rightarrow \pow{A_i} $, that associates any subjective
-representation $\gamma_i(G) = (\theta,e)$ of $G$ with a set of prescribed actions
-for $i$ in $G$ under $i$'s subjective representation of $G$. We drop the index $i$ for
-readability in the following.
+representation $\gamma_i(G) = (\theta,e)$ of $G$ with a set of prescribed actions for $i$ in
+$G$ under $i$'s subjective representation of $G$. We drop the index $i$ for readability in the
+following.
 
@@
 % selection function (maxmopin expected utility) gives rise to an intersting parallel with
-% classical choice rules.
+% classic choice rules.
 
@@
 
-\subsection{Choice mechanisms \& classical choice rules}
+\subsection{Choice mechanisms \& classic choice rules}
 
@@
 either in a restricted class of games, or in general. This is also the case here.
-
-\begin{table}[t]
-  \centering
-  \begin{tabular}{ccc}
-    preference type & belief type & corresponding choice rule \\ \midrule
-    $\tau^\pi$ & $\overline{\mu}$ & Laplace \\
-    $\tau^\pi$ & $\Delta$ & maxmin \\ 
-    $\tau^{reg}$ & $\overline{\mu}$ & Laplace \\
-    $\tau^{reg}$ & $\Delta$ & regret minimization \\ 
-  \end{tabular}
-  \caption{Overview relevant choice mechanisms and the corresponding (behaviorally equivalent) classical choice rule}
-  \label{tab:CMs}
-\end{table}
 
@@
 \item We argue that this ``meta-evolutionary'' approach could eventually help explain attested
-  deviations of human decision making from the classical ideal: choice behavior evolved to be
+  deviations of human decision making from the classic ideal: choice behavior evolved to be
   an ``ecologically rational'', near-optimal adaptation to the environment
@@
   \item We argue that this ``meta-evolutionary'' approach could eventually help explain
-    attested deviations of human decision making from the classical ideal: choice behavior
+    attested deviations of human decision making from the classic ideal: choice behavior
     evolved to be an ``ecologically rational'', near-optimal adaptation to the environment

### 2015-12-18 paper/paper.tex
sec com

@@
 A \emph{choice mechanism} is a map from choice situations to action choices that, unlike the
-classic rules visited above, contains an explicit level of subjective representation of a
-decision situation. Let us think of a choice mechanism as a pair of functions
+classic choice rules visited above, contains an explicit level of subjective representation of
+a decision situation. Let us think of a choice mechanism as a pair of functions
 ($\gamma,\kappa$), where $\gamma$ is a \emph{subjective representation scheme} and $\kappa$ is
@@
 $\gamma_i(G) = (\theta, e_i)$ where
-$\theta \mycolon \bigtimes_{i \in N} A_i \rightarrow \mathbb{R}$ is a (subjective) payoff
-function for agent $i$ suitable for $G$.
-
-$\mathcal{G} \rightarrow \Theta \times E$, where $\mathcal{G}$ is a class of
-
-Formally, given a class of strategic games $\mathcal{G}$, the subjective representation scheme
-for agent $i$ is a function $\gamma_i: \mathcal{G} \rightarrow \Theta \times E$ that gives a
-subjective preference $\theta \in \Theta$ and an epistemic state $e \in E$ for any game
-$G \in \mathcal{G}$. A subjective preference $\theta$ for $G$ and $i$ is just a utility
-function for $G$. This can but need not be different from the actual payoff function of $G$. An
-epistemic state $e$ for $G$ and $i$ is some specification of $i$'s uncertainty about the
-co-players' behavior.
-
-\bigskip
-
-The action selection function $\kappa$ maps such a subjective representation onto a concrete
-action choice. An action selection function for agent $i$ is a function
-$\kappa_i: \Theta \times E \rightarrow \pow{A_i} $, that associates any subjective
-representation $\gamma_i(G) = (\theta,e)$ of $G$ with a set of prescribed actions for $i$ in
-$G$ under $i$'s subjective representation of $G$. We drop the index $i$ for readability in the
-following.
-
-To keep matters simple the focus is on \emph{uniform} and \emph{general} ways of forming
-preferences and beliefs consistently across decision situations. We consider two
-\emph{preference types} and two \emph{belief types}: subjective preferences either coincide
-with the actual, true payoffs or are given by the regret transformation of the actual game;
-beliefs are either precise probabilistic beliefs modelled by a single probability distribution,
-or they are imprecise probabilistic beliefs modelled by a set of probability distributions. The
-action selection function $\kappa$ is fixed to \textit{maxmin expected utility}
-\citep{gilsch89}, for reasons explained in the following.
-
-% It turns out that whether $\tau^{reg}$ can have a fitness advantage over $\tau^\pi$ depends on
-% the general \emph{kind} of (probabilistic) beliefs that DM's form about the opponent's
-% behavior. In other words, we even abstract away from the content of the DM's beliefs about his
-% opponents' behavior that he could have acquiresd by learning or observation, but first turn on
-% the more general question of how uncertainty should be represented in order to interact with
-% subjective preferences in such a way that the resulting behavior will be fitness enhancing for
-% the DM in the long run. We consider therefore two \emph{belief types} (to be defined below):
-% imprecise belief types $\Delta(A_{-i})$, who have a set of probabilistic beliefs about the
-% opponents' behavior and precise belief types $\overline{\mu}$ who have a single probabilistic
-% belief.
-
-% The following subsection describes what these belief types are and how a single action
-% selection function (maxmopin expected utility) gives rise to an intersting parallel with
-% classic choice rules.
+$\theta \mycolon \bigtimes_{i \in N} A_i \rightarrow \mathbb{R}$ is payoff function suitable
+for $G$, and $e_i$ is some representation of $i$'s uncertainty about the co-player's
+behavior. We consider two \emph{preference types}: the \emph{objective type} maps each game
+onto its own, true payoff function; The \emph{regret type} maps each game onto its regret
+transformation, as introduced above. We also consider two \emph{belief types}: the
+\emph{precise type} represents uncertainty in a single probability distribution
+$\mu_i \in \Delta(\Acts_{-i})$ about the co-players' behavior; the \emph{imprecise type}
+represents uncertainty as a set of probability distributions $X \subseteq \Delta(\Acts_{-i})$.
+It is convenient to conceptualize precise beliefs as a special case of imprecise beliefs by
+looking at $\mu_i$ as a stand-in for the singleton set $\set{\mu_i}$. More details about
+imprecise probabilities and our initial assumption of ignorance are given in
+Section~\ref{sec:impr-prob-beli} below.
+
+The only action choice function $\kappa$ that we consider here is \emph{maximinimization of
+  expected (subjective) utilities} (see Section~\ref{sec:impr-prob-beli} for
+motivation).
+
+\begin{definition}[Maximinimization of expected (subjective) utility]
+  \label{def:maxminSEU}
+  Fix a strategic game $G$. Let agent $i$'s subjective representation scheme
+  $\gamma_i(G) = (\theta, e_i)$ be such that $\theta$ is $i$'s subjective payoff function for
+  $G$ and $e_i$ is a (possibly singleton) set of probability distributions in
+  $\Delta(\Acts_{-i})$. Agent $i$'s expected (subjetive) utility for act $\myact{i}$ and
+  $\mu \in e$ is
+  $\EU(\myact{i}, \mu) = \sum_{\myact{-i} \in \Acts_{-i}} \mu(\myact{-i}) \theta(\myact{i},
+  \myact{-i})$.
+  Act $\myact{i}^*$ is selected by maximinimization of expected (subjective) utility iff:
+  $\myact{i}^* \in \arg \max_{\myact{i} \in \Acts_{i}} \min_{\mu \in e} \EU(\myact{i}, \mu)$.
+\end{definition}
+
+Maximinimization under a precise (singleton set) probabilistic belief is just standard
+maximization of expected utilities. Moreover, given the same precise (singleton set)
+probabilistic belief, the choices of objective and regret preference types are exactly the
+same.
+
+\begin{fact} \label{fact:maxEU-minReg} For any strategic game $G$ and any arbitrary precise
+  (singleton set) probabilistic belief about the opponents' behavior, the acts selected by
+  maximization of expected utility for $G$ are exactly the acts selected by the maximization of
+  expected utility for the negative regret transformation of $G$
+  \citep[e.g.,][]{HalpernPass2012:Iterated-Regret}. This also holds for solitary decision
+  problems.
+\end{fact}
+
+This means that as far as behavior is concerned, regret types cannot be distinguished from
+objective types, as long as both hold precise beliefs. This will be central in understanding
+later results: under precise beliefs evolution will not favor either preference type over the
+other. On the other hand, if paired with imprecise beliefs, different behavioral predictions
+arise. However, in the special case of $2 \times 2$ symmetric games, another noteworthy general
+result holds.
+
+\begin{fact} \label{fact:equivalence2x2} In the class of $2 \times 2$ symmetric games, acts
+  selected by Laplace's rule are exactly the acts selected by regret minimization. 
+\end{fact}
+
+In the following, we assume that agents are maximally ignorant, so that precise types have a
+(singleton set containing a) flat probability distribution
+$\overline{\mu}_i \in \Delta(\Acts_{-i})$ and imprecise types consider all probabilistic
+beliefs about the co-players' behavior $\overline{X} = \Delta(\Acts_{-i})$. In that case, the
+considered choice mechanisms are behaviorally equivalent to classic choice rules, as summarized
+in Table~\ref{tab:CMs}. This means that most of the following results which we would like to
+interpret as results about the evolutionary fitness of subjective representation schemes have
+value also for anyone interested only in a comparison of the ecological value of classic choice
+rules. This also means that, given Fact~\ref{fact:equivalence2x2}, all choice mechanisms are
+behaviorally equivalent on $2 \times 2$ symmetric games, except for objective preference types
+with imprecise beliefs.
 
@@
 given by the player's preference type over the set of probabilities given by the belief type.
-
-\subsection{Choice mechanisms \& classic choice rules}
-
-By fixing the action selection component to maxmin expected utility, and allowing two belief and
-two preference types, we regain all the choice rules considered in sectionNN from a more general and unified standpoint, as it is summed up in
-Table~\ref{tab:CMs}. \\
-We are now in the position of formally deriving behavior from a pair $(\theta, e) \in \Theta \times E$.
-
-\begin{definition} \label{def:utility-belief}
-
-Given a game $G$, an action $a_i \in A_i$, and a belief $\mu \in \lbrace \mu' \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu'(a_{-i}) = 1 \rbrace$, we define $\tau(G)(a_i, \mu):= \sum_{a_{-i} \in A_{-i}} \tau(G)(a_i, a_{-i}) \cdot \mu(a_{-i})$.
-
-\end{definition}
-
-\begin{definition} \label{def:maxminSEU}
-
-Given a game $G$, a preference type $\tau$ and a belief type $e$, we define $\kappa(\tau(G), e):= \lbrace a_i \in A_i : a_i \in \text{max}_{a'_i \in A_i} \text{ min}_{\mu \in e} \text{ } \tau(G)(a'_i, \mu) \rbrace$.\footnote{As already specified in the previous example, we assume that, whenever the set $\kappa(\tau(G), e)$ is not a singleton, the player $(\tau, e)$ will mix with equal probability among the actions in $\kappa(\tau(G), e)$.}
-
-\end{definition}
-
-It is then worth stressing that $\kappa(\tau^{\pi}, \Delta)$ turns out to be the actual payoff
-maximinimizer, $\kappa(\tau^{reg}, \Delta)$ corresponds to the regret minimizer,
-$\kappa(\tau^{\pi}, \overline{\mu})$ is the expected actual payoff maximizer (with flat beliefs), and
-$\kappa(\tau^{reg}, \overline{\mu})$ is the expected regret minimizer (with flat beliefs).
-Moreover, different subjective preferences and belief types can give rise to identical action predictions,
-either in a restricted class of games, or in general. This is also the case here.
-
-\begin{fact} \label{fact:maxEU-minReg} For any strategic game $G$ and any arbitrary
-  probabilistic belief $\mu \in \Delta$ about the opponents' behavior, the acts
-  selected by maximization of expected utility for $G$ under $\mu$ are exactly the acts
-  selected by the maximization of expected utility for the negative regret transformation of $G$
-  under $\mu$ \citep[e.g.,][]{HalpernPass2012:Iterated-Regret}.
-\end{fact}
-
-\noindent In other words, given the same probabilistic belief, maximization of expected
-(objective) payoff and minimization of expected regret are behaviorally
-equivalent. This holds for arbitrary games, as well as for solitary decision situations. On the
-other hand, the following does not hold in general:
-
-\begin{fact} \label{fact:equivalence2x2}
-In the class of $2 \times 2$ symmetric games, players $(\tau^{reg}, \Delta)$, $(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg},\overline{\mu})$ are behaviorally equivalent.
-\end{fact}
-
-\begin{example}
-  Consider the game in Figure \ref{coordgame1} again. When a player characterized
-  by\footnote{To ease notation in the following we will refer to the pair
-    $(\text{preference type } \tau,\text{ belief type } e)$ as the \textit{player type}.} preference
-  type $ \tau^{reg} $ and belief type $ \Delta $ faces the game in Figure
-  \ref{coordgame1}, her preference type gives rise to the representation $\tau^{reg}(G^C)$ in
-  Figure \ref{coordgame1reg}. Then, maximinimizing expected utility over the probability
-  simplex $ \Delta $ given the game in Figure \ref{coordgame1reg} corresponds to
-  playing the standard maxmin strategy [REF] of that game.\footnote{Notice that this is the
-    case for any game: given a game $G$, maximinimizing expected utility over the probability
-    simplex $ \Delta $ amounts to playing the standard maxmin strategy of $G$.} This,
-  in turn, corresponds to the regret minimizing action of the original game $G^C$ of Figure
-  \ref{coordgame1}, namely action $II$, as we have seen in Section \ref{sec:choice-rules}. A
-  player $(\tau^{reg},\overline{\mu})$ instead has subjective representation $\tau^{reg}(G^C)$
-  of Figure \ref{coordgame1reg} and a flat probability measure
-  $\overline{\mu}=(\frac{1}{2}I,\frac{1}{2}II)$ over the co-player's actions. Consequently,
-  such a player would play action $II$, i.e., the action that maximinimizes expected utility
-  given the flat probability measure $\overline{\mu}$. Similarly, a player
-  $(\tau^{\pi},\Delta)$ will have the subjective representation coinciding with the
-  objective fitness game, i.e., $ \tau^{\pi}(G^C)= G^C $. Then, both actions $I$ and $II$
-  maximinimize expected utility over the probability simplex $ \Delta $. Hence, a
-  player $(\tau^{\pi},\Delta)$ will be indifferent between $I$ and $II$, and will
-  randomize with equal probability $(\frac{1}{2}I,\frac{1}{2}II)$. Finally, a player
-  $(\tau^{\pi},\overline{\mu})$ maximinimizes the objective fitness game $G^C$ of Figure
-  \ref{coordgame1} with flat probability $\overline{\mu}$ over the co-player's actions, i.e.,
-  maximizes objective utility given $\overline{\mu}$. In game $G^C$ this yields action $II$.
-
-\end{example}
-
-%\todo[inline]{should we explain here, or very soon, what the resulting types really are: regret minimizers, maxmin players \dots}
-
-Many other alternatives different from maxmin could produce behavior: choice rules like minmax, maxmax, and minmin would similarly generate behavior in case of a lack of precise probabilistic belief.
-As it should be clear by now, here we postulate that players use maxmin for two main reasons.
-First, among other possible choice rules maxmin is not only intuitively appealing but also corroborated from an empirical point of view.
-Secondly, our main interest is the evolution of different patterns of subjective conceptualizations of games, and we want to show that the veridical representation is not necessarily the fittest and may not be evolutionarily stable.
-Assuming that all players use a fixed rule (maxmin expected utility) independent of their preference and belief type allows us to factor the choice rule out of the selection process and to focus on subjective representations only.
-
-\iffalse
-
-\begin{fact} \label{fact:maxEU-minReg}
-
-For any probability measure $\mu$, maximization of expected utility and minimization of expected regret are behaviorally equivalent.
-
-\end{fact}
-
-\noindent As we have seen in the previous example, this is not the case in the presence of (radical) uncertainty, in the sense of representation of belief state in terms of a set of probability, as in $ \Delta $.
-\fi
 

### 2015-12-18 paper/paper.tex
rewrite sec com

@@
 \begin{align}
+  \label{eq:FittnessChoiceMechGamePairwise}
   F(c, c') = \int P(g) \  \utils_g(c,c') \text{ d} g \,.
@@
 and $F(c,c') > F(c',c')$. It is neutrally stable if for all $c'$ either (i) $F(c,c) > F(c',c)$
-or (ii) $F(c,c) = F(c',c)$ and $F(c,c') \ge F(c',c')$. Similarly, evolutionary dynamics can be
-applied to meta games. We will later turn towards the replicator dynamic
+or (ii) $F(c,c) = F(c',c)$ and $F(c,c') \ge F(c',c')$
+\citep{Maynard-Smith1982:Evolution-and-t}. Similarly, evolutionary dynamics can be applied to
+meta games. We will later turn towards the replicator dynamic
 \citep{TaylorJonker1978:Evolutionary-St} and the replicator mutator dynamic
@@
 
-Maximinimization under a precise (singleton set) probabilistic belief is just standard
-maximization of expected utilities. Moreover, given the same precise (singleton set)
-probabilistic belief, the choices of objective and regret preference types are exactly the
-same.
-
-\begin{fact} \label{fact:maxEU-minReg} For any strategic game $G$ and any arbitrary precise
-  (singleton set) probabilistic belief about the opponents' behavior, the acts selected by
-  maximization of expected utility for $G$ are exactly the acts selected by the maximization of
-  expected utility for the negative regret transformation of $G$
-  \citep[e.g.,][]{HalpernPass2012:Iterated-Regret}. This also holds for solitary decision
-  problems.
+\begin{fact} \label{fact:singleton probability set}
+Maximinimization under a precise (singleton set) belief is just standard
+maximization of expected utilities.
+\end{fact}
+
+\begin{fact} \label{fact:maxEU-minReg} Under an identical precise (singleton set) belief, the
+  acts selected by maximization of expected utility in game $G$ are exactly the acts selected
+  by the maximization of expected utility for the negative regret transformation of $G$
+  \citep[e.g.,][]{HalpernPass2012:Iterated-Regret}.
 \end{fact}
@@
 other. On the other hand, if paired with imprecise beliefs, different behavioral predictions
-arise. However, in the special case of $2 \times 2$ symmetric games, another noteworthy general
-result holds.
-
-\begin{fact} \label{fact:equivalence2x2} In the class of $2 \times 2$ symmetric games, acts
-  selected by Laplace's rule are exactly the acts selected by regret minimization. 
-\end{fact}
-
-In the following, we assume that agents are maximally ignorant, so that precise types have a
+arise.
+
+In the following, we assume that agents are maximally uncertain, so that precise types have a
 (singleton set containing a) flat probability distribution
@@
 value also for anyone interested only in a comparison of the ecological value of classic choice
-rules. This also means that, given Fact~\ref{fact:equivalence2x2}, all choice mechanisms are
-behaviorally equivalent on $2 \times 2$ symmetric games, except for objective preference types
-with imprecise beliefs.
-
-\subsection{Imprecise probabilistic beliefs}
+rules.
+
+Maximal uncertainty also means that, given Fact~\ref{fact:equivalence2x2}, all choice
+mechanisms are behaviorally equivalent on $2 \times 2$ symmetric games, except for objective
+preference types with imprecise beliefs.
+
+\begin{fact} \label{fact:equivalence2x2} In the class of $2 \times 2$ symmetric games, acts
+  selected by Laplace's rule are exactly the acts selected by regret minimization. 
+\end{fact}
+
+\section{The basic model}
+\label{sec:basic-model-1}
+
+\subsection{Simulation results}
+\label{sec:simulation-results}
+
+To demonstrate the usefulness of a meta-game approach, let us concentrate first on a basic
+model that contains the four choice mechanisms obtained from crossing the preference and belief
+types introduced in Section~\ref{sec:basic-notions}. From now on we speak of types when we mean
+pairs like $(\text{reg}, \text{imp})$, a choice mechanism with regret-based preferences and
+imprecise beliefs, or $(\text{obj}, \text{prc})$, one with objective preferences and precise
+beliefs.
+
+Meta games factor in statistical properties of the environment. For a particular empirical
+purposes, one would consult a specific class of games $\mathcal{G}$ with appropriate, possibly
+empirically informed probabilities $P(G)$ in order to match the natural environment of a given
+population. But for our theoretical purposes we adopt another approach, since we would not know
+how to justify any more specific assumption. To begin with, let $\mathcal{G}$ be a set of
+symmetric 2-player games with two acts. A game is then individuated solely by its payoff
+function, which is essentially a matrix with four numbers. As for occurrence probabilities of
+games, we imagine that entries in a game's payoff matrix are i.i.d.~random variables sampled
+uniformly from set $ \lbrace 0, \dots, 10 \rbrace$.  Using Monte Carlo simulation, we can then
+approximate the relevant fitness values of Equation~(\ref{eq:FittnessChoiceMechGamePairwise})
+to construct meta game payoffs. Results based on $100,000$ randomly sampled games are given in
+Table~\ref{tab:ExpectedFitness_4Types}.\footnote{Concretely, $100,000$ games were sampled
+  repeatedly by choosing independently four integers between 0 and 10 uniformly at random. For
+  each game, the action choices of all four choice mechanisms were determined and payoffs from
+  all pairwise encounters recorded. (Whenever a choice mechanism would not select a unique
+  action in a given game, we recorded unbiased averages over all selected actions.)  The number
+  in each cell of Table~\ref{tab:ExpectedFitness_4Types} is the average payoff for the choice
+  mechanism listed in the row when matched with the choice mechanism in the column.}
+
+\begin{table}[t]
+\centering
+\begin{tabular}{ccccc}
+  \toprule
+ & $\text{reg}, \text{imp}$ 
+ & $\text{obj}, \text{imp}$ 
+ & $\text{reg}, \text{prc}$ 
+ & $\text{obj}, \text{prc}$ \\ 
+  \midrule
+  $\text{reg}, \text{imp}$ & 6.663 & 6.662 & 6.663 & 6.663 \\ 
+  $\text{obj}, \text{imp}$ & 6.486 & 6.484 & 6.486 & 6.486 \\ 
+  $\text{reg}, \text{prc}$ & 6.663 & 6.662 & 6.663 & 6.663 \\  
+  $\text{obj}, \text{prc}$ & 6.663 & 6.662 & 6.663 & 6.663 \\ 
+   \bottomrule
+\end{tabular}                    
+\caption{Average evolutionary fitness from Monte Carlo simulations of 100,000 symmetric $2 \times 2$ games}
+\label{tab:ExpectedFitness_4Types}
+\end{table}
+
+Simulation results obviously reflect Fact~\ref{fact:equivalence2x2} in that all encounters in
+which types $(\text{reg}, \text{imp})$, $(\text{reg}, \text{prc})$ or
+$(\text{obj}, \text{prc})$ are substituted for one another yield identical results. More
+interestingly, Table~\ref{tab:ExpectedFitness_4Types} shows that the maxmin strategy
+$(\text{obj}, \text{imp})$ is strictly dominated by the three other strategies: in each column
+(i.e., for each kind of opponent), the maxmin strategy is strictly worse than any of the other
+three competitors. This has a number of interesting consequences.
+
+Let's begin with a restricted scenario and look at more and more complex cases afterwards. If
+we restrict attention to only imprecise belief types, then a state in which every agent has
+regret-based preferences is the only \emph{evolutionarily stable state}. More strongly, since
+$(\text{obj}, \text{imp})$ is strictly dominated by $(\text{reg}, \text{imp})$, we expect
+selection that is driven by expected fitness to invariably weed out $(\text{obj}, \text{imp})$,
+the maxmin choice rule, in favor of $(\text{reg}, \text{imp})$, regret minimization. In other
+words, when taking average payoffs over the class of random games considered here, regret
+minimization is a better classic choice rule than the maxmin rule from an evolutionary point of
+view, despite the fact that the former, but not the latter, entertains non-veridical subjective
+preferences.
+
+Next, if we look at the competition between all four types represented in
+Table~\ref{tab:ExpectedFitness_4Types}, $(\text{reg}, \text{imp})$ is no longer evolutionarily
+stable. Rather, given behavioral equivalence (Fact~\ref{fact:equivalence2x2}), types
+$(\text{reg}, \text{imp})$, $(\text{reg}, \text{prc})$, and $(\text{obj}, \text{prc})$ are all
+\emph{neutrally stable} \citep{Maynard-Smith1982:Evolution-and-t}. But since
+$(\text{obj}, \text{imp})$ is strictly dominated and so disfavored by fitness-based selection,
+we are still drawn to conclude that maxmin behavior is weeded out in favor of a population with
+a random distribution of the remaining three types.
+
+Simulation results of the (discrete time) \emph{replicator dynamics}
+\citep{TaylorJonker1978:Evolutionary-St} indeed show that random initial population
+configurations are attracted to states with only three player types:
+$(\text{reg}, \text{imp})$, $(\text{reg}, \text{prc})$ and $(\text{obj}, \text{prc})$. The
+relative proportions of these depend on the initial population. This variability disappears if
+we add a small mutation rate to the dynamics. Take a fixed, small mutation rate $\epsilon$ for
+the probability that a player's preference type \emph{or} her belief type changes to another
+preference type or belief type. The probability that a player randomly mutates into a
+completely different player with altogether different preference type and belief type would
+then be $\epsilon^2$. With these assumptions about ``component-wise mutations'', numerical
+simulations of the (discrete time) \emph{replicator mutator dynamics}
+\citep{Nowak2006:Evolutionary-Dy} show that already for very small mutation rates almost all
+initial populations converge to a single fixed point in which the majority of players are
+regret types. For instance, with $\epsilon = 0.001$, almost all initial populations are
+attracted to a final distribution with proportions:\todo{recalculate these numbers for the
+  actual 4x4 game!}
+
+\begin{center}
+  \begin{tabular}{cccc}
+    $(\text{reg}, \text{imp})$ & $(\text{obj}, \text{imp})$ & $(\text{reg},
+      \text{prc})$ & $(\text{obj}, \text{prc})$ \\ \hline
+    0.289  & 0.021 &   0.398 &    0.289 
+  \end{tabular}
+\end{center}
+
+What this suggests is that, if biological evolution selects behavior-generating mechanisms, not
+behavior as such, it need not be the case that behaviorally equivalent mechanisms are treated
+equally all the while. If mutation probabilities are a function of individual components (i.e.,
+preference and belief types) of such behavior-generating mechanisms, it can be the case that
+certain components are more strongly favored by a process of random mutation and
+selection. This is exactly the case with regret-based subjective preferences in the present
+example. Since regret-based subjective preferences are much better in connection with imprecise
+beliefs than veridical preferences are, the proportion of expected regret minimizers,
+$(\text{reg}, \text{prc})$, in the attracting state is substantially higher than that of
+expected utility maximizers, $(\text{obj}, \text{prc})$, even though these types are
+behaviorally equivalent.
+
+\subsection{Analytical results}
+\label{sec:analytical-results}
+
+Results based on the single meta-game in Table~\ref{tab:ExpectedFitness_4Types}, which was
+obtained by Monte Carlo simulation, are not fully general and possibly spoiled by random
+fluctuations in the sampling procedure. Fortunately, for the case of $2 \times 2$ symmetric
+games, the main result that maxmin types $(\text{obj}, \text{imp})$ are strictly dominated can
+also be shown analytically for generous general conditions on how likely randomly sampled games
+are.
+
+\begin{proposition} \label{proposition1}
+  Let $\mathcal{G}$ be the class of $2 \times 2$ symmetric games with payoffs sampled from a
+  set of i.i.d.~values with at least three elements in the support. Then,
+  $(\text{reg}, \text{imp})$ strictly dominates $(\text{reg}, \text{prc})$ in the resulting
+  meta-game.
+\end{proposition}
+
+\begin{corollary} \label{corollary1} Considering only $(\text{obj}, \text{imp})$ and
+  $(\text{reg}, \text{imp})$, and letting $\mathcal{G}$ be the class of $2 \times 2$ symmetric
+  games with payoffs sampled from a set of i.i.d.~values with at least three elements in the
+  support, the unique evolutionarily stable state is a monomorphic population of
+  $(\text{reg}, \text{imp})$-players.
+\end{corollary}
+
+Proofs for Proposition \ref{proposition1} and Corollary~\ref{corollary1} are given in
+Appendix~\ref{sec:proofs}. They tell us that the main conclusions drawn in the previous section
+based on the approximated meta game in Table~\ref{tab:ExpectedFitness_4Types} hold more
+generally for any class of games in which the probability of encountering a game is the product
+of independently sampling four identically distributed payoff values. As before,
+$(\text{reg}, \text{imp})$, $(\text{obj}, \text{prc})$, and $(\text{reg}, \text{prc})$ players
+will be neutrally stable, and fitness-based selection will tend to weed out maxmin play and
+leave us with a population of arbitrary frequency of $(\text{reg}, \text{imp})$,
+$(\text{obj}, \text{prc})$, and $(\text{reg}, \text{prc})$ players. This shows that there is
+support for the main conceptual point that we wanted to make: non-veridical subjective
+preference relations \emph{can}, under specific circumstances, persist under evolutionary
+selection based on objective fitness. Moreover, regret-based preferences can not only persist,
+but even be favored by natural selection if agents may have imprecise beliefs. This holds
+generally for playing arbitrary $2 \times 2$ symmetric games whose payoffs are sampled
+identically and independently at random.
+
+\section{Extensions}
+\label{sec:extensions}
+
+How do the basic results from the previous section carry over to more encompassing, richer
+models? Section~\ref{sec:more-types} first introduces further conceptually interesting
+preference types that have been considered in evolutionary game theory. Section~\ref{sec:n-times-n}
+then addresses the case of $n \times n$ games for $n \ge 2$. Finally, to put our results into
+a broader perspective, Section~\ref{sec:solitary-decisions} ends with a brief comparison of
+game situations with cases of solitary decision making.
+
+\subsection{More types}
+\label{sec:more-types}
+
+In evolutionary game theory other types of player have been investigated.
+A famous example is the \textit{altruistic type} [REF], introduced in the literature in order to explain the possible survival of altruistic behavior.
+In our framework, we can represent the altruistic type as follows.
+
+\iffalse
+
+\begin{definition}[Altruistic preference] \label{defn:altpref}
+
+For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{alt}: A \rightarrow \mathbb{R} $ such that $ \theta^{alt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \sum_{j \neq i} \pi(a_{j},a_{-j})$.\footnote{A more general formulation [see: REFERENCES] would be to define an $ \alpha$-altruistic type, for $\alpha \in [0,1]$, with subjective utility $ \theta^{\alpha lt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \alpha \sum_{j \neq i} \pi(a_{j},a_{-j})$.
+Since we are not interested in the evolution of degrees of altruism here, we simply fix $ \alpha = 1 $.}
+
+\end{definition}
+
+\fi
+
+\begin{definition}[Altruistic type] \label{defn:alttype}
+
+Given a two player game  $ G $, the \textit{altruistic type} $\tau^{alt}$ is characterized by the subjective utility function $\tau^{alt}(G)(a_i, a_j):=\pi_i(a_i,a_j) + \pi_j(a_i,a_j)$.\footnote{A more general formulation would be to define an $ \alpha$-altruistic type, for $\alpha \in [0,1]$, with subjective utility $ \tau^{\alpha lt}(G)(a_i, a_j):=\pi_i(a_i,a_j) + \alpha \pi_j(a_i,a_j)$.
+Since we are not interested in the evolution of degrees of altruism, here we simply fix $ \alpha = 1 $.}
+
+\end{definition}
+
+\noindent As opposite to the altruistic type, it is possible to define a \textit{competitive type}.
+
+\iffalse
+
+\begin{definition}[Competitive preference] \label{defn:compref}
+
+For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the competitive preference $ \theta^{com}: A \rightarrow \mathbb{R} $ such that $ \theta^{com}(a_i,a_{-i})=\pi(a_i,a_{-i}) - \sum_{j \neq i} \pi(a_{j},a_{-j})$.
+
+\end{definition}
+
+\fi
+
+\begin{definition}[Competitive type] \label{defn:comtype}
+
+Given a two player game  $ G $, the \textit{competitive type} $\tau^{com}$ is characterized by the subjective utility function $\tau^{com}(G)(a_i, a_j):=\pi_i(a_i,a_j) - \pi_j(a_i,a_j)$.
+
+\end{definition}
+
+Similarly to the evolutionary competition that we simulated before, we can study the
+evolutionary fitness of this extended set of players when they are all represented in the
+population. Table~\ref{tab:ExpectedFitness_2x2_Full} shows simulation results that approximate the
+expected fitness in the relevant meta-game.
+
+\begin{table}[]
+\centering
+\footnotesize
+\begin{tabular}{ccccccccc}
+  \hline
+ & $(\text{reg}, \text{imp})$ 
+ & $(\text{obj}, \text{imp})$ 
+ & $(\tau^{com}, \text{imp})$
+ & $(\tau^{alt}, \text{imp})$
+ & $(\text{reg}, \text{prc})$ 
+ & $(\text{obj}, \text{prc})$ 
+ & $(\tau^{com}, \text{prc})$
+ & $(\tau^{alt}, \text{prc})$ \\ 
+  \hline
+  $(\text{reg}, \text{imp})$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
+  $(\text{obj}, \text{imp})$ & 6.486 & 6.484 & 6.088 & 6.703 & 6.486 & 6.486 & 6.088 & 6.875 \\
+  $(\tau^{com}, \text{imp})$ & 6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\
+  $(\tau^{alt}, \text{imp})$ & 5.949 & 5.722 & 5.326 & 6.396 & 5.949 & 5.949 & 5.326 & 6.568 \\
+  $(\text{reg}, \text{prc})$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
+  $(\text{obj}, \text{prc})$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
+  $(\tau^{com}, \text{prc})$ & 6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\
+  $(\tau^{alt}, \text{prc})$ & 6.331 & 5.893 & 5.497 & 6.566 & 6.331 & 6.331 & 5.497 & 7.152 \\
+   \hline                          
+\end{tabular}                      
+\caption{Average payoff in simulations of 100,000
+  randomly generated $2 \times 2$ symmetric games}
+\label{tab:ExpectedFitness_2x2_Full}        
+\end{table}
+
+\todo[inline]{is it true that competitive preferences types are behaviorally equivalent under
+  either epistemic type? can we show that?}
+
+The approximations in Table~\ref{tab:ExpectedFitness_2x2_Full} confirm basic intuitions about
+altruistic and competitive types: averaging over randomly sampled games, everybody would like
+to have an altruistic opponent and nobody would like to play against a competitive
+opponent. Perhaps more surprisingly, altruistic types come up strictly dominated by competitive
+types, but competitive types themselves are worse off against all opponent types except against
+maxmin players $(\text{obj}, \text{imp})$ than any of the behaviorally equivalent types
+$(\text{reg}, \text{imp})$, $(\text{obj}, \text{prc})$, and
+$(\text{reg}, \text{prc})$. 
+\iffalse
+This is a noteworthy results in the light of the fact that
+evolving altruistic preferences have been shown to support cooperative behavior in a single
+stage game \myalert{[CITE]}. In contrast,
+averaging over payoffs in multiple stage games, like we do here, makes altruistic preferences
+prime victims of evolutionary eradication.
+\fi
+It is easy to see then that the previous result still obtains for the larger meta-game in
+Table~\ref{tab:ExpectedFitness_2x2_Full}: $(\text{reg}, \text{imp})$,
+$(\text{obj}, \text{prc})$, and $(\text{reg}, \text{prc})$ are still neutrally stable;
+all simulations of the (discrete-time) replicator dynamic on the $8 \times 8$ meta-game from
+Table~\ref{tab:ExpectedFitness_2x2_Full} end up in populations consisting of only these players
+in arbitrary proportion.
+
+\iffalse
+
+The following proposition (partially) confirms this result.\todo{rephrase to acknowledge all
+  epistemic types?}
+
+\begin{proposition} \label{proposition2}
+
+Fix $\Lambda = \lbrace (\text{obj}, \text{imp}), (\text{reg}, \text{imp}), (\tau^{alt}, \text{imp}), (\tau^{com}, \text{imp}) \rbrace$ and $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex, set of i.i.d.
+values.
+Then, $(\text{reg}, \text{imp})$ is the only evolutionarily stable player in the population.
+
+\end{proposition}
+
+\begin{proof}
+See Appendix.\todo{is this there already?}
+\end{proof}
+
+\fi
+
+In sum, the presence of other plausible preference types, such as competitive and altruistic
+types does not undermine the previous results about the evolutionary drive towards regret-based
+subjective preferences.
+
+\subsection{More actions: $n \times n$ symmetric games}
+\label{sec:n-times-n}
+
+Results from Section~\ref{sec:results:-basic-model} relied heavily on
+Fact~\ref{fact:equivalence2x2} that, for the special case of $2 \times 2$ symmetric games,
+regret minimization $(\text{reg}, \text{imp})$ is behaviorally equivalent with expected
+regret minimization $(\text{reg}, \text{prc})$ and expected utility maximization
+$(\text{obj}, \text{prc})$. This is no longer true when we look at arbitrary $n \times n$
+games with $n \ge 2$. We should therefore see what happens in a broader class of games.
+
+Table~\ref{tab:ExpectedFitness_10x10} gives approximations for expected fitness in a
+meta-game over a class of $n \times n$ symmetric games where $n$ is randomly drawn from
+$\set{2, \dots, 10}$. Concretely, the numbers in Table~\ref{tab:ExpectedFitness_10x10} are
+averages of payoffs obtained in 100,000 randomly sampled games, where each game was sampled by
+first picking a number of acts $n \in \set{2, \dots, 10}$ uniformly at random, and then filling
+the resulting $n \times n$ payoff matrix of the stage game with i.i.d.~sampled payoffs as
+before.
+
+\begin{table}[]
+\centering
+\footnotesize
+\begin{tabular}{ccccccccc}
+  \toprule
+ & $(\text{reg}, \text{imp})$ 
+ & $(\text{obj}, \text{imp})$ 
+ & $(\tau^{com}, \text{imp})$
+ & $(\tau^{alt}, \text{imp})$
+ & $(\text{reg}, \text{prc})$ 
+ & $(\text{obj}, \text{prc})$ 
+ & $(\tau^{com}, \text{prc})$
+ & $(\tau^{alt}, \text{prc})$ \\ 
+  \midrule
+  $(\text{reg}, \text{imp})$ & 6.567 & 6.570 & 5.650 & 6.992 & 6.564 & 6.564 & 5.593 & 7.409 \\
+  $(\text{obj}, \text{imp})$ & 6.476 & 6.483 & 5.896 & 6.818 & 6.484 & 6.484 & 5.850 & 7.124 \\
+  $(\tau^{com}, \text{imp})$ & 6.468 & 6.647 & 5.512 & 7.169 & 6.578 & 6.578 & 5.577 & 7.354 \\
+  $(\tau^{alt}, \text{imp})$ & 5.968 & 5.923 & 5.363 & 6.685 & 5.975 & 5.975 & 5.086 & 6.973 \\
+  $(\text{reg}, \text{prc})$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
+  $(\text{obj}, \text{prc})$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
+  $(\tau^{com}, \text{prc})$ & 6.529 & 6.680 & 5.445 & 7.276 & 6.542 & 6.542 & 5.521 & 7.440 \\
+  $(\tau^{alt}, \text{prc})$ & 6.450 & 6.337 & 5.772 & 6.978 & 6.457 & 6.457 & 5.479 & 7.500 \\
+   \bottomrule                         
+\end{tabular}                      
+\caption{Average payoff in simulations of 100,000
+  randomly generated $n \times n$ symmetric games with $n$ randomly drawn from $\set{2, \dots, 10}$.}
+\label{tab:ExpectedFitness_10x10}        
+\end{table}
+
+As is to be expected, average payoffs obtained in games with more than 2 acts are higher, as
+can be seen by comparing Table~\ref{tab:ExpectedFitness_10x10} with
+Table~\ref{tab:ExpectedFitness_2x2_Full}. But increases in approximate expected fitness are not
+uniform. Most importantly, the regret minimizing type $(\text{reg}, \text{imp})$ is
+strictly dominated by $(\text{reg}, \text{prc})$ and by $(\text{obj}, \text{prc})$ in
+the meta-game from Table~\ref{tab:ExpectedFitness_10x10}. This means that while regret
+minimization \emph{can} thrive in some evolutionary contexts, there are also contexts where it
+is demonstrably worse off.
+
+Still, although this may be bad news for regret minimizing types
+$(\text{reg}, \text{imp})$, it is not the case that regret types \emph{as such} are weeded
+out by selection. Since, by Fact~\ref{fact:maxEU-minReg}, $(\text{reg}, \text{prc})$ and
+$(\text{obj}, \text{prc})$ are generally behaviorally equivalent, it remains that
+selection based on meta-games constructed from $n \times n$ games will still not eradicate all
+regret types. So, although regret types may not be selected for in this case, they are also not
+selected against.
+
+On the other hand, there are plenty of ways in which the basic insight from
+Proposition~\ref{proposition1} that regret-based preferences can be strictly better than
+veridical objective preferences in case of radical uncertainty could make for situations in
+which evolution would select for regret types exclusively, even in $n \times n$ games. If, for
+example, epistemic types of players are not what biological evolution selects, but rather
+something that the particular choice situation would exogenously give us, then regret-based
+preference \emph{can} again drive out veridical preferences altogether. For concreteness,
+suppose that only preference types compete and that agents' belief types are exogenously
+given, in such a way that agents hold flat probabilistic beliefs $\text{prc}$ with probability
+$1-p$ and are of type $\text{imp}$ with probability $p$. This transforms the meta-game from
+Table~\ref{tab:ExpectedFitness_10x10} into the simpler $4 \times 4$ game in which the payoff
+obtained for a preference type is the weighted average over the payoffs of that preference
+types in Table~\ref{tab:ExpectedFitness_10x10}. Setting $p = 0.02$ for illustration, we get the
+meta-game in Table~\ref{tab:ExogeneousEpistemics}.
+
+\begin{table}[]
+\centering
+\begin{tabular}{ccccc}
+  \toprule
+  & $\text{reg}$ 
+  & $\text{obj}$ 
+  & $\tau^{com}$
+  & $\tau^{alt}$ \\ 
+  \midrule
+  $\text{reg} $ & 6.926 & 6.926 & 5.942 & 7.757 \\ 
+  $\text{obj} $ & 6.924 & 6.924 & 5.948 & 7.751 \\ 
+  $\tau^{com }$ & 6.566 & 6.570 & 5.481 & 7.434 \\ 
+  $\tau^{alt} $ & 6.463 & 6.461 & 5.478 & 7.469 \\ 
+   \bottomrule
+\end{tabular}
+\caption{Meta-game for the evolutionary competition between preference types when epistemic types are exogenously
+  given}
+\label{tab:ExogeneousEpistemics}
+\end{table}
+
+The only evolutionarily stable state of this meta-game is the regret type. Accordingly, all of
+our simulation runs of the (discrete-time) replicator dynamic converged to monomorphic
+regret-type populations. The reason why regret types prosper is because they have a substantial
+payoff advantage if paired with radical uncertainty. If radical uncertainty is exogenously
+given as something unavoidable that happens to agents (e.g., in situation where they really have no
+way of narrowing down the probability set), and even if that happens only very
+infrequently (i.e., for rather low $p$), regret types \emph{will} outperform veridical
+preference types, as well as competitive and altruistic types.
+
+\subsection{Solitary decisions}
+\label{sec:solitary-decisions}
+
+\todo[inline]{text in this section and the next is rough and unpolished, only intended to have
+  the basic results recorded, so that we can reshape the article around the basic results}
+
+To see how different choice mechanisms behave in evolutionary competition based on solitary decision
+problems, we approximated, much in the spirit of meta-games, average accumulated payoffs
+obtained in randomly generated solitary decision problems. For our purposes, a decision problem
+$\tuple{S, \Acts, u}$ consists of a set of world states $S$, a set of acts
+$\Acts$, and a utility function $u \mycolon S \times \Acts \rightarrow
+\mathbb{R}$.
+We generated arbitrary decision problems by selecting numbers of states and acts
+$n_s, n_\act \in \set{2, \dots, 10}$ and then filling the utility table, so to speak, by
+independently picking a number $u(s, \act) \in \set{0, 10}$ uniformly at random, just
+as we did before with symmetric games. Unlike with two-player games, we need to also sample the
+actual state of the world, which we selected uniformly at random from the available states in
+the current decision problem. Player types, consisting of epistemic types $\text{prc}$ and
+$\text{imp}$ and preference types $\text{reg}$ and $\text{obj}$, give rise to behavior in
+the same way as before.\footnote{Obviously, now with $ \text{imp} \equiv \text{imp}(S) :=\lbrace \mu \in \mathbb{R}^{S}: \sum_{s \in S} \mu(s) = 1 \rbrace$.} (It is obviously not possible to carry altruistic or competitive
+preference types over to solitary decision making.) As before, we recorded the behavioral
+decisions for each of the four relevant player types in each sampled decision problem, and
+determined the actual payoff obtained, given the actual state. Average payoff over 100,000 decision
+problems are given in Table~\ref{tab:SolitaryDecisions}.
+
+\begin{table}
+  \centering
+  \begin{tabular}{cccc}
+    \toprule
+   $(\text{reg}, \text{imp})$ 
+ & $(\text{obj}, \text{imp})$ 
+ & $(\text{reg}, \text{prc})$ 
+ & $(\text{obj}, \text{prc})$ 
+ \\ \midrule
+    6.318 & 6.237 & 6.661 & 6.661 \\ \bottomrule
+  \end{tabular}
+  \caption{Average payoffs over 100,000 simulated solitary decision problems}
+  \label{tab:SolitaryDecisions}
+\end{table}
+
+Facts~\ref{fact:maxEU-minReg} and \ref{fact:equivalence2x2} still apply:
+$(\text{reg}, \text{prc})$ and $(\text{obj}, \text{prc})$ are behaviorally equivalent
+in general, and $(\text{reg}, \text{imp})$ is behaviorally equivalent to the former two in
+decision problems with 2 states and 2 acts. \todo{show this?} We see this in part in the
+results in Table~\ref{tab:SolitaryDecisions} in that the averages for $(\text{reg},
+  \text{prc})$ and $(\text{obj}, \text{prc})$ are identical. But since we included decision
+problems with more acts and more states as well, the averages for regret minimizers
+$(\text{reg}, \text{imp})$ are not identical to the one of $(\text{reg},
+  \text{prc})$ and $(\text{obj}, \text{prc})$. They are, in fact, lower, but not as low as
+those of the minimax choosers.
+
+What that means is that basically every relevant result we have seen about game situations is also borne out
+when reasoning about solitary decisions. Evolutionary selection based on objective fitness will
+not select against regret-based subjective preferences, as these are indistinguishable from
+veridical preferences when paired with probabilistic beliefs. But when paired with
+non-probabilistic belief types, regret-based preferences actually outperform veridical
+preferences. Consequently, if there is a chance, however small, that agents must fall back onto
+non-probabilistic beliefs, evolution will actually positively select for non-veridical
+regret-based preferences.
+
+\iffalse
+\subsection{Arbitrary probabilistic beliefs}
+\label{sec:arbitr-prob-beli}
+
+So far, we have assumed that epistemic types $\text{prc}$ hold an unbiased, flat belief. It is
+worthwhile considering what happens when this assumption is relaxed and we allow agents with
+probabilistic beliefs to make use of the full spectrum of probabilistic beliefs. It should be
+clear that quality of beliefs directly impacts prospects of successful decision making: if a
+decision maker knows the actual state, or can put a high level of credence on the actual state,
+accumulated fitness can be expected to be high. We see this, unsurprisingly, in numerical
+simulations. We looked at the average payoff accumulated in 100,000 decision problems sampled
+as before, except that for belief types with probabilistic beliefs we sampled a random
+probabilistic belief $p$ (from an unbiased Dirichlet distribution) and chose the actual world
+state with probability weights $p$. This effectively implements a bias for beliefs of the
+decision maker that tend to put more weight on the actual state (although the procedure does
+admittedly perverse the natural chicken-and-egg logic in this case that the actual world state
+should come first and beliefs be a function of it). As a result, the average payoffs of types
+$\tuple{\text{reg}, \text{prc}}$ and $\tuple{\text{obj}, \text{prc}}$ are still the exact same
+(because we compare what agents with different preference types would do under the same
+beliefs; we are not interested in statistical fluctuations given one type better beliefs by
+pure happenstance), but with $7.125$ notably higher than before. In effect, better
+probabilistic beliefs lead to better decisions. If agents can learn, reason and extrapolate to
+form better probabilistic beliefs, that will help them whenever they take their beliefs into
+account.
+
+But this is orthogonal to the arguments in this paper, where the focus is on possibilities for
+the evolution of non-veridical preferences. We know from Fact~\ref{fact:maxEU-minReg} that
+regret types and veridical preference types, when paired with probabilistic belief types that
+maximize/minimize expectations, are behaviorally equivalent, \emph{no matter what they believe},
+as long as they belief the same. So, if learning, insight and statistical knowledge of a
+recurrent situation \emph{can} be brought to bear, this will not make evolution select against
+regret-based preferences. If, on the other hand, agents have no basis for probabilistic
+beliefs, then we have shown that there are general and basic circumstances in which
+regret-based preferences can actually be selected, despite their non-veridicality.
+\fi
+
+\section{Conclusion} \label{sec:conclusion}
+
+The assumption that players and decision makers maximize their (subjective) preferences is central through all economic literature, and the maximization of actual (objective) payoffs is often justified by appealing to evolutionary arguments and natural
+selection. In contrast to the standard view, we showed the
+existence of player types with subjective utilities different
+from the actual payoffs that can outperform types whose
+subjective utilities coincide with the actual payoffs.
+While the literature on evolution of preference has focused
+on fixed games, or fixed types of games, we have adopted a
+more general approach here. We suggested that attention
+to “meta-games” is crucial, because what may be a good
+subjective representation in one type of game (e.g., cooperative preferences in the Prisoner’s Dilemma class) need not
+be generally beneficial. Taken together, we presented a variety of plausible circumstances in which evolutionary competition between choice
+mechanisms on a larger class of games can favor subjective
+preference representations focusing on regret.
+
+Finally, we hope to help the research direction towards a broader perspective on evolutionary game theory, as outlined by recent works in theoretical biology \citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be}.
+In partcular, the meta-game approach allows the researcher to both explicitly model the relevant features of the environment and shift the target of evolution from plain behavior to more general behavioral patterns, or choice mechanisms.
+Several uses and improvements of the present model are still possible in many respects.
+We can sketch some of them here.
+For example, the evolutionary investigation of different risk and ambiguity attitudes when competing against each other in an evolutionarily richer environment may bring new insights on both behavioral and theoretic decision making under uncertainty, as well as on many issues in theoretical biology and behavioral ecology.
+
+\appendix
+
+\section{Background on imprecise probabilistic beliefs}
 \label{sec:impr-prob-beli}
 
-Consider the following problem.
-I have, on the desk in front of me, a bag containing either red or black marbles.
-There is no further information about the distribution of the two colors.
-What is then the probability that I will draw a red marble?
-As in \citet{walley96}, we are not talking about physical probability, but rather about epistemic probability, i.e., the subjective probability that an agent attributes to an event.
-In the literature there are two traditional ways of answering this kind of questions.
-According to standard Bayesianism, one should always be able to determine a precise betting rate (that immediately translates into a precise probability distribution), which is fair, in the sense that the DM is indifferent between betting on or against red at the fair rate, and would bet on red at any rate that is more favourable than the fair rate and against red at any rate that is less favourable.
-In the case of the bag on my desk, a strict Bayesian, in the absence of any further information, would probably rely on the \textit{principle of insufficient reason} and answer that the DM should have a uniform distribution that considers all the outcomes equipossible.
-\\
-The second answer involves imprecise probabilities and is related to the literature about unmeasurable uncertainty.
-Many authors argued in favor of this kind of approach \citep[e.g.,][]{levi74,gardsah82,walley96}.
-Since it is consistent with the information available that all the marbles are red, or that no marble is red, the resulting model should take it into account and specify a lower probability of red $\underline{P}(R)$ and an upper probability of red $\overline{P}(R)$ that define an interval of possible probabilistic beliefs [$\underline{P}(R), \overline{P}(R)$].
-Given the information available in this case we would have $\underline{P}(R)=0$ and $\overline{P}(R)=1$.
-This approach appears particularly relevant in a game theoretical context.
-Indeed, in a recent paper \citet{BattCerrMM15} write:
+Consider the following problem. I have, on the desk in front of me, a bag containing either red
+or black marbles. There is no further information about the distribution of the two
+colors. What is then the probability that I will draw a red marble? As in \citet{walley96}, we
+are not talking about physical probability, but rather about epistemic probability, i.e., the
+subjective probability that an agent attributes to an event.  In the literature there are two
+traditional ways of answering this. According to standard Bayesianism, one should always be
+able to determine a precise betting rate (that immediately translates into a precise
+probability distribution), which is fair, in the sense that the DM is indifferent between
+betting on or against red at the fair rate, and would bet on red at any rate that is more
+favourable than the fair rate and against red at any rate that is less favourable. In the case
+of the bag on my desk, a strict Bayesian, in the absence of any further information, would
+probably rely on the \textit{principle of insufficient reason} and answer that the DM should
+have a uniform distribution that considers all the outcomes equipossible.
+
+The second answer involves imprecise probabilities and is related to the literature about
+unmeasurable uncertainty. Many authors argued in favor of this kind of approach
+\citep[e.g.,][]{levi74,gardsah82,walley96}. Since it is consistent with the information
+available that all the marbles are red, or that no marble is red, the resulting model should
+take it into account and specify a lower probability of red $\underline{P}(R)$ and an upper
+probability of red $\overline{P}(R)$ that define an interval of possible probabilistic beliefs
+[$\underline{P}(R), \overline{P}(R)$]. Given the information available in this case we would
+have $\underline{P}(R)=0$ and $\overline{P}(R)=1$. This approach appears particularly relevant
+in a game theoretical context. Indeed, in a recent paper \citet{BattCerrMM15} write:
 
 \begin{quote}
-Such uncertainty is inherent in situations of strategic interaction. This is quite obvious when such situations have been faced only a few times.
+  Such uncertainty is inherent in situations of strategic interaction. This is quite obvious
+  when such situations have been faced only a few times.\todo{insert page number}
 \end{quote}
 
-In evolutionary game theory, for instance, players in a population obviously face uncertainty about the composition of the population that they are part of, and consequently about the co-player that they are randomly paired with at each round and about the co-players' action.
-We represent this uncertainty in two different ways that correspond to the two approaches discussed above: a Bayesian uniform distribution and an imprecise probability set.
-This amounts to having two different belief types, $ \overline{\mu}$ and $ \Delta $, where $\overline{\mu}$ stands for the uniform distribution and $\Delta$ is the probability set, defined as follows:
-
-\begin{itemize}
-
-\item $ \Delta \equiv \Delta(A_{-i}) :=\lbrace \mu \in \mathbb{R}^{A_{-i}}: \sum_{a_{-i} \in A_{-i}} \mu(a_{-i}) = 1 \rbrace$;
-
-\item $\overline{\mu} \in \Delta$ is the probability measure over the co-players' actions such that: $\forall a_{-i} \in A_{-i}$, $\overline{\mu}(a_{-i})= \frac{1}{|A_{-i}|}$.
-
-\end{itemize}
-
-Hence, we consider two possible epistemic states in the face of uncertainty.
-The belief type $\Delta$ represents a situation of non-Bayesian radical uncertainty, where the players are not able to narrow down the set of probability distributions to a single one and they consider all of them as possible.
-The other belief type $\overline{\mu}$ conceptualizes the uncertainty about the population by using the principle of insufficient reason and ascribes equal probability to all the possible alternatives.
-As we have seen, both options are reasonable and justifiable ways to deal with situations of uncertainty.
-\\
-
-In decision theory, the imprecise probability model is in line with most of the representation results of decision making under uncertainty \citep[e.g.,][]{gilsch89,KlibMarMuk05,GhirMar02}, and seems justified by empirical observations too.
-
-A prominent example is Ellsberg's paradox (\citet{ells61}).
-A bag contains 90 marbles, 30 are red and the remaining 60 are either black or yellow.
-A marble is to be drawn and DM can win 100€ if she guesses the color of the drawn marble.
-The DM is offered two different bets.
-In the first one she can choose to bet either on red (R) or on yellow (Y), while in the second she can bet either on red or black (RB) or on yellow or black (YB), as shown in Table \ref{Ellsberg}.
+\noindent In evolutionary game theory, for instance, players in a population obviously face
+uncertainty about the composition of the population that they are part of, and consequently
+about the co-player that they are randomly paired with at each round and about the co-players'
+action.
+
+We therefore represent extreme uncertainty in two different ways that correspond to the two
+approaches discussed above: a Bayesian uniform distribution and an imprecise probability
+set. The latter represents uncertainty for players who are not able to narrow down the set of
+probability distributions to a single one and they consider all of them as possible. The former
+precise belief type conceptualizes the uncertainty about the population by using the principle
+of insufficient reason and ascribes equal probability to all the possible alternatives. As we
+have seen, both options are reasonable and justifiable ways to deal with situations of
+uncertainty.
+
+In decision theory, the imprecise probability model is in line with most of the representation
+results of decision making under uncertainty \citep[e.g.,][]{gilsch89,KlibMarMuk05,GhirMar02},
+and seems justified by empirical observations too. A prominent example is Ellsberg's paradox
+(\citet{ells61}). A bag contains 90 marbles, 30 are red and the remaining 60 are either black
+or yellow. A marble is to be drawn and DM can win 100€ if she guesses the color of the drawn
+marble. The DM is offered two different bets. In the first one she can choose to bet either on
+red (R) or on yellow (Y), while in the second she can bet either on red or black (RB) or on
+yellow or black (YB), as shown in Table \ref{Ellsberg}.
 
@@
 
-The pattern consistently observed in experimets is: $f_{{\color{red}R}} \succ f_{{\color{yellow}Y}}$ and $f_{{\color{red}R}B} \prec f_{{\color{yellow}Y}B}$.
-This is clearly incompatible with any precise probabilistic belief about the proportion of black and yellow marbles.
-This kind of behavior has been
-famously axiomatized by Gilboa and Schmeidler in a paper from 1989.
-The choice pattern is normally explained in terms of aversion to uncertainty, and the standard representation is given by means of a set of probability measures together with maxmin rule.
-We can think of the DM in Ellsberg's example as maximinimizing expected utility over the probability set $ [\underline{P}(R)=\overline{P}(R)=\frac{1}{3},\underline{P}(Y)=0,\underline{P}(B)=0,\overline{P}(Y)=\frac{2}{3},\overline{P}(B)=\frac{2}{3}]  $.
-This amounts to calculating for any probability measure contained in the probability set the expected utility of any available action, and then to choosing the action that guarantees the highest minimal expected utility.
-The following observation is then trivial.
-
-\begin{fact} \label{fact:singleton probability set}
-Whenever the probability set is a singleton, maximinimization of
-expected utility coincides with maximization of expected utility.
-\end{fact}
-
-Evidence from experimental literature suggests that agents are mainly uncertainty
-averse [REF]. In line with empirical data,
-we assume that players in the population are uncertainty averse and conform to maxmin expected
-utility. The resulting behavior is then produced by maximinimizing the subjective utility
-given by the player's preference type over the set of probabilities given by the belief type.
-
-\section{Meta-games and the evolution of choice mechanisms}
-\label{sec:model}
-
-The standard approach in
-evolutionary game theory is not enough for our purposes, because it (i) fixes a unique and immutable
-\emph{stage game} (e.g., the prisoner's dilemma) and (ii) assumes that the object of
-evolutionary selection is behavior for that very game. Following a line of argument coming from theoretical biology and behavioral ecology
-\citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be}, we therefore turn towards the evolutionary
-competition of \emph{choice mechanisms}, i.e., general ways of selecting concrete behavior
-across a range of different situations, defined by the two functions $\gamma$ and $\kappa$. With this approach, the expected fitness of a choice
-mechanism will not be determined by a unique stage game, but it will be a
-complex function of the statistical properties of the environment: we have to take into account
-how frequently particular concrete situations of choice making are.
-
-For concreteness, let us fix a class of strategic games $\mathcal{G}$ and a probability measure
-$P \in \Delta(\mathcal{G})$ that gives the occurrence probability $P(G)$ of each game
-$G \in \mathcal{G}$. Together, a class of games and a probability measure over it can be
-thought of as a model of the environment in which different choice mechanisms compete.
-As we have seen in Definition \ref{def:maxminSEU}, given a game $G \in \mathcal{G}$, a choice mechanism prescribes the action(s) $\kappa(\gamma(G))$.
-Now imagine a huge, possibly infinite society of agents, each of which carries a choice mechanism, and a class $\mathcal{G}$ of symmetric two player games for simplicity.
-Definition \ref{def:expected evolutionary payoff} gives the expected evolutionary payoff of choice mechanism $\kappa(\tau, e)$ against choice mechanism $\kappa(\tau', e')$ in game $G \in \mathcal{G}$.
-
-\begin{definition} \label{def:expected evolutionary payoff}
-
-Given a game $G \in \mathcal{G}$, a choice mechanism $\kappa(\tau, e)$, and a choice mechanism $\kappa(\tau', e')$, we define $$\pi^G(\kappa(\tau(G), e),\kappa(\tau'(G), e')):= \sum_{a_i \in \kappa(\tau(G), e)} \sum_{a_j \in \kappa(\tau'(G), e')} \pi^G(a_i , a_j) \cdot \frac{1}{|\kappa(\tau(G), e)|} \cdot \frac{1}{|\kappa(\tau'(G), e')|}.$$
-
-\end{definition}
-
-\noindent Then the expected evolutionary fitness $EF_{\mathcal{G}}(\kappa(\tau, e))$ of an agent with
-choice mechanism $\kappa(\tau, e)$ is determined by the probability $P((\tau',e'))$ of meeting an agent with
-choice mechanism $\kappa(\tau',e')$, which we will assume is the frequency of $(\tau',e')$ in the population, the
-probability $P(G)$ of playing game $G \in \mathcal{G}$ and the evolutionary payoff
-$\pi^G(\kappa(\tau, e),\kappa(\tau', e'))$:
-
-\begin{align}
-\label{eq:EF}
-  EF_{\mathcal{G}}(\kappa(\tau, e)) := \sum_{G \in \mathcal{G}} \sum_{(\tau',e') \in T \times E} P(G) \cdot P((\tau',e')) \cdot \pi^G (\kappa(\tau(G), e),\kappa(\tau'(G), e'))\,.
-\end{align}
-
-\noindent Similarly, the expected fitness of a choice mechanism $\kappa(\tau, e)$, when playing against another choice mechanism $\kappa(\tau', e')$ is:
-\begin{align}
-  \label{eq:pairwiseEF}
-  EF_{\mathcal{G}}(\kappa(\tau, e),\kappa(\tau', e')) := \sum_{G \in \mathcal{G}}  P(G) \cdot \pi^G(\kappa(\tau(G), e),\kappa(\tau'(G), e'))\,.
-\end{align}
-
-Notice that the expected fitness of a choice mechanism is defined entirely in parallel to the
-expected payoff of an act in a fixed stage game (Definition \ref{def:expected evolutionary payoff}), except that where the latter has a simple
-payoff function, the former has an expectation over payoffs in a statistically rich
-environment. That means that we can think of evolutionary competition between choice mechanisms
-in terms of payoffs defined by a \emph{meta-game} over $\mathcal{G}$ whose ``acts'' are choice
-mechanisms and whose ``payoffs'' are the expected evolutionary payoffs of
-Equation~(\ref{eq:pairwiseEF}).\footnote{Allowing games in $\mathcal{G}$ with different numbers of players makes matters formally, but not conceptually, more complicated.
-In the following we will focus entirely on two player games, hence we can neglect further complications for the moment.}
-
-\section{The basic model}
-\label{sec:basic-model-1}
-
-To demonstrate the usefulness of a meta-game approach, let us concentrate first on a basic
-model that contains the four choice mechanisms obtained from crossing the preference and belief
-types introduced in Section~\ref{sec:basic-notions}.  For particular empirical purposes, one
-could consult a more specific class $\mathcal{G}$ with appropriate, possibly empirically
-determined probabilities $P(G)$ in order to match the natural environment of a given
-population. But for our theoretical purposes we adopt another approach.
-
-For a first basic
-model, let $\mathcal{G}$ be a set of symmetric two player games with two acts. (We will look at
-extensions and generalizations in Section~\ref{sec:extensions}). More concretely, we imagine the
-class $\mathcal{G}$ to be generated from the generic form table of Table \ref{generic form
-  table}, where $a,b,c,d$ are i.i.d.~random variables sampled from a finite set of natural
-numbers $ \lbrace 0, \dots, 10 \rbrace$.
-After a game $G \in \mathcal{G}$ is generated, players in the population are randomly paired to play the game $G$.
-Each player represents a choice mechanism, and selects an action accordingly.
-At the end of the game, the evolutionary payoffs of each player are recorded, another game $G' \in \mathcal{G}$ is generated, players are randomly paired again, and so on.
-
-\iffalse
-\begin{figure}
-\begin{center}%
-\begin{tabular}{|c|c|c|}
-\hline 
- & I & II\tabularnewline
-\hline 
-\hline 
-I & a;a & b;c\tabularnewline
-\hline 
-II & c;b & d;d\tabularnewline
-\hline 
-\end{tabular}\end{center}
-
-\protect\caption{generic form table for $2 \times 2$ symmetric games}
-\label{generic form table}
-\end{figure}
-\fi
-
-\begin{table}[]
-\centering
-%\caption{generic form table for $2 \times 2$ symmetric games}
-%\label{generic form table}
-\begin{tabular}{|l|l|l|}
-\hline
- & $I$ & $II$ \\ \hline
-$I$ & $a;a$ & $b;c$ \\ \hline
-$II$ & $c;b$ & $d;d$ \\ \hline
-\end{tabular}
-\caption{Generic form table for $2 \times 2$ symmetric games}
-\label{generic form table}
-\end{table}
-
-\subsection{Preference types}
-
-The set of all possible preference types $T$ amounts to the set of all possible functions $ \tau: \mathcal{G} \rightarrow  \Theta $, i.e., $\tau: \mathbb{R}^{4} \rightarrow \mathbb{R}^{4} $.
-However, here we want to focus on some subsets of $T$ that are also meaningful from a decision-theoretic point of view.
-As introduced in Section \ref{sec:basic-notions}, we are mainly interested in two types: the objective type and the regret type.
-In other words, we consider two prominent preference types: a type who has a veridical subjective utility that perfectly matches the objective utility (i.e., the evolutionary fitness), and a type who has a non-veridical regret-based subjective utility.
-
-\iffalse
-
-Given a game $G$ and Definition \ref{defn:parwreg}, it is straightforward to define the
-\textit{regret preference} $\theta^{reg}$ and the \textit{regret type} $\tau^{reg}$ as
-follows.
-
-\begin{definition}[Regret preference] \label{defn:regpref}
-
-For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the regret preference $ \theta^{reg}: A \rightarrow \mathbb{R} $ such that $ \theta^{reg}(a_i,a_{-i})=-\text{reg}(a_i,a_{-i}) $.\footnote{More precisely, this is the negative regret, whereas the (positive) regret, as defined in [halpass], would not have the minus sign at the beginning of the formula.
-Here it will be easier to define the regret in terms of negative regret.}
-
-\end{definition}
-
-\begin{definition}[Regret type] \label{defn:regtype}
-
-Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call regret type the function $\tau^{reg}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{reg}(G)= \theta^{reg}$.
-
-\end{definition}
-
-\noindent Similarly, let us define the \textit{objective preference} $\theta^{\pi}$ and the \textit{objective type} $ \tau^{\pi} $, that we also call $\pi$\textit{-type}, as follows.
-
-\begin{definition}[Objective preference] \label{defn:objpref}
-
-For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the objective preference $ \theta^{\pi}: A \rightarrow \mathbb{R} $ such that $ \theta^{\pi}(a_i,a_{-i})=\pi(a_i,a_{-i}) $.
-
-\end{definition}
-
-\begin{definition}[Objective type] \label{defn:objtype}
-
-Given $ \mathcal{G} $ the class of symmetric $ 2 \times 2 $ games, we call objective type, or $\pi$-type, the function $\tau^{\pi}: \mathcal{G} \rightarrow  \Theta$ such that, for all $G \in \mathcal{G}$, $ \tau^{\pi}(G)= \theta^{\pi}$.
-
-\end{definition}
-
-\fi
-
-\section{Results for the basic model}
-\label{sec:results:-basic-model}
-
-In this section we present results of computer simulations and analytical proofs for the basic
-model with the four choice mechanisms introduced in the previous sections.
-
-\subsection{Numerical simulations}
-\label{sec:numer-simul}
-
-Table~\ref{tab:ExpectedFitness_4Types} gives an approximation of expected fitness, obtained by
-numerical simulation from averaging over $100,000$ randomly sampled games in $\mathcal{G}$ with
-$a,b,c,d \in \lbrace 0, \dots, 10 \rbrace$. Games were sampled repeatedly by
-choosing independently four integers $a,b,c,d \in \lbrace 0, \dots, 10 \rbrace$ uniformly at
-random. For each game, a player type's action choices were determined and payoffs from all
-pairwise encounters recorded. (Whenever a player type would not select a unique action in a
-given game, we recorded unbiased averages over playing either action.) The number in each cell
-of Table~\ref{tab:ExpectedFitness_4Types} is the average payoff for the row player type over
-all 100,000 numbers for each pairing of player types obtained in this way. These averages
-approximate the corresponding average evolutionary fitness of the row player when matched with
-the column player.
-
-\begin{table}[t]
-\centering
-\begin{tabular}{ccccc}
-  \toprule
- & $\tau^{reg}, \Delta$ 
- & $\tau^{\pi}, \Delta$ 
- & $\tau^{reg}, \overline{\mu}$ 
- & $\tau^{\pi}, \overline{\mu}$ \\ 
-  \midrule
-  $\tau^{reg}, \Delta$ & 6.663 & 6.662 & 6.663 & 6.663 \\ 
-  $\tau^{\pi}, \Delta$ & 6.486 & 6.484 & 6.486 & 6.486 \\ 
-  $\tau^{reg}, \overline{\mu}$ & 6.663 & 6.662 & 6.663 & 6.663 \\  
-  $\tau^{\pi}, \overline{\mu}$ & 6.663 & 6.662 & 6.663 & 6.663 \\ 
-   \bottomrule
-\end{tabular}                    
-\caption{Average evolutionary fitness in simulations of 100,000 symmetric $2 \times 2$ games}
-\label{tab:ExpectedFitness_4Types}
-\end{table}
-
-Simulation results obviously reflect Fact~\ref{fact:equivalence2x2} in that all encounters in
-which types $(\tau^{reg}, \Delta)$, $(\tau^{reg}, \overline{\mu})$ or
-$(\tau^{\pi}, \overline{\mu})$ are substituted for one another yield identical results. More
-interestingly, Table~\ref{tab:ExpectedFitness_4Types} shows that the maxmin strategy
-$(\tau^{\pi}, \Delta)$ is strictly dominated by either of the three other strategies:
-in each column (i.e., for each kind of opponent), the maxmin strategy is strictly worse
-than any of the three behaviorally equivalent competitors. This has a number of interesting
-consequences.
-
-Let's begin with a restricted scenario and look at more and more complex cases afterwards. If
-we restrict attention to a population of radically uncertain players, i.e., where only
-belief type $\Delta$ exists, a population of regret types $ \tau^{reg} $ is the only
-\emph{evolutionarily stable state}. An evolutionarily stable state is a state which cannot be
-invaded by a small number of mutants. More strongly, since maxmin play is strictly dominated,
-we expect selection that is driven by expected fitness to invariably weed out maxmin behavior
-in favor of regret minimization. In other words, when taking average payoffs over the class of
-random games considered here, regret minimization is a better choice mechanism than standard maxmin
-from an evolutionary point of view, despite the fact that the former, but not the latter,
-entertains non-veridical subjective preferences.
-
-Next, if we look at the competition between all four types represented in
-Table~\ref{tab:ExpectedFitness_4Types}, $(\tau^{reg}, \Delta)$ is no longer
-evolutionarily stable. Rather, given behavioral equivalence (Fact~\ref{fact:equivalence2x2}),
-types $(\tau^{reg}, \Delta)$, $(\tau^{reg}, \overline{\mu})$, and
-$(\tau^{\pi}, \overline{\mu})$ are all \emph{neutrally stable}
-\citep{Maynard-Smith1982:Evolution-and-t}. But since $(\tau^{\pi}, \Delta)$ is strictly
-dominated and so disfavored by fitness-based selection, we are still drawn to conclude that
-maxmin behavior is weeded out in favor of a population with a random distribution of the
-remaining three types.
-
-Simulation results of the (discrete time) \emph{replicator dynamics}
-\citep{TaylorJonker1978:Evolutionary-St} indeed show that random initial population
-configurations are attracted to states with only three player types:
-$(\tau^{reg}, \Delta)$, $(\tau^{reg}, \overline{\mu})$ and
-$(\tau^{\pi}, \overline{\mu})$. The relative proportions of these depend on the initial
-population.\todo{check uniform notation for player types: round vs.~square brackets}  Nonetheless, this
-variability disappears if we add a small mutation rate to the dynamics. We assume a fixed,
-small mutation rate $\epsilon$ for the probability that a player's preference type \emph{or}
-her belief type changes to another preference type or belief type. The probability
-that a player randomly mutates into a completely different player with altogether
-different preference type and belief type would then be $\epsilon^2$. With these assumptions
-about ``component-wise mutations'', numerical simulations of the (discrete time)
-\emph{replicator mutator dynamics} \citep{Nowak2006:Evolutionary-Dy} show that already for very
-small mutation rates almost all initial populations converge to a single fixed point in which
-the majority of players are regret types. For instance, with $\epsilon = 0.001$, almost all
-initial populations are attracted to a final distribution with proportions:\todo{recalculate
-  these numbers for the actual 4x4 game!}
-
-\begin{center}
-  \begin{tabular}{ccc}
-    $(\tau^{reg}, \Delta)$ & $(\tau^{reg},
-      \overline{\mu})$ & $(\tau^{\pi}, \overline{\mu})$ \\ \hline
-    0.279  &   0.383 &    0.281 
-  \end{tabular}
-\end{center}
-
-What this suggests is that, since biological evolution selects behavior-generating mechanisms,
-not behavior as such, it need not be the case that behaviorally equivalent mechanisms are
-treated equally all the while. If mutation probabilities are a function of individual
-components (i.e., preference and belief types) of such behavior-generating mechanisms, it can be the case that certain components
-are more strongly favored by a process of random mutation and selection. This is exactly the
-case with regret-based subjective preferences in the present example. Since regret-based
-subjective preferences are much better in connection with radical uncertainty than veridical
-preferences are, the proportion of expected regret minimizers in the attracting state is
-substantially higher than that of expected utility maximizers, even though these types are
-behaviorally equivalent. In sum, component-wise mutation could have lead to a majority of
-regret-based players even if, in the context of two-by-two symmetric games, they are behaviorally indiscernible from decision makers with
-veridical preferences, because regret types are better off under radical uncertainty.
-
-\subsection{Analytical results}
-\label{sec:analytical-results}
-
-Results based on the single meta-game in Table~\ref{tab:ExpectedFitness_4Types}, which was
-obtained by averaging over numerical simulations, are not fully general and possibly spoiled by
-random fluctuations in the sampling procedure. Fortunately, for the case of two-by-two symmetric games, the main result that maxmin types $(\tau^{\pi}, \Delta)$ are
-strictly dominated can also be shown analytically for generous general conditions on how likely
-randomly sampled games are. Let $\Lambda$ denote the set of player types in the population, and fix $\kappa$ to be maxmin expected utility as usual.
-
-\begin{proposition} \label{proposition1}
-
- Fix $\Lambda = \lbrace (\tau^{\pi}, \Delta), (\tau^{reg}, \Delta) \rbrace$, and let $\mathcal{G}$ be the class
-  of $2 \times 2$ symmetric games with payoffs sampled from a
-  set of i.i.d.~values with at least three elements in the support. Then, $(\tau^{reg}, \Delta)$ is the only (strict) Nash
-  equilibrium in the resulting meta-game.
-
-\end{proposition}
-
-\begin{proof}
-See Appendix.
-\end{proof}
-
-\noindent The next corollary about evolutionary stability follows from proposition \ref{proposition1}.
-
-\begin{corollary} \label{corollary1}
-
-Fix $\Lambda = \lbrace (\tau^{\pi}, \Delta), (\tau^{reg}, \Delta) \rbrace$, and let $\mathcal{G}$ be the class
-  of $2 \times 2$ symmetric games with payoffs sampled from a
-  set of i.i.d.~values with at least three elements in the support. Then, the unique evolutionarily stable state is a monomorphic population of $(\tau^{reg}, \Delta)$-players.
-
-\iffalse
-
-  Fix $T = \lbrace \tau^{\pi}, \tau^{reg} \rbrace$,
-  $E = \lbrace \Delta(A_{-i}), \overline{\mu} \rbrace$, $\Lambda= T \times E$, and
-  $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite,
-  or compact and convex, set of i.i.d. values. Then, player type $(\tau^{\pi}, \Delta(A_{-i}))$
-  is strictly dominated by $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
-  $(\tau^{reg}, \overline{\mu})$.
-\fi
-
-\end{corollary}
-
-\begin{proof}
-See Appendix.
-\end{proof}
-
-Proposition \ref{proposition1} and Corollary~\ref{corollary1} tell us that the conclusions drawn in the previous section based on
-the meta-game in Table~\ref{tab:ExpectedFitness_4Types} hold more generally for any class of
-games in which the probability of encountering a game is the product of independently sampling
-four identically distributed payoff values. As before,
-$(\tau^{reg}, \Delta)$, $(\tau^{\pi}, \overline{\mu})$, and
-$(\tau^{reg}, \overline{\mu})$ players will be neutrally stable, and fitness-based selection will tend
-to weed out maxmin play and leave us with a population of arbitrary frequency of
-$(\tau^{reg}, \Delta)$, $(\tau^{\pi}, \overline{\mu})$, and
-$(\tau^{reg}, \overline{\mu})$ players.
-
-This shows that there is support for the main conceptual point that we wanted to make:
-non-veridical subjective preference relations \emph{can}, under specific circumstances, persist
-under evolutionary selection based on objective fitness. Moreover, regret-based preferences can
-not only persist, but even be favored by natural selection if agents are radically
-uncertain. This holds generally for playing arbitrary $2 \times 2$ symmetric games whose payoffs are
-sampled identically and independently at random.
-
-\section{Extensions}
-\label{sec:extensions}
-
-How do the basic results from the previous section carry over to more encompassing, richer
-models? Section~\ref{sec:more-types} first introduces further conceptually interesting
-preference types that have been considered in evolutionary game theory. Section~\ref{sec:n-times-n}
-then addresses the case of $n \times n$ games for $n \ge 2$. Finally, to put our results into
-a broader perspective, Section~\ref{sec:solitary-decisions} ends with a brief comparison of
-game situations with cases of solitary decision making.
-
-\subsection{More types}
-\label{sec:more-types}
-
-In evolutionary game theory other types of player have been investigated.
-A famous example is the \textit{altruistic type} [REF], introduced in the literature in order to explain the possible survival of altruistic behavior.
-In our framework, we can represent the altruistic type as follows.
-
-\iffalse
-
-\begin{definition}[Altruistic preference] \label{defn:altpref}
-
-For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{alt}: A \rightarrow \mathbb{R} $ such that $ \theta^{alt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \sum_{j \neq i} \pi(a_{j},a_{-j})$.\footnote{A more general formulation [see: REFERENCES] would be to define an $ \alpha$-altruistic type, for $\alpha \in [0,1]$, with subjective utility $ \theta^{\alpha lt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \alpha \sum_{j \neq i} \pi(a_{j},a_{-j})$.
-Since we are not interested in the evolution of degrees of altruism here, we simply fix $ \alpha = 1 $.}
-
-\end{definition}
-
-\fi
-
-\begin{definition}[Altruistic type] \label{defn:alttype}
-
-Given a two player game  $ G $, the \textit{altruistic type} $\tau^{alt}$ is characterized by the subjective utility function $\tau^{alt}(G)(a_i, a_j):=\pi_i(a_i,a_j) + \pi_j(a_i,a_j)$.\footnote{A more general formulation would be to define an $ \alpha$-altruistic type, for $\alpha \in [0,1]$, with subjective utility $ \tau^{\alpha lt}(G)(a_i, a_j):=\pi_i(a_i,a_j) + \alpha \pi_j(a_i,a_j)$.
-Since we are not interested in the evolution of degrees of altruism, here we simply fix $ \alpha = 1 $.}
-
-\end{definition}
-
-\noindent As opposite to the altruistic type, it is possible to define a \textit{competitive type}.
-
-\iffalse
-
-\begin{definition}[Competitive preference] \label{defn:compref}
-
-For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the competitive preference $ \theta^{com}: A \rightarrow \mathbb{R} $ such that $ \theta^{com}(a_i,a_{-i})=\pi(a_i,a_{-i}) - \sum_{j \neq i} \pi(a_{j},a_{-j})$.
-
-\end{definition}
-
-\fi
-
-\begin{definition}[Competitive type] \label{defn:comtype}
-
-Given a two player game  $ G $, the \textit{competitive type} $\tau^{com}$ is characterized by the subjective utility function $\tau^{com}(G)(a_i, a_j):=\pi_i(a_i,a_j) - \pi_j(a_i,a_j)$.
-
-\end{definition}
-
-Similarly to the evolutionary competition that we simulated before, we can study the
-evolutionary fitness of this extended set of players when they are all represented in the
-population. Table~\ref{tab:ExpectedFitness_2x2_Full} shows simulation results that approximate the
-expected fitness in the relevant meta-game.
-
-\begin{table}[]
-\centering
-\footnotesize
-\begin{tabular}{ccccccccc}
-  \hline
- & $(\tau^{reg}, \Delta)$ 
- & $(\tau^{\pi}, \Delta)$ 
- & $(\tau^{com}, \Delta)$
- & $(\tau^{alt}, \Delta)$
- & $(\tau^{reg}, \overline{\mu})$ 
- & $(\tau^{\pi}, \overline{\mu})$ 
- & $(\tau^{com}, \overline{\mu})$
- & $(\tau^{alt}, \overline{\mu})$ \\ 
-  \hline
-  $(\tau^{reg}, \Delta)$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
-  $(\tau^{\pi}, \Delta)$ & 6.486 & 6.484 & 6.088 & 6.703 & 6.486 & 6.486 & 6.088 & 6.875 \\
-  $(\tau^{com}, \Delta)$ & 6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\
-  $(\tau^{alt}, \Delta)$ & 5.949 & 5.722 & 5.326 & 6.396 & 5.949 & 5.949 & 5.326 & 6.568 \\
-  $(\tau^{reg}, \overline{\mu})$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
-  $(\tau^{\pi}, \overline{\mu})$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
-  $(\tau^{com}, \overline{\mu})$ & 6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\
-  $(\tau^{alt}, \overline{\mu})$ & 6.331 & 5.893 & 5.497 & 6.566 & 6.331 & 6.331 & 5.497 & 7.152 \\
-   \hline                          
-\end{tabular}                      
-\caption{Average payoff in simulations of 100,000
-  randomly generated $2 \times 2$ symmetric games}
-\label{tab:ExpectedFitness_2x2_Full}        
-\end{table}
-
-\todo[inline]{is it true that competitive preferences types are behaviorally equivalent under
-  either epistemic type? can we show that?}
-
-The approximations in Table~\ref{tab:ExpectedFitness_2x2_Full} confirm basic intuitions about
-altruistic and competitive types: averaging over randomly sampled games, everybody would like
-to have an altruistic opponent and nobody would like to play against a competitive
-opponent. Perhaps more surprisingly, altruistic types come up strictly dominated by competitive
-types, but competitive types themselves are worse off against all opponent types except against
-maxmin players $(\tau^{\pi}, \Delta)$ than any of the behaviorally equivalent types
-$(\tau^{reg}, \Delta)$, $(\tau^{\pi}, \overline{\mu})$, and
-$(\tau^{reg}, \overline{\mu})$. 
-\iffalse
-This is a noteworthy results in the light of the fact that
-evolving altruistic preferences have been shown to support cooperative behavior in a single
-stage game \myalert{[CITE]}. In contrast,
-averaging over payoffs in multiple stage games, like we do here, makes altruistic preferences
-prime victims of evolutionary eradication.
-\fi
-It is easy to see then that the previous result still obtains for the larger meta-game in
-Table~\ref{tab:ExpectedFitness_2x2_Full}: $(\tau^{reg}, \Delta)$,
-$(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$ are still neutrally stable;
-all simulations of the (discrete-time) replicator dynamic on the $8 \times 8$ meta-game from
-Table~\ref{tab:ExpectedFitness_2x2_Full} end up in populations consisting of only these players
-in arbitrary proportion.
-
-\iffalse
-
-The following proposition (partially) confirms this result.\todo{rephrase to acknowledge all
-  epistemic types?}
-
-\begin{proposition} \label{proposition2}
-
-Fix $\Lambda = \lbrace (\tau^{\pi}, \Delta), (\tau^{reg}, \Delta), (\tau^{alt}, \Delta), (\tau^{com}, \Delta) \rbrace$ and $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex, set of i.i.d.
-values.
-Then, $(\tau^{reg}, \Delta)$ is the only evolutionarily stable player in the population.
-
-\end{proposition}
-
-\begin{proof}
-See Appendix.\todo{is this there already?}
-\end{proof}
-
-\fi
-
-In sum, the presence of other plausible preference types, such as competitive and altruistic
-types does not undermine the previous results about the evolutionary drive towards regret-based
-subjective preferences.
-
-\subsection{More actions: $n \times n$ symmetric games}
-\label{sec:n-times-n}
-
-Results from Section~\ref{sec:results:-basic-model} relied heavily on
-Fact~\ref{fact:equivalence2x2} that, for the special case of $2 \times 2$ symmetric games,
-regret minimization $(\tau^{reg}, \Delta)$ is behaviorally equivalent with expected
-regret minimization $(\tau^{reg}, \overline{\mu})$ and expected utility maximization
-$(\tau^{\pi}, \overline{\mu})$. This is no longer true when we look at arbitrary $n \times n$
-games with $n \ge 2$. We should therefore see what happens in a broader class of games.
-
-Table~\ref{tab:ExpectedFitness_10x10} gives approximations for expected fitness in a
-meta-game over a class of $n \times n$ symmetric games where $n$ is randomly drawn from
-$\set{2, \dots, 10}$. Concretely, the numbers in Table~\ref{tab:ExpectedFitness_10x10} are
-averages of payoffs obtained in 100,000 randomly sampled games, where each game was sampled by
-first picking a number of acts $n \in \set{2, \dots, 10}$ uniformly at random, and then filling
-the resulting $n \times n$ payoff matrix of the stage game with i.i.d.~sampled payoffs as
-before.
-
-\begin{table}[]
-\centering
-\footnotesize
-\begin{tabular}{ccccccccc}
-  \toprule
- & $(\tau^{reg}, \Delta)$ 
- & $(\tau^{\pi}, \Delta)$ 
- & $(\tau^{com}, \Delta)$
- & $(\tau^{alt}, \Delta)$
- & $(\tau^{reg}, \overline{\mu})$ 
- & $(\tau^{\pi}, \overline{\mu})$ 
- & $(\tau^{com}, \overline{\mu})$
- & $(\tau^{alt}, \overline{\mu})$ \\ 
-  \midrule
-  $(\tau^{reg}, \Delta)$ & 6.567 & 6.570 & 5.650 & 6.992 & 6.564 & 6.564 & 5.593 & 7.409 \\
-  $(\tau^{\pi}, \Delta)$ & 6.476 & 6.483 & 5.896 & 6.818 & 6.484 & 6.484 & 5.850 & 7.124 \\
-  $(\tau^{com}, \Delta)$ & 6.468 & 6.647 & 5.512 & 7.169 & 6.578 & 6.578 & 5.577 & 7.354 \\
-  $(\tau^{alt}, \Delta)$ & 5.968 & 5.923 & 5.363 & 6.685 & 5.975 & 5.975 & 5.086 & 6.973 \\
-  $(\tau^{reg}, \overline{\mu})$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
-  $(\tau^{\pi}, \overline{\mu})$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
-  $(\tau^{com}, \overline{\mu})$ & 6.529 & 6.680 & 5.445 & 7.276 & 6.542 & 6.542 & 5.521 & 7.440 \\
-  $(\tau^{alt}, \overline{\mu})$ & 6.450 & 6.337 & 5.772 & 6.978 & 6.457 & 6.457 & 5.479 & 7.500 \\
-   \bottomrule                         
-\end{tabular}                      
-\caption{Average payoff in simulations of 100,000
-  randomly generated $n \times n$ symmetric games with $n$ randomly drawn from $\set{2, \dots, 10}$.}
-\label{tab:ExpectedFitness_10x10}        
-\end{table}
-
-As is to be expected, average payoffs obtained in games with more than 2 acts are higher, as
-can be seen by comparing Table~\ref{tab:ExpectedFitness_10x10} with
-Table~\ref{tab:ExpectedFitness_2x2_Full}. But increases in approximate expected fitness are not
-uniform. Most importantly, the regret minimizing type $(\tau^{reg}, \Delta)$ is
-strictly dominated by $(\tau^{reg}, \overline{\mu})$ and by $(\tau^{\pi}, \overline{\mu})$ in
-the meta-game from Table~\ref{tab:ExpectedFitness_10x10}. This means that while regret
-minimization \emph{can} thrive in some evolutionary contexts, there are also contexts where it
-is demonstrably worse off.
-
-Still, although this may be bad news for regret minimizing types
-$(\tau^{reg}, \Delta)$, it is not the case that regret types \emph{as such} are weeded
-out by selection. Since, by Fact~\ref{fact:maxEU-minReg}, $(\tau^{reg}, \overline{\mu})$ and
-$(\tau^{\pi}, \overline{\mu})$ are generally behaviorally equivalent, it remains that
-selection based on meta-games constructed from $n \times n$ games will still not eradicate all
-regret types. So, although regret types may not be selected for in this case, they are also not
-selected against.
-
-On the other hand, there are plenty of ways in which the basic insight from
-Proposition~\ref{proposition1} that regret-based preferences can be strictly better than
-veridical objective preferences in case of radical uncertainty could make for situations in
-which evolution would select for regret types exclusively, even in $n \times n$ games. If, for
-example, epistemic types of players are not what biological evolution selects, but rather
-something that the particular choice situation would exogenously give us, then regret-based
-preference \emph{can} again drive out veridical preferences altogether. For concreteness,
-suppose that only preference types compete and that agents' belief types are exogenously
-given, in such a way that agents hold flat probabilistic beliefs $\overline{\mu}$ with probability
-$1-p$ and are of type $\Delta$ with probability $p$. This transforms the meta-game from
-Table~\ref{tab:ExpectedFitness_10x10} into the simpler $4 \times 4$ game in which the payoff
-obtained for a preference type is the weighted average over the payoffs of that preference
-types in Table~\ref{tab:ExpectedFitness_10x10}. Setting $p = 0.02$ for illustration, we get the
-meta-game in Table~\ref{tab:ExogeneousEpistemics}.
-
-\begin{table}[]
-\centering
-\begin{tabular}{ccccc}
-  \toprule
-  & $\tau^{reg}$ 
-  & $\tau^{\pi}$ 
-  & $\tau^{com}$
-  & $\tau^{alt}$ \\ 
-  \midrule
-  $\tau^{reg} $ & 6.926 & 6.926 & 5.942 & 7.757 \\ 
-  $\tau^{\pi} $ & 6.924 & 6.924 & 5.948 & 7.751 \\ 
-  $\tau^{com }$ & 6.566 & 6.570 & 5.481 & 7.434 \\ 
-  $\tau^{alt} $ & 6.463 & 6.461 & 5.478 & 7.469 \\ 
-   \bottomrule
-\end{tabular}
-\caption{Meta-game for the evolutionary competition between preference types when epistemic types are exogenously
-  given}
-\label{tab:ExogeneousEpistemics}
-\end{table}
-
-The only evolutionarily stable state of this meta-game is the regret type. Accordingly, all of
-our simulation runs of the (discrete-time) replicator dynamic converged to monomorphic
-regret-type populations. The reason why regret types prosper is because they have a substantial
-payoff advantage if paired with radical uncertainty. If radical uncertainty is exogenously
-given as something unavoidable that happens to agents (e.g., in situation where they really have no
-way of narrowing down the probability set), and even if that happens only very
-infrequently (i.e., for rather low $p$), regret types \emph{will} outperform veridical
-preference types, as well as competitive and altruistic types.
-
-\subsection{Solitary decisions}
-\label{sec:solitary-decisions}
-
-\todo[inline]{text in this section and the next is rough and unpolished, only intended to have
-  the basic results recorded, so that we can reshape the article around the basic results}
-
-To see how different choice mechanisms behave in evolutionary competition based on solitary decision
-problems, we approximated, much in the spirit of meta-games, average accumulated payoffs
-obtained in randomly generated solitary decision problems. For our purposes, a decision problem
-$\tuple{S, \Acts, u}$ consists of a set of world states $S$, a set of acts
-$\Acts$, and a utility function $u \mycolon S \times \Acts \rightarrow
-\mathbb{R}$.
-We generated arbitrary decision problems by selecting numbers of states and acts
-$n_s, n_\act \in \set{2, \dots, 10}$ and then filling the utility table, so to speak, by
-independently picking a number $u(s, \act) \in \set{0, 10}$ uniformly at random, just
-as we did before with symmetric games. Unlike with two-player games, we need to also sample the
-actual state of the world, which we selected uniformly at random from the available states in
-the current decision problem. Player types, consisting of epistemic types $\overline{\mu}$ and
-$\Delta$ and preference types $\tau^{reg}$ and $\tau^{\pi}$, give rise to behavior in
-the same way as before.\footnote{Obviously, now with $ \Delta \equiv \Delta(S) :=\lbrace \mu \in \mathbb{R}^{S}: \sum_{s \in S} \mu(s) = 1 \rbrace$.} (It is obviously not possible to carry altruistic or competitive
-preference types over to solitary decision making.) As before, we recorded the behavioral
-decisions for each of the four relevant player types in each sampled decision problem, and
-determined the actual payoff obtained, given the actual state. Average payoff over 100,000 decision
-problems are given in Table~\ref{tab:SolitaryDecisions}.
-
-\begin{table}
-  \centering
-  \begin{tabular}{cccc}
-    \toprule
-   $(\tau^{reg}, \Delta)$ 
- & $(\tau^{\pi}, \Delta)$ 
- & $(\tau^{reg}, \overline{\mu})$ 
- & $(\tau^{\pi}, \overline{\mu})$ 
- \\ \midrule
-    6.318 & 6.237 & 6.661 & 6.661 \\ \bottomrule
-  \end{tabular}
-  \caption{Average payoffs over 100,000 simulated solitary decision problems}
-  \label{tab:SolitaryDecisions}
-\end{table}
-
-Facts~\ref{fact:maxEU-minReg} and \ref{fact:equivalence2x2} still apply:
-$(\tau^{reg}, \overline{\mu})$ and $(\tau^{\pi}, \overline{\mu})$ are behaviorally equivalent
-in general, and $(\tau^{reg}, \Delta)$ is behaviorally equivalent to the former two in
-decision problems with 2 states and 2 acts. \todo{show this?} We see this in part in the
-results in Table~\ref{tab:SolitaryDecisions} in that the averages for $(\tau^{reg},
-  \overline{\mu})$ and $(\tau^{\pi}, \overline{\mu})$ are identical. But since we included decision
-problems with more acts and more states as well, the averages for regret minimizers
-$(\tau^{reg}, \Delta)$ are not identical to the one of $(\tau^{reg},
-  \overline{\mu})$ and $(\tau^{\pi}, \overline{\mu})$. They are, in fact, lower, but not as low as
-those of the minimax choosers.
-
-What that means is that basically every relevant result we have seen about game situations is also borne out
-when reasoning about solitary decisions. Evolutionary selection based on objective fitness will
-not select against regret-based subjective preferences, as these are indistinguishable from
-veridical preferences when paired with probabilistic beliefs. But when paired with
-non-probabilistic belief types, regret-based preferences actually outperform veridical
-preferences. Consequently, if there is a chance, however small, that agents must fall back onto
-non-probabilistic beliefs, evolution will actually positively select for non-veridical
-regret-based preferences.
-
-\iffalse
-\subsection{Arbitrary probabilistic beliefs}
-\label{sec:arbitr-prob-beli}
-
-So far, we have assumed that epistemic types $\overline{\mu}$ hold an unbiased, flat belief. It is
-worthwhile considering what happens when this assumption is relaxed and we allow agents with
-probabilistic beliefs to make use of the full spectrum of probabilistic beliefs. It should be
-clear that quality of beliefs directly impacts prospects of successful decision making: if a
-decision maker knows the actual state, or can put a high level of credence on the actual state,
-accumulated fitness can be expected to be high. We see this, unsurprisingly, in numerical
-simulations. We looked at the average payoff accumulated in 100,000 decision problems sampled
-as before, except that for belief types with probabilistic beliefs we sampled a random
-probabilistic belief $p$ (from an unbiased Dirichlet distribution) and chose the actual world
-state with probability weights $p$. This effectively implements a bias for beliefs of the
-decision maker that tend to put more weight on the actual state (although the procedure does
-admittedly perverse the natural chicken-and-egg logic in this case that the actual world state
-should come first and beliefs be a function of it). As a result, the average payoffs of types
-$\tuple{\tau^{reg}, \overline{\mu}}$ and $\tuple{\tau^{\pi}, \overline{\mu}}$ are still the exact same
-(because we compare what agents with different preference types would do under the same
-beliefs; we are not interested in statistical fluctuations given one type better beliefs by
-pure happenstance), but with $7.125$ notably higher than before. In effect, better
-probabilistic beliefs lead to better decisions. If agents can learn, reason and extrapolate to
-form better probabilistic beliefs, that will help them whenever they take their beliefs into
-account.
-
-But this is orthogonal to the arguments in this paper, where the focus is on possibilities for
-the evolution of non-veridical preferences. We know from Fact~\ref{fact:maxEU-minReg} that
-regret types and veridical preference types, when paired with probabilistic belief types that
-maximize/minimize expectations, are behaviorally equivalent, \emph{no matter what they believe},
-as long as they belief the same. So, if learning, insight and statistical knowledge of a
-recurrent situation \emph{can} be brought to bear, this will not make evolution select against
-regret-based preferences. If, on the other hand, agents have no basis for probabilistic
-beliefs, then we have shown that there are general and basic circumstances in which
-regret-based preferences can actually be selected, despite their non-veridicality.
-\fi
-
-\section{Conclusion} \label{sec:conclusion}
-
-The assumption that players and decision makers maximize their (subjective) preferences is central through all economic literature, and the maximization of actual (objective) payoffs is often justified by appealing to evolutionary arguments and natural
-selection. In contrast to the standard view, we showed the
-existence of player types with subjective utilities different
-from the actual payoffs that can outperform types whose
-subjective utilities coincide with the actual payoffs.
-While the literature on evolution of preference has focused
-on fixed games, or fixed types of games, we have adopted a
-more general approach here. We suggested that attention
-to “meta-games” is crucial, because what may be a good
-subjective representation in one type of game (e.g., cooperative preferences in the Prisoner’s Dilemma class) need not
-be generally beneficial. Taken together, we presented a variety of plausible circumstances in which evolutionary competition between choice
-mechanisms on a larger class of games can favor subjective
-preference representations focusing on regret.
-
-Finally, we hope to help the research direction towards a broader perspective on evolutionary game theory, as outlined by recent works in theoretical biology \citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be}.
-In partcular, the meta-game approach allows the researcher to both explicitly model the relevant features of the environment and shift the target of evolution from plain behavior to more general behavioral patterns, or choice mechanisms.
-Several uses and improvements of the present model are still possible in many respects.
-We can sketch some of them here.
-For example, the evolutionary investigation of different risk and ambiguity attitudes when competing against each other in an evolutionarily richer environment may bring new insights on both behavioral and theoretic decision making under uncertainty, as well as on many issues in theoretical biology and behavioral ecology.
-
-\appendix
+The pattern consistently observed in experimets is:
+$f_{{\color{red}R}} \succ f_{{\color{yellow}Y}}$ and
+$f_{{\color{red}R}B} \prec f_{{\color{yellow}Y}B}$. This is clearly incompatible with any
+precise probabilistic belief about the proportion of black and yellow marbles. This kind of
+behavior has been famously axiomatized by Gilboa and Schmeidler in a paper from 1989. The
+choice pattern is normally explained in terms of aversion to uncertainty, and the standard
+representation is given by means of a set of probability measures together with maxmin rule. We
+can think of the DM in Ellsberg's example as maximinimizing expected utility over the
+probability set
+$
+[\underline{P}(R)=\overline{P}(R)=\frac{1}{3},\underline{P}(Y)=0,\underline{P}(B)=0,\overline{P}(Y)=\frac{2}{3},\overline{P}(B)=\frac{2}{3}]
+$.
+This amounts to calculating for any probability measure contained in the probability set the
+expected utility of any available action, and then to choosing the action that guarantees the
+highest minimal expected utility.
+
+Evidence from experimental literature suggests that agents are mainly uncertainty averse
+[REF]. In line with empirical data, we assume that players in the population are uncertainty
+averse and conform to maxmin expected utility. The resulting behavior is then produced by
+maximinimizing the subjective utility given by the player's preference type over the set of
+probabilities given by the belief type.
 
 \section{Proofs}
+\label{sec:proofs}
 
@@
 and on some lemmas. For brevity, let us denote the regret minimizer
-by $R$ and the maximinimizer by $M$, i.e, $R \equiv \kappa(\tau^{reg}, \Delta)$ and $M \equiv  \kappa(\tau^{\pi}, \Delta)$.
+by $R$ and the maximinimizer by $M$, i.e, $R \equiv \kappa(\text{reg}, \text{imp})$ and $M \equiv  \kappa(\text{obj}, \text{imp})$.
 Recall from Equation \ref{eq:pairwiseEF} that $EF_{\mathcal{G}}(X,Y)$ denotes the expected evolutionary fitness of choice mechanism $X$ against choice mechanism $Y$
@@
 
-\iffalse
-
-\newpage
-
-\section{Snippets}
-
-[More precisely, from the meta-game perspective many possible subjective
-transformations of the objective utility are eliminated by evolution, but we find some
-evolutionarily stable subjective utility maximizers whose utility does not coincide with the
-objective evolutionary utility. This result leaves some room in between the two extrema: we can
-understand rationality in a normative way, given by evolution, without having to discard all
-the possible subjective utility representations as irrational. CHANGE PLACE OF THIS MAYBE]
-
-\subsection{Version 2}
-
-The importance of aiming at a richer evolutionary game theory has been recently emphasized by many works in theoretical biology and behavioral ecology [Fawcett\&al., McNamara, etc.].
-The biological argument to embrace this goal is related to the criticisms towards the so-called behavioral gambit [Fawcett\&al.].
-The behavioral gambit denotes the standard approach in evolutionary game theory that puts the focus of attention on the expressed behavior, and neglects the underlying mechanisms that generate that behavior.
-From this point of view, the benefit and the reliability coming from the use of evolutionary game theory for biological purposes is also under attack.
-There are good reasons to claim that focusing on the general psychological mechanisms instead of on behavior itself as the phenotype under evolutionary selection can be more faithful and insightful for natural biology and ecology [Fawcett\&al.].
-Standard evolutionary game theory normally models the agents as playing a single fixed game, and as genetically predetermined to play fixed strategies, that consequently are the only target of natural selection in those frameworks.
-Standard models of evolutionary game theory cannot take charge of this shift of perspective until they will keep modelling a single game at a time, and until they will keep focusing on actions considered genetically encoded and fixed.
-''Instead we should expect animals to have evolved a set of psychological mechanisms which enable them to perform well on average across a range of different circumstances''[Fawcett\&al.].
-
-Attempts to overcome the behavioral gambit have recently been developed in economic literature too.
-In the last twenty years economists have been using evolutionary game-theoretical models to study evolution of preferences [cite], instead of evolution of behavior only.
-This approach is called indirect evolutionary approach, because players' behavior and actions stem from their subjective preferences, and it is aimed at investigating what subjective preferences are evolutionarily better off and robust with respect to natural selection.
-This shift from a direct evolutionary approach about observed actions and behavior to an indirect evolutionary approach takes only partly into account the behavioral gambit criticized by biologists and ecologists.
-The reason is that the models of evolution of preferences usually consider only one game at a time.
-This means that there is a single type of interaction that is supposed to drive the whole evolution of preferences: preferences are selected on the basis of one possible interaction only.
-Clearly, this approach does not take into consideration the variety of possible circumstances that animals are supposed to face during their lifetime.
-
-The meta-game model we propose pays heed to both components of the behavioral gambit.
-We retain the indirect evolutionary approach, but our agents in the population play over a class of possible games $\mathcal{G}$.
-In this way we explicitly model a range of different circumstances, as wished by theoretical biologists.
-Consequently, each agent in the population does not represent either a simple behavior or a subjective preference, but a more general player type that associates a subjective preference for each game in the class $\mathcal{G}$.
-The player type is supposed to encode the general psychological mechanisms that generate the behavior for any possible interaction in $\mathcal{G}$.
-These general psychological mechanisms then become the target of evolution, and they are selected based on the average fitness over a class of different interactions.
-
-In particular, in the following we mainly deal with two types of agents: players whose subjective preference coincides with the evolutionary fitness, and players whose subjective preference is defined in terms of regret.
-It turns out that psychological mechanisms and subjective conceptualizations based on regret can outperform more veridical conceptualizations coinciding with the evolutionary fitness.
-This is just an example of the kind of insights and results that we can gain by adopting a meta-game perspective and by shifting the focus of our attention to psychological mechanisms and subjective conceptualizations as the phenotype under selection.
-
--maybe to add: difference with learning. Fawcett\&al. talk more about differences in learning, whereas we model differences in subjective conceptualizations.
-
-[A pivotal element of economics and decision theory is the definition of rationality as
-maximization of subjective preferences.]
-
-\begin{itemize}
-\item We present an approach to studying evolutionary selection of \emph{choice principles},
-  i.e., ways of choosing consistently across several games. In other words, we would like to
-  look at the problem of ``rational choice'' from an evolutionary point of view: what choice
-  principles would be promoted, which demoted in evolutionary competition amongst each other?
-
-\item This depends on the environment; it depends on what choice situations occur how
-  frequently. Maybe some choice principle is better in some situations, while another one is
-  better in others.
-
-\item We argue that this ``meta-evolutionary'' approach could eventually help explain attested
-  deviations of human decision making from the classic ideal: choice behavior evolved to be
-  an ``ecologically rational'', near-optimal adaptation to the environment
-  \citep{Anderson1990:The-Adaptive-Ch,Anderson1991:Is-human-cognit,GigerenzerGoldstein1996:Reasoning-the-F,ChaterOaksford2000:The-Rational-An}. This
-  is inline with recent aspirations to provide an evolutionary rationale for decision making
-  processes
-  \citep[e.g.,][]{HammersteinStevens2012:Six-Reasons-for,FawcettHamblin2013:Exposing-the-be}. Here,
-  we seek to contribute to the formal machinery, an extension of evolutionary game theory, that
-  allows to capture statistical properties of the environment
-  \citep[cf.][]{McNamara2013:Towards-a-Riche}.
-\end{itemize}
-
-\subsection{The environment: meta-games}
-
-\begin{itemize}
-\item imagine huge, virtually infinite population of agents, each carrying a choice principle
-\item agents play a randomly sampled game against a randomly sampled opponent
-\item fitness is based on the average payoff of choice principle A against choice principle B,
-  taken over arbitrary games $g$ and weighted their occurrence probability $P(g)$:
-  $\int_g P(g) \times U_g(\text{CP-A}, \text{CP-B}) \text{d}g$
-\item the occurrence probability of games $g$ is the ``environment'' and, possibly, impossible to
-  derive theoretically, or to measure empirically
-\item here, use a relatively neutral approach instead that is practicable:
-  \begin{itemize}
-  \item games are individuated by their payoff matrices (no framing effects or similar)
-  \item each entry in a payoff matrix is an i.~i.~d.~random variable
-    \begin{itemize}
-    \item approach still incorporates a bias (e.g., against strategic form representations of
-      sequential games)
-    \end{itemize}
-  \end{itemize}
-\item example: average payoffs from numerical simulation of ($2 \times 2$ symmetric games)
-\item example: average payoffs from numerical simulation of ($n \times n$ symmetric games, with
-  $n$ uniformly random (up to some upper-bound))
-\end{itemize}
-
-\begin{itemize}
-\item Evolutionary game theory has become an established philosophical tool for probing into
-  conceptual issues whose complexity requires mathematical modeling.
-  \begin{itemize}
-  \item helped structure debate about foraging, mating, evolution of cooperation,
-    information-flow, deception etc.
-  \end{itemize}
-\item Most applications of EGT look at evolutionary selection of behavior in a single
-  game. There are two crude simplifications here:
-  \begin{enumerate}
-  \item The stage game is usually considered fixed, closed and immutable.
-    \begin{itemize}
-    \item there are some notable exceptions where the game is open ended, e.g., by the
-      invention of actions \citep{WordenLevin2007:Evolutionary-es,
-        McKenzie-AlexanderSkymrs2012:Inventing-New-S}
-    \end{itemize}
-  \item What evolves are behavioral strategies for the stage game \citep[what][call the
-    ``behavioral gamit'']{FawcettHamblin2013:Exposing-the-be} \myalert{(more references!
-      Gigerenzer etc.)}.
-  \end{enumerate}
-\item It has been argued that we should rather study the evolutionary selection of \emph{choice
-    mechanisms} that are adapted in a rich and variable environment
-  \citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche}.
-\item However, studies on the adaptive value of choice mechanisms have focused, for the most
-  part, on the evolutionary benefit of learning rules
-  \citep[e.g.,][]{ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o}. (\myalert{More references Harley 1981!!!, \dots}). 
-    Moreover, only little attention has been paid to
-  modeling the direct (game-theoretic) meta-competition between alternative choice mechanisms
-  \citep[see][for related criticism]{FawcettHamblin2013:Exposing-the-be}.
-\item Here, we would like to make two contributions to the literature on evolution of choice
-  mechanisms:
-  \begin{enumerate}
-  \item On the conceptual side, we argue that paying attention to the evolution of (subjective
-    representations of) preferences matters. Since almost any reasonable learning or
-    decision making process will make use of some (subjective, agent-internal (possibly
-    unconscious)) representation of the quality of choice options, the question of which such
-    representations are ecologically valuable (i.e., lead to high fitness) is central. In fact,
-    the evolution of (subjective representations of) preferences has recently been studied in
-    theoretical economics as well \myalert{add references}. However, these studies also suffer
-    from the ``behavioral gambit'' and the usual shortcomings of the closedness of the stage game. 
-  \item On the methodological side, we therefore introduce a conservative extension of the
-    standard EGT that allows us to reuse notions such as evolutionary stability / evolutionary
-    dynamics and yet helps us study the evolutionary competition between choice mechanisms in a
-    statistically variable environment. Concretely, we look at the evolutionary competition of
-    choice mechanisms in a ``meta-game'' that consists of the average expected payoffs of
-    choice mechanisms when playing arbitrary games (from a given class). In this sense, a
-    meta-game captures (the modeller's) assumptions about the relevant statistic of the
-    environment in which evolutionary forces operate.
-  \end{enumerate}
-\item To drive home our conceptual point that preference representations can matter, we try to
-  isolate, as good as we can, the evolution of preferences from considerations of learning or
-  other factors feeding a decision mechanism (such as the acquisition of ecologically useful
-  representations (think: beliefs)). (Obviously, eventually, we would like to study the
-  evolution of all of these relevant components in one swoop.)
-\item To demonstrate how this approach can be theoretically rewarding, we show that, under
-  reasonable additional assumptions, evolutionary selection can support non-veridical
-  representations of payoffs in terms of regret.
-  \begin{itemize}
-  \item We argue that this ``meta-evolutionary'' approach could eventually help explain
-    attested deviations of human decision making from the classic ideal: choice behavior
-    evolved to be an ``ecologically rational'', near-optimal adaptation to the environment
-    \citep{Anderson1990:The-Adaptive-Ch,Anderson1991:Is-human-cognit,GigerenzerGoldstein1996:Reasoning-the-F,ChaterOaksford2000:The-Rational-An}. This
-    is inline with recent aspirations to provide an evolutionary rationale for decision making
-    processes
-    \citep[e.g.,][]{HammersteinStevens2012:Six-Reasons-for,FawcettHamblin2013:Exposing-the-be}.
-  \item Non-veridical regret-based representations of payoffs are intuitively appealing (we do,
-    at least on occasion, care about counterfactual or hypothetical losses), but could also
-    help explain, for instance, that decision-makers may violate the independence axiom: human
-    and non-human decision makers can favor $A$ when presented with a choice
-    between $A$ and $B$, but prefer $B$ when presented with $A$, $B$ and $C$ \myalert{(for
-      animals cite from Fawcett page 3)} \myalert{(add
-      citation for human performance)}
-  \item We need to be careful here: we do not want to stress that this approach here (the
-    particular implemenation of a regret-based choice mechanism) explains these empirical
-    findings (better than any other line of explanation). Our point is more general and
-    methodological. Evolution of preferences is something that the literature on evolution of
-    choice mechanisms should care about. We also presented a method that can be useful and an
-    example of that method that should (succinctly) demonstrate our aforementioned conceptual
-    point that evolution of preferences is conceptually important and can give non-trivial,
-    unexpected and philosophically useful results.
-  \end{itemize}
-\item contributes to: (i) methodological reflection on evolutionary game theory, (ii) ecological
-  rationality of choice behavior, (iii) evolution of preferences literature
-\end{itemize}
-
-\bigskip
-
-\begin{itemize}
-\item The meta-game perspective that we introduce in this paper can shed more light on the duality of descriptivism and normativism, and opens
-some space in between the two extrema. 
-By keeping the evolutionary approach we want to retain a
-normative perspective on rationality, but our results show that (under certain conditions)
-evolution does not necessarily lead to identifying rationality with maximization of objective
-utility, contrary to the intuition of Alchian [cite] and Friedman [cite].
-
-In the following we mainly deal with two types of agents: players whose subjective utility is defined
-in terms of regret (as in DEFINITION), and players whose utility
-function coincides with the objective utility $\pi_i$.
-
-The justification for this choice is both historical and behavioral. Among
-the possible competitors of utility maximization, regret has always been in a prominent
-position, both from a descriptive and normative viewpoint. Indeed, Bell82 writes:
-\begin{quote}
-  By explicitly incorporating regret, expected utility theory not only becomes a better
-  descriptive predictor but also may become a more convincing guide for prescribing behavior to
-  decision makers.
-\end{quote}
-In the same year, Graham Loomes and Robert Sugden \citet{loosug82} show that a regret-based theory of choice can match
-and explain all the main experimental results of prospect theory, and claim that
-\begin{quote} [...] we shall challenge the idea that the conventional axioms [of decision
-  theory] constitute the only acceptable basis for rational choice under uncertainty. We shall
-  argue that it is no less rational to act in accordance with regret theory, and that
-  conventional expected utility theory therefore represents an unnecessarily restrictive notion
-  of rationality. \hfill \citep{loosug82}
-\end{quote}
-\end{itemize}
-
-\newpage
-
-\textbf{Proof of Proposition 2.} First we prove that regret type is evolutionarily stable against altruistic type and that altruistic type is not evolutionarily stable against regret type, and second we show that regret type is evolutionarily stable against competitive type and that competitive type is not evolutionarily stable against regret type.
-We make use of the same partition of $\mathcal{G}$ introduced in the proof of Proposition 1.
-Again, to ease notation let us write ALT and COM in the place of $(\tau^{alt}, \Delta)$ and $(\tau^{com}, \Delta)$, respectively.
-
-\begin{lemma}
-In $\mathcal{G}^I$, RM and ALT perform equally well.
-\end{lemma}
-
-\begin{proof}
-Trivial.
-\end{proof}
-
-\begin{lemma}
-In $\mathcal{G}^S$, RM is evolutionarily stable against ALT, and ALT is not evolutionarily stable against RM. 
-\end{lemma}
-
-\begin{proof}
-Let us assume, without loss of generality, that $a>c$ and $b>d$.
-We already know that RM always plays the dominant action $I$, then a population of RM players always coordinates on $I$ with a payoff of $a$.
-It is possible instead that an ALT player plays the dominated action $II$, for instance when $2d > 2a$ and $2a < b+c$.
-Then, the payoff of an ALT invader against a population of RMs is $c$.
-Since $a>c$ by assumption, we get that a RM population cannot be invaded by ALT players in this case.
-When $b+c < 2a$ and $b+c < 2d$, ALT will play $(\frac{1}{2}I;\frac{1}{2}II)$ for an expected payoff of $\frac{1}{2} a + \frac{1}{2} c$.
-Since $a > \frac{1}{2} a + \frac{1}{2} c$, a population of RMs is evolutionarily stable against ALT.
-\\
-When $2d > 2a$ and $2a < b+c$, an ALT population plays action $II$ for a payoff of $d$, whereas a RM invader plays action $I$ for a payoff of $b$.
-By assumption $b>d$, hence a population of ALTs would not be evolutionarily stable in this case.
-When $b+c < 2a$ and $b+c < 2d$, the expected payoff of a population of ALTs is $\frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d$, while the expected payoff of a RM invader is $\frac{1}{2}a+\frac{1}{2}b$.
-Since $\frac{1}{2}a+\frac{1}{2}b > \frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d$, we have that an ALT population is not evolutionarily stable against RM.
-\end{proof}
-
-\begin{lemma}
-In $\mathcal{G}^W$, RM is evolutionarily stable against ALT, and ALT is not evolutionarily stable against RM. 
-\end{lemma}
-
-\begin{proof}
-Let us assume, WLOG, that $b=d$ and $a>c$.
-We know that RM always plays the (weakly) dominant action $I$.
-Again, a RM population always coordinates on $I$ for a payoff of $a$, whereas when $2d > 2a$ and $2a < b+c$ an ALT invader plays $II$.
-Then, the payoff of an ALT invader against a population of RMs is $c$.
-Since $a>c$ by assumption, we get that a RM population cannot be invaded by ALT players in this case.
-When $b+c < 2a$ and $b+c < 2d$, ALT plays $(\frac{1}{2}I;\frac{1}{2}II)$ for an expected payoff of $\frac{1}{2} a + \frac{1}{2} c$.
-Since $a > \frac{1}{2} a + \frac{1}{2} c$, a population of RMs is evolutionarily stable against ALT.
-\\
-When $2d > 2a$ and $2a < b+c$, an ALT population plays action $II$ for a payoff of $d$, whereas a RM invader plays action $I$ for a payoff of $b$.
-Since $b=d$, we have to check the second condition for ESS: an ALT against RM gets $c$, and RM against RM gets $a$.
-By assumption $a>c$, hence an ALT population would be invaded by RM players in this case.
-When $b+c < 2a$ and $b+c < 2d$, the expected payoff of a population of ALTs is $\frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d$, while the expected payoff of a RM invader is $\frac{1}{2}a+\frac{1}{2}b$.
-Since $\frac{1}{2}a+\frac{1}{2}b > \frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d$, we again have that an ALT population is not evolutionarily stable against RM.
-\end{proof}
-
-\begin{lemma}
-In $\mathcal{G}^C$, RM is evolutionarily stable against ALT, and ALT is not evolutionarily stable against RM. 
-\end{lemma}
-
-\begin{proof}
-Let's assume, WLOG, that $a>d$.
-We know that RM plays $I$ if $ a-c > d-b $ and $II$ if $ a-c < d-b $, whereas  ALT plays $I$ if $2d<b+c$, otherwise ALT plays $(\frac{1}{2}I;\frac{1}{2}II)$.
-If $2d<b+c$, then $d-b<c-d$, hence $c>d$.
-Consequently, when $2d<b+c$ the expected payoff of an ALT population is $a$
-\end{proof}
-
-\fi
-
 \end{document}

### 2015-12-18 code/RMD_component_wise_mutation.r

@@ -1,9 +1,15 @@
 require('gtools') # for dirichlet distribution
+require('ggplot2')
 
 # get utilities
-# load(file = 'buffered_meta_game_2x2.RDATA')
-load(file = 'buffered_meta_game_10x10.RDATA')
-U = means_total
+load(file = 'buffered_meta_game_2x2.RDATA')
+# load(file = 'buffered_meta_game_10x10.RDATA')
+
+# which strategies:
+strats = c(1,2,5,6)
+
+# U = means_total
+U = means_total[strats, strats]
 
 # parameters
 e = 0.001 # epsilon mutation probability
@@ -17,14 +23,15 @@ getMutationMatrix = function(e){
               e, e^2, e^2, e^2, x, e, e, e,
               e^2, e, e^2, e^2, e, x, e, e,
               e^2, e^2, e, e^2, e, e, x, e,
-              e^2, e^2, e^2, e, e, e, e, x), nrow=8, byrow = T)
+              e^2, e^2, e^2, e, e, e, e, x), nrow=8, byrow = T)[strats, strats]
   colnames(m) = colnames(U)
   rownames(m) = rownames(U)
   return(m)
 }
 
 # initial population
-p = rdirichlet(1, rep(1,8))[1,]
+p = rdirichlet(1, rep(1,length(strats)))[1,]
+
 show(p)
 
 

### 2015-12-19 paper/paper.tex
paper almost there

@@
 \title{Smart Representations: {R}ationality and Evolution in a Richer  Environment}
-\author{Paolo Galeazzi \& Michael Franke} \date{current version: November 5, 2015}
+\author{Paolo Galeazzi \& Michael Franke} \date{current version: December 19, 2015}
 
@@
 
-% \textbf{some general notes and remarks and todo's}
-
-% \begin{itemize}
-% \item micha: let's have a term for pairs (regret type, epistemic type); I'm inclined to use ``player
-%   type'', but that's what you reserved for regret type; maybe use \myalert{meta-type}?
-% \item can we reformulate the main result (proposition 1) in terms of ``strict dominance''
-%   and/or strict Nash equilibrium? sometimes the proof is not ideally precise because it
-%   actually shows something stronger, namely strict dominance, but everything is formulated in
-%   terms of stability; using dominance is also better for arguments about evolutionary dynamics:
-%   dynamics can be attracted by states that are not evolutionarily stable (even if there is an
-%   ESS), but dominated strategies will die out in any case;
-% \item should we give definitions for ESS and NSS in the main text?
-% \item should we include definitions of the replicator dynamic and/or the replicator mutator
-%   dynamic?
-% \item the most important issue with this text is still that we need to motivate why we care
-%   about non-probabilistic beliefs and/or security strategies; everything else will fall into
-%   place when that is done
-% \item an important ingredient in our argument pro regret is that radical uncertainty could be
-%   exogenously given; as it stands this occurs rather ``suddenly'' in the paper and should
-%   ideally be prepared and motivated earlier (e.g., in Sections 2 and 3)
-% \item a major contribution of our paper is the ``meta-game'' approach, but in the current
-%   version I feel that this is not stressed sufficiently; the introduction and the beginning of
-%   section 3 could do a bit more to carve out this idea as something generally cool; especially
-%   the formula from 3.4 could occur earlier (albeit in more general notation);
-% \end{itemize}
-
-% \newpage
-
 \maketitle
+
+\begin{abstract}
+  Standard applications of evolutionary game theory look at a single, fixed game and focus on
+  the evolution of behavior for that game alone. Instead, this paper uses tools from
+  evolutionary game theory to study the evolutionary competition between \emph{choice
+    mechanisms} in a rich and variable environment. A choice mechanism is a way of representing
+  a decision situation, paired with a method for choosing an act based on this (possibly false)
+  subjective representation. We demonstrate the usefulness of this approach by a case study
+  that compares a number of classic proposals of what it means to make a rational choice. Our
+  main result is that regret-based preference representations can be evolutionarily selected
+  for, despite being non-veridical.
+\end{abstract}
 
@@
 % specifically the competition of subjective representations of choice situations, in a
-% variable environment. Concretely, we look at evolutionary ``meta-games'' whose ``acts'' are
+% variable environment. Concretely, we look at evolutionary ``meta games'' whose ``acts'' are
 % choice mechanisms and whose ``payoffs'' represent the average expected fitness that different
 % choice mechanisms would accrue when playing arbitrary games (from a given class, with a given
-% occurrence probability). In this sense, a meta-game captures (the modeller's) assumptions
+% occurrence probability). In this sense, a meta game captures (the modeller's) assumptions
 % about the relevant statistics of the environment in which evolutionary forces operate, while
@@
 
-\section{Choice mechanisms: preferences, beliefs and action choice}
+\section{Classic choice rules and choice mechanisms}
 \label{sec:basic-notions}
@@
 $\gamma_i(G) = (\theta, e_i)$ where
-$\theta \mycolon \bigtimes_{i \in N} A_i \rightarrow \mathbb{R}$ is payoff function suitable
+$\theta \mycolon \bigtimes_{j \in N} A_j \rightarrow \mathbb{R}$ is a payoff function suitable
 for $G$, and $e_i$ is some representation of $i$'s uncertainty about the co-player's
 behavior. We consider two \emph{preference types}: the \emph{objective type} maps each game
-onto its own, true payoff function; The \emph{regret type} maps each game onto its regret
+onto its own, true payoff function; the \emph{regret type} maps each game onto its regret
 transformation, as introduced above. We also consider two \emph{belief types}: the
 \emph{precise type} represents uncertainty in a single probability distribution
-$\mu_i \in \Delta(\Acts_{-i})$ about the co-players' behavior; the \emph{imprecise type}
+$\mu \in \Delta(\Acts_{-i})$ about the co-players' behavior; the \emph{imprecise type}
 represents uncertainty as a set of probability distributions $X \subseteq \Delta(\Acts_{-i})$.
 It is convenient to conceptualize precise beliefs as a special case of imprecise beliefs by
-looking at $\mu_i$ as a stand-in for the singleton set $\set{\mu_i}$. More details about
-imprecise probabilities and our initial assumption of ignorance are given in
-Section~\ref{sec:impr-prob-beli} below.
-
-The only action choice function $\kappa$ that we consider here is \emph{maximinimization of
-  expected (subjective) utilities} (see Section~\ref{sec:impr-prob-beli} for
-motivation).
+looking at $\mu$ as a stand-in for the singleton set $\set{\mu}$. Background on imprecise
+probabilities is provided in Appendix~\ref{sec:impr-prob-beli}.
+
+The action choice function $\kappa$ that we consider here is \emph{maximinimization of expected
+  (subjective) utilities} (see Section~\ref{sec:impr-prob-beli} for motivation).
 
@@
   $G$ and $e_i$ is a (possibly singleton) set of probability distributions in
-  $\Delta(\Acts_{-i})$. Agent $i$'s expected (subjetive) utility for act $\myact{i}$ and
+  $\Delta(\Acts_{-i})$. Agent $i$'s expected (subjetive) utility for act $\myact{i}$ and belief
   $\mu \in e$ is
@@
   \myact{-i})$.
-  Act $\myact{i}^*$ is selected by maximinimization of expected (subjective) utility iff:
+  Act $\myact{i}^*$ is selected by maximinimization of expected (subjective) utility iff
   $\myact{i}^* \in \arg \max_{\myact{i} \in \Acts_{i}} \min_{\mu \in e} \EU(\myact{i}, \mu)$.
@@
 objective types, as long as both hold precise beliefs. This will be central in understanding
-later results: under precise beliefs evolution will not favor either preference type over the
+later results: under precise beliefs, evolution will not favor either preference type over the
 other. On the other hand, if paired with imprecise beliefs, different behavioral predictions
@@
 (singleton set containing a) flat probability distribution
-$\overline{\mu}_i \in \Delta(\Acts_{-i})$ and imprecise types consider all probabilistic
-beliefs about the co-players' behavior $\overline{X} = \Delta(\Acts_{-i})$. In that case, the
+$\overline{\mu} \in \Delta(\Acts_{-i})$ and imprecise types consider all probabilistic beliefs
+about the co-players' behavior $\overline{X} = \Delta(\Acts_{-i})$. In that case, the
 considered choice mechanisms are behaviorally equivalent to classic choice rules, as summarized
@@
 
-Maximal uncertainty also means that, given Fact~\ref{fact:equivalence2x2}, all choice
-mechanisms are behaviorally equivalent on $2 \times 2$ symmetric games, except for objective
-preference types with imprecise beliefs.
+Under maximal uncertainty, all four choice mechanisms considered here are behaviorally
+equivalent on $2 \times 2$ symmetric games, except for objective preference types with
+imprecise beliefs:
 
@@
 
-To demonstrate the usefulness of a meta-game approach, let us concentrate first on a basic
-model that contains the four choice mechanisms obtained from crossing the preference and belief
-types introduced in Section~\ref{sec:basic-notions}. From now on we speak of types when we mean
-pairs like $(\text{reg}, \text{imp})$, a choice mechanism with regret-based preferences and
-imprecise beliefs, or $(\text{obj}, \text{prc})$, one with objective preferences and precise
-beliefs.
-
-Meta games factor in statistical properties of the environment. For a particular empirical
-purposes, one would consult a specific class of games $\mathcal{G}$ with appropriate, possibly
+To demonstrate the usefulness of a meta game approach, let us concentrate first on a basic
+model that contains the four choice mechanisms from Table~\ref{tab:CMs}. From now on we speak
+of types when we mean pairs like $(\text{reg}, \text{imp})$, a choice mechanism with
+regret-based preferences and imprecise beliefs, or $(\text{obj}, \text{prc})$, one with
+objective preferences and precise beliefs.
+
+Meta games factor in statistical properties of the environment. For particular empirical
+purposes, one would consult a specific class of games $\mathcal{G}$ with appropriate,
 empirically informed probabilities $P(G)$ in order to match the natural environment of a given
@@
 $(\text{obj}, \text{prc})$ are substituted for one another yield identical results. More
-interestingly, Table~\ref{tab:ExpectedFitness_4Types} shows that the maxmin strategy
-$(\text{obj}, \text{imp})$ is strictly dominated by the three other strategies: in each column
-(i.e., for each kind of opponent), the maxmin strategy is strictly worse than any of the other
-three competitors. This has a number of interesting consequences.
+interestingly, Table~\ref{tab:ExpectedFitness_4Types} shows that $(\text{obj}, \text{imp})$,
+the maxmin strategy, is strictly dominated by the three other strategies: in each column (i.e.,
+for each kind of opponent), the maxmin strategy is strictly worse than any of the other three
+competitors. This has a number of interesting consequences.
 
@@
 completely different player with altogether different preference type and belief type would
-then be $\epsilon^2$. With these assumptions about ``component-wise mutations'', numerical
+then be $\epsilon^2$. With these assumptions about ``component-wise mutations,'' numerical
 simulations of the (discrete time) \emph{replicator mutator dynamics}
@@
 regret types. For instance, with $\epsilon = 0.001$, almost all initial populations are
-attracted to a final distribution with proportions:\todo{recalculate these numbers for the
-  actual 4x4 game!}
+attracted to a final distribution with proportions:
 
@@
 
-Results based on the single meta-game in Table~\ref{tab:ExpectedFitness_4Types}, which was
+Results based on the single meta game in Table~\ref{tab:ExpectedFitness_4Types}, which was
 obtained by Monte Carlo simulation, are not fully general and possibly spoiled by random
@@
   $(\text{reg}, \text{imp})$ strictly dominates $(\text{reg}, \text{prc})$ in the resulting
-  meta-game.
+  meta game.
 \end{proposition}
@@
 models? Section~\ref{sec:more-types} first introduces further conceptually interesting
-preference types that have been considered in evolutionary game theory. Section~\ref{sec:n-times-n}
-then addresses the case of $n \times n$ games for $n \ge 2$. Finally, to put our results into
-a broader perspective, Section~\ref{sec:solitary-decisions} ends with a brief comparison of
-game situations with cases of solitary decision making.
+preference types that have been considered in the recent
+literature. Section~\ref{sec:n-times-n} then addresses the case of $n \times n$ games for
+$n \ge 2$. Finally, to put our results into a broader perspective,
+Section~\ref{sec:solitary-decisions} ends with a brief comparison of game situations with cases
+of solitary decision making.
 
@@
 
-In evolutionary game theory other types of player have been investigated.
-A famous example is the \textit{altruistic type} [REF], introduced in the literature in order to explain the possible survival of altruistic behavior.
-In our framework, we can represent the altruistic type as follows.
-
-\iffalse
-
-\begin{definition}[Altruistic preference] \label{defn:altpref}
-
-For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the altruistic preference $ \theta^{alt}: A \rightarrow \mathbb{R} $ such that $ \theta^{alt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \sum_{j \neq i} \pi(a_{j},a_{-j})$.\footnote{A more general formulation [see: REFERENCES] would be to define an $ \alpha$-altruistic type, for $\alpha \in [0,1]$, with subjective utility $ \theta^{\alpha lt}(a_i,a_{-i})=\pi(a_i,a_{-i}) + \alpha \sum_{j \neq i} \pi(a_{j},a_{-j})$.
-Since we are not interested in the evolution of degrees of altruism here, we simply fix $ \alpha = 1 $.}
+Beyond objective and regret-based preferences, other preference types have been investigated. A
+famous example is the \textit{altruistic type} \textcolor{red}{[INSERT REFERENCE]}, summoned to
+explain the possibility of altruistic behavior. At the other end of the spectrum, the \emph{competitive
+type} is located.
+
+\begin{definition}[Altruistic and competitive types] \label{defn:alttype}
+
+  Fix a two player game $G$ with actual payoff function $\pi$. The \textit{altruistic type}
+  represents $G$'s payoffs as $\theta(a_i, a_j):=\pi_i(a_i,a_j) + \pi_j(a_i,a_j)$.\footnote{A
+    more general formulation would be to define an $ \alpha$-altruistic type, for
+    $\alpha \in [0,1]$, with subjective utility
+    $ \theta_\alpha(a_i, a_j):=\pi_i(a_i,a_j) + \alpha \pi_j(a_i,a_j)$. Since we are not
+    interested in the evolution of degrees of altruism, here we simply fix $ \alpha = 1 $.} The
+  \emph{competitive type} represents $G$'s payoffs as
+  $\theta(a_i, a_j):=\pi_i(a_i,a_j) - \pi_j(a_i,a_j)$.
 
 \end{definition}
-
-\fi
-
-\begin{definition}[Altruistic type] \label{defn:alttype}
-
-Given a two player game  $ G $, the \textit{altruistic type} $\tau^{alt}$ is characterized by the subjective utility function $\tau^{alt}(G)(a_i, a_j):=\pi_i(a_i,a_j) + \pi_j(a_i,a_j)$.\footnote{A more general formulation would be to define an $ \alpha$-altruistic type, for $\alpha \in [0,1]$, with subjective utility $ \tau^{\alpha lt}(G)(a_i, a_j):=\pi_i(a_i,a_j) + \alpha \pi_j(a_i,a_j)$.
-Since we are not interested in the evolution of degrees of altruism, here we simply fix $ \alpha = 1 $.}
-
-\end{definition}
-
-\noindent As opposite to the altruistic type, it is possible to define a \textit{competitive type}.
-
-\iffalse
-
-\begin{definition}[Competitive preference] \label{defn:compref}
-
-For a game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, we define the competitive preference $ \theta^{com}: A \rightarrow \mathbb{R} $ such that $ \theta^{com}(a_i,a_{-i})=\pi(a_i,a_{-i}) - \sum_{j \neq i} \pi(a_{j},a_{-j})$.
-
-\end{definition}
-
-\fi
-
-\begin{definition}[Competitive type] \label{defn:comtype}
-
-Given a two player game  $ G $, the \textit{competitive type} $\tau^{com}$ is characterized by the subjective utility function $\tau^{com}(G)(a_i, a_j):=\pi_i(a_i,a_j) - \pi_j(a_i,a_j)$.
-
-\end{definition}
-
-Similarly to the evolutionary competition that we simulated before, we can study the
-evolutionary fitness of this extended set of players when they are all represented in the
-population. Table~\ref{tab:ExpectedFitness_2x2_Full} shows simulation results that approximate the
-expected fitness in the relevant meta-game.
 
@@
  & $(\text{obj}, \text{imp})$ 
- & $(\tau^{com}, \text{imp})$
- & $(\tau^{alt}, \text{imp})$
+ & $(\text{com}, \text{imp})$
+ & $(\text{alt}, \text{imp})$
  & $(\text{reg}, \text{prc})$ 
  & $(\text{obj}, \text{prc})$ 
- & $(\tau^{com}, \text{prc})$
- & $(\tau^{alt}, \text{prc})$ \\ 
+ & $(\text{com}, \text{prc})$
+ & $(\text{alt}, \text{prc})$ \\ 
   \hline
@@
   $(\text{obj}, \text{imp})$ & 6.486 & 6.484 & 6.088 & 6.703 & 6.486 & 6.486 & 6.088 & 6.875 \\
-  $(\tau^{com}, \text{imp})$ & 6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\
-  $(\tau^{alt}, \text{imp})$ & 5.949 & 5.722 & 5.326 & 6.396 & 5.949 & 5.949 & 5.326 & 6.568 \\
+  $(\text{com}, \text{imp})$ & 6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\
+  $(\text{alt}, \text{imp})$ & 5.949 & 5.722 & 5.326 & 6.396 & 5.949 & 5.949 & 5.326 & 6.568 \\
   $(\text{reg}, \text{prc})$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
   $(\text{obj}, \text{prc})$ & 6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\
-  $(\tau^{com}, \text{prc})$ & 6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\
-  $(\tau^{alt}, \text{prc})$ & 6.331 & 5.893 & 5.497 & 6.566 & 6.331 & 6.331 & 5.497 & 7.152 \\
+  $(\text{com}, \text{prc})$ & 6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\
+  $(\text{alt}, \text{prc})$ & 6.331 & 5.893 & 5.497 & 6.566 & 6.331 & 6.331 & 5.497 & 7.152 \\
    \hline                          
 \end{tabular}                      
-\caption{Average payoff in simulations of 100,000
-  randomly generated $2 \times 2$ symmetric games}
+\caption{Average evolutionary fitness from Monte Carlo simulations of 100,000 symmetric $2 \times 2$ games}
 \label{tab:ExpectedFitness_2x2_Full}        
@@
 
-\todo[inline]{is it true that competitive preferences types are behaviorally equivalent under
-  either epistemic type? can we show that?}
-
-The approximations in Table~\ref{tab:ExpectedFitness_2x2_Full} confirm basic intuitions about
-altruistic and competitive types: averaging over randomly sampled games, everybody would like
-to have an altruistic opponent and nobody would like to play against a competitive
-opponent. Perhaps more surprisingly, altruistic types come up strictly dominated by competitive
-types, but competitive types themselves are worse off against all opponent types except against
-maxmin players $(\text{obj}, \text{imp})$ than any of the behaviorally equivalent types
-$(\text{reg}, \text{imp})$, $(\text{obj}, \text{prc})$, and
-$(\text{reg}, \text{prc})$. 
-\iffalse
-This is a noteworthy results in the light of the fact that
-evolving altruistic preferences have been shown to support cooperative behavior in a single
-stage game \myalert{[CITE]}. In contrast,
-averaging over payoffs in multiple stage games, like we do here, makes altruistic preferences
-prime victims of evolutionary eradication.
-\fi
-It is easy to see then that the previous result still obtains for the larger meta-game in
+Table~\ref{tab:ExpectedFitness_2x2_Full} shows results of further Monte Carlo simulations that
+approximate the expected fitness in the relevant meta game with all types considered so
+far. These results confirm basic intuitions about altruistic and competitive types: averaging
+over randomly sampled games, everybody would like to have an altruistic opponent and nobody
+would like to play against a competitive opponent. Perhaps more surprisingly, altruistic types
+come up strictly dominated by competitive types, but competitive types themselves are worse off
+against all opponent types except against maxmin players $(\text{obj}, \text{imp})$ than any of
+the behaviorally equivalent types $(\text{reg}, \text{imp})$, $(\text{obj}, \text{prc})$, and
+$(\text{reg}, \text{prc})$.  \iffalse This is a noteworthy results in the light of the fact
+that evolving altruistic preferences have been shown to support cooperative behavior in a
+single stage game \myalert{[CITE]}. In contrast, averaging over payoffs in multiple stage
+games, like we do here, makes altruistic preferences prime victims of evolutionary eradication.
+\fi It is easy to see then that the previous result still obtains for the larger meta game in
 Table~\ref{tab:ExpectedFitness_2x2_Full}: $(\text{reg}, \text{imp})$,
 $(\text{obj}, \text{prc})$, and $(\text{reg}, \text{prc})$ are still neutrally stable;
-all simulations of the (discrete-time) replicator dynamic on the $8 \times 8$ meta-game from
-Table~\ref{tab:ExpectedFitness_2x2_Full} end up in populations consisting of only these players
-in arbitrary proportion.
-
-\iffalse
-
-The following proposition (partially) confirms this result.\todo{rephrase to acknowledge all
-  epistemic types?}
-
-\begin{proposition} \label{proposition2}
-
-Fix $\Lambda = \lbrace (\text{obj}, \text{imp}), (\text{reg}, \text{imp}), (\tau^{alt}, \text{imp}), (\tau^{com}, \text{imp}) \rbrace$ and $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex, set of i.i.d.
-values.
-Then, $(\text{reg}, \text{imp})$ is the only evolutionarily stable player in the population.
-
-\end{proposition}
-
-\begin{proof}
-See Appendix.\todo{is this there already?}
-\end{proof}
-
-\fi
+simulation runs of the (discrete-time) replicator dynamic on the $8 \times 8$ meta game from
+Table~\ref{tab:ExpectedFitness_2x2_Full} all ended up in populations consisting of only these
+players in arbitrary proportion.
 
 In sum, the presence of other plausible preference types, such as competitive and altruistic
-types does not undermine the previous results about the evolutionary drive towards regret-based
-subjective preferences.
+types does not undermine, but rather strengthens the previous results about the evolutionary
+drive towards regret-based subjective preferences.
 
@@
 
-Results from Section~\ref{sec:results:-basic-model} relied heavily on
-Fact~\ref{fact:equivalence2x2} that, for the special case of $2 \times 2$ symmetric games,
-regret minimization $(\text{reg}, \text{imp})$ is behaviorally equivalent with expected
-regret minimization $(\text{reg}, \text{prc})$ and expected utility maximization
-$(\text{obj}, \text{prc})$. This is no longer true when we look at arbitrary $n \times n$
-games with $n \ge 2$. We should therefore see what happens in a broader class of games.
-
-Table~\ref{tab:ExpectedFitness_10x10} gives approximations for expected fitness in a
-meta-game over a class of $n \times n$ symmetric games where $n$ is randomly drawn from
-$\set{2, \dots, 10}$. Concretely, the numbers in Table~\ref{tab:ExpectedFitness_10x10} are
-averages of payoffs obtained in 100,000 randomly sampled games, where each game was sampled by
-first picking a number of acts $n \in \set{2, \dots, 10}$ uniformly at random, and then filling
-the resulting $n \times n$ payoff matrix of the stage game with i.i.d.~sampled payoffs as
-before.
+Results from Section~\ref{sec:basic-model-1} relied heavily on Fact~\ref{fact:equivalence2x2}
+that, for the special case of $2 \times 2$ symmetric games, regret minimization
+$(\text{reg}, \text{imp})$ is behaviorally equivalent with expected regret minimization
+$(\text{reg}, \text{prc})$ and expected utility maximization $(\text{obj}, \text{prc})$. This
+is no longer true when we look at arbitrary $n \times n$ games with $n \ge 2$. Let us see what
+happens in a broader class of games.
+
+Table~\ref{tab:ExpectedFitness_10x10} gives approximations of expected fitness in a class of
+$n \times n$ symmetric games where $n$ is randomly drawn from $\set{2, \dots, 10}$. Concretely,
+the numbers in Table~\ref{tab:ExpectedFitness_10x10} are averages of payoffs obtained in
+100,000 randomly sampled games, where each game was sampled by first picking a number of acts
+$n \in \set{2, \dots, 10}$ uniformly at random, and then filling the necessary $n \times n$
+payoff matrix with i.i.d.~sampled numbers, as before.
 
@@
  & $(\text{obj}, \text{imp})$ 
- & $(\tau^{com}, \text{imp})$
- & $(\tau^{alt}, \text{imp})$
+ & $(\text{com}, \text{imp})$
+ & $(\text{alt}, \text{imp})$
  & $(\text{reg}, \text{prc})$ 
  & $(\text{obj}, \text{prc})$ 
- & $(\tau^{com}, \text{prc})$
- & $(\tau^{alt}, \text{prc})$ \\ 
+ & $(\text{com}, \text{prc})$
+ & $(\text{alt}, \text{prc})$ \\ 
   \midrule
@@
   $(\text{obj}, \text{imp})$ & 6.476 & 6.483 & 5.896 & 6.818 & 6.484 & 6.484 & 5.850 & 7.124 \\
-  $(\tau^{com}, \text{imp})$ & 6.468 & 6.647 & 5.512 & 7.169 & 6.578 & 6.578 & 5.577 & 7.354 \\
-  $(\tau^{alt}, \text{imp})$ & 5.968 & 5.923 & 5.363 & 6.685 & 5.975 & 5.975 & 5.086 & 6.973 \\
+  $(\text{com}, \text{imp})$ & 6.468 & 6.647 & 5.512 & 7.169 & 6.578 & 6.578 & 5.577 & 7.354 \\
+  $(\text{alt}, \text{imp})$ & 5.968 & 5.923 & 5.363 & 6.685 & 5.975 & 5.975 & 5.086 & 6.973 \\
   $(\text{reg}, \text{prc})$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
   $(\text{obj}, \text{prc})$ & 6.908 & 6.918 & 5.988 & 7.456 & 6.929 & 6.929 & 5.934 & 7.783 \\
-  $(\tau^{com}, \text{prc})$ & 6.529 & 6.680 & 5.445 & 7.276 & 6.542 & 6.542 & 5.521 & 7.440 \\
-  $(\tau^{alt}, \text{prc})$ & 6.450 & 6.337 & 5.772 & 6.978 & 6.457 & 6.457 & 5.479 & 7.500 \\
+  $(\text{com}, \text{prc})$ & 6.529 & 6.680 & 5.445 & 7.276 & 6.542 & 6.542 & 5.521 & 7.440 \\
+  $(\text{alt}, \text{prc})$ & 6.450 & 6.337 & 5.772 & 6.978 & 6.457 & 6.457 & 5.479 & 7.500 \\
    \bottomrule                         
 \end{tabular}                      
-\caption{Average payoff in simulations of 100,000
-  randomly generated $n \times n$ symmetric games with $n$ randomly drawn from $\set{2, \dots, 10}$.}
+\caption{Average evolutionary fitness for 100,000 randomly generated $n \times n$ symmetric games with $n$ randomly drawn from $\set{2, \dots, 10}$.}
 \label{tab:ExpectedFitness_10x10}        
@@
 
-As is to be expected, average payoffs obtained in games with more than 2 acts are higher, as
-can be seen by comparing Table~\ref{tab:ExpectedFitness_10x10} with
-Table~\ref{tab:ExpectedFitness_2x2_Full}. But increases in approximate expected fitness are not
-uniform. Most importantly, the regret minimizing type $(\text{reg}, \text{imp})$ is
-strictly dominated by $(\text{reg}, \text{prc})$ and by $(\text{obj}, \text{prc})$ in
-the meta-game from Table~\ref{tab:ExpectedFitness_10x10}. This means that while regret
-minimization \emph{can} thrive in some evolutionary contexts, there are also contexts where it
-is demonstrably worse off.
-
-Still, although this may be bad news for regret minimizing types
-$(\text{reg}, \text{imp})$, it is not the case that regret types \emph{as such} are weeded
-out by selection. Since, by Fact~\ref{fact:maxEU-minReg}, $(\text{reg}, \text{prc})$ and
-$(\text{obj}, \text{prc})$ are generally behaviorally equivalent, it remains that
-selection based on meta-games constructed from $n \times n$ games will still not eradicate all
-regret types. So, although regret types may not be selected for in this case, they are also not
+The most important result is that the regret minimizing type $(\text{reg}, \text{imp})$ is
+strictly dominated by $(\text{reg}, \text{prc})$ and by $(\text{obj}, \text{prc})$ in the
+meta game from Table~\ref{tab:ExpectedFitness_10x10}. This means that while regret minimization
+\emph{can} thrive in some evolutionary contexts, there are also contexts where it is
+demonstrably worse off. While this may be bad news for regret minimizing types
+$(\text{reg}, \text{imp})$, it is not the case that regret types \emph{as such} are weeded out
+by selection. Since, by Fact~\ref{fact:maxEU-minReg}, $(\text{reg}, \text{prc})$ and
+$(\text{obj}, \text{prc})$ are generally behaviorally equivalent, it remains that selection
+based on meta games constructed from $n \times n$ games will still not eradicate all regret
+types. So, although regret types may not be selected for in this case, they are also not
 selected against.
@@
 Proposition~\ref{proposition1} that regret-based preferences can be strictly better than
-veridical objective preferences in case of radical uncertainty could make for situations in
-which evolution would select for regret types exclusively, even in $n \times n$ games. If, for
+veridical objective preferences in case of imprecise beliefs could make for situations in which
+evolution would select for regret types exclusively, even in $n \times n$ games. If, for
 example, epistemic types of players are not what biological evolution selects, but rather
@@
 preference \emph{can} again drive out veridical preferences altogether. For concreteness,
-suppose that only preference types compete and that agents' belief types are exogenously
-given, in such a way that agents hold flat probabilistic beliefs $\text{prc}$ with probability
-$1-p$ and are of type $\text{imp}$ with probability $p$. This transforms the meta-game from
-Table~\ref{tab:ExpectedFitness_10x10} into the simpler $4 \times 4$ game in which the payoff
-obtained for a preference type is the weighted average over the payoffs of that preference
-types in Table~\ref{tab:ExpectedFitness_10x10}. Setting $p = 0.02$ for illustration, we get the
-meta-game in Table~\ref{tab:ExogeneousEpistemics}.
+suppose that only preference types compete and that agents' belief types are exogenously given,
+in such a way that agents hold precise beliefs with probability $p$ and otherwise imprecise
+beliefs. This transforms the meta game from Table~\ref{tab:ExpectedFitness_10x10} into the
+simpler $4 \times 4$ game in which the payoff obtained for a preference type is the weighted
+average over the payoffs of the choice mechanisms including that preference type in
+Table~\ref{tab:ExpectedFitness_10x10}. Setting $p = 0.98$ for illustration, we get the meta
+game in Table~\ref{tab:ExogeneousEpistemics}.
 
@@
   & $\text{obj}$ 
-  & $\tau^{com}$
-  & $\tau^{alt}$ \\ 
+  & $\text{com}$
+  & $\text{alt}$ \\ 
   \midrule
@@
   $\tau^{com }$ & 6.566 & 6.570 & 5.481 & 7.434 \\ 
-  $\tau^{alt} $ & 6.463 & 6.461 & 5.478 & 7.469 \\ 
+  $\text{alt} $ & 6.463 & 6.461 & 5.478 & 7.469 \\ 
    \bottomrule
 \end{tabular}
-\caption{Meta-game for the evolutionary competition between preference types when epistemic types are exogenously
-  given}
+\caption{Meta game for the evolutionary competition between preference types when epistemic types are exogenously
+  given (see main text)}
 \label{tab:ExogeneousEpistemics}
@@
 
-The only evolutionarily stable state of this meta-game is the regret type. Accordingly, all of
+The only evolutionarily stable state of this meta game is the regret type. Accordingly, all of
 our simulation runs of the (discrete-time) replicator dynamic converged to monomorphic
 regret-type populations. The reason why regret types prosper is because they have a substantial
-payoff advantage if paired with radical uncertainty. If radical uncertainty is exogenously
-given as something unavoidable that happens to agents (e.g., in situation where they really have no
-way of narrowing down the probability set), and even if that happens only very
-infrequently (i.e., for rather low $p$), regret types \emph{will} outperform veridical
-preference types, as well as competitive and altruistic types.
+payoff advantage if paired with imprecise beliefs. If radical uncertainty is exogenously given
+as something unavoidable that happens to agents (e.g., in situation where they really have no
+way of narrowing down the probability set), and even if that happens only very infrequently
+(i.e., for rather low $p$), regret types \emph{will} outperform veridical preference types, as
+well as competitive and altruistic types.
 
@@
 
-\todo[inline]{text in this section and the next is rough and unpolished, only intended to have
-  the basic results recorded, so that we can reshape the article around the basic results}
-
-To see how different choice mechanisms behave in evolutionary competition based on solitary decision
-problems, we approximated, much in the spirit of meta-games, average accumulated payoffs
-obtained in randomly generated solitary decision problems. For our purposes, a decision problem
-$\tuple{S, \Acts, u}$ consists of a set of world states $S$, a set of acts
-$\Acts$, and a utility function $u \mycolon S \times \Acts \rightarrow
-\mathbb{R}$.
-We generated arbitrary decision problems by selecting numbers of states and acts
+To see how different choice mechanisms behave in evolutionary competition based on solitary
+decision problems, we approximated, much in the spirit of meta games, average accumulated
+payoffs obtained in randomly generated solitary decision problems. For our purposes, a decision
+problem $\tuple{S, \Acts, u}$ consists of a set of world states $S$, a set of acts $\Acts$, and
+a utility function $u \mycolon S \times \Acts \rightarrow \mathbb{R}$.  We generated arbitrary
+decision problems by selecting, uniformly at random, numbers of states and acts
 $n_s, n_\act \in \set{2, \dots, 10}$ and then filling the utility table, so to speak, by
-independently picking a number $u(s, \act) \in \set{0, 10}$ uniformly at random, just
-as we did before with symmetric games. Unlike with two-player games, we need to also sample the
-actual state of the world, which we selected uniformly at random from the available states in
-the current decision problem. Player types, consisting of epistemic types $\text{prc}$ and
-$\text{imp}$ and preference types $\text{reg}$ and $\text{obj}$, give rise to behavior in
-the same way as before.\footnote{Obviously, now with $ \text{imp} \equiv \text{imp}(S) :=\lbrace \mu \in \mathbb{R}^{S}: \sum_{s \in S} \mu(s) = 1 \rbrace$.} (It is obviously not possible to carry altruistic or competitive
-preference types over to solitary decision making.) As before, we recorded the behavioral
-decisions for each of the four relevant player types in each sampled decision problem, and
-determined the actual payoff obtained, given the actual state. Average payoff over 100,000 decision
-problems are given in Table~\ref{tab:SolitaryDecisions}.
+i.i.d.~samples for each $u(s, \act) \in \set{0, 10}$, uniformly at random. Unlike with
+two-player games, we need to also sample the actual state of the world, which we selected
+uniformly at random from the available states in the current decision problem. As player types,
+we considered the original cast of four from Table~\ref{tab:CMs} again, since altruistic and
+competitive preferences are meaningless in solitary decision situations. As before, the
+relevant fitness measure, defined in Equation~(\ref{eq:FittnessChoiceMechSolitary}), was
+approximated by Monte Carlo simulation, the results of which are given in
+Table~\ref{tab:SolitaryDecisions}.
 
@@
   \end{tabular}
-  \caption{Average payoffs over 100,000 simulated solitary decision problems}
+  \caption{Expected fitness of choice mechanisms approximated from 100,000 simulated solitary
+    decision problems (see main text)}
   \label{tab:SolitaryDecisions}
@@
 Facts~\ref{fact:maxEU-minReg} and \ref{fact:equivalence2x2} still apply:
-$(\text{reg}, \text{prc})$ and $(\text{obj}, \text{prc})$ are behaviorally equivalent
-in general, and $(\text{reg}, \text{imp})$ is behaviorally equivalent to the former two in
-decision problems with 2 states and 2 acts. \todo{show this?} We see this in part in the
-results in Table~\ref{tab:SolitaryDecisions} in that the averages for $(\text{reg},
-  \text{prc})$ and $(\text{obj}, \text{prc})$ are identical. But since we included decision
-problems with more acts and more states as well, the averages for regret minimizers
-$(\text{reg}, \text{imp})$ are not identical to the one of $(\text{reg},
-  \text{prc})$ and $(\text{obj}, \text{prc})$. They are, in fact, lower, but not as low as
-those of the minimax choosers.
-
-What that means is that basically every relevant result we have seen about game situations is also borne out
-when reasoning about solitary decisions. Evolutionary selection based on objective fitness will
-not select against regret-based subjective preferences, as these are indistinguishable from
-veridical preferences when paired with probabilistic beliefs. But when paired with
-non-probabilistic belief types, regret-based preferences actually outperform veridical
-preferences. Consequently, if there is a chance, however small, that agents must fall back onto
-non-probabilistic beliefs, evolution will actually positively select for non-veridical
-regret-based preferences.
+$(\text{reg}, \text{prc})$ and $(\text{obj}, \text{prc})$ are behaviorally equivalent in
+general, and $(\text{reg}, \text{imp})$ is behaviorally equivalent to the former two in
+decision problems with 2 states and 2 acts. This shows in the results from
+Table~\ref{tab:SolitaryDecisions} in that the averages for $(\text{reg}, \text{prc})$ and
+$(\text{obj}, \text{prc})$ are identical. But since we included decision problems with more
+acts and more states as well, the averages for regret minimizers $(\text{reg}, \text{imp})$ are
+not identical to the one of $(\text{reg}, \text{prc})$ and $(\text{obj}, \text{prc})$. They
+are, in fact, lower, but not as low as those of $(\text{obj}, \text{imp})$.
+
+This means that every relevant result we have seen about game situations is also borne out for
+solitary decisions. Evolutionary selection based on objective fitness will not select against
+regret-based subjective preferences, as these are indistinguishable from veridical preferences
+when paired with precise beliefs. But when paired with imprecise beliefs, regret-based
+preferences outperform veridical preferences. Consequently, if there is a chance, however
+small, that agents fall back onto imprecise beliefs, evolution will actually positively select
+for non-veridical regret-based preferences.
 
@@
 more general approach here. We suggested that attention
-to “meta-games” is crucial, because what may be a good
+to “meta games” is crucial, because what may be a good
 subjective representation in one type of game (e.g., cooperative preferences in the Prisoner’s Dilemma class) need not
@@
 
-Finally, we hope to help the research direction towards a broader perspective on evolutionary game theory, as outlined by recent works in theoretical biology \citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be}.
-In partcular, the meta-game approach allows the researcher to both explicitly model the relevant features of the environment and shift the target of evolution from plain behavior to more general behavioral patterns, or choice mechanisms.
-Several uses and improvements of the present model are still possible in many respects.
-We can sketch some of them here.
-For example, the evolutionary investigation of different risk and ambiguity attitudes when competing against each other in an evolutionarily richer environment may bring new insights on both behavioral and theoretic decision making under uncertainty, as well as on many issues in theoretical biology and behavioral ecology.
+Meta games are a useful tool for probing into conceptual questions about the ecological
+rationality of choice mechanisms. The approach is rich and general, with many possible further
+applications imaginable beyond the case study presented here. For example, the evolutionary
+investigation of different risk and ambiguity attitudes when competing against each other in an
+evolutionarily richer environment may bring new insights on both behavioral and theoretic
+decision making under uncertainty, as well as on many issues in theoretical biology and
+behavioral ecology. Moreover, variability in the action selection function has been entirely
+ignored in this paper. Finally, while this paper only used dummy models of diverse decision
+environments, the meta game approach also allows for empirically informed models of rich and
+variable environments.
 

### 2015-12-23 paper/paper.tex
proof revision

@@
 
-Section \ref{sec:rati--subj} reviews different accounts of rationality in decision theory and
-relates the approach we take here to the existing literature on the topic. Section
-\ref{sec:basic-notions} introduces relevant decision- and game-theoretic notions. Sections
-\ref{sec:model} and \ref{sec:basic-model-1} define the evolutionary framework, and Section
-\ref{sec:results:-basic-model} presents the main results of the paper. Section
-\ref{sec:extensions} extends the evolutionary analysis by introducing more choice mechanisms in
-the model and by investigating the evolutionary performances of different choice mechanisms
-when facing arbitrary decision problems. Finally, in Section \ref{sec:conclusion} we reflect on
-the results achieved.
-
-\todo[inline]{rewrite overview after restructuring}
+Section \ref{sec:rati--subj} reviews different views of rational choice and relates the
+approach we take here to the existing literature. Section \ref{sec:basic-notions} introduces
+relevant decision- and game-theoretic notions and spells out four choice mechanisms on whose
+evolutionary competition we will zoom in Section~\ref{sec:basic-model-1}, which presents the
+main results of the paper. Section \ref{sec:extensions} extends the evolutionary analysis by
+introducing more choice mechanisms and alternative models of the environment.
 
@@
   Let $S$ be a (finite) set of states of the world and $A$ a (finite) set of actions. Given a
-  probability distribution $\mu$ over $S$ and a utility function
-  $u \mycolon S \times A \rightarrow \mathbb{R} $, an action $a^* \in A$ is a rational choice
+  probability distribution $\mu$ over $S$ and a payoff function
+  $\pi \mycolon S \times A \rightarrow \mathbb{R} $, an action $a^* \in A$ is a rational choice
   if it maximizes the \emph{(subjective) expected utility}
-  $\EU(a) = \sum_{s \in S} \mu(s) \ u(s, a)$.
+  $\EU(a) = \sum_{s \in S} \mu(s) \ \pi(s, a)$.
 \end{definition}
@@
   \label{eq:FittnessChoiceMechSolitary}
-  F(c) = \int P(d) \  \utils_d(c) \text{ d} d \,,
+  F(c) = \int P(d) \  \pi_d(c) \text{ d} d \,,
 \end{align}
-where $P(d)$ is the probability (density) of $d$ occurring and $\Utils_d(c)$ is the payoff of
+where $P(d)$ is the probability (density) of $d$ occurring and $\pi_d(c)$ is the payoff of
 the act selected by $c$ in $d$. Probability measure $P(d)$ is our model of the statistical
@@
   \label{eq:FittnessChoiceMechGame}
-  F(c) = \int \int P(g) \  P(c') \  \utils_g(c,c') \text{ d} g \,,
+  F(c) = \int \int P(g) \  P(c') \  \pi_g(c,c') \text{ d} g \,,
 \end{align}
 where $P(g)$ is the probability (density) of game $g$, $P(c')$ is the probability of
-encountering a co-player who uses choice mechanism $c'$ and $\utils_g(c,c')$ is the payoff for
+encountering a co-player who uses choice mechanism $c'$ and $\pi_g(c,c')$ is the payoff for
 a $c$-player in $g$ against the $c'$-player, given by the payoff in $g$ of the actions that $c$
@@
   \label{eq:FittnessChoiceMechGamePairwise}
-  F(c, c') = \int P(g) \  \utils_g(c,c') \text{ d} g \,.
+  F(c, c') = \int P(g) \  \pi_g(c,c') \text{ d} g \,.
 \end{align}
@@
   $\pi \mycolon C \times C \rightarrow \mathbb{R}$ such that
-  $\pi(c,c') = F(c,c') = \int P(g) \  \utils_g(c,c') \text{ d} g$.
+  $\pi(c,c') = F(c,c') = \int P(g) \  \pi_g(c,c') \text{ d} g$.
 \end{definition}
@@
 
-Proofs for Proposition \ref{proposition1} and Corollary~\ref{corollary1} are given in
-Appendix~\ref{sec:proofs}. They tell us that the main conclusions drawn in the previous section
-based on the approximated meta game in Table~\ref{tab:ExpectedFitness_4Types} hold more
-generally for any class of games in which the probability of encountering a game is the product
-of independently sampling four identically distributed payoff values. As before,
-$(\text{reg}, \text{imp})$, $(\text{obj}, \text{prc})$, and $(\text{reg}, \text{prc})$ players
-will be neutrally stable, and fitness-based selection will tend to weed out maxmin play and
-leave us with a population of arbitrary frequency of $(\text{reg}, \text{imp})$,
-$(\text{obj}, \text{prc})$, and $(\text{reg}, \text{prc})$ players. This shows that there is
-support for the main conceptual point that we wanted to make: non-veridical subjective
-preference relations \emph{can}, under specific circumstances, persist under evolutionary
-selection based on objective fitness. Moreover, regret-based preferences can not only persist,
-but even be favored by natural selection if agents may have imprecise beliefs. This holds
-generally for playing arbitrary $2 \times 2$ symmetric games whose payoffs are sampled
-identically and independently at random.
+A proofs for Proposition \ref{proposition1} is given in Appendix~\ref{sec:proofs}. The result
+tells us that the main conclusions drawn in the previous section based on the approximated meta
+game in Table~\ref{tab:ExpectedFitness_4Types} hold more generally for any class of games in
+which the probability of encountering a game is the product of independently sampling four
+identically distributed payoff values. As before, $(\text{reg}, \text{imp})$,
+$(\text{obj}, \text{prc})$, and $(\text{reg}, \text{prc})$ players will be neutrally stable,
+and fitness-based selection will tend to weed out maxmin play and leave us with a population of
+arbitrary frequency of $(\text{reg}, \text{imp})$, $(\text{obj}, \text{prc})$, and
+$(\text{reg}, \text{prc})$ players. This shows that there is support for the main conceptual
+point that we wanted to make: non-veridical subjective preference relations \emph{can}, under
+specific circumstances, persist under evolutionary selection based on objective
+fitness. Moreover, regret-based preferences can not only persist, but even be favored by
+natural selection if agents may have imprecise beliefs. This holds generally for playing
+arbitrary $2 \times 2$ symmetric games whose payoffs are sampled identically and independently
+at random.
 
@@
 
-The proof of Proposition \ref{proposition1} relies on a partition of $\mathcal{G}$,
-and on some lemmas. For brevity, let us denote the regret minimizer
-by $R$ and the maximinimizer by $M$, i.e, $R \equiv \kappa(\text{reg}, \text{imp})$ and $M \equiv  \kappa(\text{obj}, \text{imp})$.
-Recall from Equation \ref{eq:pairwiseEF} that $EF_{\mathcal{G}}(X,Y)$ denotes the expected evolutionary fitness of choice mechanism $X$ against choice mechanism $Y$
-with respect to the class of fitness games $\mathcal{G}$.
+The proof of Proposition \ref{proposition1} relies on a partition of $\mathcal{G}$, and on some
+lemmas. For brevity, let us denote the regret minimizer $(\text{reg}, \text{imp})$ by $R$ and
+the maximinimizer $(\text{obj}, \text{imp})$ by $M$. Following
+Equation~(\ref{eq:FittnessChoiceMechGamePairwise}), let $F_{\mathcal{G}}(X,Y)$ denotes the of
+choice mechanism $X$ against choice mechanism $Y$ on the possibly restricted class of fitness
+games $\mathcal{G}$.
 
@@
 
-\noindent \textbf{Proof of Proposition \ref{proposition1}.} By definition of strict Nash equilibrium, we have to
-show that in the class $\mathcal{G}$ of symmetric $2\times2$ games with payoffs sampled from a set of i.i.d. values with at least 3 elements in the support, it holds:
+\noindent \textbf{Proof of Proposition \ref{proposition1}.} By definition of strict dominance,
+we have to show that in the class $\mathcal{G}$ of symmetric $2\times2$ games with payoffs
+sampled from a set of i.i.d. values with at least 3 elements in the support, it holds:
+\begin{multicols}{2}
   \begin{itemize}
-\item[(i)] $EF_{\mathcal{G}}(R,R)>EF_{\mathcal{G}}(M,R);$
-\item[(ii)] $EF_{\mathcal{G}}(M,M)<EF_{\mathcal{G}}(R,M).$
+  \item[(i)] $F_{\mathcal{G}}(R,R)>F_{\mathcal{G}}(M,R);$
+  \item[(ii)] $F_{\mathcal{G}}(M,M)<F_{\mathcal{G}}(R,M).$
   \end{itemize}
-
-\noindent To show
-the result we will use the following partition of $\mathcal{G}$.
+\end{multicols}
+
+\noindent To show this we use the following partition of $\mathcal{G}$, based on payoffs parameterized as
+follows:
+\begin{center}
+  \begin{tabular}{ccc}
+    \toprule
+    & $I$ & $II$ \\ \midrule
+    $I$ & $a$ & $b$ \\
+    $II$ & $c$ & $d$ \\ \bottomrule
+  \end{tabular}
+\end{center}
 \begin{enumerate}
@@
 \end{enumerate}
-Before proving the lemmas, it is convenient to fix some notation. Let us call $x,y,z$ the 3 elements in the support, and without loss of generality suppose that $ x > y > z $. 
-We denote by $C$ a coordination game in $\mathcal{C}$ with
-payoffs $a_{C}$, $b_{C}$, $c_{C}$, and $d_{C}$;
-similarly for games $A \in \mathcal{A}$, $S \in \mathcal{S}$, $W \in \mathcal{W}$, and $B \in \mathcal{B}$. 
-Let us denote by $I_{RC}$ the event that a $R$-player plays action $I$ in the game $C$; and similarly for action $II$, for player $M$, and for games $A$, $S$, $W$ and $B$.
-We first consider the case of i.i.d.
-sampling with finite support.
-
-\medskip{}
-
-\begin{lemma} \label{lemma:S-B games}
-$R$ and $M$ perform equally well in $\mathcal{S}$
-and in $\mathcal{B}$. 
+Before proving the lemmas, it is convenient to fix some notation. Let us call $x,y,z$ the 3
+elements in the support, and without loss of generality suppose that $ x > y > z $.  We denote
+by $C$ a coordination game in $\mathcal{C}$ with payoffs $a_{C}$, $b_{C}$, $c_{C}$, and
+$d_{C}$; similarly for games $A \in \mathcal{A}$, $S \in \mathcal{S}$, $W \in \mathcal{W}$, and
+$B \in \mathcal{B}$.  Let us denote by $I_{RC}$ the event that an $R$-player plays action $I$ in
+the game $C$; and similarly for action $II$, for player $M$, and for games $A$, $S$, $W$ and
+$B$. We first consider the case of i.i.d. sampling with finite support.
+
+\begin{lemma} \label{lemma:S-B games} $R$ and $M$ perform equally well in $\mathcal{S}$ and in
+  $\mathcal{B}$.
 \end{lemma}
@@
 \begin{proof}
-By definition of regret minimization and maxmin it
-is easy to check that whenever in a game there is a strongly dominant
-action $a^{\$}$, then $a^{\$}$ is both the maxmin action and the
-regret minimizing action. Then, for all the games in $\mathcal{S}$,
-$R$ chooses action $a$ if and only if $M$ chooses action $a$. Consequently,
-$R$ and $M$ always perform equally (well) in $\mathcal{S}$. In
-the case of $\mathcal{B}$ it is trivial to see that all the players
+  By definition of regret minimization and maxmin it is easy to check that whenever in a game
+  there is a strongly dominant action $a^{\$}$, then $a^{\$}$ is both the maxmin action and the
+  regret minimizing action. Then, for all the games in $\mathcal{S}$, $R$ chooses action $a$ if
+  and only if $M$ chooses action $a$. Consequently, $R$ and $M$ always perform equally (well)
+  in $\mathcal{S}$. In the case of $\mathcal{B}$ it is trivial to see that all the players
   perform equally.
@@
 
-\medskip{}
-
-\begin{lemma} \label{lemma:W games}
-In $\mathcal{W}$, $(R,R)$ is the only (strict) Nash equilibrium.
+\begin{lemma} \label{lemma:W games} In $\mathcal{W}$, $R$ strictly dominates $M$.
 \end{lemma}
@@
 \begin{proof}
-Assume without loss of generality that $b=d$. There are two situations that we have to check: (i) $b=d \geq a,c$ and $ a \neq c $; (ii) $b=d \leq a,c$ and $ a \neq c $.
-In the first case it
-is easy to see that $R$ and $M$ perform equally well. Indeed, given
-(i), both $R$ and $M$ choose action $I$ if $a>c$, and action $II$
-if $c>a$. If case (ii) holds instead, we have that $R$ plays $I$
-if $a>c$ and $II$ if $c>a$ as before, but $M$ plays $(\frac{1}{2}I;\frac{1}{2}II)$,
-since both $I$ and $II$ maximize the minimal payoff. Consider now
-a population of $R$ and $M$ playing games from the class $\mathcal{W}$.
-Whenever (i) is the case both $R$ and $M$ perform equally. Suppose that
-(ii) is the case and that $a>c$, without loss of generality.
-Then,  $EF(R,R)=a>\frac{1}{2}a+\frac{1}{2}c=EF(M,R)$, whereas $EF(M,M)=\frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d<\frac{1}{2}a+\frac{1}{2}b=EF(R,M)$.
-Hence, we have that in general $EF_{\mathcal{W}}(R,R)>EF_{\mathcal{W}}(M,R),\mbox{ and }EF_{\mathcal{W}}(M,M)<EF_{\mathcal{W}}(R,M)$.
+  Assume without loss of generality that $b=d$. There are two situations that we have to check:
+  (i) $b=d \geq a,c$ and $ a \neq c $; (ii) $b=d \leq a,c$ and $ a \neq c $.\todo{what about
+    $a < b = d < c$ and $c < b = d < a$?}\ In the first case it is easy to see that $R$ and $M$
+  perform equally well. Indeed, given (i), both $R$ and $M$ choose action $I$ if $a>c$, and
+  action $II$ if $c>a$. If case (ii) holds instead, we have that $R$ plays $I$ if $a>c$ and
+  $II$ if $c>a$ as before, but $M$ plays $(\frac{1}{2}I;\frac{1}{2}II)$, since both $I$ and
+  $II$ maximize the minimal payoff. Consider now a population of $R$ and $M$ playing games from
+  the class $\mathcal{W}$.  Whenever (i) is the case both $R$ and $M$ perform equally. Suppose
+  that (ii) is the case and $W \in mathcal{W}$ is such that $a>c$, without loss of generality. Then,
+  $\pi_W(R,R)=a>\frac{1}{2}a+\frac{1}{2}c=\pi_W(M,R)$, whereas
+  $\pi_W(M,M)=\frac{1}{4}a+\frac{1}{4}b+\frac{1}{4}c+\frac{1}{4}d<\frac{1}{2}a+\frac{1}{2}b=\pi_W(R,M)$.
+  Hence, we have that in general
+  $F_{\mathcal{W}}(R,R)>F_{\mathcal{W}}(M,R),\mbox{ and
+  }F_{\mathcal{W}}(M,M)<F_{\mathcal{W}}(R,M)$.
 \end{proof}
 
-\medskip{}
-
-Since it is not difficult to see that both $(R,R)$ and $(M,M)$ are strict Nash equilibria in $\mathcal{C}$, and that $(R,R)$ and $(M,M)$ are not Nash equilibria in $\mathcal{A}$, the main part of
-the proof will be to show that $(R,R)$ is the only (strict) Nash equilibrium in the class $\mathcal{C}\cup\mathcal{A}$, that is:
+Since it is not difficult to see that both $(R,R)$ and $(M,M)$ are strict Nash equilibria in
+$\mathcal{C}$, and that $(R,R)$ and $(M,M)$ are not Nash equilibria in $\mathcal{A}$, the main
+part of the proof will be to show that $R$ strictly dominates $C$ in the class
+$\mathcal{C}\cup\mathcal{A}$, that is:
+\begin{multicols}{2}
   \begin{itemize}
-\item[(i')] $EF_{\mathcal{C}\cup\mathcal{A}}(R,R)>EF_{\mathcal{C}\cup\mathcal{A}}(M,R),$
-\item[(ii')] $EF_{\mathcal{C}\cup\mathcal{A}}(M,M)<EF_{\mathcal{C}\cup\mathcal{A}}(R,M).$
+  \item[(i')] $F_{\mathcal{C}\cup\mathcal{A}}(R,R)>F_{\mathcal{C}\cup\mathcal{A}}(M,R),$
+  \item[(ii')] $F_{\mathcal{C}\cup\mathcal{A}}(M,M)<F_{\mathcal{C}\cup\mathcal{A}}(R,M).$
   \end{itemize}
+\end{multicols}
 
@@
 
-\medskip{}
-
-\begin{definition}[$\phi$] \label{def:bijection phi}
-The permutation $\phi(a,b,c,d)=(c,d,a,b)$ defines a bijective function $\phi:\mathcal{C}\rightarrow\mathcal{A}$ that for each
-coordination game $C\in\mathcal{C}$ with payoffs $(a_{C},b_{C},c_{C},d_{C})$
-gives the anti-coordination game $A\in\mathcal{A}$ with payoffs
-$(a_{A},b_{A},c_{A},d_{A})=(c_{C},d_{C},a_{C},b_{C})$.
+\begin{definition}[$\phi$] \label{def:bijection phi} The permutation $\phi(a,b,c,d)=(c,d,a,b)$
+  defines a bijective function $\phi:\mathcal{C}\rightarrow\mathcal{A}$ that for each
+  coordination game $C\in\mathcal{C}$ with payoffs $(a_{C},b_{C},c_{C},d_{C})$ gives the
+  anti-coordination game $A\in\mathcal{A}$ with payoffs
+  $(a_{A},b_{A},c_{A},d_{A})=(c_{C},d_{C},a_{C},b_{C})$. Essentially, $\phi$ is swapping rows
+  in the payoff matrix.
 \end{definition}
 
-\medskip{}
-
 \begin{lemma} \label{lemma:probabilities coord-ant}
+Occurrence probability of $C$ equals that of $\phi(C)$: $P(\phi(C))=P(C)$.
+\end{lemma}
+
+\begin{proof}
+  By definition, each game $C\equiv(a_{C},b_{C},c_{C},d_{C})$ is such that $a_{C}>c_{C}$ and
+  $d_{C}>b_{C}$, and each game $A\equiv(a_{A},b_{A},c_{A},d_{A})$ is such that $a_{A}<c_{A}$
+  and $d_{A}>b_{A}$. Given that $a,b,c,d$ are i.i.d. random variables and that a sequence of
+  i.i.d. random variables is exchangeable, it is clear that the probability of
+  $(a_{C},b_{C},c_{C},d_{C})$ equals the probability of $(c_{C},d_{C},a_{C},b_{C})$.  Hence,
   $P(\phi(C))=P(C)$.
-\end{lemma}
-
-\begin{proof}
-By definition, each game $C\equiv(a_{C},b_{C},c_{C},d_{C})$
-is such that $a_{C}>c_{C}$ and $d_{C}>b_{C}$, and
-each game $A\equiv(a_{A},b_{A},c_{A},d_{A})$
-is such that $a_{A}<c_{A}$ and $d_{A}>b_{A}$. Given that
-$a,b,c,d$ are i.i.d. random variables and that a sequence of i.i.d. random variables is exchangeable,
-it is clear that the probability of $(a_{C},b_{C},c_{C},d_{C})$ equals the probability of $(c_{C},d_{C},a_{C},b_{C})$.
-Hence, $P(\phi(C))=P(C)$.
 \end{proof}
 
-\medskip{}
-
-\begin{lemma} \label{lemma:probabilities actions coord-ant}
-Let $P(E)$ be the probability of event $E$, then
-it holds that:
+\begin{lemma} \label{lemma:probabilities actions coord-ant} Let $P(E)$ be the probability of
+  event $E$, e.g., $P(I_{RC})$ is the probability that a random $R$-player plays act $I$ is
+  fixed coordination game $C$, which is either 0, $.5$ or 1, depending on $C$.  It then holds
+  that:
 \begin{itemize}
@@
 \begin{proof}
-It is easy to check that if $b_{C}-d_{C}>c_{C}-a_{C}$,
-a $R$-player plays action $I$ in $C$; that if $b_{C}-d_{C}<c_{C}-a_{C}$,
-$R$ plays $II$; and that if $b_{C}-d_{C}=c_{C}-a_{C}$,
-a $R$-player is indifferent between $I$ and $II$ in $C$, and
-we assume that randomizes with $(\frac{1}{2}I;\frac{1}{2}II)$. Similarly,
-if $a_{A}-c_{A}>d_{A}-b_{A}$, a $R$-player plays action
-$I$ in $A$; if $a_{A}-c_{A}<d_{A}-b_{A}$, $R$
-plays $II$; and if $a_{A}-c_{A}=d_{A}-b_{A}$, a
-$R$-player is indifferent between $I$ and $II$ in $A$, and randomizes
-with $(\frac{1}{2}I;\frac{1}{2}II)$. Consequently, if $b_{C}-d_{C}>c_{C}-a_{C}$,
-then $P(I_{RC})=1$, and by definition of $\phi$ we have
-$P(II_{R\phi(C)})=1$. Likewise, if $b_{C}-d_{C}<c_{C}-a_{C}$,
-then $P(II_{RC})=1=P(I_{R\phi(C)})$; and if $b_{C}-d_{C}=c_{C}-a_{C}$,
+  It is easy to check that if $b_{C}-d_{C}>c_{C}-a_{C}$, an $R$-player plays action $I$ in $C$;
+  that if $b_{C}-d_{C}<c_{C}-a_{C}$, $R$ plays $II$; and that if $b_{C}-d_{C}=c_{C}-a_{C}$, a
+  $R$-player is indifferent between $I$ and $II$ in $C$, and so randomizes with
+  $(\frac{1}{2}I;\frac{1}{2}II)$. Similarly, if $a_{A}-c_{A}>d_{A}-b_{A}$, an $R$-player plays
+  action $I$ in $A$; if $a_{A}-c_{A}<d_{A}-b_{A}$, $R$ plays $II$; and if
+  $a_{A}-c_{A}=d_{A}-b_{A}$, an $R$-player is indifferent between $I$ and $II$ in $A$, and
+  randomizes with $(\frac{1}{2}I;\frac{1}{2}II)$. Consequently, if $b_{C}-d_{C}>c_{C}-a_{C}$,
+  then $P(I_{RC})=1$, and by definition of $\phi$ we have $P(II_{R\phi(C)})=1$. Likewise, if
+  $b_{C}-d_{C}<c_{C}-a_{C}$, then $P(II_{RC})=1=P(I_{R\phi(C)})$; and if
+  $b_{C}-d_{C}=c_{C}-a_{C}$,
   then $P(I_{RC})=P(II_{RC})=\frac{1}{2}=P(II_{R\phi(C)})=P(I_{R\phi(C)})$. \\
-In the same way, in coordination games we have that if $b_{C}>c_{C}$,
-a $M$-player plays $I$; if $c_{C}>b_{C}$, a $M$-player plays
-$II$; and if $b_{C}=c_{C}$, $M$ is indifferent between $I$
-and $II$, and plays $(\frac{1}{2}I;\frac{1}{2}II)$. In anti-coordination
-games instead, if $a_{A}>d_{A}$, $M$ plays $I$; if $a_{A}<d_{A}$,
-$M$ plays $II$; if $a_{A}=d_{A}$, $M$ plays $(\frac{1}{2}I;\frac{1}{2}II)$.
-By definition of $\phi$: $P(I_{MC})=1=P(II_{M\phi(C)})$
-if $b_{C}>c_{C}$; $P(II_{MC})=1=P(I_{M\phi(C)})$
-if $c_{C}>b_{C}$; and $P(I_{MC})=P(II_{MC})=\frac{1}{2}=P(II_{M\phi(C)})=P(I_{M\phi(C)})$
-if $b_{C}=c_{C}$.
+  In the same way, in coordination games we have that if $b_{C}>c_{C}$, an $M$-player plays $I$;
+  if $c_{C}>b_{C}$, an $M$-player plays $II$; and if $b_{C}=c_{C}$, $M$ is indifferent between
+  $I$ and $II$, and plays $(\frac{1}{2}I;\frac{1}{2}II)$. In anti-coordination games instead,
+  if $a_{A}>d_{A}$, $M$ plays $I$; if $a_{A}<d_{A}$, $M$ plays $II$; if $a_{A}=d_{A}$, $M$
+  plays $(\frac{1}{2}I;\frac{1}{2}II)$.  By definition of $\phi$:
+  $P(I_{MC})=1=P(II_{M\phi(C)})$ if $b_{C}>c_{C}$; $P(II_{MC})=1=P(I_{M\phi(C)})$ if
+  $c_{C}>b_{C}$; and $P(I_{MC})=P(II_{MC})=\frac{1}{2}=P(II_{M\phi(C)})=P(I_{M\phi(C)})$ if
+  $b_{C}=c_{C}$.
 \end{proof}
-
-\medskip{}
 
@@
 It holds that:
+\begin{multicols}{2}
   \begin{itemize}
   \item $a_{C}>d_{C}\rightarrow(I_{MC}\subset I_{RC})$;
+  \item $a^{C}=d^{C}\rightarrow I_{MC}=I_{RC}$.
   \item $a_{C}<d_{C}\rightarrow(II_{MC}\subset II_{RC})$;
-\item $a^{C}=d^{C}\rightarrow I_{MC}=I_{RC}$.
   \end{itemize}
+\end{multicols}
 \end{lemma}
@@
 \begin{proof}
-If $b_{C}-d_{C}>c_{C}-a_{C}$, $R$ plays
-$I$, and if $b_{C}-d_{C}=c_{C}-a_{C}$, $R$ plays
-$(\frac{1}{2}I;\frac{1}{2}II)$, whereas if $b_{C}>c_{C}$,
-$M$ plays $I$, and if $b_{C}=c_{C}$, $M$ plays $(\frac{1}{2}I;\frac{1}{2}II)$.
-Then, $I_{RC}$ implies that $b_{C}-d_{C}\geq c_{C}-a_{C}$,
-and $I_{MC}$ implies that $b_{C}\geq c_{C}$. Moreover,
-on the assumption that $a_{C}>d_{C}$, it is easy to check
-that $b_{C}\geq c_{C}$ implies $b_{C}-d_{C}>c_{C}-a_{C}$.
-Hence, in any $C$ with $a_{C}>d_{C}$ it holds that $I_{MC}\mbox{ implies }I_{RC}$,
-i.e., $a_{C}>d_{C}\rightarrow(I_{MC}\subseteq I_{RC})$.
-Instead, it is possible that $a_{C}>d_{C}$, $b_{C}-d_{C}>c_{C}-a_{C}$
-and $b_{C}<c_{C}$ hold simultaneously, so that $I_{MC}\nsupseteq I_{RC}$.
-Consequently: $a_{C}>d_{C}\rightarrow(I_{MC}\subset I_{RC})$.
-By symmetric argument it can be shown that $a_{C}<d_{C}\rightarrow(II_{MC}\subset II_{RC})$
-too. \\
-Finally, when $a_{C}=d_{C}$ it holds that: $b_{C}-d_{C}>c_{C}-a_{C}$
-iff $b_{C}>c_{C}$; $b_{C}-d_{C}<c_{C}-a_{C}$
-iff $b_{C}<c_{C}$; and $b_{C}-d_{C}=c_{C}-a_{C}$
-iff $b_{C}=c_{C}$. Hence, $a_{C}=d_{C}\rightarrow I_{MC}=I_{RC}$.
+  If $b_{C}-d_{C}>c_{C}-a_{C}$, $R$ plays $I$, and if $b_{C}-d_{C}=c_{C}-a_{C}$, $R$ plays
+  $(\frac{1}{2}I;\frac{1}{2}II)$, whereas if $b_{C}>c_{C}$, $M$ plays $I$, and if
+  $b_{C}=c_{C}$, $M$ plays $(\frac{1}{2}I;\frac{1}{2}II)$.  Then, $I_{RC}$ implies that
+  $b_{C}-d_{C}\geq c_{C}-a_{C}$, and $I_{MC}$ implies that $b_{C}\geq c_{C}$. Moreover, on the
+  assumption that $a_{C}>d_{C}$, it is easy to check that $b_{C}\geq c_{C}$ implies
+  $b_{C}-d_{C}>c_{C}-a_{C}$.  Hence, in any $C$ with $a_{C}>d_{C}$ it holds that
+  $I_{MC}\mbox{ implies }I_{RC}$, i.e., $a_{C}>d_{C}\rightarrow(I_{MC}\subseteq I_{RC})$.
+  Instead, it is possible that $a_{C}>d_{C}$, $b_{C}-d_{C}>c_{C}-a_{C}$ and $b_{C}<c_{C}$ hold
+  simultaneously, so that $I_{MC}\nsupseteq I_{RC}$.  Consequently:
+  $a_{C}>d_{C}\rightarrow(I_{MC}\subset I_{RC})$.  By a symmetric argument it can be shown that
+  $a_{C}<d_{C}\rightarrow(II_{MC}\subset II_{RC})$ too. Finally, when $a_{C}=d_{C}$ it holds
+  that: $b_{C}-d_{C}>c_{C}-a_{C}$ iff $b_{C}>c_{C}$; $b_{C}-d_{C}<c_{C}-a_{C}$ iff
+  $b_{C}<c_{C}$; and $b_{C}-d_{C}=c_{C}-a_{C}$ iff $b_{C}=c_{C}$. Hence,
+  $a_{C}=d_{C}\rightarrow I_{MC}=I_{RC}$.
 \end{proof}
 
-\medskip{}
-
-\noindent We are now ready to prove that:
-\begin{itemize}
-\item[(i')] $EF_{\mathcal{C}\cup\mathcal{A}}(R,R)>EF_{\mathcal{C}\cup\mathcal{A}}(M,R);$
-\item[(ii')] $EF_{\mathcal{C}\cup\mathcal{A}}(M,M)<EF_{\mathcal{C}\cup\mathcal{A}}(R,M).$
-\end{itemize}
-We can rewrite $EF_{\mathcal{C}\cup\mathcal{A}}(R,R)>EF_{\mathcal{C}\cup\mathcal{A}}(M,R)$
-more explicitly as:
-
-\medskip{}
-
-\noindent $\sum_{C \in \mathcal{C}}P(C)[P(I_{RC}\cap I_{RC})\cdot a_{C}+P(II_{RC}\cap II_{RC})\cdot d_{C}+P(I_{RC}\cap II_{RC})\cdot b_{C}+P(II_{RC}\cap I_{RC})\cdot c_{C}]+\sum_{A \in \mathcal{A}}P(A)[P(I_{RA}\cap I_{RA})\cdot a_{A}+P(II_{RA}\cap II_{RA})\cdot d_{A}+P(I_{RA}\cap II_{RA})\cdot b_{A}+P(II_{RA}\cap I_{RA})\cdot c_{A}] > \sum_{C \in \mathcal{C}}P(C)[P(I_{RC}\cap I_{MC})\cdot a_{C}+P(II_{RC}\cap II_{MC})\cdot d_{C}+P(I_{RC}\cap II_{MC})\cdot c_{C}+P(II_{RC}\cap I_{MC})\cdot b_{C}]+\sum_{A \in \mathcal{A}}P(A)[P(I_{RA}\cap I_{MA})\cdot a_{A}+P(II_{RA}\cap II_{MA})\cdot d_{A}+P(I_{RA}\cap II_{MA})\cdot c_{A}+P(II_{RA}\cap I_{MA})\cdot b_{A}]$
-\medskip{}
-
-\noindent Then, the next derivation follows. By Lemma \ref{lemma:probabilities coord-ant} and Lemma \ref{lemma:probabilities actions coord-ant}, we can express
-everything in terms of $C$ only:
-\begin{itemize}
-
-%\item $\sum_{C}P(C)[P(I_{RC}\cap I_{RC})\cdot a_{C}+P(II_{RC}\cap II_{RC})\cdot d_{C}+P(I_{RC}\cap II_{RC})\cdot b_{C}+P(II_{RC}\cap I_{RC})\cdot c_{C}]+\sum_{A}P(A)[P(I_{RA}\cap I_{RA})\cdot a_{A}+P(II_{RA}\cap II_{RA})\cdot d_{A}+P(I_{RA}\cap II_{RA})\cdot b_{A}+P(II_{RA}\cap I_{RA})\cdot c_{A}] > \sum_{C}P(C)[P(I_{RC}\cap I_{MC})\cdot a_{C}+P(II_{RC}\cap II_{MC})\cdot d_{C}+P(I_{RC}\cap II_{MC})\cdot c_{C}+P(II_{RC}\cap I_{MC})\cdot b_{C}]+\sum_{A}P(A)[P(I_{RA}\cap I_{MA})\cdot a_{A}+P(II_{RA}\cap II_{MA})\cdot d_{A}+P(I_{RA}\cap II_{MA})\cdot c_{A}+P(II_{RA}\cap I_{MA})\cdot b_{A}]$
-
-\item $\sum_{C}P(C)[P(I_{RC}\cap I_{RC})\cdot a_{C}+P(II_{RC}\cap II_{RC})\cdot d_{C}+P(I_{RC}\cap II_{RC})\cdot b_{C}+P(II_{RC}\cap I_{RC})\cdot c_{C} +P(II_{RC}\cap II_{RC})\cdot c_{C}+P(I_{RC}\cap I_{RC})\cdot b_{C}+P(II_{RC}\cap I_{RC})\cdot d_{C}+P(I_{RC}\cap II_{RC})\cdot a_{C}] > \sum_{C}P(C)[P(I_{RC}\cap I_{MC})\cdot a_{C}+P(II_{RC}\cap II_{MC})\cdot d_{C}+P(I_{RC}\cap II_{MC})\cdot c_{C}+P(II_{RC}\cap I_{MC})\cdot b_{C}+P(II_{RC}\cap II_{MC})\cdot c_{C}+P(I_{RC}\cap I_{MC})\cdot b_{C}+P(II_{RC}\cap I_{MC})\cdot a_{C}+P(I_{RC}\cap II_{MC})\cdot d_{C}]$
-
-\item $\sum_{C}P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) + P(I_{RC}\cap II_{RC})) + b_{C} \cdot  (P(I_{RC}\cap II_{RC}) + P(I_{RC}\cap I_{RC})) + c_{C} \cdot (P(II_{RC}\cap I_{RC}) +P(II_{RC}\cap II_{RC})) + d_{C} \cdot (P(II_{RC}\cap II_{RC})+P(II_{RC}\cap I_{RC}))]> \sum_{C}P(C)[a_{C} \cdot (P(I_{RC}\cap I_{MC})+P(II_{RC}\cap I_{MC})) + b_{C} \cdot (P(II_{RC}\cap I_{MC})+P(I_{RC}\cap I_{MC})) + c_{C} \cdot (P(I_{RC}\cap II_{MC})+P(II_{RC}\cap II_{MC})) + d_{C} \cdot (P(II_{RC}\cap II_{MC})+P(I_{RC}\cap II_{MC}))]$
-
-\end{itemize}
-
-\noindent Now let us split into $a>d$ and $a<d$, and consider $a>d$ first.
-Notice that, by Lemma \ref{lemma:action implications}, the case $a=d$ is irrelevant in order to
-discriminate between $R$ and $M$. If $a>d$, by Lemma \ref{lemma:action implications} we can eliminate
-the cases where $R$ plays $II$ and $M$ plays $I$:
-
-\begin{itemize}
-
-\item $\sum_{C_{a>d}} P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) + P(I_{RC}\cap II_{RC})) + b_{C} \cdot  (P(I_{RC}\cap II_{RC}) + P(I_{RC}\cap I_{RC})) + c_{C} \cdot (P(II_{RC}\cap I_{RC}) +P(II_{RC}\cap II_{RC})) + d_{C} \cdot (P(II_{RC}\cap II_{RC})+P(II_{RC}\cap I_{RC}))]>
-\sum_{C_{a>d}} P(C)[a_{C} \cdot P(I_{RC}\cap I_{MC}) + b_{C} \cdot P(I_{RC}\cap I_{MC}) + c_{C} \cdot (P(I_{RC}\cap II_{MC})+P(II_{RC}\cap II_{MC})) + d_{C} \cdot (P(II_{RC}\cap II_{MC})+P(I_{RC}\cap II_{MC}))]$
-
-\item $\sum_{C_{a>d}} P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) + P(I_{RC}\cap II_{RC})- P(I_{RC}\cap I_{MC})) + b_{C} \cdot  (P(I_{RC}\cap II_{RC}) + P(I_{RC}\cap I_{RC})- P(I_{RC}\cap I_{MC})) + c_{C} \cdot (P(II_{RC}\cap I_{RC}) +P(II_{RC}\cap II_{RC})- P(I_{RC}\cap II_{MC})- P(II_{RC}\cap II_{MC})) + d_{C} \cdot (P(II_{RC}\cap II_{RC})+P(II_{RC}\cap I_{RC})- P(II_{RC}\cap II_{MC})- P(I_{RC}\cap II_{MC}))]> 0$
-
-\end{itemize}
+We are now ready to prove that
+$F_{\mathcal{C}\cup\mathcal{A}}(R,R)>F_{\mathcal{C}\cup\mathcal{A}}(M,R)$. With notation like
+$P(I_{RC} \cup I_{RC})$ denoting the probability that a random $R$-player plays $I$ and another
+$R$-player plays $I$ as well in game $C$, rewrite this as:
+\begin{align*}
+  & \sum_{C \in \mathcal{C}}P(C)[P(I_{RC}\cap I_{RC})\cdot a_{C}+P(II_{RC}\cap II_{RC})\cdot
+  d_{C}+P(I_{RC}\cap II_{RC})\cdot b_{C}+P(II_{RC}\cap I_{RC})\cdot c_{C}] 
+  \\ + & \sum_{A \in
+    \mathcal{A}}P(A)[P(I_{RA}\cap I_{RA})\cdot a_{A}+P(II_{RA}\cap II_{RA})\cdot
+  d_{A}+P(I_{RA}\cap II_{RA})\cdot b_{A}+P(II_{RA}\cap I_{RA})\cdot c_{A}]\\
+  > & \sum_{C \in
+    \mathcal{C}}P(C)[P(I_{RC}\cap I_{MC})\cdot a_{C}+P(II_{RC}\cap II_{MC})\cdot
+  d_{C}+P(I_{RC}\cap II_{MC})\cdot c_{C}+P(II_{RC}\cap I_{MC})\cdot b_{C}] \\
+   + & \sum_{A \in
+    \mathcal{A}}P(A)[P(I_{RA}\cap I_{MA})\cdot a_{A}+P(II_{RA}\cap II_{MA})\cdot
+  d_{A}+P(I_{RA}\cap II_{MA})\cdot c_{A}+P(II_{RA}\cap I_{MA})\cdot b_{A}]
+\end{align*}
+
+\noindent By Lemma \ref{lemma:probabilities coord-ant} and Lemma \ref{lemma:probabilities
+  actions coord-ant}, we can express everything in terms of $C$ only:
+\begin{align*}
+  & \textstyle{\sum_{C}} P(C)[P(I_{RC}\cap I_{RC})\cdot a_{C}+P(II_{RC}\cap II_{RC})\cdot d_{C}+P(I_{RC}\cap
+  II_{RC})\cdot b_{C}+P(II_{RC}\cap I_{RC})\cdot c_{C} + \\
+  & \ \ \ \ P(II_{RC}\cap II_{RC})\cdot c_{C}+P(I_{RC}\cap I_{RC})\cdot b_{C}+P(II_{RC}\cap
+  I_{RC})\cdot d_{C}+P(I_{RC}\cap
+  II_{RC})\cdot a_{C}] \\
+  > & \textstyle{\sum_{C}}P(C)[P(I_{RC}\cap I_{MC})\cdot a_{C}+P(II_{RC}\cap II_{MC})\cdot
+  d_{C}+P(I_{RC}\cap II_{MC})\cdot c_{C}+P(II_{RC}\cap I_{MC})\cdot b_{C} + \\
+  & \ \ \ \ P(II_{RC}\cap II_{MC})\cdot c_{C}+P(I_{RC}\cap I_{MC})\cdot b_{C}+P(II_{RC}\cap
+  I_{MC})\cdot a_{C}+P(I_{RC}\cap II_{MC})\cdot d_{C}]
+\end{align*}
+This simplifies to:
+\begin{align*}
+  & \textstyle{\sum_{C}}P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) + P(I_{RC}\cap II_{RC})) + b_{C}
+  \cdot (P(I_{RC}\cap II_{RC}) + P(I_{RC}\cap I_{RC})) + 
+\\ & \ \ \ \ c_{C} \cdot
+  (P(II_{RC}\cap I_{RC}) +P(II_{RC}\cap II_{RC})) + d_{C} \cdot (P(II_{RC}\cap
+  II_{RC})+P(II_{RC}\cap I_{RC}))] 
+\\ > & \textstyle{\sum_{C}}P(C)[a_{C} \cdot (P(I_{RC}\cap
+  I_{MC})+P(II_{RC}\cap I_{MC})) + b_{C} \cdot (P(II_{RC}\cap I_{MC})+P(I_{RC}\cap I_{MC})) + \\
+  & \ \ \ \ c_{C} \cdot (P(I_{RC}\cap II_{MC})+P(II_{RC}\cap II_{MC})) + d_{C} \cdot (P(II_{RC}\cap
+  II_{MC})+P(I_{RC}\cap II_{MC}))]
+\end{align*}
+
+\noindent Now let us split into $a>d$ and $a<d$, and consider $a>d$ first.  Notice that, by
+Lemma \ref{lemma:action implications}, the case $a=d$ is irrelevant in order to discriminate
+between $R$ and $M$. If $a>d$, by Lemma \ref{lemma:action implications} we can eliminate the
+cases where $R$ plays $II$ and $M$ plays $I$:
+\begin{align*}
+  & \textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) + P(I_{RC}\cap II_{RC})) + b_{C} \cdot
+  (P(I_{RC}\cap II_{RC}) + P(I_{RC}\cap I_{RC})) \\ 
+  & \ \ \ \ + c_{C} \cdot (P(II_{RC}\cap I_{RC})
+  +P(II_{RC}\cap II_{RC})) + d_{C} \cdot (P(II_{RC}\cap II_{RC})+P(II_{RC}\cap I_{RC}))] \\
+  > & 
+  \textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot P(I_{RC}\cap I_{MC}) + b_{C} \cdot P(I_{RC}\cap I_{MC}) +
+  c_{C} \cdot (P(I_{RC}\cap II_{MC})+P(II_{RC}\cap II_{MC})) \\ 
+  & \ \ \ \ + d_{C} \cdot (P(II_{RC}\cap
+  II_{MC})+P(I_{RC}\cap II_{MC}))]
+\end{align*}
+Rewrite:
+\begin{align*}
+  & \textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) + P(I_{RC}\cap II_{RC})-
+  P(I_{RC}\cap I_{MC})) \\ 
+  & \ \ \ \ + b_{C} \cdot (P(I_{RC}\cap II_{RC}) + P(I_{RC}\cap I_{RC})-
+  P(I_{RC}\cap I_{MC})) \\ 
+  & \ \ \ \ + c_{C} \cdot (P(II_{RC}\cap I_{RC}) +P(II_{RC}\cap II_{RC})-
+  P(I_{RC}\cap II_{MC})- P(II_{RC}\cap II_{MC})) \\ 
+  & \ \ \ \ + d_{C} \cdot (P(II_{RC}\cap
+  II_{RC})+P(II_{RC}\cap I_{RC})- P(II_{RC}\cap II_{MC})- P(I_{RC}\cap II_{MC}))]> 0
+\end{align*}
 
@@
 
-\noindent This means that, when (1) is the case, $(R,R)$ is not a strict Nash equilibrium. To prove that $(R,R)$ is strict we then have to show that the inequality is strict when case (2) obtains. \\
-When (2) is the case, it is easy to check, by Lemma \ref{lemma:action implications}, that $P(I_{RC} \cap I_{RC})-P(I_{RC}\cap I_{MC})=P(I_{RC}\cap II_{MC})$
-and $P(II_{RC}\cap II_{MC})=P(II_{RC} \cap II_{RC})$.
-Consequently, we have:
+\noindent This means that, on the class of $\mathcal{C} \cup \mathcal{A}$-games where $a>c$ and
+where (1) is the case, $R$ and $M$ are equally fit. This changes when we turn to (2). In that
+case, it is easy to check, by Lemma \ref{lemma:action implications}, that
+$P(I_{RC} \cap I_{RC})-P(I_{RC}\cap I_{MC})=P(I_{RC}\cap II_{MC})$ and
+$P(II_{RC}\cap II_{MC})=P(II_{RC} \cap II_{RC})$.\todo{please explain a bit}\ Consequently, we
+have:
 
@@
 \end{itemize}
+
+\noindent We know that $I_{RC}$ implies that $a_{C}-c_{C}\geq d_{C}-b_{C}$.
+% and $II_{MC}$ implies that $b_{C}\leq c_{C}$.
+Since we have assumed that $a_{C}-c_{C}\neq d_{C}-b_{C}$, we have that
+$a_{C}-c_{C} > d_{C}-b_{C}$. Hence, the inequality
+$$\sum_{C_{a>d}} P(C)[P(I_{RC}\cap II_{MC})\cdot (a_{C} + b_{C} - c_{C} - d_{C})]> 0$$
+is satisfied. So, in the class of $\mathcal{C} \cup \mathcal{A}$-games where $a >c$, $R$
+strictly dominates $C$. Symmetrically, from $a<d$ and by distinguishing between the two cases
+(1) and (2) as before, in the end we get:
+\begin{itemize}
+\item $\sum_{C_{a<d}} P(C)[-\frac{1}{2}a_{C}- \frac{1}{2}b_{C} + \frac{1}{2}c_{C} + \frac{1}{2}d_{C}]= 0$; and
+\item $\sum_{C_{a<d}} P(C)[P(II_{RC}\cap I_{MC})\cdot (-a_{C} - b_{C} + c_{C} + d_{C})]> 0$.
+\end{itemize}
+\noindent Hence, we can conclude that $R$ strictly dominates $M$ on the class
+$\mathcal{C}\cup\mathcal{A}$. Notice that in case of i.i.d. sampling with infinite support,
+games in $\mathcal{B} $ and $\mathcal{W} $ never arise, but the proof is the same for the
+remaining games in $\mathcal{S}$, $\mathcal{C} $ and $\mathcal{A}$.
+
 \medskip{}
 
-\noindent We know that $I_{RC}$ implies that $a_{C}-c_{C}\geq d_{C}-b_{C}$.
-%and $II_{MC}$ implies that $b_{C}\leq c_{C}$. 
-Since we have assumed that $a_{C}-c_{C}\neq d_{C}-b_{C}$, we have that $a_{C}-c_{C} > d_{C}-b_{C}$. Hence, the inequality 
-$$\sum_{C_{a>d}} P(C)[P(I_{RC}\cap II_{MC})\cdot (a_{C} + b_{C} - c_{C} - d_{C})]> 0$$
-is satisfied. So, when (2) obtains, $(R,R)$ is a strict Nash equilibrium.
-%From $b_{C}-d_{C}\geq c_{C}-a_{C}$, it is easy to see that $\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{RC}\cap II_{MC})\cdot[a_{C}-c_{C}]\geq\sum_{G_{a>d}^{C}}P(G_{a>d}^{C})\cdot P(I_{RC}\cap II_{MC})\cdot[d_{C}-b_{C}]$ holds.
-When the event $I_{RC}\cap II_{MC}$ obtains on the assumption that $a_{C}>d_{C}$, there are only three possible payoff orderings: $a>c\geq d>b$, $a>d>c>b$, and $a>d>c=b$.
-If games are randomly sampled from a finite set with i.i.d.
-values for $a,b,c$ and $d$, then $a>d>c=b$ occurs with positive probability, and the last formula of the derivation holds with strict inequality too.
-Hence, RM is evolutionarily stable when the value set for $a,b,c,d$ is finite.
-\\
-%If i.i.d.
-values are sampled from a compact and convex set instead, it is again easy to see that $\forall a,d,c\ \exists\epsilon$ such that $\forall b\in(d,d+\epsilon)$ the above formula holds with strict inequality.
-We can simply take $\epsilon\equiv\frac{a-c}{2}$, and the interval $(d,d+\epsilon)$ always has positive probability.
-Hence, RM is evolutionarily stable when the value set for $a,b,c,d$ is a compact and convex set too.
-\\
-Symmetrically, from $a<d$ and by distinguishing between the two cases (1) and (2) as before, in the end  we get:
-
-\begin{itemize}
-
-\item[(1)] $\sum_{C_{a<d}} P(C)[-\frac{1}{2}a_{C}- \frac{1}{2}b_{C} + \frac{1}{2}c_{C} + \frac{1}{2}d_{C}]= 0$; and
-
-\item[(2)] $\sum_{C_{a<d}} P(C)[P(II_{RC}\cap I_{MC})\cdot (-a_{C} - b_{C} + c_{C} + d_{C})]> 0$.
-
-\end{itemize}
-
-\noindent Hence, we can conclude that $(R,R)$ is a strict Nash equilibrium in the class $\mathcal{C}\cup\mathcal{A}$. \\
-In case of i.i.d.
-sampling with infinite support instead, games in $\mathcal{B} $ and $\mathcal{W} $ never arise, and the proof is the same for the remaining games in $\mathcal{S}$,  $\mathcal{C} $ and $\mathcal{A} $.
-
-\medskip{}
-
-The second half of the result is that $(M,M)$ is not a (strict) Nash equilibrium in $\mathcal{C}\cup\mathcal{A}$: $EF_{\mathcal{C}\cup\mathcal{A}}(M,M)<EF_{\mathcal{C}\cup\mathcal{A}}(R,M)$.
-As before, we write it more explicitly as:
-
-\medskip{}
+It remains to be shown that
+$F_{\mathcal{C}\cup\mathcal{A}}(M,M)<F_{\mathcal{C}\cup\mathcal{A}}(R,M)$. As before, spell
+this out as:
 
@@
 
-\noindent We now distinguish between (1) $b=c$, (2) $b>c$, and (3) $b<c$.
-Notice that either (1) or (2), together with $a>d$, implies $I_{RC}$.
-Then we obtain\footnote{Note that here, when we only have 3 elements in the support, case (2) is impossible.
-However, we can insure that cases (1) and (3) will eventually obtain.
-Again, this will be enough for the theorem to hold.}:
+\noindent We now distinguish between (1) $b=c$, (2) $b>c$, and (3) $b<c$. Notice that either
+(1) or (2), together with $a>d$, implies $I_{RC}$. Then we obtain\footnote{Note that here, when
+  we only have 3 elements in the support, case (2) is impossible, but cases (1) and (3) can
+  occur with positive probability, and this enough for our purpose.}:
 \begin{itemize}
@@
 
-\noindent Finally, we can conclude that $(M,M)$ is
-not a (strict) Nash equilibrium, and therefore $(R,R)$ is the unique strict Nash equilibrium. \\
-As before, when we have i.i.d.
-sampling with infinite support, games in $\mathcal{W}$ and $\mathcal{B}$ never occur, and the proof is the same for all the other cases.
-Hence, both when the support of $a,b,c,d$
-is finite, and when the support is infinite, $(R,R)$ is the only (strict) Nash equilibrium. This concludes the proof. $\dashv$
-
-\vspace{1cm}
-
-\noindent \textbf{Proof of Corollary \ref{corollary1}.} Let us recall the definition of evolutionarily stable strategy and neutrally stable strategy.
-
-\medskip{}
-
-\begin{definition}[ESS-NSS] \label{def:ESS-NSS}
-A strategy $s^{\$}$ is \emph{evolutionarily stable
-(ESS)} if for any other strategy $s$:
-\begin{enumerate}
-\item $\pi(s^{\$},s^{\$})>\pi(s,s^{\$})$, or
-\item $\pi(s^{\$},s^{\$})=\pi(s,s^{\$})$ and $\pi(s^{\$},s)>\pi(s,s)$.
-\end{enumerate}
-\noindent A strategy $s^{\$}$ is \emph{neutrally stable (NSS)} if
-for any other strategy $s$:
-\begin{enumerate}
-\item $\pi(s^{\$},s^{\$})>\pi(s,s^{\$})$, or
-\item $\pi(s^{\$},s^{\$})=\pi(s,s^{\$})$ and $\pi(s^{\$},s)\geq\pi(s,s)$.
-\end{enumerate}
-\end{definition}
-
-\medskip{}
-
-\noindent Then we extend Definition \ref{def:ESS-NSS} to include choice mechanisms.
-
-\begin{definition}[ESM-NSM] \label{def:ESM-NSM}
-Given a class of games $\mathcal{G}$, a choice mechanism $(\gamma, \kappa)$ is \emph{evolutionarily stable
-(ESM)} if for any other choice mechanism $(\gamma', \kappa')$:
-\begin{enumerate}
-\item $EF_{\mathcal{G}}((\gamma, \kappa),(\gamma, \kappa))>EF_{\mathcal{G}}((\gamma', \kappa'),(\gamma, \kappa))$, or
-\item $EF_{\mathcal{G}}((\gamma, \kappa),(\gamma, \kappa))=EF_{\mathcal{G}}((\gamma', \kappa'),(\gamma, \kappa))$ and $EF_{\mathcal{G}}((\gamma, \kappa),(\gamma', \kappa'))>EF_{\mathcal{G}}((\gamma', \kappa'),(\gamma', \kappa'))$.
-\end{enumerate}
-\noindent A choice mechanism $(\gamma, \kappa)$ is \emph{neutrally stable (NSM)} if
-for any other choice mechanism $(\gamma', \kappa')$:
-\begin{enumerate}
-\item $EF_{\mathcal{G}}((\gamma, \kappa),(\gamma, \kappa))>EF_{\mathcal{G}}((\gamma', \kappa'),(\gamma, \kappa))$, or
-\item $EF_{\mathcal{G}}((\gamma, \kappa),(\gamma, \kappa))= EF_{\mathcal{G}}((\gamma', \kappa'),(\gamma, \kappa))$ and $EF_{\mathcal{G}}((\gamma, \kappa),(\gamma', \kappa'))\geq EF_{\mathcal{G}}((\gamma', \kappa'),(\gamma', \kappa'))$.
-\end{enumerate}
-\end{definition}
-
-\noindent From Proposition \ref{proposition1} we know that:
-
-\begin{itemize}
-\item[(i)] $EF_{\mathcal{G}}(R,R)>EF_{\mathcal{G}}(M,R);$
-\item[(ii)] $EF_{\mathcal{G}}(M,M)<EF_{\mathcal{G}}(R,M).$
-\end{itemize}
-
-\noindent Then, from Definition \ref{def:ESM-NSM} it immediately follows that the unique evolutionarily stable state is a monomorphic population of $R$-players. $\dashv$
+\noindent Finally, we can conclude that
+$F_{\mathcal{C}\cup\mathcal{A}}(M,M)<F_{\mathcal{C}\cup\mathcal{A}}(R,M)$. As before, notice
+that, when we have i.i.d. sampling with infinite support, games in $\mathcal{W}$ and
+$\mathcal{B}$ never occur, but the proof is the same for all the other cases. Hence, both when
+the support of $a,b,c,d$ is finite, and when the support is infinite, $R$ strictly dominates
+$M$ under the conditions assumed. \hfill $\dashv$
 

### 2016-01-25 paper/paper.tex
Paolo almost final

@@
     mechanisms} in a rich and variable environment. A choice mechanism is a way of representing
-  a decision situation, paired with a method for choosing an act based on this (possibly false)
+  a decision situation, paired with a method for choosing an act based on this 
   subjective representation. We demonstrate the usefulness of this approach by a case study
@@
 
-Evolutionary game theory has become an established philosophical tool for probing into
-conceptual issues whose complexity requires mathematical modelling at a high level of
-abstraction.  Abstraction entails simplifying assumptions. Evolutionary game models frequently
+%Evolutionary game theory has become an established philosophical tool for probing into
+%conceptual issues whose complexity requires mathematical modelling at a high level of
+%abstraction.  Abstraction entails simplifying assumptions.
+
+If agents deal with a rich and variable environment, they have to face many different choice
+situations.
+Standard evolutionary game models frequently
 simplify reality in two ways that are relevant for present purposes. Firstly, the environment
-is represented as a fixed, closed and immutable \emph{stage game}; secondly, the focus of
-evolutionary selection is behavior for this stage game alone. In contrast, some argue for
-studying instead the evolutionary competition of general \emph{choice mechanisms} in a rich and
+is represented as a fixed \emph{stage game}; secondly, the focus of
+evolutionary selection is behavior for that stage game alone. In contrast, some argue for
+studying the evolutionary competition of general \emph{choice mechanisms} in a rich and
 variable environment
@@
 
-If agents deal with a rich and variable environment, they face many different choice
-situations. A choice mechanism associates decision situations with action choices. A crucial
-part of any choice mechanism is a \emph{subjective representation} of the decision situation,
-in particular a manner of forming preferences and beliefs about a possibly uncertain world (see
+In full generality, a choice mechanism associates decision situations with action choices. A crucial
+part of a choice mechanism is the \emph{subjective representation} of the decision situation,
+in particular the manner of forming preferences and beliefs about a possibly uncertain world (see
 Figure~\ref{fig:ChoiceMechanism} below). This paper asks: which preference and belief
-representations are ecologically valuable (i.e., lead to high fitness)? The evolution of
+representations are ecologically valuable and lead to high fitness?
+The evolution of
 preferences has been subject of recent interest in theoretical economics
-\citep[e.g.,][]{algweib13,DekElyYlan07,RobSam11}. The particular contribution of this paper is
-to provide a case, spelled out formally, that questions of preference evolution should take
-variability in belief representation into account as well. As a point in case, we demonstrate
+\citep[e.g.,][]{algweib13,DekElyYlan07,RobSam11}. A contribution of this paper is
+to provide a case that questions of preference evolution should take
+variability in uncertainty representation into account as well. As a point in case, we demonstrate
 that if agents have imprecise probabilistic beliefs \citep[e.g.][]{gardsah82,levi74,walley96},
@@
 Section \ref{sec:rati--subj} reviews different views of rational choice and relates the
-approach we take here to the existing literature. Section \ref{sec:basic-notions} introduces
-relevant decision- and game-theoretic notions and spells out four choice mechanisms on whose
-evolutionary competition we will zoom in Section~\ref{sec:basic-model-1}, which presents the
+approach we take here to the existing literature. Section \ref{sec:basic-notions} introduces the
+relevant decision- and game-theoretic notions, and
+%spells out four choice mechanisms on whose
+%evolutionary competition we zoom in 
+Section~\ref{sec:basic-model-1} presents the
 main results of the paper. Section \ref{sec:extensions} extends the evolutionary analysis by
@@
 
-\section{Rationality, subjective representation schemes \& meta games}
+\section{Rationality, representations \& meta-games}
 \label{sec:rati--subj}
@@
 The standard textbook definition of \textit{rationality} in economics and decision theory
-traces back to the seminal work of \citet{deFinetti37}, \citet{Neumannvon-NeumannMorgenstern1944:Theory-of-Games}
-and \citet{Savage1954:The-Foundations}. It says that choice is rational only if it maximizes
+traces back to the seminal work by \citet{deFinetti37}, \citet{Neumannvon-NeumannMorgenstern1944:Theory-of-Games}
+and \citet{Savage1954:The-Foundations}. It says that a choice is rational only if it maximizes
 (subjective) expected utility.
@@
   \label{def:rationality}
-  Let $S$ be a (finite) set of states of the world and $A$ a (finite) set of actions. Given a
-  probability distribution $\mu$ over $S$ and a payoff function
-  $\pi \mycolon S \times A \rightarrow \mathbb{R} $, an action $a^* \in A$ is a rational choice
+  Let $S$ be a (finite) set of states and $A$ a (finite) set of actions. Given a
+  probability measure $\mu$ over $S$ and a payoff function
+  $u \mycolon S \times A \rightarrow \mathbb{R} $, an action $a^* \in A$ is rational
   if it maximizes the \emph{(subjective) expected utility}
-  $\EU(a) = \sum_{s \in S} \mu(s) \ \pi(s, a)$.
+  $\EU(a, \mu) := \sum_{s \in S} \mu(s) \ u(s, a)$.
 \end{definition}
@@
 \noindent Expected utility is subjective in the sense that it is a function of subjective
-preferences and subjective beliefs of the decision maker (DM). To wit, a choice can be
+beliefs $\mu$ and subjective preferences $u$ of the decision maker (DM). To wit, a choice can be
 rational, i.e., the best choice from the DM's point of view, even if based on peculiar beliefs
@@
 parameters in the presented choice task. Similarly for social decision making, including social
-preferences such as fairness, reciprocity or similar, allows us to describe as rational
-empirically observed behavior, such as in experimental prisoners' dilemmas or public goods
+preferences such as fairness, altruism or similar, allows us to describe as rational
+empirically observed behavior, such as in experimental Prisoner's Dilemmas or public goods
 games, that might otherwise appear irrational \citep[e.g.,][]{fehrschmidt99,charrab02}.
@@
 therefore emphasizes that there are many ways in which ascriptions of beliefs and preferences
-are constrained by normative considerations of rationality as well. As for beliefs, where
-possible, subjective beliefs should reflect objective chance. Where this is impossible,
-temporal consistency of choices constrains rational subjective beliefs, else exploitation by
-Dutch books is possible. As for preferences, in certain situations it may make sense to
+should be constrained by normative considerations of rationality as well. As for beliefs, where
+possible, subjective beliefs should reflect objective chance. 
+%Where this is impossible,
+%temporal consistency of choices constrains rational subjective beliefs, else exploitation by
+%Dutch books is possible. 
+As for preferences, in certain situations it may make sense to
 postulate on normative grounds that subjective preferences should be oriented towards tracking
-objective fitness. For instance, profit maximization seems a reasonable assumption for
-characterizing outcomes in a competitive market because only firms behaving in a manner that is
-consistent with profit maximization will survive in the long run \myalert{(Alchian,
-  Friedman)}.\todo{@Paolo: please add references}
+objective fitness. For instance, profit maximization seems a necessary requirement for
+evolution in a competitive market because only firms behaving according to profit maximization will survive in the long run \citep[e.g.,][]{alch50,Fried53}.
 
@@
 \citep[e.g.,][]{Anderson1991:Is-human-cognit,ChaterOaksford2000:The-Rational-An,HagenChater2012:Decision-Making}. \todo{more
-  references} Adaptationism aims to explain choice behavior by appeal to evolutionary
-considerations: DMs have acquired choice mechanisms that have proved to be adpative in a rich
-and variable environment. A choice mechanism could be a set of distinct heuristics (the DM's
+  references} Adaptationism aims to explain rational behavior by appeal to evolutionary
+considerations: DMs have acquired choice mechanisms that have proved to be adpative with respect to the variable environment where they have evolved.
+A choice mechanism can be a set of distinct heuristics (the DM's
 \emph{adaptive toolbox}) that have little in common
 \citep[e.g.,][]{TverskyKahnemann1981:The-Framing-of-,GigerenzerGoldstein1996:Reasoning-the-F,ScheibehenneRieskamp2013:Testing-the-Ada}. But
-to relate to the philosophical debate about the nature of rational choice, we here suggest to
-think of a choice mechanism as a map from choice situations to action choices that contains an
-explicit level of subjective representation of a decision situation (see
-Figure~\ref{fig:ChoiceMechanism}). We are most interested in the question which
-\emph{subjective representation schemes}, i.e., general ways of forming preferences and
-beliefs, are better than others from an evolutionary point of view.
+to closely relate to the literature on evolution of preferences and to the philosophical debate about the nature of rational choice in general, we here suggest to
+think of a choice mechanism as a map from choice situations to action choices which includes an
+explicit level of subjective representation of the situation, that we call \emph{subjective representation scheme} (see
+Figure~\ref{fig:ChoiceMechanism}). Specifically, a subjective representation scheme is a general way of forming preferences and
+beliefs about the choice situation, and we are most interested in the question which
+subjective representations are better than others from an evolutionary point of view.
 
@@
     centered, below of = environment, node distance = 2cm] (situation)
-    {environment produces random \\ \textbf{decision situation} $d$};
+    {environment produces random \\ \textbf{decision situation} $D$};
 
@@
     centered, below of = situation] (representation) 
-    {\textbf{subjective representation} $s$ of $d$ \\ \textcolor{gray}{[preference, beliefs, \dots]}};
+    {\textbf{subjective representation} of $D$ \\ \textcolor{gray}{[preference, beliefs, \dots]}};
 
@@
     centered, below of = representation] (action)
-    {\textbf{action choice} $a$ based on $s$};
+    {\textbf{action choice} $a$};
 
     \node[rounded corners, draw, rectangle, minimum height = 0.75cm, text width=6cm, text
-    centered, below of = action,node distance = 1.5cm] (payoff) {\textbf{payoff} for $a$ in $d$};
+    centered, below of = action,node distance = 1.5cm] (payoff) {\textbf{payoff} for $a$ in $D$};
 
@@
   \caption{Schematic representation of action choice. A choice mechanism maps decision
-    situation $d$ to action choice $a$ by way of representing $d$ in terms of subjective
-    preferences and subjective beliefs.}
+    situation $D$ to action choice $a$ by means of a representation of $D$ in terms of a subjective
+    preference and a subjective belief.}
   \label{fig:ChoiceMechanism}
@@
 choice mechanism that contains it, all else equal. The fitness of a choice mechanism $c$ is the
-expected payoff of $c$ over arbitrary decision situations $d$:
+expected payoff of $c$ over arbitrary decision situations $D$:
 \begin{align}
   \label{eq:FittnessChoiceMechSolitary}
-  F(c) = \int P(d) \  \pi_d(c) \text{ d} d \,,
+  F(c) = \int P(D) \  \pi_D(c) \text{ d} D \,,
 \end{align}
-where $P(d)$ is the probability (density) of $d$ occurring and $\pi_d(c)$ is the payoff of
-the act selected by $c$ in $d$. Probability measure $P(d)$ is our model of the statistical
-properties of a rich and variable environment.
-
-The same logic also applies to situations of social decision making. A game $g$ is also a
-decision situation, albeit a more complex one. A choice mechanism $c$ maps $g$ onto an action
-choice in $g$. The fitness of $c$ is then:\footnote{We assume for simplicity of exposition that
-  all games with positive occurrence probability are two player games.}
+where $P(D)$ is the probability (density) of $D$ occurring and $\pi_D(c)$ is the evolutionary payoff of
+the act selected by $c$ in $D$. The probability measure $P(D)$ encodes the statistical
+properties of the environment.
+
+The same logic also applies to game contexts and social decision making. A game $G$ is also a
+choice situation, albeit a more complex one. A choice mechanism $c$ maps $G$ onto an action
+choice in $G$. The fitness of $c$ is then:\footnote{We assume for simplicity of exposition that
+  all games with positive occurrence probability are symmetric two-player games.}
 \begin{align}
   \label{eq:FittnessChoiceMechGame}
-  F(c) = \int \int P(g) \  P(c') \  \pi_g(c,c') \text{ d} g \,,
+  F(c) = \int \int P(G) \  P(c') \  \pi_G(c,c') \text{ d} c' \text{ d} G  \,,
 \end{align}
-where $P(g)$ is the probability (density) of game $g$, $P(c')$ is the probability of
-encountering a co-player who uses choice mechanism $c'$ and $\pi_g(c,c')$ is the payoff for
-a $c$-player in $g$ against the $c'$-player, given by the payoff in $g$ of the actions that $c$
-and $c'$ select in $g$. For the most part, we will focus on the more complex case of social
-decision making here. Results about solitary decision making follow from parallel arguments
+where $P(G)$ is the probability (density) of game $G$, $P(c')$ is the probability of
+encountering a co-player who uses choice mechanism $c'$ and $\pi_G(c,c')$ is the evolutionary payoff for
+a $c$-player in $G$ against the $c'$-player, given by the actions that $c$
+and $c'$ select in $G$. For the most part, we will focus on the more complex case of game situations. Results about solitary decision making follow from parallel arguments
 (see Section~\ref{sec:extensions}).
 
-\emph{Meta games} are abstract models for the evolutionary competition between choice
-mechanisms in social decision making contexts. The expected payoff for a $c$-player in a random
-encounter with a $c'$-player is the average of payoffs obtained in a random game $g$ weighted
-by $g$'s occurrence probability:
+\emph{Meta-games} are abstract models for the evolutionary competition between choice
+mechanisms in interactive decision making contexts. The expected payoff for a $c$-player in a random
+encounter with a $c'$-player is the average of payoffs obtained in a random symmetric game $G$ weighted
+by $G$'s occurrence probability:
 \begin{align}
   \label{eq:FittnessChoiceMechGamePairwise}
-  F(c, c') = \int P(g) \  \pi_g(c,c') \text{ d} g \,.
+  F(c, c') = \int P(G) \  \pi_G(c,c') \text{ d} G \,.
 \end{align}
 
-\begin{definition}[Meta game]
+\begin{definition}[Meta-game]
   \label{def:MetaGame}
-  Let $C$ be a set of choice mechanisms and let $P(g)$ give the occurrence probability of game
-  $g$ in the environment. The meta game that captures selection of choice mechanisms in this
-  environment is the one-population evolutionary game with strategies $C$ and payoff function
-  $\pi \mycolon C \times C \rightarrow \mathbb{R}$ such that
-  $\pi(c,c') = F(c,c') = \int P(g) \  \pi_g(c,c') \text{ d} g$.
+  Let $CM$ be a set of choice mechanisms and let $P(G)$ give the occurrence probability of symmetric game
+  $G$ in the environment. The meta-game that captures selection of choice mechanisms in this
+  environment is the one-population evolutionary game with strategies $CM$ and payoff function
+  $\pi \mycolon CM \times CM \rightarrow \mathbb{R}$ such that
+  $\pi(c,c') = F(c,c')$.
+  % = \int P(G) \  \pi_G(c,c') \text{ d} G$.
 \end{definition}
 
-Standard notions of evolutionary game theory can be applied to meta games as well. A choice
-principle $c$ is a strict Nash equilibrium if $F(c,c) > F(c',c)$ for all $c'$; it is
+Standard notions of evolutionary game theory can be applied to meta-games as well. A choice
+mechanism $c$ is a strict Nash equilibrium if $F(c,c) > F(c',c)$ for all $c'$; it is
 evolutionarily stable if for all $c'$ either (i) $F(c,c) > F(c',c)$ or (ii) $F(c,c) = F(c',c)$
-and $F(c,c') > F(c',c')$. It is neutrally stable if for all $c'$ either (i) $F(c,c) > F(c',c)$
+and $F(c,c') > F(c',c')$; it is neutrally stable if for all $c'$ either (i) $F(c,c) > F(c',c)$
 or (ii) $F(c,c) = F(c',c)$ and $F(c,c') \ge F(c',c')$
 \citep{Maynard-Smith1982:Evolution-and-t}. Similarly, evolutionary dynamics can be applied to
-meta games. We will later turn towards the replicator dynamic
-\citep{TaylorJonker1978:Evolutionary-St} and the replicator mutator dynamic
-\citep[e.g.][]{Nowak2006:Evolutionary-Dy}.\todo{footnote with caveat about agent-level
-  processes}
+meta-games. We will later turn towards replicator dynamics
+\citep{TaylorJonker1978:Evolutionary-St} and replicator mutator dynamics
+\citep[e.g.][]{Nowak2006:Evolutionary-Dy}.
+%\todo{footnote with caveat about agent-level processes}
 
@@
 
-We submit that meta games are a useful tool for structuring and sharpening conceptual inquiry
+We submit that meta-games are a useful tool for structuring and sharpening conceptual inquiry
 in a domain that is notorious for its fuzziness and elusiveness. To show how this approach can
-be applied to the benefit of conceptual debate, we consider the evolution of preference
-\citep[e.g.,][]{algweib13,DekElyYlan07,RobSam11}. Concretely, we here pit two different ways of
-representing preferences against each other: (i) veridical representations that correctly
-reflect objective fitness, and (ii) non-veridical subjective preferences in terms of regret
-\citep[e.g.,][]{Savage1951:The-theory-of-s,}. We show that subjective, non-veridical preference
-representations based on a notion of regret can be adaptive and even outperform objective,
-veridical representations of the actual, true fitness, when agents, at least on occasion, hold
+be applied to the benefit of conceptual debate, we consider the evolution of preferences
+\citep[e.g.,][]{algweib13,DekElyYlan07,RobSam11}. 
+%Concretely, we here pit two different ways of
+%representing preferences against each other: (i) veridical representations that correctly
+%reflect objective fitness, and (ii) non-veridical subjective preferences in terms of regret
+%\citep[e.g.,][]{Savage1951:The-theory-of-s,}. 
+We show that subjective, non-veridical preference
+representations based on a notion of regret can be adaptive and even outperform objective representations of the true evolutionary fitness, when agents, at least on occasion, hold
 \emph{imprecise probabilistic beliefs} \citep[e.g.,][]{gilsch89,levi74,gardsah82} and make
-decisions based on a security choice rule (here: the maxmin rule applied to expected
-utility). This case study strips the generality of a meta game approach down to a perspicuous
-comparison between only four choice mechanisms, summarized in Table~\ref{tab:CMs}: the
-cross-product of two different preference representations (veridical vs.~regret) and two
-different belief representations (precise vs.~imprecise).
-
+decisions based on a security choice rule (here: the maxmin rule).\footnote{Decision-theoretic background and justifications for the use of maxmin and imprecise probabilities is given in Appendix~\ref{sec:impr-prob-beli}.}
+
+The case study under consideration strips the generality of a meta-game approach down to a perspicuous
+comparison between four choice mechanisms, summarized in Table~\ref{tab:CMs}.
+% the cross-product of two different preference representations (veridical vs.~regret) and two
+%different belief representations (precise vs.~imprecise). 
 \begin{table}[t]
@@
   \begin{tabular}{cccc}
-    \multicolumn{2}{c}{subjective representation} & action selection & corresponding choice
-    rule \\  \cmidrule(r){1-2}
+  \multicolumn{3}{c}{choice mechanism} \\  \cmidrule(r){1-3}
+    \multicolumn{2}{c}{subjective representation} & action selection & corresponding classic rule \\  \cmidrule(r){1-2}
     preference type & belief type  \\ \midrule
-    objective fitness & precise & maxmin EU &  Laplace \\
-    objective fitness & precise & maxmin EU & maxmin \\ 
-    regret & imprecise & maxmin EU & Laplace \\
+    objective fitness & precise & maxmin EU &  Laplace rule \\
+    objective fitness & imprecise & maxmin EU & maxmin \\ 
+    regret & precise & maxmin EU & Laplace rule \\
     regret & imprecise & maxmin EU & regret minimization \\ 
@@
   \caption{Overview relevant choice mechanisms and the corresponding (behaviorally equivalent)
-    classic choice rules. All notions are explained in the main text.}
+    classic choice rules.}
   \label{tab:CMs}
 \end{table}
-
+\iffalse
 This exclusive selection of choice mechanisms is motivated by a number of
 considerations. Firstly, the set of conceivable choice mechanisms is vast. Most of that
-conceivable vastness is utter nonsense. Some selection of plausible candidates is required in
-any case. Secondly, a severe restriction to only a small number of suitable candidates will
+conceivable vastness is utter nonsense, and some selection of plausible candidates is required in
+any case. Secondly, a restriction to only a small number of suitable candidates will
 help demonstrate more distinctly how a meta game approach may help structure philosophical
-inquiry. This is our main goal. Thirdly, our case study adds to the recent literature on the
-evolution of preferences by clearly demonstrating the possibly non-trivial interaction between
-preference and belief representations, all else equal. This is our secondary goal. Finally, the
-four choice mechanism that we look at here, although phrased in terms of preference and belief
-representations, map onto well-known classic proposals for rational choice (see
+inquiry, which is our main goal. Thirdly, our case study adds to the recent literature on the
+evolution of preferences by making evident the possibly non-trivial interaction between
+preference and belief representations, all else equal. This is our secondary goal. 
+Finally,
+\fi 
+The
+four choice mechanisms,  
+%that we look at here
+although phrased in terms of preference and belief
+representations, map onto well-known classic proposals for rational decision making (see
 Table~\ref{tab:CMs}). In other words, there is also an argument by historical relevance for our
@@
 
-\subsection{Classic rules for rational choice} 
+\subsection{Classic rules for decision making}
 \label{sec:choice-rules}
@@
 The classic literature on rational choice contains a number of proposals for which acts a
-player should choose if she is rational. Maximization of expected utilities, as
-given in Definition~\ref{def:rationality}, is only one of them. Here, we consider three others:
-(i) maxmin, (ii) Laplace's rule and (iii) regret minimization. All of these apply to games and
-solitary decision situations. We focus on games, but definitions carry over straightforwardly.
-
-A strategic game is a tuple $ G=\tuple{ N, (A_i , \pi_i)_{i \in N} }$ with $N$ a finite set of
-players, $A_i$ a finite set of acts and $\pi_i$ a payoff function for each player $i \in N$.
+player should choose if she is rational. Maximization of expected utility, as
+given in Definition~\ref{def:rationality}, is just one of them, possible only if DM holds a precise probabilistic belief.
+Here, we consider three others:
+(i) maxmin, (ii) Laplace rule, and (iii) regret minimization. 
+%All of these apply to games and
+%solitary decision situations.
+We focus on games first, but definitions carry over straightforwardly to solitary decisions.
+
+A strategic-form game is a tuple $ G=\tuple{ N, (A_i , \pi_i)_{i \in N} }$ with $N$ a finite set of
+players, $A_i$ a finite set of acts and $\pi_i: \bigtimes_{j \in N} A_j \rightarrow \mathbb{R}$ a payoff function for each player $i \in N$.
 Part of this paper will focus on symmetric games with two players. A two-player game is
@@
 Figure~\ref{coordgame1}. The numbers give the payoff for the player choosing a row act against
-an opponent choosing a column act. Since the game is symmetric, it suffices to give just these
+a co-player choosing a column act. Since the game is symmetric, it suffices to give just these
 numbers.
 
-Rational choice from maximization of expected utilities, as given in
+Rational choice from maximization of expected utility, as given in
 Definition~\ref{def:rationality}, applies to games as follows. To say which acts are rational,
-it requires specifying a belief of the DM. Let $A_{-i} = \bigtimes A_j$ for all $j \neq i$ be
+it requires specifying a precise probabilistic belief of DM. Let $A_{-i} := \bigtimes_{j \neq i} A_j$ be
 the set of all \emph{profiles} of acts for all players except $i$. If player $i$ has a belief
-$\mu_i \in \Delta(A_{-i})$ about the behavior of his opponents, he chooses rationally only if
+$\mu_i \in \Delta(A_{-i})$ about the behavior of his co-players, he chooses rationally only if
 his choice $a^*_i$ maximizes expected utility
-$\EU(a_i) := \sum_{\act_{-i} \in \Acts_{-i}} \mu_i(\act_{-i}) \myts \pi_i(a_i, a_{-i})$. For
-the example in Figure~\ref{coordgame1}, a rational player would choose act $I$ exactly when he
-believes that his opponent will choose act $I$ with a probability of at least
+$\EU(a_i, \mu) := \sum_{\act_{-i} \in \Acts_{-i}} \mu_i(\act_{-i}) \myts \pi_i(a_i, a_{-i})$. For
+the example in Figure~\ref{coordgame1}, an expected utility maximizer would choose act $I$ only if he
+believes that his co-player is going to choose act $I$ with a probability of at least
 $\nicefrac{2}{3}$.
 
-Perhaps the most well-known classic rule that does not require explicitly stating the DM's
-beliefs is the \emph{maxmin rule}. It tells our agent to choose act $\act^*$ only if it
+Perhaps the most well-known classic rule that does not require precise probabilistic
+beliefs is the \emph{maxmin rule}. It prescribes to choose act $\act^*$ only if it
 maximizes payoffs for all worst case scenarios:
-$\act^* \in \argmax_{\myact{i} \in \Acts_i} \min_{\myact{-i} \in \Acts_{-1}} \pi_i(\myact{i},
-\myact{-1})$.
-For the example in Figure~\ref{coordgame1}, the maximim rule looks at the minima in each row,
-asking: what is the worst possible outcome for each row act? It is $0$ in either
-case. Consequently, the maxmin rule would not favor either act: players choosing by the maxmin
+$\act^* \in \argmax_{a_i \in \Acts_i} \min_{a_{-i} \in \Acts_{-i}} \pi_i(a_{i},
+a_{-i})$.
+For the example in Figure~\ref{coordgame1}, the minimum of both acts is 0: players choosing by maxmin
 rule would be indifferent between acts $I$ and $II$.
 
-\emph{Laplace's rule} selects $\act^*$ if
-$\act^* \in \argmax_{\myact{-i} \in \Acts_{-i}} \sum_{\myact{-i}} \pi(\myact{i}, \myact{-i})$.
-Laplace's rule is equivalent to expected utility maximization under a \emph{flat belief} that
-assigns equal probability to all of the opponents' choices. In the coordination game of
-Figure~\ref{coordgame1}, Laplace's rule selects act $II$.
-
-The final classic rule that is relevant for our purposes here is \emph{regret
+\emph{Laplace rule} selects $\act^*$ if
+$\act^* \in \argmax_{a_{i} \in \Acts_{i}} \sum_{a_{-i}} \pi(a_{i}, a_{-i})$.
+Laplace rule is equivalent to expected utility maximization under a \emph{flat belief} that
+assigns equal probability to all of the co-players' choices. In the coordination game of
+Figure~\ref{coordgame1}, Laplace rule selects act $II$.
+
+The final classic rule that is relevant for our purposes is \emph{regret
   minimization}. The notion of regret in decision theory dates back at least to the work by
@@
 \citet{HalpernPass2012:Iterated-Regret} showed how the use of regret minimization can give
-solutions to game theoretical puzzles (like the Traveller's dilemma) in a way that is closer to
+solutions to game theoretical-puzzles (like the Traveller's dilemma and the Centipede game) in a way that is closer to
 everyday intuition and empirical data. In this paper the notion of regret is defined as in
@@
 
-\begin{definition}[Regret, Regret Minimization] \label{defn:regret} Given a strategic game
+\begin{definition}[Regret, Regret Minimization] \label{defn:regret} Given a game
   $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the \emph{pairwise regret} of player $i$'s
-  act $a_i$ against profile $a_{-1}$ is
-  $\text{reg}(a_i,a_{-i}):= \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $, where
+  act $a_i$ against profile $a_{-i}$ is
+  $\text{preg}(a_i,a_{-i}):= \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $, where
   $a_i^\$ \in \argmax_{a_i \in A_i} \pi_i(a_i, a_{-i})$ denotes $i$'s best reply to the
-  opponents' actions $a_{-i}$. The \emph{regret} of $a_i$ is then
-  $\text{reg}(a_i):= \text{max}_{a_{-i}\in A_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $. An
+  co-players' actions $a_{-i}$. The \emph{regret} of $a_i$ is then
+  $\text{reg}(a_i):= \text{max}_{a_{-i}\in A_{-i}} \text{preg}(a_i,a_{-i}) $. An
   action $a^{*}_i $ is regret minimizing if
-  $a^{*}_i \in \text{min}_{a_i} \text{max}_{a_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $.
+  $a^{*}_i \in \text{argmin}_{a_i} \text{max}_{a_{-i}} \text{preg}(a_i,a_{-i})$.
 \end{definition}
 
-To illustrate, Figure~\ref{coordgame1reg} shows the pairwise regrets and the regrets of each
-row-player action for the coordination game in Figure \ref{coordgame1}. We have
-$\text{reg}(I)=2$, because when the other player chooses act $I$ the pairwise regret
-$\text{reg}(I,I)$ is $0$ since $I$ is a best reply to act $I$, and when the other player
-chooses act $II$ the pairwise regret $\text{reg}(I, II)$ is $2$ since
-$\pi_i(II,II)-\pi_i(I,II)=2$. With the same reasoning, $\text{reg}(II)=1$. A regret minimizing
-player would therefore choose act $II$.
+\noindent To illustrate, Figure~\ref{coordgame1reg} shows the pairwise regrets and the regrets for the game of Figure~\ref{coordgame1}. 
+We have
+$\text{reg}(I)=2$, because $\text{preg}(I,II)=2$, whereas $ \text{preg}(I,I)=0 $. With the same reasoning, $\text{reg}(II)=1$. A regret minimizer would therefore choose act $II$.
 
@@
     \centering
-    \begin{tabular}{cccc}
+    \begin{tabular}{ccc|c}
       \toprule
-      & $\text{reg}( \cdot, I)$ & $\text{reg}(\cdot, II)$ & $\text{reg}(\cdot)$ \\
+      & $\text{preg}( \cdot, I)$ & $\text{preg}(\cdot, II)$ & $\text{reg}(\cdot)$ \\
       \midrule
@@
 Regret minimization is intimately related to the maxmin rule. Let the \emph{negative regret
-  transformation} of a strategic game $G$ be the game $G'$ derived from $G$ by replacing the payoff
-function $\pi$ of $G$ with $\pi'$ such that $\pi'_i(a_i, a_{-i}) = - reg(a_i,a_{-1})$, i.e.,
-the payoff of all players is the pairwise negative regret (under the payoffs from $G$). For
+  transformation} of a strategic game $G$ be the game $G^r$ derived from $G$ by replacing the payoff
+functions $\pi_i$ of $G$ with the negative pairwise regrets $-\text{preg}(a_i,a_{-i})$. For
 example, the negative regret transformation of the game in Figure~\ref{coordgame1} would have the
@@
 
-\noindent Acts selected by the maxmin rule for the negative regret transformation of $G$ are
+\noindent Then, for any game $G$, acts selected by maxmin rule for the negative regret transformation of $G$ are
 always exactly the acts selected by regret minimization for the original game $G$.
-
 This means that we can think of the maxmin rule and regret minimization as essentially the same
-operation on different subjective representations of preference: while maxmin considers actual
+action selection function on different subjective representations of preferences: while maxmin considers actual
 objective payoffs, regret minimization considers non-veridical, regret-based subjective
-preferences. As the example of Figure~\ref{coordgame1} shows, different subjective preferences
-can give rise to different choice prescriptions all else equal. While maxmin is indifferent
+utilities. As the example of Figure~\ref{coordgame1} shows, different subjective preferences
+can give rise to different choices, all else equal. While maxmin is indifferent
 between $I$ and $II$, regret minimization uniquely selects $II$.
 
-In sum, classic proposals for rational choice are normative prescription of action choices
-for a rational agent. Such prescriptions may rest on implicit assumptions about what the DM
-believes (e.g., when interpreting Laplace's rule as rational choice under flat beliefs). They may
-also make implicit assumptions about what the DM prefers (e.g., when reconstructing regret
-minimization in terms of maxmin-choices on the regret transformation). This is rather messy. To
-disentangle and avoid confusion, we turn to choice mechanisms.
+In sum, classic proposals for rational decision making are normative prescriptions of action choices
+for DM. Such prescriptions may rest on implicit assumptions about what DM
+believes (e.g., when interpreting Laplace rule as expected utility maximization under flat beliefs). They may
+also make implicit assumptions about what DM prefers (e.g., when considering regret-based preferences). This is rather messy. To disentangle, we rephrase all the above in terms of choice mechanisms.
 
@@
 
-A \emph{choice mechanism} is a map from choice situations to action choices that, unlike the
-classic choice rules visited above, contains an explicit level of subjective representation of
-a decision situation. Let us think of a choice mechanism as a pair of functions
+A \emph{choice mechanism} is a map from choice situations to action choices that contains an explicit level, in terms of preferences and beliefs, of subjective representation of
+the choice situation. Concretely, let us think of a choice mechanism as a pair of functions
 ($\gamma,\kappa$), where $\gamma$ is a \emph{subjective representation scheme} and $\kappa$ is
@@
 
-The subjective representation scheme $\gamma_i$ of agent $i$ is a function $\gamma_i$ that
-takes a strategic game $G = \tuple{ N, (A_i , \pi_i)_{i \in N} }$ and maps it onto
-$\gamma_i(G) = (\theta, e_i)$ where
-$\theta \mycolon \bigtimes_{j \in N} A_j \rightarrow \mathbb{R}$ is a payoff function suitable
-for $G$, and $e_i$ is some representation of $i$'s uncertainty about the co-player's
-behavior. We consider two \emph{preference types}: the \emph{objective type} maps each game
-onto its own, true payoff function; the \emph{regret type} maps each game onto its regret
-transformation, as introduced above. We also consider two \emph{belief types}: the
-\emph{precise type} represents uncertainty in a single probability distribution
-$\mu \in \Delta(\Acts_{-i})$ about the co-players' behavior; the \emph{imprecise type}
-represents uncertainty as a set of probability distributions $X \subseteq \Delta(\Acts_{-i})$.
+The subjective representation scheme $\gamma_i$ of agent $i$ is a function that
+takes a game $G = \tuple{ N, (A_i , \pi_i)_{i \in N} }$ and maps it onto
+$\gamma_i(G) = (\theta, e)$ where
+$\theta \mycolon \bigtimes_{j \in N} A_j \rightarrow \mathbb{R}$ is a subjective utility function (the \emph{preference type} of the player), and $e$ is some subjective representation of a player's uncertainty about the co-players'
+behavior (the \emph{belief type} of the player). As already anticipated, we mostly consider two preference types here: the \emph{objective type} maps each game
+onto its own, true evolutionary payoffs (i.e., $ \theta = \pi_i $); the \emph{regret type} maps each game onto its negative regret
+transformation (i.e., $ \theta = -\text{preg} $). We also consider two belief types: the
+\emph{precise type} represents uncertainty about the co-players in a single probability measure
+$\mu \in \Delta(\Acts_{-i})$; the \emph{imprecise type}
+represents uncertainty as a set of probability measures $\Gamma \subseteq \Delta(\Acts_{-i})$.
 It is convenient to conceptualize precise beliefs as a special case of imprecise beliefs by
-looking at $\mu$ as a stand-in for the singleton set $\set{\mu}$. Background on imprecise
-probabilities is provided in Appendix~\ref{sec:impr-prob-beli}.
-
-The action choice function $\kappa$ that we consider here is \emph{maximinimization of expected
-  (subjective) utilities} (see Section~\ref{sec:impr-prob-beli} for motivation).
-
-\begin{definition}[Maximinimization of expected (subjective) utility]
+looking at $\mu$ as a stand-in for the singleton set $\set{\mu}$.
+The action selection function $\kappa_i(\gamma_i(G)) \subseteq A_i$ that we consider here is \emph{maximinimization of expected utility} (see Appendix~\ref{sec:impr-prob-beli} for motivations).
+
+\begin{definition}[Maximinimization of expected utility]
   \label{def:maxminSEU}
-  Fix a strategic game $G$. Let agent $i$'s subjective representation scheme
-  $\gamma_i(G) = (\theta, e_i)$ be such that $\theta$ is $i$'s subjective payoff function for
-  $G$ and $e_i$ is a (possibly singleton) set of probability distributions in
-  $\Delta(\Acts_{-i})$. Agent $i$'s expected (subjetive) utility for act $\myact{i}$ and belief
+  Fix a game $G$. Let agent $i$'s subjective representation scheme
+  $\gamma_i(G) = (\theta, e)$ be such that $\theta$ is $i$'s subjective utility function and $e \subseteq \Delta(\Acts_{-i})$ is a (possibly singleton) set of probability measures.
+Agent $i$'s expected utility for act $a_{i}$ and belief
   $\mu \in e$ is
-  $\EU(\myact{i}, \mu) = \sum_{\myact{-i} \in \Acts_{-i}} \mu(\myact{-i}) \theta(\myact{i},
-  \myact{-i})$.
-  Act $\myact{i}^*$ is selected by maximinimization of expected (subjective) utility iff
-  $\myact{i}^* \in \arg \max_{\myact{i} \in \Acts_{i}} \min_{\mu \in e} \EU(\myact{i}, \mu)$.
+  $\EU(a_{i}, \mu) = \sum_{a_{-i} \in \Acts_{-i}} \mu(a_{-i}) \theta(a_{i},
+  a_{-i})$.
+  Act $a_{i}^*$ is selected by maximinimization of expected utility iff
+  $a_{i}^* \in \arg \max_{a_{i} \in \Acts_{i}} \min_{\mu \in e} \EU(a_{i}, \mu)$.
 \end{definition}
 
+\iffalse
 \begin{fact} \label{fact:singleton probability set}
 Maximinimization under a precise (singleton set) belief is just standard
-maximization of expected utilities.
+maximization of expected utility (Definition~\ref{def:rationality}).
 \end{fact}
-
-\begin{fact} \label{fact:maxEU-minReg} Under an identical precise (singleton set) belief, the
-  acts selected by maximization of expected utility in game $G$ are exactly the acts selected
-  by the maximization of expected utility for the negative regret transformation of $G$
-  \citep[e.g.,][]{HalpernPass2012:Iterated-Regret}.
+\fi
+
+\begin{fact} \label{fact:maxEU-minReg} 
+%Under an identical precise (singleton set) belief, the
+%  acts selected by maximization of expected evolutionary payoff in game $G$ are exactly the acts selected
+%  by the maximization of expected utility for the negative regret transformation of $G$
+Under an identical precise (singleton set) belief, maximization of expected evolutionary payoff and minimization of expected regret coincide. %\citep[e.g.,][]{HalpernPass2012:Iterated-Regret}.
 \end{fact}
 
-This means that as far as behavior is concerned, regret types cannot be distinguished from
-objective types, as long as both hold precise beliefs. This will be central in understanding
-later results: under precise beliefs, evolution will not favor either preference type over the
-other. On the other hand, if paired with imprecise beliefs, different behavioral predictions
+\noindent This means that objective and regret types are behaviorally indistinguishable, as long as both hold precise beliefs. 
+%This will be central in understanding later results. 
+On the other hand, if paired with imprecise beliefs, different behavioral predictions
 arise.
@@
 In the following, we assume that agents are maximally uncertain, so that precise types have a
-(singleton set containing a) flat probability distribution
-$\overline{\mu} \in \Delta(\Acts_{-i})$ and imprecise types consider all probabilistic beliefs
-about the co-players' behavior $\overline{X} = \Delta(\Acts_{-i})$. In that case, the
+(singleton set containing a) uniform probability measure
+$\overline{\mu} \in \Delta(\Acts_{-i})$ and imprecise types entertain all probabilistic beliefs
+about the co-players' behavior $\overline{\Gamma} = \Delta(\Acts_{-i})$. In that case, the
 considered choice mechanisms are behaviorally equivalent to classic choice rules, as summarized
-in Table~\ref{tab:CMs}. This means that most of the following results which we would like to
-interpret as results about the evolutionary fitness of subjective representation schemes have
-value also for anyone interested only in a comparison of the ecological value of classic choice
+in Table~\ref{tab:CMs}.
+This means that most of the following results which we interpret as results about the evolutionary fitness of different subjective representations are also relevant for a comparison of the ecological value of classic choice
 rules.
@@
 Under maximal uncertainty, all four choice mechanisms considered here are behaviorally
-equivalent on $2 \times 2$ symmetric games, except for objective preference types with
+equivalent on $2 \times 2$ symmetric games, except for objective types with
 imprecise beliefs:
 
-\begin{fact} \label{fact:equivalence2x2} In the class of $2 \times 2$ symmetric games, acts
-  selected by Laplace's rule are exactly the acts selected by regret minimization. 
+\begin{fact} \label{fact:equivalence2x2} In the class of $2 \times 2$ symmetric games, the acts
+  selected by Laplace rule are exactly the acts selected by regret minimization.
 \end{fact}
 
-\section{The basic model}
+\section{The model}
 \label{sec:basic-model-1}
@@
 
-To demonstrate the usefulness of a meta game approach, let us concentrate first on a basic
+To demonstrate the usefulness of the meta-game approach, let us concentrate first on a basic
 model that contains the four choice mechanisms from Table~\ref{tab:CMs}. From now on we speak
-of types when we mean pairs like $(\text{reg}, \text{imp})$, a choice mechanism with
-regret-based preferences and imprecise beliefs, or $(\text{obj}, \text{prc})$, one with
-objective preferences and precise beliefs.
-
-Meta games factor in statistical properties of the environment. For particular empirical
+of types when we mean pairs $(\text{preference type}, \text{belief type})$, like $(\text{reg}, \text{imp})$ or $(\text{obj}, \text{prc})$.
+
+Meta-games factor in statistical properties of the environment. For particular empirical
 purposes, one would consult a specific class of games $\mathcal{G}$ with appropriate,
 empirically informed probabilities $P(G)$ in order to match the natural environment of a given
-population. But for our theoretical purposes we adopt another approach, since we would not know
-how to justify any more specific assumption. To begin with, let $\mathcal{G}$ be a set of
-symmetric 2-player games with two acts. A game is then individuated solely by its payoff
-function, which is essentially a matrix with four numbers. As for occurrence probabilities of
-games, we imagine that entries in a game's payoff matrix are i.i.d.~random variables sampled
-uniformly from set $ \lbrace 0, \dots, 10 \rbrace$.  Using Monte Carlo simulation, we can then
-approximate the relevant fitness values of Equation~(\ref{eq:FittnessChoiceMechGamePairwise})
-to construct meta game payoffs. Results based on $100,000$ randomly sampled games are given in
+population. 
+%But for our theoretical purposes we adopt another approach. 
+For our theoretical purposes, let $\mathcal{G}$ be a set of
+symmetric two-player games with two acts for a start. A game is then individuated solely by its payoff
+function, which is a matrix with four numbers. As for occurrence probabilities of
+games, we imagine that entries in a game's matrix are i.i.d.~random variables sampled
+uniformly from set $ \lbrace 0, \dots, 10 \rbrace$.  Using Monte Carlo simulations, we can then
+approximate the values of Equation~(\ref{eq:FittnessChoiceMechGamePairwise})
+to construct meta-game payoffs. Results based on $100,000$ randomly sampled games are given in
 Table~\ref{tab:ExpectedFitness_4Types}.\footnote{Concretely, $100,000$ games were sampled
@@
 interestingly, Table~\ref{tab:ExpectedFitness_4Types} shows that $(\text{obj}, \text{imp})$,
-the maxmin strategy, is strictly dominated by the three other strategies: in each column (i.e.,
-for each kind of opponent), the maxmin strategy is strictly worse than any of the other three
+the maxmin strategy, is strictly dominated by the three other types: in each column (i.e.,
+for each kind of co-player), the maxmin strategy is strictly worse than any of the other three
 competitors. This has a number of interesting consequences.
 
-Let's begin with a restricted scenario and look at more and more complex cases afterwards. If
-we restrict attention to only imprecise belief types, then a state in which every agent has
+If we restrict attention to only imprecise belief types, then a monomorphic state in which every agent has
 regret-based preferences is the only \emph{evolutionarily stable state}. More strongly, since
 $(\text{obj}, \text{imp})$ is strictly dominated by $(\text{reg}, \text{imp})$, we expect
-selection that is driven by expected fitness to invariably weed out $(\text{obj}, \text{imp})$,
-the maxmin choice rule, in favor of $(\text{reg}, \text{imp})$, regret minimization. In other
-words, when taking average payoffs over the class of random games considered here, regret
-minimization is a better classic choice rule than the maxmin rule from an evolutionary point of
-view, despite the fact that the former, but not the latter, entertains non-veridical subjective
-preferences.
+selection that is driven by (expected) fitness to invariably weed out maxmin players $(\text{obj}, \text{imp})$ in favor of $(\text{reg}, \text{imp})$, regret minimization. 
+In other
+words, over the class of games considered here, regret
+minimization is a better classic rule than maxmin from an evolutionary point of
+view.
 
@@
 $(\text{reg}, \text{imp})$, $(\text{reg}, \text{prc})$ and $(\text{obj}, \text{prc})$. The
-relative proportions of these depend on the initial population. This variability disappears if
+relative proportions of these depend on the initial shares in the population. This variability disappears if
 we add a small mutation rate to the dynamics. Take a fixed, small mutation rate $\epsilon$ for
 the probability that a player's preference type \emph{or} her belief type changes to another
-preference type or belief type. The probability that a player randomly mutates into a
-completely different player with altogether different preference type and belief type would
-then be $\epsilon^2$. With these assumptions about ``component-wise mutations,'' numerical
+preference or belief type. The probability that a player's type randomly mutates into a
+completely different type with altogether different preference type and belief type would
+then be $\epsilon^2$. With these assumptions about ``component-wise mutations'', numerical
 simulations of the (discrete time) \emph{replicator mutator dynamics}
 \citep{Nowak2006:Evolutionary-Dy} show that already for very small mutation rates almost all
-initial populations converge to a single fixed point in which the majority of players are
+initial population states converge to a single fixed point in which the majority of players are
 regret types. For instance, with $\epsilon = 0.001$, almost all initial populations are
@@
 behavior as such, it need not be the case that behaviorally equivalent mechanisms are treated
-equally all the while. If mutation probabilities are a function of individual components (i.e.,
-preference and belief types) of such behavior-generating mechanisms, it can be the case that
-certain components are more strongly favored by a process of random mutation and
-selection. This is exactly the case with regret-based subjective preferences in the present
-example. Since regret-based subjective preferences are much better in connection with imprecise
+equally all the while. If mutation probabilities are a function of individual components, it can be the case that
+certain components of such behavior-generating mechanisms are more strongly favored by a process of random mutation and
+selection. This is exactly the case with regret-based preferences. Since regret-based preferences are much better in connection with imprecise
 beliefs than veridical preferences are, the proportion of expected regret minimizers,
@@
 
-Results based on the single meta game in Table~\ref{tab:ExpectedFitness_4Types}, which was
-obtained by Monte Carlo simulation, are not fully general and possibly spoiled by random
+Results based on the single meta game in Table~\ref{tab:ExpectedFitness_4Types} are not fully general and possibly spoiled by random
 fluctuations in the sampling procedure. Fortunately, for the case of $2 \times 2$ symmetric
 games, the main result that maxmin types $(\text{obj}, \text{imp})$ are strictly dominated can
-also be shown analytically for generous general conditions on how likely randomly sampled games
-are.
+also be shown analytically for generous general conditions.
 
@@
   set of i.i.d.~values with at least three elements in the support. Then,
-  $(\text{reg}, \text{imp})$ strictly dominates $(\text{reg}, \text{prc})$ in the resulting
-  meta game.
+  $(\text{reg}, \text{imp})$ strictly dominates $(\text{obj}, \text{imp})$ in the resulting
+  meta-game.
 \end{proposition}
 
-\begin{corollary} \label{corollary1} Considering only $(\text{obj}, \text{imp})$ and
-  $(\text{reg}, \text{imp})$, and letting $\mathcal{G}$ be the class of $2 \times 2$ symmetric
-  games with payoffs sampled from a set of i.i.d.~values with at least three elements in the
-  support, the unique evolutionarily stable state is a monomorphic population of
-  $(\text{reg}, \text{imp})$-players.
+\begin{proof}
+See Appendix~\ref{sec:proofs}.
+\end{proof}
+
+\begin{corollary} \label{corollary1} If we only consider imprecise belief types, $(\text{obj}, \text{imp})$ and
+  $(\text{reg}, \text{imp})$, and letting $\mathcal{G}$ be as in Proposition~\ref{proposition1}, then the unique evolutionarily stable state is a monomorphic population of
+  $(\text{reg}, \text{imp})$ players.
 \end{corollary}
 
-A proofs for Proposition \ref{proposition1} is given in Appendix~\ref{sec:proofs}. The result
-tells us that the main conclusions drawn in the previous section based on the approximated meta
-game in Table~\ref{tab:ExpectedFitness_4Types} hold more generally for any class of games in
-which the probability of encountering a game is the product of independently sampling four
-identically distributed payoff values. As before, $(\text{reg}, \text{imp})$,
-$(\text{obj}, \text{prc})$, and $(\text{reg}, \text{prc})$ players will be neutrally stable,
-and fitness-based selection will tend to weed out maxmin play and leave us with a population of
-arbitrary frequency of $(\text{reg}, \text{imp})$, $(\text{obj}, \text{prc})$, and
-$(\text{reg}, \text{prc})$ players. This shows that there is support for the main conceptual
-point that we wanted to make: non-veridical subjective preference relations \emph{can}, under
-specific circumstances, persist under evolutionary selection based on objective
-fitness. Moreover, regret-based preferences can not only persist, but even be favored by
-natural selection if agents may have imprecise beliefs. This holds generally for playing
-arbitrary $2 \times 2$ symmetric games whose payoffs are sampled identically and independently
-at random.
+%Obviously, $(\text{reg}, \text{imp})$,
+%$(\text{obj}, \text{prc})$, and $(\text{reg}, \text{prc})$ players will be neutrally stable, as before. 
+%and fitness-based selection will tend to weed out maxmin play and leave us with a population of
+%arbitrary frequency of $(\text{reg}, \text{imp})$, $(\text{obj}, \text{prc})$, and
+%$(\text{reg}, \text{prc})$ players. 
+The result shows that there is support for the main conceptual
+point that we wanted to make: 
+%non-veridical representations \emph{can}, under
+%specific circumstances, persist under evolutionary selection based on objective
+%fitness. Moreover, 
+non-veridical regret-based preferences representations can not only persist, but even be favored by
+natural selection if agents may have imprecise beliefs.
+This
+tells us that the main conclusions drawn in the previous section based on the approximated meta-game of Table~\ref{tab:ExpectedFitness_4Types} hold more generally 
+for
+arbitrary $2 \times 2$ symmetric games with i.i.d. sampled payoffs.
 
@@
 
-How do the basic results from the previous section carry over to more encompassing, richer
+How do the basic results from the previous section carry over to even more encompassing and richer
 models? Section~\ref{sec:more-types} first introduces further conceptually interesting
-preference types that have been considered in the recent
-literature. Section~\ref{sec:n-times-n} then addresses the case of $n \times n$ games for
+preference types that have been considered in the literature. Section~\ref{sec:n-times-n} then addresses the case of $n \times n$ games for
 $n \ge 2$. Finally, to put our results into a broader perspective,
@@
 Beyond objective and regret-based preferences, other preference types have been investigated. A
-famous example is the \textit{altruistic type} \textcolor{red}{[INSERT REFERENCE]}, summoned to
+famous example is the \textit{altruistic type} \citep[e.g.,][]{Beck76,BestGuth98}, summoned to
 explain the possibility of altruistic behavior. At the other end of the spectrum, the \emph{competitive
@@
 
-  Fix a two player game $G$ with actual payoff function $\pi$. The \textit{altruistic type}
-  represents $G$'s payoffs as $\theta(a_i, a_j):=\pi_i(a_i,a_j) + \pi_j(a_i,a_j)$.\footnote{A
+  Fix a two-player game $G$ with actual evolutionary payoff functions $\pi_i$. The \textit{altruistic type}
+  has subjective utility $\theta(a_i, a_j):=\pi_i(a_i,a_j) + \pi_j(a_i,a_j)$.\footnote{A
     more general formulation would be to define an $ \alpha$-altruistic type, for
@@
     interested in the evolution of degrees of altruism, here we simply fix $ \alpha = 1 $.} The
-  \emph{competitive type} represents $G$'s payoffs as
+  \emph{competitive type} has subjective utility
   $\theta(a_i, a_j):=\pi_i(a_i,a_j) - \pi_j(a_i,a_j)$.
@@
 
-Table~\ref{tab:ExpectedFitness_2x2_Full} shows results of further Monte Carlo simulations that
-approximate the expected fitness in the relevant meta game with all types considered so
-far. These results confirm basic intuitions about altruistic and competitive types: averaging
-over randomly sampled games, everybody would like to have an altruistic opponent and nobody
-would like to play against a competitive opponent. Perhaps more surprisingly, altruistic types
-come up strictly dominated by competitive types, but competitive types themselves are worse off
-against all opponent types except against maxmin players $(\text{obj}, \text{imp})$ than any of
+Table~\ref{tab:ExpectedFitness_2x2_Full} shows results of Monte Carlo simulations that
+approximate the expected fitness in the relevant meta-game with all types considered so
+far. These results confirm basic intuitions about altruistic and competitive types: everybody would like to have an altruistic co-player and nobody
+would like to play with a competitive player. Perhaps more surprisingly, $(\text{alt}, \text{imp})$
+come up strictly dominated by $(\text{com}, \text{imp})$, but competitive types themselves are worse off
+against all types except against maxmin players $(\text{obj}, \text{imp})$ than any of
 the behaviorally equivalent types $(\text{reg}, \text{imp})$, $(\text{obj}, \text{prc})$, and
-$(\text{reg}, \text{prc})$.  \iffalse This is a noteworthy results in the light of the fact
+$(\text{reg}, \text{prc})$.
+\iffalse This is a noteworthy results in the light of the fact
 that evolving altruistic preferences have been shown to support cooperative behavior in a
@@
 games, like we do here, makes altruistic preferences prime victims of evolutionary eradication.
-\fi It is easy to see then that the previous result still obtains for the larger meta game in
+\fi
+It is easy to see then that the previous result still obtains for the larger meta-game in
 Table~\ref{tab:ExpectedFitness_2x2_Full}: $(\text{reg}, \text{imp})$,
 $(\text{obj}, \text{prc})$, and $(\text{reg}, \text{prc})$ are still neutrally stable;
-simulation runs of the (discrete-time) replicator dynamic on the $8 \times 8$ meta game from
-Table~\ref{tab:ExpectedFitness_2x2_Full} all ended up in populations consisting of only these
-players in arbitrary proportion.
+simulation runs of the (discrete-time) replicator dynamics on the $8 \times 8$ meta-game from
+Table~\ref{tab:ExpectedFitness_2x2_Full} all end up in population states consisting of only these
+three types in arbitrary proportion.
 
 In sum, the presence of other plausible preference types, such as competitive and altruistic
-types does not undermine, but rather strengthens the previous results about the evolutionary
-drive towards regret-based subjective preferences.
-
-\subsection{More actions: $n \times n$ symmetric games}
+types, does not undermine, but rather strengthens the previous results about the evolutionary
+drive towards regret-based preferences.
+
+\subsection{More actions}
 \label{sec:n-times-n}
 
-Results from Section~\ref{sec:basic-model-1} relied heavily on Fact~\ref{fact:equivalence2x2}
-that, for the special case of $2 \times 2$ symmetric games, regret minimization
-$(\text{reg}, \text{imp})$ is behaviorally equivalent with expected regret minimization
-$(\text{reg}, \text{prc})$ and expected utility maximization $(\text{obj}, \text{prc})$. This
-is no longer true when we look at arbitrary $n \times n$ games with $n \ge 2$. Let us see what
+Results from Section~\ref{sec:basic-model-1} relied heavily on Fact~\ref{fact:equivalence2x2}, that
+is no longer true when we look at arbitrary $n \times n$ games. Let us see what
 happens in a broader class of games.
 
-Table~\ref{tab:ExpectedFitness_10x10} gives approximations of expected fitness in a class of
-$n \times n$ symmetric games where $n$ is randomly drawn from $\set{2, \dots, 10}$. Concretely,
-the numbers in Table~\ref{tab:ExpectedFitness_10x10} are averages of payoffs obtained in
-100,000 randomly sampled games, where each game was sampled by first picking a number of acts
+Table~\ref{tab:ExpectedFitness_10x10} gives approximations of expected fitness in the class of
+$n \times n$ symmetric games. Concretely,
+the numbers in Table~\ref{tab:ExpectedFitness_10x10} are averages of evolutionary payoffs obtained in
+100,000 randomly sampled symmetric games, where each game was sampled by first picking a number of acts
 $n \in \set{2, \dots, 10}$ uniformly at random, and then filling the necessary $n \times n$
@@
 strictly dominated by $(\text{reg}, \text{prc})$ and by $(\text{obj}, \text{prc})$ in the
-meta game from Table~\ref{tab:ExpectedFitness_10x10}. This means that while regret minimization
+meta-game from Table~\ref{tab:ExpectedFitness_10x10}. This means that while simple regret minimization
 \emph{can} thrive in some evolutionary contexts, there are also contexts where it is
@@
 by selection. Since, by Fact~\ref{fact:maxEU-minReg}, $(\text{reg}, \text{prc})$ and
-$(\text{obj}, \text{prc})$ are generally behaviorally equivalent, it remains that selection
-based on meta games constructed from $n \times n$ games will still not eradicate all regret
-types. So, although regret types may not be selected for in this case, they are also not
+$(\text{obj}, \text{prc})$ are behaviorally equivalent in general, it remains that selection
+based on meta-games constructed from $n \times n$ games will still not eradicate regret
+preferences. So, although regret types may not be selected for in this case, they are also not
 selected against.
@@
 evolution would select for regret types exclusively, even in $n \times n$ games. If, for
-example, epistemic types of players are not what biological evolution selects, but rather
+example, the belief type of a player is a trait that biological evolution has no bite on, but rather
 something that the particular choice situation would exogenously give us, then regret-based
-preference \emph{can} again drive out veridical preferences altogether. For concreteness,
+preferences \emph{can} again drive out veridical preferences altogether. For concreteness,
 suppose that only preference types compete and that agents' belief types are exogenously given,
-in such a way that agents hold precise beliefs with probability $p$ and otherwise imprecise
-beliefs. This transforms the meta game from Table~\ref{tab:ExpectedFitness_10x10} into the
-simpler $4 \times 4$ game in which the payoff obtained for a preference type is the weighted
+in such a way that both players hold precise beliefs with probability $p$ and they both have imprecise
+beliefs otherwise. This transforms the meta-game from Table~\ref{tab:ExpectedFitness_10x10} into a
+simpler $4 \times 4$ meta-game in which the payoff obtained for a preference type is the weighted
 average over the payoffs of the choice mechanisms including that preference type in
-Table~\ref{tab:ExpectedFitness_10x10}. Setting $p = 0.98$ for illustration, we get the meta
-game in Table~\ref{tab:ExogeneousEpistemics}.
-
+Table~\ref{tab:ExpectedFitness_10x10}. Setting $p = 0.98$ for illustration, we get the meta-game in Table~\ref{tab:ExogeneousEpistemics}.
 \begin{table}[]
@@
   $\text{obj} $ & 6.924 & 6.924 & 5.948 & 7.751 \\ 
-  $\tau^{com }$ & 6.566 & 6.570 & 5.481 & 7.434 \\ 
+  $\text{com }$ & 6.566 & 6.570 & 5.481 & 7.434 \\ 
   $\text{alt} $ & 6.463 & 6.461 & 5.478 & 7.469 \\ 
@@
 \end{table}
-
-The only evolutionarily stable state of this meta game is the regret type. Accordingly, all of
-our simulation runs of the (discrete-time) replicator dynamic converged to monomorphic
+The only evolutionarily stable state of this meta-game is a monomorphic population of regret types. Accordingly, all of
+our simulation runs of the (discrete-time) replicator dynamics converge to monomorphic
 regret-type populations. The reason why regret types prosper is because they have a substantial
-payoff advantage if paired with imprecise beliefs. If radical uncertainty is exogenously given
+fitness advantage if paired with imprecise beliefs (Proposition~\ref{proposition1}). If imprecise uncertainty is exogenously given
 as something unavoidable that happens to agents (e.g., in situation where they really have no
@@
 To see how different choice mechanisms behave in evolutionary competition based on solitary
-decision problems, we approximated, much in the spirit of meta games, average accumulated
-payoffs obtained in randomly generated solitary decision problems. For our purposes, a decision
-problem $\tuple{S, \Acts, u}$ consists of a set of world states $S$, a set of acts $\Acts$, and
-a utility function $u \mycolon S \times \Acts \rightarrow \mathbb{R}$.  We generated arbitrary
+decision making, we approximated, much in the spirit of meta-games, average accumulated
+fitness obtained in randomly generated solitary decision problems. For our purposes, a decision
+problem $\tuple{S, \Acts, \pi}$ consists of a set of states $S$, a set of acts $\Acts$, and
+a payoff function $\pi \mycolon S \times \Acts \rightarrow \mathbb{R}$.  We generate arbitrary
 decision problems by selecting, uniformly at random, numbers of states and acts
 $n_s, n_\act \in \set{2, \dots, 10}$ and then filling the utility table, so to speak, by
-i.i.d.~samples for each $u(s, \act) \in \set{0, 10}$, uniformly at random. Unlike with
+i.i.d.~samples for each $\pi(s, \act) \in \set{0, 10}$. Unlike with
 two-player games, we need to also sample the actual state of the world, which we selected
 uniformly at random from the available states in the current decision problem. As player types,
-we considered the original cast of four from Table~\ref{tab:CMs} again, since altruistic and
-competitive preferences are meaningless in solitary decision situations. As before, the
+we considered the original cast of four from Table~\ref{tab:CMs}, since altruistic and
+competitive types are meaningless in solitary decision situations. As before, the
 relevant fitness measure, defined in Equation~(\ref{eq:FittnessChoiceMechSolitary}), was
@@
 general, and $(\text{reg}, \text{imp})$ is behaviorally equivalent to the former two in
-decision problems with 2 states and 2 acts. This shows in the results from
+decision problems with two states and two acts. This shows in the results from
 Table~\ref{tab:SolitaryDecisions} in that the averages for $(\text{reg}, \text{prc})$ and
 $(\text{obj}, \text{prc})$ are identical. But since we included decision problems with more
-acts and more states as well, the averages for regret minimizers $(\text{reg}, \text{imp})$ are
-not identical to the one of $(\text{reg}, \text{prc})$ and $(\text{obj}, \text{prc})$. They
-are, in fact, lower, but not as low as those of $(\text{obj}, \text{imp})$.
+acts and more states as well, the average for regret minimizers $(\text{reg}, \text{imp})$ is
+not identical to the one of $(\text{reg}, \text{prc})$ and $(\text{obj}, \text{prc})$. It
+is, in fact, lower, but again not as low as that of $(\text{obj}, \text{imp})$.
 
@@
 solitary decisions. Evolutionary selection based on objective fitness will not select against
-regret-based subjective preferences, as these are indistinguishable from veridical preferences
+regret-based preferences, as these are indistinguishable from veridical preferences
 when paired with precise beliefs. But when paired with imprecise beliefs, regret-based
@@
 existence of player types with subjective utilities different
-from the actual payoffs that can outperform types whose
-subjective utilities coincide with the actual payoffs.
-While the literature on evolution of preference has focused
-on fixed games, or fixed types of games, we have adopted a
+from the actual evolutionary payoffs that can outperform types whose
+subjective utilities coincide with the evolutionary payoffs.
+While the literature on evolution of preferences has focused
+on fixed games, we have adopted a
 more general approach here. We suggested that attention
-to “meta games” is crucial, because what may be a good
+to “meta-games” is crucial, because what may be a good
 subjective representation in one type of game (e.g., cooperative preferences in the Prisoner’s Dilemma class) need not
 be generally beneficial. Taken together, we presented a variety of plausible circumstances in which evolutionary competition between choice
-mechanisms on a larger class of games can favor subjective
-preference representations focusing on regret.
-
-Meta games are a useful tool for probing into conceptual questions about the ecological
-rationality of choice mechanisms. The approach is rich and general, with many possible further
+mechanisms on a larger class of games can favor non-veridical preference representations focusing on regret.
+
+Meta-games are useful tools for probing into conceptual questions about ecological
+rationality. The approach is rich and general, with many possible further
 applications imaginable beyond the case study presented here. For example, the evolutionary
-investigation of different risk and ambiguity attitudes when competing against each other in an
-evolutionarily richer environment may bring new insights on both behavioral and theoretic
+investigation of different risk and ambiguity attitudes when competing against each other may bring new insights on both behavioral and theoretic
 decision making under uncertainty, as well as on many issues in theoretical biology and
@@
 ignored in this paper. Finally, while this paper only used dummy models of diverse decision
-environments, the meta game approach also allows for empirically informed models of rich and
+environments, the meta-game approach also allows for empirically informed models of rich and
 variable environments.
@@
 traditional ways of answering this. According to standard Bayesianism, one should always be
-able to determine a precise betting rate (that immediately translates into a precise
-probability distribution), which is fair, in the sense that the DM is indifferent between
-betting on or against red at the fair rate, and would bet on red at any rate that is more
-favourable than the fair rate and against red at any rate that is less favourable. In the case
+able to determine a precise betting rate, that immediately translates into a precise
+probability distribution. In the case
 of the bag on my desk, a strict Bayesian, in the absence of any further information, would
 probably rely on the \textit{principle of insufficient reason} and answer that the DM should
-have a uniform distribution that considers all the outcomes equipossible.
+have a uniform measure that considers all the outcomes equipossible.
 
@@
   Such uncertainty is inherent in situations of strategic interaction. This is quite obvious
-  when such situations have been faced only a few times.\todo{insert page number}
+  when such situations have been faced only a few times. (p. 646)
 \end{quote}
@@
 uncertainty about the composition of the population that they are part of, and consequently
-about the co-player that they are randomly paired with at each round and about the co-players'
+about the co-player that they are randomly paired with at each round and about the co-player's
 action.
 
-We therefore represent extreme uncertainty in two different ways that correspond to the two
-approaches discussed above: a Bayesian uniform distribution and an imprecise probability
+We therefore represent maximal uncertainty in two different ways that correspond to the two
+approaches discussed above: a Bayesian uniform measure and an imprecise probability
 set. The latter represents uncertainty for players who are not able to narrow down the set of
-probability distributions to a single one and they consider all of them as possible. The former
+probability measures to a single one and they consider all of them as possible. The former
 precise belief type conceptualizes the uncertainty about the population by using the principle
@@
 or yellow. A marble is to be drawn and DM can win 100€ if she guesses the color of the drawn
-marble. The DM is offered two different bets. In the first one she can choose to bet either on
+marble. DM is offered two different bets. In the first one she can choose to bet either on
 red (R) or on yellow (Y), while in the second she can bet either on red or black (RB) or on
@@
 precise probabilistic belief about the proportion of black and yellow marbles. This kind of
-behavior has been famously axiomatized by Gilboa and Schmeidler in a paper from 1989. The
-choice pattern is normally explained in terms of aversion to uncertainty, and the standard
+behavior has been famously axiomatized by \citet{gilsch89}. The
+choice pattern is normally explained in terms of aversion to unmeasurable uncertainty, and the standard
 representation is given by means of a set of probability measures together with maxmin rule. We
-can think of the DM in Ellsberg's example as maximinimizing expected utility over the
+can think of DM in Ellsberg's example as maximinimizing expected utility over the
 probability set
 $
-[\underline{P}(R)=\overline{P}(R)=\frac{1}{3},\underline{P}(Y)=0,\underline{P}(B)=0,\overline{P}(Y)=\frac{2}{3},\overline{P}(B)=\frac{2}{3}]
+[\underline{P}(R)=\overline{P}(R)=\frac{1}{3}, \underline{P}(Y)= \underline{P}(B)=0, \overline{P}(Y)= \overline{P}(B)=\frac{2}{3}]
 $.
@@
 
-Evidence from experimental literature suggests that agents are mainly uncertainty averse
+Evidence from experimental literature suggests that agents are mostly uncertainty averse
 [REF]. In line with empirical data, we assume that players in the population are uncertainty
@@
 $d_{C}$; similarly for games $A \in \mathcal{A}$, $S \in \mathcal{S}$, $W \in \mathcal{W}$, and
-$B \in \mathcal{B}$.  Let us denote by $I_{RC}$ the event that an $R$-player plays action $I$ in
+$B \in \mathcal{B}$.  Let us denote by $I_{RC}$ the event that a $R$-player plays action $I$ in
 the game $C$; and similarly for action $II$, for player $M$, and for games $A$, $S$, $W$ and
@@
 \begin{proof}
-  Assume without loss of generality that $b=d$. There are two situations that we have to check:
-  (i) $b=d \geq a,c$ and $ a \neq c $; (ii) $b=d \leq a,c$ and $ a \neq c $.\todo{what about
-    $a < b = d < c$ and $c < b = d < a$?}\ In the first case it is easy to see that $R$ and $M$
-  perform equally well. Indeed, given (i), both $R$ and $M$ choose action $I$ if $a>c$, and
-  action $II$ if $c>a$. If case (ii) holds instead, we have that $R$ plays $I$ if $a>c$ and
-  $II$ if $c>a$ as before, but $M$ plays $(\frac{1}{2}I;\frac{1}{2}II)$, since both $I$ and
+  Assume without loss of generality that $b=d$, and that $ a>c $. There are two cases that we have to check:
+  (i) $c < b=d$ and (ii) $c \geq b=d$. In the first case it is easy to see that $R$ and $M$
+  perform equally: act $I$ is the choice of both $R$ and $M$.
+In the case of (ii) instead we have that $I$ is the regret minimizing action, whereas both actions have the same minimum and $M$ plays $(\frac{1}{2}I;\frac{1}{2}II)$, since both $I$ and
   $II$ maximize the minimal payoff. Consider now a population of $R$ and $M$ playing games from
-  the class $\mathcal{W}$.  Whenever (i) is the case both $R$ and $M$ perform equally. Suppose
-  that (ii) is the case and $W \in mathcal{W}$ is such that $a>c$, without loss of generality. Then,
+  the class $\mathcal{W}$.  Whenever (i) is the case $R$ and $M$ perform equally well. But suppose $W \in \mathcal{W}$ and (ii) is the case. Then,
   $\pi_W(R,R)=a>\frac{1}{2}a+\frac{1}{2}c=\pi_W(M,R)$, whereas
@@
 
-Since it is not difficult to see that both $(R,R)$ and $(M,M)$ are strict Nash equilibria in
+\noindent Since it is not difficult to see that both $(R,R)$ and $(M,M)$ are strict Nash equilibria in
 $\mathcal{C}$, and that $(R,R)$ and $(M,M)$ are not Nash equilibria in $\mathcal{A}$, the main
@@
   anti-coordination game $A\in\mathcal{A}$ with payoffs
-  $(a_{A},b_{A},c_{A},d_{A})=(c_{C},d_{C},a_{C},b_{C})$. Essentially, $\phi$ is swapping rows
+  $(a_{A},b_{A},c_{A},d_{A})=(c_{C},d_{C},a_{C},b_{C})$. Essentially, $\phi$ swaps rows
   in the payoff matrix.
@@
   $d_{C}>b_{C}$, and each game $A\equiv(a_{A},b_{A},c_{A},d_{A})$ is such that $a_{A}<c_{A}$
-  and $d_{A}>b_{A}$. Given that $a,b,c,d$ are i.i.d. random variables and that a sequence of
+  and $d_{A}<b_{A}$. Given that $a,b,c,d$ are i.i.d. random variables and that a sequence of
   i.i.d. random variables is exchangeable, it is clear that the probability of
@@
 \begin{lemma} \label{lemma:probabilities actions coord-ant} Let $P(E)$ be the probability of
-  event $E$, e.g., $P(I_{RC})$ is the probability that a random $R$-player plays act $I$ is
-  fixed coordination game $C$, which is either 0, $.5$ or 1, depending on $C$.  It then holds
-  that:
+  event $E$, e.g., $P(I_{RC})$ is the probability that a random $R$-player plays act $I$ in coordination game $C$, which is either 0, $.5$ or 1.  It then holds that:
 \begin{itemize}
@@
 \begin{proof}
-  It is easy to check that if $b_{C}-d_{C}>c_{C}-a_{C}$, an $R$-player plays action $I$ in $C$;
+  It is easy to check that if $b_{C}-d_{C}>c_{C}-a_{C}$, a $R$-player plays action $I$ in $C$;
   that if $b_{C}-d_{C}<c_{C}-a_{C}$, $R$ plays $II$; and that if $b_{C}-d_{C}=c_{C}-a_{C}$, a
   $R$-player is indifferent between $I$ and $II$ in $C$, and so randomizes with
-  $(\frac{1}{2}I;\frac{1}{2}II)$. Similarly, if $a_{A}-c_{A}>d_{A}-b_{A}$, an $R$-player plays
+  $(\frac{1}{2}I;\frac{1}{2}II)$. Similarly, if $a_{A}-c_{A}>d_{A}-b_{A}$, a $R$-player plays
   action $I$ in $A$; if $a_{A}-c_{A}<d_{A}-b_{A}$, $R$ plays $II$; and if
-  $a_{A}-c_{A}=d_{A}-b_{A}$, an $R$-player is indifferent between $I$ and $II$ in $A$, and
+  $a_{A}-c_{A}=d_{A}-b_{A}$, a $R$-player is indifferent between $I$ and $II$ in $A$, and
   randomizes with $(\frac{1}{2}I;\frac{1}{2}II)$. Consequently, if $b_{C}-d_{C}>c_{C}-a_{C}$,
@@
   then $P(I_{RC})=P(II_{RC})=\frac{1}{2}=P(II_{R\phi(C)})=P(I_{R\phi(C)})$. \\
-  In the same way, in coordination games we have that if $b_{C}>c_{C}$, an $M$-player plays $I$;
-  if $c_{C}>b_{C}$, an $M$-player plays $II$; and if $b_{C}=c_{C}$, $M$ is indifferent between
+  In the same way, in coordination games we have that if $b_{C}>c_{C}$, a $M$-player plays $I$;
+  if $c_{C}>b_{C}$, a $M$-player plays $II$; and if $b_{C}=c_{C}$, $M$ is indifferent between
   $I$ and $II$, and plays $(\frac{1}{2}I;\frac{1}{2}II)$. In anti-coordination games instead,
@@
 It holds that:
-\begin{multicols}{2}
   \begin{itemize}
-  \item $a_{C}>d_{C}\rightarrow(I_{MC}\subset I_{RC})$;
+  \item $a_{C}>d_{C}\rightarrow(I_{MC}\subseteq I_{RC})$;
   \item $a^{C}=d^{C}\rightarrow I_{MC}=I_{RC}$.
-  \item $a_{C}<d_{C}\rightarrow(II_{MC}\subset II_{RC})$;
+  \item $a_{C}<d_{C}\rightarrow(II_{MC}\subseteq II_{RC})$;
   \end{itemize}
-\end{multicols}
 \end{lemma}
@@
 \begin{proof}
-  If $b_{C}-d_{C}>c_{C}-a_{C}$, $R$ plays $I$, and if $b_{C}-d_{C}=c_{C}-a_{C}$, $R$ plays
-  $(\frac{1}{2}I;\frac{1}{2}II)$, whereas if $b_{C}>c_{C}$, $M$ plays $I$, and if
-  $b_{C}=c_{C}$, $M$ plays $(\frac{1}{2}I;\frac{1}{2}II)$.  Then, $I_{RC}$ implies that
+The event that $R$ plays action $I$, $I_{RC}$, with positive probability is the event that $b_{C}-d_{C} \geq c_{C}-a_{C}$: if $b_{C}-d_{C}>c_{C}-a_{C}$, $R$ plays $I$, and if $b_{C}-d_{C}=c_{C}-a_{C}$, $R$ plays
+  $(\frac{1}{2}I;\frac{1}{2}II)$. Similarly, the event that $I_{MC}$ has positive occurrence is the event that $b_{C} \geq c_{C}$: if $b_{C}>c_{C}$, $M$ plays $I$, and if
+  $b_{C}=c_{C}$, $M$ plays $(\frac{1}{2}I;\frac{1}{2}II)$. 
+Then, $I_{RC}$ implies that
   $b_{C}-d_{C}\geq c_{C}-a_{C}$, and $I_{MC}$ implies that $b_{C}\geq c_{C}$. Moreover, on the
@@
 Instead, it is possible that $a_{C}>d_{C}$, $b_{C}-d_{C}>c_{C}-a_{C}$ and $b_{C}<c_{C}$ hold
-  simultaneously, so that $I_{MC}\nsupseteq I_{RC}$.  Consequently:
-  $a_{C}>d_{C}\rightarrow(I_{MC}\subset I_{RC})$.  By a symmetric argument it can be shown that
-  $a_{C}<d_{C}\rightarrow(II_{MC}\subset II_{RC})$ too. Finally, when $a_{C}=d_{C}$ it holds
+  simultaneously, so that $I_{MC}\nsupseteq I_{RC}$.
+By a symmetric argument it can be shown that
+  $a_{C}<d_{C}\rightarrow(II_{MC}\subseteq II_{RC})$ too. Finally, when $a_{C}=d_{C}$ it holds
   that: $b_{C}-d_{C}>c_{C}-a_{C}$ iff $b_{C}>c_{C}$; $b_{C}-d_{C}<c_{C}-a_{C}$ iff
@@
 
-We are now ready to prove that
+\vspace{.5cm}
+
+\noindent We are now ready to prove that
 $F_{\mathcal{C}\cup\mathcal{A}}(R,R)>F_{\mathcal{C}\cup\mathcal{A}}(M,R)$. With notation like
-$P(I_{RC} \cup I_{RC})$ denoting the probability that a random $R$-player plays $I$ and another
-$R$-player plays $I$ as well in game $C$, rewrite this as:
+$P(I_{RC} \cap I_{RC})$ denoting the probability that a random $R$-player plays $I$ and another
+$R$-player plays $I$ as well in game $C$, rewrite the inequality as:
 \begin{align*}
@@
 Then, from (1) we have\footnote{Note that when we have only 3 elements in the support it is not guaranteed that case (1), together with $a>d$, may arise in a coordination game, whereas it is guaranteed that case (2), together with $a>d$, occurs with some positive probability.
-If we take for instance $x= 5, y= 2, z= 1$, then case (1) cannot obtain, whereas if we take $x= 3, y= 2, z= 1$, both (1) and (2) may obtain ($a=3, b=1, c=2, d=2$ for case (1), and $a=3, b=1, c=2, d=2$ for case (2).
+If we take for instance $x= 5, y= 2, z= 1$, then case (1) cannot obtain, whereas if we take $x= 3, y= 2, z= 1$, both (1) and (2) may obtain ($a=3, b=1, c=2, d=2$ for case (1), and $a=3, b=1, c=2, d=2$ for case (2)).
 Moreover, under the assumption that $a>d$, having 3 elements in the support is a necessary and sufficient condition for case (2) to have positive occurrence in a coordination game.
 As it will be clear in the following, a positive occurrence of case (2) only is enough for the theorem to hold.}:
-
-\begin{itemize}
-
-\item $\sum_{C_{a>d}} P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) + P(I_{RC}\cap II_{RC})) + b_{C} \cdot  (P(I_{RC}\cap II_{RC}) + P(I_{RC}\cap I_{RC})) + c_{C} \cdot (P(II_{RC}\cap I_{RC}) +P(II_{RC}\cap II_{RC})- P(I_{RC}\cap II_{MC})- P(II_{RC}\cap II_{MC})) + d_{C} \cdot (P(II_{RC}\cap II_{RC})+P(II_{RC}\cap I_{RC})- P(II_{RC}\cap II_{MC})- P(I_{RC}\cap II_{MC}))]> 0$
-
-\item $\sum_{C_{a>d}} P(C)[a_{C} \cdot (\frac{1}{4}+\frac{1}{4}) + b_{C} \cdot  (\frac{1}{4}+\frac{1}{4}) + c_{C} \cdot (\frac{1}{4}+\frac{1}{4}-\frac{1}{2}-\frac{1}{2}) + d_{C} \cdot (\frac{1}{4}+\frac{1}{4}-\frac{1}{2}-\frac{1}{2})]> 0$
-
-\item $\sum_{C_{a>d}} P(C)[\frac{1}{2}a_{C}+ \frac{1}{2}b_{C} - \frac{1}{2}c_{C} - \frac{1}{2}d_{C}]> 0$
-
-\end{itemize}
+\begin{align*} 
+& \textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) + P(I_{RC}\cap II_{RC})) + b_{C} \cdot  (P(I_{RC}\cap II_{RC}) + P(I_{RC}\cap I_{RC}))\\
+& \ \ \ \ + c_{C} \cdot (P(II_{RC}\cap I_{RC}) +P(II_{RC}\cap II_{RC})- P(I_{RC}\cap II_{MC})- P(II_{RC}\cap II_{MC}))\\
+& \ \ \ \ + d_{C} \cdot (P(II_{RC}\cap II_{RC})+P(II_{RC}\cap I_{RC})- P(II_{RC}\cap II_{MC})- P(I_{RC}\cap II_{MC}))]> 0
+\end{align*}
+\begin{align*}
+\textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot (\frac{1}{4}+\frac{1}{4}) + b_{C} \cdot  (\frac{1}{4}+\frac{1}{4}) + c_{C} \cdot (\frac{1}{4}+\frac{1}{4}-\frac{1}{2}-\frac{1}{2}) + d_{C} \cdot (\frac{1}{4}+\frac{1}{4}-\frac{1}{2}-\frac{1}{2})]> 0
+\end{align*}
+\begin{align*}
+\textstyle{\sum_{C_{a>d}}} P(C)[\frac{1}{2}a_{C}+ \frac{1}{2}b_{C} - \frac{1}{2}c_{C} - \frac{1}{2}d_{C}]> 0
+\end{align*}
 
@@
 
-\noindent This means that, on the class of $\mathcal{C} \cup \mathcal{A}$-games where $a>c$ and
+\noindent This means that where $a_{C}>d_{C}$ and
 where (1) is the case, $R$ and $M$ are equally fit. This changes when we turn to (2). In that
-case, it is easy to check, by Lemma \ref{lemma:action implications}, that
-$P(I_{RC} \cap I_{RC})-P(I_{RC}\cap I_{MC})=P(I_{RC}\cap II_{MC})$ and
-$P(II_{RC}\cap II_{MC})=P(II_{RC} \cap II_{RC})$.\todo{please explain a bit}\ Consequently, we
-have:
-
-\begin{itemize}
-
-\item $\sum_{C_{a>d}} P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) - P(I_{RC}\cap I_{MC})) + b_{C} \cdot  (P(I_{RC}\cap I_{RC})- P(I_{RC}\cap I_{MC})) + c_{C} \cdot (P(II_{RC}\cap II_{RC})- P(I_{RC}\cap II_{MC})- P(II_{RC}\cap II_{MC})) + d_{C} \cdot (P(II_{RC}\cap II_{RC})- P(II_{RC}\cap II_{MC})- P(I_{RC}\cap II_{MC}))]> 0$
-
-\item $\sum_{C_{a>d}} P(C)[a_{C} \cdot P(I_{RC}\cap II_{MC}) + b_{C} \cdot  P(I_{RC}\cap II_{MC}) - c_{C} \cdot P(I_{RC}\cap II_{MC}) - d_{C} \cdot P(I_{RC}\cap II_{MC})]> 0$
-
-\item $\sum_{C_{a>d}} P(C)[P(I_{RC}\cap II_{MC})\cdot (a_{C} + b_{C} - c_{C} - d_{C})]> 0$
-
-\end{itemize}
-
+case, since $a_{C}>d_{C}\rightarrow(I_{MC}\subseteq I_{RC})$ by Lemma \ref{lemma:action implications}, we have that
+$P(I_{RC} \cap I_{RC})-P(I_{RC}\cap I_{MC})=P(I_{RC}\cap II_{MC})$. Moreover, when $a_{C}>d_{C}$, $b_{C}\geq c_{C}$ implies
+  $b_{C}-d_{C}>c_{C}-a_{C}$ (see Lemma \ref{lemma:action implications}).
+Consequently, when $M$ plays either $I$ or $  (\frac{1}{2}I;\frac{1}{2}II)$, $R$ always plays $I$.
+Hence, whenever $a_{C}>d_{C}$ and (2) obtain, it also holds that $P(II_{RC}\cap II_{MC})=P(II_{RC} \cap II_{RC})$.
+In this case we can simplify:
+\begin{align*}
+& \textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) - P(I_{RC}\cap I_{MC})) + b_{C} \cdot  (P(I_{RC}\cap I_{RC})- P(I_{RC}\cap I_{MC})) \\
+& \ \ \ \ + c_{C} \cdot (P(II_{RC}\cap II_{RC})- P(I_{RC}\cap II_{MC})- P(II_{RC}\cap II_{MC})) \\
+& \ \ \ \ + d_{C} \cdot (P(II_{RC}\cap II_{RC})- P(II_{RC}\cap II_{MC})- P(I_{RC}\cap II_{MC}))]> 0
+\end{align*}
+\begin{align*}
+\textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot P(I_{RC}\cap II_{MC}) + b_{C} \cdot  P(I_{RC}\cap II_{MC}) - c_{C} \cdot P(I_{RC}\cap II_{MC}) - d_{C} \cdot P(I_{RC}\cap II_{MC})]> 0
+\end{align*}
+\begin{align*}
+\textstyle{\sum_{C_{a>d}}} P(C)[P(I_{RC}\cap II_{MC})\cdot (a_{C} + b_{C} - c_{C} - d_{C})]> 0
+\end{align*}
 \noindent We know that $I_{RC}$ implies that $a_{C}-c_{C}\geq d_{C}-b_{C}$.
@@
 $$\sum_{C_{a>d}} P(C)[P(I_{RC}\cap II_{MC})\cdot (a_{C} + b_{C} - c_{C} - d_{C})]> 0$$
-is satisfied. So, in the class of $\mathcal{C} \cup \mathcal{A}$-games where $a >c$, $R$
-strictly dominates $C$. Symmetrically, from $a<d$ and by distinguishing between the two cases
+is satisfied. So, when $a_{C}>d_{C}$, $R$
+strictly dominates $M$. Symmetrically, from $a<d$ and by distinguishing between the two cases
 (1) and (2) as before, in the end we get:
 \begin{itemize}
-\item $\sum_{C_{a<d}} P(C)[-\frac{1}{2}a_{C}- \frac{1}{2}b_{C} + \frac{1}{2}c_{C} + \frac{1}{2}d_{C}]= 0$; and
-\item $\sum_{C_{a<d}} P(C)[P(II_{RC}\cap I_{MC})\cdot (-a_{C} - b_{C} + c_{C} + d_{C})]> 0$.
+\item[(1)] $\sum_{C_{a<d}} P(C)[-\frac{1}{2}a_{C}- \frac{1}{2}b_{C} + \frac{1}{2}c_{C} + \frac{1}{2}d_{C}]= 0$; and
+\item[(2)] $\sum_{C_{a<d}} P(C)[P(II_{RC}\cap I_{MC})\cdot (-a_{C} - b_{C} + c_{C} + d_{C})]> 0$.
 \end{itemize}
-\noindent Hence, we can conclude that $R$ strictly dominates $M$ on the class
+\noindent Hence, we can conclude that $R$ strictly dominates $M$ in the class
 $\mathcal{C}\cup\mathcal{A}$. Notice that in case of i.i.d. sampling with infinite support,
@@
 
-It remains to be shown that
+\noindent It remains to be shown that
 $F_{\mathcal{C}\cup\mathcal{A}}(M,M)<F_{\mathcal{C}\cup\mathcal{A}}(R,M)$. As before, spell
 this out as:
-
-\noindent $\sum_{C}P(C)[P(I_{MC}\cap I_{MC})\cdot a_{C}+P(II_{MC}\cap II_{MC})\cdot d_{C}+P(I_{MC}\cap II_{MC})\cdot b_{C}+P(II_{MC}\cap I_{MC})\cdot c_{C}]+\sum_{A}P(A)[P(I_{MA}\cap I_{MA})\cdot a_{A}+P(II_{MA}\cap II_{MA})\cdot d_{A}+P(I_{MA}\cap II_{MA})\cdot b_{A}+P(II_{MA}\cap I_{MA})\cdot c_{A}] < \sum_{C}P(C)[P(I_{RC}\cap I_{MC})\cdot a_{C}+P(II_{RC}\cap II_{MC})\cdot d_{C}+P(I_{RC}\cap II_{MC})\cdot b_{C}+P(II_{RC}\cap I_{MC})\cdot c_{C}]+\sum_{A}P(A)[P(I_{RA}\cap I_{MA})\cdot a_{A}+P(II_{RA}\cap II_{MA})\cdot d_{A}+P(I_{RA}\cap II_{MA})\cdot b_{A}+P(II_{RA}\cap I_{MA})\cdot c_{A}]$.
-\medskip{}
+\begin{align*}
+& \sum_{C}P(C)[P(I_{MC}\cap I_{MC})\cdot a_{C}+P(II_{MC}\cap II_{MC})\cdot d_{C}+P(I_{MC}\cap II_{MC})\cdot b_{C}+P(II_{MC}\cap I_{MC})\cdot c_{C}] \\
++ & \sum_{A}P(A)[P(I_{MA}\cap I_{MA})\cdot a_{A}+P(II_{MA}\cap II_{MA})\cdot d_{A}+P(I_{MA}\cap II_{MA})\cdot b_{A}+P(II_{MA}\cap I_{MA})\cdot c_{A}] \\
+< & \sum_{C}P(C)[P(I_{RC}\cap I_{MC})\cdot a_{C}+P(II_{RC}\cap II_{MC})\cdot d_{C}+P(I_{RC}\cap II_{MC})\cdot b_{C}+P(II_{RC}\cap I_{MC})\cdot c_{C}]\\ 
++ & \sum_{A}P(A)[P(I_{RA}\cap I_{MA})\cdot a_{A}+P(II_{RA}\cap II_{MA})\cdot d_{A}+P(I_{RA}\cap II_{MA})\cdot b_{A}+P(II_{RA}\cap I_{MA})\cdot c_{A}]
+\end{align*}
 
@@
 
-\medskip{}
-\noindent $\sum_{C_{a>d}} P(C)[a_{C} \cdot (P(I_{MC}\cap I_{MC}) + P(I_{MC}\cap II_{MC})- P(I_{RC}\cap I_{MC}) - P(I_{RC}\cap II_{MC})) + b_{C} \cdot  (P(I_{MC}\cap I_{MC}) + P(I_{MC}\cap II_{MC})- P(I_{RC}\cap I_{MC}) - P(I_{RC}\cap II_{MC})) + c_{C} \cdot (P(II_{MC}\cap I_{MC}) +P(II_{MC}\cap II_{MC})- P(II_{RC}\cap II_{MC})) + d_{C} \cdot (P(II_{MC}\cap II_{MC})+P(II_{MC}\cap I_{MC})- P(II_{RC}\cap II_{MC}))]< 0$
-\medskip{}
+\begin{align*} & \textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot (P(I_{MC}\cap I_{MC}) + P(I_{MC}\cap II_{MC})- P(I_{RC}\cap I_{MC}) - P(I_{RC}\cap II_{MC}))\\ & + b_{C} \cdot  (P(I_{MC}\cap I_{MC}) + P(I_{MC}\cap II_{MC})- P(I_{RC}\cap I_{MC}) - P(I_{RC}\cap II_{MC}))\\ & + c_{C} \cdot (P(II_{MC}\cap I_{MC}) +P(II_{MC}\cap II_{MC})- P(II_{RC}\cap II_{MC})) \\ & + d_{C} \cdot (P(II_{MC}\cap II_{MC})+P(II_{MC}\cap I_{MC})- P(II_{RC}\cap II_{MC}))]< 0
+\end{align*}
 
@@
 
-\item[(2)] $\sum_{C_{a<d}} P(C)[a_{C} \cdot (P(I_{MC}\cap I_{MC}) - P(I_{RC}\cap I_{MC})) + b_{C} \cdot  (P(I_{MC}\cap I_{MC}) - P(I_{RC}\cap I_{MC})) + c_{C} \cdot (- P(II_{RC}\cap I_{MC})) + d_{C} \cdot (- P(II_{RC}\cap I_{MC}))] \leq 0$
+\item[(2)] $\sum_{C_{a<d}} P(C)[a_{C} \cdot (P(I_{MC}\cap I_{MC}) - P(I_{RC}\cap I_{MC})) + b_{C} \cdot  (P(I_{MC}\cap I_{MC}) - P(I_{RC}\cap I_{MC})) + c_{C} \cdot (- P(II_{RC}\cap I_{MC})) + d_{C} \cdot (- P(II_{RC}\cap I_{MC}))] \leq 0$;
 

### 2016-01-25 paper/paper.tex
micha minor edits

@@
 evolutionary game theory with evolutionary selection of choice mechanisms in variable
-environments \citep[see related work
-by][]{ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o}.\todo{More references
-  Harley 1981!!!, O Conor \dots}
+environments \citep[see, inter alia, related work
+by][]{Harley1981:Learning-the-Ev,ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o,OConnor2016:Evolving-to-Gen}.
 
@@
 An alternative view on rationality of choice is \emph{adaptationism}
-\citep[e.g.,][]{Anderson1991:Is-human-cognit,ChaterOaksford2000:The-Rational-An,HagenChater2012:Decision-Making}. \todo{more
-  references} Adaptationism aims to explain rational behavior by appeal to evolutionary
-considerations: DMs have acquired choice mechanisms that have proved to be adpative with respect to the variable environment where they have evolved.
-A choice mechanism can be a set of distinct heuristics (the DM's
+\citep[e.g.,][]{Anderson1991:Is-human-cognit,ChaterOaksford2000:The-Rational-An,HagenChater2012:Decision-Making}. Adaptationism
+aims to explain rational behavior by appeal to evolutionary considerations: DMs have acquired
+choice mechanisms that have proved to be adpative with respect to the variable environment
+where they have evolved. A choice mechanism can be a set of distinct heuristics (the DM's
 \emph{adaptive toolbox}) that have little in common
 \citep[e.g.,][]{TverskyKahnemann1981:The-Framing-of-,GigerenzerGoldstein1996:Reasoning-the-F,ScheibehenneRieskamp2013:Testing-the-Ada}. But
-to closely relate to the literature on evolution of preferences and to the philosophical debate about the nature of rational choice in general, we here suggest to
-think of a choice mechanism as a map from choice situations to action choices which includes an
-explicit level of subjective representation of the situation, that we call \emph{subjective representation scheme} (see
-Figure~\ref{fig:ChoiceMechanism}). Specifically, a subjective representation scheme is a general way of forming preferences and
-beliefs about the choice situation, and we are most interested in the question which
-subjective representations are better than others from an evolutionary point of view.
+to closely relate to the literature on evolution of preferences and to the philosophical debate
+about the nature of rational choice in general, we here suggest to think of a choice mechanism
+as a map from choice situations to action choices which includes an explicit level of
+subjective representation of the situation, that we call \emph{subjective representation
+  scheme} (see Figure~\ref{fig:ChoiceMechanism}). Specifically, a subjective representation
+scheme is a general way of forming preferences and beliefs about the choice situation, and we
+are most interested in the question which subjective representations are better than others
+from an evolutionary point of view.
 
@@
 %that we look at here
-although phrased in terms of preference and belief
-representations, map onto well-known classic proposals for rational decision making (see
-Table~\ref{tab:CMs}). In other words, there is also an argument by historical relevance for our
-selection. To see this, we first recapitulate the relevant classics ---to have a handy label,
-we call them \emph{classic rules}--- and then show how they relate to our notion of choice
-mechanism.
+although phrased in terms of preference and belief representations, map onto well-known classic
+proposals for rational decision making (see Table~\ref{tab:CMs}). In other words, there is also
+motivation from historical relevance for our selection. To see this, we first recapitulate the
+relevant classics ---to have a handy label, we call them \emph{classic rules}--- and then show
+how they relate to our notion of choice mechanism.
 
@@
 %fitness. Moreover, 
-non-veridical regret-based preferences representations can not only persist, but even be favored by
+non-veridical regret-based preference representations can not only persist, but even be favored by
 natural selection if agents may have imprecise beliefs.
@@
 
-How do the basic results from the previous section carry over to even more encompassing and richer
-models? Section~\ref{sec:more-types} first introduces further conceptually interesting
-preference types that have been considered in the literature. Section~\ref{sec:n-times-n} then addresses the case of $n \times n$ games for
-$n \ge 2$. Finally, to put our results into a broader perspective,
-Section~\ref{sec:solitary-decisions} ends with a brief comparison of game situations with cases
-of solitary decision making.
+How do the basic results from the previous section carry over to richer models?
+Section~\ref{sec:more-types} first introduces further conceptually interesting preference types
+that have been considered in the literature. Section~\ref{sec:n-times-n} then addresses the
+case of $n \times n$ games for $n \ge 2$. Finally, Section~\ref{sec:solitary-decisions} ends
+with a brief comparison of game situations with cases of solitary decision making.
 
@@
 far. These results confirm basic intuitions about altruistic and competitive types: everybody would like to have an altruistic co-player and nobody
-would like to play with a competitive player. Perhaps more surprisingly, $(\text{alt}, \text{imp})$
+would like to play against a competitive player. Perhaps more surprisingly, $(\text{alt}, \text{imp})$
 come up strictly dominated by $(\text{com}, \text{imp})$, but competitive types themselves are worse off
@@
 simulation runs of the (discrete-time) replicator dynamics on the $8 \times 8$ meta-game from
-Table~\ref{tab:ExpectedFitness_2x2_Full} all end up in population states consisting of only these
+Table~\ref{tab:ExpectedFitness_2x2_Full} end up in population states consisting of only these
 three types in arbitrary proportion.
@@
 We therefore represent maximal uncertainty in two different ways that correspond to the two
-approaches discussed above: a Bayesian uniform measure and an imprecise probability
+approaches discussed in the main text: a Bayesian uniform measure and an imprecise probability
 set. The latter represents uncertainty for players who are not able to narrow down the set of
@@
 Evidence from experimental literature suggests that agents are mostly uncertainty averse
-[REF]. In line with empirical data, we assume that players in the population are uncertainty
-averse and conform to maxmin expected utility. The resulting behavior is then produced by
-maximinimizing the subjective utility given by the player's preference type over the set of
-probabilities given by the belief type.
+\textcolor{red}{[REF]}. In line with empirical data, we assume that players in the population
+are uncertainty averse and conform to maxmin expected utility. The resulting behavior is then
+produced by maximinimizing the subjective utility given by the player's preference type over
+the set of probabilities given by the belief type.
 
@@
 the maximinimizer $(\text{obj}, \text{imp})$ by $M$. Following
-Equation~(\ref{eq:FittnessChoiceMechGamePairwise}), let $F_{\mathcal{G}}(X,Y)$ denotes the of
-choice mechanism $X$ against choice mechanism $Y$ on the possibly restricted class of fitness
-games $\mathcal{G}$.
+Equation~(\ref{eq:FittnessChoiceMechGamePairwise}), let $F_{\mathcal{G}}(X,Y)$ denote the
+expected payoff of choice mechanism $X$ against choice mechanism $Y$ on the possibly restricted
+class of fitness games $\mathcal{G}$.
 
@@
 we have to show that in the class $\mathcal{G}$ of symmetric $2\times2$ games with payoffs
-sampled from a set of i.i.d. values with at least 3 elements in the support, it holds:
+sampled from a set of i.i.d. values with at least 3 elements in the support, it holds that:
 \begin{multicols}{2}
@@
 \noindent We now distinguish between (1) $b=c$, (2) $b>c$, and (3) $b<c$. Notice that either
-(1) or (2), together with $a>d$, implies $I_{RC}$. Then we obtain\footnote{Note that here, when
+(1) or (2), together with $a>d$, implies $I_{RC}$. Then we obtain:\footnote{Note that here, when
   we only have 3 elements in the support, case (2) is impossible, but cases (1) and (3) can
-  occur with positive probability, and this enough for our purpose.}:
+  occur with positive probability, and this enough for our purpose.}
 \begin{itemize}

### 2016-01-29 paper/paperBlinded.tex
PHoS version

--- 2016-01-25 paper/paper.tex
@@
-\documentclass[fleqn,reqno,11pt]{article}
+\documentclass[fleqn,reqno,12pt]{article}
 
@@
 \usepackage{MnSymbol}
-\usepackage{a4wide}
+
+\usepackage{geometry}
+ % \geometry{
+ % a4paper,
+ % left=300mm,
+ % right=250mm,
+ % top=400mm,
+ % bottom=400mm
+ % }
+
+\pagenumbering{gobble} 
+\usepackage[document]{ragged2e}
+
+\doublespacing
 
@@
 \title{Smart Representations: {R}ationality and Evolution in a Richer  Environment}
-\author{Paolo Galeazzi \& Michael Franke} \date{current version: December 19, 2015}
+
+\date{}
 
@@
   subjective representation. We demonstrate the usefulness of this approach by a case study
-  that compares a number of classic proposals of what it means to make a rational choice. Our
+  that compares a number of classic proposals for decision making. Our
   main result is that regret-based preference representations can be evolutionarily selected
@@
 variable environment
-\citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche}. To show that
+\citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche,HammStev12}. To show that
 there is no tension here, this paper introduces a method for reconciling established notions of
@@
 $\theta \mycolon \bigtimes_{j \in N} A_j \rightarrow \mathbb{R}$ is a subjective utility function (the \emph{preference type} of the player), and $e$ is some subjective representation of a player's uncertainty about the co-players'
-behavior (the \emph{belief type} of the player). As already anticipated, we mostly consider two preference types here: the \emph{objective type} maps each game
+behavior (the \emph{epistemic} or \emph{belief type} of the player). As already anticipated, we mostly consider two preference types here: the \emph{objective type} maps each game
 onto its own, true evolutionary payoffs (i.e., $ \theta = \pi_i $); the \emph{regret type} maps each game onto its negative regret
@@
 
-Evidence from experimental literature suggests that agents are mostly uncertainty averse
-\textcolor{red}{[REF]}. In line with empirical data, we assume that players in the population
+Evidence from experimental literature suggests that agents are mostly uncertainty averse \citep[e.g.,][]{TrautKuil16}. In line with empirical data, we assume that players in the population
 are uncertainty averse and conform to maxmin expected utility. The resulting behavior is then

### 2016-02-01 paper/paperBlinded.tex
style changes

@@
 \usepackage{etex}
-\usepackage[nobiblatex]{helpers/mypackages}
+
+\RequirePackage{amsmath}            % Formeln
+\RequirePackage{amsfonts}           % Fonts for Formulas
+\RequirePackage{amssymb}
+\RequirePackage{amsthm}
+\RequirePackage{dsfont}             % double stroke fonts
+\RequirePackage[final]{graphicx}
+\RequirePackage{booktabs}
+\RequirePackage{enumerate}
+\RequirePackage{paralist}
+\RequirePackage[all]{xy}            
+\RequirePackage{url}
+
+\RequirePackage{txfonts} % for strict implication symbols
+\RequirePackage{soul}
+\RequirePackage{relsize} % provides command \relsize{+/-x} for relative
+                     % font size changes
+\RequirePackage[german,english]{babel}
+\RequirePackage[utf8]{inputenc}
+\RequirePackage[T1]{fontenc} 
+\RequirePackage{xypic}
+\RequirePackage{multicol}
+\RequirePackage{subcaption}
+\RequirePackage{tikz}
+\usetikzlibrary{arrows,shapes,automata,backgrounds,petri,fit,decorations.pathmorphing}
+\RequirePackage{units}
+
+\RequirePackage{dialogue}
+
+\RequirePackage{setspace}
+
+\RequirePackage[colorinlistoftodos,color=lightgray,bordercolor=blue,textsize=footnotesize]{todonotes}
+
+\RequirePackage{xspace} % for \xspace in definition of acronyms etc.
+
+\RequirePackage[final,            % override "draft" which means "no nothing"
+            colorlinks,       % rather than outlining them in boxes
+            linkcolor=black,   % override truly awful colour choices
+            citecolor=black,   %   (ditto)
+            urlcolor=black,    %   (ditto)
+            plainpages=false, % to overcome complaints with multiple
+            pdfpagelabels,    % multiple page 1-s due to preface
+            hypertexnames=false % solves warning, but interferes with
+                                % index and \autoref apparently
+            ]{hyperref}
+
 \usepackage[backend=bibtex,natbib=true,style=authoryear-comp,backend=bibtex,doi=false,url=false]{biblatex}
+
 \bibliography{choicePrince,biblio}
-\usepackage{helpers/myenvironments}
-\usepackage{helpers/mycommands}
+
+\newtheoremstyle{Satz}
+   {}                      %Space above
+   {1em}                  %Space below
+   {\normalfont}           %Body font
+   {}                      %Indent amount (empty = no indent,
+                           %\parindent = para indent)
+   {\normalfont}           %Thm head font
+   {.}                     %Punctuation after thm head
+   {.8em}                  %Space after thm head: " " = normal interword
+                           %space; \newline = linebreak
+   {\bfseries\thmname{#1}\thmnumber{ #2}\thmnote{ (#3)}}
+                           %Thm head spec (can be left empty, meaning
+                           %`normal')
+
+\theoremstyle{Satz}
+\newtheorem{theorem}{Theorem} 
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{proposition}{Proposition}
+\newtheorem{fact}{Fact}
+\newtheorem{claim}{Claim} 
+\newtheorem{remark}[theorem]{Remark}
+\newtheorem{exercise}{Exercise} 
+\newtheorem{problem}{Problem}
+\newtheorem{corollary}{Corollary}
+\newtheorem{example}{Example}
+
+\newtheoremstyle{Bsp}
+   {}                      %Space above
+   {1em}                  %Space below
+   {\itshape}           %Body font
+   {}                      %Indent amount (empty = no indent,
+                           %\parindent = para indent)
+   {\normalfont}           %Thm head font
+   {.}                     %Punctuation after thm head
+   {.8em}                  %Space after thm head: " " = normal interword
+                           %space; \newline = linebreak
+   {\thmname{#1}\thmnumber{ #2}\thmnote{ (#3)}}
+                           %Thm head spec (can be left empty, meaning
+                           %`normal')
+\theoremstyle{Bsp}
+% \newtheorem{example}[theorem]{Example}
+
+% Math --------------------
+\newcommand{\set}[1]{\left\{#1\right\}}
+\newcommand{\tuple}[1]{\left \langle #1\right\rangle}
+\newcommand{\card}[1]{\left \lvert \, #1 \, \right\rvert}
+\newcommand{\abs}[1]{\lvert #1 \rvert}
+\newcommand{\setbar}{\ensuremath{\thinspace \mid \thinspace}}
+\newcommand{\probbar}{\ensuremath{\mid}}
+\DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator*{\argmin}{arg\,min}
+\newcommand{\df}{\rightarrow}
+\newcommand{\es}{\emptyset}
+\newcommand{\den}[1]{\left [\! \left [ #1 \right ]\! \right]}
+% \newcommand{\den}[1]{\left \llbracket #1  \right \rrbracket} % this would use fourier package which makes 'cases' environment bad
+\newcommand{\no}{\noindent}
+\newcommand{\hin}{"$\Rightarrow$" }
+\newcommand{\rueck}{"$\Leftarrow$" }
+\newcommand{\exs}{\vspace{.15cm}}
+\newcommand{\pow}[1]{\ensuremath{\mathcal{P}(#1)}}	% Powerset
+\newcommand{\restr}{{\restriction}}
+\newcommand{\implicates}{\ensuremath{\leadsto}}  % arrow for
+                                % implicatures in examples
+\newcommand{\update}[2]{\ensuremath{#1[#2]}}
+\newcommand{\myts}{\ensuremath{\thinspace}}
+\newcommand{\mycolon}{\ensuremath{\thinspace \colon \thinspace}}
+\newcommand{\mydot}{\ensuremath{\thinspace . \thinspace}}
+
+\makeatletter
+\newcommand{\prob}{\@ifstar
+  \simpleprob%
+  \condprob%
+}
+\def\simpleprob(#1){\ensuremath{\Pr(#1)}}
+\def\condprob(#1|#2){\ensuremath{\Pr(#1 \,|\, #2)}}
+\makeatother
+
+% General Text Markup--------------------
+\newcommand{\runex}[1]{\begin{center}#1\end{center}}
+\newcommand{\mydef}[1]{\textsc{#1}}  		% definitions
+\newcommand{\markdef}[1]{\textsc{#1}}  		% definitions; alternative
+\newcommand{\myment}[1]{\emph{#1}}  	% first mentions
+\newcommand{\myword}[1]{\textbf{\texttt{#1}}}	% refering to the word
+\newcommand{\myemph}[1]{\emph{#1}}			% emphasis
+\newenvironment{exnonum}{
+  \begin{list}{}{
+    \setlength{\leftmargin}{2.5em}
+    \setlength{\rightmargin}{2.5em}
+    %\setlength{\itemindent}{-1.5em}
+  }
+}{
+  \end{list}
+}
+
+% Slanted Fractions
+\newcommand{\myslantfrac}[2]{\msf{#1}{#2}}
+\newcommand{\msf}[2]{\ensuremath{\nicefrac{#1}{#2}}}
+\newcommand{\msftext}[2]{\nicefrac{#1}{#2}}
+
+% Symbols for Conditionals
+\newcommand{\cond}{\ensuremath{>}}
+\newcommand{\bicond}{\ensuremath{\Leftrightarrow}}
+\newcommand{\strcondWill}{\ensuremath{\boxRight}}
+\newcommand{\strcondMight}{\ensuremath{\DiamondRight}}
+
+% Signaling Games & IBR
+\newcommand{\sen}{\ensuremath{S}\xspace}		% Sender variable
+\newcommand{\mysen}[1]{\ensuremath{\sen^{#1}}} % Sender of type XYZ
+\newcommand{\rec}{\ensuremath{R}\xspace}		% Receiver variable
+\newcommand{\myrec}[1]{\ensuremath{\rec_{#1}}} % Receiver of type XYZ
+\newcommand{\States}{\ensuremath{T}\xspace}		% Set of States
+\newcommand{\state}{\ensuremath{t}\xspace}		% single states
+\newcommand{\mystate}[1]{\ensuremath{\state_{\text{#1}}}\xspace} %meaningful states
+\newcommand{\Messgs}{\ensuremath{M}\xspace}		% Set of Messages
+\newcommand{\messg}{\ensuremath{m}\xspace}		% single messages
+\newcommand{\mymessg}[1]{\ensuremath{\messg_{\text{#1}}}\xspace} %meaningful messages
+\newcommand{\cost}{\ensuremath\operatorname{C}} % cost function
+\newcommand{\Acts}{\ensuremath{A}\xspace}		% Set of R-actions
+\newcommand{\act}{\ensuremath{a}\xspace}		% single action
+\newcommand{\myact}[1]{\ensuremath{\act_{\text{#1}}}\xspace} %meaningful
+\newcommand{\Worlds}{\ensuremath{W}}		% Worlds
+\newcommand{\world}{\ensuremath{w}}		% single world
+\newcommand{\myworld}[1]{\ensuremath{\world_{\text{#1}}}} %named world
+\newcommand{\util}{\ensuremath{\operatorname{U}}}	% Utility function
+\newcommand{\Util}{\ensuremath{\operatorname{U}}}	% Utility function
+\newcommand{\utils}{\ensuremath{\operatorname{U}}}	% Utility function
+\newcommand{\Utils}{\ensuremath{\operatorname{U}}}	% Utility function
+\newcommand{\RealUtil}{\ensuremath{\operatorname{V}}}	% material payoffs
+\newcommand{\Sstrat}{\ensuremath{\sigma}} % Behav/Probab Sender strategy
+\newcommand{\Sstrats}{\ensuremath{\mathcal{S}}}	% Set of S-strategies
+\newcommand{\Spure}{\ensuremath{s}} % Pure sender strategy
+\newcommand{\Spures}{\ensuremath{\mathsf{S}}} % Set of pure sen strategies
+\newcommand{\Smixed}{\ensuremath{\tilde{s}}} % Mixed sender strategy
+\newcommand{\Smixeds}{\ensuremath{\Delta(\Messgs^\States)}}
+\newcommand{\SpuresW}{\ensuremath{\mathsf{S}}} 
+\newcommand{\SpuresS}{\ensuremath{\mathsf{S}^{{\mathrm{S}}}}}
+\newcommand{\Rstrat}{\ensuremath{\rho}} % Behav/Probab Receiver strategy
+\newcommand{\Rstrats}{\ensuremath{\mathcal{R}}}	% Set of R-Strategies
+\newcommand{\Rpure}{\ensuremath{r}} % Pure receiver strategy
+\newcommand{\Rpures}{\ensuremath{\mathsf{R}}} % Set of pure rec strategies
+\newcommand{\Rmixed}{\ensuremath{\tilde{r}}} % Mixed receiver strategy
+\newcommand{\Rmixeds}{\ensuremath{\Delta(\Acts^\Messgs)}} 
+\newcommand{\RpuresW}{\ensuremath{\mathsf{R}}} 
+\newcommand{\RpuresS}{\ensuremath{\mathsf{R}^{\mathrm{S}}}} 
+\newcommand{\PureBR}{\ensuremath{\operatorname{BR}}} % Set of pure best responses
+\newcommand{\ProbBR}{\ensuremath{\operatorname{BR_{Prob}}}} % Set of mixed best responses
+\newcommand{\bel}{\ensuremath{\pi}}
+\newcommand{\Bels}{\ensuremath{\Pi}}
+\newcommand{\Sbel}{\ensuremath{\pi_{\sen}}}
+\newcommand{\Sbels}{\ensuremath{\Pi_{\sen}}}
+\newcommand{\Rbel}{\ensuremath{\pi_{\rec}}}
+\newcommand{\Rbels}{\ensuremath{\Pi_{\rec}}}
+\newcommand{\EU}{\ensuremath{\operatorname{EU}}} % Expected Utility
+\newcommand{\EV}{\ensuremath{\operatorname{EV}}} % Expected Response Utility
+\newcommand{\BR}{\ensuremath{\operatorname{BR}}} % Best Response
+\newcommand{\QR}{\ensuremath{\operatorname{QR}}} % Quantal Response
+\newcommand{\WBR}{\ensuremath{\text{{\relsize{-1}W}BR}}} % Weak Best Response
+\newcommand{\SBR}{\ensuremath{\text{{\relsize{-1}W}BR}}} % Strong Best Response
+\newcommand{\interpr}{\ensuremath{\delta}} % Interpretation strategy
+
+% OT Stuff
+\newcommand{\Gen}{\ensuremath{\operatorname{Gen}}} % Generator
+\newcommand{\Eval}{\ensuremath{\operatorname{Eval}}} % Evaluator
+\newcommand{\Con}{\ensuremath{\operatorname{Con}}} % Constraints
+\newcommand{\metsuc}{\ensuremath{\succ}} % Symbol for BiOT metric
+\newcommand{\metsuceq}{\ensuremath{\succeq}} % Symbol for BiOT metric
+\newcommand{\Go}[1]{\operatorname{Pool}_{#1}}
+\newcommand{\Oo}[1]{\operatorname{Opt}_{#1}}
+\newcommand{\Bo}[1]{\operatorname{Blo}_{#1}}
+\newcommand{\Gr}[1]{\operatorname{GAM^{\rho}}_{#1}}
+\newcommand{\Or}[1]{\operatorname{OPT^{\rho}}_{#1}}
+\newcommand{\Br}[1]{\operatorname{BLO^{\rho}}_{#1}}
+
+% Abbreviations/Acronyms:
+\newcommand{\acro}[1]{\textsc{#1}\xspace}
+\newcommand{\acros}[1]{\textsc{#1}{\relsize{-1}s}\xspace}
+\newcommand{\bc}{\acro{bc}} % Biscuit Conditional(s)
+\newcommand{\bcs}{\acros{bc}}
+\newcommand{\cbc}{\acro{cbc}} % Counterfactual BCs
+\newcommand{\cbcs}{\acros{cbc}}
+\newcommand{\ibr}{\acro{ibr}} % IBR model
+\newcommand{\iqr}{\acro{iqr}} % IQR model
+\newcommand{\rsa}{\acro{rsa}} % RSA model
+\newcommand{\ot}{\acro{ot}} % BiOT
+\newcommand{\biot}{\acro{b{\relsize{-1}i}ot}} % BiOT
+\newcommand{\tom}{\acro{t{\relsize{-1}o}m}} % ToM
+\newcommand{\fc}{\acro{fc}} % Free Choice
+\newcommand{\cp}{\acro{cp}} % Conditional Perfection
+\newcommand{\uc}{\acro{uc}} % Unconditional Readings
+\newcommand{\pbe}{\acro{pbe}}   % Perfect Bayesian Equil.
+\newcommand{\pbes}{\acros{pbe}}
+\newcommand{\forind}{\acro{fi}} % forward induction
+\newcommand{\tcp}{\acro{tcp}} % truth ceteris paribus
+\newcommand{\cmr}{\acro{cmr}} % credible message rationalizability
+\newcommand{\cm}{\acro{cm}} % credible message (profile) (Rabin)
+\newcommand{\condition}[2]{\acro{#1}{#2}} % conditions 
+\newcommand{\br}{\acro{br}} % best response (property)
+\newcommand{\wbr}{\acro{{\relsize{-1}w}br}} % weak best response (property)
+\newcommand{\sbr}{\acro{{\relsize{-1}s}br}} % strong best response (property)
+\newcommand{\curb}{\acro{curb}} % curb sets
+\newcommand{\gtp}{\acro{gtp}} % game theoretic pragmatics
+\newcommand{\sda}{\acro{sda}} % simplification of disjunctive antecedents
+\newcommand{\decprob}{\ensuremath{\mathcal{D}}}
+\newcommand{\ques}{\ensuremath{\mathfrak{Q}}}
+\newcommand{\vsi}{\acro{vsi}}
+\newcommand{\evsi}{\acro{evsi}}
+\newcommand{\uv}{\acro{uv}}
+\newcommand{\qud}{\acro{qud}}
+\newcommand{\NE}{\acro{ne}}
+\newcommand{\NEs}{\acros{ne}}
+\newcommand{\SNE}{\acro{sne}}
+\newcommand{\SNEs}{\acros{sne}}
+\newcommand{\SG}{\acro{sg}}
+\newcommand{\SGs}{\acros{sg}}
+\newcommand{\KO}{\textsc{ko\relsize{-1}bs}} % Kennedy's observation
+\newcommand{\EVP}{\acro{evp}}    % extreme-value principle
+\newcommand{\illc}{\acro{illc}}
+
+% Evolution
+\newcommand{\EGT}{\acro{egt}}
+\newcommand{\ESS}{\acro{ess}}
+\newcommand{\ESSs}{\acros{ess}}
+\newcommand{\NSS}{\acro{nss}}
+\newcommand{\NSSs}{\acros{nss}}
+\newcommand{\sigsys}{\textsc{SigSys}\xspace} % signaling system
+\newcommand{\sigsyss}{\textsc{SigSys{\relsize{-1}s}}\xspace} % signaling system Plural
+
+\newcommand{\fin}{\rule{0mm}{1mm}\hfill{\rule{1.5cm}{0.2pt}}}
+
+%Properly typeset tilde for URLs
+\def\urltilde{\kern -.15em\lower .7ex\hbox{\~{}}\kern .04em}
+
+% Beamer footnote for references:
+\newcommand{\beamfn}[1]{
+  \vfill
+      \begin{footnotesize}
+        \leftskip 0.1in
+        \parindent -0.1in
+       \hspace{-0.3cm}\rule{2cm}{0.01cm}\\ \vspace{-0.15cm}
+        #1
+      \end{footnotesize}
+}
+
+\newcommand{\myvec}[1]{\ensuremath{\mathbf{#1}}}
+\newcommand{\transpose}[1]{\ensuremath{\operatorname{T}(#1)}}
+\newcommand{\normalize}[1]{\ensuremath{\operatorname{N}(#1)}}
+
+\newcommand{\dn}[1]{\draftnote{#1}}
+\newcommand{\fn}[1]{\footnote{#1}}
+
+\newcommand{\stateunmarked}{\ensuremath{\state}\xspace}
+\newcommand{\statemarked}{\ensuremath{\state^*}\xspace}
+\newcommand{\messgunmarked}{\ensuremath{\messg}\xspace}
+\newcommand{\messgmarked}{\ensuremath{\messg^*}\xspace}
+\newcommand{\actunmarked}{\ensuremath{\act}\xspace}
+\newcommand{\actmarked}{\ensuremath{\act^*}\xspace}
+
+\newcommand{\sunmarked}{\ensuremath{\state}\xspace}
+\newcommand{\smarked}{\ensuremath{\state^*}\xspace}
+\newcommand{\munmarked}{\ensuremath{\messg}\xspace}
+\newcommand{\mmarked}{\ensuremath{\messg^*}\xspace}
+\newcommand{\aunmarked}{\ensuremath{\act}\xspace}
+\newcommand{\amarked}{\ensuremath{\act^*}\xspace}
+
+\newcommand{\ssome}{\mystate{\exists\neg\forall}}
+\newcommand{\sall}{\mystate{\forall}}
+\newcommand{\msome}{\mymessg{some}}
+\newcommand{\mall}{\mymessg{all}}
+\newcommand{\asome}{\myact{\exists\neg\forall}}
+\newcommand{\aall}{\myact{\forall}}
+
+% for repeating examples with gb4e
+
+\newcounter{myexememory}
+\newenvironment{exer}[1]
+{
+\setcounter{myexememory}{\value{exx}}
+\setcounter{exx}{\getrefnumber{#1}}
+\addtocounter{exx}{-1}  
+\begin{exe}
+}
+{
+\end{exe}
+\setcounter{exx}{\value{myexememory}}
+}
+
+\newenvironment{nakedlist}{
+  \begin{list}{\quad}{}
+}
+{
+  \end{list}
+}
+
+\DefineNamedColor{named}{mycol}{cmyk}{0.6,0.6,0,0}
+\DefineNamedColor{named}{mygray}{cmyk}{0.05,0.05,0.05,0.05}
+\DefineNamedColor{named}{mygraylight}{cmyk}{0.017,0.017,0.017,0.017}
+\DefineNamedColor{named}{mycol2}{cmyk}{0.8,0,0.8,0.2}
+
+\newcommand{\mymark}[1]{{\color{mycol}{#1}}}
+
+\DeclareMathOperator{\expo}{exp}
+
+\newcommand{\mygray}[1]{{\textcolor{gray}{#1}}}
+\newcommand{\mycol}[1]{{\textcolor{mycol}{#1}}}
+\newcommand{\mycolh}[1]{{\textcolor{mycol2}{#1}}}
+
+% \usepackage{calc}
+\newsavebox\CBox
+\newcommand\msout[2][0.5pt]{%
+  \ifmmode\sbox\CBox{$#2$}\else\sbox\CBox{#2}\fi%
+  \makebox[0pt][l]{\usebox\CBox}%  
+  \rule[0.5\ht\CBox-#1/2]{\wd\CBox}{#1}}
+
+\newcommand{\greensquare}{\raisebox{1.5pt}{\textcolor{Green}{\Large{\ensuremath{\blacksquare}}}}}
+\newcommand{\bluecircle}{\textcolor{blue}{\Huge{\ensuremath{\bullet}}}}
+\newcommand{\greencircle}{\textcolor{Green}{\Huge{\ensuremath{\bullet}}}}
+
+\newcommand{\greensquareS}{\raisebox{1.5pt}{\textcolor{Green}{\normalsize{\ensuremath{\blacksquare}}}}}
+\newcommand{\greensquareSS}{\raisebox{1.5pt}{\textcolor{Green}{\footnotesize{\ensuremath{\blacksquare}}}}}
+\newcommand{\bluecircleS}{\textcolor{blue}{\Large{\ensuremath{\bullet}}}}
+\newcommand{\greencircleS}{\textcolor{Green}{\Large{\ensuremath{\bullet}}}}
+
+\newcommand{\soc}{\ensuremath{\theta}\xspace}
 
@@
 \usepackage{MnSymbol}
+
+\usepackage{titlesec}
 
@@
 \pagenumbering{gobble} 
-\usepackage[document]{ragged2e}
+% left justification:
+\raggedright
+
+%\usepackage{authblk}
+
+% misc
+\usepackage{graphicx}
+\usepackage{babel}
+\usepackage{amsmath}
+
+\makeatletter
+\makeatother
+
+% Customisations specific to Philosophy of Science:
+
+% paper size, margins, etc:
+\usepackage{geometry}
+\geometry{verbose,letterpaper,tmargin=1.5in,bmargin=1.5in,lmargin=1.25in,rmargin=1in}
 
@@
 
+\renewcommand{\footnotesize}{\normalsize}
+
+\usepackage{setspace} % load setspace before footmisc
+
+\usepackage{footmisc}
+\setlength{\footnotesep}{\baselineskip}
+
+\usepackage{setspace,caption}
+\AtBeginCaption{\doublespacing}
+
+\renewcommand{\footnotelayout}{\doublespacing}
+
 % Figure Captions
@@
 \setlength{\captionmargin}{20pt}
-\renewcommand{\captionfont}{\small}
+\renewcommand{\captionfont}{\normalsize}
 \setlength{\belowcaptionskip}{7pt} % standard is 0pt
@@
 
+%\titleformat{\subsection}
+%       {\normalfont\fontfamily{phv}\fontsize{12}{17}\itshape}{\thesubsection}{1em}{}
+
+\usepackage{titlesec}
+\titleformat*{\section}{\bf}
+\titleformat*{\subsection}{\it}
+\titleformat*{\subsubsection}{\it}
+
+% indentation
+\setlength\parindent{12pt}
+
 \begin{document}
@@
 \begin{abstract}
+\normalsize
   Standard applications of evolutionary game theory look at a single, fixed game and focus on
@@
 \end{abstract}
+
+\newpage
 
@@
 in particular the manner of forming preferences and beliefs about a possibly uncertain world (see
-Figure~\ref{fig:ChoiceMechanism} below). This paper asks: which preference and belief
+figure~\ref{fig:ChoiceMechanism} below). This paper asks: which preference and belief
 representations are ecologically valuable and lead to high fitness?
@@
 
-\section{Rationality, representations \& meta-games}
+\section{Rationality, Representations and Meta-games}
 \label{sec:rati--subj}
@@
 aims to explain rational behavior by appeal to evolutionary considerations: DMs have acquired
-choice mechanisms that have proved to be adpative with respect to the variable environment
+choice mechanisms that have proved to be adaptive with respect to the variable environment
 where they have evolved. A choice mechanism can be a set of distinct heuristics (the DM's
@@
 subjective representation of the situation, that we call \emph{subjective representation
-  scheme} (see Figure~\ref{fig:ChoiceMechanism}). Specifically, a subjective representation
+  scheme} (see figure~\ref{fig:ChoiceMechanism}). Specifically, a subjective representation
 scheme is a general way of forming preferences and beliefs about the choice situation, and we
@@
 
-\section{Classic choice rules and choice mechanisms}
+\section{Classic Choice Rules and Choice Mechanisms}
 \label{sec:basic-notions}
@@
 The case study under consideration strips the generality of a meta-game approach down to a perspicuous
-comparison between four choice mechanisms, summarized in Table~\ref{tab:CMs}.
+comparison between four choice mechanisms, summarized in table~\ref{tab:CMs}.
 % the cross-product of two different preference representations (veridical vs.~regret) and two
@@
 although phrased in terms of preference and belief representations, map onto well-known classic
-proposals for rational decision making (see Table~\ref{tab:CMs}). In other words, there is also
+proposals for rational decision making (see table~\ref{tab:CMs}). In other words, there is also
 motivation from historical relevance for our selection. To see this, we first recapitulate the
@@
 
-\subsection{Classic rules for decision making}
+\subsection{Classic Rules for Decision Making}
 \label{sec:choice-rules}
@@
 $\pi_1(a_k, a_j) = \pi_2(a_j, a_k)$ for all $a_j,a_k \in A_1$. An example is given in
-Figure~\ref{coordgame1}. The numbers give the payoff for the player choosing a row act against
+figure~\ref{coordgame1}. The numbers give the payoff for the player choosing a row act against
 a co-player choosing a column act. Since the game is symmetric, it suffices to give just these
@@
 $\EU(a_i, \mu) := \sum_{\act_{-i} \in \Acts_{-i}} \mu_i(\act_{-i}) \myts \pi_i(a_i, a_{-i})$. For
-the example in Figure~\ref{coordgame1}, an expected utility maximizer would choose act $I$ only if he
+the example in figure~\ref{coordgame1}, an expected utility maximizer would choose act $I$ only if he
 believes that his co-player is going to choose act $I$ with a probability of at least
@@
 a_{-i})$.
-For the example in Figure~\ref{coordgame1}, the minimum of both acts is 0: players choosing by maxmin
+For the example in figure~\ref{coordgame1}, the minimum of both acts is 0: players choosing by maxmin
 rule would be indifferent between acts $I$ and $II$.
@@
 assigns equal probability to all of the co-players' choices. In the coordination game of
-Figure~\ref{coordgame1}, Laplace rule selects act $II$.
+figure~\ref{coordgame1}, Laplace rule selects act $II$.
 
@@
 
-\noindent To illustrate, Figure~\ref{coordgame1reg} shows the pairwise regrets and the regrets for the game of Figure~\ref{coordgame1}. 
+\noindent To illustrate, figure~\ref{coordgame1reg} shows the pairwise regrets and the regrets for the game of figure~\ref{coordgame1}. 
 We have
@@
 functions $\pi_i$ of $G$ with the negative pairwise regrets $-\text{preg}(a_i,a_{-i})$. For
-example, the negative regret transformation of the game in Figure~\ref{coordgame1} would have the
+example, the negative regret transformation of the game in figure~\ref{coordgame1} would have the
 following payoff matrix, i.e., the negatives of the pairwise regrets given in
-Figure~\ref{coordgame1reg}:
+figure~\ref{coordgame1reg}:
 
@@
 objective payoffs, regret minimization considers non-veridical, regret-based subjective
-utilities. As the example of Figure~\ref{coordgame1} shows, different subjective preferences
+utilities. As the example of figure~\ref{coordgame1} shows, different subjective preferences
 can give rise to different choices, all else equal. While maxmin is indifferent
@@
 
-\subsection{Choice mechanisms}
+\subsection{Choice Mechanisms}
 \label{sec:choice-mechanisms}
@@
 ($\gamma,\kappa$), where $\gamma$ is a \emph{subjective representation scheme} and $\kappa$ is
-an \emph{action selection function} (see Figure~\ref{fig:ChoiceMechanism}).
+an \emph{action selection function} (see figure~\ref{fig:ChoiceMechanism}).
 
@@
 considered choice mechanisms are behaviorally equivalent to classic choice rules, as summarized
-in Table~\ref{tab:CMs}.
+in table~\ref{tab:CMs}.
 This means that most of the following results which we interpret as results about the evolutionary fitness of different subjective representations are also relevant for a comparison of the ecological value of classic choice
@@
 
-\section{The model}
+\section{The Model}
 \label{sec:basic-model-1}
 
-\subsection{Simulation results}
+\subsection{Simulation Results}
 \label{sec:simulation-results}
@@
 To demonstrate the usefulness of the meta-game approach, let us concentrate first on a basic
-model that contains the four choice mechanisms from Table~\ref{tab:CMs}. From now on we speak
+model that contains the four choice mechanisms from table~\ref{tab:CMs}. From now on we speak
 of types when we mean pairs $(\text{preference type}, \text{belief type})$, like $(\text{reg}, \text{imp})$ or $(\text{obj}, \text{prc})$.
@@
 to construct meta-game payoffs. Results based on $100,000$ randomly sampled games are given in
-Table~\ref{tab:ExpectedFitness_4Types}.\footnote{Concretely, $100,000$ games were sampled
+table~\ref{tab:ExpectedFitness_4Types}.\footnote{Concretely, $100,000$ games were sampled
   repeatedly by choosing independently four integers between 0 and 10 uniformly at random. For
@@
   action in a given game, we recorded unbiased averages over all selected actions.)  The number
-  in each cell of Table~\ref{tab:ExpectedFitness_4Types} is the average payoff for the choice
+  in each cell of table~\ref{tab:ExpectedFitness_4Types} is the average payoff for the choice
   mechanism listed in the row when matched with the choice mechanism in the column.}
@@
 $(\text{obj}, \text{prc})$ are substituted for one another yield identical results. More
-interestingly, Table~\ref{tab:ExpectedFitness_4Types} shows that $(\text{obj}, \text{imp})$,
+interestingly, table~\ref{tab:ExpectedFitness_4Types} shows that $(\text{obj}, \text{imp})$,
 the maxmin strategy, is strictly dominated by the three other types: in each column (i.e.,
@@
 Next, if we look at the competition between all four types represented in
-Table~\ref{tab:ExpectedFitness_4Types}, $(\text{reg}, \text{imp})$ is no longer evolutionarily
+table~\ref{tab:ExpectedFitness_4Types}, $(\text{reg}, \text{imp})$ is no longer evolutionarily
 stable. Rather, given behavioral equivalence (Fact~\ref{fact:equivalence2x2}), types
@@
 
-\subsection{Analytical results}
+\subsection{Analytical Results}
 \label{sec:analytical-results}
 
-Results based on the single meta game in Table~\ref{tab:ExpectedFitness_4Types} are not fully general and possibly spoiled by random
+Results based on the single meta game in table~\ref{tab:ExpectedFitness_4Types} are not fully general and possibly spoiled by random
 fluctuations in the sampling procedure. Fortunately, for the case of $2 \times 2$ symmetric
@@
 This
-tells us that the main conclusions drawn in the previous section based on the approximated meta-game of Table~\ref{tab:ExpectedFitness_4Types} hold more generally 
+tells us that the main conclusions drawn in the previous section based on the approximated meta-game of table~\ref{tab:ExpectedFitness_4Types} hold more generally 
 for
@@
 
-\subsection{More types}
+\subsection{More Types}
 \label{sec:more-types}
@@
 \footnotesize
+\resizebox{\columnwidth}{!}{
 \begin{tabular}{ccccccccc}
@@
 \end{tabular}    
+}                  
 \caption{Average evolutionary fitness from Monte Carlo simulations of 100,000 symmetric $2 \times 2$ games}
@@
 It is easy to see then that the previous result still obtains for the larger meta-game in
-Table~\ref{tab:ExpectedFitness_2x2_Full}: $(\text{reg}, \text{imp})$,
+table~\ref{tab:ExpectedFitness_2x2_Full}: $(\text{reg}, \text{imp})$,
 $(\text{obj}, \text{prc})$, and $(\text{reg}, \text{prc})$ are still neutrally stable;
 simulation runs of the (discrete-time) replicator dynamics on the $8 \times 8$ meta-game from
-Table~\ref{tab:ExpectedFitness_2x2_Full} end up in population states consisting of only these
+table~\ref{tab:ExpectedFitness_2x2_Full} end up in population states consisting of only these
 three types in arbitrary proportion.
@@
 
-\subsection{More actions}
+\subsection{More Actions}
 \label{sec:n-times-n}
@@
 $n \times n$ symmetric games. Concretely,
-the numbers in Table~\ref{tab:ExpectedFitness_10x10} are averages of evolutionary payoffs obtained in
+the numbers in table~\ref{tab:ExpectedFitness_10x10} are averages of evolutionary payoffs obtained in
 100,000 randomly sampled symmetric games, where each game was sampled by first picking a number of acts
@@
 \end{tabular}  
+}                    
 \caption{Average evolutionary fitness for 100,000 randomly generated $n \times n$ symmetric games with $n$ randomly drawn from $\set{2, \dots, 10}$.}
@@
 strictly dominated by $(\text{reg}, \text{prc})$ and by $(\text{obj}, \text{prc})$ in the
-meta-game from Table~\ref{tab:ExpectedFitness_10x10}. This means that while simple regret minimization
+meta-game from table~\ref{tab:ExpectedFitness_10x10}. This means that while simple regret minimization
 \emph{can} thrive in some evolutionary contexts, there are also contexts where it is
@@
 in such a way that both players hold precise beliefs with probability $p$ and they both have imprecise
-beliefs otherwise. This transforms the meta-game from Table~\ref{tab:ExpectedFitness_10x10} into a
+beliefs otherwise. This transforms the meta-game from table~\ref{tab:ExpectedFitness_10x10} into a
 simpler $4 \times 4$ meta-game in which the payoff obtained for a preference type is the weighted
 average over the payoffs of the choice mechanisms including that preference type in
-Table~\ref{tab:ExpectedFitness_10x10}. Setting $p = 0.98$ for illustration, we get the meta-game in Table~\ref{tab:ExogeneousEpistemics}.
+table~\ref{tab:ExpectedFitness_10x10}. Setting $p = 0.98$ for illustration, we get the meta-game in table~\ref{tab:ExogeneousEpistemics}.
 \begin{table}[]
@@
 
-\subsection{Solitary decisions}
+\subsection{Solitary Decisions}
 \label{sec:solitary-decisions}
@@
 uniformly at random from the available states in the current decision problem. As player types,
-we considered the original cast of four from Table~\ref{tab:CMs}, since altruistic and
+we considered the original cast of four from table~\ref{tab:CMs}, since altruistic and
 competitive types are meaningless in solitary decision situations. As before, the
@@
 approximated by Monte Carlo simulation, the results of which are given in
-Table~\ref{tab:SolitaryDecisions}.
+table~\ref{tab:SolitaryDecisions}.
 
@@
 decision problems with two states and two acts. This shows in the results from
-Table~\ref{tab:SolitaryDecisions} in that the averages for $(\text{reg}, \text{prc})$ and
+table~\ref{tab:SolitaryDecisions} in that the averages for $(\text{reg}, \text{prc})$ and
 $(\text{obj}, \text{prc})$ are identical. But since we included decision problems with more
@@
 
-\section{Background on imprecise probabilistic beliefs}
+\section{Background on Imprecise Probabilities}
 \label{sec:impr-prob-beli}
@@
   Such uncertainty is inherent in situations of strategic interaction. This is quite obvious
-  when such situations have been faced only a few times. (p. 646)
+  when such situations have been faced only a few times. (p.~646)
 \end{quote}
@@
 red (R) or on yellow (Y), while in the second she can bet either on red or black (RB) or on
-yellow or black (YB), as shown in Table \ref{Ellsberg}.
+yellow or black (YB), as shown in table \ref{Ellsberg}.
 
@@
 
-The pattern consistently observed in experimets is:
+The pattern consistently observed in experiments is:
 $f_{{\color{red}R}} \succ f_{{\color{yellow}Y}}$ and
@@
 
-\noindent To show this we use the following partition of $\mathcal{G}$, based on payoffs parameterized as
+\noindent To show this we use the following partition of $\mathcal{G}$, based on payoffs parametrized as
 follows:
@@
 \begin{align*}
-  & \sum_{C \in \mathcal{C}}P(C)[P(I_{RC}\cap I_{RC})\cdot a_{C}+P(II_{RC}\cap II_{RC})\cdot
+   \sum_{C \in \mathcal{C}}P(C) & [P(I_{RC}\cap I_{RC})\cdot a_{C}+P(II_{RC}\cap II_{RC})\cdot
   d_{C}+P(I_{RC}\cap II_{RC})\cdot b_{C}+P(II_{RC}\cap I_{RC})\cdot c_{C}] 
-  \\ + & \sum_{A \in
-    \mathcal{A}}P(A)[P(I_{RA}\cap I_{RA})\cdot a_{A}+P(II_{RA}\cap II_{RA})\cdot
+  \\ + \sum_{A \in
+    \mathcal{A}}P(A) & [P(I_{RA}\cap I_{RA})\cdot a_{A}+P(II_{RA}\cap II_{RA})\cdot
   d_{A}+P(I_{RA}\cap II_{RA})\cdot b_{A}+P(II_{RA}\cap I_{RA})\cdot c_{A}]\\
-  > & \sum_{C \in
-    \mathcal{C}}P(C)[P(I_{RC}\cap I_{MC})\cdot a_{C}+P(II_{RC}\cap II_{MC})\cdot
+  > \sum_{C \in
+    \mathcal{C}}P(C) & [P(I_{RC}\cap I_{MC})\cdot a_{C}+P(II_{RC}\cap II_{MC})\cdot
   d_{C}+P(I_{RC}\cap II_{MC})\cdot c_{C}+P(II_{RC}\cap I_{MC})\cdot b_{C}] \\
-   + & \sum_{A \in
-    \mathcal{A}}P(A)[P(I_{RA}\cap I_{MA})\cdot a_{A}+P(II_{RA}\cap II_{MA})\cdot
+   + \sum_{A \in
+    \mathcal{A}}P(A) & [P(I_{RA}\cap I_{MA})\cdot a_{A}+P(II_{RA}\cap II_{MA})\cdot
   d_{A}+P(I_{RA}\cap II_{MA})\cdot c_{A}+P(II_{RA}\cap I_{MA})\cdot b_{A}]
 \end{align*}
-
 \noindent By Lemma \ref{lemma:probabilities coord-ant} and Lemma \ref{lemma:probabilities
@@
 \end{align*}
-
 \noindent Now let us split into $a>d$ and $a<d$, and consider $a>d$ first.  Notice that, by
@@
   (P(I_{RC}\cap II_{RC}) + P(I_{RC}\cap I_{RC})) \\ 
-  & \ \ \ \ + c_{C} \cdot (P(II_{RC}\cap I_{RC})
+  & \ \ + c_{C} \cdot (P(II_{RC}\cap I_{RC})
   +P(II_{RC}\cap II_{RC})) + d_{C} \cdot (P(II_{RC}\cap II_{RC})+P(II_{RC}\cap I_{RC}))] \\
@@
 \end{align*}
-
 \noindent We now distinguish between two cases: (1) $ a-c = d-b $ and (2) $  a-c \neq d-b $.
@@
 As it will be clear in the following, a positive occurrence of case (2) only is enough for the theorem to hold.}:
+
 \begin{align*} 
@@
 \end{align*}
+that is
 \begin{align*}
@@
 \end{align*}
-\begin{align*}
-\textstyle{\sum_{C_{a>d}}} P(C)[\frac{1}{2}a_{C}+ \frac{1}{2}b_{C} - \frac{1}{2}c_{C} - \frac{1}{2}d_{C}]> 0
-\end{align*}
-
+%\begin{align*}
+%\textstyle{\sum_{C_{a>d}}} P(C)[\frac{1}{2}a_{C}+ \frac{1}{2}b_{C} - \frac{1}{2}c_{C} - \frac{1}{2}d_{C}]> 0
+%\end{align*}
 \noindent Since we have assumed $ a-c = d-b $, the last inequality is not satisfied. We have instead:
@@
 \begin{align*}
-\textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot P(I_{RC}\cap II_{MC}) + b_{C} \cdot  P(I_{RC}\cap II_{MC}) - c_{C} \cdot P(I_{RC}\cap II_{MC}) - d_{C} \cdot P(I_{RC}\cap II_{MC})]> 0
+\textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot P(I_{RC}\cap II_{MC}) + b_{C} \cdot  P(I_{RC}\cap II_{MC}) \\- c_{C} \cdot P(I_{RC}\cap II_{MC}) - d_{C} \cdot P(I_{RC}\cap II_{MC})]> 0
 \end{align*}
@@
 \end{align*}
-
 \noindent When $a>d$, similarly to the above derivation, we get: 
-
 \begin{align*} & \textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot (P(I_{MC}\cap I_{MC}) + P(I_{MC}\cap II_{MC})- P(I_{RC}\cap I_{MC}) - P(I_{RC}\cap II_{MC}))\\ & + b_{C} \cdot  (P(I_{MC}\cap I_{MC}) + P(I_{MC}\cap II_{MC})- P(I_{RC}\cap I_{MC}) - P(I_{RC}\cap II_{MC}))\\ & + c_{C} \cdot (P(II_{MC}\cap I_{MC}) +P(II_{MC}\cap II_{MC})- P(II_{RC}\cap II_{MC})) \\ & + d_{C} \cdot (P(II_{MC}\cap II_{MC})+P(II_{MC}\cap I_{MC})- P(II_{RC}\cap II_{MC}))]< 0
 \end{align*}
-
 \noindent We now distinguish between (1) $b=c$, (2) $b>c$, and (3) $b<c$. Notice that either
@@
 \end{itemize}
-
 \noindent When $a<d$, the derivation proceeds symmetrically and we get: 
-
 \begin{itemize}
@@
 \end{itemize}
-
 \noindent Finally, we can conclude that

### 2016-06-24 paper/rev1_paperBlinded.tex
revision version by Paolo

--- 2016-02-01 paper/paperBlinded.tex
@@
 
+\usetikzlibrary{decorations.pathreplacing}
+\usetikzlibrary{calc}
+
 \title{Smart Representations: {R}ationality and Evolution in a Richer  Environment}
@@
   subjective representation. We demonstrate the usefulness of this approach by a case study
-  that compares a number of classic proposals for decision making. Our
+  that compares a number of classic proposals for decision making. The
   main result is that regret-based preference representations can be evolutionarily selected
@@
 preferences has been subject of recent interest in theoretical economics
-\citep[e.g.,][]{algweib13,DekElyYlan07,RobSam11}. A contribution of this paper is
-to provide a case that questions of preference evolution should take
-variability in uncertainty representation into account as well. As a point in case, we demonstrate
-that if agents have imprecise probabilistic beliefs \citep[e.g.][]{gardsah82,levi74,walley96},
-preference representations in terms of regret can be selected for, even though they may deviate
-from the true, objective fitness that evolutionary selection operates on.
+\citep[e.g.,][]{algweib13,DekElyYlan07,RobSam11}. Here, we argue that questions of preference evolution should take
+variability in uncertainty representation into account as well. In relation to this, 
+the main contributions of this work are essentially three.
+First, we show that the way agents form beliefs, and the type of uncertainty that they entertain in particular, is a key aspect for the evolutionary success.
+Second, we demonstrate
+that if agents have imprecise probabilistic beliefs \citep[e.g.][]{gardsah82,levi74,walley96}, faithful and objective representation in terms of true, real evolutionary fitness can be outperformed by
+subjective (e.g., regret-based) preference representations that deviate
+from the true fitness that natural selection operates on.
+Third, although a few examples along similar lines have recently been introduced (REFERENCES), our approach based on a meta-game model is very uncustomary in the literature, and contributes to widen the methods of evolutionary game theory beyond the traditional single-game framework.
 
@@
 
-Section \ref{sec:rati--subj} reviews different views of rational choice and relates the
-approach we take here to the existing literature. Section \ref{sec:basic-notions} introduces the
-relevant decision- and game-theoretic notions, and
+The paper is organized as follows. Section \ref{sec:rati--subj} reviews different views of rational choice and relates the
+approach we take here to the existing literature. Sections \ref{sec:subj-ut,bel,dec-rules} and \ref{sec:subj-rep,ev-fit} introduce the
+relevant decision-theoretic and game-theoretic notions, while Sections \ref{sec:metagame} and \ref{sec:model} present the model.
 %spells out four choice mechanisms on whose
 %evolutionary competition we zoom in 
-Section~\ref{sec:basic-model-1} presents the
-main results of the paper. Section \ref{sec:extensions} extends the evolutionary analysis by
-introducing more choice mechanisms and alternative models of the environment.
-
-\section{Rationality, Representations and Meta-games}
+The main results of the paper are in Section~\ref{sec:results}, and Section \ref{sec:extensions} extends the evolutionary analysis by
+introducing more choice mechanisms and alternative models of the environment. Finally, Section \ref{sec:conclusion} concludes.
+
+\section{Rationality and Representations}
 \label{sec:rati--subj}
@@
 
-\begin{definition}[Rational choice from maximization of expected utility]
-  \label{def:rationality}
-  Let $S$ be a (finite) set of states and $A$ a (finite) set of actions. Given a
-  probability measure $\mu$ over $S$ and a payoff function
-  $u \mycolon S \times A \rightarrow \mathbb{R} $, an action $a^* \in A$ is rational
-  if it maximizes the \emph{(subjective) expected utility}
-  $\EU(a, \mu) := \sum_{s \in S} \mu(s) \ u(s, a)$.
-\end{definition}
-
 \noindent Expected utility is subjective in the sense that it is a function of subjective
-beliefs $\mu$ and subjective preferences $u$ of the decision maker (DM). To wit, a choice can be
+beliefs and subjective preferences of the decision maker (DM). To wit, a choice can be
 rational, i.e., the best choice from the DM's point of view, even if based on peculiar beliefs
@@
 to closely relate to the literature on evolution of preferences and to the philosophical debate
-about the nature of rational choice in general, we here suggest to think of a choice mechanism
+about the nature of rational choice, we here suggest to think of a choice mechanism
 as a map from choice situations to action choices which includes an explicit level of
-subjective representation of the situation, that we call \emph{subjective representation
-  scheme} (see figure~\ref{fig:ChoiceMechanism}). Specifically, a subjective representation
-scheme is a general way of forming preferences and beliefs about the choice situation, and we
-are most interested in the question which subjective representations are better than others
+\emph{subjective representation} of the situation. Specifically, a subjective representation is a general way of forming preferences and beliefs about the choice situation, and we
+are most interested in the question which subjective representations, and which choice mechanisms in general, are better than others
 from an evolutionary point of view.
+
+\iffalse
 
@@
 \end{figure}
-
-The fitness of a subjective representation scheme is measured in terms of the fitness of a
-choice mechanism that contains it, all else equal. The fitness of a choice mechanism $c$ is the
-expected payoff of $c$ over arbitrary decision situations $D$:
-\begin{align}
-  \label{eq:FittnessChoiceMechSolitary}
-  F(c) = \int P(D) \  \pi_D(c) \text{ d} D \,,
-\end{align}
-where $P(D)$ is the probability (density) of $D$ occurring and $\pi_D(c)$ is the evolutionary payoff of
-the act selected by $c$ in $D$. The probability measure $P(D)$ encodes the statistical
-properties of the environment.
-
-The same logic also applies to game contexts and social decision making. A game $G$ is also a
-choice situation, albeit a more complex one. A choice mechanism $c$ maps $G$ onto an action
-choice in $G$. The fitness of $c$ is then:\footnote{We assume for simplicity of exposition that
-  all games with positive occurrence probability are symmetric two-player games.}
-\begin{align}
-  \label{eq:FittnessChoiceMechGame}
-  F(c) = \int \int P(G) \  P(c') \  \pi_G(c,c') \text{ d} c' \text{ d} G  \,,
-\end{align}
-where $P(G)$ is the probability (density) of game $G$, $P(c')$ is the probability of
-encountering a co-player who uses choice mechanism $c'$ and $\pi_G(c,c')$ is the evolutionary payoff for
-a $c$-player in $G$ against the $c'$-player, given by the actions that $c$
-and $c'$ select in $G$. For the most part, we will focus on the more complex case of game situations. Results about solitary decision making follow from parallel arguments
-(see Section~\ref{sec:extensions}).
-
-\emph{Meta-games} are abstract models for the evolutionary competition between choice
-mechanisms in interactive decision making contexts. The expected payoff for a $c$-player in a random
-encounter with a $c'$-player is the average of payoffs obtained in a random symmetric game $G$ weighted
-by $G$'s occurrence probability:
-\begin{align}
-  \label{eq:FittnessChoiceMechGamePairwise}
-  F(c, c') = \int P(G) \  \pi_G(c,c') \text{ d} G \,.
-\end{align}
-
-\begin{definition}[Meta-game]
-  \label{def:MetaGame}
-  Let $CM$ be a set of choice mechanisms and let $P(G)$ give the occurrence probability of symmetric game
-  $G$ in the environment. The meta-game that captures selection of choice mechanisms in this
-  environment is the one-population evolutionary game with strategies $CM$ and payoff function
-  $\pi \mycolon CM \times CM \rightarrow \mathbb{R}$ such that
-  $\pi(c,c') = F(c,c')$.
-  % = \int P(G) \  \pi_G(c,c') \text{ d} G$.
-\end{definition}
-
-Standard notions of evolutionary game theory can be applied to meta-games as well. A choice
-mechanism $c$ is a strict Nash equilibrium if $F(c,c) > F(c',c)$ for all $c'$; it is
-evolutionarily stable if for all $c'$ either (i) $F(c,c) > F(c',c)$ or (ii) $F(c,c) = F(c',c)$
-and $F(c,c') > F(c',c')$; it is neutrally stable if for all $c'$ either (i) $F(c,c) > F(c',c)$
-or (ii) $F(c,c) = F(c',c)$ and $F(c,c') \ge F(c',c')$
-\citep{Maynard-Smith1982:Evolution-and-t}. Similarly, evolutionary dynamics can be applied to
-meta-games. We will later turn towards replicator dynamics
-\citep{TaylorJonker1978:Evolutionary-St} and replicator mutator dynamics
-\citep[e.g.][]{Nowak2006:Evolutionary-Dy}.
-%\todo{footnote with caveat about agent-level processes}
-
-\section{Classic Choice Rules and Choice Mechanisms}
-\label{sec:basic-notions}
 
@@
 
-\subsection{Classic Rules for Decision Making}
-\label{sec:choice-rules}
-
 The classic literature on rational choice contains a number of proposals for which acts a
@@
 
-A strategic-form game is a tuple $ G=\tuple{ N, (A_i , \pi_i)_{i \in N} }$ with $N$ a finite set of
-players, $A_i$ a finite set of acts and $\pi_i: \bigtimes_{j \in N} A_j \rightarrow \mathbb{R}$ a payoff function for each player $i \in N$.
-Part of this paper will focus on symmetric games with two players. A two-player game is
-symmetric if players have the same action set, $A_1 = A_2$, and payoffs are symmetric:
-$\pi_1(a_k, a_j) = \pi_2(a_j, a_k)$ for all $a_j,a_k \in A_1$. An example is given in
-figure~\ref{coordgame1}. The numbers give the payoff for the player choosing a row act against
-a co-player choosing a column act. Since the game is symmetric, it suffices to give just these
-numbers.
-
-Rational choice from maximization of expected utility, as given in
-Definition~\ref{def:rationality}, applies to games as follows. To say which acts are rational,
-it requires specifying a precise probabilistic belief of DM. Let $A_{-i} := \bigtimes_{j \neq i} A_j$ be
-the set of all \emph{profiles} of acts for all players except $i$. If player $i$ has a belief
-$\mu_i \in \Delta(A_{-i})$ about the behavior of his co-players, he chooses rationally only if
-his choice $a^*_i$ maximizes expected utility
-$\EU(a_i, \mu) := \sum_{\act_{-i} \in \Acts_{-i}} \mu_i(\act_{-i}) \myts \pi_i(a_i, a_{-i})$. For
-the example in figure~\ref{coordgame1}, an expected utility maximizer would choose act $I$ only if he
-believes that his co-player is going to choose act $I$ with a probability of at least
-$\nicefrac{2}{3}$.
-
-Perhaps the most well-known classic rule that does not require precise probabilistic
-beliefs is the \emph{maxmin rule}. It prescribes to choose act $\act^*$ only if it
-maximizes payoffs for all worst case scenarios:
-$\act^* \in \argmax_{a_i \in \Acts_i} \min_{a_{-i} \in \Acts_{-i}} \pi_i(a_{i},
-a_{-i})$.
-For the example in figure~\ref{coordgame1}, the minimum of both acts is 0: players choosing by maxmin
-rule would be indifferent between acts $I$ and $II$.
-
-\emph{Laplace rule} selects $\act^*$ if
-$\act^* \in \argmax_{a_{i} \in \Acts_{i}} \sum_{a_{-i}} \pi(a_{i}, a_{-i})$.
-Laplace rule is equivalent to expected utility maximization under a \emph{flat belief} that
-assigns equal probability to all of the co-players' choices. In the coordination game of
-figure~\ref{coordgame1}, Laplace rule selects act $II$.
-
-The final classic rule that is relevant for our purposes is \emph{regret
-  minimization}. The notion of regret in decision theory dates back at least to the work by
-\citet{Savage1951:The-theory-of-s}, and has later been developed by \citet{bell82}, \citet{fish82} and \citet{loosug82} independently. Lately,
+A \emph{choice mechanism} is a map from choice situations to action choices that contains an explicit level, in terms of preferences and beliefs, of subjective representation of
+the choice situation. Concretely, let us think of a choice mechanism as a pair of functions
+($\gamma,\kappa$), where $\gamma$ is a \emph{subjective representation scheme} and $\kappa$ is
+an \emph{action selection function} (see figure~\ref{fig:ChoiceMechanism}).
+
+\noindent This means that objective and regret types are behaviorally indistinguishable, as long as both hold precise beliefs. 
+%This will be central in understanding later results. 
+On the other hand, if paired with imprecise beliefs, different behavioral predictions
+arise.
+
+In the following, we assume that agents are maximally uncertain, so that precise types have a
+(singleton set containing a) uniform probability measure
+$\overline{\mu} \in \Delta(\Acts_{-i})$ and imprecise types entertain all probabilistic beliefs
+about the co-players' behavior $\overline{\Gamma} = \Delta(\Acts_{-i})$. In that case, the
+considered choice mechanisms are behaviorally equivalent to classic choice rules, as summarized
+in table~\ref{tab:CMs}.
+This means that most of the following results which we interpret as results about the evolutionary fitness of different subjective representations are also relevant for a comparison of the ecological value of classic choice
+rules.
+
+\fi
+
+\section{Subjective Utilities, Beliefs and Decision Rules} \label{sec:subj-ut,bel,dec-rules}
+
+We view a choice mechanism as the combination of three different things: a \textit{subjective utility} (or preference), a \textit{subjective belief} and a \textit{decision rule}.
+In general, the agent's action choice will depend both on the agent's utility at different possible outcomes of the choice situation and on the agent's beliefs about the realization of these outcomes.
+The decision rule then combines the agent's subjective utility and belief, and dictates how the agent should act in case of a choice situation whose consequences are uncertain.
+Therefore, a decision rule is a function that associates an action choice with the agent's utility and beliefs:
+$$ \text{Decision Rule: Utility }\times\text{ Beliefs } \rightarrow \text{ Actions.}  $$
+The utility of an agent can be formally expressed by a function $u:W \times A \rightarrow \mathbb{R} $, where $A$ stands for a (finite) set of actions available to the agent and $W$ is a (finite) set of possible states of the world.
+There are many different ways to describe beliefs, but here we assume that the agent's beliefs are represented in terms of a (possibly singleton) set of probability functions $\Gamma \subseteq \Delta(W) $ over the possible states of the world.
+In line with this definition, we can consider different decision rules, such as:
+\begin{enumerate}
+
+\item \textbf{Maxmin}: $$ a^*(u,\Gamma)= \argmax_{a \in A} \min_{\mu \in \Gamma} \sum_{w\in W} u(w,a)  \mu(w).$$
+
+\item \textbf{Maximax}: $$ a^*(u,\Gamma)= \argmax_{a \in A} \max_{\mu \in \Gamma} \sum_{w\in W} u(w,a)  \mu(w).$$
+
+\item \textbf{Laplace rule}: $$ a^*(u,\Gamma)= \argmax_{a \in A} \sum_{w\in W} \frac{1}{|W|}  u(w,a) .$$
+
+\item \textbf{Expected utility maximization} (for $\Gamma$ singleton): $$ a^*(u,\Gamma)= \argmax_{a \in A} \sum_{w\in W} u(w,a)  \mu(w).$$
+
+\end{enumerate}
+
+It is worth noticing that both maxmin and maximax boil down to expected utility maximization when the set  $\Gamma$ is a singleton, and in turn expected utility maximization reduces to Laplace rule when the belief $\mu$ is a uniform probability over the states.
+
+\section{Subjective Representations and Evolutionary Fitness} \label{sec:subj-rep,ev-fit}
+
+For a choice mechanism to prescribe an action, the decision rule  needs to be given a specific subjective utility and belief as input, as described in the previous section.
+We then call \textit{subjective representation} of the decision problem the pair $(u,\Gamma)$ of a subjective utility and a subjective belief.
+In other words, a subjective representation is a general way of forming preferences and beliefs about the choice situation.
+
+The literature on evolution of preferences (REFERENCES) mainly focuses on the evolutionary selection of subjective utilities uniquely.
+Instead, it will be clear from our model that different subjective beliefs may have a fundamental role in determining the evolutionary success of subjective utilities, and therefore the interplay between utilities and beliefs needs to be taken into account explicitly.
+So, here we
+are most interested in the question which subjective representations are better than others
+from an evolutionary point of view. In order to investigate this issue we are going to use the machinery of evolutionary game theory.
+
+A game is an interactive decision situation. 
+For a given game $G=\langle N, (A_i,\pi^G_i)_{i \in N} \rangle$, let us denote the evolutionary payoff, or \textit{fitness}, of player $i$ by the function $\pi^G_i: \Pi_{i \in N} A_i \rightarrow \mathbb{R}$, where $A_i$ is player $i$'s (finite) set of actions.
+For simplicity of exposition we assume that
+  all games that are played are symmetric two-player games, that is, games such that: $N:=\{1,2\}$, $A_1 = A_2 $, and $\pi^G_1(a_1, a'_2)= \pi^G_2(a'_1, a_2)=:\pi^G(a,a')$.\footnote{Since payoff functions are symmetric, we will simply write $\pi^G(a, a')$ for $\pi^G_1(a_1, a'_2)$ and $A:=A_1=A_2$, as usual.
+However, notice that all the definitions and results can be extended to more general cases.} Then, the evolutionary fitness of a subjective representation $(u,\Gamma)$ is measured in terms of the fitness of a
+choice mechanism that contains it, all else equal. 
+Formally, the fitness of a choice mechanism $c$ against choice mechanism $c'$ in a symmetric two-player game $G=\langle \{1,2\}, A, \pi^G \rangle$ is the
+expected payoff of $c$ against $c'$ in $G$:
+
+$$
+ F_G(c,c')= \pi^G(a_c^*(u^G,\Gamma),a_{c'}^*(u^G,\Gamma)), \footnote{Whenever a choice mechanism would not select a unique
+  action, we assume that the player chooses one of the equally optimal actions at random.
+I.e., $F_G(c,c')= \sum_{a \in a_c^*(u^G,\Gamma)} \sum_{a' \in a_{c'}^*(u^G,\Gamma)} \frac{1}{|a_c^*(u^G,\Gamma)|} \frac{1}{|a_{c'}^*(u^G,\Gamma)|} \pi^G(a,a')$.}
+$$
+where $a^*_c$ is the decision rule of choice mechanism $c$.
+Given the game theoretic setting, the subjective utility $u$ is now a function $u^G:A \times A \rightarrow \mathbb{R}$, and the subjective belief $\Gamma$ is a set of probability functions over the co-player's actions, $ \Gamma \subseteq \Delta(A) $.
+
+However, studying the fitness and the evolutionary selection of different choice mechanisms by the use of a fixed, single game may look like a rather restrictive perspective and possibly biased by the choice of the particular game.
+To avoid these limitations, we extend the standard single-game framework of evolutionary game theory by considering a \textit{class} of possible games that can be played within a population.
+Although not completely novel (seeREFERENCES), this approach has started being investigated only very recently, and we maintain that it can shed new light on the evolution of behavior, and it can open to much broader perspectives on evolutionary game theory in general.
+
+\section{The Meta-Game} \label{sec:metagame}
+
+The ground for the evolutionary competition of choice mechanisms will consist of a class $\mathcal{G}$ of possible two-player symmetric games, together with a probability measure $P_{\mathcal{G}}(G)$ for the occurrence probability of game $G \in \mathcal{G}$.
+In more biological terms, the probability measure $P_{\mathcal{G}}$ encodes the statistical
+properties of the environment.
+We then call \textit{meta-game} the tuple $ MG=\langle CM, \mathcal{G}, P_{\mathcal{G}},F \rangle$, where $CM$ is a set of choice mechanisms, $\mathcal{G}$ is a class of possible games, $P_{\mathcal{G}}(G)$ is the probability of game $G$ to occur, and $F:CM \times CM \rightarrow \mathbb{R}$ is the fitness function, defined as:
+\begin{align}
+  \label{eq:FittnessChoiceMechGamePairwise}
+  F(c, c') = \int P_{\mathcal{G}}(G) \  F_G(c,c') \text{ d} G \,.
+\end{align}
+Hence, $F(c,c')$ determines the evolutionary payoff of choice mechanism $c$ against $c'$ in the meta-game.
+The set $CM$ is though of as the set of choice mechanisms present within a given population that is playing the games from the class $\mathcal{G}$.
+Consequently, it is possible to compute the average fitness of $c$ against the population, that is given by:
+\begin{align}
+  \label{eq:FittnessChoiceMechGame}
+  F(c) = \int P_{M}(c') \ F(c,c') \text{ d} c' = \int \int P_{\mathcal{G}}(G) \  P_{M}(c') \  F_G(c,c') \text{ d} c' \text{ d} G  \,,
+\end{align}
+where $P_{M}(c')$ is the probability of
+encountering a co-player with choice mechanism $c'$.
+
+Meta-games are then abstract models for the evolutionary competition between choice
+mechanisms in interactive decision making contexts.
+Standard notions of evolutionary game theory apply to meta-games as well. A choice
+mechanism $c$ is a strict Nash equilibrium if $F(c,c) > F(c',c)$ for all $c'$; it is
+evolutionarily stable if for all $c'$ either (i) $F(c,c) > F(c',c)$ or (ii) $F(c,c) = F(c',c)$
+and $F(c,c') > F(c',c')$; it is neutrally stable if for all $c'$ either (i) $F(c,c) > F(c',c)$
+or (ii) $F(c,c) = F(c',c)$ and $F(c,c') \ge F(c',c')$
+\citep{Maynard-Smith1982:Evolution-and-t}. Similarly, evolutionary dynamics can be applied to
+meta-games. We will later turn towards replicator dynamics
+\citep{TaylorJonker1978:Evolutionary-St} and replicator mutator dynamics
+\citep[e.g.][]{Nowak2006:Evolutionary-Dy}.
+%\todo{footnote with caveat about agent-level processes}
+
+\section{The Model} \label{sec:model}
+
+At first, the main subjective utilities that are going to compete against each other for the survival of the fittest are essentially two:
+\begin{enumerate}
+\item the \textit{objective} utility, defined by: for all $G \in \mathcal{G}$,
+$$\text{obj}^G(a,a')=\pi^G(a,a');$$
+\item the \textit{regret}, defined by: for all $G \in \mathcal{G}$,
+$$\text{reg}^G(a,a') =\pi^G(a,a')- \max_{a''\in A} \pi^G(a'',a').$$
+\end{enumerate}
+
+For a start, the subjective beliefs that we take into consideration are also two:
+\begin{enumerate}
+\item $prc$: a precise uniform belief $\overline{\mu}$ such that $\overline{\mu}(a)=\frac{1}{|A|}$ for all $a\in A$;
+\item $imp$: a maximally imprecise belief $\overline{\Gamma}=\Delta(A)$.
+\end{enumerate}
+
+Although a thorough discussion of this issue goes beyond the scope of this work, let us say that these two kinds of belief underlie two different and alternative views on uncertainty.
+In front of uncertain events, a strict Bayesian will always form a precise belief, specified by a \textit{single} probability $\mu$.
+In the absence of any information about future uncertain events, the Bayesian would then invoke the \textit{principle of insufficient reason}, and accordingly choose a uniform probability over the possible outcomes.
+On the contrary, more recently many authors (REFERENCES) argued against the obligation of representing a belief by means of a single probability measure, opposite to the Bayesian prescriptions.
+They argue instead in favor of a more general account, according to which uncertainty can be unmeasurable, and represented by a (closed and convex) set of probabilities.
+This line of thought has been originated in decision theory by the famous Ellsberg's paradoxes (REF), and appears extremely relevant
+in game-theoretical contexts too. Indeed, in a recent paper \citet{BattCerrMM15} write:
+
+\begin{quote}
+  Such uncertainty is inherent in situations of strategic interaction. This is quite obvious
+  when such situations have been faced only a few times. (p.~646)
+\end{quote}
+
+\noindent In evolutionary game theory, for instance, players will obviously face
+uncertainty about the composition of the population that they are part of, and consequently
+about the co-player that they are randomly paired with at each round and about the co-player's
+action. In case of complete lack of information, a non-Bayesian player would thus entertain maximal unmeasurable uncertainty, i.e., a maximally imprecise belief. 
+As already anticipated,  we will see that the way agents can form beliefs, and the possibility of holding imprecise beliefs in particular, may have a fundamental impact on their evolutionary success.
+
+As for the decision rule, we assume that the players use the maxmin rule. This is in line with most of the representation
+results of decision making under uncertainty \citep[e.g.,][]{gilsch89,KlibMarMuk05,GhirMar02},
+and seems justified by empirical observations too.
+Ellsberg's paradoxes are prominent examples (\citet{ells61}), and evidence from experimental literature suggests that agents are mostly uncertainty averse \citep[e.g.,][]{TrautKuil16}.
+
+Finally, note that when the maxmin rule acts on subjective representation (obj, imp), the generated behavior corresponds to the classic maxmin (REF:vNM).
+When the maxmin rule acts on subjective representation (reg, imp), the agent's behavior is known as \textit{regret minimization}.
+The notion of regret in decision theory dates back at least to the work by
+\citet{Savage1951:The-theory-of-s}, and has later been developed by \citet{bell82}, \citet{fish82} and \citet{loosug82} independently. Recently,
 \citet{HalpernPass2012:Iterated-Regret} showed how the use of regret minimization can give
 solutions to game theoretical-puzzles (like the Traveller's dilemma and the Centipede game) in a way that is closer to
-everyday intuition and empirical data. In this paper the notion of regret is defined as in
-\citet{HalpernPass2012:Iterated-Regret}:
-
-\begin{definition}[Regret, Regret Minimization] \label{defn:regret} Given a game
-  $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the \emph{pairwise regret} of player $i$'s
-  act $a_i$ against profile $a_{-i}$ is
-  $\text{preg}(a_i,a_{-i}):= \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $, where
-  $a_i^\$ \in \argmax_{a_i \in A_i} \pi_i(a_i, a_{-i})$ denotes $i$'s best reply to the
-  co-players' actions $a_{-i}$. The \emph{regret} of $a_i$ is then
-  $\text{reg}(a_i):= \text{max}_{a_{-i}\in A_{-i}} \text{preg}(a_i,a_{-i}) $. An
-  action $a^{*}_i $ is regret minimizing if
-  $a^{*}_i \in \text{argmin}_{a_i} \text{max}_{a_{-i}} \text{preg}(a_i,a_{-i})$.
-\end{definition}
-
-\noindent To illustrate, figure~\ref{coordgame1reg} shows the pairwise regrets and the regrets for the game of figure~\ref{coordgame1}. 
-We have
-$\text{reg}(I)=2$, because $\text{preg}(I,II)=2$, whereas $ \text{preg}(I,I)=0 $. With the same reasoning, $\text{reg}(II)=1$. A regret minimizer would therefore choose act $II$.
-
+everyday intuition and empirical data. In this paper the notion of regret defined earlier is the same as in
+\citet{HalpernPass2012:Iterated-Regret}. Two facts stem from these observations.
+The first is related to our focus on different types of uncertainty that players may entertain.
+\begin{fact} \label{fact:maxEU-minReg} 
+%Under an identical precise (singleton set) belief, the
+%  acts selected by maximization of expected evolutionary payoff in game $G$ are exactly the acts selected
+%  by the maximization of expected utility for the negative regret transformation of $G$
+Under any identical precise (Bayesian) belief, maximization of expected evolutionary payoff and minimization of expected regret are behaviorally equivalent.
+%\citep[e.g.,][]{HalpernPass2012:Iterated-Regret}.
+\end{fact}
+\noindent The second fact highlights another behavioral equivalence, which we will make use of shortly in the following section.
+\begin{fact} \label{fact:equivalence2x2} In the class of $2 \times 2$ symmetric games, the acts
+  selected by Laplace rule are exactly the acts selected by regret minimization.
+\end{fact}
+
+\subsection{Example}
+Consider the coordination game in evolutionary payoffs $G$ depicted in figure \ref{coordgame1}.
+Since the game is symmetric, it suffices to specify the payoffs for the row player.
+Figure \ref{coordgame1} also represents the objective utility $\text{obj}^G$, since $\text{obj}^G= \pi^G$ by definition, whereas figure \ref{coordgame1reg} pictures the representation of $G$ in terms of regret-based utilities.
+While classic maxmin is indifferent
+between $I$ and $II$ (figure \ref{coordgame1}), regret minimization uniquely selects $II$ (figure \ref{coordgame1reg}).
 \begin{figure}
-
+\begin{center}
   \begin{subfigure}[b]{0.3\textwidth}
@@
     \end{tabular}
-    \caption{Coordination game $G^C$}
+    \caption{Coordination game $G$.}
     \label{coordgame1}
@@
     \centering
-    \begin{tabular}{ccc|c}
-      \toprule
-      & $\text{preg}( \cdot, I)$ & $\text{preg}(\cdot, II)$ & $\text{reg}(\cdot)$ \\
-      \midrule
-      I  & 0 & 2 & 2 \\ 
-      II & 1 & 0 & 1\\
-      \bottomrule
-    \end{tabular}
-    \caption{Pairwise regrets and regrets}
-    \label{coordgame1reg}
-  \end{subfigure}
-  \caption{A coordination game (left) and regrets associated with the row player's acts (right).}
-    \label{coordgame1mainFig}
-\end{figure}
-
-% \begin{example}[The Traveller's Dilemma \citep{HalpernPass2012:Iterated-Regret}]
-% \label{example:TravelersDilemma}
-% Let us now consider the Traveller's Dilemma case. The story behind the game goes as
-% follows. There are two travellers, Ann and Bob, who lost their luggages. Ann and Bob had
-% exactly the same luggage and they had insured the luggages with the same insurance company. The
-% insurance policy is that the two travellers have to separately claim a certain amount between
-% 2\$ and 100\$ for the reimbursement, and if they both claim the same amount then they will be
-% reimbursed by that amount. Otherwise, if one of them claims more than the other, then the one
-% who claimed the higher amount will get the lower amount minus 2\$, while the one who claimed
-% the lower amount will get what (s)he claimed plus 2\$. The game is symmetric, and the payoff
-% function for both players is:
-% \begin{align*}
-%   \pi_i(a_i,a_{-i}) = \begin{cases} a_i \text{ \hspace{1cm} if } a_i = a_{-i} \\ a_i + 2 \text{
-%       \hspace{.4cm} if } a_i < a_{-i} \\ a_{-i} -2 \text{ \hspace{.25cm} if } a_{-i} <
-%     a_i \end{cases}
-% \end{align*}
-% By a simple computation we have:  $\forall a_i \in \lbrace 96\$, ..., 100\$ \rbrace \text{, }
-% \text{reg}(a_i)=3 $ and $\forall a_i \in \lbrace 2\$, ..., 95\$ \rbrace \text{, }
-% \text{reg}(a_i)>3$. If we now eliminate all the actions that do not minimize regret in the
-% first place and iterate the regret minimization only on the action set $\lbrace 96\$, ...,
-% 100\$ \rbrace$, we get that 97\$ is the action that minimize regret. Indeed, $\text{reg}(97)=2$
-% and $\forall a_i \in \lbrace 96\$, 98\$, 99\$, 100\$ \rbrace \text{, } \text{reg}(a_i)=3
-% $. Hence, one step of regret minimizing reasoning eliminates all the actions smaller than 96\$,
-% and if we iterate the process once more the unique outcome is 97\$. Finally, it is worth
-% noticing that the only rationalizable equilibrium of the game corresponds to the outcome
-% $(2,2)$, that is consequently the only Nash equilibrium, the only perfect equilibrium, and the
-% only sequential equilibrium of the game.
-
-% \begin{itemize}
-% \item \textcolor{red}{add here:}
-%   \begin{itemize}  
-%   \item outcome of rationalizability (max-EU)
-%   \item outcome of maxmin rule
-%   \item outcome of Laplace rule
-%   \end{itemize}
-
-% \end{itemize}
-
-%  $ \medsquare $
-
-% \end{example}
-
-Regret minimization is intimately related to the maxmin rule. Let the \emph{negative regret
-  transformation} of a strategic game $G$ be the game $G^r$ derived from $G$ by replacing the payoff
-functions $\pi_i$ of $G$ with the negative pairwise regrets $-\text{preg}(a_i,a_{-i})$. For
-example, the negative regret transformation of the game in figure~\ref{coordgame1} would have the
-following payoff matrix, i.e., the negatives of the pairwise regrets given in
-figure~\ref{coordgame1reg}:
-
-\begin{center}
     \begin{tabular}{ccc}
@@
     \end{tabular}
+    \caption{Regret-based representation of $G$.}
+    \label{coordgame1reg}
+  \end{subfigure}
+  \caption{A coordination game (left) and the associated regret representation (right).}
+    \label{coordgame1mainFig}
     \end{center}
-
-\noindent Then, for any game $G$, acts selected by maxmin rule for the negative regret transformation of $G$ are
-always exactly the acts selected by regret minimization for the original game $G$.
-This means that we can think of the maxmin rule and regret minimization as essentially the same
-action selection function on different subjective representations of preferences: while maxmin considers actual
-objective payoffs, regret minimization considers non-veridical, regret-based subjective
-utilities. As the example of figure~\ref{coordgame1} shows, different subjective preferences
-can give rise to different choices, all else equal. While maxmin is indifferent
-between $I$ and $II$, regret minimization uniquely selects $II$.
-
-In sum, classic proposals for rational decision making are normative prescriptions of action choices
-for DM. Such prescriptions may rest on implicit assumptions about what DM
-believes (e.g., when interpreting Laplace rule as expected utility maximization under flat beliefs). They may
-also make implicit assumptions about what DM prefers (e.g., when considering regret-based preferences). This is rather messy. To disentangle, we rephrase all the above in terms of choice mechanisms.
-
-\subsection{Choice Mechanisms}
-\label{sec:choice-mechanisms}
-
-A \emph{choice mechanism} is a map from choice situations to action choices that contains an explicit level, in terms of preferences and beliefs, of subjective representation of
-the choice situation. Concretely, let us think of a choice mechanism as a pair of functions
-($\gamma,\kappa$), where $\gamma$ is a \emph{subjective representation scheme} and $\kappa$ is
-an \emph{action selection function} (see figure~\ref{fig:ChoiceMechanism}).
-
-The subjective representation scheme $\gamma_i$ of agent $i$ is a function that
-takes a game $G = \tuple{ N, (A_i , \pi_i)_{i \in N} }$ and maps it onto
-$\gamma_i(G) = (\theta, e)$ where
-$\theta \mycolon \bigtimes_{j \in N} A_j \rightarrow \mathbb{R}$ is a subjective utility function (the \emph{preference type} of the player), and $e$ is some subjective representation of a player's uncertainty about the co-players'
-behavior (the \emph{epistemic} or \emph{belief type} of the player). As already anticipated, we mostly consider two preference types here: the \emph{objective type} maps each game
-onto its own, true evolutionary payoffs (i.e., $ \theta = \pi_i $); the \emph{regret type} maps each game onto its negative regret
-transformation (i.e., $ \theta = -\text{preg} $). We also consider two belief types: the
-\emph{precise type} represents uncertainty about the co-players in a single probability measure
-$\mu \in \Delta(\Acts_{-i})$; the \emph{imprecise type}
-represents uncertainty as a set of probability measures $\Gamma \subseteq \Delta(\Acts_{-i})$.
-It is convenient to conceptualize precise beliefs as a special case of imprecise beliefs by
-looking at $\mu$ as a stand-in for the singleton set $\set{\mu}$.
-The action selection function $\kappa_i(\gamma_i(G)) \subseteq A_i$ that we consider here is \emph{maximinimization of expected utility} (see Appendix~\ref{sec:impr-prob-beli} for motivations).
-
-\begin{definition}[Maximinimization of expected utility]
-  \label{def:maxminSEU}
-  Fix a game $G$. Let agent $i$'s subjective representation scheme
-  $\gamma_i(G) = (\theta, e)$ be such that $\theta$ is $i$'s subjective utility function and $e \subseteq \Delta(\Acts_{-i})$ is a (possibly singleton) set of probability measures.
-Agent $i$'s expected utility for act $a_{i}$ and belief
-  $\mu \in e$ is
-  $\EU(a_{i}, \mu) = \sum_{a_{-i} \in \Acts_{-i}} \mu(a_{-i}) \theta(a_{i},
-  a_{-i})$.
-  Act $a_{i}^*$ is selected by maximinimization of expected utility iff
-  $a_{i}^* \in \arg \max_{a_{i} \in \Acts_{i}} \min_{\mu \in e} \EU(a_{i}, \mu)$.
-\end{definition}
-
-\iffalse
-\begin{fact} \label{fact:singleton probability set}
-Maximinimization under a precise (singleton set) belief is just standard
-maximization of expected utility (Definition~\ref{def:rationality}).
-\end{fact}
-\fi
-
-\begin{fact} \label{fact:maxEU-minReg} 
-%Under an identical precise (singleton set) belief, the
-%  acts selected by maximization of expected evolutionary payoff in game $G$ are exactly the acts selected
-%  by the maximization of expected utility for the negative regret transformation of $G$
-Under an identical precise (singleton set) belief, maximization of expected evolutionary payoff and minimization of expected regret coincide. %\citep[e.g.,][]{HalpernPass2012:Iterated-Regret}.
-\end{fact}
-
-\noindent This means that objective and regret types are behaviorally indistinguishable, as long as both hold precise beliefs. 
-%This will be central in understanding later results. 
-On the other hand, if paired with imprecise beliefs, different behavioral predictions
-arise.
-
-In the following, we assume that agents are maximally uncertain, so that precise types have a
-(singleton set containing a) uniform probability measure
-$\overline{\mu} \in \Delta(\Acts_{-i})$ and imprecise types entertain all probabilistic beliefs
-about the co-players' behavior $\overline{\Gamma} = \Delta(\Acts_{-i})$. In that case, the
-considered choice mechanisms are behaviorally equivalent to classic choice rules, as summarized
-in table~\ref{tab:CMs}.
-This means that most of the following results which we interpret as results about the evolutionary fitness of different subjective representations are also relevant for a comparison of the ecological value of classic choice
-rules.
-
-Under maximal uncertainty, all four choice mechanisms considered here are behaviorally
-equivalent on $2 \times 2$ symmetric games, except for objective types with
-imprecise beliefs:
-
-\begin{fact} \label{fact:equivalence2x2} In the class of $2 \times 2$ symmetric games, the acts
-  selected by Laplace rule are exactly the acts selected by regret minimization.
-\end{fact}
-
-\section{The Model}
-\label{sec:basic-model-1}
+\end{figure}
+
+\section{Results}\label{sec:results}
 
@@
 
-To demonstrate the usefulness of the meta-game approach, let us concentrate first on a basic
-model that contains the four choice mechanisms from table~\ref{tab:CMs}. From now on we speak
-of types when we mean pairs $(\text{preference type}, \text{belief type})$, like $(\text{reg}, \text{imp})$ or $(\text{obj}, \text{prc})$.
-
-Meta-games factor in statistical properties of the environment. For particular empirical
+Since we keep the decision rule fixed, a player's choice mechanism will only depend on the player's subjective representation $ (u,\Gamma) $.
+For brevity, from now on we will refer to the pair $ (u,\Gamma)$, like $(\text{reg}, \text{imp})$ or $(\text{obj}, \text{prc})$, as the \textit{type} of the player.
+Sometimes we will also name types by referring to the subjective utility, for instance $(\text{reg}, \text{imp})$ and $(\text{reg}, \text{prc})$ are regret types.
+
+As we noticed, meta-games factor in statistical properties of the environment. For particular empirical
 purposes, one would consult a specific class of games $\mathcal{G}$ with appropriate,
-empirically informed probabilities $P(G)$ in order to match the natural environment of a given
+empirically informed probabilities $P_{\mathcal{G}}$ in order to match the natural environment of a given
 population. 
@@
 symmetric two-player games with two acts for a start. A game is then individuated solely by its payoff
-function, which is a matrix with four numbers. As for occurrence probabilities of
-games, we imagine that entries in a game's matrix are i.i.d.~random variables sampled
-uniformly from set $ \lbrace 0, \dots, 10 \rbrace$.  Using Monte Carlo simulations, we can then
-approximate the values of Equation~(\ref{eq:FittnessChoiceMechGamePairwise})
+function, i.e., by a quadruple of numbers $G=(a,b,c,d)$. As for the occurrence probability $P_{\mathcal{G}}(G)$ of
+game $G$, we imagine that the values $a,b,c,d$ are i.i.d.~random variables sampled from the set $ \lbrace 0, \dots, 10 \rbrace$ according to uniform probability $P_{V}$.
+The probability distribution of games is thus the fourfold product of $P_{V}$, that is, $P_{\mathcal{G}}=P_{V}^{4}$.
+Using Monte Carlo simulations, we can then
+approximate the values of equation~(\ref{eq:FittnessChoiceMechGamePairwise})
 to construct meta-game payoffs. Results based on $100,000$ randomly sampled games are given in
@@
   each game, the action choices of all four choice mechanisms were determined and payoffs from
-  all pairwise encounters recorded. (Whenever a choice mechanism would not select a unique
-  action in a given game, we recorded unbiased averages over all selected actions.)  The number
+  all pairwise encounters recorded. The number
   in each cell of table~\ref{tab:ExpectedFitness_4Types} is the average payoff for the choice
@@
 \end{tabular}                    
-\caption{Average evolutionary fitness from Monte Carlo simulations of 100,000 symmetric $2 \times 2$ games}
+\caption{Average evolutionary fitness from Monte Carlo simulations of 100,000 symmetric $2 \times 2$ games.}
 \label{tab:ExpectedFitness_4Types}
@@
 
-If we restrict attention to only imprecise belief types, then a monomorphic state in which every agent has
+If we restrict attention to subjective representations with imprecise beliefs only, then a monomorphic state in which every agent has
 regret-based preferences is the only \emph{evolutionarily stable state}. More strongly, since
@@
 selection that is driven by (expected) fitness to invariably weed out maxmin players $(\text{obj}, \text{imp})$ in favor of $(\text{reg}, \text{imp})$, regret minimization. 
-In other
-words, over the class of games considered here, regret
-minimization is a better classic rule than maxmin from an evolutionary point of
-view.
+In terms of choice rules, this means that regret
+minimization is evolutionarily better than maxmin, over the class of games considered here.
+In terms of subjective preferences, it shows that players using the objective representation that directly looks at fitness (possibly money, or profit) are outperformed by non-veridical (regret) representations, when players' beliefs are imprecise.
 
@@
 we add a small mutation rate to the dynamics. Take a fixed, small mutation rate $\epsilon$ for
-the probability that a player's preference type \emph{or} her belief type changes to another
-preference or belief type. The probability that a player's type randomly mutates into a
-completely different type with altogether different preference type and belief type would
+the probability that a player's subjective utility \emph{or} her subjective belief changes to another
+utility or belief. The probability that a player's subjective representation randomly mutates into a
+completely different representation with altogether different utility and belief would
 then be $\epsilon^2$. With these assumptions about ``component-wise mutations'', numerical
@@
 \citep{Nowak2006:Evolutionary-Dy} show that already for very small mutation rates almost all
-initial population states converge to a single fixed point in which the majority of players are
-regret types. For instance, with $\epsilon = 0.001$, almost all initial populations are
+initial population states converge to a single fixed point in which the majority of players have
+regret-based utility. For instance, with $\epsilon = 0.001$, almost all initial populations are
 attracted to a final distribution with proportions:
@@
 
-Results based on the single meta game in table~\ref{tab:ExpectedFitness_4Types} are not fully general and possibly spoiled by random
+Results based on the single meta-game in table~\ref{tab:ExpectedFitness_4Types} are not fully general and possibly spoiled by random
 fluctuations in the sampling procedure. Fortunately, for the case of $2 \times 2$ symmetric
-games, the main result that maxmin types $(\text{obj}, \text{imp})$ are strictly dominated can
-also be shown analytically for generous general conditions.
+games, the main result that maxmin types $(\text{obj}, \text{imp})$ are strictly dominated by regret minimizers can
+also be shown analytically for considerably general conditions.
 
 \begin{proposition} \label{proposition1}
-  Let $\mathcal{G}$ be the class of $2 \times 2$ symmetric games with payoffs sampled from a
-  set of i.i.d.~values with at least three elements in the support. Then,
+  Let $\mathcal{G}$ be the class of $2 \times 2$ symmetric games $G=(a,b,c,d)$ generated by i.i.d.~sampling $a,b,c,d$ from a
+  set of values with at least three elements in the support. Then,
   $(\text{reg}, \text{imp})$ strictly dominates $(\text{obj}, \text{imp})$ in the resulting
@@
 \begin{proof}
-See Appendix~\ref{sec:proofs}.
+All proofs are in Appendix~\ref{sec:proofs}.
 \end{proof}
@@
 %fitness. Moreover,
-non-veridical regret-based preference representations can not only persist, but even be favored by
-natural selection if agents may have imprecise beliefs.
+objective preference representations are not necessarily favored by
+natural selection. In particular, under generous circumstances objective preferences are outperformed by non-veridical regret preferences, if agents may have imprecise beliefs.
 This
@@
 
+Even more in general, we can show that the same result obtains for any imprecise belief, not only for maximally uncertain players. 
+Let the uncertainty held by a player be defined by a closed and convex set of probabilities $ [s,t] \subseteq \Delta(A) $ over the co-player's actions, where $s$ is the lower probability and $t$ is the upper probability of action $II$.
+We can then prove the following proposition, which
+is the equivalent of Proposition~\ref{proposition1} for any possible (not necessarily
+maximal) degree of uncertainty $[s,t]$, with $s \neq t$. There is only one difference: we are
+now going to require i.i.d. drawing of a \emph{continuous} random variable. This is due
+to the fact that, for arbitrarily small intervals $[s,t]$, objective players $([s,t],\text{obj})$
+and regret players $([s,t],\text{reg})$ can behave as holding a unique probability measure
+(precise belief) if the underlying payoff space is not dense. The reason for this technical requirement
+will become clearer from the proof.
+
+\begin{proposition} \label{proposition2}
+In the class of $2\times2$ symmetric games generated by i.i.d. drawing
+of a continuous random variable that takes values in a real interval
+$(\underline{r},\overline{r})$ with probability density $P_V$, for
+any imprecise belief $[s,t]$, the only
+evolutionarily stable state of a population with regret players $([s,t],\text{reg})$
+and objective players $([s,t],\text{obj})$ is a monomorphic state of $([s,t],\text{reg})$
+players.
+\end{proposition}
+
 \section{Extensions}
@@
 How do the basic results from the previous section carry over to richer models?
-Section~\ref{sec:more-types} first introduces further conceptually interesting preference types
+Section~\ref{sec:more-types} first introduces further conceptually interesting subjective representations
 that have been considered in the literature. Section~\ref{sec:n-times-n} then addresses the
 case of $n \times n$ games for $n \ge 2$. Finally, Section~\ref{sec:solitary-decisions} ends
-with a brief comparison of game situations with cases of solitary decision making.
-
-\subsection{More Types}
+with a brief comparison to the case of solitary decision making.
+
+\subsection{More Representations}
 \label{sec:more-types}
 
-Beyond objective and regret-based preferences, other preference types have been investigated. A
-famous example is the \textit{altruistic type} \citep[e.g.,][]{Beck76,BestGuth98}, summoned to
-explain the possibility of altruistic behavior. At the other end of the spectrum, the \emph{competitive
-type} is located.
-
-\begin{definition}[Altruistic and competitive types] \label{defn:alttype}
-
-  Fix a two-player game $G$ with actual evolutionary payoff functions $\pi_i$. The \textit{altruistic type}
-  has subjective utility $\theta(a_i, a_j):=\pi_i(a_i,a_j) + \pi_j(a_i,a_j)$.\footnote{A
-    more general formulation would be to define an $ \alpha$-altruistic type, for
-    $\alpha \in [0,1]$, with subjective utility
-    $ \theta_\alpha(a_i, a_j):=\pi_i(a_i,a_j) + \alpha \pi_j(a_i,a_j)$. Since we are not
-    interested in the evolution of degrees of altruism, here we simply fix $ \alpha = 1 $.} The
-  \emph{competitive type} has subjective utility
-  $\theta(a_i, a_j):=\pi_i(a_i,a_j) - \pi_j(a_i,a_j)$.
-
-\end{definition}
+Beyond objective and regret-based utilities, other subjective preferences have been investigated, especially in behavioral economics and in evolutionary game theory. A
+famous example is the \textit{altruistic} preference \citep[e.g.,][]{Beck76,BestGuth98}, summoned to
+explain the possibility of altruistic behavior. At the other end of the spectrum, the \emph{competitive}
+preference is located. The two subjective utilities are defined as follows.
+\begin{enumerate}
+\item \textit{altruistic} utility: for all $G \in \mathcal{G}$, $\text{alt}^G(a,a') = \pi^G(a,a') + \pi^G(a',a)$;\footnote{A
+    more general formulation would be to define $ \alpha$-altruistic utility, for
+    $\alpha \in [0,1]$,
+    $ u^G_\alpha(a, a')=\pi^G(a,a') + \alpha \pi^G(a',a)$. Since we are not
+    interested in the evolution of degrees of altruism, here we simply fix $ \alpha = 1 $. Analogously for $\alpha$-competitive utilities too.}
+\item \textit{competitive} utility: for all $G \in \mathcal{G}$, $\text{com}^G(a,a') = \pi^G(a,a') - \pi^G(a',a)$.
+\end{enumerate}
 
@@
 }                  
-\caption{Average evolutionary fitness from Monte Carlo simulations of 100,000 symmetric $2 \times 2$ games}
+\caption{Average evolutionary fitness from Monte Carlo simulations of 100,000 symmetric $2 \times 2$ games.}
 \label{tab:ExpectedFitness_2x2_Full}        
@@
 Table~\ref{tab:ExpectedFitness_2x2_Full} shows results of Monte Carlo simulations that
-approximate the expected fitness in the relevant meta-game with all types considered so
+approximate the expected fitness in the relevant meta-game with all the subjective representations considered so
 far. These results confirm basic intuitions about altruistic and competitive types: everybody would like to have an altruistic co-player and nobody
@@
 \fi
-It is easy to see then that the previous result still obtains for the larger meta-game in
+It is easy to see then that the previous results still obtain for the larger meta-game in
 table~\ref{tab:ExpectedFitness_2x2_Full}: $(\text{reg}, \text{imp})$,
@@
 
-In sum, the presence of other plausible preference types, such as competitive and altruistic
-types, does not undermine, but rather strengthens the previous results about the evolutionary
-drive towards regret-based preferences.
+In sum, the presence of other subjective representations, such as those based on altruistic or competitive utilities, does not undermine, but rather strengthens our previous results.
 
@@
 Results from Section~\ref{sec:basic-model-1} relied heavily on Fact~\ref{fact:equivalence2x2}, that
-is no longer true when we look at arbitrary $n \times n$ games. Let us see what
-happens in a broader class of games.
-
+is no longer true when we look at arbitrary $n \times n$ games. 
 Table~\ref{tab:ExpectedFitness_10x10} gives approximations of expected fitness in the class of
@@
 meta-game from table~\ref{tab:ExpectedFitness_10x10}. This means that while simple regret minimization
-\emph{can} thrive in some evolutionary contexts, there are also contexts where it is
+can thrive in some evolutionary contexts, there are also contexts where it is
 demonstrably worse off. While this may be bad news for regret minimizing types
@@
 $(\text{obj}, \text{prc})$ are behaviorally equivalent in general, it remains that selection
-based on meta-games constructed from $n \times n$ games will still not eradicate regret
-preferences. So, although regret types may not be selected for in this case, they are also not
-selected against.
+based on meta-games constructed from $n \times n$ games will still not eradicate regret preferences.
+%So, although regret types may not be selected for in this case, they are also not selected against.
 
 On the other hand, there are plenty of ways in which the basic insight from
-Proposition~\ref{proposition1} that regret-based preferences can be strictly better than
-veridical objective preferences in case of imprecise beliefs could make for situations in which
+Propositions~\ref{proposition1} and \ref{proposition2} that regret-based utilities are strictly better than
+veridical objective utilities in case of imprecise beliefs can make for situations in which
 evolution would select for regret types exclusively, even in $n \times n$ games. If, for
-example, the belief type of a player is a trait that biological evolution has no bite on, but rather
-something that the particular choice situation would exogenously give us, then regret-based
-preferences \emph{can} again drive out veridical preferences altogether. For concreteness,
-suppose that only preference types compete and that agents' belief types are exogenously given,
-in such a way that both players hold precise beliefs with probability $p$ and they both have imprecise
+example, the belief of a player is a trait that biological evolution has no bite on, but rather
+something that the particular choice situation would exogenously give us (possibly because of the different amount of information available in different choice situations), then regret-based
+preferences can again drive out veridical preferences altogether. For example,
+suppose that only preferences compete and that agents' beliefs are exogenously given,
+in such a way that both players hold precise (Bayesian) uniform beliefs with probability $p$ and they both have maximally imprecise
 beliefs otherwise. This transforms the meta-game from table~\ref{tab:ExpectedFitness_10x10} into a
-simpler $4 \times 4$ meta-game in which the payoff obtained for a preference type is the weighted
-average over the payoffs of the choice mechanisms including that preference type in
+simpler $4 \times 4$ meta-game in which the payoff obtained by a subjective utility is the weighted
+average over the payoffs of the subjective representations including that utility in
 table~\ref{tab:ExpectedFitness_10x10}. Setting $p = 0.98$ for illustration, we get the meta-game in table~\ref{tab:ExogeneousEpistemics}.
@@
 \end{tabular}
-\caption{Meta game for the evolutionary competition between preference types when epistemic types are exogenously
-  given (see main text)}
+\caption{Meta-game for the evolutionary competition between subjective utilities when beliefs are exogenously
+  given (see main text).}
 \label{tab:ExogeneousEpistemics}
 \end{table}
-The only evolutionarily stable state of this meta-game is a monomorphic population of regret types. Accordingly, all of
+The only evolutionarily stable state of this meta-game is again a monomorphic population of regret types. Accordingly, all
 our simulation runs of the (discrete-time) replicator dynamics converge to monomorphic
-regret-type populations. The reason why regret types prosper is because they have a substantial
-fitness advantage if paired with imprecise beliefs (Proposition~\ref{proposition1}). If imprecise uncertainty is exogenously given
-as something unavoidable that happens to agents (e.g., in situation where they really have no
-way of narrowing down the probability set), and even if that happens only very infrequently
-(i.e., for rather low $p$), regret types \emph{will} outperform veridical preference types, as
-well as competitive and altruistic types.
+regret-type populations. The reason why regret-based utilities prosper is because they have a substantial
+fitness advantage when paired with imprecise beliefs (Propositions~\ref{proposition1} and \ref{proposition2}). If unmeasurable uncertainty is exogenously given
+as something that happens to agents because of the information available in some choice situations, and even if that happens only very infrequently
+(i.e., for rather low $p$), regret preferences will outperform objective preferences, as
+well as competitive and altruistic preferences.
 
@@
 fitness obtained in randomly generated solitary decision problems. For our purposes, a decision
-problem $\tuple{S, \Acts, \pi}$ consists of a set of states $S$, a set of acts $\Acts$, and
-a payoff function $\pi \mycolon S \times \Acts \rightarrow \mathbb{R}$.  We generate arbitrary
+problem $D=\tuple{W, \Acts, \pi^D}$ consists of a set of states of the world $W$, a set of acts $\Acts$, and
+a payoff function $\pi^D: W \times \Acts \rightarrow \mathbb{R}$.  We generate arbitrary
 decision problems by selecting, uniformly at random, numbers of states and acts
-$n_s, n_\act \in \set{2, \dots, 10}$ and then filling the utility table, so to speak, by
-i.i.d.~samples for each $\pi(s, \act) \in \set{0, 10}$. Unlike with
+$n_w, n_\act \in \set{2, \dots, 10}$ and then filling the utility table, so to speak, by
+i.i.d.~samples for each $\pi^D(w, \act) \in \set{0, 10}$. Unlike with
 two-player games, we need to also sample the actual state of the world, which we selected
-uniformly at random from the available states in the current decision problem. As player types,
-we considered the original cast of four from table~\ref{tab:CMs}, since altruistic and
+uniformly at random from the available states in the current decision problem. Accordingly, the fitness of choice mechanism $c$ in decision problem $D$ is given by:
+$$F_D(c)= \pi^D(w,a_c^*(u^D,\Gamma))\mu(w).$$
+As subjective representations,
+we considered the original cast of four from table~\ref{tab:ExpectedFitness_4Types}, since altruistic and
 competitive types are meaningless in solitary decision situations. As before, the
-relevant fitness measure, defined in Equation~(\ref{eq:FittnessChoiceMechSolitary}), was
+relevant fitness measure, defined in equation~(\ref{eq:FittnessChoiceMechSolitary}), was
 approximated by Monte Carlo simulation, the results of which are given in
 table~\ref{tab:SolitaryDecisions}.
+\begin{align}
+  \label{eq:FittnessChoiceMechSolitary}
+  F(c) = \int P_{\mathcal{D}}(D) \  F_D(c) \text{ d} D 
+\end{align}
 
@@
   \caption{Expected fitness of choice mechanisms approximated from 100,000 simulated solitary
-    decision problems (see main text)}
+    decision problems (see main text).}
   \label{tab:SolitaryDecisions}
@@
 solitary decisions. Evolutionary selection based on objective fitness will not select against
-regret-based preferences, as these are indistinguishable from veridical preferences
+regret preferences, as these are indistinguishable from veridical preferences
 when paired with precise beliefs. But when paired with imprecise beliefs, regret-based
-preferences outperform veridical preferences. Consequently, if there is a chance, however
+utilities outperform objective utilities. Consequently, if there is a chance, however
 small, that agents fall back onto imprecise beliefs, evolution will actually positively select
@@
 
+\section{Related Literature}
+
+do you think we really need a section for this?
+
 \section{Conclusion} \label{sec:conclusion}
@@
 
+\iffalse
 \section{Background on Imprecise Probabilities}
@@
 
+\fi
+
 \section{Proofs}
@@
 the maximinimizer $(\text{obj}, \text{imp})$ by $M$. Following
-Equation~(\ref{eq:FittnessChoiceMechGamePairwise}), let $F_{\mathcal{G}}(X,Y)$ denote the
+equation~(\ref{eq:FittnessChoiceMechGamePairwise}), let $F_{\mathcal{G}}(X,Y)$ denote the
 expected payoff of choice mechanism $X$ against choice mechanism $Y$ on the possibly restricted
@@
 
+\vspace{.5cm}
+
+\noindent \textbf{Proof of Proposition \ref{proposition2}.} Take an arbitrary real interval $(\underline{r},\overline{r})$, where
+$\underline{r}$ is the infimum and $\overline{r}$ is the supremum,
+and let $P$ be the PDF over $(\underline{r},\overline{r})$. Given
+Lemma \ref{lemma:probabilities coord-ant}, we focus on the case of coordination games. Now fix a set
+of probabilities $[s,t]$, corresponding to the uncertainty of the
+players about the co-player's action. As we have seen, objective and
+regret types will behave exactly the same when $s=t$ and $[s,t]$
+reduces to a single probability. Notice that objective and regret
+will also be indistinguishable when there is no game such that $s<\frac{a-c}{a-c+d-b}<t$.
+It is then a necessary condition for regret types to be better than
+objective types that the two types behave differently at least in
+some games. Geometrically, the ratio $\frac{a-c}{a-c+d-b}$ denotes
+the intersection point of the lines corresponding to action $I$ and
+action $II$ (figure~\ref{fig:graphstrictinf1-2})
+\begin{figure}
+\centering\begin{tikzpicture}[scale=.9]
+
+%
+\draw [-, very thick]  (0,0) to (5,0);
+%
+\draw [-, very thick] (0,0) to (0,5);
+
+%
+\draw [-, very thick] (5,0) to (5,5);
+
+%
+\node (zero) [] at (-.75,-.5) {$P(II)=0$};
+
+%
+\node (s) [] at (2,0)
+  [label=below:{$s$}] {|};
+%
+\node (t) [] at (4,0)
+  [label=below:{$t$}] {|};
+%
+%\node (st) [] at (3,0)
+ % [label=below:{$s + \nicefrac{\epsilon}{2}$}] {};
+
+\draw [dashed] (2,0) -- (2,5);
+\draw [dashed] (4,0) -- (4,5);
+
+\draw [dotted] (3,0) -- (3,5);
+
+%
+\node (a') [] at (1.8,2.6)
+  [label=left:{}] {$a'$};
+\node (c') [] at (2.2,2)
+  [label=left:{}] {$c'$};
+\node (d') [] at (4.2,4)
+  [label=left:{}] {$d'$};
+\node (b') [] at (4.2,2.6)
+  [label=left:{}] {$b'$};
+
+%
+\node (0y) [] at (0,0)
+  [label=left:{$c$}] {};
+\node (1y) [] at (0,1)
+  [label=left:{}] {-};
+\node (2y) [] at (0,2)
+  [label=above right:{$I$}] [label=left:{$a$}] {-};
+
+\node (3y) [] at (0,3)
+  [label=left:{}] {-};
+\node (4y) [] at (0,4)
+  [label=left:{}] {-};
+\node (5y) [] at (0,5)
+  [label=left:{}] {-};
+%
+\node (1yy) [] at (5,1)
+  [label=left:{}] {-};
+\node (2yy) [] at (5,2)
+  [label=left:{}] {-};
+
+\node (3yy) [] at (5,3)
+  [label=right:{$b$}] {-};
+\node (4yy) [] at (5,4)
+  [label=left:{}] {-};
+\node (5yy) [] at (5,5)
+  [label=left:{$II$}] [label=right:{$d$}] {-};
+%
+
+\node (p1) [] at (5,0)
+  [label=below:{$1$}] {};
+
+%
+
+%
+\draw [-, very thick] (0,2) to (5,3);
+%
+\draw [-, very thick] (0,0) to (5,5);
+%
+
+\draw[decorate,decoration={brace,amplitude=10}](5,5)--(5,3)node [black,midway,xshift=25pt] {\footnotesize $d-b$};
+%
+\draw[decorate,decoration={brace,amplitude=10}](0,0)--(0,2)node [black,midway,xshift=-25pt] {\footnotesize $a-c$};
+%
+
+\end{tikzpicture}\protect\caption{Example of strictly informative coordination game.}
+\label{fig:graphstrictinf1-2}
+\end{figure}
+. If there is no game where such an intersection point falls into
+the interval $[s',t']$, for some $s'\neq t'$, then whenever players
+hold the set of probabilities $[s',t']$ they will perceive any game
+that can arise as having a dominant action, i.e., as a strong dominance
+game in partition cell $\mathcal{S}$. Note also that the ratio $\frac{a-c}{a-c+d-b}$
+takes values in the interval $(0,1)$, since to get $\frac{a-c}{a-c+d-b}=0$
+we shall have $a=c$ and for $\frac{a-c}{a-c+d-b}=1$ we need $d=b$,
+which have no probability of occurrence for continuous random variables.
+Furthermore, the ratio $\frac{a-c}{a-c+d-b}$ is dense in $(0,1)$,
+and consequently in any interval $[s,t]\subset(0,1)$. Indeed, for
+any rational number $\frac{m}{n}\in[s,t]$, we can always find $a,b,c,d\in(\underline{r},\overline{r})$
+such that $\frac{a-c}{a-c+d-b}=\frac{m}{n}$ as follows. It is not
+difficult to see that for this to be the case we must have 
+\[
+a-(a-b)\frac{m}{n}=c+(d-c)\frac{m}{n}.
+\]
+This equation reduces to
+\begin{equation}
+\frac{n-m}{n}a+\frac{m}{n}b=\frac{n-m}{n}c+\frac{m}{n}d,\label{eq:hit the point}
+\end{equation}
+which is an equality between two convex combinations with the same
+weights $\frac{n-m}{n}$ and $\frac{m}{n}$. Then, whatever $a,b\in(\underline{r},\overline{r})$
+we pick it is always possible to find (infinitely many) $c,d\in(a,b)\subset(\underline{r},\overline{r})$
+such that equation (\ref{eq:hit the point}) is satisfied. Indeed,
+for any $x\in(0,1)$ we have that $c=(\frac{n-m}{n}a+\frac{m}{n}b)x+a(1-x)$
+and $d=(\frac{n-m}{n}a+\frac{m}{n}b)x+b(1-x)$ satisfy equation (\ref{eq:hit the point}).
+This shows that for any rational number $\frac{m}{n}\in[s,t]$ we
+can always find $c,d\in(a,b)\subset(\underline{r},\overline{r})$
+such that $\frac{a-c}{a-c+d-b}=\frac{m}{n}$, and so we can always
+find $a,b,c,d\in(\underline{r},\overline{r})$ such that $\frac{a-c}{a-c+d-b}=\frac{m}{n}$.
+Since rational numbers are dense in $\mathbb{R}$, they are also dense
+in any real interval $[s,t]\subset(0,1)$. Hence, the ratio $\frac{a-c}{a-c+d-b}$
+is dense in $[s,t]$.
+
+Once we have proven the density of $\frac{a-c}{a-c+d-b}$ for coordination
+games $G=(a,b,c,d)$ in any real interval $[s,t]\subset(0,1)$, the
+rest of the proof is connected to the proof of Proposition \ref{proposition1}. Specifically,
+for a given interval $[s,t]$ we define
+\begin{equation}
+\begin{array}{ccccc}
+a' & := & (1-s)a+sb & = & a+s(b-a)\\
+b' & := & (1-t)a+tb & = & a+t(b-a)\\
+c' & := & (1-s)c+sd & = & c+s(d-c)\\
+d' & := & (1-t)c+td & = & c+t(d-c)
+\end{array}\label{eq:a'b'c'd'}
+\end{equation}
+The equivalent of Lemmas \ref{lemma:probabilities coord-ant}, \ref{lemma:probabilities actions coord-ant} and \ref{lemma:action implications} as well as the rest of the proof of Proposition \ref{proposition1} hold also for $a',b',c',d'$.
+\hfill $\dashv$
+
+\newpage
+
 \printbibliography[heading=bibintoc]

### 2016-06-24 paper/rev1_paperBlinded.tex
paper revision first half

@@
 
+\definecolor{Red}{RGB}{178,34,34}
+\newcommand{\mf}[1]{\textcolor{Red}{[mf: #1]}}
+
 \title{Smart Representations: {R}ationality and Evolution in a Richer  Environment}
@@
 \begin{abstract}
-\normalsize
-  Standard applications of evolutionary game theory look at a single, fixed game and focus on
-  the evolution of behavior for that game alone. Instead, this paper uses tools from
-  evolutionary game theory to study the evolutionary competition between \emph{choice
-    mechanisms} in a rich and variable environment. A choice mechanism is a way of representing
-  a decision situation, paired with a method for choosing an act based on this 
+  \normalsize Standard applications of evolutionary game theory look at a single, fixed game
+  and focus on the evolution of behavior for that game alone. Instead, this paper uses tools
+  from evolutionary game theory to study the evolutionary competition between \emph{choice
+    mechanisms} in a rich and variable environment. A choice mechanism is a way of subjectively
+  representing a decision situation, paired with a method for choosing an act based on this
   subjective representation. We demonstrate the usefulness of this approach by a case study
-  that compares a number of classic proposals for decision making. The
-  main result is that regret-based preference representations can be evolutionarily selected
-  for, despite being non-veridical.
+  that shows how subjective preference representations in terms of regret that differ from the
+  actual fitness can be evolutionarily advantageous.
 \end{abstract}
@@
 If agents deal with a rich and variable environment, they have to face many different choice
-situations.
-Standard evolutionary game models frequently
-simplify reality in two ways that are relevant for present purposes. Firstly, the environment
-is represented as a fixed \emph{stage game}; secondly, the focus of
-evolutionary selection is behavior for that stage game alone. In contrast, some argue for
+situations.  Standard evolutionary game models frequently simplify reality in at least two
+ways. Firstly, the environment is represented as a fixed \emph{stage game}; secondly, the focus
+of evolutionary selection is behavior for that stage game alone. In contrast, some argue for
 studying the evolutionary competition of general \emph{choice mechanisms} in a rich and
 variable environment
-\citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche,HammStev12}. To show that
-there is no tension here, this paper introduces a method for reconciling established notions of
-evolutionary game theory with evolutionary selection of choice mechanisms in variable
-environments \citep[see, inter alia, related work
-by][]{Harley1981:Learning-the-Ev,ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o,OConnor2016:Evolving-to-Gen}.
-
-In full generality, a choice mechanism associates decision situations with action choices. A crucial
-part of a choice mechanism is the \emph{subjective representation} of the decision situation,
-in particular the manner of forming preferences and beliefs about a possibly uncertain world (see
-figure~\ref{fig:ChoiceMechanism} below). This paper asks: which preference and belief
-representations are ecologically valuable and lead to high fitness?
-The evolution of
+\citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche,HammStev12}. In
+response to this and adding to recent like-minded approaches, this paper introduces a general
+meta-game model that conservatively extends the scope of evolutionary game theory to deal with
+evolutionary selection of choice mechanisms in variable environments \citep[see, inter alia,
+related work
+by][]{Harley1981:Learning-the-Ev,ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o,OConnor2016:Evolving-to-Gen}.\mf{please
+insert more references here; maybe use a footnote right here to pick out some of the most
+important related pieces and say how our contribution is novel and shiny}
+
+A choice mechanism associates decision situations with action choices. A crucial part of a
+choice mechanism is the \emph{subjective representation} of the decision situation, in
+particular the manner of forming preferences and beliefs about a possibly uncertain world. To
+show the usefulness of the meta-game approach, this paper asks: which preference and belief
+representations are ecologically valuable and lead to high fitness? The evolution of
 preferences has been subject of recent interest in theoretical economics
-\citep[e.g.,][]{algweib13,DekElyYlan07,RobSam11}. Here, we argue that questions of preference evolution should take
-variability in uncertainty representation into account as well. In relation to this, 
-the main contributions of this work are essentially three.
-First, we show that the way agents form beliefs, and the type of uncertainty that they entertain in particular, is a key aspect for the evolutionary success.
-Second, we demonstrate
-that if agents have imprecise probabilistic beliefs \citep[e.g.][]{gardsah82,levi74,walley96}, faithful and objective representation in terms of true, real evolutionary fitness can be outperformed by
-subjective (e.g., regret-based) preference representations that deviate
-from the true fitness that natural selection operates on.
-Third, although a few examples along similar lines have recently been introduced (REFERENCES), our approach based on a meta-game model is very uncustomary in the literature, and contributes to widen the methods of evolutionary game theory beyond the traditional single-game framework.
+\citep[e.g.,][]{algweib13,DekElyYlan07,RobSam11}. Here, we argue that questions of preference
+evolution should take variability in uncertainty representation into account as well. We
+demonstrate that if agents have imprecise probabilistic beliefs
+\citep[e.g.][]{gardsah82,levi74,walley96}, faithful and objective representation in terms of
+true, real evolutionary fitness can be outperformed by subjective (e.g., regret-based)
+preference representations that deviate from the true fitness that natural selection operates
+on.
 
@@
 
-The paper is organized as follows. Section \ref{sec:rati--subj} reviews different views of rational choice and relates the
-approach we take here to the existing literature. Sections \ref{sec:subj-ut,bel,dec-rules} and \ref{sec:subj-rep,ev-fit} introduce the
-relevant decision-theoretic and game-theoretic notions, while Sections \ref{sec:metagame} and \ref{sec:model} present the model.
-%spells out four choice mechanisms on whose
-%evolutionary competition we zoom in 
-The main results of the paper are in Section~\ref{sec:results}, and Section \ref{sec:extensions} extends the evolutionary analysis by
-introducing more choice mechanisms and alternative models of the environment. Finally, Section \ref{sec:conclusion} concludes.
-
-\section{Rationality and Representations}
+The paper is organized as follows. Section \ref{sec:rati--subj} sets the scene by reviewing
+different perspectives no rational choice. Section~\ref{sec:subj-ut,bel,dec-rules} then
+introduces the meta-game approach. In doing so it covers key notions such as choice mechanism,
+decision rules and subjective representations, all with an eye towards the specific application
+to the evolution of preferences in Section~\ref{sec:model}. Section~\ref{sec:results} contains
+our main results for this application and Section \ref{sec:extensions} discusses some
+interesting extensions.
+
+\section{Rationality and Subjective Representations}
 \label{sec:rati--subj}
@@
 \emph{redescriptionism} of observable behavior. For example,
-\citet{KahnemannTversky1979:Prospect-Theory} famously demonstrated that what appear to be
-violations of rationality norms in human decision making can be explained on the assumption
-that subjects' beliefs and preferences deviate systematically from the objectively given
-parameters in the presented choice task. Similarly for social decision making, including social
-preferences such as fairness, altruism or similar, allows us to describe as rational
-empirically observed behavior, such as in experimental Prisoner's Dilemmas or public goods
-games, that might otherwise appear irrational \citep[e.g.,][]{fehrschmidt99,charrab02}.
+% \citet{KahnemannTversky1979:Prospect-Theory} famously demonstrated that what appear to be
+% violations of rationality norms in human decision making can be explained on the assumption
+% that subjects' beliefs and preferences deviate systematically from the objectively given
+% parameters in the presented choice task. Similarly
+in the case of social decision making, including considerations of fairness allows us to
+describe as rational empirically observed behavior, such as in experimental Prisoner's Dilemmas
+or public goods games, that might otherwise appear irrational
+\citep[e.g.,][]{fehrschmidt99,charrab02}.
 
@@
 therefore emphasizes that there are many ways in which ascriptions of beliefs and preferences
-should be constrained by normative considerations of rationality as well. As for beliefs, where
-possible, subjective beliefs should reflect objective chance. 
-%Where this is impossible,
-%temporal consistency of choices constrains rational subjective beliefs, else exploitation by
-%Dutch books is possible. 
-As for preferences, in certain situations it may make sense to
-postulate on normative grounds that subjective preferences should be oriented towards tracking
-objective fitness. For instance, profit maximization seems a necessary requirement for
-evolution in a competitive market because only firms behaving according to profit maximization will survive in the long run \citep[e.g.,][]{alch50,Fried53}.
+should be constrained by normative considerations of rationality as well: e.g., subjective
+beliefs should reflect objective chance where possible; subjective preferences should be
+oriented towards tracking objective fitness. For instance, profit maximization seems a
+necessary requirement for evolution in a competitive market because only firms behaving
+according to profit maximization will survive in the long run \citep[e.g.,][]{alch50,Fried53}.
 
@@
 
-\iffalse
-
-\begin{figure}
-  \centering
-  \begin{tikzpicture}[node distance = 2.25cm]
-
-  \begin{scope}
-
-    \node[] (environment) {};
-
-    \node[rounded corners, draw, rectangle, minimum height = 0.75cm, text width=6cm, text
-    centered, below of = environment, node distance = 2cm] (situation)
-    {environment produces random \\ \textbf{decision situation} $D$};
-
-    \node[rounded corners, draw, rectangle, minimum height = 0.75cm, text width=6cm, text
-    centered, below of = situation] (representation) 
-    {\textbf{subjective representation} of $D$ \\ \textcolor{gray}{[preference, beliefs, \dots]}};
-
-    \node[rounded corners, draw, rectangle, minimum height = 0.75cm, text width=6cm, text
-    centered, below of = representation] (action)
-    {\textbf{action choice} $a$};
-
-    \node[rounded corners, draw, rectangle, minimum height = 0.75cm, text width=6cm, text
-    centered, below of = action,node distance = 1.5cm] (payoff) {\textbf{payoff} for $a$ in $D$};
-
-    \draw[->, thick]
-    ([xshift=-1.75cm,yshift=-0.5cm]situation.center)--([xshift=-1.75cm,yshift=0.55cm]representation.center)
-    node[midway, right] {subj.~representation scheme $\gamma$};
-
-    \draw[->, thick]
-    ([xshift=-1.75cm,yshift=-0.55cm]representation.center)--([xshift=-1.75cm,yshift=0.5cm]action.center)
-    node[midway, right] {action selection function $\kappa$};
-
-    \draw[->, thick]
-    ([xshift=-1.75cm,yshift=-0.55cm]action.center)--([xshift=-1.75cm,yshift=0.5cm]payoff.center)
-    node[midway, right] {};
-
-    \node[minimum height = 0.75cm, text width=6cm, text
-    centered, right of = representation, xshift = 2cm, rotate = 90] (mechanism) {choice mechanism};
-
-    \begin{pgfonlayer}{background}
-             \node [rounded corners, dashed,
-       very thick,draw=black!40,fit={($(situation.south)+(0,-10pt)$) 
-                                     ($(mechanism.west)+(+5pt,+50pt)$) 
-                                     % ($(action.north)+(0,+10pt)$) 
-                                     ($(representation.west)+(-7pt,0)$)
-                                   }] (box) {};
-    \end{pgfonlayer}
-
-  \end{scope}
-
-\end{tikzpicture}
-  \caption{Schematic representation of action choice. A choice mechanism maps decision
-    situation $D$ to action choice $a$ by means of a representation of $D$ in terms of a subjective
-    preference and a subjective belief.}
-  \label{fig:ChoiceMechanism}
-\end{figure}
-
-We submit that meta-games are a useful tool for structuring and sharpening conceptual inquiry
-in a domain that is notorious for its fuzziness and elusiveness. To show how this approach can
-be applied to the benefit of conceptual debate, we consider the evolution of preferences
-\citep[e.g.,][]{algweib13,DekElyYlan07,RobSam11}. 
-%Concretely, we here pit two different ways of
-%representing preferences against each other: (i) veridical representations that correctly
-%reflect objective fitness, and (ii) non-veridical subjective preferences in terms of regret
-%\citep[e.g.,][]{Savage1951:The-theory-of-s,}. 
-We show that subjective, non-veridical preference
-representations based on a notion of regret can be adaptive and even outperform objective representations of the true evolutionary fitness, when agents, at least on occasion, hold
-\emph{imprecise probabilistic beliefs} \citep[e.g.,][]{gilsch89,levi74,gardsah82} and make
-decisions based on a security choice rule (here: the maxmin rule).\footnote{Decision-theoretic background and justifications for the use of maxmin and imprecise probabilities is given in Appendix~\ref{sec:impr-prob-beli}.}
-
-The case study under consideration strips the generality of a meta-game approach down to a perspicuous
-comparison between four choice mechanisms, summarized in table~\ref{tab:CMs}.
-% the cross-product of two different preference representations (veridical vs.~regret) and two
-%different belief representations (precise vs.~imprecise). 
-\begin{table}[t]
-  \centering
-  \begin{tabular}{cccc}
-  \multicolumn{3}{c}{choice mechanism} \\  \cmidrule(r){1-3}
-    \multicolumn{2}{c}{subjective representation} & action selection & corresponding classic rule \\  \cmidrule(r){1-2}
-    preference type & belief type  \\ \midrule
-    objective fitness & precise & maxmin EU &  Laplace rule \\
-    objective fitness & imprecise & maxmin EU & maxmin \\ 
-    regret & precise & maxmin EU & Laplace rule \\
-    regret & imprecise & maxmin EU & regret minimization \\ 
-  \end{tabular}
-  \caption{Overview relevant choice mechanisms and the corresponding (behaviorally equivalent)
-    classic choice rules.}
-  \label{tab:CMs}
-\end{table}
-\iffalse
-This exclusive selection of choice mechanisms is motivated by a number of
-considerations. Firstly, the set of conceivable choice mechanisms is vast. Most of that
-conceivable vastness is utter nonsense, and some selection of plausible candidates is required in
-any case. Secondly, a restriction to only a small number of suitable candidates will
-help demonstrate more distinctly how a meta game approach may help structure philosophical
-inquiry, which is our main goal. Thirdly, our case study adds to the recent literature on the
-evolution of preferences by making evident the possibly non-trivial interaction between
-preference and belief representations, all else equal. This is our secondary goal. 
-Finally,
-\fi 
-The
-four choice mechanisms,  
-%that we look at here
-although phrased in terms of preference and belief representations, map onto well-known classic
-proposals for rational decision making (see table~\ref{tab:CMs}). In other words, there is also
-motivation from historical relevance for our selection. To see this, we first recapitulate the
-relevant classics ---to have a handy label, we call them \emph{classic rules}--- and then show
-how they relate to our notion of choice mechanism.
-
-The classic literature on rational choice contains a number of proposals for which acts a
-player should choose if she is rational. Maximization of expected utility, as
-given in Definition~\ref{def:rationality}, is just one of them, possible only if DM holds a precise probabilistic belief.
-Here, we consider three others:
-(i) maxmin, (ii) Laplace rule, and (iii) regret minimization. 
-%All of these apply to games and
-%solitary decision situations.
-We focus on games first, but definitions carry over straightforwardly to solitary decisions.
-
-A \emph{choice mechanism} is a map from choice situations to action choices that contains an explicit level, in terms of preferences and beliefs, of subjective representation of
-the choice situation. Concretely, let us think of a choice mechanism as a pair of functions
-($\gamma,\kappa$), where $\gamma$ is a \emph{subjective representation scheme} and $\kappa$ is
-an \emph{action selection function} (see figure~\ref{fig:ChoiceMechanism}).
-
-\noindent This means that objective and regret types are behaviorally indistinguishable, as long as both hold precise beliefs. 
-%This will be central in understanding later results. 
-On the other hand, if paired with imprecise beliefs, different behavioral predictions
-arise.
-
-In the following, we assume that agents are maximally uncertain, so that precise types have a
-(singleton set containing a) uniform probability measure
-$\overline{\mu} \in \Delta(\Acts_{-i})$ and imprecise types entertain all probabilistic beliefs
-about the co-players' behavior $\overline{\Gamma} = \Delta(\Acts_{-i})$. In that case, the
-considered choice mechanisms are behaviorally equivalent to classic choice rules, as summarized
-in table~\ref{tab:CMs}.
-This means that most of the following results which we interpret as results about the evolutionary fitness of different subjective representations are also relevant for a comparison of the ecological value of classic choice
-rules.
-
-\fi
-
-\section{Subjective Utilities, Beliefs and Decision Rules} \label{sec:subj-ut,bel,dec-rules}
+\section{Choice Mechanisms  \& Meta-Games} 
+\label{sec:subj-ut,bel,dec-rules}
 
@@
 $$ \text{Decision Rule: Utility }\times\text{ Beliefs } \rightarrow \text{ Actions.}  $$
-The utility of an agent can be formally expressed by a function $u:W \times A \rightarrow \mathbb{R} $, where $A$ stands for a (finite) set of actions available to the agent and $W$ is a (finite) set of possible states of the world.
-There are many different ways to describe beliefs, but here we assume that the agent's beliefs are represented in terms of a (possibly singleton) set of probability functions $\Gamma \subseteq \Delta(W) $ over the possible states of the world.
-In line with this definition, we can consider different decision rules, such as:
+The utility of an agent can be formally expressed by a function
+$u:W \times A \rightarrow \mathbb{R} $, where $A$ stands for a (finite) set of actions
+available to the agent and $W$ is a (finite) set of possible states of the world. There are
+many different ways to describe beliefs, but for concreteness of later applications we here
+assume that the agent's beliefs are represented in terms of a (possibly singleton) set of
+probability functions $\Gamma \subseteq \Delta(W) $ over the possible states of the
+world. Examples of well-known decision rules from the literature that will be useful later are:
 \begin{enumerate}
 
-\item \textbf{Maxmin}: $$ a^*(u,\Gamma)= \argmax_{a \in A} \min_{\mu \in \Gamma} \sum_{w\in W} u(w,a)  \mu(w).$$
-
-\item \textbf{Maximax}: $$ a^*(u,\Gamma)= \argmax_{a \in A} \max_{\mu \in \Gamma} \sum_{w\in W} u(w,a)  \mu(w).$$
-
-\item \textbf{Laplace rule}: $$ a^*(u,\Gamma)= \argmax_{a \in A} \sum_{w\in W} \frac{1}{|W|}  u(w,a) .$$
-
-\item \textbf{Expected utility maximization} (for $\Gamma$ singleton): $$ a^*(u,\Gamma)= \argmax_{a \in A} \sum_{w\in W} u(w,a)  \mu(w).$$
+\item \textbf{Maxmin}: $$ a^*(u,\Gamma)= \argmax_{a \in A} \min_{\mu \in \Gamma} \sum_{w\in W} u(w,a)  \mu(w)$$
+
+\item \textbf{Maximax}: $$ a^*(u,\Gamma)= \argmax_{a \in A} \max_{\mu \in \Gamma} \sum_{w\in W} u(w,a)  \mu(w)$$
+
+\item \textbf{Laplace rule}: $$ a^*(u,\Gamma)= \argmax_{a \in A} \sum_{w\in W} \frac{1}{|W|}  u(w,a) $$
+
+\item \textbf{Expected utility maximization} (for $\Gamma$ singleton): $$ a^*(u,\Gamma)= \argmax_{a \in A} \sum_{w\in W} u(w,a)  \mu(w)$$
 
@@
 
-It is worth noticing that both maxmin and maximax boil down to expected utility maximization when the set  $\Gamma$ is a singleton, and in turn expected utility maximization reduces to Laplace rule when the belief $\mu$ is a uniform probability over the states.
-
-\section{Subjective Representations and Evolutionary Fitness} \label{sec:subj-rep,ev-fit}
-
-For a choice mechanism to prescribe an action, the decision rule  needs to be given a specific subjective utility and belief as input, as described in the previous section.
-We then call \textit{subjective representation} of the decision problem the pair $(u,\Gamma)$ of a subjective utility and a subjective belief.
-In other words, a subjective representation is a general way of forming preferences and beliefs about the choice situation.
-
-The literature on evolution of preferences (REFERENCES) mainly focuses on the evolutionary selection of subjective utilities uniquely.
-Instead, it will be clear from our model that different subjective beliefs may have a fundamental role in determining the evolutionary success of subjective utilities, and therefore the interplay between utilities and beliefs needs to be taken into account explicitly.
-So, here we
-are most interested in the question which subjective representations are better than others
-from an evolutionary point of view. In order to investigate this issue we are going to use the machinery of evolutionary game theory.
-
-A game is an interactive decision situation. 
-For a given game $G=\langle N, (A_i,\pi^G_i)_{i \in N} \rangle$, let us denote the evolutionary payoff, or \textit{fitness}, of player $i$ by the function $\pi^G_i: \Pi_{i \in N} A_i \rightarrow \mathbb{R}$, where $A_i$ is player $i$'s (finite) set of actions.
-For simplicity of exposition we assume that
-  all games that are played are symmetric two-player games, that is, games such that: $N:=\{1,2\}$, $A_1 = A_2 $, and $\pi^G_1(a_1, a'_2)= \pi^G_2(a'_1, a_2)=:\pi^G(a,a')$.\footnote{Since payoff functions are symmetric, we will simply write $\pi^G(a, a')$ for $\pi^G_1(a_1, a'_2)$ and $A:=A_1=A_2$, as usual.
-However, notice that all the definitions and results can be extended to more general cases.} Then, the evolutionary fitness of a subjective representation $(u,\Gamma)$ is measured in terms of the fitness of a
-choice mechanism that contains it, all else equal. 
-Formally, the fitness of a choice mechanism $c$ against choice mechanism $c'$ in a symmetric two-player game $G=\langle \{1,2\}, A, \pi^G \rangle$ is the
-expected payoff of $c$ against $c'$ in $G$:
+It is worth noticing that both maxmin and maximax boil down to expected utility maximization
+when the set $\Gamma$ is a singleton, and in turn expected utility maximization reduces to
+Laplace rule when the belief $\mu$ is a uniform probability over the states.  \mf{do we need
+  ``maximax''?}
+
+As mentioned previously, for a choice mechanism to prescribe an action, the decision rule needs
+to be given a specific subjective utility and belief as input. A \textit{subjective
+  representation} of a decision problem is the pair $(u,\Gamma)$, consisting of a subjective
+utility and a subjective belief. We are specifically interest in general and systematic ways of
+forming such subjective representations across many different decision situations.
+
+% The literature on evolution of preferences (REFERENCES) mainly focuses on the evolutionary
+% selection of subjective utilities uniquely. Instead, it will be clear from our model that
+% different subjective beliefs may have a fundamental role in determining the evolutionary
+% success of subjective utilities, and therefore the interplay between utilities and beliefs
+% needs to be taken into account explicitly.  So, here we are most interested in the question
+% which subjective representations are better than others from an evolutionary point of
+% view. In order to investigate this issue we are going to use the machinery of evolutionary
+% game theory.
+
+A game is an interactive decision situation.  For a given game
+$G=\langle N, (A_i,\pi^G_i)_{i \in N} \rangle$, let us denote the evolutionary payoff, or
+\textit{fitness}, of player $i$ by the function
+$\pi^G_i: \Pi_{i \in N} A_i \rightarrow \mathbb{R}$, where $A_i$ is player $i$'s (finite) set
+of actions. For simplicity of exposition we assume that all games that are played are symmetric
+two-player games where $N:=\{1,2\}$, $A_1 = A_2 $ and
+$\pi^G_1(a_1, a'_2)= \pi^G_2(a'_1, a_2)=:\pi^G(a,a')$.\footnote{Since payoff functions are
+  symmetric, we will simply write $\pi^G(a, a')$ for $\pi^G_1(a_1, a'_2)$ and $A:=A_1=A_2$, as
+  usual. However, notice that all the definitions and results can be extended to more general
+  cases.} Then, the evolutionary fitness of a subjective representation $(u_c,\Gamma_c)$ is
+measured in terms of the fitness of a choice mechanism that contains it, all else equal.
+Formally, the fitness payoff of a choice mechanism $c$ against choice mechanism $c'$ in a
+symmetric two-player game $G=\langle \{1,2\}, A, \pi^G \rangle$ is the expected payoff of $c$
+against $c'$ in $G$:
 
 $$
- F_G(c,c')= \pi^G(a_c^*(u^G,\Gamma),a_{c'}^*(u^G,\Gamma)), \footnote{Whenever a choice mechanism would not select a unique
-  action, we assume that the player chooses one of the equally optimal actions at random.
-I.e., $F_G(c,c')= \sum_{a \in a_c^*(u^G,\Gamma)} \sum_{a' \in a_{c'}^*(u^G,\Gamma)} \frac{1}{|a_c^*(u^G,\Gamma)|} \frac{1}{|a_{c'}^*(u^G,\Gamma)|} \pi^G(a,a')$.}
+F_G(c,c')= \pi^G(a_c^*(u_c^G,\Gamma_c),a_{c'}^*(u_{c'}^G,\Gamma_{c'})), \footnote{Whenever a choice mechanism
+  would not select a unique action, we assume that the player chooses one of the equally
+  optimal actions at random. I.e., $F_G(c,c')=
+  \sum_{a \in a_c^*(u_c^G,\Gamma_c)} \sum_{a' \in a_{c'}^*(u_{c'}^G,\Gamma_{c'})}
+  \frac{1}{|a_c^*(u_c^G,\Gamma_c)|} \frac{1}{|a_{c'}^*(u_{c'}^G,\Gamma_{c'})|} \pi^G(a,a')$.}
 $$
-where $a^*_c$ is the decision rule of choice mechanism $c$.
-Given the game theoretic setting, the subjective utility $u$ is now a function $u^G:A \times A \rightarrow \mathbb{R}$, and the subjective belief $\Gamma$ is a set of probability functions over the co-player's actions, $ \Gamma \subseteq \Delta(A) $.
-
-However, studying the fitness and the evolutionary selection of different choice mechanisms by the use of a fixed, single game may look like a rather restrictive perspective and possibly biased by the choice of the particular game.
-To avoid these limitations, we extend the standard single-game framework of evolutionary game theory by considering a \textit{class} of possible games that can be played within a population.
-Although not completely novel (seeREFERENCES), this approach has started being investigated only very recently, and we maintain that it can shed new light on the evolution of behavior, and it can open to much broader perspectives on evolutionary game theory in general.
-
-\section{The Meta-Game} \label{sec:metagame}
-
-The ground for the evolutionary competition of choice mechanisms will consist of a class $\mathcal{G}$ of possible two-player symmetric games, together with a probability measure $P_{\mathcal{G}}(G)$ for the occurrence probability of game $G \in \mathcal{G}$.
-In more biological terms, the probability measure $P_{\mathcal{G}}$ encodes the statistical
-properties of the environment.
-We then call \textit{meta-game} the tuple $ MG=\langle CM, \mathcal{G}, P_{\mathcal{G}},F \rangle$, where $CM$ is a set of choice mechanisms, $\mathcal{G}$ is a class of possible games, $P_{\mathcal{G}}(G)$ is the probability of game $G$ to occur, and $F:CM \times CM \rightarrow \mathbb{R}$ is the fitness function, defined as:
+where $a^*_c$ is the decision rule of choice mechanism $c$. Given the game theoretic setting,
+the subjective utility $u_c$ is now a function $u_c^G:A \times A \rightarrow \mathbb{R}$, and
+the subjective belief $\Gamma_c$ is a set of probability functions over the co-player's
+actions, $ \Gamma \subseteq \Delta(A)$.
+
+However, studying the fitness and the evolutionary selection of different choice mechanisms by
+the use of a fixed, single game may look like a rather restrictive perspective and possibly
+biased by the choice of the particular game. To avoid these limitations, we consider a
+\textit{class} of possible games that can be played within a population
+(REFERENCES). \mf{please insert some references to other papers that use a multi-game approach
+  as well.} Towards this end, fix a class $\mathcal{G}$ of possible two-player symmetric games,
+together with a probability measure $P_{\mathcal{G}}(G)$ for the occurrence probability of game
+$G \in \mathcal{G}$. The probability measure $P_{\mathcal{G}}$ encodes the statistical
+properties of the environment. A \textit{meta-game} is the tuple
+$ MG=\langle CM, \mathcal{G}, P_{\mathcal{G}},F \rangle$, where $CM$ is a set of choice
+mechanisms, $\mathcal{G}$ is a class of possible games, $P_{\mathcal{G}}(G)$ is the probability
+of game $G$ to occur, and $F:CM \times CM \rightarrow \mathbb{R}$ is the fitness function,
+defined as:
 \begin{align}
@@
 \end{align}
-Hence, $F(c,c')$ determines the evolutionary payoff of choice mechanism $c$ against $c'$ in the meta-game.
-The set $CM$ is though of as the set of choice mechanisms present within a given population that is playing the games from the class $\mathcal{G}$.
-Consequently, it is possible to compute the average fitness of $c$ against the population, that is given by:
+Hence, $F(c,c')$ determines the evolutionary payoff of choice mechanism $c$ against $c'$ in the
+meta-game. The set $CM$ can be thought of as the set of choice mechanisms present within a given
+population that is playing the games from the class $\mathcal{G}$. Consequently, it is possible
+to compute the average fitness of $c$ against the population, that is given by:
 \begin{align}
@@
 
-Meta-games are then abstract models for the evolutionary competition between choice
-mechanisms in interactive decision making contexts.
-Standard notions of evolutionary game theory apply to meta-games as well. A choice
-mechanism $c$ is a strict Nash equilibrium if $F(c,c) > F(c',c)$ for all $c'$; it is
-evolutionarily stable if for all $c'$ either (i) $F(c,c) > F(c',c)$ or (ii) $F(c,c) = F(c',c)$
-and $F(c,c') > F(c',c')$; it is neutrally stable if for all $c'$ either (i) $F(c,c) > F(c',c)$
-or (ii) $F(c,c) = F(c',c)$ and $F(c,c') \ge F(c',c')$
-\citep{Maynard-Smith1982:Evolution-and-t}. Similarly, evolutionary dynamics can be applied to
-meta-games. We will later turn towards replicator dynamics
-\citep{TaylorJonker1978:Evolutionary-St} and replicator mutator dynamics
+Meta-games are then abstract models for the evolutionary competition between choice mechanisms
+in interactive decision making contexts.  Standard notions of evolutionary game theory apply to
+meta-games as well. For example, a choice mechanism $c$ is a strict Nash equilibrium if
+$F(c,c) > F(c',c)$ for all $c'$; it is evolutionarily stable if for all $c'$ either (i)
+$F(c,c) > F(c',c)$ or (ii) $F(c,c) = F(c',c)$ and $F(c,c') > F(c',c')$; it is neutrally stable
+if for all $c'$ either (i) $F(c,c) > F(c',c)$ or (ii) $F(c,c) = F(c',c)$ and
+$F(c,c') \ge F(c',c')$ \citep{Maynard-Smith1982:Evolution-and-t}. Similarly, evolutionary
+dynamics can be applied to meta-games. We will later turn towards the replicator dynamic
+\citep{TaylorJonker1978:Evolutionary-St} and the replicator mutator dynamic
 \citep[e.g.][]{Nowak2006:Evolutionary-Dy}.
-%\todo{footnote with caveat about agent-level processes}
-
-\section{The Model} \label{sec:model}
-
-At first, the main subjective utilities that are going to compete against each other for the survival of the fittest are essentially two:
+
+\section{Example Application: Evolution of Preferences} \label{sec:model}
+
+To demonstrate the potential usefulness of a meta-game approach, we will compare a small
+selection of general ways of forming utility and preference representations against each
+other. As for utilities, consider initially:
 \begin{enumerate}
@@
 
-Although a thorough discussion of this issue goes beyond the scope of this work, let us say that these two kinds of belief underlie two different and alternative views on uncertainty.
-In front of uncertain events, a strict Bayesian will always form a precise belief, specified by a \textit{single} probability $\mu$.
-In the absence of any information about future uncertain events, the Bayesian would then invoke the \textit{principle of insufficient reason}, and accordingly choose a uniform probability over the possible outcomes.
-On the contrary, more recently many authors (REFERENCES) argued against the obligation of representing a belief by means of a single probability measure, opposite to the Bayesian prescriptions.
-They argue instead in favor of a more general account, according to which uncertainty can be unmeasurable, and represented by a (closed and convex) set of probabilities.
-This line of thought has been originated in decision theory by the famous Ellsberg's paradoxes (REF), and appears extremely relevant
-in game-theoretical contexts too. Indeed, in a recent paper \citet{BattCerrMM15} write:
+Although a thorough discussion of this issue goes beyond the scope of this work, let us say
+that these two kinds of belief underlie two different and alternative views on
+uncertainty. Faced with uncertain events, a strict Bayesian will always form a precise belief,
+specified by a \textit{single} probability $\mu$. In the absence of any information about
+future uncertain events, the Bayesian would then invoke the \textit{principle of insufficient
+  reason}, and accordingly choose a uniform probability over the possible outcomes. In
+contrast, others have argued against the obligation of representing a belief by means of a
+single probability measure, opposite to the Bayesian prescriptions (REFERENCES). They argue
+instead in favor of a more general account, according to which uncertainty can be unmeasurable,
+and represented by a (closed and convex) set of probabilities. This line of thought has been
+originated in decision theory by the famous Ellsberg's paradoxes (REF), and appears extremely
+relevant in game-theoretical contexts too. Indeed, in a recent paper \citet{BattCerrMM15}
+write:
 
@@
 
-\noindent In evolutionary game theory, for instance, players will obviously face
-uncertainty about the composition of the population that they are part of, and consequently
-about the co-player that they are randomly paired with at each round and about the co-player's
-action. In case of complete lack of information, a non-Bayesian player would thus entertain maximal unmeasurable uncertainty, i.e., a maximally imprecise belief. 
-As already anticipated,  we will see that the way agents can form beliefs, and the possibility of holding imprecise beliefs in particular, may have a fundamental impact on their evolutionary success.
+\noindent In evolutionary game theory, for instance, players will obviously face uncertainty
+about the composition of the population that they are part of, and consequently about the
+co-player that they are randomly paired with at each round and about the co-player's action. In
+case of complete lack of information, a non-Bayesian player would thus entertain maximal
+unmeasurable uncertainty, i.e., a maximally imprecise belief.\footnote{Such a radical
+  uncertainty could ensue, for example, if agents had no conception of their co-player or her
+  preferences. Unsophisticated agents, as considered in evolutionary game theory, might be
+  entirely unaware of the fact that they are engaged in social decision making \cite[e.g.,][for
+  game theoretic models of unawareness]{HeifetzMeier2009:Dynamic-Unaware}. IT is therefore
+  certainly not entirely ludicrous to consider radical uncertainty first and tend to more
+  sophisticated ways of forming beliefs later (more on this below).} As already anticipated, we
+will see that the way agents can form beliefs, and the possibility of holding imprecise beliefs
+in particular, may have a fundamental impact on their evolutionary success.
 
@@
 
-Finally, note that when the maxmin rule acts on subjective representation (obj, imp), the generated behavior corresponds to the classic maxmin (REF:vNM).
-When the maxmin rule acts on subjective representation (reg, imp), the agent's behavior is known as \textit{regret minimization}.
-The notion of regret in decision theory dates back at least to the work by
-\citet{Savage1951:The-theory-of-s}, and has later been developed by \citet{bell82}, \citet{fish82} and \citet{loosug82} independently. Recently,
+Finally, note that when the maxmin rule acts on subjective representation (obj, imp), the
+generated behavior corresponds to the classic maxmin (REF:vNM). When the maxmin rule acts on
+subjective representation (reg, imp), the agent's behavior is known as \textit{regret
+  minimization}.\footnote{The notion of regret in decision theory dates back at least to the
+  work by \citet{Savage1951:The-theory-of-s}, and has later been developed by \citet{bell82},
+  \citet{fish82} and \citet{loosug82} independently. Recently,
   \citet{HalpernPass2012:Iterated-Regret} showed how the use of regret minimization can give
-solutions to game theoretical-puzzles (like the Traveller's dilemma and the Centipede game) in a way that is closer to
-everyday intuition and empirical data. In this paper the notion of regret defined earlier is the same as in
-\citet{HalpernPass2012:Iterated-Regret}. Two facts stem from these observations.
-The first is related to our focus on different types of uncertainty that players may entertain.
+  solutions to game theoretical-puzzles (like the Traveller's dilemma and the Centipede game)
+  in a way that is closer to everyday intuition and empirical data. In this paper the notion of
+  regret defined earlier is the same as in \citet{HalpernPass2012:Iterated-Regret}.} Two facts
+stem from these observations.  The first is related to our focus on different types of
+uncertainty that players may entertain.
 \begin{fact} \label{fact:maxEU-minReg} 
@@
 
-\subsection{Example}
-Consider the coordination game in evolutionary payoffs $G$ depicted in figure \ref{coordgame1}.
-Since the game is symmetric, it suffices to specify the payoffs for the row player.
-Figure \ref{coordgame1} also represents the objective utility $\text{obj}^G$, since $\text{obj}^G= \pi^G$ by definition, whereas figure \ref{coordgame1reg} pictures the representation of $G$ in terms of regret-based utilities.
-While classic maxmin is indifferent
-between $I$ and $II$ (figure \ref{coordgame1}), regret minimization uniquely selects $II$ (figure \ref{coordgame1reg}).
+Here is a simple example that shows these choice mechanisms in action. Consider the
+coordination game in evolutionary payoffs $G$ depicted in figure \ref{coordgame1}. Since the
+game is symmetric, it suffices to specify the payoffs for the row player. Figure
+\ref{coordgame1} also represents the objective utility $\text{obj}^G$, since
+$\text{obj}^G= \pi^G$ by definition, whereas figure \ref{coordgame1reg} pictures the
+representation of $G$ in terms of regret-based utilities. While classic maxmin is indifferent
+between $I$ and $II$ (figure \ref{coordgame1}), regret minimization uniquely selects $II$
+(figure \ref{coordgame1reg}).
 \begin{figure}
@@
 
-\section{Results}\label{sec:results}
+\section{Some Results for the Example Scenario}\label{sec:results}
 

### 2016-06-25 paper/rev1_paperBlinded.tex
paper revisions first round complete

@@
 
-As we noticed, meta-games factor in statistical properties of the environment. For particular empirical
-purposes, one would consult a specific class of games $\mathcal{G}$ with appropriate,
-empirically informed probabilities $P_{\mathcal{G}}$ in order to match the natural environment of a given
-population. 
-%But for our theoretical purposes we adopt another approach. 
-For our theoretical purposes, let $\mathcal{G}$ be a set of
-symmetric two-player games with two acts for a start. A game is then individuated solely by its payoff
-function, i.e., by a quadruple of numbers $G=(a,b,c,d)$. As for the occurrence probability $P_{\mathcal{G}}(G)$ of
-game $G$, we imagine that the values $a,b,c,d$ are i.i.d.~random variables sampled from the set $ \lbrace 0, \dots, 10 \rbrace$ according to uniform probability $P_{V}$.
-The probability distribution of games is thus the fourfold product of $P_{V}$, that is, $P_{\mathcal{G}}=P_{V}^{4}$.
-Using Monte Carlo simulations, we can then
-approximate the values of equation~(\ref{eq:FittnessChoiceMechGamePairwise})
-to construct meta-game payoffs. Results based on $100,000$ randomly sampled games are given in
+As we noticed, meta-games factor in statistical properties of the environment. For particular
+empirical purposes, one could consult a specific class of games $\mathcal{G}$ with appropriate,
+maybe empirically informed probabilities $P_{\mathcal{G}}$ in order to match the natural
+environment of a given population. For our purposes, let $\mathcal{G}$ be a set of symmetric
+two-player games with two acts for a start. A game is then individuated solely by its payoff
+function, i.e., by a quadruple of numbers $G=(a,b,c,d)$. As for the occurrence probability
+$P_{\mathcal{G}}(G)$ of game $G$, we imagine that the values $a,b,c,d$ are i.i.d.~random
+variables sampled from the set $ \lbrace 0, \dots, 10 \rbrace$ according to uniform probability
+$P_{V}$. Using Monte Carlo simulations, we can then approximate the values of
+equation~(\ref{eq:FittnessChoiceMechGamePairwise}) to construct meta-game payoffs. Results
+based on $100,000$ randomly sampled games are given in
 table~\ref{tab:ExpectedFitness_4Types}.\footnote{Concretely, $100,000$ games were sampled
@@
   each game, the action choices of all four choice mechanisms were determined and payoffs from
-  all pairwise encounters recorded. The number
-  in each cell of table~\ref{tab:ExpectedFitness_4Types} is the average payoff for the choice
-  mechanism listed in the row when matched with the choice mechanism in the column.}
+  all pairwise encounters recorded. The number in each cell of
+  table~\ref{tab:ExpectedFitness_4Types} is the average payoff for the choice mechanism listed
+  in the row when matched with the choice mechanism in the column.}
 
@@
 completely different representation with altogether different utility and belief would
-then be $\epsilon^2$. With these assumptions about ``component-wise mutations'', numerical
+then be $\epsilon^2$. With these assumptions about ``component-wise mutations,'' numerical
 simulations of the (discrete time) \emph{replicator mutator dynamics}
@@
 %fitness. Moreover,
-objective preference representations are not necessarily favored by
-natural selection. In particular, under generous circumstances objective preferences are outperformed by non-veridical regret preferences, if agents may have imprecise beliefs.
-This
-tells us that the main conclusions drawn in the previous section based on the approximated meta-game of table~\ref{tab:ExpectedFitness_4Types} hold more generally 
-for
-arbitrary $2 \times 2$ symmetric games with i.i.d. sampled payoffs.
-
-Even more in general, we can show that the same result obtains for any imprecise belief, not only for maximally uncertain players. 
-Let the uncertainty held by a player be defined by a closed and convex set of probabilities $ [s,t] \subseteq \Delta(A) $ over the co-player's actions, where $s$ is the lower probability and $t$ is the upper probability of action $II$.
-We can then prove the following proposition, which
-is the equivalent of Proposition~\ref{proposition1} for any possible (not necessarily
+objective preference representations are not necessarily favored by natural selection;
+objective preferences can be outperformed by non-veridical regret preferences, if agents may
+have imprecise beliefs.  This tells us that the main conclusions drawn in the previous section
+based on the approximated meta-game of table~\ref{tab:ExpectedFitness_4Types} hold more
+generally for arbitrary $2 \times 2$ symmetric games with i.i.d. sampled payoffs.
+
+This result presupposes occasional imprecise beliefs and the maximin decision rule (more on
+this below). The assumed imprecise beliefs do not need to be maximally uncertain, however.  Let
+the uncertainty held by a player be defined by a closed and convex set of probabilities
+$ [s,t] \subseteq \Delta(A) $ over the co-player's actions, where $s$ is the lower probability
+and $t$ is the upper probability of action $II$.  We can then prove the following proposition,
+which is the equivalent of Proposition~\ref{proposition1} for any possible (not necessarily
 maximal) degree of uncertainty $[s,t]$, with $s \neq t$. There is only one difference: we are
-now going to require i.i.d. drawing of a \emph{continuous} random variable. This is due
-to the fact that, for arbitrarily small intervals $[s,t]$, objective players $([s,t],\text{obj})$
-and regret players $([s,t],\text{reg})$ can behave as holding a unique probability measure
-(precise belief) if the underlying payoff space is not dense. The reason for this technical requirement
+now going to require i.i.d. drawing of a \emph{continuous} random variable. This is due to the
+fact that, for arbitrarily small intervals $[s,t]$, objective players $([s,t],\text{obj})$ and
+regret players $([s,t],\text{reg})$ can behave as holding a unique probability measure (precise
+belief) if the underlying payoff space is not dense. The reason for this technical requirement
 will become clearer from the proof.
 
-\begin{proposition} \label{proposition2}
-In the class of $2\times2$ symmetric games generated by i.i.d. drawing
-of a continuous random variable that takes values in a real interval
-$(\underline{r},\overline{r})$ with probability density $P_V$, for
-any imprecise belief $[s,t]$, the only
-evolutionarily stable state of a population with regret players $([s,t],\text{reg})$
-and objective players $([s,t],\text{obj})$ is a monomorphic state of $([s,t],\text{reg})$
-players.
+\begin{proposition} \label{proposition2} In the class of $2\times2$ symmetric games generated
+  by i.i.d. drawing of a continuous random variable from a distribution with density $P_v$ with
+  support $(\underline{r},\overline{r})$, for any imprecise
+  belief $[s,t]$, the only evolutionarily stable state of a population with regret players
+  $([s,t],\text{reg})$ and objective players $([s,t],\text{obj})$ is a monomorphic state of
+  $([s,t],\text{reg})$ players.
 \end{proposition}
+
+This tells us that regret-based preferences can also outperform objective preference
+representations when agents are capable of learning or otherwise restrict their assumptions
+about the co-player's behavior as long as there is, at least on occasion, some imprecision in
+their beliefs. We will enlarge on the issue of belief formation after having covered some more
+relevant extensions in the next section.
 
@@
 How do the basic results from the previous section carry over to richer models?
-Section~\ref{sec:more-types} first introduces further conceptually interesting subjective representations
-that have been considered in the literature. Section~\ref{sec:n-times-n} then addresses the
-case of $n \times n$ games for $n \ge 2$. Finally, Section~\ref{sec:solitary-decisions} ends
-with a brief comparison to the case of solitary decision making.
-
-\subsection{More Representations}
+Section~\ref{sec:more-types} first introduces further conceptually interesting subjective
+representations that have been considered in the literature. Section~\ref{sec:n-times-n} then
+addresses the case of $n \times n$ games for $n \ge 2$. Finally,
+Section~\ref{sec:solitary-decisions} ends with a brief comparison to the case of solitary
+decision making.
+
+\subsection{More Preference Types}
 \label{sec:more-types}
 
-Beyond objective and regret-based utilities, other subjective preferences have been investigated, especially in behavioral economics and in evolutionary game theory. A
-famous example is the \textit{altruistic} preference \citep[e.g.,][]{Beck76,BestGuth98}, summoned to
-explain the possibility of altruistic behavior. At the other end of the spectrum, the \emph{competitive}
-preference is located. The two subjective utilities are defined as follows.
+Our claim is not that regret types are the best on the market. We have only compared regret
+types to objective types so far. The space of possible preference types is enormous. Let us
+look at least at two other types of subjective preferences have been investigated, especially
+in behavioral economics and in evolutionary game theory. A famous example is the
+\textit{altruistic} preference \citep[e.g.,][]{Beck76,BestGuth98}, summoned to explain the
+possibility of altruistic behavior. At the other end of the spectrum, the \emph{competitive}
+preference is located. The two subjective utilities are defined as follows:
 \begin{enumerate}
@@
 table~\ref{tab:ExpectedFitness_2x2_Full} end up in population states consisting of only these
-three types in arbitrary proportion.
+three types in variable proportion.
 
@@
 
-Results from Section~\ref{sec:basic-model-1} relied heavily on Fact~\ref{fact:equivalence2x2}, that
+Results from Section~\ref{sec:results} relied heavily on Fact~\ref{fact:equivalence2x2}, which
 is no longer true when we look at arbitrary $n \times n$ games.
 Table~\ref{tab:ExpectedFitness_10x10} gives approximations of expected fitness in the class of
-$n \times n$ symmetric games. Concretely,
-the numbers in table~\ref{tab:ExpectedFitness_10x10} are averages of evolutionary payoffs obtained in
-100,000 randomly sampled symmetric games, where each game was sampled by first picking a number of acts
-$n \in \set{2, \dots, 10}$ uniformly at random, and then filling the necessary $n \times n$
-payoff matrix with i.i.d.~sampled numbers, as before.
+$n \times n$ symmetric games. Concretely, the numbers in table~\ref{tab:ExpectedFitness_10x10}
+are averages of evolutionary payoffs obtained in 100,000 randomly sampled symmetric games,
+where each game was sampled by first picking a number of acts $n \in \set{2, \dots, 10}$
+uniformly at random, and then filling the necessary $n \times n$ payoff matrix with
+i.i.d.~sampled numbers, as before.
 
@@
 strictly dominated by $(\text{reg}, \text{prc})$ and by $(\text{obj}, \text{prc})$ in the
-meta-game from table~\ref{tab:ExpectedFitness_10x10}. This means that while simple regret minimization
-can thrive in some evolutionary contexts, there are also contexts where it is
+meta-game from table~\ref{tab:ExpectedFitness_10x10}. This means that while simple regret
+minimization can thrive in some evolutionary contexts, there are also contexts where it is
 demonstrably worse off. While this may be bad news for regret minimizing types
@@
 $(\text{obj}, \text{prc})$ are behaviorally equivalent in general, it remains that selection
-based on meta-games constructed from $n \times n$ games will still not eradicate regret preferences.
-%So, although regret types may not be selected for in this case, they are also not selected against.
+based on meta-games constructed from $n \times n$ games will still not eradicate regret
+preferences. %So, although regret types may not be selected for in this case, they are also not selected against.
 
 On the other hand, there are plenty of ways in which the basic insight from
-Propositions~\ref{proposition1} and \ref{proposition2} that regret-based utilities are strictly better than
-veridical objective utilities in case of imprecise beliefs can make for situations in which
-evolution would select for regret types exclusively, even in $n \times n$ games. If, for
-example, the belief of a player is a trait that biological evolution has no bite on, but rather
-something that the particular choice situation would exogenously give us (possibly because of the different amount of information available in different choice situations), then regret-based
-preferences can again drive out veridical preferences altogether. For example,
-suppose that only preferences compete and that agents' beliefs are exogenously given,
-in such a way that both players hold precise (Bayesian) uniform beliefs with probability $p$ and they both have maximally imprecise
-beliefs otherwise. This transforms the meta-game from table~\ref{tab:ExpectedFitness_10x10} into a
-simpler $4 \times 4$ meta-game in which the payoff obtained by a subjective utility is the weighted
-average over the payoffs of the subjective representations including that utility in
-table~\ref{tab:ExpectedFitness_10x10}. Setting $p = 0.98$ for illustration, we get the meta-game in table~\ref{tab:ExogeneousEpistemics}.
+Propositions~\ref{proposition1} and \ref{proposition2} can make for situations in which
+evolution would favor regret types, even in $n \times n$ games. If, for example, the belief of
+a player is a trait that biological evolution has no bite on, but rather something that the
+particular choice situation would exogenously give us (possibly because of the different amount
+of information available in different choice situations), then regret-based preferences can
+again drive out veridical preferences altogether. For example, suppose that only preferences
+compete and that agents' beliefs are exogenously given, in such a way that both players hold
+precise (Bayesian) uniform beliefs with probability $p$ and they both have maximally imprecise
+beliefs otherwise. This transforms the meta-game from table~\ref{tab:ExpectedFitness_10x10}
+into a simpler $4 \times 4$ meta-game in which the payoff obtained by a subjective utility is
+the weighted average over the payoffs of the subjective representations including that utility
+in table~\ref{tab:ExpectedFitness_10x10}. Setting $p = 0.98$ for illustration, we get the
+meta-game in table~\ref{tab:ExogeneousEpistemics}.
 \begin{table}[]
@@
 
-\iffalse
-\subsection{Arbitrary probabilistic beliefs}
-\label{sec:arbitr-prob-beli}
-
-So far, we have assumed that epistemic types $\text{prc}$ hold an unbiased, flat belief. It is
-worthwhile considering what happens when this assumption is relaxed and we allow agents with
-probabilistic beliefs to make use of the full spectrum of probabilistic beliefs. It should be
-clear that quality of beliefs directly impacts prospects of successful decision making: if a
-decision maker knows the actual state, or can put a high level of credence on the actual state,
-accumulated fitness can be expected to be high. We see this, unsurprisingly, in numerical
-simulations. We looked at the average payoff accumulated in 100,000 decision problems sampled
-as before, except that for belief types with probabilistic beliefs we sampled a random
-probabilistic belief $p$ (from an unbiased Dirichlet distribution) and chose the actual world
-state with probability weights $p$. This effectively implements a bias for beliefs of the
-decision maker that tend to put more weight on the actual state (although the procedure does
-admittedly perverse the natural chicken-and-egg logic in this case that the actual world state
-should come first and beliefs be a function of it). As a result, the average payoffs of types
-$\tuple{\text{reg}, \text{prc}}$ and $\tuple{\text{obj}, \text{prc}}$ are still the exact same
-(because we compare what agents with different preference types would do under the same
-beliefs; we are not interested in statistical fluctuations given one type better beliefs by
-pure happenstance), but with $7.125$ notably higher than before. In effect, better
-probabilistic beliefs lead to better decisions. If agents can learn, reason and extrapolate to
-form better probabilistic beliefs, that will help them whenever they take their beliefs into
-account.
-
-But this is orthogonal to the arguments in this paper, where the focus is on possibilities for
-the evolution of non-veridical preferences. We know from Fact~\ref{fact:maxEU-minReg} that
-regret types and veridical preference types, when paired with probabilistic belief types that
-maximize/minimize expectations, are behaviorally equivalent, \emph{no matter what they believe},
-as long as they belief the same. So, if learning, insight and statistical knowledge of a
-recurrent situation \emph{can} be brought to bear, this will not make evolution select against
-regret-based preferences. If, on the other hand, agents have no basis for probabilistic
-beliefs, then we have shown that there are general and basic circumstances in which
-regret-based preferences can actually be selected, despite their non-veridicality.
-\fi
-
-\section{Related Literature}
-
-do you think we really need a section for this?
+\subsection{Informed or Sophisticated Beliefs}
+
+Since our main purpose here was to illustrate the potential usefulness of a meta-game approach
+by a comparison of regret and objective preference schemes, we have neglected entirely a very
+important and interesting issue, namely the evolution of ways of forming more concrete beliefs
+about a co-player's likely behavior or the actual state of the world. It is obvious (and shows
+in numerical simulations) that agents whose beliefs are more likely to put more weight on the
+actual world state (in solitary decisions) or on the co-player's actual choice will accrue
+higher fitness-payoffs than radically uncertain players. For reasons of space we must,
+unfortunately, leave a deeper exploration of belief type evolution to another occasion. Two
+remarks are in order nonetheless. Firstly, belief type evolution can be studied without
+conceptual hurdles in a meta-game approach, so that there is no principled argument here
+against the main methodological contribution of this paper. Secondly, our results regarding the
+comparison between regret and objective preference types remain to be informative, even if we
+allow agents to learn or reason strategically. This is because we know from
+Fact~\ref{fact:maxEU-minReg} that regret and objective preferences come up behaviorally
+equivalent when paired with precise probabilistic beliefs (given a maximin decision rule). This
+holds no matter what the content of that belief is. So, if learning, reasoning or statistical
+knowledge of a recurrent situation \emph{can} be brought to bear, this will not make evolution
+select against regret-based preferences. If, on the other hand, agents resort to imprecise
+beliefs at least occasionally (e.g., when they are unaware of the co-player or her utilities,
+or when strategic reasoning cannot reduce all uncertainty about the opponent's choice), then we
+have shown that there are general and basic circumstances in which regret-based preferences
+could even be favored by natural selected over objective preferences.
 
@@
 
-The assumption that players and decision makers maximize their (subjective) preferences is central through all economic literature, and the maximization of actual (objective) payoffs is often justified by appealing to evolutionary arguments and natural
-selection. In contrast to the standard view, we showed the
-existence of player types with subjective utilities different
-from the actual evolutionary payoffs that can outperform types whose
-subjective utilities coincide with the evolutionary payoffs.
-While the literature on evolution of preferences has focused
-on fixed games, we have adopted a
-more general approach here. We suggested that attention
-to “meta-games” is crucial, because what may be a good
-subjective representation in one type of game (e.g., cooperative preferences in the Prisoner’s Dilemma class) need not
-be generally beneficial. Taken together, we presented a variety of plausible circumstances in which evolutionary competition between choice
-mechanisms on a larger class of games can favor non-veridical preference representations focusing on regret.
+The assumption that players and decision makers maximize their (subjective) preferences is
+central through all economic literature, and the maximization of actual (objective) payoffs is
+often justified by appealing to evolutionary arguments and natural selection. In contrast to
+the standard view, we showed the existence of player types with subjective utilities different
+from the actual evolutionary payoffs that can outperform types whose subjective utilities
+coincide with the evolutionary payoffs.  While the literature on evolution of preferences has
+focused on fixed games, we have adopted a more general approach here. We suggested that
+attention to “meta-games” is crucial, because what may be a good subjective representation in
+one type of game (e.g., cooperative preferences in the Prisoner’s Dilemma class) need not be
+generally beneficial. Taken together, we presented a variety of plausible circumstances in
+which evolutionary competition between choice mechanisms on a larger class of games can favor
+non-veridical preference representations focusing on regret.
 
 Meta-games are useful tools for probing into conceptual questions about ecological
-rationality. The approach is rich and general, with many possible further
-applications imaginable beyond the case study presented here. For example, the evolutionary
-investigation of different risk and ambiguity attitudes when competing against each other may bring new insights on both behavioral and theoretic
-decision making under uncertainty, as well as on many issues in theoretical biology and
-behavioral ecology. Moreover, variability in the action selection function has been entirely
-ignored in this paper. Finally, while this paper only used dummy models of diverse decision
-environments, the meta-game approach also allows for empirically informed models of rich and
-variable environments.
+rationality. The approach is rich and general, with many possible further applications
+imaginable beyond the case study presented here. For example, the evolutionary investigation of
+different risk and ambiguity attitudes when competing against each other may bring new insights
+on both behavioral and theoretic decision making under uncertainty, as well as on many issues
+in theoretical biology and behavioral ecology. Moreover, this paper only considered one
+decision rule (maximin), leaving it to future work to explore evolutionary competition here as
+well. Finally, while this paper only used dummy models of diverse decision environments, the
+meta-game approach also allows for empirically informed models of rich and variable
+environments.
 

### 2016-06-30 paper/rev1_paperBlinded.tex
Paolo edits

@@
   from evolutionary game theory to study the evolutionary competition between \emph{choice
-    mechanisms} in a rich and variable environment. A choice mechanism is a way of subjectively
+    mechanisms} in a rich and variable multi-game environment. A choice mechanism is a way of subjectively
   representing a decision situation, paired with a method for choosing an act based on this
   subjective representation. We demonstrate the usefulness of this approach by a case study
-  that shows how subjective preference representations in terms of regret that differ from the
+  that shows how subjective representations in terms of regret that differ from the
   actual fitness can be evolutionarily advantageous.
@@
 response to this and adding to recent like-minded approaches, this paper introduces a general
-meta-game model that conservatively extends the scope of evolutionary game theory to deal with
-evolutionary selection of choice mechanisms in variable environments \citep[see, inter alia,
-related work
-by][]{Harley1981:Learning-the-Ev,ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o,OConnor2016:Evolving-to-Gen}.\mf{please
-insert more references here; maybe use a footnote right here to pick out some of the most
-important related pieces and say how our contribution is novel and shiny}
+\emph{meta-game} model that conservatively extends the scope of evolutionary game theory to deal with
+evolutionary selection of choice mechanisms in variable environments \citep[see also][]{Harley1981:Learning-the-Ev,ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o,OConnor2016:Evolving-to-Gen,RayoBecker07,Zollman2008,SkyrmsZollman10,BednarPage07}.\footnote{In particular, similar ideas appear in \citep{RayoBecker07,Zollman2008,BednarPage07}.
+\citep{BednarPage07} use a multi-game framework, composed of a fixed selection of six possible games, to study the emergence of different cultural behaviors, and model agents as finite-state automata playing games from the fixed selection.
+\citep{Zollman2008} explains seemingly ``irrational'' fair behavior in social dilemmas (like the Ultimatum game) by means of a model where agents have to play the Ultimatum game together with the Nash bargaining game, but they are constrained to choose the same strategy for both games.
+Finally, \citep{RayoBecker07} consider, in a more decision-theoretic setting, what subjective utility function a cognitively limited agent should be endowed with in order to maximize her evolutionary fitness.
+Our framework can then be viewed as a generalization of those models, mainly in that here players do not suffer any cognitive constraint, and we allow for larger and possibly variable classes of games.}
 
@@
 evolution should take variability in uncertainty representation into account as well. We
-demonstrate that if agents have imprecise probabilistic beliefs
-\citep[e.g.][]{gardsah82,levi74,walley96}, faithful and objective representation in terms of
+demonstrate that if agents have \emph{imprecise} probabilistic beliefs
+\citep[e.g.,][]{gardsah82,levi74,walley96}, faithful and objective representations in terms of
 true, real evolutionary fitness can be outperformed by subjective (e.g., regret-based)
@@
 The paper is organized as follows. Section \ref{sec:rati--subj} sets the scene by reviewing
-different perspectives no rational choice. Section~\ref{sec:subj-ut,bel,dec-rules} then
-introduces the meta-game approach. In doing so it covers key notions such as choice mechanism,
-decision rules and subjective representations, all with an eye towards the specific application
-to the evolution of preferences in Section~\ref{sec:model}. Section~\ref{sec:results} contains
-our main results for this application and Section \ref{sec:extensions} discusses some
-interesting extensions.
+different perspectives on rational choice. Section~\ref{sec:subj-ut,bel,dec-rules}
+introduces the meta-game approach. In doing so, it covers key notions such as choice mechanisms,
+decision rules and subjective representations, all with an eye towards the evolutionary applications
+of Section~\ref{sec:model}. Section~\ref{sec:results} contains
+the main results, and Section \ref{sec:extensions} discusses some
+interesting extensions. Finally, Section~\ref{sec:conclusion} concludes.
 
@@
 \citep[e.g.,][]{Anderson1991:Is-human-cognit,ChaterOaksford2000:The-Rational-An,HagenChater2012:Decision-Making}. Adaptationism
-aims to explain rational behavior by appeal to evolutionary considerations: DMs have acquired
+aims to explain rational behavior by appealing to evolutionary considerations: DMs have acquired
 choice mechanisms that have proved to be adaptive with respect to the variable environment
@@
 about the nature of rational choice, we here suggest to think of a choice mechanism
-as a map from choice situations to action choices which includes an explicit level of
-\emph{subjective representation} of the situation. Specifically, a subjective representation is a general way of forming preferences and beliefs about the choice situation, and we
+as a map from choice situations to action choices which includes an explicit level of subjective representation of the situation.
+Specifically, a \emph{subjective representation} is a general way of forming preferences and beliefs about the choice situation, and we
 are most interested in the question which subjective representations, and which choice mechanisms in general, are better than others
@@
 
-\section{Choice Mechanisms  \& Meta-Games} 
+\section{Choice Mechanisms and Meta-Games} 
 \label{sec:subj-ut,bel,dec-rules}
@@
 $$ \text{Decision Rule: Utility }\times\text{ Beliefs } \rightarrow \text{ Actions.}  $$
-The utility of an agent can be formally expressed by a function
+The subjective utility of an agent can be formally expressed by a function
 $u:W \times A \rightarrow \mathbb{R} $, where $A$ stands for a (finite) set of actions
@@
 many different ways to describe beliefs, but for concreteness of later applications we here
-assume that the agent's beliefs are represented in terms of a (possibly singleton) set of
+assume that the agent's beliefs are represented in terms of a (possibly singleton) convex compact set of
 probability functions $\Gamma \subseteq \Delta(W) $ over the possible states of the
-world. Examples of well-known decision rules from the literature that will be useful later are:
+world. Given a utility $u$ and a belief $\Gamma$, examples of well-known decision rules from the literature that we will encounter later are:
 \begin{enumerate}
@@
 when the set $\Gamma$ is a singleton, and in turn expected utility maximization reduces to
-Laplace rule when the belief $\mu$ is a uniform probability over the states.  \mf{do we need
-  ``maximax''?}
+Laplace rule when the belief $\mu$ is a uniform probability over the states.
 
 As mentioned previously, for a choice mechanism to prescribe an action, the decision rule needs
-to be given a specific subjective utility and belief as input. A \textit{subjective
-  representation} of a decision problem is the pair $(u,\Gamma)$, consisting of a subjective
-utility and a subjective belief. We are specifically interest in general and systematic ways of
+to be given a specific utility $u$ and belief $\Gamma$ as input. We call the pair $(u,\Gamma)$ a \textit{subjective
+  representation} of the decision problem. In the following, we investigate the evolutionary fitness of general and systematic ways of
 forming such subjective representations across many different decision situations.
@@
 
-A game is an interactive decision situation.  For a given game
+A \emph{fitness game} is an interactive decision situation.  For a given fitness game
 $G=\langle N, (A_i,\pi^G_i)_{i \in N} \rangle$, let us denote the evolutionary payoff, or
@@
 $\pi^G_1(a_1, a'_2)= \pi^G_2(a'_1, a_2)=:\pi^G(a,a')$.\footnote{Since payoff functions are
-  symmetric, we will simply write $\pi^G(a, a')$ for $\pi^G_1(a_1, a'_2)$ and $A:=A_1=A_2$, as
-  usual. However, notice that all the definitions and results can be extended to more general
-  cases.} Then, the evolutionary fitness of a subjective representation $(u_c,\Gamma_c)$ is
-measured in terms of the fitness of a choice mechanism that contains it, all else equal.
-Formally, the fitness payoff of a choice mechanism $c$ against choice mechanism $c'$ in a
-symmetric two-player game $G=\langle \{1,2\}, A, \pi^G \rangle$ is the expected payoff of $c$
-against $c'$ in $G$:
+  symmetric, we simply write $\pi^G(a, a')$ for $\pi^G_1(a_1, a'_2)$ and $A:=A_1=A_2$, as
+  usual. However, notice that all definitions and results can be extended to more general
+  cases.} The fitness of a choice mechanism $c$ with decision rule $a_{c}^{*}$ and subjective representation $(u_c,\Gamma_c)$ is
+measured in terms of the expected evolutionary payoff of $c$.
+Formally, the fitness of choice mechanism $c$ against choice mechanism $c'$ in a
+symmetric two-player game $G=\langle \{1,2\}, A, \pi^G \rangle$ is given by:
 
 $$
-F_G(c,c')= \pi^G(a_c^*(u_c^G,\Gamma_c),a_{c'}^*(u_{c'}^G,\Gamma_{c'})), \footnote{Whenever a choice mechanism
+F_G(c,c')= \pi^G(a_c^*(u_c^G,\Gamma_c),a_{c'}^*(u_{c'}^G,\Gamma_{c'})). \footnote{Whenever a choice mechanism
   would not select a unique action, we assume that the player chooses one of the equally
@@
 $$
-where $a^*_c$ is the decision rule of choice mechanism $c$. Given the game theoretic setting,
-the subjective utility $u_c$ is now a function $u_c^G:A \times A \rightarrow \mathbb{R}$, and
+Given the game theoretic setting,
+the subjective utility $u^{G}_c$ is now a function $u_c^G:A \times A \rightarrow \mathbb{R}$, and
 the subjective belief $\Gamma_c$ is a set of probability functions over the co-player's
-actions, $ \Gamma \subseteq \Delta(A)$.
+actions, $ \Gamma_c \subseteq \Delta(A)$.
 
@@
 biased by the choice of the particular game. To avoid these limitations, we consider a
-\textit{class} of possible games that can be played within a population
-(REFERENCES). \mf{please insert some references to other papers that use a multi-game approach
-  as well.} Towards this end, fix a class $\mathcal{G}$ of possible two-player symmetric games,
+\textit{class} of possible games. Towards this end, fix a class $\mathcal{G}$ of possible two-player symmetric games,
 together with a probability measure $P_{\mathcal{G}}(G)$ for the occurrence probability of game
-$G \in \mathcal{G}$. The probability measure $P_{\mathcal{G}}$ encodes the statistical
-properties of the environment. A \textit{meta-game} is the tuple
+$G \in \mathcal{G}$. Intuitively, the probability $P_{\mathcal{G}}$ encodes the statistical
+properties of the environment. A \textit{meta-game} is then a tuple
 $ MG=\langle CM, \mathcal{G}, P_{\mathcal{G}},F \rangle$, where $CM$ is a set of choice
 mechanisms, $\mathcal{G}$ is a class of possible games, $P_{\mathcal{G}}(G)$ is the probability
-of game $G$ to occur, and $F:CM \times CM \rightarrow \mathbb{R}$ is the fitness function,
+of game $G$ to occur, and $F:CM \times CM \rightarrow \mathbb{R}$ is the (meta-)fitness function,
 defined as:
@@
 Hence, $F(c,c')$ determines the evolutionary payoff of choice mechanism $c$ against $c'$ in the
-meta-game. The set $CM$ can be thought of as the set of choice mechanisms present within a given
-population that is playing the games from the class $\mathcal{G}$. Consequently, it is possible
+meta-game. The set $CM$ can be thought of as the set of choice mechanisms that are present within a given
+population playing the games from the class $\mathcal{G}$. Consequently, it is possible
 to compute the average fitness of $c$ against the population, that is given by:
@@
 $F(c,c') \ge F(c',c')$ \citep{Maynard-Smith1982:Evolution-and-t}. Similarly, evolutionary
-dynamics can be applied to meta-games. We will later turn towards the replicator dynamic
-\citep{TaylorJonker1978:Evolutionary-St} and the replicator mutator dynamic
-\citep[e.g.][]{Nowak2006:Evolutionary-Dy}.
-
-\section{Example Application: Evolution of Preferences} \label{sec:model}
-
-To demonstrate the potential usefulness of a meta-game approach, we will compare a small
-selection of general ways of forming utility and preference representations against each
-other. As for utilities, consider initially:
+dynamics can be applied to meta-games. Later we will also turn towards a dynamical analysis in terms of replicator dynamics
+\citep{TaylorJonker1978:Evolutionary-St} and replicator mutator dynamics
+\citep[e.g.,][]{Nowak2006:Evolutionary-Dy}.
+
+\section{Evolution of Preferences} \label{sec:model}
+
+To demonstrate the usefulness of a meta-game approach, we compare a
+selection of general ways of forming belief and preference representations against each
+other. As for subjective preferences, consider initially:
 \begin{enumerate}
@@
 
+As motivation for this comparison, it is to be stressed that regret minimization is one of the main alternatives to utility (or value) maximization in the literature on decision criteria (see also \cite{bleWakker15}).
 For a start, the subjective beliefs that we take into consideration are also two:
@@
 specified by a \textit{single} probability $\mu$. In the absence of any information about
-future uncertain events, the Bayesian would then invoke the \textit{principle of insufficient
+future uncertain events, the Bayesian would mostly invoke the \textit{principle of insufficient
   reason}, and accordingly choose a uniform probability over the possible outcomes. In
 contrast, others have argued against the obligation of representing a belief by means of a
-single probability measure, opposite to the Bayesian prescriptions (REFERENCES). They argue
-instead in favor of a more general account, according to which uncertainty can be unmeasurable,
-and represented by a (closed and convex) set of probabilities. This line of thought has been
-originated in decision theory by the famous Ellsberg's paradoxes (REF), and appears extremely
-relevant in game-theoretical contexts too. Indeed, in a recent paper \citet{BattCerrMM15}
+single probability measure, opposite to the Bayesian paradigm (e.g., \cite{GilbMarin13}). They argue
+instead in favor of a more encompassing account, according to which uncertainty can be \emph{unmeasurable},
+and represented by a (convex and compact) set of probabilities (e.g., \cite{gilsch89}). This line of thought has been
+originated in decision theory by the famous Ellsberg's paradoxes \citep{ells61}, and appears extremely
+relevant in game-theoretic contexts too. Indeed, in a recent paper \citet{BattCerrMM15}
 write:
@@
 \begin{quote}
-  Such uncertainty is inherent in situations of strategic interaction. This is quite obvious
+  Such [unmeasurable] uncertainty is inherent in situations of strategic interaction. This is quite obvious
   when such situations have been faced only a few times. (p.~646)
@@
 
-\noindent In evolutionary game theory, for instance, players will obviously face uncertainty
-about the composition of the population that they are part of, and consequently about the
+\noindent In evolutionary game theory, for instance, players obviously face uncertainty
+about the composition of the population that they are part of, and consequently about the (type of)
 co-player that they are randomly paired with at each round and about the co-player's action. In
-case of complete lack of information, a non-Bayesian player would thus entertain maximal
+case of complete lack of information about the composition of the population, a non-Bayesian player would thus entertain maximal
 unmeasurable uncertainty, i.e., a maximally imprecise belief.\footnote{Such a radical
-  uncertainty could ensue, for example, if agents had no conception of their co-player or her
+  uncertainty could ensue, for example, if agents have no conception of their co-player or her
   preferences. Unsophisticated agents, as considered in evolutionary game theory, might be
-  entirely unaware of the fact that they are engaged in social decision making \cite[e.g.,][for
-  game theoretic models of unawareness]{HeifetzMeier2009:Dynamic-Unaware}. IT is therefore
-  certainly not entirely ludicrous to consider radical uncertainty first and tend to more
+  entirely unaware of the fact that they are engaged in social decision making (see \cite{HeifetzMeier2009:Dynamic-Unaware}, for
+  game-theoretic models of unawareness). It is therefore
+  not ludicrous to consider radical uncertainty first and tend to more
   sophisticated ways of forming beliefs later (more on this below).} As already anticipated, we
-will see that the way agents can form beliefs, and the possibility of holding imprecise beliefs
-in particular, may have a fundamental impact on their evolutionary success.
-
-As for the decision rule, we assume that the players use the maxmin rule. This is in line with most of the representation
-results of decision making under uncertainty \citep[e.g.,][]{gilsch89,KlibMarMuk05,GhirMar02},
-and seems justified by empirical observations too.
-Ellsberg's paradoxes are prominent examples (\citet{ells61}), and evidence from experimental literature suggests that agents are mostly uncertainty averse \citep[e.g.,][]{TrautKuil16}.
+will see that the way agents form beliefs, and the possibility of holding imprecise beliefs
+in particular, can have a fundamental impact on their evolutionary success.
+
+As for the decision rule, we assume that players use the maxmin rule. This is in line with many representation
+results of decision making under unmeasurable uncertainty \citep[e.g.,][]{gilsch89,GhirMar02},
+and seems corroborated by empirical findings too.
+Ellsberg's paradoxes are prominent examples (\citet{ells61}), and evidence from experimental literature suggests that agents are generally averse to unmeasurable uncertainty \citep[e.g.,][]{TrautKuil16}.
 
 Finally, note that when the maxmin rule acts on subjective representation (obj, imp), the
-generated behavior corresponds to the classic maxmin (REF:vNM). When the maxmin rule acts on
+generated behavior corresponds to the classic maxmin strategy \citep{neumorg44}. When the maxmin rule acts on
 subjective representation (reg, imp), the agent's behavior is known as \textit{regret
@@
   work by \citet{Savage1951:The-theory-of-s}, and has later been developed by \citet{bell82},
-  \citet{fish82} and \citet{loosug82} independently. Recently,
+  \citet{Fishburn1982} and \citet{loosug82} independently. Recently,
   \citet{HalpernPass2012:Iterated-Regret} showed how the use of regret minimization can give
-  solutions to game theoretical-puzzles (like the Traveller's dilemma and the Centipede game)
+  solutions to game-theoretic puzzles (like the Traveller's dilemma and the Centipede game)
   in a way that is closer to everyday intuition and empirical data. In this paper the notion of
@@
 %  by the maximization of expected utility for the negative regret transformation of $G$
-Under any identical precise (Bayesian) belief, maximization of expected evolutionary payoff and minimization of expected regret are behaviorally equivalent.
+For any precise (Bayesian) and identical belief, maximization of expected (objective) utility and minimization of expected regret are behaviorally equivalent.
 %\citep[e.g.,][]{HalpernPass2012:Iterated-Regret}.
@@
 Here is a simple example that shows these choice mechanisms in action. Consider the
-coordination game in evolutionary payoffs $G$ depicted in figure \ref{coordgame1}. Since the
-game is symmetric, it suffices to specify the payoffs for the row player. Figure
+coordination fitness game $G$ depicted in figure \ref{coordgame1}. Since the
+game is symmetric, it suffices to specify the evolutionary payoffs for the row player. Figure
 \ref{coordgame1} also represents the objective utility $\text{obj}^G$, since
@@
 
-\section{Some Results for the Example Scenario}\label{sec:results}
+\section{Results}\label{sec:results}
 
@@
 
-Since we keep the decision rule fixed, a player's choice mechanism will only depend on the player's subjective representation $ (u,\Gamma) $.
+Since for now we keep the decision rule fixed to maxmin, a player's choice mechanism will only depend on the player's subjective representation $ (u,\Gamma) $.
 For brevity, from now on we will refer to the pair $ (u,\Gamma)$, like $(\text{reg}, \text{imp})$ or $(\text{obj}, \text{prc})$, as the \textit{type} of the player.
-Sometimes we will also name types by referring to the subjective utility, for instance $(\text{reg}, \text{imp})$ and $(\text{reg}, \text{prc})$ are regret types.
-
-As we noticed, meta-games factor in statistical properties of the environment. For particular
+Sometimes we will also distinguish types by referring to the subjective utility only, for instance $(\text{reg}, \text{imp})$ and $(\text{reg}, \text{prc})$ are regret types.
+
+As observed earlier, meta-games factor in statistical properties of the environment. For particular
 empirical purposes, one could consult a specific class of games $\mathcal{G}$ with appropriate,
-maybe empirically informed probabilities $P_{\mathcal{G}}$ in order to match the natural
-environment of a given population. For our purposes, let $\mathcal{G}$ be a set of symmetric
-two-player games with two acts for a start. A game is then individuated solely by its payoff
+maybe empirically informed probability $P_{\mathcal{G}}$ in order to match the natural
+environment of a given population. For our theoretic purposes, let $\mathcal{G}$ be a set of symmetric
+two-player fitness games with two acts for a start. Each game $G \in \mathcal{G}$ is then individuated solely by its payoff
 function, i.e., by a quadruple of numbers $G=(a,b,c,d)$. As for the occurrence probability
@@
 equation~(\ref{eq:FittnessChoiceMechGamePairwise}) to construct meta-game payoffs. Results
-based on $100,000$ randomly sampled games are given in
-table~\ref{tab:ExpectedFitness_4Types}.\footnote{Concretely, $100,000$ games were sampled
+based on $100.000$ randomly sampled games are given in
+table~\ref{tab:ExpectedFitness_4Types}.\footnote{Concretely, $100.000$ games were sampled
   repeatedly by choosing independently four integers between 0 and 10 uniformly at random. For
@@
 \end{tabular}                    
-\caption{Average evolutionary fitness from Monte Carlo simulations of 100,000 symmetric $2 \times 2$ games.}
+\caption{Average evolutionary fitness from Monte Carlo simulations of 100.000 symmetric $2 \times 2$ games.}
 \label{tab:ExpectedFitness_4Types}
@@
 the maxmin strategy, is strictly dominated by the three other types: in each column (i.e.,
-for each kind of co-player), the maxmin strategy is strictly worse than any of the other three
+for each type of co-player), the maxmin strategy is strictly worse than any of the three
 competitors. This has a number of interesting consequences.
@@
 In terms of choice rules, this means that regret
-minimization is evolutionarily better than maxmin, over the class of games considered here.
+minimization is evolutionarily better than maxmin over the class of games considered.
 In terms of subjective preferences, it shows that players using the objective representation that directly looks at fitness (possibly money, or profit) are outperformed by non-veridical (regret) representations, when players' beliefs are imprecise.
@@
 table~\ref{tab:ExpectedFitness_4Types}, $(\text{reg}, \text{imp})$ is no longer evolutionarily
-stable. Rather, given behavioral equivalence (Fact~\ref{fact:equivalence2x2}), types
+stable. Given behavioral equivalence (Fact~\ref{fact:equivalence2x2}), types
 $(\text{reg}, \text{imp})$, $(\text{reg}, \text{prc})$, and $(\text{obj}, \text{prc})$ are all
@@
 $(\text{reg}, \text{imp})$, $(\text{reg}, \text{prc})$ and $(\text{obj}, \text{prc})$. The
-relative proportions of these depend on the initial shares in the population. This variability disappears if
+relative proportions of these depend on the initial shares in the population. This variability fully disappears if
 we add a small mutation rate to the dynamics. Take a fixed, small mutation rate $\epsilon$ for
@@
 
-\begin{corollary} \label{corollary1} If we only consider imprecise belief types, $(\text{obj}, \text{imp})$ and
-  $(\text{reg}, \text{imp})$, and letting $\mathcal{G}$ be as in Proposition~\ref{proposition1}, then the unique evolutionarily stable state is a monomorphic population of
+\begin{corollary} \label{corollary1} Let $\mathcal{G}$ be as in Proposition~\ref{proposition1}. If we only consider imprecise belief types, $(\text{obj}, \text{imp})$ and
+  $(\text{reg}, \text{imp})$, then the unique evolutionarily stable state is a monomorphic population of
   $(\text{reg}, \text{imp})$ players.
@@
 objective preference representations are not necessarily favored by natural selection;
-objective preferences can be outperformed by non-veridical regret preferences, if agents may
+objective preferences are outperformed by non-veridical regret preferences if agents
 have imprecise beliefs.  This tells us that the main conclusions drawn in the previous section
@@
 
-This result presupposes occasional imprecise beliefs and the maximin decision rule (more on
-this below). The assumed imprecise beliefs do not need to be maximally uncertain, however.  Let
-the uncertainty held by a player be defined by a closed and convex set of probabilities
+This result presupposes at least occasional imprecise beliefs. The assumed imprecise beliefs do not need to be maximally uncertain, however.  Let
+the uncertainty held by a player be defined by a convex compact set of probabilities
 $ [s,t] \subseteq \Delta(A) $ over the co-player's actions, where $s$ is the lower probability
@@
 \begin{proposition} \label{proposition2} In the class of $2\times2$ symmetric games generated
-  by i.i.d. drawing of a continuous random variable from a distribution with density $P_v$ with
-  support $(\underline{r},\overline{r})$, for any imprecise
+  by i.i.d. drawing of a continuous random variable from a distribution with density $P_V$ and
+  support $(\underline{r},\overline{r}) \subseteq \mathbb{R}$, for any imprecise
   belief $[s,t]$, the only evolutionarily stable state of a population with regret players
@@
 
-This tells us that regret-based preferences can also outperform objective preference
-representations when agents are capable of learning or otherwise restrict their assumptions
+This tells us that regret-based preferences can outperform objective preference
+representations when agents are also capable of learning or otherwise restrict their assumptions
 about the co-player's behavior as long as there is, at least on occasion, some imprecision in
@@
 representations that have been considered in the literature. Section~\ref{sec:n-times-n} then
-addresses the case of $n \times n$ games for $n \ge 2$. Finally,
+addresses the case of symmetric two-player $n \times n$ games for $n \ge 2$. Finally,
 Section~\ref{sec:solitary-decisions} ends with a brief comparison to the case of solitary
@@
 
-Our claim is not that regret types are the best on the market. We have only compared regret
-types to objective types so far. The space of possible preference types is enormous. Let us
-look at least at two other types of subjective preferences have been investigated, especially
+The space of possible preference types is enormous, and we have only compared regret
+and objective types so far. Let us now
+look at two other types of subjective preferences that have been investigated, especially
 in behavioral economics and in evolutionary game theory. A famous example is the
@@
 }                  
-\caption{Average evolutionary fitness from Monte Carlo simulations of 100,000 symmetric $2 \times 2$ games.}
+\caption{Average evolutionary fitness from Monte Carlo simulations of 100.000 symmetric $2 \times 2$ games.}
 \label{tab:ExpectedFitness_2x2_Full}        
@@
 would like to play against a competitive player. Perhaps more surprisingly, $(\text{alt}, \text{imp})$
-come up strictly dominated by $(\text{com}, \text{imp})$, but competitive types themselves are worse off
+comes up strictly dominated by $(\text{com}, \text{imp})$, but competitive types themselves are worse off
 against all types except against maxmin players $(\text{obj}, \text{imp})$ than any of
@@
 \fi
-It is easy to see then that the previous results still obtain for the larger meta-game in
+It is thus easy to see that the previous results still obtain for the larger meta-game in
 table~\ref{tab:ExpectedFitness_2x2_Full}: $(\text{reg}, \text{imp})$,
@@
 $n \times n$ symmetric games. Concretely, the numbers in table~\ref{tab:ExpectedFitness_10x10}
-are averages of evolutionary payoffs obtained in 100,000 randomly sampled symmetric games,
-where each game was sampled by first picking a number of acts $n \in \set{2, \dots, 10}$
-uniformly at random, and then filling the necessary $n \times n$ payoff matrix with
+are averages of evolutionary payoffs obtained in 100.000 randomly sampled symmetric games,
+where each fitness game $G$ was sampled by first picking a number of acts $n^G \in \set{2, \dots, 10}$
+uniformly at random, and then filling the necessary $n^G \times n^G$ payoff matrix with
 i.i.d.~sampled numbers, as before.
@@
 }                    
-\caption{Average evolutionary fitness for 100,000 randomly generated $n \times n$ symmetric games with $n$ randomly drawn from $\set{2, \dots, 10}$.}
+\caption{Average evolutionary fitness for 100.000 randomly generated $n \times n$ symmetric games with $n$ randomly drawn from $\set{2, \dots, 10}$.}
 \label{tab:ExpectedFitness_10x10}        
@@
 
-On the other hand, there are plenty of ways in which the basic insight from
+On the other hand, there are plenty of ways in which the basic insights from
 Propositions~\ref{proposition1} and \ref{proposition2} can make for situations in which
@@
 of information available in different choice situations), then regret-based preferences can
-again drive out veridical preferences altogether. For example, suppose that only preferences
+again drive out veridical preferences altogether. For example, suppose that only preference representations
 compete and that agents' beliefs are exogenously given, in such a way that both players hold
@@
 beliefs otherwise. This transforms the meta-game from table~\ref{tab:ExpectedFitness_10x10}
-into a simpler $4 \times 4$ meta-game in which the payoff obtained by a subjective utility is
-the weighted average over the payoffs of the subjective representations including that utility
+into a simpler $4 \times 4$ meta-game in which the payoff obtained by a subjective preference is
+the weighted average over the payoffs of the subjective representations including that preference
 in table~\ref{tab:ExpectedFitness_10x10}. Setting $p = 0.98$ for illustration, we get the
@@
 decision problems by selecting, uniformly at random, numbers of states and acts
-$n_w, n_\act \in \set{2, \dots, 10}$ and then filling the utility table, so to speak, by
+$n^{D}_w, n^{D}_\act \in \set{2, \dots, 10}$ and then filling the payoff table, so to speak, by
 i.i.d.~samples for each $\pi^D(w, \act) \in \set{0, 10}$. Unlike with
@@
 uniformly at random from the available states in the current decision problem. Accordingly, the fitness of choice mechanism $c$ in decision problem $D$ is given by:
-$$F_D(c)= \pi^D(w,a_c^*(u^D,\Gamma))\mu(w).$$
+$$F_D(c)= \pi^D(w,a_c^*(u_c^D,\Gamma_c))\overline{\mu}(w),$$ with $ \overline{\mu}(w)= \frac{1}{n_w^D}$ for all $w$.
 As subjective representations,
@@
 relevant fitness measure, defined in equation~(\ref{eq:FittnessChoiceMechSolitary}), was
-approximated by Monte Carlo simulation, the results of which are given in
+approximated by Monte Carlo simulations, the results of which are given in
 table~\ref{tab:SolitaryDecisions}.
@@
 \end{align}
-
 \begin{table}
@@
   \end{tabular}
-  \caption{Expected fitness of choice mechanisms approximated from 100,000 simulated solitary
+  \caption{Expected fitness of choice mechanisms approximated from 100.000 simulated solitary
     decision problems (see main text).}
@@
 \end{table}
-
 Facts~\ref{fact:maxEU-minReg} and \ref{fact:equivalence2x2} still apply:
@@
 utilities outperform objective utilities. Consequently, if there is a chance, however
-small, that agents fall back onto imprecise beliefs, evolution will actually positively select
+small, that agents fall back on imprecise beliefs, evolution will actually positively select
 for non-veridical regret-based preferences.
 
-\subsection{Informed or Sophisticated Beliefs}
-
-Since our main purpose here was to illustrate the potential usefulness of a meta-game approach
-by a comparison of regret and objective preference schemes, we have neglected entirely a very
-important and interesting issue, namely the evolution of ways of forming more concrete beliefs
-about a co-player's likely behavior or the actual state of the world. It is obvious (and shows
-in numerical simulations) that agents whose beliefs are more likely to put more weight on the
-actual world state (in solitary decisions) or on the co-player's actual choice will accrue
-higher fitness-payoffs than radically uncertain players. For reasons of space we must,
+\subsection{Sophisticated Beliefs}
+
+Since one of our main purposes was to illustrate the usefulness of a meta-game approach
+by the case study of objective and regret preferences, we have partially neglected an 
+important and interesting issue, namely the evolution of ways of forming beliefs
+about co-players' behavior or the actual state of the world. For reasons of space we must,
 unfortunately, leave a deeper exploration of belief type evolution to another occasion. Two
 remarks are in order nonetheless. Firstly, belief type evolution can be studied without
-conceptual hurdles in a meta-game approach, so that there is no principled argument here
+conceptual hurdles in the meta-game framework, so that there is no principled argument
 against the main methodological contribution of this paper. Secondly, our results regarding the
-comparison between regret and objective preference types remain to be informative, even if we
-allow agents to learn or reason strategically. This is because we know from
+comparison between regret and objective types remain to be informative, even if we
+allow agents to learn or reason strategically.\footnote{Some research has recently been done along these lines.
+See in particular \cite{RobalinoRobson16,Mengel12,Mohlin12}.} This is because we know from
 Fact~\ref{fact:maxEU-minReg} that regret and objective preferences come up behaviorally
-equivalent when paired with precise probabilistic beliefs (given a maximin decision rule). This
+equivalent when paired with precise probabilistic beliefs (given identical decision rule). This
 holds no matter what the content of that belief is. So, if learning, reasoning or statistical
-knowledge of a recurrent situation \emph{can} be brought to bear, this will not make evolution
+knowledge about a recurrent situation can be brought to bear, this will not make evolution
 select against regret-based preferences. If, on the other hand, agents resort to imprecise
 beliefs at least occasionally (e.g., when they are unaware of the co-player or her utilities,
-or when strategic reasoning cannot reduce all uncertainty about the opponent's choice), then we
+or when strategic reasoning cannot reduce all uncertainty about the co-player's choice), then we
 have shown that there are general and basic circumstances in which regret-based preferences
-could even be favored by natural selected over objective preferences.
+are favored by natural selection over objective preferences.
 
@@
 
-The assumption that players and decision makers maximize their (subjective) preferences is
+The assumption that players and decision makers maximize their (subjective) utility is
 central through all economic literature, and the maximization of actual (objective) payoffs is
@@
 from the actual evolutionary payoffs that can outperform types whose subjective utilities
-coincide with the evolutionary payoffs.  While the literature on evolution of preferences has
+coincide with the evolutionary payoffs.
+Here the claim is not that regret preferences are the best on the market, but rather that utilities that perfectly mirror evolutionary fitness can be outclassed by subjective utilities that differ from the objective fitness.
+While the literature on evolution of preferences has
 focused on fixed games, we have adopted a more general approach here. We suggested that
@@
 
-Meta-games are useful tools for probing into conceptual questions about ecological
-rationality. The approach is rich and general, with many possible further applications
-imaginable beyond the case study presented here. For example, the evolutionary investigation of
-different risk and ambiguity attitudes when competing against each other may bring new insights
-on both behavioral and theoretic decision making under uncertainty, as well as on many issues
-in theoretical biology and behavioral ecology. Moreover, this paper only considered one
-decision rule (maximin), leaving it to future work to explore evolutionary competition here as
-well. Finally, while this paper only used dummy models of diverse decision environments, the
-meta-game approach also allows for empirically informed models of rich and variable
-environments.
+%Meta-games are useful tools for probing into conceptual questions about ecological rationality.
+The approach is rich and general, with many possible further applications imaginable beyond the case study presented here.
+For example, the evolutionary investigation of different risk and ambiguity attitudes when competing against each other may bring new insights on both behavioral and theoretic decision making under uncertainty, as well as on many issues in theoretical biology and behavioral ecology.
+Moreover, this paper only considered one decision rule (maxmin), leaving it to future work to explore evolutionary competition of different rules as well.
+Finally, while this paper only used dummy models of diverse decision environments, the meta-game approach also allows for empirically informed models of rich and variable environments.
 
@@
 \noindent Hence, we can conclude that $R$ strictly dominates $M$ in the class
-$\mathcal{C}\cup\mathcal{A}$. Notice that in case of i.i.d. sampling with infinite support,
+$\mathcal{C}\cup\mathcal{A}$. Notice that in case of i.i.d. sampling with continuous support,
 games in $\mathcal{B} $ and $\mathcal{W} $ never arise, but the proof is the same for the
@@
 $F_{\mathcal{C}\cup\mathcal{A}}(M,M)<F_{\mathcal{C}\cup\mathcal{A}}(R,M)$. As before, notice
-that, when we have i.i.d. sampling with infinite support, games in $\mathcal{W}$ and
+that, when we have i.i.d. sampling with continuous support, games in $\mathcal{W}$ and
 $\mathcal{B}$ never occur, but the proof is the same for all the other cases. Hence, both when
@@
 \end{equation}
-The equivalent of Lemmas \ref{lemma:probabilities coord-ant}, \ref{lemma:probabilities actions coord-ant} and \ref{lemma:action implications} as well as the rest of the proof of Proposition \ref{proposition1} hold also for $a',b',c',d'$.
+Substituting $ a',b',c',d'$ for $a,b,c,d$, Lemmas \ref{lemma:S-B games}, \ref{lemma:W games}, \ref{lemma:probabilities coord-ant}, \ref{lemma:probabilities actions coord-ant} and \ref{lemma:action implications} as well as the rest of the proof of Proposition \ref{proposition1} hold unchanged.
 \hfill $\dashv$

### 2016-06-30 paper/rev1_paperBlinded.tex
paper revision micha final edits

@@
 response to this and adding to recent like-minded approaches, this paper introduces a general
-\emph{meta-game} model that conservatively extends the scope of evolutionary game theory to deal with
-evolutionary selection of choice mechanisms in variable environments \citep[see also][]{Harley1981:Learning-the-Ev,ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o,OConnor2016:Evolving-to-Gen,RayoBecker07,Zollman2008,SkyrmsZollman10,BednarPage07}.\footnote{In particular, similar ideas appear in \citep{RayoBecker07,Zollman2008,BednarPage07}.
-\citep{BednarPage07} use a multi-game framework, composed of a fixed selection of six possible games, to study the emergence of different cultural behaviors, and model agents as finite-state automata playing games from the fixed selection.
-\citep{Zollman2008} explains seemingly ``irrational'' fair behavior in social dilemmas (like the Ultimatum game) by means of a model where agents have to play the Ultimatum game together with the Nash bargaining game, but they are constrained to choose the same strategy for both games.
-Finally, \citep{RayoBecker07} consider, in a more decision-theoretic setting, what subjective utility function a cognitively limited agent should be endowed with in order to maximize her evolutionary fitness.
-Our framework can then be viewed as a generalization of those models, mainly in that here players do not suffer any cognitive constraint, and we allow for larger and possibly variable classes of games.}
+\emph{meta-game} model that conservatively extends the scope of evolutionary game theory to
+deal with evolutionary selection of choice mechanisms in variable environments \citep[see
+also][]{Harley1981:Learning-the-Ev,ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o,OConnor2016:Evolving-to-Gen,RayoBecker07,Zollman2008,SkyrmsZollman10,BednarPage07}.\footnote{Some
+  of these contributions are very closely related to ours. \citet{BednarPage07} use a
+  multi-game framework, composed of a fixed selection of six possible games, to study the
+  emergence of different cultural behaviors, and model agents as finite-state automata playing
+  games from the fixed selection. \citet{Zollman2008} explains seemingly ``irrational'' fair
+  behavior in social dilemmas (like the Ultimatum game) by means of a model where agents have
+  to play the Ultimatum game together with the Nash bargaining game, but they are constrained
+  to choose the same strategy for both games. Finally, \citet{RayoBecker07} consider, in a more
+  decision-theoretic setting, what subjective utility function a cognitively limited agent
+  should be endowed with in order to maximize her evolutionary fitness. Our framework can then
+  be viewed as a generalization of those models, mainly in that here players do not necessarily
+  have any specific cognitive limitations, and we allow for larger and possibly variable
+  classes of games.}
 
@@
 \citep[e.g.,][]{gardsah82,levi74,walley96}, faithful and objective representations in terms of
-true, real evolutionary fitness can be outperformed by subjective (e.g., regret-based)
+true evolutionary fitness can be outperformed by subjective (e.g., regret-based)
 preference representations that deviate from the true fitness that natural selection operates
@@
 The paper is organized as follows. Section \ref{sec:rati--subj} sets the scene by reviewing
-different perspectives on rational choice. Section~\ref{sec:subj-ut,bel,dec-rules}
-introduces the meta-game approach. In doing so, it covers key notions such as choice mechanisms,
-decision rules and subjective representations, all with an eye towards the evolutionary applications
-of Section~\ref{sec:model}. Section~\ref{sec:results} contains
-the main results, and Section \ref{sec:extensions} discusses some
-interesting extensions. Finally, Section~\ref{sec:conclusion} concludes.
+different perspectives on rational choice. Section~\ref{sec:subj-ut,bel,dec-rules} introduces
+the meta-game approach. In doing so, it covers key notions such as choice mechanisms, decision
+rules and subjective representations, all with an eye towards the evolutionary application of
+Section~\ref{sec:model}. Section~\ref{sec:results} contains the main results for that
+application, and Section \ref{sec:extensions} discusses some interesting extensions. Finally,
+Section~\ref{sec:conclusion} concludes.
 
@@
 \citep[e.g.,][]{Anderson1991:Is-human-cognit,ChaterOaksford2000:The-Rational-An,HagenChater2012:Decision-Making}. Adaptationism
-aims to explain rational behavior by appealing to evolutionary considerations: DMs have acquired
-choice mechanisms that have proved to be adaptive with respect to the variable environment
-where they have evolved. A choice mechanism can be a set of distinct heuristics (the DM's
-\emph{adaptive toolbox}) that have little in common
+aims to explain rational behavior by appealing to evolutionary considerations: DMs have
+acquired choice mechanisms that have proved to be adaptive with respect to the variable
+environment where they have evolved. A choice mechanism can be a set of distinct heuristics
+(the DM's \emph{adaptive toolbox}) that have little in common
 \citep[e.g.,][]{TverskyKahnemann1981:The-Framing-of-,GigerenzerGoldstein1996:Reasoning-the-F,ScheibehenneRieskamp2013:Testing-the-Ada}. But
 to closely relate to the literature on evolution of preferences and to the philosophical debate
-about the nature of rational choice, we here suggest to think of a choice mechanism
-as a map from choice situations to action choices which includes an explicit level of subjective representation of the situation.
-Specifically, a \emph{subjective representation} is a general way of forming preferences and beliefs about the choice situation, and we
-are most interested in the question which subjective representations, and which choice mechanisms in general, are better than others
-from an evolutionary point of view.
+about the nature of rational choice, we here suggest to think of a choice mechanism as a map
+from choice situations to action choices which includes an explicit level of subjective
+representation of the situation. Specifically, a \emph{subjective representation} is a general
+way of forming preferences and beliefs about the choice situation. We are most interested in
+the question which subjective representations, and which choice mechanisms in general, are
+better than others from an evolutionary point of view.
 
@@
 
-We view a choice mechanism as the combination of three different things: a \textit{subjective utility} (or preference), a \textit{subjective belief} and a \textit{decision rule}.
-In general, the agent's action choice will depend both on the agent's utility at different possible outcomes of the choice situation and on the agent's beliefs about the realization of these outcomes.
-The decision rule then combines the agent's subjective utility and belief, and dictates how the agent should act in case of a choice situation whose consequences are uncertain.
-Therefore, a decision rule is a function that associates an action choice with the agent's utility and beliefs:
+We view a choice mechanism as the combination of three different things: a \textit{subjective
+  utility} (or preference), a \textit{subjective belief} and a \textit{decision rule}. In
+general, the agent's action choice will depend both on the agent's utility at different
+possible outcomes of the choice situation and on the agent's beliefs about the realization of
+these outcomes. The decision rule then combines the agent's subjective utility and belief, and
+dictates how the agent should act: a decision rule is a function that associates an action
+choice with the agent's utility and beliefs:
 $$ \text{Decision Rule: Utility }\times\text{ Beliefs } \rightarrow \text{ Actions.}  $$
@@
 It is worth noticing that both maxmin and maximax boil down to expected utility maximization
-when the set $\Gamma$ is a singleton, and in turn expected utility maximization reduces to
+when the set $\Gamma$ is a singleton, and in turn expected utility maximization reduces to the
 Laplace rule when the belief $\mu$ is a uniform probability over the states.
@@
 As mentioned previously, for a choice mechanism to prescribe an action, the decision rule needs
-to be given a specific utility $u$ and belief $\Gamma$ as input. We call the pair $(u,\Gamma)$ a \textit{subjective
-  representation} of the decision problem. In the following, we investigate the evolutionary fitness of general and systematic ways of
-forming such subjective representations across many different decision situations.
+to be given a specific utility $u$ and belief $\Gamma$ as input. We call the pair $(u,\Gamma)$
+a \textit{subjective representation} of the decision situation. In the following, we investigate
+the evolutionary fitness of general and systematic ways of forming such subjective
+representations across many different decision situations.
 
@@
 
-However, studying the fitness and the evolutionary selection of different choice mechanisms by
-the use of a fixed, single game may look like a rather restrictive perspective and possibly
-biased by the choice of the particular game. To avoid these limitations, we consider a
-\textit{class} of possible games. Towards this end, fix a class $\mathcal{G}$ of possible two-player symmetric games,
-together with a probability measure $P_{\mathcal{G}}(G)$ for the occurrence probability of game
+Going beyond a single fixed fitness game, we consider a \textit{class} of possible games. For
+concreteness, let $\mathcal{G}$ be a class of two-player symmetric games, together with a
+probability measure $P_{\mathcal{G}}(G)$ for the occurrence probability of game
 $G \in \mathcal{G}$. Intuitively, the probability $P_{\mathcal{G}}$ encodes the statistical
@@
 mechanisms, $\mathcal{G}$ is a class of possible games, $P_{\mathcal{G}}(G)$ is the probability
-of game $G$ to occur, and $F:CM \times CM \rightarrow \mathbb{R}$ is the (meta-)fitness function,
-defined as:
+of game $G$ to occur, and $F:CM \times CM \rightarrow \mathbb{R}$ is the (meta-)fitness
+function, defined as:
 \begin{align}
@@
 contrast, others have argued against the obligation of representing a belief by means of a
-single probability measure, opposite to the Bayesian paradigm (e.g., \cite{GilbMarin13}). They argue
-instead in favor of a more encompassing account, according to which uncertainty can be \emph{unmeasurable},
-and represented by a (convex and compact) set of probabilities (e.g., \cite{gilsch89}). This line of thought has been
-originated in decision theory by the famous Ellsberg's paradoxes \citep{ells61}, and appears extremely
-relevant in game-theoretic contexts too. Indeed, in a recent paper \citet{BattCerrMM15}
-write:
+single probability measure, opposite to the Bayesian paradigm (e.g., \cite{GilbMarin13}). They
+argue instead in favor of a more encompassing account, according to which uncertainty can be
+\emph{unmeasurable}, and represented by a (convex and compact) set of probabilities (e.g.,
+\cite{gilsch89}). This line of thought has its origin in decision theory, motivated by
+Ellsberg's famous paradoxes \citep{ells61}, and appears extremely relevant in game-theoretic
+contexts too. Indeed, in a recent paper \citet{BattCerrMM15} write:
 
@@
 
-As for the decision rule, we assume that players use the maxmin rule. This is in line with many representation
-results of decision making under unmeasurable uncertainty \citep[e.g.,][]{gilsch89,GhirMar02},
-and seems corroborated by empirical findings too.
-Ellsberg's paradoxes are prominent examples (\citet{ells61}), and evidence from experimental literature suggests that agents are generally averse to unmeasurable uncertainty \citep[e.g.,][]{TrautKuil16}.
-
-Finally, note that when the maxmin rule acts on subjective representation (obj, imp), the
-generated behavior corresponds to the classic maxmin strategy \citep{neumorg44}. When the maxmin rule acts on
-subjective representation (reg, imp), the agent's behavior is known as \textit{regret
+As for the decision rule, we assume that players use the maxmin rule. This is in line with many
+representation results of decision making under unmeasurable uncertainty
+\citep[e.g.,][]{gilsch89,GhirMar02}, and seems corroborated by empirical findings
+too. Ellsberg's paradoxes are prominent examples \citep{ells61}, and evidence from experimental
+literature suggests that agents are generally averse to unmeasurable uncertainty
+\citep[e.g.,][]{TrautKuil16}.
+
+Finally, note that when the maxmin rule acts on subjective representations of type (obj, imp),
+i.e., objective preferences and imprecise beliefs, the generated behavior corresponds to the
+classic maxmin strategy \citep{neumorg44}. When the maxmin rule acts on subjective
+representation (reg, imp), the agent's behavior is known as \textit{regret
   minimization}.\footnote{The notion of regret in decision theory dates back at least to the
@@
   \citet{HalpernPass2012:Iterated-Regret} showed how the use of regret minimization can give
-  solutions to game-theoretic puzzles (like the Traveller's dilemma and the Centipede game)
-  in a way that is closer to everyday intuition and empirical data. In this paper the notion of
+  solutions to game-theoretic puzzles (like the Traveller's dilemma and the Centipede game) in
+  a way that is closer to everyday intuition and empirical data. In this paper the notion of
   regret defined earlier is the same as in \citet{HalpernPass2012:Iterated-Regret}.} Two facts
-stem from these observations.  The first is related to our focus on different types of
+follow from these observations.  The first is related to our focus on different types of
 uncertainty that players may entertain.
@@
 %  by the maximization of expected utility for the negative regret transformation of $G$
-For any precise (Bayesian) and identical belief, maximization of expected (objective) utility and minimization of expected regret are behaviorally equivalent.
-%\citep[e.g.,][]{HalpernPass2012:Iterated-Regret}.
+  For any precise (Bayesian) belief $\mu$, maximization of expected (objective) utility based
+  on $\mu$ and minimization of expected regret based on $\mu$ are behaviorally
+  equivalent. %\citep[e.g.,][]{HalpernPass2012:Iterated-Regret}.
 \end{fact}
-\noindent The second fact highlights another behavioral equivalence, which we will make use of shortly in the following section.
+\noindent The second fact highlights another behavioral equivalence, which we will make use of
+shortly in the following section.
 \begin{fact} \label{fact:equivalence2x2} In the class of $2 \times 2$ symmetric games, the acts
-  selected by Laplace rule are exactly the acts selected by regret minimization.
+  selected by the Laplace rule are exactly the acts selected by regret minimization.
 \end{fact}
@@
 maybe empirically informed probability $P_{\mathcal{G}}$ in order to match the natural
-environment of a given population. For our theoretic purposes, let $\mathcal{G}$ be a set of symmetric
+environment of a given population. For our present purposes, let $\mathcal{G}$ be a set of symmetric
 two-player fitness games with two acts for a start. Each game $G \in \mathcal{G}$ is then individuated solely by its payoff
@@
 and $t$ is the upper probability of action $II$.  We can then prove the following proposition,
-which is the equivalent of Proposition~\ref{proposition1} for any possible (not necessarily
+which is the analogue of Proposition~\ref{proposition1} for any possible (not necessarily
 maximal) degree of uncertainty $[s,t]$, with $s \neq t$. There is only one difference: we are
@@
 This tells us that regret-based preferences can outperform objective preference
-representations when agents are also capable of learning or otherwise restrict their assumptions
+representations when agents are also capable of learning or otherwise restricting their assumptions
 about the co-player's behavior as long as there is, at least on occasion, some imprecision in
@@
 
-Since one of our main purposes was to illustrate the usefulness of a meta-game approach
-by the case study of objective and regret preferences, we have partially neglected an 
-important and interesting issue, namely the evolution of ways of forming beliefs
-about co-players' behavior or the actual state of the world. For reasons of space we must,
-unfortunately, leave a deeper exploration of belief type evolution to another occasion. Two
-remarks are in order nonetheless. Firstly, belief type evolution can be studied without
-conceptual hurdles in the meta-game framework, so that there is no principled argument
-against the main methodological contribution of this paper. Secondly, our results regarding the
-comparison between regret and objective types remain to be informative, even if we
-allow agents to learn or reason strategically.\footnote{Some research has recently been done along these lines.
-See in particular \cite{RobalinoRobson16,Mengel12,Mohlin12}.} This is because we know from
+Since one of our main purposes was to illustrate the usefulness of a meta-game approach by the
+case study of objective and regret preferences, we have partially neglected an important and
+interesting issue, namely the evolution of ways of forming beliefs about co-players' behavior
+or the actual state of the world. For reasons of space we must, unfortunately, leave a deeper
+exploration of belief type evolution to another occasion. Two remarks are in order
+nonetheless. Firstly, belief type evolution can be studied without conceptual hurdles in the
+meta-game framework, so that there is no principled argument against the main methodological
+contribution of this paper. Secondly, our results regarding the comparison between regret and
+objective types remain to be informative, even if we allow agents to learn or reason
+strategically.\footnote{Some research has recently been done along these lines. See in
+  particular \cite{RobalinoRobson16,Mengel12,Mohlin12}.} This is because we know from
 Fact~\ref{fact:maxEU-minReg} that regret and objective preferences come up behaviorally
@@
 beliefs at least occasionally (e.g., when they are unaware of the co-player or her utilities,
-or when strategic reasoning cannot reduce all uncertainty about the co-player's choice), then we
-have shown that there are general and basic circumstances in which regret-based preferences
-are favored by natural selection over objective preferences.
+or when strategic reasoning cannot reduce all uncertainty about the co-player's choice), then
+regret-based preferences can be favored by natural selection over objective preferences.
 
@@
 
-The assumption that players and decision makers maximize their (subjective) utility is
-central through all economic literature, and the maximization of actual (objective) payoffs is
+The assumption that players and decision makers maximize their (subjective) utility is central
+through in the economics literature, and the maximization of actual (objective) payoffs is
 often justified by appealing to evolutionary arguments and natural selection. In contrast to
@@
 from the actual evolutionary payoffs that can outperform types whose subjective utilities
-coincide with the evolutionary payoffs.
-Here the claim is not that regret preferences are the best on the market, but rather that utilities that perfectly mirror evolutionary fitness can be outclassed by subjective utilities that differ from the objective fitness.
-While the literature on evolution of preferences has
-focused on fixed games, we have adopted a more general approach here. We suggested that
-attention to “meta-games” is crucial, because what may be a good subjective representation in
-one type of game (e.g., cooperative preferences in the Prisoner’s Dilemma class) need not be
-generally beneficial. Taken together, we presented a variety of plausible circumstances in
-which evolutionary competition between choice mechanisms on a larger class of games can favor
-non-veridical preference representations focusing on regret.
+coincide with the evolutionary payoffs. The claim is not that regret preferences are the best
+on the market, but rather that utilities that perfectly mirror evolutionary fitness can be
+outclassed by subjective utilities that differ from the objective fitness.  While the
+literature on evolution of preferences has focused on fixed games, we have adopted a more
+general approach here. We suggested that attention to “meta-games” is crucial, because what may
+be a good subjective representation in one type of game (e.g., cooperative preferences in the
+Prisoner’s Dilemma class) need not be generally beneficial. Taken together, we presented a
+variety of plausible circumstances in which evolutionary competition between choice mechanisms
+on a larger class of games can favor non-veridical preference representations focusing on
+regret.
 

### 2016-09-23 paper/PoS_paper_final.tex
Final version

--- 2016-06-30 paper/rev1_paperBlinded.tex
@@
 
-\usepackage{geometry}
+%\usepackage{geometry}
  % \geometry{
@@
 % paper size, margins, etc:
-\usepackage{geometry}
-\geometry{verbose,letterpaper,tmargin=1.5in,bmargin=1.5in,lmargin=1.25in,rmargin=1in}
+\usepackage[top=4cm, bottom=4cm, left=3cm, right=2.5cm]{geometry}
+%\geometry{verbose,letterpaper,tmargin=1.5in,bmargin=1.5in,lmargin=1.25in,rmargin=1in}
 
@@
 
+\title{Smart Representations: {R}ationality and Evolution in a Richer  Environment}
+\author{Paolo Galeazzi $^{1}$ and Michael Franke $^{2}$\\
+{\footnotesize
+$^{1}$ ILLC, University of Amsterdam, The Netherlands; email: pagale87@gmail.com}\\
+{\footnotesize
+$^{2}$ Department of Linguistics, University of T\"{u}bingen, Germany; email: mchfranke@gmail.com}
+}
+\date{}
+
 \begin{document}
-
+\begin{titlepage}
 \maketitle
@@
 \end{abstract}
+
+\footnotetext{The research of Paolo Galeazzi leading to these results
+  has received funding from the European Research Council under the
+  European Community’s Seventh Framework Programme (FP7/2007-2013)/ERC
+  Grant agreement No. 283963. Michael Franke’s work was supported by
+  the Institutional Strategy of the University of T\"{u}bingen (DFG,
+  ZUK 63). The authors are also grateful to Gerhard J{\"a}ger for
+  funding this work. We want to thank all the participants in
+  Decisions, Games and Logic ’15 workshop at London School of
+  Economics, in LogiCIC workshop 2014 at the University of Amsterdam,
+  and in Bridges 2 workshop at Rutgers University for the valuable
+  feedback. Special thanks go to Pierpaolo Battigalli, Massimo
+  Marinacci, Valerio Nispi Landi, Tommaso Orlando, Eric Pacuit, Erik
+  Quaeghebeur, Rasmus Rendsvig, Teddy Seidenfeld, Peter Wakker, and
+  Kevin Zollman for their attention and comments. We are also grateful
+for the helpful comments we received by two anonymous reviewers.}
+
+\end{titlepage}
 
@@
 also][]{Harley1981:Learning-the-Ev,ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o,OConnor2016:Evolving-to-Gen,RayoBecker07,Zollman2008,SkyrmsZollman10,BednarPage07}.\footnote{Some
-  of these contributions are very closely related to ours. \citet{BednarPage07} use a
+  of these contributions are closely related to ours. \citet{BednarPage07} use a
   multi-game framework, composed of a fixed selection of six possible games, to study the
@@
 concreteness, let $\mathcal{G}$ be a class of two-player symmetric games, together with a
-probability measure $P_{\mathcal{G}}(G)$ for the occurrence probability of game
-$G \in \mathcal{G}$. Intuitively, the probability $P_{\mathcal{G}}$ encodes the statistical
+probability measure $P_G(G')$ for the occurrence probability of game
+$G' \in \mathcal{G}$. Intuitively, the probability $P_G$ encodes the statistical
 properties of the environment. A \textit{meta-game} is then a tuple
-$ MG=\langle CM, \mathcal{G}, P_{\mathcal{G}},F \rangle$, where $CM$ is a set of choice
-mechanisms, $\mathcal{G}$ is a class of possible games, $P_{\mathcal{G}}(G)$ is the probability
-of game $G$ to occur, and $F:CM \times CM \rightarrow \mathbb{R}$ is the (meta-)fitness
+$ MG=\langle CM, \mathcal{G}, P_G,F \rangle$, where $CM$ is a set of choice
+mechanisms, $\mathcal{G}$ is a class of possible games, $P_G(G')$ is the probability
+of game $G'$ to occur, and $F:CM \times CM \rightarrow \mathbb{R}$ is the (meta-)fitness
 function, defined as:
@@
   \label{eq:FittnessChoiceMechGamePairwise}
-  F(c, c') = \int P_{\mathcal{G}}(G) \  F_G(c,c') \text{ d} G \,.
+  F(c, c') = \int  F_G(c,c') \text{ d} P_G(G) \,.
 \end{align}
@@
   \label{eq:FittnessChoiceMechGame}
-  F(c) = \int P_{M}(c') \ F(c,c') \text{ d} c' = \int \int P_{\mathcal{G}}(G) \  P_{M}(c') \  F_G(c,c') \text{ d} c' \text{ d} G  \,,
+  F(c) = \int F(c,c') \text{ d} P_{c}(c') = \int \int   F_G(c,c') \text{ d} P_c(c') \text{ d} P_G(G)  \,,
 \end{align}
-where $P_{M}(c')$ is the probability of
+where $P_c(c')$ is the probability of
 encountering a co-player with choice mechanism $c'$.
@@
 Ellsberg's famous paradoxes \citep{ells61}, and appears extremely relevant in game-theoretic
-contexts too. Indeed, in a recent paper \citet{BattCerrMM15} write:
-
-\begin{quote}
-  Such [unmeasurable] uncertainty is inherent in situations of strategic interaction. This is quite obvious
-  when such situations have been faced only a few times. (p.~646)
-\end{quote}
-
-\noindent In evolutionary game theory, for instance, players obviously face uncertainty
+contexts too. Indeed, in a recent paper \citet{BattCerrMM15} write: ``Such [unmeasurable] uncertainty is inherent in situations of strategic interaction. This is quite obvious
+  when such situations have been faced only a few times.''
+
+In evolutionary game theory, for instance, players obviously face uncertainty
 about the composition of the population that they are part of, and consequently about the (type of)
@@
 empirical purposes, one could consult a specific class of games $\mathcal{G}$ with appropriate,
-maybe empirically informed probability $P_{\mathcal{G}}$ in order to match the natural
+maybe empirically informed probability $P_G$ in order to match the natural
 environment of a given population. For our present purposes, let $\mathcal{G}$ be a set of symmetric
@@
 function, i.e., by a quadruple of numbers $G=(a,b,c,d)$. As for the occurrence probability
-$P_{\mathcal{G}}(G)$ of game $G$, we imagine that the values $a,b,c,d$ are i.i.d.~random
+$P_G(G)$ of game $G$, we imagine that the values $a,b,c,d$ are i.i.d.~random
 variables sampled from the set $ \lbrace 0, \dots, 10 \rbrace$ according to uniform probability
@@
 maximal) degree of uncertainty $[s,t]$, with $s \neq t$. There is only one difference: we are
-now going to require i.i.d. drawing of a \emph{continuous} random variable. This is due to the
-fact that, for arbitrarily small intervals $[s,t]$, objective players $([s,t],\text{obj})$ and
-regret players $([s,t],\text{reg})$ can behave as holding a unique probability measure (precise
+now going to require i.i.d. drawing of a \emph{continuous} random variable with uniform distribution. This is due to the
+fact that, for arbitrarily small intervals $[s,t]$, objective players $(\text{obj},[s,t])$ and
+regret players $(\text{reg},[s,t])$ can behave as holding a unique probability measure (precise
 belief) if the underlying payoff space is not dense. The reason for this technical requirement
@@
 
-\begin{proposition} \label{proposition2} In the class of $2\times2$ symmetric games generated
-  by i.i.d. drawing of a continuous random variable from a distribution with density $P_V$ and
-  support $(\underline{r},\overline{r}) \subseteq \mathbb{R}$, for any imprecise
-  belief $[s,t]$, the only evolutionarily stable state of a population with regret players
-  $([s,t],\text{reg})$ and objective players $([s,t],\text{obj})$ is a monomorphic state of
-  $([s,t],\text{reg})$ players.
+\begin{proposition} \label{proposition2} Let $\mathcal{G}$ be the class of symmetric $2\times2$ games generated
+  by i.i.d. drawing of a continuous random variable with uniform distribution over any set of values, and fix any imprecise
+  belief $[s,t]$. Then the only evolutionarily stable state of a population with regret players
+  $(\text{reg},[s,t])$ and objective players $(\text{obj},[s,t])$ is a monomorphic state of
+  $(\text{reg},[s,t])$ players.
 \end{proposition}
@@
 \begin{enumerate}
-\item \textit{altruistic} utility: for all $G \in \mathcal{G}$, $\text{alt}^G(a,a') = \pi^G(a,a') + \pi^G(a',a)$;\footnote{A
+\item \textit{altruistic} utility: for all $G \in \mathcal{G}$, $\text{alt}^G(a,a') = \pi^G(a,a') + \pi^G(a',a)$;
+\item \textit{competitive} utility: for all $G \in \mathcal{G}$, $\text{com}^G(a,a') = \pi^G(a,a') - \pi^G(a',a)$.\footnote{A
     more general formulation would be to define $ \alpha$-altruistic utility, for
@@
     $ u^G_\alpha(a, a')=\pi^G(a,a') + \alpha \pi^G(a',a)$. Since we are not
-    interested in the evolution of degrees of altruism, here we simply fix $ \alpha = 1 $. Analogously for $\alpha$-competitive utilities too.}
-\item \textit{competitive} utility: for all $G \in \mathcal{G}$, $\text{com}^G(a,a') = \pi^G(a,a') - \pi^G(a',a)$.
+    interested in the evolution of degrees of altruism, here we simply fix $ \alpha = 1 $.
+Analogously for $\alpha$-competitive utilities too.
+Other possible generalizations could also take into account combinations of all these preferences with different decision rules.
+Maximax, minimax and minimin, for example, would be possible rules for choice.
+Here we opted for maxmin because we were specifically interested in comparing maxmin and regret minimization, as these are two major alternatives for decision making.}
 \end{enumerate}
@@
   \label{eq:FittnessChoiceMechSolitary}
-  F(c) = \int P_{\mathcal{D}}(D) \  F_D(c) \text{ d} D 
+  F(c) = \int  F_D(c) \text{ d} P_{D}(D) 
 \end{align}
@@
 
-Since one of our main purposes was to illustrate the usefulness of a meta-game approach by the
-case study of objective and regret preferences, we have partially neglected an important and
-interesting issue, namely the evolution of ways of forming beliefs about co-players' behavior
-or the actual state of the world. For reasons of space we must, unfortunately, leave a deeper
-exploration of belief type evolution to another occasion. Two remarks are in order
-nonetheless. Firstly, belief type evolution can be studied without conceptual hurdles in the
-meta-game framework, so that there is no principled argument against the main methodological
-contribution of this paper. Secondly, our results regarding the comparison between regret and
-objective types remain to be informative, even if we allow agents to learn or reason
-strategically.\footnote{Some research has recently been done along these lines. See in
-  particular \cite{RobalinoRobson16,Mengel12,Mohlin12}.} This is because we know from
+Since one of our main purposes was to illustrate the usefulness of a meta-game approach
+by the case study of objective and regret preferences, we have partially neglected an 
+important and interesting issue, namely the evolution of ways of forming beliefs
+about co-players' behavior or the actual state of the world. For reasons of space we must,
+unfortunately, leave a deeper exploration of belief type evolution to another occasion. Two
+remarks are in order nonetheless. Firstly, belief type evolution can be studied without
+conceptual hurdles in the meta-game framework, so that there is no principled argument
+against the main methodological contribution of this paper. Secondly, our results regarding the
+comparison between regret and objective types remain to be informative, even if we
+allow agents to learn or reason strategically.\footnote{Some research has recently been done along these lines.
+See in particular \cite{RobalinoRobson16,Mengel12,Mohlin12}.} This is because we know from
 Fact~\ref{fact:maxEU-minReg} that regret and objective preferences come up behaviorally
@@
 beliefs at least occasionally (e.g., when they are unaware of the co-player or her utilities,
-or when strategic reasoning cannot reduce all uncertainty about the co-player's choice), then
-regret-based preferences can be favored by natural selection over objective preferences.
+or when strategic reasoning cannot reduce all uncertainty about the co-player's choice), then regret-based preferences
+can be favored by natural selection over objective preferences.
 
@@
 
-The assumption that players and decision makers maximize their (subjective) utility is central
-through in the economics literature, and the maximization of actual (objective) payoffs is
+The assumption that players and decision makers maximize their (subjective) utility is
+central through all economic literature, and the maximization of actual (objective) payoffs is
 often justified by appealing to evolutionary arguments and natural selection. In contrast to
@@
 from the actual evolutionary payoffs that can outperform types whose subjective utilities
-coincide with the evolutionary payoffs. The claim is not that regret preferences are the best
-on the market, but rather that utilities that perfectly mirror evolutionary fitness can be
-outclassed by subjective utilities that differ from the objective fitness.  While the
-literature on evolution of preferences has focused on fixed games, we have adopted a more
-general approach here. We suggested that attention to “meta-games” is crucial, because what may
-be a good subjective representation in one type of game (e.g., cooperative preferences in the
-Prisoner’s Dilemma class) need not be generally beneficial. Taken together, we presented a
-variety of plausible circumstances in which evolutionary competition between choice mechanisms
-on a larger class of games can favor non-veridical preference representations focusing on
-regret.
+coincide with the evolutionary payoffs.
+Here the claim is not that regret preferences are the best on the market, but rather that utilities that perfectly mirror evolutionary fitness can be outclassed by subjective utilities that differ from the objective fitness.
+While the literature on evolution of preferences has
+focused on fixed games, we have adopted a more general approach here. We suggested that
+attention to “meta-games” is crucial, because what may be a good subjective representation in
+one type of game (e.g., cooperative preferences in the Prisoner’s Dilemma) need not be
+generally beneficial. 
+%Taken together, we presented a variety of plausible circumstances in which evolutionary competition between choice mechanisms on a larger class of games can favor non-veridical preference representations focusing on regret.
 
@@
 Finally, while this paper only used dummy models of diverse decision environments, the meta-game approach also allows for empirically informed models of rich and variable environments.
+
+\newpage
 
@@
 \begin{align*}
-  & \textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) + P(I_{RC}\cap II_{RC})) + b_{C} \cdot
-  (P(I_{RC}\cap II_{RC}) + P(I_{RC}\cap I_{RC})) \\ 
-  & \ \ + c_{C} \cdot (P(II_{RC}\cap I_{RC})
-  +P(II_{RC}\cap II_{RC})) + d_{C} \cdot (P(II_{RC}\cap II_{RC})+P(II_{RC}\cap I_{RC}))] \\
-  > & 
-  \textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot P(I_{RC}\cap I_{MC}) + b_{C} \cdot P(I_{RC}\cap I_{MC}) +
-  c_{C} \cdot (P(I_{RC}\cap II_{MC})+P(II_{RC}\cap II_{MC})) \\ 
-  & \ \ \ \ + d_{C} \cdot (P(II_{RC}\cap
-  II_{MC})+P(I_{RC}\cap II_{MC}))]
-\end{align*}
-Rewrite:
-\begin{align*}
   & \textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) + P(I_{RC}\cap II_{RC})-
@@
 \begin{align*}
-& \textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) + P(I_{RC}\cap II_{RC})) + b_{C} \cdot  (P(I_{RC}\cap II_{RC}) + P(I_{RC}\cap I_{RC}))\\
-& \ \ \ \ + c_{C} \cdot (P(II_{RC}\cap I_{RC}) +P(II_{RC}\cap II_{RC})- P(I_{RC}\cap II_{MC})- P(II_{RC}\cap II_{MC}))\\
-& \ \ \ \ + d_{C} \cdot (P(II_{RC}\cap II_{RC})+P(II_{RC}\cap I_{RC})- P(II_{RC}\cap II_{MC})- P(I_{RC}\cap II_{MC}))]> 0
-\end{align*}
-that is
-\begin{align*}
 \textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot (\frac{1}{4}+\frac{1}{4}) + b_{C} \cdot  (\frac{1}{4}+\frac{1}{4}) + c_{C} \cdot (\frac{1}{4}+\frac{1}{4}-\frac{1}{2}-\frac{1}{2}) + d_{C} \cdot (\frac{1}{4}+\frac{1}{4}-\frac{1}{2}-\frac{1}{2})]> 0
@@
 Hence, whenever $a_{C}>d_{C}$ and (2) obtain, it also holds that $P(II_{RC}\cap II_{MC})=P(II_{RC} \cap II_{RC})$.
-In this case we can simplify:
-\begin{align*}
-& \textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) - P(I_{RC}\cap I_{MC})) + b_{C} \cdot  (P(I_{RC}\cap I_{RC})- P(I_{RC}\cap I_{MC})) \\
-& \ \ \ \ + c_{C} \cdot (P(II_{RC}\cap II_{RC})- P(I_{RC}\cap II_{MC})- P(II_{RC}\cap II_{MC})) \\
-& \ \ \ \ + d_{C} \cdot (P(II_{RC}\cap II_{RC})- P(II_{RC}\cap II_{MC})- P(I_{RC}\cap II_{MC}))]> 0
-\end{align*}
-\begin{align*}
-\textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot P(I_{RC}\cap II_{MC}) + b_{C} \cdot  P(I_{RC}\cap II_{MC}) \\- c_{C} \cdot P(I_{RC}\cap II_{MC}) - d_{C} \cdot P(I_{RC}\cap II_{MC})]> 0
-\end{align*}
+In this case we can simplify to:
 \begin{align*}
@@
 \noindent Hence, we can conclude that $R$ strictly dominates $M$ in the class
-$\mathcal{C}\cup\mathcal{A}$. Notice that in case of i.i.d. sampling with continuous support,
-games in $\mathcal{B} $ and $\mathcal{W} $ never arise, but the proof is the same for the
-remaining games in $\mathcal{S}$, $\mathcal{C} $ and $\mathcal{A}$.
+$\mathcal{C}\cup\mathcal{A}$.
 
@@
 \end{align*}
-\noindent When $a>d$, similarly to the above derivation, we get: 
-\begin{align*} & \textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot (P(I_{MC}\cap I_{MC}) + P(I_{MC}\cap II_{MC})- P(I_{RC}\cap I_{MC}) - P(I_{RC}\cap II_{MC}))\\ & + b_{C} \cdot  (P(I_{MC}\cap I_{MC}) + P(I_{MC}\cap II_{MC})- P(I_{RC}\cap I_{MC}) - P(I_{RC}\cap II_{MC}))\\ & + c_{C} \cdot (P(II_{MC}\cap I_{MC}) +P(II_{MC}\cap II_{MC})- P(II_{RC}\cap II_{MC})) \\ & + d_{C} \cdot (P(II_{MC}\cap II_{MC})+P(II_{MC}\cap I_{MC})- P(II_{RC}\cap II_{MC}))]< 0
-\end{align*}
-\noindent We now distinguish between (1) $b=c$, (2) $b>c$, and (3) $b<c$. Notice that either
+\noindent Similarly to the above derivation, we consider $a>d$ first, and we now distinguish between (1) $b=c$, (2) $b>c$, and (3) $b<c$. Notice that either
 (1) or (2), together with $a>d$, implies $I_{RC}$. Then we obtain:\footnote{Note that here, when
@@
 \noindent Finally, we can conclude that
-$F_{\mathcal{C}\cup\mathcal{A}}(M,M)<F_{\mathcal{C}\cup\mathcal{A}}(R,M)$. As before, notice
-that, when we have i.i.d. sampling with continuous support, games in $\mathcal{W}$ and
-$\mathcal{B}$ never occur, but the proof is the same for all the other cases. Hence, both when
-the support of $a,b,c,d$ is finite, and when the support is infinite, $R$ strictly dominates
-$M$ under the conditions assumed. \hfill $\dashv$
+$F_{\mathcal{C}\cup\mathcal{A}}(M,M)<F_{\mathcal{C}\cup\mathcal{A}}(R,M)$.
+
+When we have i.i.d. sampling with continuous support, games in $\mathcal{W}$ and
+$\mathcal{B}$ never occur, and the proof for the other cases reduces to the proof of Proposition \ref{proposition2} for $s=0$ and $t=1$. \hfill $\dashv$
 
@@
 
-\noindent \textbf{Proof of Proposition \ref{proposition2}.} Take an arbitrary real interval $(\underline{r},\overline{r})$, where
-$\underline{r}$ is the infimum and $\overline{r}$ is the supremum,
-and let $P$ be the PDF over $(\underline{r},\overline{r})$. Given
-Lemma \ref{lemma:probabilities coord-ant}, we focus on the case of coordination games. Now fix a set
-of probabilities $[s,t]$, corresponding to the uncertainty of the
-players about the co-player's action. As we have seen, objective and
-regret types will behave exactly the same when $s=t$ and $[s,t]$
-reduces to a single probability. Notice that objective and regret
-will also be indistinguishable when there is no game such that $s<\frac{a-c}{a-c+d-b}<t$.
-It is then a necessary condition for regret types to be better than
-objective types that the two types behave differently at least in
-some games. Geometrically, the ratio $\frac{a-c}{a-c+d-b}$ denotes
-the intersection point of the lines corresponding to action $I$ and
-action $II$ (figure~\ref{fig:graphstrictinf1-2})
-\begin{figure}
-\centering\begin{tikzpicture}[scale=.9]
-
-%
-\draw [-, very thick]  (0,0) to (5,0);
-%
-\draw [-, very thick] (0,0) to (0,5);
-
-%
-\draw [-, very thick] (5,0) to (5,5);
-
-%
-\node (zero) [] at (-.75,-.5) {$P(II)=0$};
-
-%
-\node (s) [] at (2,0)
-  [label=below:{$s$}] {|};
-%
-\node (t) [] at (4,0)
-  [label=below:{$t$}] {|};
-%
-%\node (st) [] at (3,0)
- % [label=below:{$s + \nicefrac{\epsilon}{2}$}] {};
-
-\draw [dashed] (2,0) -- (2,5);
-\draw [dashed] (4,0) -- (4,5);
-
-\draw [dotted] (3,0) -- (3,5);
-
-%
-\node (a') [] at (1.8,2.6)
-  [label=left:{}] {$a'$};
-\node (c') [] at (2.2,2)
-  [label=left:{}] {$c'$};
-\node (d') [] at (4.2,4)
-  [label=left:{}] {$d'$};
-\node (b') [] at (4.2,2.6)
-  [label=left:{}] {$b'$};
-
-%
-\node (0y) [] at (0,0)
-  [label=left:{$c$}] {};
-\node (1y) [] at (0,1)
-  [label=left:{}] {-};
-\node (2y) [] at (0,2)
-  [label=above right:{$I$}] [label=left:{$a$}] {-};
-
-\node (3y) [] at (0,3)
-  [label=left:{}] {-};
-\node (4y) [] at (0,4)
-  [label=left:{}] {-};
-\node (5y) [] at (0,5)
-  [label=left:{}] {-};
-%
-\node (1yy) [] at (5,1)
-  [label=left:{}] {-};
-\node (2yy) [] at (5,2)
-  [label=left:{}] {-};
-
-\node (3yy) [] at (5,3)
-  [label=right:{$b$}] {-};
-\node (4yy) [] at (5,4)
-  [label=left:{}] {-};
-\node (5yy) [] at (5,5)
-  [label=left:{$II$}] [label=right:{$d$}] {-};
-%
-
-\node (p1) [] at (5,0)
-  [label=below:{$1$}] {};
-
-%
-
-%
-\draw [-, very thick] (0,2) to (5,3);
-%
-\draw [-, very thick] (0,0) to (5,5);
-%
-
-\draw[decorate,decoration={brace,amplitude=10}](5,5)--(5,3)node [black,midway,xshift=25pt] {\footnotesize $d-b$};
-%
-\draw[decorate,decoration={brace,amplitude=10}](0,0)--(0,2)node [black,midway,xshift=-25pt] {\footnotesize $a-c$};
-%
-
-\end{tikzpicture}\protect\caption{Example of strictly informative coordination game.}
-\label{fig:graphstrictinf1-2}
-\end{figure}
-. If there is no game where such an intersection point falls into
-the interval $[s',t']$, for some $s'\neq t'$, then whenever players
-hold the set of probabilities $[s',t']$ they will perceive any game
-that can arise as having a dominant action, i.e., as a strong dominance
-game in partition cell $\mathcal{S}$. Note also that the ratio $\frac{a-c}{a-c+d-b}$
-takes values in the interval $(0,1)$, since to get $\frac{a-c}{a-c+d-b}=0$
-we shall have $a=c$ and for $\frac{a-c}{a-c+d-b}=1$ we need $d=b$,
-which have no probability of occurrence for continuous random variables.
-Furthermore, the ratio $\frac{a-c}{a-c+d-b}$ is dense in $(0,1)$,
-and consequently in any interval $[s,t]\subset(0,1)$. Indeed, for
-any rational number $\frac{m}{n}\in[s,t]$, we can always find $a,b,c,d\in(\underline{r},\overline{r})$
-such that $\frac{a-c}{a-c+d-b}=\frac{m}{n}$ as follows. It is not
-difficult to see that for this to be the case we must have 
-\[
-a-(a-b)\frac{m}{n}=c+(d-c)\frac{m}{n}.
-\]
-This equation reduces to
-\begin{equation}
-\frac{n-m}{n}a+\frac{m}{n}b=\frac{n-m}{n}c+\frac{m}{n}d,\label{eq:hit the point}
-\end{equation}
-which is an equality between two convex combinations with the same
-weights $\frac{n-m}{n}$ and $\frac{m}{n}$. Then, whatever $a,b\in(\underline{r},\overline{r})$
-we pick it is always possible to find (infinitely many) $c,d\in(a,b)\subset(\underline{r},\overline{r})$
-such that equation (\ref{eq:hit the point}) is satisfied. Indeed,
-for any $x\in(0,1)$ we have that $c=(\frac{n-m}{n}a+\frac{m}{n}b)x+a(1-x)$
-and $d=(\frac{n-m}{n}a+\frac{m}{n}b)x+b(1-x)$ satisfy equation (\ref{eq:hit the point}).
-This shows that for any rational number $\frac{m}{n}\in[s,t]$ we
-can always find $c,d\in(a,b)\subset(\underline{r},\overline{r})$
-such that $\frac{a-c}{a-c+d-b}=\frac{m}{n}$, and so we can always
-find $a,b,c,d\in(\underline{r},\overline{r})$ such that $\frac{a-c}{a-c+d-b}=\frac{m}{n}$.
-Since rational numbers are dense in $\mathbb{R}$, they are also dense
-in any real interval $[s,t]\subset(0,1)$. Hence, the ratio $\frac{a-c}{a-c+d-b}$
-is dense in $[s,t]$.
-
-Once we have proven the density of $\frac{a-c}{a-c+d-b}$ for coordination
-games $G=(a,b,c,d)$ in any real interval $[s,t]\subset(0,1)$, the
-rest of the proof is connected to the proof of Proposition \ref{proposition1}. Specifically,
-for a given interval $[s,t]$ we define
+\noindent \textbf{Proof of Proposition \ref{proposition2}.} 
+As shown in Figure~\ref{subfig:coord-game-I-II-1-1}, given a game
+$(a,b,c,d)$, action $I$ corresponds to the line $a+(b-a)x$, while
+action $II$ corresponds to the line $c+(d-c)x$. The slope of action
+$I$ is then $(b-a)$, and the slope of action $II$ is $(d-c)$.
+Action $I$ is steeper than action $II$ if $|b-a|>|d-c|$, and action
+$II$ is steeper than action $I$ if the reverse of the last inequality
+holds. Given a belief $\Gamma=[s,t]$, let us define
 \begin{equation}
@@
 \end{equation}
-Substituting $ a',b',c',d'$ for $a,b,c,d$, Lemmas \ref{lemma:S-B games}, \ref{lemma:W games}, \ref{lemma:probabilities coord-ant}, \ref{lemma:probabilities actions coord-ant} and \ref{lemma:action implications} as well as the rest of the proof of Proposition \ref{proposition1} hold unchanged.
-\hfill $\dashv$
+Next, type $R$ is indifferent between the two acts if $\frac{c-a}{c-a+b-d}-s=t-\frac{c-a}{c-a+b-d}$,
+and prefers $I$ over $II$ if $\frac{c-a}{c-a+b-d}-s<t-\frac{c-a}{c-a+b-d}$.
+For succinctness, let us abbreviate $Z:=c-a+b-d$. Whenever $|d-c|>|b-a|$
+and $\frac{c-a}{Z}-s\leq t-\frac{c-a}{Z}$, it is the case that $a'>d'$,
+so that $M$ prefers $I$ over $II$. Indeed, when $s=t=\frac{c-a}{Z}$,
+we have that $a'=d'=\frac{cb-ad}{Z}$. When we enlarge the interval
+$\Gamma$ by moving $s$ to the left of $\frac{c-a}{Z}$ and $t$
+to the right of $\frac{c-a}{Z}$ by the same extent, such that $\frac{c-a}{Z}-s=t-\frac{c-a}{Z}$,
+we get that $a'>d'$, since $a'$ moved by $(a-b)(\frac{c-a}{Z}-s)$
+while $d'$ moved by $(d-c)(t-\frac{c-a}{Z})$. Consequently, in a
+game where action $II$ is steeper than action $I$, the only possible
+way in which the two types can differ is $M$ playing $I$ and $R$
+playing $II$, since we will never observe $M$ playing $II$ and
+$R$ playing $I$ in such games. By a similar argument, when action
+$I$ is steeper than action $II$, the only possible way in which
+the two types can differ is $M$ playing $II$ and $R$ playing $I$.
+Hence, whenever one of the actions is steeper than the other, the
+two types can differ in only one of the two possible ways. Finally,
+when action $I$ and action $II$ are equally steep, $|d-c|=|b-a|$,
+then one type strictly prefers one action if and only if the other
+type does too. We say that a game is \emph{relevant} if the two types
+play different actions.
+
+Since the two cases are symmetric, consider the case $|d-c|>|b-a|$.
+Suppose that $c$ and $d$ have been drawn such that $c<d$. For $|d-c|>|b-a|$
+to hold, the game has to be a coordination game, otherwise we would
+have $b>d$ and $c>a$, so $|d-c|<|b-a|$.
+
+If the game is a coordination game, the two types choose differently
+if and only if
+\[
+s<\frac{c-a}{Z}<\frac{s+t}{2}
+\]
+and
+\[
+b'>c'.
+\]
+Consider all the points $P\in(s,\frac{s+t}{2})$. Each of these points
+can be expressed as a linear combination:
+\[
+\frac{ks+(n-k)t}{n},
+\]
+for $k>\frac{n}{2}$. By simple algebra, for each point in $P\in(s,\frac{s+t}{2})$
+and $c<d$, the point 
+\[
+c+\frac{ks+(n-k)t}{n}(d-c)
+\]
+expresses the expected value of action $II$ for $P=\frac{ks+(n-k)t}{n}$,
+i.e., it is the $y$-value of the line corresponding to action $II$
+when $x=\frac{ks+(n-k)t}{n}$. Then, given a two-dimensional point
+$(x_{0},y_{0})$, the sheaf of lines passing through that point is
+defined by all the equations 
+\[
+y-y_{0}=m(x-x_{0})
+\]
+for $m\in\mathbb{R}$. (The vertical line $m=\infty$ is excluded
+from the sheaf, but it is not relevant for the proof.) Consequently,
+given the two-dimensional point 
+\[
+\left(\frac{ks+(n-k)t}{n},\, c+\frac{ks+(n-k)t}{n}(d-c)\right),
+\]
+the sheaf of lines passing through that point is defined by the set
+of equations, for $m\in\mathbb{R}$: 
+\[
+y=m\left(x-\frac{ks+(n-k)t}{n}\right)+c+\frac{ks+(n-k)t}{n}(d-c).
+\]
+If, for each equation in the set, we define 
+\begin{equation}
+\begin{array}{cc}
+a^{\diamond}:= & m\left(-\frac{ks+(n-k)t}{n}\right)+c+\frac{ks+(n-k)t}{n}(d-c)\\
+b^{\diamond}:= & m\left(1-\frac{ks+(n-k)t}{n}\right)+c+\frac{ks+(n-k)t}{n}(d-c)
+\end{array}\label{eq:a-b-1}
+\end{equation}
+then each equation corresponds to a possible game\medskip{}
+
+\hfill{}%
+\begin{tabular}{|c|c|c|}
+\cline{2-3} 
+\multicolumn{1}{c|}{} & $I$ & $II$\tabularnewline
+\hline 
+$I$ & $a^{\diamond}$ & $b^{\diamond}$\tabularnewline
+\hline 
+$II$ & $c$ & $d$\tabularnewline
+\hline 
+\end{tabular}\hfill{}
+
+\medskip{}
+such that
+\[
+\frac{c-a^{\diamond}}{c-a^{\diamond}+b^{\diamond}-d}=\frac{ks+(n-k)t}{n}.
+\]
+By algebraic computations, the condition $d-c>|a^{\diamond}-b^{\diamond}|$
+is equivalent to 
+\[
+|m|<d-c.
+\]
+Moreover, among the coordination games such that $d-c>|a^{\diamond}-b^{\diamond}|$,
+the relevant ones are those that also satisfy $b'>c'$, otherwise
+type $M$ would not (strictly) prefer $I$ over $II$. If we rewrite
+$a',b',c',d'$ as in equation~\ref{eq:a'b'c'd'}, then the inequality
+$b'>c'$ reduces to 
+\[
+m\left(\frac{k}{k-n}\right)<d-c.
+\]
+
+By symmetric arguments, whenever $c>d$, the only possible relevant
+games for the same interval $[s,t]$ are anti-coordination games for
+which 
+\[
+\frac{s+t}{2}<\frac{c-a}{Z}<t,
+\]
+and such that $c-d>|a-b|$, and that $a'>d'$. Similarly, for $k<\frac{n}{2}$,
+these correspond to all games 
+\[
+y=m\left(x-\frac{ks+(n-k)t}{n}\right)+c+\frac{ks+(n-k)t}{n}(d-c)
+\]
+such that 
+\[
+|m|<c-d
+\]
+and 
+\[
+m\left(\frac{k-n}{k}\right)>d-c.
+\]
+
+Consider now the following bijective function $\psi:\mathcal{C}\rightarrow\mathcal{A}$
+between coordination and anti-coordination games, that, for $d>c$,
+associates the coordination game 
+\[
+y=m\left(x-\frac{ks+(n-k)t}{n}\right)+c+\frac{ks+(n-k)t}{n}(d-c)
+\]
+with the anti-coordination game
+\[
+y=-m\left(x-\frac{(n-k)s+kt}{n}\right)+d+\frac{(n-k)s+kt}{n}(c-d).
+\]
+Essentially, $\psi$ changes $c$ to $d$, $m$ to $-m$, and $k$
+to $n-k$. In particular, note that $\psi$ is a bijection that, for
+a fixed interval $[s,t]$, sends relevant coordination games to relevant
+anti-coordination games. Figure~\ref{fig:games-eq-I-II-1-1} gives
+a graphical example of the bijection.
+\begin{figure}
+
+\begin{subfigure}[b]{0.3\textwidth}
+\begin{tikzpicture}[scale=0.85]
+
+%
+\draw [-, very thick]  (0,0) to (5,0);
+%
+\draw [-, very thick] (0,0) to (0,5);
+
+%
+\draw [-, very thick] (5,0) to (5,5);
+
+%
+\node (zero) [] at (-.95,-.5) {$P(II)=0$};
+
+%
+%\node (s) [] at (1,0)[label=below:{$s$}] {|};
+%
+\node (s) [] at (1.5,0)
+  [label=below:{$\frac{3s+t}{4}$}] {|};
+%
+%\node (t) [] at (3,0) [label=below:{$\overline{\lambda}$}] {|};
+%
+%\node (st) [] at (3,0)
+ % [label=below:{$s + \nicefrac{\epsilon}{2}$}] {};
+
+\draw [dashed] (1,0) -- (1,5);
+\draw [dashed] (3,0) -- (3,5);
+
+\draw [dotted] (2,0) -- (2,5);
+
+%
+\node (0y) [] at (0,0)
+  [label=left:{}] {};
+\node (1y) [] at (0,1)
+  [label=left:{}] {$\bullet$};
+\node (2y) [] at (0,2)
+   [label=left:{$c$}] {$\bullet$};
+
+\node (3y) [] at (0,3)
+  [label=right:{$I$}] {$\bullet$};
+\node (4y) [] at (0,4)
+  [label=left:{}] [label=below right:{}] {$\bullet$};
+\node (5y) [] at (0,5)
+  [label=left:{}] {$\bullet$};
+%
+\node (1yy) [] at (5,1)
+  [label=left:{}] {$\bullet$};
+\node (2yy) [] at (5,2)
+  [label=right:{}] {$\bullet$};
+
+\node (3yy) [] at (5,3)
+  [label=right:{}] {$\bullet$};
+\node (4yy) [] at (5,4)
+   {$\bullet$};
+\node (5yy) [] at (5,5)
+  [label=left:{$II$}] [label=right:{$d$}] {$\bullet$};
+%
+
+\node (p1) [] at (5,0)
+  [label=below:{$1$}] {};
+
+%
+\node (4y) [] at (-.5,2.6)
+  [label=left:{}] [label=below right:{}] {$a^{\diamond}$};
+\node (4y) [] at (5.6,3.6)
+  [label=left:{}] [label=below right:{}] {$b^{\diamond}$};
+
+%
+\draw [-, very thick] (0,2.6) to (5,3.6);
+%
+\draw [-, very thick] (0,2) to (5,5);
+%
+
+\end{tikzpicture}
+\caption{Game $G$.}
+\label{subfig:coord-game-I-II-1-1}
+\end{subfigure}
+\hspace{3cm}
+\begin{subfigure}[b]{0.3\textwidth}
+\begin{tikzpicture}[scale=.85]
+
+%
+\draw [-, very thick]  (8,0) to (13,0);
+%
+\draw [-, very thick] (8,0) to (8,5);
+
+%
+\draw [-, very thick] (13,0) to (13,5);
+%
+
+%
+%\node (s2) [] at (9,0) [label=below:{$\underline{\lambda}$}] {|};
+%
+\node (s2) [] at (10.5,0)
+  [label=below:{$\frac{s+3t}{4}$}] {|};
+%
+%\node (st2) [] at (11,0)
+ % [label=below:{$s + \nicefrac{\epsilon}{2}$}] {};
+%
+%\node (t2) [] at (11,0) [label=below:{$\overline{\lambda}$}] {|};
+%
+
+\draw [dashed] (9,0) -- (9,5);
+\draw [dashed] (11,0) -- (11,5);
+
+\draw [dotted] (10,0) -- (10,5);
+
+\node (zero2) [] at (8,0)
+  [label=below:{$0$}] {};
+\node (0yy2) [] at (13,1)
+  [label=right:{}] {};
+
+%
+\node (0y2) [] at (8,0)
+  [label=left:{}] {};
+\node (1y2) [] at (8,1)
+  [label=left:{}] {$\bullet$};
+\node (2y2) [] at (8,2)
+  [label=left:{}] {$\bullet$};
+
+\node (3y2) [] at (8,3) {$\bullet$};
+
+\node (4y2) [] at (8,4)
+  [label=right:{}] [label=left:{$\psi(a^{\diamond})$}] {$\bullet$};
+\node (5y2) [] at (8,5) 
+[label=right:{$II$}] [label=left:{$\psi(d)$}] {$\bullet$};
+%
+\node (1yy2) [] at (13,1)
+  [label=right:{}] {$\bullet$};
+\node (2yy2) [] at (13,2)
+  [label=right:{$\psi(c)$}] {$\bullet$};
+\node (2yy2) [] at (13,3)
+ [label=right:{$\psi(b^{\diamond})$}] {$\bullet$};
+
+\node (4yy2) [] at (13,4)
+  [label=below left:{$I$}] {$\bullet$};
+\node (5yy2) [] at (13,5)
+  [label=left:{}] {$\bullet$};
+%
+
+\node (p12) [] at (13,0)
+  [label=below:{$1$}] {};
+
+%
+\draw [-, very thick] (8,4) to (13,3);
+%
+\draw [-, very thick] (8,5) to (13,2);
+%
+
+\end{tikzpicture}
+\caption{Game $\psi(G)$.}
+\label{subfig:ant-game-I-II-1-1}
+\end{subfigure}
+\protect\caption{Examples of coordination game $C$ and corresponding anti-coordination
+game $\psi(C)$.}
+\label{fig:games-eq-I-II-1-1}
+
+\end{figure}
+
+We can then pair these two games and consider the average fitness
+in $\{C,\psi(C)\}$ of $(\text{reg},[s,t])$ against $(\text{reg},[s,t])$, and then compare it to the
+fitness of $(\text{obj},[s,t])$ against $(\text{reg},[s,t])$, denoted respectively by $M$ and $R$ henceforth. In the pair of relevant games $C$ and
+$\psi(C)$, $R$ strictly dominates $M$ if 
+\[
+F_{\{C,\psi(C)\}}(R,R)>F_{\{C,\psi(C)\}}(M,R)
+\]
+and
+\[
+F_{\{C,\psi(C)\}}(R,M)>F_{\{C,\psi(C)\}}(M,M).
+\]
+Consider the first inequality. Since both $C$ and $\psi(C)$ are
+relevant with respect to the interval $[s,t]$, it implies that $F_{\{C,\psi(C)\}}(R,R)=d+c$,
+and $F_{\{C,\psi(C)\}}(M,R)=b^{\diamond}+\psi(b^{\diamond})$. Therefore,
+the first inequality is equivalent to 
+\[
+\frac{d+c}{2}>\frac{b^{\diamond}+\psi(b^{\diamond})}{2},
+\]
+which can be spelled out as
+\[
+\begin{array}{ccc}
+d+c & > & m\left(1-\frac{ks+(n-k)t}{n}\right)+c+\frac{ks+(n-k)t}{n}(d-c)\\
+ & - & m\left(1-\frac{(n-k)s+kt}{n}\right)+d+\frac{(n-k)s+kt}{n}(c-d)
+\end{array}
+\]
+After some computations, the previous inequality boils down to
+\[
+d-c>m,
+\]
+which we know it is the case, since we have seen that the condition
+$d-c>|a^{\diamond}-b^{\diamond}|$ is equivalent to $d-c>|m|$.
+
+Finally, from the previous argument it follows that, for any given
+interval $[s,t]$, if we consider the set of all relevant coordination
+games, let's denote it by $\mathcal{C}^{r}$, and the set of all relevant
+anti-coordination games $\mathcal{A}^{r}$, then it holds that
+\[
+F_{\{\mathcal{C}^{r}\cup\mathcal{A}^{r}\}}(R,R)>F_{\{\mathcal{C}^{r}\cup\mathcal{A}^{r}\}}(M,R).
+\]
+Let us now check that the second inequality for $R$ to strictly dominate
+$M$ also holds. In $\{C,\psi(C)\}$, that is equivalent to 
+\[
+d+c>a^{\diamond}+\psi(a^{\diamond}),
+\]
+which amounts to $m<d-c$. As before, it then follows that 
+\[
+F_{\{\mathcal{C}^{r}\cup\mathcal{A}^{r}\}}(R,M)>F_{\{\mathcal{C}^{r}\cup\mathcal{A}^{r}\}}(M,M).
+\]
+Therefore, $R$ strictly dominates $M$. \hfill $\dashv$
 
